### 2022-08-30 draft/ms-adj-draft.Rmd
initial setup

---
output:
  # bookdown::word_document2:
    # reference_docx: "word-template.docx"
  bookdown::pdf_document2:
    toc: no
    number_sections: no
    pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
    latex_engine: xelatex
always_allow_html: true
header-includes:
  #- \usepackage{setspace}\doublespace
  # - \usepackage[nolists, fighead, tabhead]{endfloat}
  # - \usepackage{endnotes}
  # - \let\footnote=\endnote
#- \setlength{\headheight}{14.5pt}
#- \setlength{\headheight}{13.6pt}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \lhead{N.I. Hoffmann}
- \rhead{`r format(Sys.time(), '%B %e, %Y')`}
# - \newcommand{\beginsupplement}{\setcounter{table}{0}  
# \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} 
# \renewcommand{\thefigure}{A\arabic{figure}}}

editor_options: 
  chunk_output_type: console

citeproc: no
fontfamily: mathpazo
# fontsize: 12pt
geometry: margin=1in
indent: yes
link-citations: yes
linkcolor: blue
lang: 'en-US'

bibliography: "/Users/nathan/Documents/My Library.bib" 
# bibliography: "My Library.bib"  
csl: apa.csl
# csl: american-sociological-association.csl

title: "Comparing Advanced Adjustment Methods on Clustered Education Data"
subtitle: "Statistics MS Thesis"
author:  Nathan I. Hoffmann
#   | Department of Sociology, UCLA
date: "`r format(Sys.time(), '%B %e, %Y')`"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T)
options("yaml.eval.expr" = TRUE)

library(haven)
library(tidyverse)

knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})

options("yaml.eval.expr" = TRUE, scipen = 3, digits = 2)

uclablue = '#2774AE'
gray = '#808080'
black = '#000000'
ucla_palette = c(black, uclablue, gray)

# theme_set(theme_cowplot(font_family = 'Palatino') + 
theme_set(theme_classic(base_family = 'Palatino') + 
      theme(legend.title=element_blank(), 
         panel.grid.major.y = element_line('grey80'),
         legend.background = element_rect(fill = alpha("white", 0.5))
         ))
ggplot <- function(...) ggplot2::ggplot(...) + 
  scale_color_brewer(palette="Dark2") +
  scale_fill_brewer(palette="Dark2")

kable <- function(...) knitr::kable(..., format.args = list(big.mark = ","))
```

```{r load}
# data from mx0.5
pisa <- readRDS(here('data', 'pisa.rds'))

pisa <- pisa %>%
  filter(across(c(female,  mom_ed, dad_ed, early_ed, cultural_pos, home_ed, age),
                ~ !is.na(.x))) %>%
  mutate(
    country = case_when(
       country == '034400' ~ 'Hong Kong',
       country == '044600'~ 'Macao',
       country == 'Russian Federation' ~ 'Russia',
       country == 'United States of America' ~ 'United States',
       T ~ country
     ),
   birth_country = case_when(
       birth_country == '034400' ~ 'Hong Kong',
       birth_country == '044600'~ 'Macao',
       birth_country == 'United States of America' ~ 'United States',
       T ~ birth_country
     ),
   immigrant = case_when(
    birth_country != country ~ T,
    birth_country == country ~ F
    )) %>%
  # include immigrants with a birth country in the dataset, or non-immigrants
  filter((immigrant == T & birth_country %in% unique(pisa$country)) | 
           immigrant == F) %>%
   mutate(school_id = paste0(year, school_id),
         village = school_location == 'Village',
         non_urban = ifelse(!is.na(school_location), school_location %in% c('Village', 'Small Town', 'Town'), NA),
         match_country = ifelse(immigrant == T, birth_country, country))

# Include only match_country with at least 5 imm and 5 non-imm
n_min <- 5
match_country_imm <- pisa %>%
  filter(immigrant == T) %>%
  group_by(match_country) %>%
  count() %>% 
  filter(n >= n_min) %>%
  pull(match_country)

match_country_nonimm <- pisa %>%
  filter(immigrant == F) %>%
  group_by(match_country) %>%
  count() %>% 
  filter(n >= n_min) %>%
  pull(match_country)

pisa <- pisa %>%
  filter(match_country %in% match_country_imm,
         match_country %in% match_country_nonimm,
         # Remove match_country with no immigrants
         match_country %in% unique(pisa$match_country[pisa$immigrant == T])
         )
```

This thesis aims to compare different advanced adjustment methods.

\newpage

# References

### 2022-09-16 draft/ms-adj-draft.Rmd
test
intro

@@
 
-title: "Comparing Advanced Adjustment Methods on Clustered Education Data"
+title: "Comparing Flexible Adjustment Methods for Causal Inference on Nested Survey Data"
 subtitle: "Statistics MS Thesis"
@@
 
+library(broom)
+library(knitr)
 library(haven)
@@
 # data from mx0.5
-pisa <- readRDS(here('data', 'pisa.rds'))
+pisa <- readRDS('/Users/nathan/Google Drive/1 UCLA/Dissertation/diss-prop/data/pisa.rds') %>%
+  mutate(age = as.numeric(age))
 
 pisa <- pisa %>%
-  filter(across(c(female,  mom_ed, dad_ed, early_ed, cultural_pos, home_ed, age),
+  filter(across(c(female,  mom_ed, dad_ed, early_ed, cultural_pos, home_ed, age,
+                  math1, math2, math3, math4, math5,
+                  read1, read2, read3, read4, read5,
+                  scie1, scie2, scie3, scie4, scie5),
                 ~ !is.na(.x))) %>%
@@
          match_country %in% unique(pisa$match_country[pisa$immigrant == T])
-         )
+         ) %>%
+  mutate(immigrant = as.numeric(immigrant))
 ```
 
+# Abstract
+
 This thesis aims to compare different advanced adjustment methods.
+It will compare Imben & Rubins propensity matching, stabilized IPWs, TMLE, double machine learning (Chernozhukov et al 2018), Ratkovic (2021), and BART.
+
+# Introduction
+
+Statistical methods for flexible covariate adjustment in causal inference have proliferated in recent years.
+These methods have a number of strengths over traditional regression methods: They make few functional form assumptions, easily handle large numbers of covariates, and produce interpretable treatment effect estimates.
+Despite their advantages, these methods remain underutilized by social scientists.
+Part of the barrier has been lack of familiarity with these methods, with few introductions existing.
+There has also been little guidance regarding which method is appropriate for particular types of data.
+
+This paper makes advances on both of these fronts.
+First, it is a guide to some of the latest methods in flexible covariate adjustment, explaining the methods to a social scientist audience.
+Second, it compares these methods using a type of data that social scientists frequently encounter, but on which these methods have been rarely applied: nested survey data.
+It does this by using both simulated data where the treatment effect estimate is known, and then using real-world complex survey data from the Program for International Student Assessment (PISA).
+
+After presenting OLS regression as a baseline, the paper covers Targeted Maximum Likelihood Estimation, double machine learning (Chernozhukov et al 2018), PLCE (Ratkovic 2022), and BART.
+
+# Overview of Techniques
+
+# Preliminary Findings
+
+```{r test-sample}
+
+set.seed(185)
+pisa_test <- bind_rows(
+  pisa %>%
+    filter(match_country == 'Albania', immigrant == T) %>%
+    select(math1, immigrant, mom_ed, dad_ed,
+                          female, early_ed, cultural_pos, home_ed, age) ,
+    #sample_n(200),
+  pisa %>%
+    filter(match_country == 'Albania', immigrant == F) %>%
+        select(math1, immigrant, mom_ed, dad_ed,
+                          female, early_ed, cultural_pos, home_ed, age) 
+    #sample_n(200)
+  )
+
+# pisa_test <- pisa %>%
+#     filter(match_country == 'Albania') %>%
+#  select(math1, immigrant, mom_ed, dad_ed,
+#                          female, early_ed, cultural_pos, home_ed, age)
+
+#  filter(match_country %in% c('Portugal', 'Germany', 'United States'))
+```
+
+```{r tmle, eval = F}
+# Y = outcome
+# A = binary treatment
+# W = covariates
+
+tmle_out <- with(pisa_test, tmle::tmle(
+                Y = math1,
+                A = as.logical(immigrant),
+                W = select(pisa_test, mom_ed, dad_ed, 
+                          female, early_ed, cultural_pos, home_ed, age),
+                verbose = T))
+tmle_out
+
+# pisa %>%
+#  count(match_country, immigrant) %>% View()
+#   arrange(desc(n))
+
+```
+
+```{r dml, eval = F}
+dml_data <- DoubleML::DoubleMLData$new(as.data.frame(pisa_test),
+                y_col = 'math1',
+                d_cols = 'immigrant',
+                x_cols = c('mom_ed', 'dad_ed', 'female', 'early_ed', 
+                'cultural_pos', 'home_ed', 'age'))
+
+library(mlr3)
+library(mlr3learners)
+# surpress messages from mlr3 package during fitting
+lgr::get_logger("mlr3")$set_threshold("warn")
+
+learner = lrn("regr.ranger", num.trees=500, 
+              max.depth=5, min.node.size=2)
+ml_g = learner$clone()
+ml_m = learner$clone()
+
+set.seed(185)
+
+obj_dml_plr = DoubleML::DoubleMLPLR$new(dml_data, ml_g=ml_g, ml_m=ml_m)
+obj_dml_plr$fit()
+print(obj_dml_plr)
+```
+
+```{r plce, eval = F}
+plce_out <- with(pisa_test, PLCE::plce(
+                y = math1,
+                treat = immigrant,
+                X = as.matrix(select(pisa_test, mom_ed, dad_ed, #early_ed,
+                          female, cultural_pos, home_ed, age))))
+
+```
+
+```{r bart}
+set.seed(159)
+bart_out <- bartCause::bartc(
+  response = pisa_test$math1,
+  treatment = pisa_test$immigrant,
+  confounders = as.data.frame(select(pisa_test, mom_ed, dad_ed,
+                          female, early_ed, cultural_pos, home_ed, age))
+  )
+
+summary(bart_out)
+
+# sensitivity analysis:
+# Dorie et al., Statistics in Medicine, 2016
+# treatSens (CRAN) -- use BART option
+```
 

### 2022-10-03 draft/ms-adj-draft.Rmd
first PAA abstract draft

@@
 #- \setlength{\headheight}{13.6pt}
-- \usepackage{fancyhdr}
-- \pagestyle{fancy}
-- \lhead{N.I. Hoffmann}
-- \rhead{`r format(Sys.time(), '%B %e, %Y')`}
+# - \usepackage{fancyhdr}
+# - \pagestyle{fancy}
+# - \lhead{N.I. Hoffmann}
+# - \rhead{`r format(Sys.time(), '%B %e, %Y')`}
 # - \newcommand{\beginsupplement}{\setcounter{table}{0}  
@@
 fontfamily: mathpazo
-# fontsize: 12pt
-geometry: margin=1in
+#fontsize: 11pt
+geometry: margin=.6in
 indent: yes
@@
 
-title: "Comparing Flexible Adjustment Methods for Causal Inference on Nested Survey Data"
-subtitle: "Statistics MS Thesis"
-author:  Nathan I. Hoffmann
-#   | Department of Sociology, UCLA
-date: "`r format(Sys.time(), '%B %e, %Y')`"
+# title: "Comparing Flexible Adjustment Methods for Causal Inference on Nested Survey Data"
+# subtitle: "Statistics MS Thesis"
+# author:  Nathan I. Hoffmann
+# #   | Department of Sociology, UCLA
+# date: "`r format(Sys.time(), '%B %e, %Y')`"
 
@@
 library(knitr)
+library(here)
 library(haven)
@@
 
-# Abstract
+<!-- # Abstract -->
 
-This thesis aims to compare different advanced adjustment methods.
+<!-- This thesis aims to compare different advanced adjustment methods.
 It will compare Imben & Rubins propensity matching, stabilized IPWs, TMLE, double machine learning (Chernozhukov et al 2018), Ratkovic (2021), and BART.
+-->
 
@@
 Statistical methods for flexible covariate adjustment in causal inference have proliferated in recent years.
-These methods have a number of strengths over traditional regression methods: They make few functional form assumptions, easily handle large numbers of covariates, and produce interpretable treatment effect estimates.
-Despite their advantages, these methods remain underutilized by social scientists.
-Part of the barrier has been lack of familiarity with these methods, with few introductions existing.
-There has also been little guidance regarding which method is appropriate for particular types of data.
+These methods have a number of strengths over traditional regression methods: They make few functional form assumptions, can accommodate large numbers of covariates, and produce easily interpretable treatment effect estimates.
+Many of these methods also have a "double robust" property: They estimate one model for the treatment exposure and another for the outcome, and as long as at least one is correctly specified, then the treatment effect will be estimated consistently.
+Despite their apparent advantages, these methods remain underutilized by social scientists.
+Part of the barrier has been lack of familiarity with these methods.
+It has also been unclear how these methods compare, or whether such methods actually perform better than traditional methods in finite samples.
+<!-- And when researchers want to use an existing R package for these methods, the array of possible estimation methods and other options can be dizzying.   -->
 
-This paper makes advances on both of these fronts.
-First, it is a guide to some of the latest methods in flexible covariate adjustment, explaining the methods to a social scientist audience.
-Second, it compares these methods using a type of data that social scientists frequently encounter, but on which these methods have been rarely applied: nested survey data.
-It does this by using both simulated data where the treatment effect estimate is known, and then using real-world complex survey data from the Program for International Student Assessment (PISA).
+This paper makes advances on these fronts.
+First, it is a guide to some of the latest methods in doubly robust, flexible covariate adjustment for causal inference, explaining the methods to a social scientist audience.
+Second, it compares these methods to more traditional statistical methods using a type of data that social scientists frequently encounter: cross-national survey data.
+It does this by using both simulated data where the treatment effect estimate is known, and then using complex survey data from the Program for International Student Assessment (PISA).
 
-After presenting OLS regression as a baseline, the paper covers Targeted Maximum Likelihood Estimation, double machine learning (Chernozhukov et al 2018), PLCE (Ratkovic 2022), and BART.
+Methods covered include Targeted Maximum Likelihood Estimation [TMLE, @vanderlaan_2006_targeted], Double or Debiased Machine Learning [DML, @chernozhukov_2018_double], and Augmented Inverse Propensity Weighting [AIPW, @glynn_2010_introduction].
+This paper reviews the theory behind these methods as well as simple R implementations of them on simulations and real data.
+These methods are compared to two methods commonly used by social scientists: ordinary least squares (OLS) regression, and matching on propensity scores estimated from logistic regression (PSM).
+
+# Conceptual Overview
+
+Doubly robust methods estimate two models:
+
+- an *outcome model*
+
+$$\mu_d(X_i) = E(Y_i \mid D_i = d, X_i)$$
+
+- and an *exposure model* (or treatment model or propensity score):
+
+$$\pi(X_i) = E(D_i \mid X_i)$$
+
+where $\mu_d(\cdot)$ is the model of control or treatment $D_i = d=\{0, 1\}$, $X_i$ is a vector of covariates for unit $i = 1, \ldots, N$ for treatment (1) and control (0), $Y_i$ is the outcome, and $\pi(\cdot)$ is the exposure model.
+The covariates included in $X_i$ can be different for the two models.
+
+An estimator is called "doubly robust" if it achieves consistent estimation of the ATE (or whatever estimand the researcher is interested in) as long as *at least one* of these two models is consistently estimated.
+This means that the outcome model can be completely misspecified, but as long as the exposure model is correct, our estimation of the ATE will be consistent.
+This also means that the exposure model can be completely wrong, as along as the outcome model is correct.
+
+<!-- ## Origins of Doubly Robust Methods -->
+
+<!-- According to @bang_2005_doubly, doubly robust methods have their origins in missing data models.
+@robins_1994_estimation and @rotnitzky_1998_semiparametric developed augmented orthogonal inverse probability-weighted (AIPW) estimators in missing data models, and @scharfstein_1999_adjusting showed that AIPW was doubly robust and extended to causal inference.
+-->
+
+<!-- But @kang_2007_demystifying argue that doubly robust methods are older.
+They cite work by @cassel_1976_results, who proposed “generalized regression estimators” for population means from surveys where sampling weights must be estimated.
+Arguably, doubly robust methods go back even further than this.
+The form of doubly robust methods is similar to residual-on-residual regression, which dates back to @frisch_1933_partial famous FWL theorem: -->
+
+<!-- $$\beta_D = \frac{\text{Cov}(\tilde Y_i, \tilde D_i)}{\text{Var}(\tilde D_i)}$$ -->
+
+<!-- where $\tilde D_i$ is the residual part of $D_i$ after regressing it on $X_i$, and $\tilde Y_i$ is the residual part of $Y_i$ after regressing it on $X_i$.
+This formulation writes the regression coefficient as composed of an outcome model ($\tilde Y_i$) and exposure model ($\tilde D_i$), the two models used in doubly robust estimators.
+-->
+
+<!-- There are also links between doubly robust methods and matching with regression adjustment.
+This work goes back to at least @rubin_1973_use, who suggested that regression adjustment in matched data produces less biased estimates that either matching (exposure adjustment) or regression (outcome adjustment) do by themselves.
+-->
+
+## Assumptions
+
+Most doubly robust methods require almost all of the standard assumptions necessary formost methods that depend on selection on observables.
+Although some doubly robust methods relax one or two of these, the six standard assumptions are:
+
+1. Consistency
+2. Positivity/overlap
+3. One version of treatment
+4. No interference
+5. IID observations
+6. Conditional ignorability: $\{Y_{i0}, Y_{i1}\} \perp \!\!\! \perp D_i \mid X_i$
+
+Special attention should be paid to Assumption 6: doubly robust methods will not work if we do not measure an important confounder that affects both treatment and exposure.
+But notably, the doubly robust methods covered in this tutorial make no functional form assumptions.
+Most use flexible machine learning algorithms to estimate both the outcome and exposure models, with regularization (often through cross-fitting) to avoid overfitting.
+
+## A simple demonstration
+
+To demonstrate double robustness, this section presents one of the simpler doubly robust estimators: Augmented Inverse Propensity Weighting (AIPW) [@glynn_2010_introduction].
+We can write this estimator as follows:
+
+$$\begin{aligned}
+\widehat{ATE} = &\frac{1}{N} \sum_{i=1}^N \left( \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) \right) 
+- \frac{1}{N} \sum_{i=1}^N \left( \frac{(1-D_i)(Y_i - \hat \mu_0 (X_i))}{1-\hat \pi(X_i)} + \hat \mu_0(X_i) \right)
+\end{aligned}$$
+
+For each individual in the sample, this estimator calculates two quantities:
+
+- The treated potential outcome
+
+$$\hat Y_{1i} = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i)$$
+
+- The control potential outcome
+
+$$\hat Y_{0i} = \frac{(1-D_i)(Y_i - \hat \mu_0 (X_i))}{1-\hat \pi(X_i)} + \hat \mu_0(X_i)$$
+
+Let's focus on the treated model:
+
+$$\hat Y_{1i} = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i)$$
+
+First, assume that the outcome model $\mu_1(X_i)$ is *correctly* specified and the exposure model $\pi(X_i)$ is *incorreclty* specified.
+Let's also assume (for now) that we're dealing with a treated unit, i.e.
+$D_i = 1$.
+Then
+
+$$\hat \mu_1 (X_i) = Y_i$$
+
+and hence
+
+$$\hat Y_{1i} = \frac{D_i(0)}{\hat \pi (X_i)} + \hat \mu_1(X_i) = \hat \mu_1(X_i).$$
+
+So the model relies *only* on the outcome model.
+The incorrectly specified exposure model completely disappears from the equation.
+If we're dealing with a control unit ($D_i=0$), we get the same result:
+
+$$\hat Y_{1i} = \frac{0(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) = \hat \mu_1(X_i).$$
+
+Now, what if the *exposure* model $\pi(X_i)$ is correctly specified and the outcome model $\mu_1(X)$ is incorrect? First, we rewrite the estimator for the treated outcome:
+
+$$\begin{aligned}
+\hat Y_{1i}& = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) \\
+&= \frac{D_iY_i}{\hat \pi (X_i)} - \frac{D_i\hat \mu_1 (X_i)}{\hat \pi (X_i)} + \frac{\hat \pi (X_i)\hat \mu_1(X_i)}{\hat \pi (X_i)} \\
+& = \frac{D_iY_i}{\hat \pi (X_i)} - \left( \frac{D_i - \hat \pi(X_i)}{\hat \pi (X_i)}\right) \hat \mu_1(X_i). &&(*)
+\end{aligned}$$
+
+Since the exposure model is correclty specified, we have $D_i = \hat \pi(X_i)$ on average, so
+
+$$E[D_i - \hat \pi(X_i)] = 0.$$
+
+This means that the second term in equation $(*)$ is 0, so
+
+$$E[\hat Y_{1i}]= E \left [ \frac{D_iY_i}{\hat \pi (X_i)}\right].$$
+
+This shows that when the exposure model is correct, then the estimator depends *only* on the exposure model. We can make similar arguments for the control model $\hat Y_{0i}$.
+
+This demonstration shows that this estimator achieves double robustness: the estimator is robust to misspecification of either the exposure or the outcome model (but not both).
 
 # Overview of Techniques  
+Each of the methods reviewed in this paper can be thought of as a collection of estimation techniques.
+Each involves a model for the outcome and another for the treatment exposure, but the ways these relate and are combined varies from method to method.
+Choice of estimation technique for these two models is left to the discretion of the user; often ensemble learning is recommended, but in practice simpler methods can also work well.
+
+*Augmented Inverse Propensity Weighting (AIPW)*: The oldest of these modern methods, AIPW arose in the context of missing data imputation.
+As shown in the demonstration above, the method simply combines estimates from a model for the treatment exposure, $\pi(X)$, and a model for the outcome, $\mu(X)$.
+The name comes from the close similarity to inverse propensity weights (IPW), but whereas IPW only weights for propensity of treatment, AIPW "augments" these weights with an estimate of the response surface as well.
+
+*Targeted Maximum Likelihood Estimation (TMLE)*: TMLE begins by estimating the relevant part of the data-generating distribution $P(Y)$, i.e.
+the conditional density $Q = P(Y \mid X)$.
+It next estimates the exposure model.
+Although any estimation method can be used for these steps, the originators of the method suggest using a "super learner," i.e.
+ensemble learning with cross-validation.
+Next, the exposure model is used to calculate a "clever covariate," which is similar to an IPW.
+The coefficient for this clever covariate is estimated using maximum likelihood -- whence the "MLE" in "TMLE." Finally, the estimate of $Q$ is updated in a function involving the clever covariate.
+This process can be iterated, but usually one iteration is enough.
+The estimate of the distribution $Q$ can be used to calculate the estimand of interest.
+
+*Double or Debiased Machine Learning* (DML): The most recent of the methods reviewed here, DML is motivated by the need to handle problems with high-dimensional nuisance parameters, i.e.
+a large number of measured confounders.
+Flexible machine learning is appropriate for this task, but such methods suffer from regularization bias.
+DML removes this bias in a two-step procedure.
+First, it solves the auxiliary problem of estimating the treatment exposure model $E(D|X) =  \pi(X)$.
+It then uses this model to remove bias: Neyman orthogonalization allows the creation of an orthogonalized regressor, essentially partialing out the effect of covariates $X$ from treatment $D$.
+The debiased $D$ is then used to estimate the conditional mean of the outcome $E(Y\mid X) = \mu(X)$, which can be used to calculate the estimand of interest.
+
+These methods have many similarities. How do the results they give compare? The next section tests the performance of each in practice.
 
@@
 
-```{r test-sample}
+## Monte Carlo Simulations
 
+The structure of these simulations is based on @kang_2007_demystifying.
+For each unit $i = 1, \ldots, n$, let $Z = (z_{i1}, z_{i2}, z_{i3}, z_{i4})^\top$ be distributed independently as $N(0,I)$, where $I$ is the $4 \times 4$ identity matrix.
+Furthermore, let $d_i \in \{0,1\}$ be an indicator for treatment status with a Bernoulli distribution with probability $\pi_i$ of receiving treatment status.
+Values of $\pi_i$ are generated as:
+$$\pi_i = \text{expit}(z_{i1} +0.5z_{i2}-0.33z_{i3} -0.2z_{i4}),$$
+where $\text{expit}(\cdot) = \exp(\cdot)/(1 + \exp(\cdot)).$ These are then used as the probability of treatment assignment in a series of Bernoulli draws for $d_i$. Outcomes $y_i$ are generated as
+$$y_i = 500 + 50d_i + 30z_{i1} -35z_{i2} - 60z_{i3} + 50z_{i4} + \epsilon_i,$$
+where $\epsilon_i \sim N(0,10)$. Now assume that the researcher cannot measure the $z_{ij}$'s. Instead we observe $X = (x_{i1}, x_{i2}, x_{i3}, x_{i4})^\top$ :
+$$\begin{aligned}
+x_{i1} &= \exp(z_{i1}/2) \\
+x_{i2} &= z_2 / (1+\exp(z_{i1})) + 10 \\
+x_{i3} &= (z_{i1} z_{i3} /25 + 0.6)^3 \\
+x_{i4} &= (z_2 + z_4 + 20)^2 \\
+\end{aligned}$$
+
+For these preliminary results, datasets of 200 observations are generated 100 times. For each estimation method, three specifications are used:
+
+- "correct": the model is fitted to the true data-generating variables, $Z$
+- "incorrect": the model is fitted to the transformed variables $X$
+- "ovb": the model is fitted to $(x_2, x_3, x_4)^\top$ ($x_1$ is omitted).
+
+Results are shown in Table \@ref(tab:sim-results).
+Estimation methods include ordinary least squares regression ("OLS"),  propensity-score matching with scores estimated from logistic regression using the `MatchIt` package ("PSM"), the augmented inverse propensity weighted estimator with generalized additive models using the `CausalGAM` package (AIPW), targeted maximum likelihood estimation using the `tmle` package (TMLE), and double/debiased machine learning with random forests with the `DoubleML` and `mlr3` packages.
+
+Surprisingly, the double robust methods do not necessarily perform better.
+All methods perform well when the true data-generating variables are provided.
+When transformed variables are provided instead, bias, RMSE, and MAE rise for all of the estimation methods, even those that use flexible methods to model the response and treatment assignment surfaces.
+DML performs relatively well but RMSE and MAE still rise somewhat.
+When a variable is omitted, all of the methods perform poorly.
+
+```{r sim}
+expit <- function(x){exp(x) / (1+exp(x))}
+
+sim_n <- function(n, mu = c(0, 0, 0, 0), Sigma = diag(c(1,1,1,1))){
+  z <- MASS::mvrnorm(n, mu, Sigma)
+  z1 <- z[,1]
+  z2 <- z[,2]
+  z3 <- z[,3]
+  z4 <- z[,4]
+  epsilon <- rnorm(n, 0, 10)
+
+  pi <- expit(z1 + 0.5*z2 -.33*z3 - .2*z4)
+  d <- rbinom(n, 1, pi)
+
+  y <- 475 + 50*d + 30*z1 -35*z2 - 60*z3 + 50*z4 + epsilon
+
+  x1 <- exp(z1/2)
+  x2 <- z2 / (1+exp(z1)) + 10
+  x3 <- (z1 * z3 / 25 + 0.6)^3
+  x4 <- (z2 * z4 + 20)^2
+  return(data.frame(
+    z1 = z1,
+    z2 = z2,
+    z3 = z3,
+    z4 = z4,
+    pi = pi,
+    d = d,
+    y = y,
+    x1 = x1,
+    x2 = x2, 
+    x3 = x3,
+    x4 = x4
+  ))
+}
+
+set.seed(1858)
+sim_200 <- replicate(100, sim_n(200), simplify = F)
+sim_1000 <- replicate(100, sim_n(1000), simplify = F)
+sim_10000 <- replicate(100, sim_n(10000), simplify = F)
+```
+
+```{r lm-sim, eval = F}
+lm_sim <- function(dat){
+  n <- length(dat)
+  lm_list_true <- list()
+  lm_list_false <- list()
+  lm_list_ovb <- list()
+  for(i in 1:n){
+    lm_out_true <- lm(y ~ d + z1 + z2 + z3 + z4, dat[[i]])
+    lm_list_true[[i]] <- lm_out_true$coefficients[['d']]
+
+    lm_out_false <- lm(y ~ d + x1 + x2 + x3 + x4, dat[[i]])
+    lm_list_false[[i]] <- lm_out_false$coefficients[['d']]
+
+    lm_out_ovb <- lm(y ~ d + x2 + x3 + x4, dat[[i]])
+    lm_list_ovb[[i]] <- lm_out_ovb$coefficients[['d']]
+  }
+
+  return(list(
+    n = nrow(dat[[i]]),
+    correct = unlist(lm_list_true),
+    incorrect = unlist(lm_list_false),
+    ovb = unlist(lm_list_ovb)))
+}
+
+perform <- function(est_list, label){
+  perform_list <- list()
+
+  for(i in 1:(length(est_list)-1)){
+    est <- unlist(est_list[[i+1]])
+    bias <- mean(est-50)
+    percent_bias <- 100 * bias / sd(est)
+    rmse <- sqrt(mean((est - 50)^2))
+    mae <- median(abs(est - 50))
+
+    perform_list[[i]] <- data.frame(label = label, n = est_list[['n']], 
+                                    model = names(est_list)[i+1], 
+                                    bias, percent_bias, rmse, mae)
+  }
+  return(bind_rows(perform_list))
+}
+
+lm_sim_200 <- lm_sim(sim_200) 
+# lm_sim_1000 <- lm_sim(sim_1000) 
+# lm_sim_10000 <- lm_sim(sim_10000)
+
+lm_df <- bind_rows(
+  perform(lm_sim_200, 'OLS'),
+  )
+
+write_csv(lm_df, here('files', 'lm_df.csv'))
+```
+
+```{r psm-sim, eval = F}
+psm_sim <- function(dat){
+  n <- length(dat)
+  psm_list_true <- list()
+  psm_list_false <- list()
+  lm_list_ovb <- list()
+  for(i in 1:n){
+    match_true <- MatchIt::matchit(d ~ z1 + z2 + z3 + z4,
+                           data = dat[[i]],
+                           method = 'nearest',
+                           distance = 'glm')
+
+    psm_out_true <- lm(y ~ d + z1 + z2 + z3 + z4, 
+                       MatchIt::match.data(match_true), 
+                       weights = weights)
+
+    match_false <- MatchIt::matchit(d ~ x1 + x2 + x3 + x4,
+                           data = dat[[i]],
+                           method = 'nearest',
+                           distance = 'glm')
+
+    psm_out_false <- lm(y ~ d + x1 + x2 + x3 + x4, 
+                       MatchIt::match.data(match_false), 
+                       weights = weights)
+
+    match_ovb <- MatchIt::matchit(d ~ x2 + x3 + x4,
+                           data = dat[[i]],
+                           method = 'nearest',
+                           distance = 'glm')
+
+    psm_out_ovb <- lm(y ~ d + x2 + x3 + x4, 
+                       MatchIt::match.data(match_false), 
+                       weights = weights)
+
+    psm_list_true[[i]] <- psm_out_true$coefficients[['d']]
+    psm_list_false[[i]] <- psm_out_false$coefficients[['d']]
+    psm_list_ovb[[i]] <- psm_out_ovb$coefficients[['d']]
+  }
+
+  return(list(n = nrow(dat[[i]]),
+              correct = unlist(psm_list_true),
+              incorrect = unlist(psm_list_false),
+              ovb = unlist(psm_list_ovb)))
+}
+
+psm_sim_200 <- psm_sim(sim_200) 
+# psm_sim_1000 <- psm_sim(sim_1000) 
+# psm_sim_10000 <- psm_sim(sim_10000)
+
+psm_df <- bind_rows(
+  perform(psm_sim_200, 'PSM'),
+  )
+
+write_csv(psm_df, here('files', 'psm_df.csv'))
+```
+
+```{r aipw-sim, eval = F}
+aipw_sim <- function(dat, seed = 185){
+  library(gam)
+
+  set.seed(seed)
+  n <- length(dat)
+  aipw_list_true <- list()
+  aipw_list_false <- list()
+  aipw_list_ovb <- list()
+
+  for(i in 1:n){
+
+    print(i)
+
+    correct <- CausalGAM::estimate.ATE(
+        pscore.formula = d ~ s(z1) + s(z2) + s(z3) + s(z4),
+        pscore.family = binomial,
+        outcome.formula.t = y ~ s(z1) + s(z2) + s(z3) + s(z4),
+        outcome.formula.c = y ~ s(z1) + s(z2) + s(z3) + s(z4),
+        outcome.family = gaussian,
+        treatment.var = 'd',
+        data=dat[[i]],
+        divby0.action="t",
+        divby0.tol=0.001,
+        var.gam.plot=FALSE,
+        nboot=50)
+
+    incorrect <- CausalGAM::estimate.ATE(
+        pscore.formula = d ~ s(x1) + s(x2) + s(x3) + s(x4),
+        pscore.family = binomial,
+        outcome.formula.t = y ~ s(x1) + s(x2) + s(x3) + s(x4),
+        outcome.formula.c = y ~ s(x1) + s(x2) + s(x3) + s(x4),
+        outcome.family = gaussian,
+        treatment.var = 'd',
+        data=dat[[i]],
+        divby0.action="t",
+        divby0.tol=0.001,
+        var.gam.plot=FALSE,
+        nboot=50)
+
+    ovb <- CausalGAM::estimate.ATE(
+        pscore.formula = d ~ s(x2) + s(x3) + s(x4),
+        pscore.family = binomial,
+        outcome.formula.t = y ~ s(x2) + s(x3) + s(x4),
+        outcome.formula.c = y ~ s(x2) + s(x3) + s(x4),
+        outcome.family = gaussian,
+        treatment.var = 'd',
+        data=dat[[i]],
+        divby0.action="t",
+        divby0.tol=0.001,
+        var.gam.plot=FALSE,
+        nboot=50)
+
+    aipw_list_true[[i]] <- correct$ATE.AIPW.hat
+    aipw_list_false[[i]] <- incorrect$ATE.AIPW.hat
+    aipw_list_ovb[[i]] <- ovb$ATE.AIPW.hat
+  }
+
+  return(list(n = nrow(dat[[i]]),
+              correct = unlist(aipw_list_true),
+              incorrect = unlist(aipw_list_false),
+              ovb = unlist(aipw_list_ovb)))
+}
+
+aipw_out <- aipw_sim(sim_200)
+
+aipw_df <- perform(aipw_out, 'AIPW')
+
+write_csv(aipw_df,  here('files', 'aipw_df.csv'))
+
+```
+
+```{r tmle-sim, eval = F}
+
+tmle_sim <- function(dat){
+  n <- length(dat)
+
+  tmle_list_true_true <- list()
+  tmle_list_false_true <- list()
+  tmle_list_true_false <- list()
+  tmle_list_false_false <- list()
+  tmle_list_ovb_ovb <- list()
+
+  for(i in 1:n){
+
+    print(i)
+
+    tmle_false_false <- with(
+      dat[[i]],
+      tmle::tmle(
+        Y = y,
+        A = d,
+        W = data.frame(z1, z2, z3, z4, x1, x2, x3, x4),
+        Qform = Y ~ A + x1 + x2 + x3 + x4,
+        gform = A ~ x1 + x2 + x3 + x4))
+
+    tmle_false_true <- with(
+      dat[[i]],
+      tmle::tmle(
+        Y = y,
+        A = d,
+        W = data.frame(z1, z2, z3, z4, x1, x2, x3, x4),
+        Qform = Y ~ A + x1 + x2 + x3 + x4,
+        gform = A ~ z1 + z2 + z3 + z4))
+
+    tmle_true_false <- with(
+      dat[[i]],
+      tmle::tmle(
+        Y = y,
+        A = d,
+        W = data.frame(z1, z2, z3, z4, x1, x2, x3, x4),
+        Qform = Y ~ A + z1 + z2 + z3 + z4,
+        gform = A ~ x1 + x2 + x3 + x4))
+
+    tmle_true_true <- with(
+      dat[[i]],
+      tmle::tmle(
+        Y = y,
+        A = d,
+        W = data.frame(z1, z2, z3, z4, x1, x2, x3, x4),
+        Qform = Y ~ A + z1 + z2 + z3 + z4,
+        gform = A ~ z1 + z2 + z3 + z4))
+
+    tmle_ovb_ovb <- with(
+      dat[[i]],
+      tmle::tmle(
+        Y = y,
+        A = d,
+        W = data.frame(x2, x3, x4),
+        Qform = Y ~ A + x2 + x3 + x4,
+        gform = A ~ x2 + x3 + x4))
+
+    tmle_list_true_true[[i]] <- tmle_true_true$estimates$ATE$psi
+    tmle_list_true_false[[i]] <- tmle_true_false$estimates$ATE$psi
+    tmle_list_false_true[[i]] <- tmle_false_true$estimates$ATE$psi
+    tmle_list_false_false[[i]] <- tmle_false_false$estimates$ATE$psi
+    tmle_list_ovb_ovb[[i]] <- tmle_ovb_ovb$estimates$ATE$psi
+  }
+
+  return(list(n = nrow(dat[[i]]),
+              correct_correct = unlist(tmle_list_true_true),
+              correct_incorrect = unlist(tmle_list_true_false),
+              incorrect_correct = unlist(tmle_list_false_true),
+              incorrect_incorrect = unlist(tmle_list_false_false),
+              ovb = unlist(tmle_list_ovb_ovb))
+         )
+}
+
+tmle_out <- tmle_sim(sim_200)
+
+tmle_df <- perform(tmle_out, 'TMLE')
+
+write_csv(tmle_df, here('files', 'tmle_df.csv'))
+```
+
+```{r dml-sim, eval = F}
+dml_sim <- function(dat, seed = 185){
+  library(mlr3)
+  library(mlr3learners)
+
+  set.seed(seed)
+
+  n <- length(dat)
+
+  correct_list <- list()
+  incorrect_list <- list()
+  ovb_list <- list()
+
+  for(i in 1:n){
+    print(i)
+
+    lgr::get_logger("mlr3")$set_threshold("warn")
+
+    learner = lrn("regr.ranger", num.trees=500, 
+                  max.depth=5, min.node.size=2)
+    ml_l = learner$clone()
+    ml_m = learner$clone()
+
+    correct = DoubleML::DoubleMLPLR$new(
+      DoubleML::DoubleMLData$new(dat[[i]],
+                                 y_col = 'y',
+                                 d_cols = 'd',
+                                 x_cols = c('z1', 'z2', 'z3', 'z4')), 
+      ml_l=ml_l, ml_m=ml_m)
+    correct$fit()
+    correct_list[[i]] <- correct$all_coef[[1,1]]
+
+    incorrect = DoubleML::DoubleMLPLR$new(
+      DoubleML::DoubleMLData$new(dat[[i]],
+                                 y_col = 'y',
+                                 d_cols = 'd',
+                                 x_cols = c('x1', 'x2', 'x3', 'x4')), 
+      ml_l=ml_l, ml_m=ml_m)
+    incorrect$fit()
+    incorrect_list[[i]] <- incorrect$all_coef[[1,1]]
+
+    ovb = DoubleML::DoubleMLPLR$new(
+      DoubleML::DoubleMLData$new(dat[[i]],
+                                 y_col = 'y',
+                                 d_cols = 'd',
+                                 x_cols = c('x2', 'x3', 'x4')), 
+      ml_l=ml_l, ml_m=ml_m)
+    ovb$fit()
+    ovb_list[[i]] <- ovb$all_coef[[1,1]]
+
+  }
+  return(list(n = nrow(dat[[i]]),
+              correct = unlist(correct_list),
+              incorrect = unlist(incorrect_list),
+              ovb = unlist(ovb_list))
+         )
+}
+
+dml_out <- dml_sim(sim_200)
+
+dml_df <- perform(dml_out, 'DML')
+
+write_csv(dml_df, here('files', 'dml_df.csv'))
+```
+
+```{r sim-results}
+bind_rows(
+  read_csv(here('files', 'lm_df.csv')),
+  read_csv(here('files', 'psm_df.csv')),
+  read_csv(here('files', 'aipw_df.csv')),
+  read_csv(here('files', 'tmle_df.csv')) %>%
+    filter(model %in% c('correct_correct', 'incorrect_incorrect', 'ovb')) %>%
+    mutate(model = c('correct', 'incorrect', 'ovb')),
+  read_csv(here('files', 'dml_df.csv'))
+  ) %>%
+  kableExtra::kable(booktabs = T, 
+                    linesep = '',
+                    caption = 'Results of Monte Carlo simulations over 100 replications.
+Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, and mae is median absolute error.')
+```
+
+```{r test-sample, eval = F}
 set.seed(185)
@@
 
-```{r bart}
+```{r bart, eval = F}
 set.seed(159)
@@
 
-\newpage
+# Next Steps
+The Monte Carlo simulations presented here use small sample sizes and few variables, while double robust methods are perhaps most advantageous for large, high-dimensional samples.
+In the final paper, the simulations here will be supplemented samples of 1,000 and 10,000, and all will be replicated 1,000 times.
+Data sets with many covariates will also be simulated.
+The final paper will also test these methods on cross-national PISA test score data and provide R code to implement these methods.
 

### 2022-12-01 draft/ms-adj-draft.Rmd
very preliminary draft

@@
 header-includes:
-  #- \usepackage{setspace}\doublespace
+  - \usepackage{setspace}\doublespace
   # - \usepackage[nolists, fighead, tabhead]{endfloat}
@@
 #fontsize: 11pt
-geometry: margin=.6in
+# geometry: margin=.6in
 indent: yes
@@
 
-# title: "Comparing Flexible Adjustment Methods for Causal Inference on Nested Survey Data"
-# subtitle: "Statistics MS Thesis"
-# author:  Nathan I. Hoffmann
-# #   | Department of Sociology, UCLA
-# date: "`r format(Sys.time(), '%B %e, %Y')`"
+title: "Demystifying Double Robust, Flexible Adjustment Methods for Causal Inference"
+#subtitle: "PAA 2023"
+author:  Nathan I. Hoffmann
+#   | Department of Sociology, UCLA
+date: "`r format(Sys.time(), '%B %e, %Y')`"
+
+abstract: "Double robust methods for flexible covariate adjustment in causal inference have proliferated in recent years.
+Despite their apparent advantages, these methods remain underutilized by social scientists.
+It is also unclear whether these methods actually outperform more traditional methods in finite samples.
+This paper has two aims: it is a guide to some of the latest methods in doubly robust, flexible covariate adjustment for causal inference, and it compares these methods to more traditional statistical methods.
+It does this by using both simulated data where the treatment effect estimate is known, and then using complex survey data from the Program for International Student Assessment (PISA).
+Methods covered include Targeted Maximum Likelihood Estimation, Double/Debiased Machine Learning, and Augmented Inverse Propensity Weighting.
+Although these methods are robust to either the exposure or response model being misspecified, preliminary results show that, when both models are incorrect, bias grows rapidly in small samples."
 
@@
 
-<!-- ## Origins of Doubly Robust Methods -->
-
-<!-- According to @bang_2005_doubly, doubly robust methods have their origins in missing data models.
+## Origins of Doubly Robust Methods
+
+According to @bang_2005_doubly, doubly robust methods have their origins in missing data models.
 @robins_1994_estimation and @rotnitzky_1998_semiparametric developed augmented orthogonal inverse probability-weighted (AIPW) estimators in missing data models, and @scharfstein_1999_adjusting showed that AIPW was doubly robust and extended to causal inference.
--->
-
-<!-- But @kang_2007_demystifying argue that doubly robust methods are older.
+
+But @kang_2007_demystifying argue that doubly robust methods are older.
 They cite work by @cassel_1976_results, who proposed “generalized regression estimators” for population means from surveys where sampling weights must be estimated.
 Arguably, doubly robust methods go back even further than this.
-The form of doubly robust methods is similar to residual-on-residual regression, which dates back to @frisch_1933_partial famous FWL theorem: -->
-
-<!-- $$\beta_D = \frac{\text{Cov}(\tilde Y_i, \tilde D_i)}{\text{Var}(\tilde D_i)}$$ -->
-
-<!-- where $\tilde D_i$ is the residual part of $D_i$ after regressing it on $X_i$, and $\tilde Y_i$ is the residual part of $Y_i$ after regressing it on $X_i$.
+The form of doubly robust methods is similar to residual-on-residual regression, which dates back to @frisch_1933_partial famous FWL theorem:
+
+$$\beta_D = \frac{\text{Cov}(\tilde Y_i, \tilde D_i)}{\text{Var}(\tilde D_i)}$$
+
+where $\tilde D_i$ is the residual part of $D_i$ after regressing it on $X_i$, and $\tilde Y_i$ is the residual part of $Y_i$ after regressing it on $X_i$.
 This formulation writes the regression coefficient as composed of an outcome model ($\tilde Y_i$) and exposure model ($\tilde D_i$), the two models used in doubly robust estimators.
--->
-
-<!-- There are also links between doubly robust methods and matching with regression adjustment.
+
+There are also links between doubly robust methods and matching with regression adjustment.
 This work goes back to at least @rubin_1973_use, who suggested that regression adjustment in matched data produces less biased estimates that either matching (exposure adjustment) or regression (outcome adjustment) do by themselves.
--->
 
@@
 
-# Preliminary Findings
-
-## Monte Carlo Simulations
+# Methods
+
+For the comparisons in the next section, estimation methods include ordinary least squares regression ("OLS"),  propensity-score matching with scores estimated from logistic regression using the `MatchIt` package ("PSM"), the augmented inverse propensity weighted estimator with generalized additive models using the `CausalGAM` package (AIPW), targeted maximum likelihood estimation using the `tmle` package (TMLE) with the default Superlearner that relies on the `SL.glm`,` SL.step`, and `GL.glm.interaction` functions, and double/debiased machine learning with random forests with the `DoubleML` and `mlr3` packages.
+
+# Results
+
+## Simulation based on Kang & Schafer (2007)
 
@@
 \end{aligned}$$
-
-For these preliminary results, datasets of 200 observations are generated 100 times. For each estimation method, three specifications are used:
-
-- "correct": the model is fitted to the true data-generating variables, $Z$
-- "incorrect": the model is fitted to the transformed variables $X$
-- "ovb": the model is fitted to $(x_2, x_3, x_4)^\top$ ($x_1$ is omitted).
-
-Results are shown in Table \@ref(tab:sim-results).
-Estimation methods include ordinary least squares regression ("OLS"),  propensity-score matching with scores estimated from logistic regression using the `MatchIt` package ("PSM"), the augmented inverse propensity weighted estimator with generalized additive models using the `CausalGAM` package (AIPW), targeted maximum likelihood estimation using the `tmle` package (TMLE), and double/debiased machine learning with random forests with the `DoubleML` and `mlr3` packages.
-
-Surprisingly, the double robust methods do not necessarily perform better.
-All methods perform well when the true data-generating variables are provided.
-When transformed variables are provided instead, bias, RMSE, and MAE rise for all of the estimation methods, even those that use flexible methods to model the response and treatment assignment surfaces.
-DML performs relatively well but RMSE and MAE still rise somewhat.
-When a variable is omitted, all of the methods perform poorly.
 
@@
         var.gam.plot=FALSE,
-        nboot=50)
+        nboot = 0)
 
@@
 
-```{r test-sample, eval = F}
+For these preliminary results, datasets of 200 observations are generated 100 times. For each estimation method, three specifications are used:
+
+- "correct": the model is fitted to the true data-generating variables, $Z$
+- "incorrect": the model is fitted to the transformed variables $X$
+- "ovb": the model is fitted to $(x_2, x_3, x_4)^\top$; i.e., $x_1$ is omitted
+
+Results are shown in Table \@ref(tab:sim-results).
+Surprisingly, the double robust methods do not necessarily perform better.
+All methods perform well when the true data-generating variables are provided.
+When transformed variables are provided instead, bias, RMSE, and MAE rise for all of the estimation methods, even those that use flexible methods to model the response and treatment assignment surfaces.
+DML performs relatively well but RMSE and MAE still rise somewhat.
+When a variable is omitted, all of the methods perform poorly.
+
+## Simluation with Dorie et al. (2019) Data
+
+In 2016, the Atlantic Causal Inference Conference hosted a competition for causal inference methods that adjust on observables.
+@dorie_2019_automated published the results of this competition, along with the data used in the competition.
+Below, I test double robust methods on the 20 data sets used for the "do-it-yourself" part of the competition.
+The data represent a hypothetical twins study investigating the impact of birth weight on IQ.
+The data have 4802 observations and 52 covariates.
+The authors of the study specify a different data generating process for the potential outcomes in each data set.
+In all cases, ignorability holds, but the authors vary the following:
+
+- degree of nonlinearity
+- percentage of treated
+- overlap for the treatment group
+- alignment (correspondence between the assignment mechanism and the response surface)
+- treatment effect heterogeneity
+- overall magnitude of the treatment effect
+
+The 20 data sets used here cover a range of these attributes; see the supplemental material from @dorie_2019_automated for details.
+For these preliminary results, I used 5 simulations of each data set, resulting in 100 data sets.
+I then calculated the same statistics as in Table \@ref(tab:sim-results): percent bias, root-mean squared error, and median average error.
+I also include the number of data sets for which the method failed and the average computation time for each data set.
+
+```{r dorie-sim, eval = F}
+set.seed(185)
+sim_list <- list()
+for(i in 1:20){ # up to 77
+  #sim_list_nest <- list()
+  for(j in 1:5){ # up to 100
+    print(paste0(i,',',j))
+    sim_list[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016, i, j, 
+                                                          extraInfo = T)
+  }
+  #sim_list[[i]] <- sim_list_nest
+}
+
+perform <- function(est_df, label){
+  est_df %>%
+    summarize(bias = mean(d - truth),
+              percent_bias = bias/sd(d),
+              rmse = sqrt(mean(d - truth)^2),
+              mae = median(abs(d - truth))) %>%
+    mutate(label = label) %>%
+    select(label, everything()) %>%
+    return()
+}
+```
+
+```{r lm-sim2, eval = F}
+lm_sim <- function(dat){
+  start_time <- Sys.time()
+  n <- length(dat)
+  lm_list <- list()
+  for(i in 1:n){
+    print(paste0(i, ' out of ', n))
+    sim_dat <- data.frame(y = dat[[i]]$y, 
+                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
+                          dat[[i]]$x)
+
+    tryCatch({
+      lm_out <- lm(y ~ d + ., sim_dat)
+      lm_list[[i]] <- data.frame(d = lm_out$coefficients[['d']],
+                                 truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
+      }, error=function(e){
+        cat("ERROR :",conditionMessage(e), "\n")
+        })
+
+  }
+
+  fail_count <- sum(sapply(lm_list, function(x) is.null(x)))
+  # in case last few are errors
+  fail_count <- ifelse(length(lm_list) == n, fail_count, fail_count + (n - length(lm_list)))
+
+  return(list(
+    est_df = bind_rows(lm_list),
+    fail_count = fail_count,
+    comp_time = as.numeric(Sys.time() - start_time)/(n-fail_count))
+    )
+}
+
+lm_sim_out <- lm_sim(sim_list)
+
+lm_df <- perform(lm_sim_out$est_df, 'OLS') %>%
+  mutate(fail_count = lm_sim_out$fail_count,
+         comp_time = lm_sim_out$comp_time)
+
+write_csv(lm_df, here('files', 'lm_df2.csv'))
+```
+
+```{r psm-sim2, eval = F}
+psm_sim <- function(dat){
+  start_time <- Sys.time()
+  n <- length(dat)
+  psm_list <- list()
+  for(i in 1:n){
+    print(paste0(i, ' out of ', n))
+    sim_dat <- data.frame(y = dat[[i]]$y, 
+                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
+                          dat[[i]]$x)
+
+    form <- as.formula(paste0('d ~ ', paste(names(sim_dat[3:60]), collapse = '+')))
+    match_out <- MatchIt::matchit(form,
+                           data = sim_dat,
+                           method = 'nearest',
+                           distance = 'glm')
+
+    # match_data <- MatchIt::match.data(match_out) 
+    # apply(match_data, 1, unique)
+    form2 <- as.formula(paste0('y ~ d + ', paste(names(sim_dat[3:60]), collapse = '+')))
+
+  tryCatch({
+    psm_out <- lm(form2, 
+                  MatchIt::match.data(match_out), 
+                  weights = weights)
+    psm_list[[i]] <- data.frame(d = psm_out$coefficients[['d']],
+                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
+
+  }, error=function(e){
+    cat("ERROR :",conditionMessage(e), "\n")
+    })
+
+  }
+
+  fail_count <- sum(sapply(psm_list, function(x) is.null(x)))
+  # in case last few are errors
+  fail_count <- ifelse(length(psm_list) == n, fail_count, fail_count + (n - length(psm_list)))
+
+  end_time <- Sys.time()
+
+  return(list(
+    est_df = bind_rows(psm_list),
+    fail_count = fail_count,
+    comp_time = as.numeric(end_time - start_time)/(n-fail_count))
+  )
+}
+
+psm_sim_out <- psm_sim(sim_list) 
+# psm_sim_1000 <- psm_sim(sim_1000) 
+# psm_sim_10000 <- psm_sim(sim_10000)
+
+psm_df <- perform(psm_sim_out$est_df, 'PSM') %>%
+  mutate(fail_count = psm_sim_out$fail_count,
+         comp_time = psm_sim_out$comp_time)
+
+write_csv(psm_df, here('files', 'psm_df2.csv'))
+```
+
+```{r aipw-sim2, eval = F}
+aipw_sim <- function(dat, seed = 185){
+  library(gam)
+
+  start_time <- Sys.time()
+
+  set.seed(seed)
+  n <- length(dat)
+  aipw_list <- list()
+  # fail_count <- 0
+
+  for(i in 1:n){
+    print(paste0(i, ' out of ', n))
+    sim_dat <- data.frame(y = dat[[i]]$y, 
+                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
+                          dat[[i]]$x) %>%
+      mutate(across(where(is.factor), as.character))
+
+    # Need to filter out cases without overlap (CausalGAM does not)
+    treat_levels <- sim_dat %>% 
+      filter(d == 1) %>%
+      select(where(is.character)) %>%
+      sapply(unique)
+    control_levels <- sim_dat %>% 
+      filter(d == 0) %>%
+      select(where(is.character)) %>%
+      sapply(unique)
+
+    for(j in 1:length(treat_levels)){
+      if(!all(c(treat_levels[[j]] %in% control_levels[[j]]),control_levels[[j]] %in% treat_levels[[j]])){
+        # print(names(treat_levels)[j])
+        # print(treat_levels[[j]])
+        # print(control_levels[[j]])
+
+        var_name <- names(treat_levels)[j]
+
+        sim_dat <- sim_dat %>%
+          filter(!!sym(var_name) %in% c(treat_levels[[j]]) &
+                   !!sym(var_name) %in% c(control_levels[[j]]))
+
+        # fail_count <- fail_count + 1
+      }
+    }
+
+    class_vec <- sapply(sim_dat, function(x) class(x))
+    cont_names <- names(sim_dat[, class_vec == 'numeric'])
+    cont_names <- cont_names[3:length(cont_names)]
+    not_cont_names <- names(sim_dat[, class_vec != 'numeric'])
+
+    pscore_form <- as.formula(paste0('d ~ s(', 
+                                     paste(cont_names, collapse = ') + s('), ') +',
+                                     paste(not_cont_names, collapse = ' + ')))
+    outcome_form <- as.formula(paste0('y ~ s(', 
+                                     paste(cont_names, collapse = ') + s('), ') +',
+                                     paste(not_cont_names, collapse = ' + ')))
+
+    tryCatch({
+      aipw_out <- CausalGAM::estimate.ATE(
+      pscore.formula = pscore_form,
+      pscore.family = binomial,
+      outcome.formula.t =outcome_form,
+      outcome.formula.c = outcome_form,
+      outcome.family = gaussian,
+      treatment.var = 'd',
+      data = sim_dat,
+      divby0.action="t",
+      divby0.tol=0.001,
+      var.gam.plot=FALSE,
+      nboot=0)
+
+      aipw_list[[i]] <- data.frame(d = aipw_out$ATE.AIPW.hat,
+                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
+
+  }, error=function(e){
+    cat("ERROR :",conditionMessage(e), "\n")
+    })
+  }
+
+  fail_count <- sum(sapply(aipw_list, function(x) is.null(x)))
+  # in case last few are errors
+  fail_count <- ifelse(length(aipw_list) == n, fail_count, fail_count + (n - length(aipw_list)))
+
+  return(list(
+      est_df = bind_rows(aipw_list),
+      fail_count = fail_count,
+      comp_time = as.numeric(Sys.time() - start_time)/(n-fail_count))
+  )
+}
+
+aipw_out <- aipw_sim(sim_list)
+
+aipw_df <- perform(aipw_out$est_df, 'AIPW') %>%
+  mutate(fail_count = aipw_out$fail_count,
+         comp_time = aipw_out$comp_time)
+
+write_csv(aipw_df,  here('files', 'aipw_df2.csv'))
+
+```
+
+```{r tmle-sim2, eval = F}
+
+tmle_sim <- function(dat){
+  start_time <- Sys.time()
+
+  n <- length(dat)
+
+  tmle_list <- list()
+
+  pscore_form <- as.formula(paste0('A ~ ', 
+                                   paste(names(dat[[1]]$x), collapse = ' + ')))
+  outcome_form <- as.formula(paste0('y ~ A +', 
+                                   paste(names(dat[[1]]$x), collapse = ' + ')))
+
+  for(i in 1:n){
+
+    print(paste0(i, ' out of ', n))
+    sim_dat <- data.frame(Y = dat[[i]]$y, 
+                          A = ifelse(dat[[i]]$z == 'trt', 1, 0), 
+                          dat[[i]]$x)
+
+   tryCatch({
+
+    tmle_out <- tmle::tmle(
+                Y = sim_dat$Y,
+                A = sim_dat$A,
+                W = select(sim_dat, x_1:x_58),
+                Qform = Y ~ .,
+                gform = A ~ .)
+
+      tmle_list[[i]] <- data.frame(d = tmle_out$estimates$ATE$psi,
+                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
+
+  }, error=function(e){
+    cat("ERROR :",conditionMessage(e), "\n")
+    })
+  }
+
+  fail_count <- sum(sapply(tmle_list, function(x) is.null(x)))
+  # in case last few are errors
+  fail_count <- ifelse(length(tmle_list) == n, fail_count, fail_count + (n - length(tmle_list)))
+
+ return(list(
+      est_df = bind_rows(tmle_list),
+      fail_count = fail_count,
+      comp_time = as.numeric(Sys.time() - start_time)/(n-fail_count))
+  )
+}
+
+tmle_out <- tmle_sim(sim_list)
+
+tmle_df <- perform(tmle_out$est_df, 'TMLE') %>%
+  mutate(fail_count = tmle_out$fail_count,
+         comp_time = tmle_out$comp_time)
+
+write_csv(tmle_df, here('files', 'tmle_df2.csv'))
+```
+
+```{r dml-sim2, eval = F}
+dml_sim <- function(dat, seed = 185){
+  library(mlr3)
+  library(mlr3learners)
+
+  start_time <- Sys.time()
+
+  set.seed(seed)
+
+  n <- length(dat)
+
+  dml_list <- list()
+
+  for(i in 1:n){
+    print(paste0(i, ' out of ', n))
+    sim_dat <- data.frame(y = dat[[i]]$y, 
+                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
+                          dat[[i]]$x)
+
+    lgr::get_logger("mlr3")$set_threshold("warn")
+
+    learner = lrn("regr.ranger", num.trees=500, 
+                  max.depth=5, min.node.size=2)
+    ml_l = learner$clone()
+    ml_m = learner$clone()
+
+    tryCatch({
+      dml_out <- DoubleML::DoubleMLPLR$new(
+        DoubleML::DoubleMLData$new(sim_dat,
+                                 y_col = 'y',
+                                 d_cols = 'd',
+                                 x_cols = names(dat[[i]]$x)), 
+        ml_l=ml_l, ml_m=ml_m)
+
+      dml_out$fit()
+      dml_list[[i]] <- data.frame(d = dml_out$all_coef[[1,1]],
+                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
+
+  }, error=function(e){
+    cat("ERROR :",conditionMessage(e), "\n")
+    })
+  }
+
+  fail_count <- sum(sapply(dml_list, function(x) is.null(x)))
+  # in case last few are errors
+  fail_count <- ifelse(length(dml_list) == n, fail_count, fail_count + (n - length(dml_list)))
+
+  return(list(
+      est_df = bind_rows(dml_list),
+      fail_count = fail_count,
+      comp_time = as.numeric(Sys.time() - start_time)/(n-fail_count))
+      )
+}
+
+dml_out <- dml_sim(sim_list)
+
+dml_df <- perform(dml_out$est_df, 'DML') %>%
+  mutate(fail_count = dml_out$fail_count,
+         comp_time = dml_out$comp_time)
+
+write_csv(dml_df, here('files', 'dml_df2.csv'))
+```
+
+```{r dorie-results}
+bind_rows(
+  read_csv(here('files', 'lm_df2.csv')),
+  read_csv(here('files', 'psm_df2.csv')),
+  read_csv(here('files', 'aipw_df2.csv')),
+  read_csv(here('files', 'tmle_df2.csv')),
+  read_csv(here('files', 'dml_df2.csv'))
+  ) %>%
+  select(-comp_time) %>%
+  kableExtra::kable(booktabs = T, 
+                    linesep = '',
+                    caption = 'Results of Monte Carlo simulations using the first 20 datasets from Dorie et al.
+(2019), 5 replications each.
+Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is average computation time measured in seconds for each dataset.')
+```
+
+Results are shown in Table \@ref(tab:dorie-results).
+The methods all have similar levels of bias and error, but AIPW performs better than the other methods on all measures.
+AIPW did fail, however, on the most data sets; the package `CausalGAM` package does not do well with lack of overlap of factor variables between treated and control groups.
+
+## Tests on PISA Data
+
+```{r test-sample, eval = T}
 set.seed(185)
@@
         select(math1, immigrant, mom_ed, dad_ed,
-                          female, early_ed, cultural_pos, home_ed, age) 
-    #sample_n(200)
+                          female, early_ed, cultural_pos, home_ed, age) %>%
+    sample_n(1000)
   )
@@
 
-```{r tmle, eval = F}
+```{r lm-pisa, eval = F}
+lm_out_pisa <- lm(math1 ~ immigrant + mom_ed + dad_ed + 
+                          female + early_ed + cultural_pos + home_ed + age, 
+                   pisa_test) %>%
+  tidy()
+
+lm_df <- data.frame(method = 'OLS',
+                     ATE = pull(lm_out_pisa, estimate)[lm_out_pisa$term == 'immigrant'],
+                     se = pull(lm_out_pisa, std.error)[lm_out_pisa$term == 'immigrant'])
+```
+
+```{r psm-pisa, eval = F}
+match_pisa <- MatchIt::matchit(immigrant ~ mom_ed + dad_ed + 
+                          female + early_ed + cultural_pos + home_ed + age,
+                       data = pisa_test,
+                       method = 'nearest',
+                       distance = 'glm')
+
+psm_out_pisa <- lm(math1 ~ immigrant + mom_ed + dad_ed + 
+                          female + early_ed + cultural_pos + home_ed + age, 
+                   MatchIt::match.data(match_pisa), 
+                   weights = weights)
+
+psm_df <- lmtest::coeftest(psm_out_pisa, 
+                            vcov. = sandwich::vcovCL, 
+                            cluster = ~subclass) %>%
+  tidy()
+
+psm_df <- data.frame(method = 'PSM',
+                     ATE = pull(psm_df, estimate)[psm_df$term == 'immigrant'],
+                     se = pull(psm_df, std.error)[psm_df$term == 'immigrant'])
+```
+
+```{r aipw-pisa, eval = F}
+library(gam)
+
+pisa_test_dummies <- pisa_test %>%
+  select(-early_ed) %>%
+  bind_cols(model.matrix(~ early_ed, data = pisa_test)) %>%
+  as.data.frame()
+
+aipw_pisa_out <- CausalGAM::estimate.ATE(
+        pscore.formula = immigrant ~ s(mom_ed) + s(dad_ed) + female + 
+          `early_ed0-1` + `early_ed1+` + s(cultural_pos) + s(home_ed) + s(age),
+        pscore.family = binomial,
+        outcome.formula.t = math1 ~ s(mom_ed) + s(dad_ed) + female + 
+          `early_ed0-1` + `early_ed1+` + s(cultural_pos) + s(home_ed) + s(age),
+        outcome.formula.c = math1 ~ s(mom_ed) + s(dad_ed) + female + 
+          `early_ed0-1` + `early_ed1+` + s(cultural_pos) + s(home_ed) + s(age),
+        outcome.family = gaussian,
+        treatment.var = 'immigrant',
+        data = pisa_test_dummies,
+        divby0.action="t",
+        divby0.tol=0.001,
+        var.gam.plot=FALSE,
+        nboot = 0)
+
+aipw_df <- data.frame(method = 'AIPW',
+                     ATE = aipw_pisa_out$ATE.AIPW.hat,
+                     se = aipw_pisa_out$ATE.AIPW.asymp.SE)
+```
+
+```{r tmle-pisa, eval = F}
 # Y = outcome
@@
                 Y = math1,
-                A = as.logical(immigrant),
+                A = immigrant,
                 W = select(pisa_test, mom_ed, dad_ed, 
@@
                 verbose = T))
-tmle_out
-
-# pisa %>%
-#  count(match_country, immigrant) %>% View()
-#   arrange(desc(n))
+
+tmle_df <- data.frame(method = 'TMLE',
+           ATE = tmle_out$estimates$ATE$psi,
+           se = sqrt(tmle_out$estimates$ATE$var.psi))
 
@@
               max.depth=5, min.node.size=2)
-ml_g = learner$clone()
+ml_l = learner$clone()
 ml_m = learner$clone()
@@
 
-obj_dml_plr = DoubleML::DoubleMLPLR$new(dml_data, ml_g=ml_g, ml_m=ml_m)
+obj_dml_plr = DoubleML::DoubleMLPLR$new(dml_data, ml_l=ml_l, ml_m=ml_m)
 obj_dml_plr$fit()
-print(obj_dml_plr)
+
+dml_df <- data.frame(method = 'DML',
+           ATE = obj_dml_plr$all_coef,
+           se = obj_dml_plr$se[['immigrant']])
 ```
@@
 
+For the comparison using real data, the analysis uses pooled 2012, 2015, and 2018 waves of the Programme for Student Assessment (PISA), which assesses 15-year-olds’ reading, math, and science skills every three years in dozens of countries worldwide.
+The goal is to estimate an effect of migration, so `r sum(pisa$immigrant == 1)` immigrant adolescents are compared to  `r sum(pisa$immigrant == 0)` non-migrants in their countries of origin.
+Outcome variables consist of reading, math, and science scores, which the OECD constructs to have a global mean of 500 and standard deviation of 100.
+I adjust for the pre-migration characteristics of mother's and father's education (measured in 6-category ISCED, entered as a continuous variable in regressions), cultural possessions, home educational resources, age, a categorical variable for early childhood education and care (ECEC), survey year, and two-category gender.
+
+For these preliminary results, only one group is considered: children born in Albania.
+`r sum(pisa_test$immigrant == 1)` immigrant Albanians are compared to 1,000 non-immigrant Albanians.
+In addition, only math scores are considered.
+Results using different methods are presented in Table \@ref(tab:pisa-results).
+
+Compared to the other methods, OLS regression estimates a more negative effect of migration on math scores.
+However, ATE estimates are fairly similar across the other estimation methods, as are standard errors.
+
+```{r pisa-results}
+# bind_rows(lm_df, psm_df, aipw_df, tmle_df, dml_df)  %>%
+#   write_csv(here('files', 'pisa_df.csv'))
+
+read_csv(here('files', 'pisa_df.csv')) %>%
+  kableExtra::kable(booktabs = T, 
+                    linesep = '',
+                    caption = 'Results of methods tested on PISA math scores for 440 immigrant and 1000 non-immigrant Albanian students.
+The ATE estimates the effect of migration on the math1 test score of 15-year-olds in the survey, with adjustments for parents\' education, cultural possessions, home educational resources, age, a categorical variable for early childhood education and care (ECEC), survey year, and two-category gender.')
+```
+
 # Next Steps
-The Monte Carlo simulations presented here use small sample sizes and few variables, while double robust methods are perhaps most advantageous for large, high-dimensional samples.
-In the final paper, the simulations here will be supplemented samples of 1,000 and 10,000, and all will be replicated 1,000 times.
-Data sets with many covariates will also be simulated.
-The final paper will also test these methods on cross-national PISA test score data and provide R code to implement these methods.
+
+- simulations over more data sets
+- testing methods on larger samples of PISA data
+- R code to implement these methods
 

### 2023-02-17 draft/ms-adj-draft-old.Rmd
new simulations + linear

--- 2022-12-01 draft/ms-adj-draft.Rmd
@@
 # data from mx0.5
-pisa <- readRDS('/Users/nathan/Google Drive/1 UCLA/Dissertation/diss-prop/data/pisa.rds') %>%
+pisa <- readRDS('/Users/nathan/My Drive/1 UCLA/Dissertation/diss-prop/data/pisa.rds') %>%
   mutate(age = as.numeric(age))
@@
     print(paste0(i,',',j))
-    sim_list[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016, i, j, 
-                                                          extraInfo = T)
+    sim_list[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016, 
+                                      i, j, extraInfo = T)
   }
@@
 }
+
+# dat <- sim_list
+# i <- '3,1'
+# 
+# sim_dat <- data.frame(y = dat[[i]]$y, 
+#                           d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
+#                           dat[[i]]$x)
+# lm_out <- lm(y ~ d + ., sim_dat)
+# lm_list[[i]] <- data.frame(d = lm_out$coefficients[['d']],
+#                            truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
+
+sim_linear <- list()
+  for(j in 1:100){ # up to 100
+    print(j)
+    sim_linear[[j]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016, 
+                                      3, j, extraInfo = T)
+
+# sim_list <- sim_linear
 ```
@@
   read_csv(here('files', 'dml_df2.csv'))
+  ) %>%
+  select(-comp_time) %>%
+  kableExtra::kable(booktabs = T, 
+                    linesep = '',
+                    caption = 'Results of Monte Carlo simulations using the first 20 datasets from Dorie et al.
+(2019), 5 replications each.
+Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is average computation time measured in seconds for each dataset.')
+```
+
+```{r dorie-results-linear}
+bind_rows(
+  read_csv(here('files', 'lm_df3.csv')),
+  read_csv(here('files', 'psm_df3.csv')),
+  read_csv(here('files', 'aipw_df3.csv')),
+  read_csv(here('files', 'tmle_df3.csv')),
+  read_csv(here('files', 'dml_df3.csv'))
   ) %>%

### 2023-02-20 draft/ms-adj-draft.Rmd
added lalonde

--- 2022-10-03 draft/ms-adj-draft.Rmd
@@
 
-```{r load}
+```{r, functions}
+perform <- function(est_df, label){
+  est_df %>%
+    summarize(bias = mean(d - truth),
+              percent_bias = bias/sd(d),
+              rmse = sqrt(mean(d - truth)^2),
+              mae = median(abs(d - truth)),
+              fail_count = first(fail_count),
+              comp_time = first(comp_time)) %>%
+    mutate(label = label,
+           n = nrow(est_df) + fail_count) %>%
+    select(label, everything()) %>%
+    return()
+}
+```
+
+```{r load, eval = F}
 # data from mx0.5
-pisa <- readRDS('/Users/nathan/Google Drive/1 UCLA/Dissertation/diss-prop/data/pisa.rds') %>%
+pisa <- readRDS('/Users/nathan/My Drive/1 UCLA/Dissertation/data/pisa.rds') %>%
   mutate(age = as.numeric(age))
@@
 
-<!-- ## Origins of Doubly Robust Methods -->
+## Origins of Doubly Robust Methods
 
-<!-- According to @bang_2005_doubly, doubly robust methods have their origins in missing data models.
+According to @bang_2005_doubly, doubly robust methods have their origins in missing data models.
 @robins_1994_estimation and @rotnitzky_1998_semiparametric developed augmented orthogonal inverse probability-weighted (AIPW) estimators in missing data models, and @scharfstein_1999_adjusting showed that AIPW was doubly robust and extended to causal inference.
--->
 
-<!-- But @kang_2007_demystifying argue that doubly robust methods are older.
+But @kang_2007_demystifying argue that doubly robust methods are older.
 They cite work by @cassel_1976_results, who proposed “generalized regression estimators” for population means from surveys where sampling weights must be estimated.
 Arguably, doubly robust methods go back even further than this.
-The form of doubly robust methods is similar to residual-on-residual regression, which dates back to @frisch_1933_partial famous FWL theorem: -->
+The form of doubly robust methods is similar to residual-on-residual regression, which dates back to @frisch_1933_partial famous FWL theorem:
 
-<!-- $$\beta_D = \frac{\text{Cov}(\tilde Y_i, \tilde D_i)}{\text{Var}(\tilde D_i)}$$ -->
+$$\beta_D = \frac{\text{Cov}(\tilde Y_i, \tilde D_i)}{\text{Var}(\tilde D_i)}$$
 
-<!-- where $\tilde D_i$ is the residual part of $D_i$ after regressing it on $X_i$, and $\tilde Y_i$ is the residual part of $Y_i$ after regressing it on $X_i$.
+where $\tilde D_i$ is the residual part of $D_i$ after regressing it on $X_i$, and $\tilde Y_i$ is the residual part of $Y_i$ after regressing it on $X_i$.
 This formulation writes the regression coefficient as composed of an outcome model ($\tilde Y_i$) and exposure model ($\tilde D_i$), the two models used in doubly robust estimators.
--->
 
-<!-- There are also links between doubly robust methods and matching with regression adjustment.
+There are also links between doubly robust methods and matching with regression adjustment.
 This work goes back to at least @rubin_1973_use, who suggested that regression adjustment in matched data produces less biased estimates that either matching (exposure adjustment) or regression (outcome adjustment) do by themselves.
--->
 
@@
 
-# Preliminary Findings
+# Methods
 
-## Monte Carlo Simulations
+For the comparisons in the next section, estimation methods include ordinary least squares regression ("OLS"),  propensity-score matching with scores estimated from logistic regression using the `MatchIt` package ("PSM"), the augmented inverse propensity weighted estimator with generalized additive models using the `CausalGAM` package (AIPW), targeted maximum likelihood estimation using the `tmle` package (TMLE) with the default Superlearner that relies on the `SL.glm`,` SL.step`, and `GL.glm.interaction` functions, and double/debiased machine learning with random forests with the `DoubleML` and `mlr3` packages.
 
-The structure of these simulations is based on @kang_2007_demystifying.
-For each unit $i = 1, \ldots, n$, let $Z = (z_{i1}, z_{i2}, z_{i3}, z_{i4})^\top$ be distributed independently as $N(0,I)$, where $I$ is the $4 \times 4$ identity matrix.
-Furthermore, let $d_i \in \{0,1\}$ be an indicator for treatment status with a Bernoulli distribution with probability $\pi_i$ of receiving treatment status.
-Values of $\pi_i$ are generated as:
-$$\pi_i = \text{expit}(z_{i1} +0.5z_{i2}-0.33z_{i3} -0.2z_{i4}),$$
-where $\text{expit}(\cdot) = \exp(\cdot)/(1 + \exp(\cdot)).$ These are then used as the probability of treatment assignment in a series of Bernoulli draws for $d_i$. Outcomes $y_i$ are generated as
-$$y_i = 500 + 50d_i + 30z_{i1} -35z_{i2} - 60z_{i3} + 50z_{i4} + \epsilon_i,$$
-where $\epsilon_i \sim N(0,10)$. Now assume that the researcher cannot measure the $z_{ij}$'s. Instead we observe $X = (x_{i1}, x_{i2}, x_{i3}, x_{i4})^\top$ :
-$$\begin{aligned}
-x_{i1} &= \exp(z_{i1}/2) \\
-x_{i2} &= z_2 / (1+\exp(z_{i1})) + 10 \\
-x_{i3} &= (z_{i1} z_{i3} /25 + 0.6)^3 \\
-x_{i4} &= (z_2 + z_4 + 20)^2 \\
-\end{aligned}$$
+# Results
 
-For these preliminary results, datasets of 200 observations are generated 100 times. For each estimation method, three specifications are used:
+## Simluation with Dorie et al. (2019) Data
 
-- "correct": the model is fitted to the true data-generating variables, $Z$
-- "incorrect": the model is fitted to the transformed variables $X$
-- "ovb": the model is fitted to $(x_2, x_3, x_4)^\top$ ($x_1$ is omitted).
+In 2016, the Atlantic Causal Inference Conference hosted a competition for causal inference methods that adjust on observables.
+@dorie_2019_automated published the results of this competition, along with the data used in the competition.
+Below, I test double robust methods on the 20 data sets used for the "do-it-yourself" part of the competition.
+The data represent a hypothetical twins study investigating the impact of birth weight on IQ.
+The data have 4802 observations and 52 covariates.
+The authors of the study specify a different data generating process for the potential outcomes in each data set.
+In all cases, ignorability holds, but the authors vary the following:
 
-Results are shown in Table \@ref(tab:sim-results).
-Estimation methods include ordinary least squares regression ("OLS"),  propensity-score matching with scores estimated from logistic regression using the `MatchIt` package ("PSM"), the augmented inverse propensity weighted estimator with generalized additive models using the `CausalGAM` package (AIPW), targeted maximum likelihood estimation using the `tmle` package (TMLE), and double/debiased machine learning with random forests with the `DoubleML` and `mlr3` packages.
+- degree of nonlinearity
+- percentage of treated
+- overlap for the treatment group
+- alignment (correspondence between the assignment mechanism and the response surface)
+- treatment effect heterogeneity
+- overall magnitude of the treatment effect
 
-Surprisingly, the double robust methods do not necessarily perform better.
-All methods perform well when the true data-generating variables are provided.
-When transformed variables are provided instead, bias, RMSE, and MAE rise for all of the estimation methods, even those that use flexible methods to model the response and treatment assignment surfaces.
-DML performs relatively well but RMSE and MAE still rise somewhat.
-When a variable is omitted, all of the methods perform poorly.
+The 20 data sets used here cover a range of these attributes; see the supplemental material from @dorie_2019_automated for details.
+For these preliminary results, I used 5 simulations of each data set, resulting in 100 data sets.
+I then calculated bias, percent bias (the estimator's bias as a percentage of its standard error), root mean squared error (rmse), and median absolute error (mae).
+I also include the number of data sets for which the method failed and the average computation time for each data set, in seconds.
 
-```{r sim}
-expit <- function(x){exp(x) / (1+exp(x))}
-
-sim_n <- function(n, mu = c(0, 0, 0, 0), Sigma = diag(c(1,1,1,1))){
-  z <- MASS::mvrnorm(n, mu, Sigma)
-  z1 <- z[,1]
-  z2 <- z[,2]
-  z3 <- z[,3]
-  z4 <- z[,4]
-  epsilon <- rnorm(n, 0, 10)
-
-  pi <- expit(z1 + 0.5*z2 -.33*z3 - .2*z4)
-  d <- rbinom(n, 1, pi)
-
-  y <- 475 + 50*d + 30*z1 -35*z2 - 60*z3 + 50*z4 + epsilon
-
-  x1 <- exp(z1/2)
-  x2 <- z2 / (1+exp(z1)) + 10
-  x3 <- (z1 * z3 / 25 + 0.6)^3
-  x4 <- (z2 * z4 + 20)^2
-  return(data.frame(
-    z1 = z1,
-    z2 = z2,
-    z3 = z3,
-    z4 = z4,
-    pi = pi,
-    d = d,
-    y = y,
-    x1 = x1,
-    x2 = x2, 
-    x3 = x3,
-    x4 = x4
-  ))
+```{r dorie-sim, eval = F}
+set.seed(185)
+sim_list <- list()
+for(i in 1:20){ # up to 77
+  #sim_list_nest <- list()
+  for(j in 1:10){ # up to 100
+    print(paste0(i,',',j))
+    sim_list[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016, 
+                                      i, j, extraInfo = T)
+  }
+  #sim_list[[i]] <- sim_list_nest
 }
 
-set.seed(1858)
-sim_200 <- replicate(100, sim_n(200), simplify = F)
-sim_1000 <- replicate(100, sim_n(1000), simplify = F)
-sim_10000 <- replicate(100, sim_n(10000), simplify = F)
+# dat <- sim_list
+# i <- '3,1'
+# 
+# sim_dat <- data.frame(y = dat[[i]]$y, 
+#                           d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
+#                           dat[[i]]$x)
+# lm_out <- lm(y ~ d + ., sim_dat)
+# lm_list[[i]] <- data.frame(d = lm_out$coefficients[['d']],
+#                            truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
+
+sim_linear <- list()
+for(i in c(1, 3))
+  for(j in 1:100){ 
+    print(paste0(i,',',j))
+    sim_linear[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016, 
+                                      3, j, extraInfo = T)
+  }
+}
+
 ```
@@
 lm_sim <- function(dat){
+  start_time <- Sys.time()
   n <- length(dat)
-  lm_list_true <- list()
-  lm_list_false <- list()
-  lm_list_ovb <- list()
+  lm_list <- list()
   for(i in 1:n){
-    lm_out_true <- lm(y ~ d + z1 + z2 + z3 + z4, dat[[i]])
-    lm_list_true[[i]] <- lm_out_true$coefficients[['d']]
+    print(paste0(i, ' out of ', n))
+    sim_dat <- data.frame(y = dat[[i]]$y, 
+                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
+                          dat[[i]]$x)
 
-    lm_out_false <- lm(y ~ d + x1 + x2 + x3 + x4, dat[[i]])
-    lm_list_false[[i]] <- lm_out_false$coefficients[['d']]
+    tryCatch({
+      lm_out <- tidy(lm(y ~ d + ., sim_dat))
+      lm_list[[i]] <- data.frame(d = lm_out[[2,2]],
+                                 se = lm_out[[2,3]],
+                                 truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
+      }, error=function(e){
+        cat("ERROR :",conditionMessage(e), "\n")
+        })
 
-    lm_out_ovb <- lm(y ~ d + x2 + x3 + x4, dat[[i]])
-    lm_list_ovb[[i]] <- lm_out_ovb$coefficients[['d']]
   }
 
+  fail_count <- sum(sapply(lm_list, function(x) is.null(x)))
+  # in case last few are errors
+  fail_count <- ifelse(length(lm_list) == n, fail_count, fail_count + (n - length(lm_list)))
+
+  end_time <- Sys.time()
+
   return(list(
-    n = nrow(dat[[i]]),
-    correct = unlist(lm_list_true),
-    incorrect = unlist(lm_list_false),
-    ovb = unlist(lm_list_ovb)))
+    est_df = bind_rows(lm_list),
+    fail_count = fail_count,
+    comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
+    )
 }
 
-perform <- function(est_list, label){
-  perform_list <- list()
+lm_sim_out <- lm_sim(sim_list) 
+lm_sim_linear <- lm_sim(sim_linear)
 
-  for(i in 1:(length(est_list)-1)){
-    est <- unlist(est_list[[i+1]])
-    bias <- mean(est-50)
-    percent_bias <- 100 * bias / sd(est)
-    rmse <- sqrt(mean((est - 50)^2))
-    mae <- median(abs(est - 50))
+lm_df <- lm_sim_out$est_df %>%
+  mutate(fail_count = lm_sim_out$fail_count,
+         comp_time = lm_sim_out$comp_time)
 
-    perform_list[[i]] <- data.frame(label = label, n = est_list[['n']], 
-                                    model = names(est_list)[i+1], 
-                                    bias, percent_bias, rmse, mae)
-  }
-  return(bind_rows(perform_list))
-}
-
-lm_sim_200 <- lm_sim(sim_200) 
-# lm_sim_1000 <- lm_sim(sim_1000) 
-# lm_sim_10000 <- lm_sim(sim_10000)
-
-lm_df <- bind_rows(
-  perform(lm_sim_200, 'OLS'),
-  )
+lm_df_linear <- lm_sim_linear$est_df %>%
+  mutate(fail_count = lm_sim_linear$fail_count,
+         comp_time = lm_sim_linear$comp_time)
 
 write_csv(lm_df, here('files', 'lm_df.csv'))
+write_csv(lm_df_linear, here('files', 'lm_df_linear.csv'))
+
+# lm_lalonde <- lm_sim(lalonde)
+
 ```
@@
 psm_sim <- function(dat){
+  start_time <- Sys.time()
   n <- length(dat)
-  psm_list_true <- list()
-  psm_list_false <- list()
-  lm_list_ovb <- list()
+  psm_list <- list()
   for(i in 1:n){
-    match_true <- MatchIt::matchit(d ~ z1 + z2 + z3 + z4,
-                           data = dat[[i]],
+    print(paste0(i, ' out of ', n))
+    sim_dat <- data.frame(y = dat[[i]]$y, 
+                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
+                          dat[[i]]$x)
+
+    form <- as.formula(paste0('d ~ ', paste(names(dat[[i]]$x), collapse = '+')))
+    match_out <- MatchIt::matchit(form,
+                           data = sim_dat,
                            method = 'nearest',
@@
 
-    psm_out_true <- lm(y ~ d + z1 + z2 + z3 + z4, 
-                       MatchIt::match.data(match_true), 
-                       weights = weights)
+    # match_data <- MatchIt::match.data(match_out) 
+    # apply(match_data, 1, unique)
+    form2 <- as.formula(paste0('y ~ d + ', paste(names(dat[[i]]$x), collapse = '+')))
 
-    match_false <- MatchIt::matchit(d ~ x1 + x2 + x3 + x4,
-                           data = dat[[i]],
-                           method = 'nearest',
-                           distance = 'glm')
+  tryCatch({
+    psm_out <- lm(form2, 
+                  MatchIt::match.data(match_out), 
+                  weights = weights) %>%
+      tidy()
+    psm_list[[i]] <- data.frame(d = psm_out[[2,2]],
+                                se = psm_out[[2,3]],
+                                truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
 
-    psm_out_false <- lm(y ~ d + x1 + x2 + x3 + x4, 
-                       MatchIt::match.data(match_false), 
-                       weights = weights)
+  }, error=function(e){
+    cat("ERROR :",conditionMessage(e), "\n")
+    })
 
-    match_ovb <- MatchIt::matchit(d ~ x2 + x3 + x4,
-                           data = dat[[i]],
-                           method = 'nearest',
-                           distance = 'glm')
-
-    psm_out_ovb <- lm(y ~ d + x2 + x3 + x4, 
-                       MatchIt::match.data(match_false), 
-                       weights = weights)
-
-    psm_list_true[[i]] <- psm_out_true$coefficients[['d']]
-    psm_list_false[[i]] <- psm_out_false$coefficients[['d']]
-    psm_list_ovb[[i]] <- psm_out_ovb$coefficients[['d']]
   }
 
-  return(list(n = nrow(dat[[i]]),
-              correct = unlist(psm_list_true),
-              incorrect = unlist(psm_list_false),
-              ovb = unlist(psm_list_ovb)))
+  fail_count <- sum(sapply(psm_list, function(x) is.null(x)))
+  # in case last few are errors
+  fail_count <- ifelse(length(psm_list) == n, fail_count, fail_count + (n - length(psm_list)))
+
+  end_time <- Sys.time()
+
+  return(list(
+    est_df = bind_rows(psm_list),
+    fail_count = fail_count,
+    comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
+  )
 }
 
-psm_sim_200 <- psm_sim(sim_200) 
-# psm_sim_1000 <- psm_sim(sim_1000) 
-# psm_sim_10000 <- psm_sim(sim_10000)
+psm_sim_out <- psm_sim(sim_list) 
+psm_sim_linear <- psm_sim(sim_linear)
 
-psm_df <- bind_rows(
-  perform(psm_sim_200, 'PSM'),
-  )
+psm_df <- psm_sim_out$est_df %>%
+  mutate(fail_count = psm_sim_out$fail_count,
+         comp_time = psm_sim_out$comp_time)
+
+psm_df_linear <- psm_sim_linear$est_df %>%
+  mutate(fail_count = psm_sim_linear$fail_count,
+         comp_time = psm_sim_linear$comp_time)
 
 write_csv(psm_df, here('files', 'psm_df.csv'))
+write_csv(psm_df_linear, here('files', 'psm_df_linear.csv'))
 ```
@@
 aipw_sim <- function(dat, seed = 185){
-  library(gam)
+
+  start_time <- Sys.time()
 
@@
   n <- length(dat)
-  aipw_list_true <- list()
-  aipw_list_false <- list()
-  aipw_list_ovb <- list()
+  aipw_list <- list()
+  # fail_count <- 0
 
   for(i in 1:n){
+    print(paste0(i, ' out of ', n))
+    sim_dat <- data.frame(y = dat[[i]]$y, 
+                          d = as.numeric(ifelse(dat[[i]]$z == 'trt', 1, 0)), 
+                          dat[[i]]$x)
 
-    print(i)
+    tryCatch({
+      sim_dat <- sim_dat %>%
+        fastDummies::dummy_cols(remove_first_dummy = T, remove_selected_columns = T) 
+      }, error=function(e){
+      })
 
-    correct <- CausalGAM::estimate.ATE(
-        pscore.formula = d ~ s(z1) + s(z2) + s(z3) + s(z4),
-        pscore.family = binomial,
-        outcome.formula.t = y ~ s(z1) + s(z2) + s(z3) + s(z4),
-        outcome.formula.c = y ~ s(z1) + s(z2) + s(z3) + s(z4),
-        outcome.family = gaussian,
-        treatment.var = 'd',
-        data=dat[[i]],
-        divby0.action="t",
-        divby0.tol=0.001,
-        var.gam.plot=FALSE,
-        nboot=50)
+    tryCatch({
+      forest <- grf::causal_forest(X = select(sim_dat, 3:length(names(sim_dat))), 
+                                   Y = sim_dat$y, W = sim_dat$d)
+      # forest <- grf::causal_forest(X = select(sim_dat, starts_with('x')), 
+      #                              Y = sim_dat$y, W = sim_dat$d)
 
-    incorrect <- CausalGAM::estimate.ATE(
-        pscore.formula = d ~ s(x1) + s(x2) + s(x3) + s(x4),
-        pscore.family = binomial,
-        outcome.formula.t = y ~ s(x1) + s(x2) + s(x3) + s(x4),
-        outcome.formula.c = y ~ s(x1) + s(x2) + s(x3) + s(x4),
-        outcome.family = gaussian,
-        treatment.var = 'd',
-        data=dat[[i]],
-        divby0.action="t",
-        divby0.tol=0.001,
-        var.gam.plot=FALSE,
-        nboot=50)
+      aipw_out <- grf::average_treatment_effect(forest, target.sample = 'treated', method = 'AIPW')
 
-    ovb <- CausalGAM::estimate.ATE(
-        pscore.formula = d ~ s(x2) + s(x3) + s(x4),
-        pscore.family = binomial,
-        outcome.formula.t = y ~ s(x2) + s(x3) + s(x4),
-        outcome.formula.c = y ~ s(x2) + s(x3) + s(x4),
-        outcome.family = gaussian,
-        treatment.var = 'd',
-        data=dat[[i]],
-        divby0.action="t",
-        divby0.tol=0.001,
-        var.gam.plot=FALSE,
-        nboot=50)
+      aipw_list[[i]] <- data.frame(d = aipw_out[[1]],
+                                   se = aipw_out[[2]],
+                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
 
-    aipw_list_true[[i]] <- correct$ATE.AIPW.hat
-    aipw_list_false[[i]] <- incorrect$ATE.AIPW.hat
-    aipw_list_ovb[[i]] <- ovb$ATE.AIPW.hat
+  }, error=function(e){
+    cat("ERROR :",conditionMessage(e), "\n")
+    })
   }
 
-  return(list(n = nrow(dat[[i]]),
-              correct = unlist(aipw_list_true),
-              incorrect = unlist(aipw_list_false),
-              ovb = unlist(aipw_list_ovb)))
+  fail_count <- sum(sapply(aipw_list, function(x) is.null(x)))
+  # in case last few are errors
+  fail_count <- ifelse(length(aipw_list) == n, fail_count, fail_count + (n - length(aipw_list)))
+
+  end_time <- Sys.time()
+
+  return(list(
+      est_df = bind_rows(aipw_list),
+      fail_count = fail_count,
+      comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
+  )
 }
 
-aipw_out <- aipw_sim(sim_200)
+aipw_out <- aipw_sim(sim_list)
+aipw_out_linear <- aipw_sim(sim_linear)
 
-aipw_df <- perform(aipw_out, 'AIPW')
+aipw_df <- aipw_out$est_df %>%
+  mutate(fail_count = aipw_out$fail_count,
+         comp_time = aipw_out$comp_time)
+
+aipw_df_linear <- aipw_out_linear$est_df %>%
+  mutate(fail_count = aipw_out_linear$fail_count,
+         comp_time = aipw_out_linear$comp_time)
 
 write_csv(aipw_df,  here('files', 'aipw_df.csv'))
+write_csv(aipw_df_linear,  here('files', 'aipw_df_linear.csv'))
 
@@
 
-tmle_sim <- function(dat){
+tmle_sim <- function(dat, seed = 185){
+  start_time <- Sys.time()
+
+  set.seed(seed)
   n <- length(dat)
-
-  tmle_list_true_true <- list()
-  tmle_list_false_true <- list()
-  tmle_list_true_false <- list()
-  tmle_list_false_false <- list()
-  tmle_list_ovb_ovb <- list()
+  tmle_list <- list()
+  # fail_count <- 0
 
   for(i in 1:n){
+    print(paste0(i, ' out of ', n))
+    sim_dat <- data.frame(y = dat[[i]]$y, 
+                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
+                          dat[[i]]$x)
 
-    print(i)
+    tryCatch({
+      sim_dat <- sim_dat %>%
+        fastDummies::dummy_cols(remove_first_dummy = T, remove_selected_columns = T) 
+      }, error=function(e){
+      })
 
-    tmle_false_false <- with(
-      dat[[i]],
-      tmle::tmle(
-        Y = y,
-        A = d,
-        W = data.frame(z1, z2, z3, z4, x1, x2, x3, x4),
-        Qform = Y ~ A + x1 + x2 + x3 + x4,
-        gform = A ~ x1 + x2 + x3 + x4))
+    tryCatch({
+      forest <- grf::causal_forest(X = select(sim_dat, 3:length(names(sim_dat))), 
+                                   Y = sim_dat$y, W = sim_dat$d)
+      # forest <- grf::causal_forest(X = select(sim_dat, starts_with('x')), 
+      #   Y = sim_dat$y, W = sim_dat$d)
 
-    tmle_false_true <- with(
-      dat[[i]],
-      tmle::tmle(
-        Y = y,
-        A = d,
-        W = data.frame(z1, z2, z3, z4, x1, x2, x3, x4),
-        Qform = Y ~ A + x1 + x2 + x3 + x4,
-        gform = A ~ z1 + z2 + z3 + z4))
+      tmle_out <- grf::average_treatment_effect(forest, target.sample = 'treated', method = 'TMLE')
 
-    tmle_true_false <- with(
-      dat[[i]],
-      tmle::tmle(
-        Y = y,
-        A = d,
-        W = data.frame(z1, z2, z3, z4, x1, x2, x3, x4),
-        Qform = Y ~ A + z1 + z2 + z3 + z4,
-        gform = A ~ x1 + x2 + x3 + x4))
+      tmle_list[[i]] <- data.frame(d = tmle_out[[1]],
+                                   se = tmle_out[[2]],
+                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
 
-    tmle_true_true <- with(
-      dat[[i]],
-      tmle::tmle(
-        Y = y,
-        A = d,
-        W = data.frame(z1, z2, z3, z4, x1, x2, x3, x4),
-        Qform = Y ~ A + z1 + z2 + z3 + z4,
-        gform = A ~ z1 + z2 + z3 + z4))
-
-    tmle_ovb_ovb <- with(
-      dat[[i]],
-      tmle::tmle(
-        Y = y,
-        A = d,
-        W = data.frame(x2, x3, x4),
-        Qform = Y ~ A + x2 + x3 + x4,
-        gform = A ~ x2 + x3 + x4))
-
-    tmle_list_true_true[[i]] <- tmle_true_true$estimates$ATE$psi
-    tmle_list_true_false[[i]] <- tmle_true_false$estimates$ATE$psi
-    tmle_list_false_true[[i]] <- tmle_false_true$estimates$ATE$psi
-    tmle_list_false_false[[i]] <- tmle_false_false$estimates$ATE$psi
-    tmle_list_ovb_ovb[[i]] <- tmle_ovb_ovb$estimates$ATE$psi
+  }, error=function(e){
+    cat("ERROR :",conditionMessage(e), "\n")
+    })
   }
 
-  return(list(n = nrow(dat[[i]]),
-              correct_correct = unlist(tmle_list_true_true),
-              correct_incorrect = unlist(tmle_list_true_false),
-              incorrect_correct = unlist(tmle_list_false_true),
-              incorrect_incorrect = unlist(tmle_list_false_false),
-              ovb = unlist(tmle_list_ovb_ovb))
+  fail_count <- sum(sapply(tmle_list, function(x) is.null(x)))
+  # in case last few are errors
+  fail_count <- ifelse(length(tmle_list) == n, fail_count, fail_count + (n - length(tmle_list)))
+
+  end_time <- Sys.time()
+
+ return(list(
+      est_df = bind_rows(tmle_list),
+      fail_count = fail_count,
+      comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
   )
@@
 
-tmle_out <- tmle_sim(sim_200)
+tmle_out <- tmle_sim(sim_list)
+tmle_out_linear <- tmle_sim(sim_linear)
 
-tmle_df <- perform(tmle_out, 'TMLE')
+tmle_df <- tmle_out$est_df %>%
+  mutate(fail_count = tmle_out$fail_count,
+         comp_time = tmle_out$comp_time)
+
+tmle_df_linear <- tmle_out_linear$est_df %>%
+  mutate(fail_count = tmle_out_linear$fail_count,
+         comp_time = tmle_out_linear$comp_time)
 
 write_csv(tmle_df, here('files', 'tmle_df.csv'))
+write_csv(tmle_df_linear, here('files', 'tmle_df_linear.csv'))
 ```
@@
 
+  start_time <- Sys.time()
+
   set.seed(seed)
@@
 
-  correct_list <- list()
-  incorrect_list <- list()
-  ovb_list <- list()
+  dml_list <- list()
 
   for(i in 1:n){
-    print(i)
+    print(paste0(i, ' out of ', n))
+    sim_dat <- data.frame(y = dat[[i]]$y, 
+                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
+                          dat[[i]]$x)
 
@@
 
-    correct = DoubleML::DoubleMLPLR$new(
-      DoubleML::DoubleMLData$new(dat[[i]],
+    tryCatch({
+      dml_out <- DoubleML::DoubleMLPLR$new(
+        DoubleML::DoubleMLData$new(sim_dat,
                                  y_col = 'y',
                                  d_cols = 'd',
-                                 x_cols = c('z1', 'z2', 'z3', 'z4')), 
+                                 x_cols = names(dat[[i]]$x)), 
         ml_l=ml_l, ml_m=ml_m)
-    correct$fit()
-    correct_list[[i]] <- correct$all_coef[[1,1]]
 
-    incorrect = DoubleML::DoubleMLPLR$new(
-      DoubleML::DoubleMLData$new(dat[[i]],
-                                 y_col = 'y',
-                                 d_cols = 'd',
-                                 x_cols = c('x1', 'x2', 'x3', 'x4')), 
-      ml_l=ml_l, ml_m=ml_m)
-    incorrect$fit()
-    incorrect_list[[i]] <- incorrect$all_coef[[1,1]]
+      dml_out$fit()
+      dml_list[[i]] <- data.frame(d = dml_out$all_coef[[1,1]],
+                                  se = dml_out$all_se[[1,1]],
+                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
 
-    ovb = DoubleML::DoubleMLPLR$new(
-      DoubleML::DoubleMLData$new(dat[[i]],
-                                 y_col = 'y',
-                                 d_cols = 'd',
-                                 x_cols = c('x2', 'x3', 'x4')), 
-      ml_l=ml_l, ml_m=ml_m)
-    ovb$fit()
-    ovb_list[[i]] <- ovb$all_coef[[1,1]]
+  }, error=function(e){
+    cat("ERROR :",conditionMessage(e), "\n")
+    })
+  }
 
-  }
-  return(list(n = nrow(dat[[i]]),
-              correct = unlist(correct_list),
-              incorrect = unlist(incorrect_list),
-              ovb = unlist(ovb_list))
+  fail_count <- sum(sapply(dml_list, function(x) is.null(x)))
+  # in case last few are errors
+  fail_count <- ifelse(length(dml_list) == n, fail_count, fail_count + (n - length(dml_list)))
+
+  end_time <- Sys.time()
+
+  return(list(
+      est_df = bind_rows(dml_list),
+      fail_count = fail_count,
+      comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
       )
@@
 
-dml_out <- dml_sim(sim_200)
+dml_out <- dml_sim(sim_list)
+dml_out_linear <- dml_sim(sim_linear)
 
-dml_df <- perform(dml_out, 'DML')
+dml_df <- dml_out$est_df %>%
+  mutate(fail_count = dml_out$fail_count,
+         comp_time = dml_out$comp_time)
+dml_df_linear <- dml_out_linear$est_df %>%
+  mutate(fail_count = dml_out_linear$fail_count,
+         comp_time = dml_out_linear$comp_time)
 
 write_csv(dml_df, here('files', 'dml_df.csv'))
+write_csv(dml_df_linear, here('files', 'dml_df_linear.csv'))
 ```
 
-```{r sim-results}
+```{r dorie-results}
 bind_rows(
-  read_csv(here('files', 'lm_df.csv')),
-  read_csv(here('files', 'psm_df.csv')),
-  read_csv(here('files', 'aipw_df.csv')),
-  read_csv(here('files', 'tmle_df.csv')) %>%
-    filter(model %in% c('correct_correct', 'incorrect_incorrect', 'ovb')) %>%
-    mutate(model = c('correct', 'incorrect', 'ovb')),
-  read_csv(here('files', 'dml_df.csv'))
+  perform(read_csv(here('files', 'lm_df.csv')), 'lm'),
+  perform(read_csv(here('files', 'psm_df.csv')), 'psm'),
+  perform(read_csv(here('files', 'aipw_df.csv')), 'aipw'),
+  perform(read_csv(here('files', 'tmle_df.csv')), 'tmle'),
+  perform(read_csv(here('files', 'dml_df.csv')), 'dml')
   ) %>%
   kableExtra::kable(booktabs = T, 
+                    digits = 3,
                     linesep = '',
-                    caption = 'Results of Monte Carlo simulations over 100 replications.
-Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, and mae is median absolute error.')
+                    caption = 'Results of Monte Carlo simulations using the first 20 datasets from Dorie et al.
+(2019), 5 replications each.
+Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is average computation time measured in seconds for each dataset.')
 ```
 
-```{r test-sample, eval = F}
-set.seed(185)
-pisa_test <- bind_rows(
-  pisa %>%
-    filter(match_country == 'Albania', immigrant == T) %>%
-    select(math1, immigrant, mom_ed, dad_ed,
-                          female, early_ed, cultural_pos, home_ed, age) ,
-    #sample_n(200),
-  pisa %>%
-    filter(match_country == 'Albania', immigrant == F) %>%
-        select(math1, immigrant, mom_ed, dad_ed,
-                          female, early_ed, cultural_pos, home_ed, age) 
-    #sample_n(200)
-  )
-
-# pisa_test <- pisa %>%
-#     filter(match_country == 'Albania') %>%
-#  select(math1, immigrant, mom_ed, dad_ed,
-#                          female, early_ed, cultural_pos, home_ed, age)
-
-#  filter(match_country %in% c('Portugal', 'Germany', 'United States'))
+```{r dorie-results-linear}
+bind_rows(
+  perform(read_csv(here('files', 'lm_df_linear.csv')), 'lm'),
+  perform(read_csv(here('files', 'psm_df_linear.csv')), 'psm'),
+  perform(read_csv(here('files', 'aipw_df_linear.csv')), 'aipw'),
+  perform(read_csv(here('files', 'tmle_df_linear.csv')), 'tmle'),
+  perform(read_csv(here('files', 'dml_df_linear.csv')), 'dml')
+  ) %>%
+  kableExtra::kable(booktabs = T, 
+                    digits = 3,
+                    linesep = '',
+                    caption = 'Results of Monte Carlo simulations using the linear DGP for dataset 3 from Dorie et al.
+(2019), 5 replications each.
+Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is average computation time measured in seconds for each dataset.')
 ```
 
-```{r tmle, eval = F}
-# Y = outcome
-# A = binary treatment
-# W = covariates
+Results are shown in Table \@ref(tab:dorie-results).
+The methods all have similar levels of bias and error, but AIPW performs better than the other methods on all measures.
+AIPW did fail, however, on the most data sets; the package `CausalGAM` package does not do well with lack of overlap of factor variables between treated and control groups.
 
-tmle_out <- with(pisa_test, tmle::tmle(
-                Y = math1,
-                A = as.logical(immigrant),
-                W = select(pisa_test, mom_ed, dad_ed, 
-                          female, early_ed, cultural_pos, home_ed, age),
-                verbose = T))
-tmle_out
+```{r lalonde-data}
+unemp_func <- function(x){
+  x %>%
+    as.data.frame() %>%
+    mutate(re74_0 = re74 == 0,
+         re75_0 = re75 == 0) 
+}
 
-# pisa %>%
-#  count(match_country, immigrant) %>% View()
-#   arrange(desc(n))
-
+lalonde_exp <- read_dta(here('data', 'nsw.dta')) %>%
+  as.data.frame() %>%
+  mutate(re75_0 = re75 == 0)
+lalonde_exp_74 <- read_dta(here('data', 'nsw_dw.dta')) %>%
+  unemp_func()
+lalonde_cps1_controls <- read_dta(here('data', 'cps_controls.dta')) %>%
+  unemp_func()
+lalonde_cps3_controls <- read_dta(here('data', 'cps_controls3.dta')) %>%
+  unemp_func()
+lalonde_psid1_controls <- read_dta(here('data', 'psid_controls.dta')) %>%
+  unemp_func()
+lalonde_psid3_controls <- read_dta(here('data', 'psid_controls3.dta')) %>%
+  unemp_func()
 ```
 
-```{r dml, eval = F}
-dml_data <- DoubleML::DoubleMLData$new(as.data.frame(pisa_test),
-                y_col = 'math1',
-                d_cols = 'immigrant',
-                x_cols = c('mom_ed', 'dad_ed', 'female', 'early_ed', 
-                'cultural_pos', 'home_ed', 'age'))
+## Comparisons using LaLonde NSW Data
 
-library(mlr3)
-library(mlr3learners)
-# surpress messages from mlr3 package during fitting
-lgr::get_logger("mlr3")$set_threshold("warn")
+As another benchmark test, I use data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NWS), as provided by @dehejia_1999_causal.
+The NWS randomly provided training to disadvantaged workers, allowing an experimental estimate of the effect of the intervention.
+This study had `r nrow(filter(lalonde_exp, treat == T))` treated and `r nrow(filter(lalonde_exp, treat == F))` control participants
 
-learner = lrn("regr.ranger", num.trees=500, 
-              max.depth=5, min.node.size=2)
-ml_g = learner$clone()
-ml_m = learner$clone()
+LaLonde compared these experimental estimates to estimates comparing the treated group to samples drawn from the Panel Study of Income Dynamics (PSID) and Westat's Matched Current Population Survey-Social Security Administration File (CPS).
+The PSID-1 sample (*n* = `r nrow(lalonde_psid1_controls)`) contains all male household heads under 55 who did not classify themselves as retired in 1975, and the PSID-3 sample (*n* = `r nrow(lalonde_psid3_controls)`) further restricts this to men who were not working in spring of 1976 or 1975.
+The CPS-1 sample (*n* = `r nrow(lalonde_cps1_controls)`) includes all CPS males under 55, and CPS-3 (*n* = `r nrow(lalonde_cps3_controls)`) restricts this two those who were not working in March 1976 whose income in 1975 was below the poverty level.
+Restricting these observational samples is meant to get closer to the population eligible for the NWS.
 
-set.seed(185)
+Following @dehejia_1999_causal, I present results for the original samples analyzed by @lalonde_1986_evaluating, but I also include results using a subsample of the experimental group that has 1974 earnings data available (`r nrow(filter(lalonde_exp_74, treat == T))` treated and `r nrow(filter(lalonde_exp_74, treat == F))` control participants).
 
-obj_dml_plr = DoubleML::DoubleMLPLR$new(dml_data, ml_g=ml_g, ml_m=ml_m)
-obj_dml_plr$fit()
-print(obj_dml_plr)
+I again compare the three double robust methods to a linear model fitted by OLS ("lm") and propensity score matching using logistic regression ("psm").
+Results are presented in Table \@ref(tab:lalonde).
+
+For the original NSW data, none of the methods perform especially well.
+For the PSID samples, none of the estimates have a positive sign, as in the experimental estimates.
+For CPS, TMLE is the only method that achieves a positive sign.
+
+Including 1974 earnings data allows much better estimates with the observational control groups.
+(Note that the restricted experimental sample has a greater experimental effect estimate than the full experimental sample.) For PSID-1, TMLE performs the best, while DML performs much worse than even OLS.
+For PSID-3, OLS and TMLE both perform well.
+For CPS-1 and CPS-3, TMLE performs the best.
+
+```{r lalonde-calc, eval = F}
+lalonde_func <- function(dataset, sample, include_74 = F){
+  set.seed(872)
+
+  if(include_74 == F){
+    lalonde_variables <- names(lalonde_exp)[3:9]
+    dataset <- bind_rows(filter(lalonde_exp, treat == 1), dataset)
+
+  } else {
+    lalonde_variables <- names(lalonde_exp_74)[3:10]
+    dataset <- bind_rows(filter(lalonde_exp_74, treat == 1), dataset)
+  }
+
+  dataset <- list(list(y = dataset$re78,
+                z = ifelse(dataset$treat == 1, 'trt', 'ctl'),
+                x = dataset[,lalonde_variables]))
+
+  lapply(list(
+    lm_sim(dataset),
+    psm_sim(dataset),
+    aipw_sim(dataset),
+    tmle_sim(dataset),
+    dml_sim(dataset)),
+  bind_cols) %>%
+    bind_rows() %>%
+    mutate(method = c('lm', 'psm', 'aipw', 'tmle', 'dml'),
+           sample = sample,
+           estimate = paste0(round(d), ' (', round(se), ')')) %>%
+    select(method, sample, estimate) 
+}
+
+bind_rows(
+  lalonde_func(filter(lalonde_exp, treat == 0), sample = 'experimental'),
+  lalonde_func(lalonde_psid1_controls, 'PSID-1'),
+  lalonde_func(lalonde_psid3_controls, 'PSID-3'),
+  lalonde_func(lalonde_cps1_controls, 'CPS-1'),
+  lalonde_func(lalonde_cps1_controls, 'CPS-3')) %>%
+    pivot_wider(names_from = 'sample', values_from = estimate) %>%
+  write_csv(here('files', 'lalonde.csv'))
+
+bind_rows(
+  lalonde_func(filter(lalonde_exp_74, treat == 0), sample = 'experimental', T),
+  lalonde_func(lalonde_psid1_controls, 'PSID-1', T),
+  lalonde_func(lalonde_psid3_controls, 'PSID-3', T),
+  lalonde_func(lalonde_cps1_controls, 'CPS-1', T),
+  lalonde_func(lalonde_cps1_controls, 'CPS-3', T)) %>%
+    pivot_wider(names_from = 'sample', values_from = estimate) %>%
+  write_csv(here('files', 'lalonde_74.csv'))
+# 
+# lalonde_cps1 <- bind_rows(filter(lalonde_exp, treat == 1), lalonde_cps1_controls)
+# lalonde_cps3 <- bind_rows(filter(lalonde_exp, treat == 1), lalonde_cps3_controls)
+# 
+# lalonde_exp <- list(list(y = as.numeric(lalonde_exp$re78),
+#                 z = ifelse(lalonde_exp$treat == 1, 'trt', 'ctl'),
+#                 x = lalonde_exp[,lalonde_variables]))
+# lalonde_cps1 <- list(list(y = lalonde_cps1$re78,
+#                 z = ifelse(lalonde_cps1$treat == 1, 'trt', 'ctl'),
+#                 x = lalonde_cps1[,lalonde_variables]))
+# lalonde_cps3 <- list(list(y = lalonde_cps3$re78,
+#                 z = ifelse(lalonde_cps3$treat == 1, 'trt', 'ctl'),
+#                 x = lalonde_cps3[,lalonde_variables]))
+# 
+# 
+# set.seed(185)
+# lapply(list(
+#     lm_sim(lalonde_exp),
+#     lm_sim(lalonde_cps1),
+#     lm_sim(lalonde_cps3),
+#     psm_sim(lalonde_exp),
+#     psm_sim(lalonde_cps1),
+#     psm_sim(lalonde_cps3),
+#     aipw_sim(lalonde_exp),
+#     aipw_sim(lalonde_cps1),
+#     aipw_sim(lalonde_cps3),
+#     tmle_sim(lalonde_exp),
+#     tmle_sim(lalonde_cps1),
+#     tmle_sim(lalonde_cps3),
+#     dml_sim(lalonde_exp),
+#     dml_sim(lalonde_cps1),
+#     dml_sim(lalonde_cps3)), 
+#   bind_cols) %>% 
+#   bind_rows()  %>%
+#   mutate(method = rep(c('lm', 'psm', 'aipw', 'tmle', 'dml'), each = 3),
+#          sample = rep(c('experimental', 'CPS-1', 'CPS-3'), 5),
+#          estimate = paste0(round(d), ' (', round(se), ')')) %>%
+#   select(method, sample, estimate) %>%
+#   pivot_wider(names_from = 'sample', values_from = estimate) %>%
+#  write_csv(here('files', 'lalonde_74.csv'))
+
+# lalonde <- CBPS::LaLonde %>%
+#   filter(re74.miss == F) %>%
+#   mutate(re74_0 = re74 == 0,
+#          re75_0 = re75 == 0)
+# 
+# lalonde_exp <- filter(lalonde, exper == 1)
+# lalonde_exp <- list(list(y = lalonde_exp$re78,
+#                 z = ifelse(lalonde_exp$treat == 1, 'trt', 'ctl'),
+#                 x = select(lalonde_exp, age:re75, re74_0, re75_0)))
+# lalonde_psid <- filter(lalonde, (exper == 1 & treat == 1) | exper == 0)
+# lalonde_psid <- list(list(y = lalonde_psid$re78,
+#                 z = ifelse(lalonde_psid$treat == 1, 'trt', 'ctl'),
+#                 x = select(lalonde_psid, age:re75, re74_0, re75_0)))
+# 
+# 
+# lalonde_cps <- MatchIt::lalonde %>%
+#   mutate(re74_0 = re74 == 0,
+#          re75_0 = re75 == 0)
+# lalonde_cps <- list(list(y = lalonde_cps$re78,
+#                 z = ifelse(lalonde_cps$treat == 1, 'trt', 'ctl'),
+#                 x = select(lalonde_cps, age:re75, re74_0, re75_0)))
+# 
+# 
+# set.seed(185)
+# lapply(list(
+#     lm_sim(lalonde_exp),
+#     lm_sim(lalonde_psid),
+#     lm_sim(lalonde_cps),
+#     psm_sim(lalonde_exp),
+#     psm_sim(lalonde_psid),
+#     psm_sim(lalonde_cps),
+#     aipw_sim(lalonde_exp),
+#     aipw_sim(lalonde_psid),
+#     aipw_sim(lalonde_cps),
+#     tmle_sim(lalonde_exp),
+#     tmle_sim(lalonde_psid),
+#     tmle_sim(lalonde_cps),
+#     dml_sim(lalonde_exp),
+#     dml_sim(lalonde_psid),
+#     dml_sim(lalonde_cps)), 
+#   bind_cols) %>% 
+#   bind_rows()  %>%
+#   mutate(method = rep(c('lm', 'psm', 'aipw', 'tmle', 'dml'), each = 3),
+#          sample = rep(c('experimental', 'PSID', 'CPS'), 5),
+#          estimate = paste0(round(d), ' (', round(se), ')')) %>%
+#   select(method, sample, estimate) %>%
+#   pivot_wider(names_from = 'sample', values_from = estimate) %>%
+#   write_csv(here('files', 'lalonde.csv'))
 ```
 
-```{r plce, eval = F}
-plce_out <- with(pisa_test, PLCE::plce(
-                y = math1,
-                treat = immigrant,
-                X = as.matrix(select(pisa_test, mom_ed, dad_ed, #early_ed,
-                          female, cultural_pos, home_ed, age))))
+```{r lalonde}
+bind_rows(
+  read_csv(here('files', 'lalonde.csv')) %>%
+    mutate(sample = 'Original LaLonde'),
+  read_csv(here('files', 'lalonde_74.csv')) %>%
+    mutate(sample = 'With 1974 earnings')) %>%
+  select(sample, method, everything()) %>%
+  kableExtra::kable(booktabs = T, 
+                    # digits = 3,
+                    # linesep = '',
+                    caption = 'ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups. Standard errors shown in parentheses.')
 
+# bind_rows(
+#   read_csv(here('files', 'lalonde.csv')) %>%
+#     mutate(sample = 'LaLonde'),
+#   read_csv(here('files', 'lalonde_74.csv')) %>%
+#     mutate(sample = 'DW (with 1974 earnings)')) %>%
+#   select(sample, everything()) %>%
+#   kableExtra::kable(booktabs = T, 
+#                     # digits = 3,
+#                     linesep = '',
+#                     caption = 'ATE estimates for Lalonde NSW data from Dehejia and Wahba (1999), with PSID ')
+
+# lalonde_exp_df <- filter(lalonde, exper == 1)
+# fit <- CBPS::CBPS(treat ~ age + educ + re75 + re74 + 
+# 			I(re75==0) + I(re74==0), 
+# 			data = lalonde_exp_df, ATT = TRUE)
+# summary(fit)
+# m.out <- MatchIt::matchit(treat ~ fitted(fit), method = "nearest", 
+# 				 data = lalonde_exp_df, replace = TRUE)
+# lm(re78 ~ treat + age + educ + re75 + re74, MatchIt::match.data(m.out), weights = weights) %>%
+#   tidy()
+# 
+# 
+# lalonde_psid_df <- filter(lalonde, (exper == 1 & treat == 1) | exper == 0)
+# fit <- CBPS::CBPS(treat ~ age + educ + re75 + re74 + 
+# 			I(re75==0) + I(re74==0), 
+# 			data = lalonde_psid_df, ATT = TRUE)
+# m.out <- MatchIt::matchit(treat ~ fitted(fit), method = "nearest", 
+# 				 data = lalonde_psid_df, replace = TRUE)
+# lm(re78 ~ treat + age + educ + re75 + re74, MatchIt::match.data(m.out), weights = weights) %>%
+#   tidy()
 ```
 
-```{r bart, eval = F}
-set.seed(159)
-bart_out <- bartCause::bartc(
-  response = pisa_test$math1,
-  treatment = pisa_test$immigrant,
-  confounders = as.data.frame(select(pisa_test, mom_ed, dad_ed,
-                          female, early_ed, cultural_pos, home_ed, age))
-  )
-
-summary(bart_out)
-
-# sensitivity analysis:
-# Dorie et al., Statistics in Medicine, 2016
-# treatSens (CRAN) -- use BART option
-```
-
-# Next Steps
-The Monte Carlo simulations presented here use small sample sizes and few variables, while double robust methods are perhaps most advantageous for large, high-dimensional samples.
-In the final paper, the simulations here will be supplemented samples of 1,000 and 10,000, and all will be replicated 1,000 times.
-Data sets with many covariates will also be simulated.
-The final paper will also test these methods on cross-national PISA test score data and provide R code to implement these methods.
-
 # References

### 2024-01-25 draft/ms-adj-draft.Rmd
before figure overhaul

@@
     toc: no
-    number_sections: no
+    number_sections: yes
     pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
@@
   # - \let\footnote=\endnote
-#- \setlength{\headheight}{14.5pt}
-#- \setlength{\headheight}{13.6pt}
-# - \usepackage{fancyhdr}
-# - \pagestyle{fancy}
-# - \lhead{N.I. Hoffmann}
-# - \rhead{`r format(Sys.time(), '%B %e, %Y')`}
+  # - \setlength{\headheight}{14.5pt}
+  # - \setlength{\headheight}{13.6pt}
+  - \usepackage{fancyhdr}
+  - \pagestyle{fancy}
+  - \lhead{N.I. Hoffmann}
+  - \rhead{`r format(Sys.time(), '%B %e, %Y')`}
 # - \newcommand{\beginsupplement}{\setcounter{table}{0}  
@@
 
-title: "Demystifying Double Robust, Flexible Adjustment Methods for Causal Inference"
-#subtitle: "PAA 2023"
-author:  Nathan I. Hoffmann
-#   | Department of Sociology, UCLA
+title: "Double Robust, Flexible Adjustment Methods for Causal Inference: An Overview and an Evaluation"
+# subtitle: "American Sociological Association Annual Meeting 2024"
+author:  Nathan I. Hoffmann, Department of Sociology, UCLA
 date: "`r format(Sys.time(), '%B %e, %Y')`"
@@
 It is also unclear whether these methods actually outperform more traditional methods in finite samples.
-This paper has two aims: it is a guide to some of the latest methods in doubly robust, flexible covariate adjustment for causal inference, and it compares these methods to more traditional statistical methods.
-It does this by using both simulated data where the treatment effect estimate is known, and then using complex survey data from the Program for International Student Assessment (PISA).
-Methods covered include Targeted Maximum Likelihood Estimation, Double/Debiased Machine Learning, and Augmented Inverse Propensity Weighting.
-Although these methods are robust to either the exposure or response model being misspecified, preliminary results show that, when both models are incorrect, bias grows rapidly in small samples."
+This paper has two aims: It is a guide to some of the latest methods in double robust, flexible covariate adjustment for causal inference, and it compares these methods to more traditional statistical methods.
+It does this by using both simulated data where the treatment effect estimate is known, and then using comparisons of experimental and observational data from the National Supported Work Demonstration.
+Methods covered include Augmented Inverse Probability Weighting, Targeted Maximum Likelihood Estimation, and Double/Debiased Machine Learning.
+Results suggest that these methods do not necessarily outperform OLS regression or matching on propensity score estimated by logistic regression, even in cases where the data generating process is not linear."
 
@@
 
+library(SuperLearner)
 library(broom)
 library(knitr)
+library(kableExtra)
 library(here)
@@
 
-```{r, functions}
-perform <- function(est_df, label){
-  est_df %>%
-    summarize(bias = mean(d - truth),
-              percent_bias = bias/sd(d),
-              rmse = sqrt(mean(d - truth)^2),
-              mae = median(abs(d - truth)),
-              fail_count = first(fail_count),
-              comp_time = first(comp_time)) %>%
-    mutate(label = label,
-           n = nrow(est_df) + fail_count) %>%
-    select(label, everything()) %>%
-    return()
-}
-```
-
-```{r load, eval = F}
-# data from mx0.5
-pisa <- readRDS('/Users/nathan/My Drive/1 UCLA/Dissertation/data/pisa.rds') %>%
-  mutate(age = as.numeric(age))
-
-pisa <- pisa %>%
-  filter(across(c(female,  mom_ed, dad_ed, early_ed, cultural_pos, home_ed, age,
-                  math1, math2, math3, math4, math5,
-                  read1, read2, read3, read4, read5,
-                  scie1, scie2, scie3, scie4, scie5),
-                ~ !is.na(.x))) %>%
-  mutate(
-    country = case_when(
-       country == '034400' ~ 'Hong Kong',
-       country == '044600'~ 'Macao',
-       country == 'Russian Federation' ~ 'Russia',
-       country == 'United States of America' ~ 'United States',
-       T ~ country
-     ),
-   birth_country = case_when(
-       birth_country == '034400' ~ 'Hong Kong',
-       birth_country == '044600'~ 'Macao',
-       birth_country == 'United States of America' ~ 'United States',
-       T ~ birth_country
-     ),
-   immigrant = case_when(
-    birth_country != country ~ T,
-    birth_country == country ~ F
-    )) %>%
-  # include immigrants with a birth country in the dataset, or non-immigrants
-  filter((immigrant == T & birth_country %in% unique(pisa$country)) | 
-           immigrant == F) %>%
-   mutate(school_id = paste0(year, school_id),
-         village = school_location == 'Village',
-         non_urban = ifelse(!is.na(school_location), school_location %in% c('Village', 'Small Town', 'Town'), NA),
-         match_country = ifelse(immigrant == T, birth_country, country))
-
-# Include only match_country with at least 5 imm and 5 non-imm
-n_min <- 5
-match_country_imm <- pisa %>%
-  filter(immigrant == T) %>%
-  group_by(match_country) %>%
-  count() %>% 
-  filter(n >= n_min) %>%
-  pull(match_country)
-
-match_country_nonimm <- pisa %>%
-  filter(immigrant == F) %>%
-  group_by(match_country) %>%
-  count() %>% 
-  filter(n >= n_min) %>%
-  pull(match_country)
-
-pisa <- pisa %>%
-  filter(match_country %in% match_country_imm,
-         match_country %in% match_country_nonimm,
-         # Remove match_country with no immigrants
-         match_country %in% unique(pisa$match_country[pisa$immigrant == T])
-         ) %>%
-  mutate(immigrant = as.numeric(immigrant))
-```
-
-<!-- # Abstract -->
-
-<!-- This thesis aims to compare different advanced adjustment methods.
-It will compare Imben & Rubins propensity matching, stabilized IPWs, TMLE, double machine learning (Chernozhukov et al 2018), Ratkovic (2021), and BART.
--->
-
-# Introduction
-
-Statistical methods for flexible covariate adjustment in causal inference have proliferated in recent years.
-These methods have a number of strengths over traditional regression methods: They make few functional form assumptions, can accommodate large numbers of covariates, and produce easily interpretable treatment effect estimates.
-Many of these methods also have a "double robust" property: They estimate one model for the treatment exposure and another for the outcome, and as long as at least one is correctly specified, then the treatment effect will be estimated consistently.
-Despite their apparent advantages, these methods remain underutilized by social scientists.
-Part of the barrier has been lack of familiarity with these methods.
-It has also been unclear how these methods compare, or whether such methods actually perform better than traditional methods in finite samples.
-<!-- And when researchers want to use an existing R package for these methods, the array of possible estimation methods and other options can be dizzying.   -->
-
-This paper makes advances on these fronts.
-First, it is a guide to some of the latest methods in doubly robust, flexible covariate adjustment for causal inference, explaining the methods to a social scientist audience.
-Second, it compares these methods to more traditional statistical methods using a type of data that social scientists frequently encounter: cross-national survey data.
-It does this by using both simulated data where the treatment effect estimate is known, and then using complex survey data from the Program for International Student Assessment (PISA).
-
-Methods covered include Targeted Maximum Likelihood Estimation [TMLE, @vanderlaan_2006_targeted], Double or Debiased Machine Learning [DML, @chernozhukov_2018_double], and Augmented Inverse Propensity Weighting [AIPW, @glynn_2010_introduction].
-This paper reviews the theory behind these methods as well as simple R implementations of them on simulations and real data.
-These methods are compared to two methods commonly used by social scientists: ordinary least squares (OLS) regression, and matching on propensity scores estimated from logistic regression (PSM).
-
-# Conceptual Overview
-
-Doubly robust methods estimate two models:
-
-- an *outcome model*
-
-$$\mu_d(X_i) = E(Y_i \mid D_i = d, X_i)$$
-
-- and an *exposure model* (or treatment model or propensity score):
-
-$$\pi(X_i) = E(D_i \mid X_i)$$
-
-where $\mu_d(\cdot)$ is the model of control or treatment $D_i = d=\{0, 1\}$, $X_i$ is a vector of covariates for unit $i = 1, \ldots, N$ for treatment (1) and control (0), $Y_i$ is the outcome, and $\pi(\cdot)$ is the exposure model.
-The covariates included in $X_i$ can be different for the two models.
-
-An estimator is called "doubly robust" if it achieves consistent estimation of the ATE (or whatever estimand the researcher is interested in) as long as *at least one* of these two models is consistently estimated.
-This means that the outcome model can be completely misspecified, but as long as the exposure model is correct, our estimation of the ATE will be consistent.
-This also means that the exposure model can be completely wrong, as along as the outcome model is correct.
-
-## Origins of Doubly Robust Methods
-
-According to @bang_2005_doubly, doubly robust methods have their origins in missing data models.
-@robins_1994_estimation and @rotnitzky_1998_semiparametric developed augmented orthogonal inverse probability-weighted (AIPW) estimators in missing data models, and @scharfstein_1999_adjusting showed that AIPW was doubly robust and extended to causal inference.
-
-But @kang_2007_demystifying argue that doubly robust methods are older.
-They cite work by @cassel_1976_results, who proposed “generalized regression estimators” for population means from surveys where sampling weights must be estimated.
-Arguably, doubly robust methods go back even further than this.
-The form of doubly robust methods is similar to residual-on-residual regression, which dates back to @frisch_1933_partial famous FWL theorem:
-
-$$\beta_D = \frac{\text{Cov}(\tilde Y_i, \tilde D_i)}{\text{Var}(\tilde D_i)}$$
-
-where $\tilde D_i$ is the residual part of $D_i$ after regressing it on $X_i$, and $\tilde Y_i$ is the residual part of $Y_i$ after regressing it on $X_i$.
-This formulation writes the regression coefficient as composed of an outcome model ($\tilde Y_i$) and exposure model ($\tilde D_i$), the two models used in doubly robust estimators.
-
-There are also links between doubly robust methods and matching with regression adjustment.
-This work goes back to at least @rubin_1973_use, who suggested that regression adjustment in matched data produces less biased estimates that either matching (exposure adjustment) or regression (outcome adjustment) do by themselves.
-
-## Assumptions
-
-Most doubly robust methods require almost all of the standard assumptions necessary formost methods that depend on selection on observables.
-Although some doubly robust methods relax one or two of these, the six standard assumptions are:
-
-1. Consistency
-2. Positivity/overlap
-3. One version of treatment
-4. No interference
-5. IID observations
-6. Conditional ignorability: $\{Y_{i0}, Y_{i1}\} \perp \!\!\! \perp D_i \mid X_i$
-
-Special attention should be paid to Assumption 6: doubly robust methods will not work if we do not measure an important confounder that affects both treatment and exposure.
-But notably, the doubly robust methods covered in this tutorial make no functional form assumptions.
-Most use flexible machine learning algorithms to estimate both the outcome and exposure models, with regularization (often through cross-fitting) to avoid overfitting.
-
-## A simple demonstration
-
-To demonstrate double robustness, this section presents one of the simpler doubly robust estimators: Augmented Inverse Propensity Weighting (AIPW) [@glynn_2010_introduction].
-We can write this estimator as follows:
-
-$$\begin{aligned}
-\widehat{ATE} = &\frac{1}{N} \sum_{i=1}^N \left( \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) \right) 
-- \frac{1}{N} \sum_{i=1}^N \left( \frac{(1-D_i)(Y_i - \hat \mu_0 (X_i))}{1-\hat \pi(X_i)} + \hat \mu_0(X_i) \right)
-\end{aligned}$$
-
-For each individual in the sample, this estimator calculates two quantities:
-
-- The treated potential outcome
-
-$$\hat Y_{1i} = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i)$$
-
-- The control potential outcome
-
-$$\hat Y_{0i} = \frac{(1-D_i)(Y_i - \hat \mu_0 (X_i))}{1-\hat \pi(X_i)} + \hat \mu_0(X_i)$$
-
-Let's focus on the treated model:
-
-$$\hat Y_{1i} = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i)$$
-
-First, assume that the outcome model $\mu_1(X_i)$ is *correctly* specified and the exposure model $\pi(X_i)$ is *incorreclty* specified.
-Let's also assume (for now) that we're dealing with a treated unit, i.e.
-$D_i = 1$.
-Then
-
-$$\hat \mu_1 (X_i) = Y_i$$
-
-and hence
-
-$$\hat Y_{1i} = \frac{D_i(0)}{\hat \pi (X_i)} + \hat \mu_1(X_i) = \hat \mu_1(X_i).$$
-
-So the model relies *only* on the outcome model.
-The incorrectly specified exposure model completely disappears from the equation.
-If we're dealing with a control unit ($D_i=0$), we get the same result:
-
-$$\hat Y_{1i} = \frac{0(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) = \hat \mu_1(X_i).$$
-
-Now, what if the *exposure* model $\pi(X_i)$ is correctly specified and the outcome model $\mu_1(X)$ is incorrect? First, we rewrite the estimator for the treated outcome:
-
-$$\begin{aligned}
-\hat Y_{1i}& = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) \\
-&= \frac{D_iY_i}{\hat \pi (X_i)} - \frac{D_i\hat \mu_1 (X_i)}{\hat \pi (X_i)} + \frac{\hat \pi (X_i)\hat \mu_1(X_i)}{\hat \pi (X_i)} \\
-& = \frac{D_iY_i}{\hat \pi (X_i)} - \left( \frac{D_i - \hat \pi(X_i)}{\hat \pi (X_i)}\right) \hat \mu_1(X_i). &&(*)
-\end{aligned}$$
-
-Since the exposure model is correclty specified, we have $D_i = \hat \pi(X_i)$ on average, so
-
-$$E[D_i - \hat \pi(X_i)] = 0.$$
-
-This means that the second term in equation $(*)$ is 0, so
-
-$$E[\hat Y_{1i}]= E \left [ \frac{D_iY_i}{\hat \pi (X_i)}\right].$$
-
-This shows that when the exposure model is correct, then the estimator depends *only* on the exposure model. We can make similar arguments for the control model $\hat Y_{0i}$.
-
-This demonstration shows that this estimator achieves double robustness: the estimator is robust to misspecification of either the exposure or the outcome model (but not both).
-
-# Overview of Techniques  
-Each of the methods reviewed in this paper can be thought of as a collection of estimation techniques.
-Each involves a model for the outcome and another for the treatment exposure, but the ways these relate and are combined varies from method to method.
-Choice of estimation technique for these two models is left to the discretion of the user; often ensemble learning is recommended, but in practice simpler methods can also work well.
-
-*Augmented Inverse Propensity Weighting (AIPW)*: The oldest of these modern methods, AIPW arose in the context of missing data imputation.
-As shown in the demonstration above, the method simply combines estimates from a model for the treatment exposure, $\pi(X)$, and a model for the outcome, $\mu(X)$.
-The name comes from the close similarity to inverse propensity weights (IPW), but whereas IPW only weights for propensity of treatment, AIPW "augments" these weights with an estimate of the response surface as well.
-
-*Targeted Maximum Likelihood Estimation (TMLE)*: TMLE begins by estimating the relevant part of the data-generating distribution $P(Y)$, i.e.
-the conditional density $Q = P(Y \mid X)$.
-It next estimates the exposure model.
-Although any estimation method can be used for these steps, the originators of the method suggest using a "super learner," i.e.
-ensemble learning with cross-validation.
-Next, the exposure model is used to calculate a "clever covariate," which is similar to an IPW.
-The coefficient for this clever covariate is estimated using maximum likelihood -- whence the "MLE" in "TMLE." Finally, the estimate of $Q$ is updated in a function involving the clever covariate.
-This process can be iterated, but usually one iteration is enough.
-The estimate of the distribution $Q$ can be used to calculate the estimand of interest.
-
-*Double or Debiased Machine Learning* (DML): The most recent of the methods reviewed here, DML is motivated by the need to handle problems with high-dimensional nuisance parameters, i.e.
-a large number of measured confounders.
-Flexible machine learning is appropriate for this task, but such methods suffer from regularization bias.
-DML removes this bias in a two-step procedure.
-First, it solves the auxiliary problem of estimating the treatment exposure model $E(D|X) =  \pi(X)$.
-It then uses this model to remove bias: Neyman orthogonalization allows the creation of an orthogonalized regressor, essentially partialing out the effect of covariates $X$ from treatment $D$.
-The debiased $D$ is then used to estimate the conditional mean of the outcome $E(Y\mid X) = \mu(X)$, which can be used to calculate the estimand of interest.
-
-These methods have many similarities. How do the results they give compare? The next section tests the performance of each in practice.
-
-# Methods
-
-For the comparisons in the next section, estimation methods include ordinary least squares regression ("OLS"),  propensity-score matching with scores estimated from logistic regression using the `MatchIt` package ("PSM"), the augmented inverse propensity weighted estimator with generalized additive models using the `CausalGAM` package (AIPW), targeted maximum likelihood estimation using the `tmle` package (TMLE) with the default Superlearner that relies on the `SL.glm`,` SL.step`, and `GL.glm.interaction` functions, and double/debiased machine learning with random forests with the `DoubleML` and `mlr3` packages.
-
-# Results
-
-## Simluation with Dorie et al. (2019) Data
-
-In 2016, the Atlantic Causal Inference Conference hosted a competition for causal inference methods that adjust on observables.
-@dorie_2019_automated published the results of this competition, along with the data used in the competition.
-Below, I test double robust methods on the 20 data sets used for the "do-it-yourself" part of the competition.
-The data represent a hypothetical twins study investigating the impact of birth weight on IQ.
-The data have 4802 observations and 52 covariates.
-The authors of the study specify a different data generating process for the potential outcomes in each data set.
-In all cases, ignorability holds, but the authors vary the following:
-
-- degree of nonlinearity
-- percentage of treated
-- overlap for the treatment group
-- alignment (correspondence between the assignment mechanism and the response surface)
-- treatment effect heterogeneity
-- overall magnitude of the treatment effect
-
-The 20 data sets used here cover a range of these attributes; see the supplemental material from @dorie_2019_automated for details.
-For these preliminary results, I used 5 simulations of each data set, resulting in 100 data sets.
-I then calculated bias, percent bias (the estimator's bias as a percentage of its standard error), root mean squared error (rmse), and median absolute error (mae).
-I also include the number of data sets for which the method failed and the average computation time for each data set, in seconds.
-
-```{r dorie-sim, eval = F}
-set.seed(185)
-sim_list <- list()
-for(i in 1:20){ # up to 77
-  #sim_list_nest <- list()
-  for(j in 1:10){ # up to 100
-    print(paste0(i,',',j))
-    sim_list[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016, 
-                                      i, j, extraInfo = T)
-  }
-  #sim_list[[i]] <- sim_list_nest
-}
-
-# dat <- sim_list
-# i <- '3,1'
-# 
-# sim_dat <- data.frame(y = dat[[i]]$y, 
-#                           d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
-#                           dat[[i]]$x)
-# lm_out <- lm(y ~ d + ., sim_dat)
-# lm_list[[i]] <- data.frame(d = lm_out$coefficients[['d']],
-#                            truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
-
-sim_linear <- list()
-for(i in c(1, 3))
-  for(j in 1:100){ 
-    print(paste0(i,',',j))
-    sim_linear[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016, 
-                                      3, j, extraInfo = T)
-  }
-}
-
-```
-
-```{r lm-sim, eval = F}
-lm_sim <- function(dat){
-  start_time <- Sys.time()
-  n <- length(dat)
-  lm_list <- list()
-  for(i in 1:n){
-    print(paste0(i, ' out of ', n))
-    sim_dat <- data.frame(y = dat[[i]]$y, 
-                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
-                          dat[[i]]$x)
-
-    tryCatch({
-      lm_out <- tidy(lm(y ~ d + ., sim_dat))
-      lm_list[[i]] <- data.frame(d = lm_out[[2,2]],
-                                 se = lm_out[[2,3]],
-                                 truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
-      }, error=function(e){
-        cat("ERROR :",conditionMessage(e), "\n")
-        })
-
-  }
-
-  fail_count <- sum(sapply(lm_list, function(x) is.null(x)))
-  # in case last few are errors
-  fail_count <- ifelse(length(lm_list) == n, fail_count, fail_count + (n - length(lm_list)))
-
-  end_time <- Sys.time()
-
-  return(list(
-    est_df = bind_rows(lm_list),
-    fail_count = fail_count,
-    comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
-    )
-}
-
-lm_sim_out <- lm_sim(sim_list) 
-lm_sim_linear <- lm_sim(sim_linear)
-
-lm_df <- lm_sim_out$est_df %>%
-  mutate(fail_count = lm_sim_out$fail_count,
-         comp_time = lm_sim_out$comp_time)
-
-lm_df_linear <- lm_sim_linear$est_df %>%
-  mutate(fail_count = lm_sim_linear$fail_count,
-         comp_time = lm_sim_linear$comp_time)
-
-write_csv(lm_df, here('files', 'lm_df.csv'))
-write_csv(lm_df_linear, here('files', 'lm_df_linear.csv'))
-
-# lm_lalonde <- lm_sim(lalonde)
-
-```
-
-```{r psm-sim, eval = F}
-psm_sim <- function(dat){
-  start_time <- Sys.time()
-  n <- length(dat)
-  psm_list <- list()
-  for(i in 1:n){
-    print(paste0(i, ' out of ', n))
-    sim_dat <- data.frame(y = dat[[i]]$y, 
-                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
-                          dat[[i]]$x)
-
-    form <- as.formula(paste0('d ~ ', paste(names(dat[[i]]$x), collapse = '+')))
-    match_out <- MatchIt::matchit(form,
-                           data = sim_dat,
-                           method = 'nearest',
-                           distance = 'glm')
-
-    # match_data <- MatchIt::match.data(match_out) 
-    # apply(match_data, 1, unique)
-    form2 <- as.formula(paste0('y ~ d + ', paste(names(dat[[i]]$x), collapse = '+')))
-
-  tryCatch({
-    psm_out <- lm(form2, 
-                  MatchIt::match.data(match_out), 
-                  weights = weights) %>%
-      tidy()
-    psm_list[[i]] <- data.frame(d = psm_out[[2,2]],
-                                se = psm_out[[2,3]],
-                                truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
-
-  }, error=function(e){
-    cat("ERROR :",conditionMessage(e), "\n")
-    })
-
-  }
-
-  fail_count <- sum(sapply(psm_list, function(x) is.null(x)))
-  # in case last few are errors
-  fail_count <- ifelse(length(psm_list) == n, fail_count, fail_count + (n - length(psm_list)))
-
-  end_time <- Sys.time()
-
-  return(list(
-    est_df = bind_rows(psm_list),
-    fail_count = fail_count,
-    comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
-  )
-}
-
-psm_sim_out <- psm_sim(sim_list) 
-psm_sim_linear <- psm_sim(sim_linear)
-
-psm_df <- psm_sim_out$est_df %>%
-  mutate(fail_count = psm_sim_out$fail_count,
-         comp_time = psm_sim_out$comp_time)
-
-psm_df_linear <- psm_sim_linear$est_df %>%
-  mutate(fail_count = psm_sim_linear$fail_count,
-         comp_time = psm_sim_linear$comp_time)
-
-write_csv(psm_df, here('files', 'psm_df.csv'))
-write_csv(psm_df_linear, here('files', 'psm_df_linear.csv'))
-```
-
-```{r aipw-sim, eval = F}
-aipw_sim <- function(dat, seed = 185){
-
-  start_time <- Sys.time()
-
-  set.seed(seed)
-  n <- length(dat)
-  aipw_list <- list()
-  # fail_count <- 0
-
-  for(i in 1:n){
-    print(paste0(i, ' out of ', n))
-    sim_dat <- data.frame(y = dat[[i]]$y, 
-                          d = as.numeric(ifelse(dat[[i]]$z == 'trt', 1, 0)), 
-                          dat[[i]]$x)
-
-    tryCatch({
-      sim_dat <- sim_dat %>%
-        fastDummies::dummy_cols(remove_first_dummy = T, remove_selected_columns = T) 
-      }, error=function(e){
-      })
-
-    tryCatch({
-      forest <- grf::causal_forest(X = select(sim_dat, 3:length(names(sim_dat))), 
-                                   Y = sim_dat$y, W = sim_dat$d)
-      # forest <- grf::causal_forest(X = select(sim_dat, starts_with('x')), 
-      #                              Y = sim_dat$y, W = sim_dat$d)
-
-      aipw_out <- grf::average_treatment_effect(forest, target.sample = 'treated', method = 'AIPW')
-
-      aipw_list[[i]] <- data.frame(d = aipw_out[[1]],
-                                   se = aipw_out[[2]],
-                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
-
-  }, error=function(e){
-    cat("ERROR :",conditionMessage(e), "\n")
-    })
-  }
-
-  fail_count <- sum(sapply(aipw_list, function(x) is.null(x)))
-  # in case last few are errors
-  fail_count <- ifelse(length(aipw_list) == n, fail_count, fail_count + (n - length(aipw_list)))
-
-  end_time <- Sys.time()
-
-  return(list(
-      est_df = bind_rows(aipw_list),
-      fail_count = fail_count,
-      comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
-  )
-}
-
-aipw_out <- aipw_sim(sim_list)
-aipw_out_linear <- aipw_sim(sim_linear)
-
-aipw_df <- aipw_out$est_df %>%
-  mutate(fail_count = aipw_out$fail_count,
-         comp_time = aipw_out$comp_time)
-
-aipw_df_linear <- aipw_out_linear$est_df %>%
-  mutate(fail_count = aipw_out_linear$fail_count,
-         comp_time = aipw_out_linear$comp_time)
-
-write_csv(aipw_df,  here('files', 'aipw_df.csv'))
-write_csv(aipw_df_linear,  here('files', 'aipw_df_linear.csv'))
-
-```
-
-```{r tmle-sim, eval = F}
-
-tmle_sim <- function(dat, seed = 185){
-  start_time <- Sys.time()
-
-  set.seed(seed)
-  n <- length(dat)
-  tmle_list <- list()
-  # fail_count <- 0
-
-  for(i in 1:n){
-    print(paste0(i, ' out of ', n))
-    sim_dat <- data.frame(y = dat[[i]]$y, 
-                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
-                          dat[[i]]$x)
-
-    tryCatch({
-      sim_dat <- sim_dat %>%
-        fastDummies::dummy_cols(remove_first_dummy = T, remove_selected_columns = T) 
-      }, error=function(e){
-      })
-
-    tryCatch({
-      forest <- grf::causal_forest(X = select(sim_dat, 3:length(names(sim_dat))), 
-                                   Y = sim_dat$y, W = sim_dat$d)
-      # forest <- grf::causal_forest(X = select(sim_dat, starts_with('x')), 
-      #   Y = sim_dat$y, W = sim_dat$d)
-
-      tmle_out <- grf::average_treatment_effect(forest, target.sample = 'treated', method = 'TMLE')
-
-      tmle_list[[i]] <- data.frame(d = tmle_out[[1]],
-                                   se = tmle_out[[2]],
-                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
-
-  }, error=function(e){
-    cat("ERROR :",conditionMessage(e), "\n")
-    })
-  }
-
-  fail_count <- sum(sapply(tmle_list, function(x) is.null(x)))
-  # in case last few are errors
-  fail_count <- ifelse(length(tmle_list) == n, fail_count, fail_count + (n - length(tmle_list)))
-
-  end_time <- Sys.time()
-
- return(list(
-      est_df = bind_rows(tmle_list),
-      fail_count = fail_count,
-      comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
-  )
-}
-
-tmle_out <- tmle_sim(sim_list)
-tmle_out_linear <- tmle_sim(sim_linear)
-
-tmle_df <- tmle_out$est_df %>%
-  mutate(fail_count = tmle_out$fail_count,
-         comp_time = tmle_out$comp_time)
-
-tmle_df_linear <- tmle_out_linear$est_df %>%
-  mutate(fail_count = tmle_out_linear$fail_count,
-         comp_time = tmle_out_linear$comp_time)
-
-write_csv(tmle_df, here('files', 'tmle_df.csv'))
-write_csv(tmle_df_linear, here('files', 'tmle_df_linear.csv'))
-```
-
-```{r dml-sim, eval = F}
-dml_sim <- function(dat, seed = 185){
-  library(mlr3)
-  library(mlr3learners)
-
-  start_time <- Sys.time()
-
-  set.seed(seed)
-
-  n <- length(dat)
-
-  dml_list <- list()
-
-  for(i in 1:n){
-    print(paste0(i, ' out of ', n))
-    sim_dat <- data.frame(y = dat[[i]]$y, 
-                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
-                          dat[[i]]$x)
-
-    lgr::get_logger("mlr3")$set_threshold("warn")
-
-    learner = lrn("regr.ranger", num.trees=500, 
-                  max.depth=5, min.node.size=2)
-    ml_l = learner$clone()
-    ml_m = learner$clone()
-
-    tryCatch({
-      dml_out <- DoubleML::DoubleMLPLR$new(
-        DoubleML::DoubleMLData$new(sim_dat,
-                                 y_col = 'y',
-                                 d_cols = 'd',
-                                 x_cols = names(dat[[i]]$x)), 
-        ml_l=ml_l, ml_m=ml_m)
-
-      dml_out$fit()
-      dml_list[[i]] <- data.frame(d = dml_out$all_coef[[1,1]],
-                                  se = dml_out$all_se[[1,1]],
-                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
-
-  }, error=function(e){
-    cat("ERROR :",conditionMessage(e), "\n")
-    })
-  }
-
-  fail_count <- sum(sapply(dml_list, function(x) is.null(x)))
-  # in case last few are errors
-  fail_count <- ifelse(length(dml_list) == n, fail_count, fail_count + (n - length(dml_list)))
-
-  end_time <- Sys.time()
-
-  return(list(
-      est_df = bind_rows(dml_list),
-      fail_count = fail_count,
-      comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
-      )
-}
-
-dml_out <- dml_sim(sim_list)
-dml_out_linear <- dml_sim(sim_linear)
-
-dml_df <- dml_out$est_df %>%
-  mutate(fail_count = dml_out$fail_count,
-         comp_time = dml_out$comp_time)
-dml_df_linear <- dml_out_linear$est_df %>%
-  mutate(fail_count = dml_out_linear$fail_count,
-         comp_time = dml_out_linear$comp_time)
-
-write_csv(dml_df, here('files', 'dml_df.csv'))
-write_csv(dml_df_linear, here('files', 'dml_df_linear.csv'))
-```
-
-```{r dorie-results}
-bind_rows(
-  perform(read_csv(here('files', 'lm_df.csv')), 'lm'),
-  perform(read_csv(here('files', 'psm_df.csv')), 'psm'),
-  perform(read_csv(here('files', 'aipw_df.csv')), 'aipw'),
-  perform(read_csv(here('files', 'tmle_df.csv')), 'tmle'),
-  perform(read_csv(here('files', 'dml_df.csv')), 'dml')
-  ) %>%
-  kableExtra::kable(booktabs = T, 
-                    digits = 3,
-                    linesep = '',
-                    caption = 'Results of Monte Carlo simulations using the first 20 datasets from Dorie et al.
-(2019), 5 replications each.
-Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is average computation time measured in seconds for each dataset.')
-```
-
-```{r dorie-results-linear}
-bind_rows(
-  perform(read_csv(here('files', 'lm_df_linear.csv')), 'lm'),
-  perform(read_csv(here('files', 'psm_df_linear.csv')), 'psm'),
-  perform(read_csv(here('files', 'aipw_df_linear.csv')), 'aipw'),
-  perform(read_csv(here('files', 'tmle_df_linear.csv')), 'tmle'),
-  perform(read_csv(here('files', 'dml_df_linear.csv')), 'dml')
-  ) %>%
-  kableExtra::kable(booktabs = T, 
-                    digits = 3,
-                    linesep = '',
-                    caption = 'Results of Monte Carlo simulations using the linear DGP for dataset 3 from Dorie et al.
-(2019), 5 replications each.
-Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is average computation time measured in seconds for each dataset.')
-```
-
-Results are shown in Table \@ref(tab:dorie-results).
-The methods all have similar levels of bias and error, but AIPW performs better than the other methods on all measures.
-AIPW did fail, however, on the most data sets; the package `CausalGAM` package does not do well with lack of overlap of factor variables between treated and control groups.
-
-```{r lalonde-data}
+```{r load}
+
 unemp_func <- function(x){
@@
 
+```{r load-sims, eval = F}
+lalonde_bootstrap <- function(dataset, sample, include_74 = F, iter = 100){
+
+  lalonde_variables <- c('age', 'education', 'black', 'hispanic', 'married', 'nodegree', 're75', 're75_0')
+  if(include_74 == F){
+        dataset <- bind_rows(filter(lalonde_exp, treat == 1), dataset)
+
+      } else {
+        lalonde_variables <- c(lalonde_variables, 're74', 're74_0')
+        dataset <- bind_rows(filter(lalonde_exp_74, treat == 1), dataset)
+      }
+
+  bootstrap_list <- list()
+
+  for(i in 1:iter){
+    dataset_bootstrap <- sample_n(dataset, nrow(dataset), replace = T)
+
+    bootstrap_list[[i]] <- list(y = dataset_bootstrap$re78,
+                  z = ifelse(dataset_bootstrap$treat == 1, 'trt', 'ctl'),
+                  x = dataset_bootstrap[,lalonde_variables],
+                  y.1 = NA, y.0 = NA,
+                  dataset = i,
+                  set = sample,
+                  size = nrow(dataset_bootstrap))
+  }
+
+  return(bootstrap_list)
+}
+
+set.seed(1859)
+sims_lalonde <- c(
+  lalonde_bootstrap(filter(lalonde_exp, treat == 0), sample = 'lalonde experimental original'),
+  lalonde_bootstrap(lalonde_psid1_controls, 'lalonde PSID-1 original'),
+  lalonde_bootstrap(lalonde_psid3_controls, 'lalonde PSID-3 original'),
+  lalonde_bootstrap(lalonde_cps1_controls, 'lalonde CPS-1 original'),
+  lalonde_bootstrap(lalonde_cps1_controls, 'lalonde CPS-3 original'),
+  lalonde_bootstrap(filter(lalonde_exp_74, treat == 0), sample = 'lalonde experimental 74', include_74 = T),
+  lalonde_bootstrap(lalonde_psid1_controls, 'lalonde PSID-1 74', include_74 = T),
+  lalonde_bootstrap(lalonde_psid3_controls, 'lalonde PSID-3 74', include_74 = T),
+  lalonde_bootstrap(lalonde_cps1_controls, 'lalonde CPS-1 74', include_74 = T),
+  lalonde_bootstrap(lalonde_cps1_controls, 'lalonde CPS-3 74', include_74 = T))
+
+# sims <- readRDS(here('files', 'sims.RDS'))
+
+sims_main <- readRDS(here('files_main', 'sims.RDS'))
+sims_large <- readRDS(here('files_large', 'sims_large.RDS'))
+sims_small <- readRDS(here('files_small', 'sims_small.RDS'))
+
+sims <- sims_main %>% append(sims_small) %>% append(sims_large) %>% append(sims_lalonde)
+
+# sims <- sims %>% append(sims_large)
+
+# sims <- readRDS(here('files', 'sims_small.RDS'))
+
+# for(i in 1:length(sims_small)){
+#   # sims_large[[i]]$size <- nrow(sims_large[[i]]$x)
+#   sims_small[[i]]$dataset <- 7
+# }
+# saveRDS(sims_large, here('files_large', 'sims_large.RDS'))
+# 
+# 
+# sims_combined <- sims %>% append(sims_small) %>% append(sims_large)
+# 
+# index_df <- data.frame(dorie_dataset = sapply(sims_combined, function(x) x$dataset),
+#                        set = sapply(sims_combined, function(x) x$set),
+#                        size = sapply(sims_combined, function(x) x$size)) %>%
+#   mutate(dataset = c(1:length(sims), 1:length(sims_small), 1:length(sims_large)))
+# 
+# lm_df <- read_csv(here('files_main', 'lm_df.csv')) %>% 
+#   mutate(set = c(rep('main', 200), rep('linear', 200))) %>%
+#   bind_rows(read_csv(here('files_small', 'lm_df.csv')) %>% mutate(set = 'small')) %>%
+#   bind_rows(read_csv(here('files_large', 'lm_df.csv')) %>% mutate(set = 'large')) %>%
+#   left_join(index_df)
+# 
+# 
+# write_csv(lm_df, here('files', 'lm_df.csv'))
+# 
+# psm_df <- read_csv(here('files_main', 'psm_df.csv')) %>% 
+#   mutate(set = ifelse(dataset <= 200, 'main', 'linear')) %>%
+#   bind_rows(read_csv(here('files_small', 'psm_df.csv')) %>% mutate(set = 'small')) %>%
+#   bind_rows(read_csv(here('files_large', 'psm_df.csv')) %>% mutate(set = 'large')) %>%
+#   left_join(index_df)
+# 
+# write_csv(lm_df, here('files', 'psm_df.csv'))
+# 
+# 
+# aipw_df <- read_csv(here('files_main/homemade', 'aipw.csv')) %>% 
+#   mutate(set = ifelse(dataset <= 200, 'main', 'linear')) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'aipw.csv')) %>% mutate(set = 'small')) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'aipw.csv')) %>% mutate(set = 'large')) %>%
+#   left_join(index_df)
+# 
+# write_csv(aipw_df, here('files/homemade', 'aipw.csv'))
+# 
+# 
+# aipw_trunc_df <- read_csv(here('files_main/homemade', 'aipw_trunc.csv')) %>% 
+#   mutate(set = ifelse(dataset <= 200, 'main', 'linear')) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'aipw_trunc.csv')) %>% mutate(set = 'small')) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'aipw_trunc.csv')) %>% mutate(set = 'large')) %>%
+#   left_join(index_df)
+# 
+# write_csv(aipw_trunc_df, here('files/homemade', 'aipw_trunc.csv'))
+# 
+# tmle_df <- read_csv(here('files_main/homemade', 'tmle.csv')) %>% 
+#   mutate(set = ifelse(dataset <= 200, 'main', 'linear')) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'tmle.csv')) %>% mutate(set = 'small')) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'tmle.csv')) %>% mutate(set = 'large')) %>%
+#   left_join(index_df)
+# 
+# write_csv(tmle_df, here('files/homemade', 'tmle.csv'))
+# 
+# dml_ols_logit_df <- read_csv(here('files_main/homemade', 'dml_ols_logit.csv')) %>%
+#   mutate(dataset = 1:nrow(.)) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'dml_ols_logit.csv')) %>% 
+#               mutate(set = 'small',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'dml_ols_logit.csv')) %>% 
+#               mutate(set = 'large',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   left_join(index_df) 
+# 
+# write_csv(dml_ols_logit_df, here('files/homemade', 'dml_ols_logit.csv'))
+# 
+# dml_grf_df <- read_csv(here('files_main/homemade', 'dml_grf.csv')) %>%
+#   mutate(dataset = 1:nrow(.)) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'dml_grf.csv')) %>% 
+#               mutate(set = 'small',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'dml_grf.csv')) %>% 
+#               mutate(set = 'large',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   select(-dorie_dataset) %>%
+#   left_join(index_df)
+# 
+# write_csv(dml_grf_df, here('files/homemade', 'dml_grf.csv'))
+# 
+# 
+# dml_superlearner_df <- read_csv(here('files_main/homemade', 'dml_superlearner.csv')) %>%
+#   mutate(dataset = 1:nrow(.)) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'dml_superlearner.csv')) %>% 
+#               mutate(set = 'small',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'dml_superlearner.csv')) %>% 
+#               mutate(set = 'large',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   select(-dorie_dataset) %>%
+#   left_join(index_df)
+# 
+# write_csv(dml_superlearner_df, here('files/homemade', 'dml_superlearner.csv'))
+
+# ols_logit_pred_combined <- readRDS(here('files_main/homemade', 'ols_logit_pred.RDS')) %>%
+#   append(readRDS(here('files_small/homemade', 'ols_logit_pred.RDS'))) %>%
+#   append(readRDS(here('files_large/homemade', 'ols_logit_pred.RDS')))
+# 
+# grf_pred_combined <- readRDS(here('files_main/homemade', 'grf_pred.RDS')) %>%
+#   append(readRDS(here('files_small/homemade', 'grf_pred.RDS'))) %>%
+#   append(readRDS(here('files_large/homemade', 'grf_pred.RDS')))
+# 
+# superlearner_pred_combined <- readRDS(here('files_main/homemade', 'superlearner_pred.RDS')) %>%
+#   append(readRDS(here('files_small/homemade', 'superlearner_pred.RDS'))) %>%
+#   append(readRDS(here('files_large/homemade', 'superlearner_pred.RDS')))
+# 
+# saveRDS(ols_logit_pred_combined, here('files/homemade', 'ols_logit_pred.RDS'))
+# saveRDS(grf_pred_combined, here('files/homemade', 'grf_pred.RDS'))
+# saveRDS(superlearner_pred_combined, here('files/homemade', 'superlearner_pred.RDS'))
+
+# dml_ols_logit <- read_csv(here('files_large/homemade', 'dml_ols_logit.csv')) 
+# 
+# dml_ols_logit %>%
+#   filter(set == 'main') %>%
+#   write_csv(here('files_main/homemade', 'dml_ols_logit.csv'))
+# 
+# dml_ols_logit %>%
+#   filter(set == 'large') %>%
+#   write_csv(here('files_large/homemade', 'dml_ols_logit.csv'))
+
+## add lalonde ####
+# read_csv(here('files_combined', 'lm_df.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde', 'lm_df.csv'))) %>%
+#   write_csv(here('files', 'lm_df.csv'))
+# 
+# 
+# read_csv(here('files_combined', 'psm_df.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde', 'psm_df.csv'))) %>%
+#   write_csv(here('files', 'psm_df.csv'))
+# 
+# read_csv(here('files_combined', 'lin.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde', 'lin.csv'))) %>%
+#   write_csv(here('files', 'lin.csv'))
+# 
+# read_csv(here('files_combined', 'gcomp.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde', 'gcomp.csv'))) %>%
+#   write_csv(here('files', 'gcomp.csv'))
+# 
+# read_csv(here('files_combined/homemade', 'aipw.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde/homemade', 'aipw.csv'))) %>%
+#   write_csv(here('files/homemade', 'aipw.csv'))
+# 
+# read_csv(here('files_combined/homemade', 'aipw_trunc.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde/homemade', 'aipw_trunc.csv'))) %>%
+#   write_csv(here('files/homemade', 'aipw_trunc.csv'))
+# 
+# read_csv(here('files_combined/homemade', 'tmle.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde/homemade', 'tmle.csv'))) %>%
+#   write_csv(here('files/homemade', 'tmle.csv'))
+# 
+# read_csv(here('files_combined/homemade', 'dml_ols_logit.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde/homemade', 'dml_ols_logit.csv'))) %>%
+#   write_csv(here('files/homemade', 'dml_ols_logit.csv'))
+# 
+# read_csv(here('files_combined/homemade', 'dml_grf.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde/homemade', 'dml_grf.csv'))) %>%
+#   write_csv(here('files/homemade', 'dml_grf.csv'))
+# 
+# read_csv(here('files_combined/homemade', 'dml_superlearner.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde/homemade', 'dml_superlearner.csv'))) %>% 
+#   write_csv(here('files/homemade', 'dml_superlearner.csv'))
+# 
+# 
+# readRDS(here('files_combined/homemade', 'ols_logit_pred.RDS')) %>%
+#   bind_rows(readRDS(here('files_lalonde/homemade', 'ols_logit_pred.RDS'))) %>%
+#   saveRDS(here('files/homemade', 'ols_logit_pred.RDS'))
+# 
+# readRDS(here('files_combined/homemade', 'grf_pred.RDS')) %>%
+#   bind_rows(readRDS(here('files_lalonde/homemade', 'grf_pred.RDS'))) %>%
+#   saveRDS(here('files/homemade', 'grf_pred.RDS'))
+# 
+# readRDS(here('files_combined/homemade', 'superlearner_pred.RDS')) %>%
+#   bind_rows(readRDS(here('files_lalonde/homemade', 'superlearner_pred.RDS'))) %>%
+#   saveRDS(here('files/homemade', 'superlearner_pred.RDS'))
+
+# dml_ols_logit_df <- read_csv(here('files_main/homemade', 'dml_ols_logit.csv')) %>%
+#   mutate(dataset = 1:nrow(.)) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'dml_ols_logit.csv')) %>% 
+#               mutate(set = 'small',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'dml_ols_logit.csv')) %>% 
+#               mutate(set = 'large',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   left_join(index_df) 
+# 
+# write_csv(dml_ols_logit_df, here('files/homemade', 'dml_ols_logit.csv'))
+# 
+# dml_grf_df <- read_csv(here('files_main/homemade', 'dml_grf.csv')) %>%
+#   mutate(dataset = 1:nrow(.)) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'dml_grf.csv')) %>% 
+#               mutate(set = 'small',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'dml_grf.csv')) %>% 
+#               mutate(set = 'large',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   select(-dorie_dataset) %>%
+#   left_join(index_df)
+# 
+# write_csv(dml_grf_df, here('files/homemade', 'dml_grf.csv'))
+# 
+# 
+# dml_superlearner_df <- read_csv(here('files_main/homemade', 'dml_superlearner.csv')) %>%
+#   mutate(dataset = 1:nrow(.)) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'dml_superlearner.csv')) %>% 
+#               mutate(set = 'small',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'dml_superlearner.csv')) %>% 
+#               mutate(set = 'large',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   select(-dorie_dataset) %>%
+#   left_join(index_df)
+# 
+# write_csv(dml_superlearner_df, here('files/homemade', 'dml_superlearner.csv'))
+
+# ols_logit_pred_combined <- readRDS(here('files_main/homemade', 'ols_logit_pred.RDS')) %>%
+#   append(readRDS(here('files_small/homemade', 'ols_logit_pred.RDS'))) %>%
+#   append(readRDS(here('files_large/homemade', 'ols_logit_pred.RDS')))
+# 
+# grf_pred_combined <- readRDS(here('files_main/homemade', 'grf_pred.RDS')) %>%
+#   append(readRDS(here('files_small/homemade', 'grf_pred.RDS'))) %>%
+#   append(readRDS(here('files_large/homemade', 'grf_pred.RDS')))
+# 
+# superlearner_pred_combined <- readRDS(here('files_main/homemade', 'superlearner_pred.RDS')) %>%
+#   append(readRDS(here('files_small/homemade', 'superlearner_pred.RDS'))) %>%
+#   append(readRDS(here('files_large/homemade', 'superlearner_pred.RDS')))
+# 
+# saveRDS(ols_logit_pred_combined, here('files/homemade', 'ols_logit_pred.RDS'))
+# saveRDS(grf_pred_combined, here('files/homemade', 'grf_pred.RDS'))
+# saveRDS(superlearner_pred_combined, here('files/homemade', 'superlearner_pred.RDS'))
+
+# dml_ols_logit <- read_csv(here('files_large/homemade', 'dml_ols_logit.csv')) 
+# 
+# dml_ols_logit %>%
+#   filter(set == 'main') %>%
+#   write_csv(here('files_main/homemade', 'dml_ols_logit.csv'))
+# 
+# dml_ols_logit %>%
+#   filter(set == 'large') %>%
+#   write_csv(here('files_large/homemade', 'dml_ols_logit.csv'))
+
+```
+
+```{r sim-homemade, eval = F}
+sim_homemade <- function(n, m = NULL){
+  if(is.null(m)){
+    m <- round(n/100)
+  }
+
+  dat <- replicate(m, rnorm(n, 0, 5)) %>% 
+    as.data.frame() 
+  dat_original <- dat
+
+  # first make treatment indicator
+  dat <- data.frame(1, dat)
+  coefs <- rnorm(m+1, 0, 2)
+  d <- round(1/(1+exp(-as.matrix(dat) %*% as.matrix(coefs))))
+
+  dat <- data.frame(dat, d)
+
+  # Set treatment effect to 2
+  coefs <- c(rnorm(m+1, 0, 2), 2)
+  y <- as.matrix(dat) %*% as.matrix(coefs) + rnorm(1)
+
+  dat <- data.frame(dat, y)
+
+  dat_new <- dat_original
+
+  transformers <- rnorm(m, 0, 2)
+
+  for(i in 1:m){
+    dat_new[,i] <- dat_new[,i] * transformers[i]
+  }
+
+  # m/4 squared terms
+  dat_new <- dat_new %>% 
+    mutate(across(sample(1:m, m/4, replace = F), function(x) x^2))
+
+  # m/4 exponentiated 
+  dat_new <- dat_new %>% 
+    mutate(across(sample(1:m, m/4, replace = F), function(x) exp(x)))
+
+  # m/4 sin 
+  dat_new <- dat_new %>% 
+    mutate(across(sample(1:m, m/4, replace = F), function(x) sin(x)))
+
+  # m/2 2-way interactions
+  for(i in 1:round(m/2)){
+    index <- sample(1:m, 2, replace = F)
+    dat_new[, index[1]] <- dat_new[,index[1]] * dat_new[,index[2]]
+  }
+
+  # m/4 3-way interactions
+  for(i in 1:round(m/4)){
+    index <- sample(1:m, 3, replace = F)
+    dat_new[, index[1]] <- dat_new[,index[1]] * dat_new[,index[2]] * dat_new[,index[3]]
+  }
+
+  dat_final <- data.frame(dat_new, d = dat[,'d'], y = dat[,'y'])
+  return(dat_final)
+}
+
+# 500, 1000, 5000, 10k, 50k, 100k
+# Set m = 1% of n
+# 50 of each 
+# then set n = 5000 and m = 10, 50, 200, 1000
+set.seed(185)
+sim_homemade_list <- list()
+for(n in c(500, 1000, 5000, 1e3, 5e3, 1e5)){
+  print(paste0('n = ', n))
+  for(i in 1:50){
+    print(i)
+    sim_homemade_list[[paste0(n, i)]] <- sim_homemade(n) %>%
+      mutate(n = n, m  = n/100, dataset = i, simulation = 'n')
+  }
+}
+for(m in c(10, 50, 200, 500, 1000)){
+  print(paste0('m = ', m))
+  for(i in 1:50){
+    print(i)
+    sim_homemade_list[[paste0(n, i)]] <- sim_homemade(n = n, m = m) %>%
+      mutate(n = n, m  = m, dataset = i, simulation = 'm')
+  }
+}
+
+saveRDS(sim_homemade_list, here('files', 'sim_homemade.RDS'))
+
+```
+
+```{r github-datageneration, eval = F}
+# from https://github.com/QuantLet/DataGenerationForCausalInference
+
+### This generates the Simulation Data as a dataframe
+# by Daniel Jacob (daniel.jacob@hu-berlin.de)
+
+# Arguments to specify are: 
+# Y = Outcome (dependend variable). Either continuous or binary. 
+# N = Number of observations (real number)
+# k = Number of covariates (real number). At least 10 
+# random_d = treatment assignment: (Either T for random assignment or F for confounding on X)
+# theta = treatment effect: (Either real number for only one theta, or "binary" {0.1,0.3}, "con" for continuous values (0.1,0.3) or "big" for {1,0.4})
+# var = Size of the variance (Noise-level)
+
+#Required Packages
+if(!require("clusterGeneration")) install.packages("clusterGeneration"); library("clusterGeneration")
+if(!require("mvtnorm")) install.packages("mvtnorm"); library("mvtnorm")
+
+datagen <- function(N,y,k,random_d,theta,var) {
+
+  N = N
+  k = k
+  b = 1 / (1:k)
+  # = Generate covariance matrix of z = #
+  sigma <- genPositiveDefMat(k, "unifcorrmat")$Sigma
+  sigma <- cov2cor(sigma)
+
+  z <- rmvnorm(N, sigma = sigma) # = Generate z = #
+
+  ### Options for D (m_(X))
+  if (random_d == T) {
+    d <- rep(c(0, 1), length.out = N)
+  } else {
+    d_prop <- pnorm(z %*% b) # D is dependent on Za
+    d <- as.numeric(rbinom(N, prob = d_prop, size = 1))
+  }
+
+  ### Options for theta
+  if (theta == "con") {
+    theta_s <- as.vector(sin(z %*% b) ^ 2)
+    theta <-
+      (theta_s - min(theta_s)) * (0.3 - 0.1) / (max(theta_s) - min(theta_s)) +
+      0.1
+  } else if (theta == "binary") {
+    theta_low <-
+      rbinom(N, pnorm((z[, 6] * (z[, 1] %*% t(
+        z[, 5]
+      )) * z[, 2]) ^ 2), size = 1)
+    theta <-
+      ifelse(theta_low == 1, 0.3, 0.1)
+  } else if (theta == "big") {
+    theta_big <-
+      rbinom(N, pnorm((z[, 6] * (z[, 1] %*% t(
+        z[, 5]
+      )) * z[, 2]) ^ 2), size = 1)
+    theta <- ifelse(theta_big == 1, 1, 0.4)
+  }  else {
+    theta == theta
+  }
+
+  g <- as.vector(cos(z %*% b) ^ 2)
+
+  if(y=="binary") {
+    y1 <- theta * d + g 
+    y1.1 <- rbinom(N,prob=pnorm(scale(y1)),size=1)
+    y <- y1.1
+  } else {y <- theta * d + g + rnorm(N,0,var)}
+
+  data <- as.data.frame(y)
+  data <- cbind(data, theta, d, z)
+  colnames(data) <- c("y", "theta", "d", c(paste0("V", 1:k)))
+
+  return(data)
+}
+
+### Example
+dataset <- datagen(y="binary",N = 2000, k = 20, random_d = F, theta = "binary", var = 1)
+summary(dataset)
+str(dataset)
+
+glm(y ~ ., data = dataset, family = binomial(link = 'logit')) %>%
+  summary()
+```
+
+```{r trash, eval = F}
+dat_transform <- function(dat){
+  # first make treatment indicator
+  coefs <- runif(ncol(dat), -1, 1)
+
+  # m/4 squared terms
+  dat <- dat %>% 
+    mutate(across(sample(1:m, m/4, replace = F), function(x) x^2))
+
+  # m/4 exponentiated 
+  dat <- dat %>% 
+    mutate(across(sample(1:ncol(dat), m/4, replace = F), function(x) exp(x)))
+
+  # m/4 sin 
+  dat <- dat %>% 
+    mutate(across(sample(1:ncol(dat), m/4, replace = F), function(x) sin(x)))
+
+  # m/2 2-way interactions
+  dat <- bind_cols(dat,
+    replicate(m/2, {
+      index <- sample(1:m, 2, replace = F)
+      dat[,index[1]] * dat[,index[2]]
+      }, simplify = T))
+
+  # m/4 3-way interactions
+  dat <- bind_cols(dat,
+    replicate(m/4, {
+      index <- sample(1:m, 3, replace = F)
+      dat[,index[1]] * dat[,index[2]] * dat[,index[3]]
+      }, simplify = T))
+
+  coefs <- runif(ncol(dat), -1, 1)
+
+  y <- as.matrix(dat) %*% as.matrix(coefs)
+
+  return(y)
+}
+
+sim_homemade <- function(m, n){
+  m <- m-2
+  dat <- replicate(m, rnorm(n, 0, 5)) %>%
+    cbind(replicate(m/4, rbinom(n, 1, .5))) %>%
+    as.data.frame()
+  dat_original <- dat
+
+  # first make treatment indicator
+  dat <- data.frame(1, dat)
+  coefs <- rnorm(ncol(dat), 0, 2)
+  d <- round(1/(1+exp(-as.matrix(dat) %*% as.matrix(coefs))))
+
+  dat <- data.frame(dat, d)
+
+  # Set treatment effect to 2
+  coefs <- c(rnorm(m+1, 0, 2), 2)
+  y <- as.matrix(dat) %*% as.matrix(coefs) + rnorm(1)
+
+  dat <- data.frame(dat, y)
+
+  dat_new <- dat_original
+
+  transformers <- rnorm(m, 0, 2)
+
+  for(i in 1:m){
+    dat_new[,i] <- dat_new[,i] * transformers[i]
+  }
+
+  # m/4 squared terms
+  dat_new <- dat_new %>% 
+    mutate(across(sample(1:m, m/4, replace = F), function(x) x^2))
+
+  # m/4 exponentiated 
+  dat_new <- dat_new %>% 
+    mutate(across(sample(1:ncol(m), m/4, replace = F), function(x) exp(x)))
+
+  # m/4 sin 
+  dat_new <- dat_new %>% 
+    mutate(across(sample(1:ncol(m), m/4, replace = F), function(x) sin(x)))
+
+  # m/2 2-way interactions
+  for(i in 1:round(m/2)){
+    index <- sample(1:m, 2, replace = F)
+    dat_new[, index[1]] <- dat_new[,index[1]] * dat_new[,index[2]]
+  }
+
+  # m/4 3-way interactions
+  for(i in 1:round(m/4)){
+    index <- sample(1:m, 3, replace = F)
+    dat_new[, index[1]] <- dat_new[,index[1]] * dat_new[,index[2]] * dat_new[,index[3]]
+  }
+
+  dat_final <- data.frame(dat_new, d = dat[,'d'], y = dat[,'y'])
+  return(dat_final)
+}
+
+```
+
+```{r functions}
+## Pred functions ####
+ols_logit_pred <- function(y, d, x){
+  if('factor' %in% unlist(lapply(x, class))){
+    x <- fastDummies::dummy_cols(x, remove_first_dummy = T, remove_selected_columns = T) 
+  }
+
+  mu_mod <- lm(y ~  d + ., data.frame(y, d, x))
+  mu1_pred <- predict(mu_mod, newdata = data.frame(y, d = 1, x))
+  mu0_pred <- predict(mu_mod, newdata = data.frame(y, d = 0, x))
+
+  pi_mod <- glm(d ~ ., data.frame(y, x), family = binomial(link = 'logit'))
+  pi_pred <- predict(pi_mod, type = 'response')
+
+  return(
+    list(
+      mu1_pred = mu1_pred, 
+      mu0_pred = mu0_pred, 
+      pi_pred = pi_pred,
+      d = d,
+      y = y
+    ))
+}
+
+grf_pred <- function(y, d, x){
+  if('factor' %in% unlist(lapply(x, class))){
+    x <- fastDummies::dummy_cols(x, remove_first_dummy = T, remove_selected_columns = T) 
+  }
+
+  forest_mu <- grf::regression_forest(X = data.frame(d, x), Y = y, 
+                                 tune.parameters = "all")
+  mu0_pred <- predict(forest_mu, newdata = data.frame(d = 0, x))$predictions
+  mu1_pred <- predict(forest_mu, newdata = data.frame(d = 1, x))$predictions
+
+  forest_pi <- grf::regression_forest(X = x, Y = d, tune.parameters = "all")
+  pi_pred <- predict(forest_pi, newdata = x)$predictions
+
+  return(
+    list(
+      mu1_pred = mu1_pred, 
+      mu0_pred = mu0_pred, 
+      pi_pred = pi_pred,
+      d = d,
+      y = y
+    ))
+}
+
+superlearner_pred <- function(y, d, x, folds = 5, seed = 158){
+  if('factor' %in% unlist(lapply(x, class))){
+    x <- fastDummies::dummy_cols(x, remove_first_dummy = T, remove_selected_columns = T) 
+  }
+
+  set.seed(seed)
+  mu_fit <- SuperLearner(
+    Y = y,
+    X = data.frame(d, x),
+    cvControl = list(V = folds),
+    SL.library=c("SL.glm", 
+                 "SL.glmnet", 
+                 "SL.xgboost"),
+    method="method.CC_nloglik", 
+    family= gaussian()
+  )
+
+  pi_fit <- SuperLearner(
+    Y = d,
+    X = x,
+    cvControl = list(V = folds),
+    SL.library=c("SL.glm", 
+                 "SL.glmnet", 
+                 "SL.xgboost"),
+    method="method.CC_nloglik", 
+    family= binomial()
+  )
+
+  return(list(
+    mu0_pred = as.numeric(predict(mu_fit, newdata = data.frame(d = 0, x), type = 'response')$library.predict %*% mu_fit$coef),
+    mu1_pred = as.numeric(predict(mu_fit, newdata = data.frame(d = 1, x), type = 'response')$library.predict %*% mu_fit$coef),
+    pi_pred = as.numeric(predict(pi_fit, type = 'response')$pred),
+    d = d,
+    y = y))
+}
+
+## Methods ####
+
+lm_sim <- function(dat){
+
+  n <- length(dat)
+  lm_list <- list()
+  for(i in 1:n){
+    start_time <- Sys.time()
+
+    print(paste0(i, ' out of ', n))
+    sim_dat <- data.frame(y = dat[[i]]$y, 
+                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
+                          dat[[i]]$x)
+
+    ate <- NA
+    tryCatch({
+      lm_out <- tidy(lm(y ~ d + ., sim_dat))
+      ate <- lm_out[[2,2]]
+
+      }, error=function(e){
+        cat("ERROR :",conditionMessage(e), "\n")
+        })
+
+    lm_list[[i]] <- data.frame(dataset = i,
+                               ate = ate,
+                               #se = lm_out[[2,3]],
+                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0),
+                               dorie_dataset = dat[[i]]$dataset,
+                               set = dat[[i]]$set,
+                               size = dat[[i]]$size,
+                               comp_time = as.numeric(difftime(Sys.time(), start_time, units = 'secs')))
+
+  }
+
+  # fail_count <- sum(sapply(lm_list, function(x) is.null(x)))
+  # # in case last few are errors
+  # fail_count <- ifelse(length(lm_list) == n, fail_count, fail_count + (n - length(lm_list)))
+
+  # end_time <- Sys.time()
+
+  return(bind_rows(lm_list))
+
+  # return(list(
+  #   est_df = bind_rows(lm_list)
+  #   fail_count = fail_count,
+  #   comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
+  #   ))
+}
+
+psm_sim <- function(dat){
+
+  n <- length(dat)
+  psm_list <- list()
+  for(i in 1:n){
+    print(paste0(i, ' out of ', n))
+
+    start_time <- Sys.time()
+
+    sim_dat <- data.frame(y = dat[[i]]$y, 
+                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
+                          dat[[i]]$x)
+
+    ate <- NA
+
+    tryCatch({
+      form <- as.formula(paste0('d ~ ', paste(names(dat[[i]]$x), collapse = '+')))
+      match_out <- MatchIt::matchit(form,
+                             data = sim_dat,
+                             method = 'nearest',
+                             distance = 'glm')
+
+      # match_data <- MatchIt::match.data(match_out) 
+      # apply(match_data, 1, unique)
+      form2 <- as.formula(paste0('y ~ d + ', paste(names(dat[[i]]$x), collapse = '+')))
+
+      psm_out <- lm(form2, 
+                    MatchIt::match.data(match_out), 
+                    weights = weights) %>%
+        tidy()
+
+      ate <- psm_out[[2,2]]
+
+  }, error=function(e){
+    cat("ERROR :",conditionMessage(e), "\n")
+    })
+
+    psm_list[[i]] <- data.frame(dataset = i,
+                                ate = ate,
+                                # se = psm_out[[2,3]],
+                                truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0),
+                                dorie_dataset = dat[[i]]$dataset,
+                                set = dat[[i]]$set,
+                                size = dat[[i]]$size,
+                                comp_time = as.numeric(difftime(Sys.time(), start_time, units = 'secs')))
+  }
+
+  # fail_count <- sum(sapply(psm_list, function(x) is.null(x)))
+  # # in case last few are errors
+  # fail_count <- ifelse(length(psm_list) == n, fail_count, fail_count + (n - length(psm_list)))
+
+  # end_time <- Sys.time()
+
+  return(bind_rows(psm_list))
+
+  # return(list(
+  #   est_df = bind_rows(psm_list),
+  #   fail_count = fail_count,
+  #   comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
+  # )
+}
+
+aipw_calc <- function(mu1_pred, mu0_pred, pi_pred, d, y){
+  n <- length(mu1_pred)
+
+  y1_pred <- (d*(y-mu1_pred))/pi_pred + mu1_pred
+  y0_pred <- ((1-d)*(y-mu0_pred))/(1-pi_pred) + mu0_pred
+
+  ate <- (1/n)*(sum(y1_pred)) - (1/n)*sum(y0_pred)
+
+  return(ate)
+}
+
+aipw_calc_trunc <- function(mu1_pred, mu0_pred, pi_pred, d, y){
+  n <- length(mu1_pred)
+
+  # pi_pred <- case_when(
+  #   pi_pred < quantile(pi_pred, .025) ~ quantile(pi_pred, .025),
+  #   pi_pred > quantile(pi_pred, .975) ~ quantile(pi_pred, .975),
+  #   T ~ pi_pred)
+
+  pi_pred <- case_when(
+    pi_pred < .01 ~ .01,
+    pi_pred > .99 ~ .99,
+    T ~ pi_pred)
+
+  y1_pred <- (d*(y-mu1_pred))/pi_pred + mu1_pred
+  y0_pred <- ((1-d)*(y-mu0_pred))/(1-pi_pred) + mu0_pred
+
+  ate <- (1/n)*(sum(y1_pred)) - (1/n)*sum(y0_pred)
+
+  return(ate)
+}
+
+tmle_calc <- function(mu1_pred, mu0_pred, pi_pred, d, y){
+  n <- length(y)
+  # H <- (d == 1)/pi_pred - (d==0)/(1-pi_pred)
+  H0 = (1-d)/(1-pi_pred)
+  H1 = d/pi_pred
+
+  epsilon <- glm(y ~ -1 + H0 + H1 + offset(qlogis((d==1)*mu1_pred + (d==0)*mu0_pred)),
+                 family = binomial(link = 'logit')) %>%
+    tidy() %>%
+    pull(estimate)
+
+  H_0 = (1-d)/(1-pi_pred)
+  H_1 = d/pi_pred
+
+  target_0 <- plogis(qlogis(mu0_pred + epsilon[1]*H_0))
+  target_1 <- plogis(qlogis(mu1_pred + epsilon[2]*H_1))
+
+  ATE <- mean((target_1 - target_0), na.rm = T)
+  return(ATE)
+}
+
+dml_pre <- function(y, d, x){
+  if('factor' %in% unlist(lapply(x, class))){
+    x <- fastDummies::dummy_cols(x, remove_first_dummy = T, remove_selected_columns = T) 
+  }
+
+  n <- length(y)
+  n_2 <- n/2
+  n_2_1 = ifelse(round(n_2) == n_2, n_2, round(n_2))
+  n_2_2 = ifelse(round(n_2) == n_2, n_2, round(n_2)+1)
+
+  # split the sample
+  random_vec <- sample(1:n, n)
+  I <- random_vec[1:n_2_1]
+  I_c <- random_vec[(n_2_1+1):n]
+
+  return(list(
+    y_I = y[I],
+    d_I = d[I],
+    x_I = x[I,], 
+    y_I_c = y[I_c],
+    d_I_c = d[I_c],
+    x_I_c = x[I_c,]
+    ))
+}
+
+dml_post <- function(y_I, d_I, x_I = NULL, y_I_c, d_I_c, x_I_c = NULL,
+                     mu_pred1, pi_pred1, mu_pred2, pi_pred2){
+
+  v1 <- d_I - pi_pred1
+  delta1 <- (sum(v1 * d_I))^-1 * sum(v1 * (y_I - pi_pred1))
+
+  v2 <- d_I_c - pi_pred2
+  delta2 <- (sum(v2 * d_I_c))^-1 * sum(v2 * (y_I_c - pi_pred2))
+
+  ate <- (delta1 + delta2)/2
+
+  return(ate)
+}
+
+## Predictor functions
+ols_logit_dml <- function(y_I, d_I, x_I, y_I_c, d_I_c, x_I_c){
+  mu_mod1 <- lm(y ~ ., data.frame(y = y_I_c, x_I_c))
+  mu_pred1 <- predict(mu_mod1, newdata = data.frame(y = y_I, x_I))
+
+  pi_mod1 <- glm(d ~ ., data.frame(d = d_I_c, x_I_c), 
+                family = binomial(link = 'logit'))
+  pi_pred1 <- predict(pi_mod1, 
+                     newdata = data.frame(d = d_I, x_I), 
+                     type = 'response')
+
+  mu_mod2 <- lm(y ~ ., data.frame(y = y_I, x_I))
+  mu_pred2 <- predict(mu_mod2, newdata = data.frame(y = y_I_c, x_I_c))
+
+  pi_mod2 <- glm(d ~ ., data.frame(d = d_I, x_I), 
+                family = binomial(link = 'logit'))
+  pi_pred2 <- predict(pi_mod2, 
+                     newdata = data.frame(d = d_I_c, x_I_c), 
+                     type = 'response')
+
+  return(list(
+    mu_pred1 = mu_pred1,
+    pi_pred1 = pi_pred1,
+    mu_pred2 = mu_pred2,
+    pi_pred2 = pi_pred2
+  ))
+}
+
+grf_dml <- function(y_I, d_I, x_I, y_I_c, d_I_c, x_I_c){
+  mu_mod1 <- grf::regression_forest(X = x_I_c, Y = y_I_c, 
+                                       tune.parameters = "all")
+  mu_pred1 <- predict(mu_mod1, newdata = x_I)$predictions
+
+  pi_mod1 <- grf::regression_forest(X = x_I_c, Y = d_I_c, tune.parameters = "all")
+  pi_pred1 <- predict(pi_mod1, newdata = x_I)$predictions
+
+  mu_mod2 <- grf::regression_forest(X = x_I, Y = y_I, 
+                                       tune.parameters = "all")
+  mu_pred2 <- predict(mu_mod2, newdata = x_I_c)$predictions
+
+  pi_mod2 <- grf::regression_forest(X = x_I, Y = d_I, tune.parameters = "all")
+  pi_pred2 <- predict(pi_mod2, newdata = x_I_c)$predictions
+
+  return(list(
+    mu_pred1 = mu_pred1,
+    pi_pred1 = pi_pred1,
+    mu_pred2 = mu_pred2,
+    pi_pred2 = pi_pred2
+  ))
+}
+
+superlearner_dml <- function(y_I, d_I, x_I, y_I_c, d_I_c, x_I_c,
+                             folds = 5){
+
+  mu_mod1 <- SuperLearner(
+    Y = y_I_c,
+    X = x_I_c,
+    cvControl = list(V = folds),
+    SL.library=c("SL.glm", 
+                 "SL.glmnet", 
+                 "SL.xgboost"),
+    method="method.CC_nloglik", 
+    family=gaussian()
+  )
+
+  pi_mod1 <- SuperLearner(
+    Y = d_I_c,
+    X = x_I_c,
+    cvControl = list(V = folds),
+    SL.library=c("SL.glm", 
+                 "SL.glmnet", 
+                 "SL.xgboost"),
+    method="method.CC_nloglik", 
+    family=binomial()
+  )
+
+  mu_pred1 <- predict(mu_mod1, newdata = x_I, type = 'response')$library.predict %*% mu_mod1$coef
+  pi_pred1 <- predict(pi_mod1, newdata = x_I, type = 'response')$pred
+
+  mu_mod2 <- SuperLearner(
+    Y = y_I,
+    X = x_I,
+    cvControl = list(V = folds),
+    SL.library=c("SL.glm", 
+                 "SL.glmnet", 
+                 "SL.xgboost"),
+    method="method.CC_nloglik", 
+    family=gaussian()
+  )
+
+  pi_mod2 <- SuperLearner(
+    Y = d_I,
+    X = x_I,
+    cvControl = list(V = folds),
+    SL.library=c("SL.glm", 
+                 "SL.glmnet", 
+                 "SL.xgboost"),
+    method="method.CC_nloglik", 
+    family=binomial()
+  )
+
+  mu_pred2 <- predict(mu_mod2, newdata = x_I_c, type = 'response')$library.predict %*% mu_mod2$coef
+  pi_pred2 <- predict(pi_mod2, newdata = x_I_c, type = 'response')$pred
+
+  return(list(
+    mu_pred1 = mu_pred1,
+    pi_pred1 = pi_pred1,
+    mu_pred2 = mu_pred2,
+    pi_pred2 = pi_pred2
+  ))
+}
+
+## Functions using double robust packages ####
+aipw_sim <- function(dat, seed = 185){
+
+  start_time <- Sys.time()
+
+  set.seed(seed)
+  n <- length(dat)
+  aipw_list <- list()
+  # fail_count <- 0
+
+  for(i in 1:n){
+    print(paste0(i, ' out of ', n))
+    sim_dat <- data.frame(y = dat[[i]]$y, 
+                          d = as.numeric(ifelse(dat[[i]]$z == 'trt', 1, 0)), 
+                          dat[[i]]$x)
+
+    tryCatch({
+      sim_dat <- sim_dat %>%
+        fastDummies::dummy_cols(remove_first_dummy = T, remove_selected_columns = T) 
+      }, error=function(e){
+      })
+
+    tryCatch({
+      forest <- grf::causal_forest(X = select(sim_dat, 3:length(names(sim_dat))), 
+                                   Y = sim_dat$y, 
+                                   W = sim_dat$d)
+      # forest <- grf::causal_forest(X = select(sim_dat, starts_with('x')), 
+      #                              Y = sim_dat$y, W = sim_dat$d)
+
+      aipw_out <- grf::average_treatment_effect(forest, target.sample = 'treated', method = 'AIPW')
+
+      aipw_list[[i]] <- data.frame(d = aipw_out[[1]],
+                                   se = aipw_out[[2]],
+                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
+
+  }, error=function(e){
+    cat("ERROR :",conditionMessage(e), "\n")
+    })
+  }
+
+  fail_count <- sum(sapply(aipw_list, function(x) is.null(x)))
+  # in case last few are errors
+  fail_count <- ifelse(length(aipw_list) == n, fail_count, fail_count + (n - length(aipw_list)))
+
+  end_time <- Sys.time()
+
+  return(list(
+      est_df = bind_rows(aipw_list),
+      fail_count = fail_count,
+      comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
+  )
+}
+
+tmle_sim <- function(dat, seed = 185){
+  start_time <- Sys.time()
+
+  set.seed(seed)
+  n <- length(dat)
+  tmle_list <- list()
+  # fail_count <- 0
+
+  for(i in 1:n){
+    print(paste0(i, ' out of ', n))
+    sim_dat <- data.frame(y = dat[[i]]$y, 
+                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
+                          dat[[i]]$x)
+
+    tryCatch({
+      sim_dat <- sim_dat %>%
+        fastDummies::dummy_cols(remove_first_dummy = T, remove_selected_columns = T) 
+      }, error=function(e){
+      })
+
+    tryCatch({
+      forest <- grf::causal_forest(X = select(sim_dat, 3:length(names(sim_dat))), 
+                                   Y = sim_dat$y, W = sim_dat$d)
+      # forest <- grf::causal_forest(X = select(sim_dat, starts_with('x')), 
+      #   Y = sim_dat$y, W = sim_dat$d)
+
+      tmle_out <- grf::average_treatment_effect(forest, target.sample = 'treated', method = 'TMLE')
+
+      tmle_list[[i]] <- data.frame(d = tmle_out[[1]],
+                                   se = tmle_out[[2]],
+                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
+
+  }, error=function(e){
+    cat("ERROR :",conditionMessage(e), "\n")
+    })
+  }
+
+  fail_count <- sum(sapply(tmle_list, function(x) is.null(x)))
+  # in case last few are errors
+  fail_count <- ifelse(length(tmle_list) == n, fail_count, fail_count + (n - length(tmle_list)))
+
+  end_time <- Sys.time()
+
+ return(list(
+      est_df = bind_rows(tmle_list),
+      fail_count = fail_count,
+      comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
+  )
+}
+
+dml_sim <- function(dat, seed = 185){
+  library(mlr3)
+  library(mlr3learners)
+
+  start_time <- Sys.time()
+
+  set.seed(seed)
+
+  n <- length(dat)
+
+  dml_list <- list()
+
+  for(i in 1:n){
+    print(paste0(i, ' out of ', n))
+    sim_dat <- data.frame(y = dat[[i]]$y, 
+                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
+                          dat[[i]]$x)
+
+    lgr::get_logger("mlr3")$set_threshold("warn")
+
+    learner = lrn("regr.ranger", num.trees=500, 
+                  max.depth=5, min.node.size=2)
+    ml_l = learner$clone()
+    ml_m = learner$clone()
+
+    tryCatch({
+      dml_out <- DoubleML::DoubleMLPLR$new(
+        DoubleML::DoubleMLData$new(sim_dat,
+                                 y_col = 'y',
+                                 d_cols = 'd',
+                                 x_cols = names(dat[[i]]$x)), 
+        ml_l=ml_l, ml_m=ml_m)
+
+      dml_out$fit()
+      dml_list[[i]] <- data.frame(d = dml_out$all_coef[[1,1]],
+                                  se = dml_out$all_se[[1,1]],
+                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
+
+  }, error=function(e){
+    cat("ERROR :",conditionMessage(e), "\n")
+    })
+  }
+
+  fail_count <- sum(sapply(dml_list, function(x) is.null(x)))
+  # in case last few are errors
+  fail_count <- ifelse(length(dml_list) == n, fail_count, fail_count + (n - length(dml_list)))
+
+  end_time <- Sys.time()
+
+  return(list(
+      est_df = bind_rows(dml_list),
+      fail_count = fail_count,
+      comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
+      )
+}
+
+## Other functions ####
+normalize <- function(x, y){(x - min(y)) / (max(y) - min(y))}
+denormalize <- function(x, y){x * (max(y) - min(y))}
+
+perform <- function(est_df, label){
+  est_df %>%
+    # mutate(d = d/truth,
+    #        truth = 1) %>%
+    summarize(bias = mean(d - truth),
+              percent_bias = bias/sd(d),
+              rmse = sqrt(mean((ate - truth)^2)),
+              mae = median(abs(d - truth))
+              # fail_count = first(fail_count),
+              # comp_time = first(comp_time)
+              ) %>%
+    mutate(label = label,
+           n = nrow(est_df) + fail_count) %>%
+    select(label, everything()) %>%
+    return()
+}
+```
+
+<!-- # Abstract -->
+
+<!-- This thesis aims to compare different advanced adjustment methods.
+It will compare Imben & Rubins propensity matching, stabilized IPWs, TMLE, double machine learning (Chernozhukov et al 2018), Ratkovic (2021), and BART.
+-->
+
+# Introduction
+
+Statistical methods for flexible covariate adjustment in causal inference have proliferated in recent years.
+These methods have a number of strengths over traditional regression methods: They make few functional form assumptions, can accommodate large numbers of covariates, and produce easily interpretable treatment effect estimates.
+Many of these methods also have a "double robust" property: They estimate one model for the treatment exposure and another for the outcome, and as long as at least one is correctly specified, then the treatment effect will be estimated consistently.
+Despite their apparent advantages, these methods remain underutilized by social scientists.
+Part of the barrier has been lack of familiarity with these methods.
+It has also been unclear how these methods compare, or whether such methods actually perform better than traditional methods in finite samples.
+<!-- And when researchers want to use an existing R package for these methods, the array of possible estimation methods and other options can be dizzying.   -->
+
+This paper makes advances on these fronts.
+First, it is a guide to some of the latest methods in double robust, flexible covariate adjustment for causal inference, explaining the methods to a social scientist audience.
+Second, it compares these methods to more traditional statistical methods using both simulations [@dorie_2019_automated] and the National Support for Work Demonstration (NSW) originally analyzed by @lalonde_1986_evaluating.
+
+Methods covered include Augmented Inverse Probability Weighting [AIPW, @glynn_2010_introduction], Targeted Maximum Likelihood Estimation [TMLE, @vanderlaan_2006_targeted], and Double or Debiased Machine Learning [DML, @chernozhukov_2018_double].
+This paper reviews the theory behind these methods as well as simple R implementations of them on simulations and real data.
+These methods are compared to two methods commonly used by social scientists: ordinary least squares (OLS) regression, and matching on propensity scores estimated from logistic regression (PSM).
+
+# Motivation
+
+## Literature Review
+
+Although previous work has compared different methods for covariate adjustment, there has not yet been a thorough evaluation and comparison of the recent and popular double robust methods of AIPW, TMLE, and DML.
+@austin_2014_comparison compares methods for matching on the propensity score.
+@dorie_2019_automated report the results for the Atlantic Causal Inference Conference 2016 competition.
+Some of the methods used incorporate TMLE but not AIPW or DML.
+@cousineau_2022_estimating evaluates the performance of optimization-baseds methods for causal inference, but these do not include the double robust methods covered in the current paper.
+@kang_2007_demystifying provide an overview and evaluation of double robust methods in the context of missing data.
+The authors consider AIPW but not TMLE or DML.
+@chatton_2020_gcomputation compare four methods: G-computation, IPW, full matching, and TMLE.
+These authors only consider one double robust method, and their focus is on omitted variable bias rather than determining which method is the most useful.
+@knaus_2022_double reviews double robust methods in an econometrics setting but does not compare them to traditional statistical methods for covaraite adjustment.
+
+## Historical Overview
+
+According to @bang_2005_doubly, double robust methods have their origins in missing data models.
+@robins_1994_estimation and @rotnitzky_1998_semiparametric developed augmented orthogonal inverse probability-weighted (AIPW) estimators in missing data models, and @scharfstein_1999_adjusting showed that AIPW was double robust and extended to causal inference (since causal inference is fundamentally a missing data problem).
+
+But @kang_2007_demystifying argue that double robust methods are older.
+They cite work by @cassel_1976_results, who proposed “generalized regression estimators” for population means from surveys where sampling weights must be estimated.
+Arguably, double robust methods go back even further than this.
+The form of double robust methods is similar to residual-on-residual regression, which dates back to @frisch_1933_partial famous FWL theorem:
+
+$$\beta_D = \frac{\text{Cov}(\tilde Y_i, \tilde D_i)}{\text{Var}(\tilde D_i)}$$
+
+where $\tilde D_i$ is the residual part of $D_i$ after regressing it on $X_i$, and $\tilde Y_i$ is the residual part of $Y_i$ after regressing it on $X_i$.
+This formulation writes the regression coefficient as composed of an outcome model ($\tilde Y_i$) and exposure model ($\tilde D_i$), the two models used in double robust estimators.
+
+There are also links between double robust methods and matching with regression adjustment.
+This work goes back to at least @rubin_1973_use, who suggested that regression adjustment in matched data produces less biased estimates that either matching (exposure adjustment) or regression (outcome adjustment) do by themselves.
+
+Today, double robust methods abound [e.g.
+@ratkovic_2023_relaxing; @sloczynski_2018_general; @arkhangelsky_2021_doublerobust; @dukes_2022_doubly; @kennedy_2023_semiparametric].
+This paper focuses on three of the more popular or fundamental methods.
+
+## Aims of Double Robust Methods
+Double robust methods for covariate adjustment aim to overcome what many consider to be the downsides of both traditional statistical methods and flexible machine learning methods.
+Statistical methods that are popular with social scientists -- such as OLS regression and matching on propensity scores from logistic regression -- have two main weaknesses that double robust methods address.
+First, they assume simple (linear or transformed linear) functional forms.
+In the presence of highly nonlinear data generating processes, they may provide biased estimates.
+Second, these methods cannot handle large numbers of covariates relative to sample size.
+While some machine learning methods can produce estimates even when the number of covariates exceeds the number of observations (such as lasso), OLS fails in this case due to the $X^\top X$ matrix not being of full rank and hence not invertible.
+In cases with many covariates, but not more than the number of observations, estimation is unstable with many traditional statistical methods.
+
+Flexible machine learning methods also have their drawbacks.
+First, naive application of these methods can result in overfitting, with predictive accuracy maximized in sample but treatment effect estimation being biased.
+Furthermore, results of these machine learning methods can be difficult to interpret without further processing.
+Machine learning methods have often been developed with a focus on prediction rather than on producing treatment effect point estimates.
+
+Double robust methods for covariate adjustment are also motivated by the idea that many older methods ignore information present in the data.
+Methods tend to model either the outcome -- as in OLS regression and G-computation -- or only the treatment assignment -- as in propensity score matching or inverse probability weighting.
+Double robust methods, on the other hand, model both of these.
+
+# Conceptual Overview
+
+Double robust methods estimate two models:
+
+- an *outcome model*
+
+$$\mu_d(X_i) = E(Y_i \mid D_i = d, X_i)$$
+
+- and an *exposure model* (or treatment model or propensity score):
+
+$$\pi(X_i) = E(D_i \mid X_i)$$
+
+where $\mu_d(\cdot)$ is the model of control or treatment $D_i = d=\{0, 1\}$, $X_i$ is a vector of covariates for unit $i = 1, \ldots, N$ for treatment (1) and control (0), $Y_i$ is the outcome, and $\pi(\cdot)$ is the exposure model.
+The covariates included in $X_i$ can be different for the two models.
+
+An estimator is called "double robust" if it achieves consistent estimation of the ATE (or whatever estimand the researcher is interested in) as long as *at least one* of these two models is consistently estimated.
+This means that the outcome model can be completely misspecified, but as long as the exposure model is correct, our estimation of the ATE will be consistent.
+This also means that the exposure model can be completely wrong, as along as the outcome model is correct.
+
+## Assumptions
+
+Most double robust methods require almost all of the standard assumptions necessary formost methods that depend on selection on observables.
+Although some double robust methods relax one or two of these, the six standard assumptions are:
+
+1. Consistency
+2. Positivity/overlap
+3. One version of treatment
+4. No interference
+5. IID observations
+6. Conditional ignorability: $\{Y_{i0}, Y_{i1}\} \perp \!\!\! \perp D_i \mid X_i$
+
+Special attention should be paid to Assumption 6: double robust methods will not work if we do not measure an important confounder that affects both treatment and exposure.
+But notably, the double robust methods covered in this tutorial make no functional form assumptions.
+These methods are designed to incorporate flexible machine learning algorithms to estimate both the outcome and exposure models, with regularization (often through cross-fitting) to avoid overfitting.
+
+# Overview of Techniques  
+Each of the methods reviewed in this paper can be thought of as a collection of estimation techniques.
+Each involves a model for the outcome and another for the treatment exposure, but the ways these relate and are combined varies from method to method.
+Choice of estimation technique for these two models is left to the discretion of the user; often ensemble learning is recommended, but in practice simpler methods can also work well.
+
+## Augmented Inverse Probability Weighting (AIPW)
+
+The oldest of these modern methods, AIPW arose in the context of missing data imputation [@robins_1994_estimation].
+@scharfstein_1999_adjusting showed that AIPW was double robust and extended to causal inference.
+Introductions to AIPW exist in the contexts of political science [@glynn_2010_introduction] and econometrics [@funk_2011_doubly].
+The `AIPW` R package provides a simple implementation of the method.
+
+AIPW combines estimates from a model for the treatment exposure, $\pi(X)$, and a model for the outcome, $\mu(X)$.
+The name comes from the close similarity to inverse probability weights (IPW), but whereas IPW only weights for probability of treatment, AIPW "augments" these weights with an estimate of the response surface.
+
+Formally, the model can be written as the difference between an estimated outcome for treated units and the estimated outcome for untreated units (see the demonstration below):
+
+$$\begin{aligned}
+\widehat{ATE}_{AIPW} = &\frac{1}{n} \sum_{i=1}^n \left( \frac{D_i(Y_i - \hat \mu_1 (\mathbf X_i))}{\hat \pi (\mathbf X_i)} + \hat \mu_1(\mathbf X_i) \right) 
+- \frac{1}{n} \sum_{i=1}^n \left( \frac{(1-D_i)(Y_i - \hat \mu_0 (\mathbf X_i))}{1-\hat \pi(\mathbf X_i)} + \hat \mu_0(\mathbf X_i) \right)
+\end{aligned}$$
+
+In practice, AIPW weights may be very small or very large, a problem that inverse probability weights also suffer from.
+This can make AIPW prone to high variance.
+To remedy this, the predicted probabilities of treatment are often truncated, setting extremely small or large weights to some less extreme value [as in the `AIPW` R package, @zhong_2021_aipw].
+
+Below is R code to implement AIPW with truncation of extreme weights.
+As with all of the double robust methods reviewed here, we begin with predicted values (such as from a machine learning algorithm) for the outcome for treated units `mu1_pred` and untreated units `mu0_pred` as well as predicted values for treatment assignment probability `pi_pred`.
+We also have `d`, the vector of actual treatment assignments, and `y`, the observed outcome values.
+
+```{r aipw-demo, eval = F, echo = T}
+require(tidyverse)
+
+aipw_calc <- function(mu1_pred, mu0_pred, pi_pred, d, y){
+  n <- length(mu1_pred)
+
+  # Truncate extreme values of the weights
+  pi_pred <- case_when(
+    pi_pred < .01 ~ .01,
+    pi_pred > .99 ~ .99,
+    T ~ pi_pred)
+
+  # Calculate the predicted outcome value for treated units
+  y1_pred <- (d*(y-mu1_pred))/pi_pred + mu1_pred
+  # Calculate the predicted outcome value for untreated units
+  y0_pred <- ((1-d)*(y-mu0_pred))/(1-pi_pred) + mu0_pred
+
+  # Calculate the ATE
+  ate <- (1/n)*(sum(y1_pred)) - (1/n)*sum(y0_pred)
+
+  return(ate)
+}
+```
+
+@glynn_2010_introduction provide an alternate but equivalent formula, where the basic inverse probability weight (IPW) estimator (which incorporates only the exposure model $\hat \pi$) is corrected using a weighted average of two outcome regression estimates:
+$$\begin{aligned}
+\widehat{ATE}_{AIPW} = & \frac{1}{n} \sum_{i=1}^n \left\{ \left[ \frac{D_i Y_i}{\hat \pi(\mathbf X_i)} - \frac{(1-D_i) Y_i}{ 1- \hat \pi(\mathbf X_i)} \right] - \frac{D_i - \hat \pi (\mathbf X_i)}{\hat \pi (\mathbf X_i)(1 - \hat pi (\mathbf X_i))} [(1- \hat \pi (\mathbf X_i)) \hat \mu_1(\mathbf X_i) + \hat \pi (\mathbf X_i) \hat \mu_0(\mathbf X_i)] \right\}
+\end{aligned}$$
+
+## Targeted Maximum Likelihood Estimation (TMLE)
+
+@vanderlaan_2006_targeted first proposed TMLE an extension and improvement of previous double robust methods, using a parametric framework and the efficient influence curve  [@hines_2022_demystifying] to obtain estimates and standard errors.
+Mark van der Laan has gone on to collaborate on both a gentle introduction [@gruber_2009_targeted], a textbook [@vanderlaan_2011_targeted], and an R package [@gruber_2012_tmle] for implementing the method.
+@schuler_2017_targeted and @luque-fernandez_2018_targeted provide introductions for epidemiologists.
+
+TMLE begins by estimating the relevant part of the data-generating distribution $P(Y)$, i.e.
+the conditional density $Q = P(Y \mid X)$.
+It next estimates the exposure model.
+Although any estimation method can be used for these steps, the originators of the method suggest using a "super learner," i.e.
+ensemble learning with cross-validation [@laan_2007_super].
+Next, the exposure model is used to calculate a "clever covariate," which is similar to an IPW.
+The coefficient for this clever covariate is estimated using maximum likelihood -- whence the "MLE" in "TMLE." Finally, the estimate of $Q$ is updated in a function involving the clever covariate.
+This process can be iterated, but usually one iteration is enough.
+The estimate of the distribution $Q$ can be used to calculate the estimand of interest.
+
+Formally, first generate estimates of $\mu_{d}(\mathbf X_i) = E(Y \mid D=d, \mathbf X_i)$ and $\pi(\mathbf X_i) = P(D=1 \mid \mathbf X_i)$. Then create the variable $H_{di}$ for targeting step:
+$$H_{di} = \frac{I(D_i = 1)}{\hat \pi (\mathbf X_i)} - \frac{I(D_i=0)}{1 - \hat \pi (\mathbf X_i)}$$
+
+Next, calculate the clever covariates for each individual in the data. These quantities are similar to inverse probability weights, with $H_{0i}$ for untreated and $H_{0i}$ for treated units:
+$$\begin{aligned}
+H_{0i}(D=0, \mathbf X_i) &= \frac{1-d_i}{1- \hat \pi (\mathbf X_i)}, &
+H_{1i}(D=1, \mathbf X_i) = \frac{d_i}{\hat \pi (\mathbf X_i)}.
+\end{aligned}$$
+
+In the next step, we estimate fluctuation parameters $\epsilon = (\epsilon_0, \epsilon_1)$ through maximum likelihood of the following logistic regression with fixed intercept $\text{logit}(\mu_{di})$:
+<!-- $$E(Y=1 \mid D, \mathbf X) = \text{logit}(\mu_{di}) + \epsilon H_{di}$$ -->
+$$\text{logit}[E(Y=1 \mid D, \mathbf X)] = \text{logit}(\hat \mu_{di}) + \epsilon_0 H_{0i} + \epsilon_1 H_{1i}$$
+
+Here we are assuming that $Y$ is a dichotomous variable taking the values of 0 or 1; the method is extended to continuous outcomes simply by normalizing the value of $Y$ to fall between 0 and 1.
+Then generate updated ("targeted") estimates of potential outcomes:
+$$\begin{aligned}
+\hat \mu_0^*(\mathbf X_i) &= \text{expit}[\text{logit}(\hat \mu_0(\mathbf X_i)) + \hat \epsilon H_{0i}]\\
+\hat \mu_1^*(\mathbf X_i) &= \text{expit}[\text{logit}(\hat \mu_1(\mathbf X_i)) + \hat \epsilon H_{1i}]
+\end{aligned}$$
+
+Finally, estimate the parameter of interest -- in this case, the ATE:
+$$\widehat{ATE}_{TMLE} = \frac{1}{n} \sum_{i=1}^n [\hat \mu_1^*(\mathbf X_i) - \hat \mu_0^*(\mathbf X_i)]$$
+
+Here is R code to implement TMLE, again with predicted outcome values `mu1_pred` and `mu0_pred` and predicted probability of treatment `pi_pred`.
+Since the outcome is bounded and continuous, it is transformed to fall between 0 and 1 via $\tilde Y_{i} = Y_i - \min(Y)/(\max(Y)-\min(Y)$.
+```{r tmle-demo, eval = F, echo = T}
+# Functions for normalization and de-normalization
+normalize <- function(x, y){(x - min(y)) / (max(y) - min(y))}
+denormalize <- function(x, y){x * (max(y) - min(y))}
+
+tmle_calc <- function(mu1_pred, mu0_pred, pi_pred, d, y){
+  # Normalize outcome variable
+  mu1_pred <- normalize(mu1_pred, y)
+  mu0_pred <- normalize(mu0_pred, y)
+  y_tilde <- normalize(y, y))
+
+  n <- length(y)
+
+  # Calculate clever covariates
+  H0 = (1-d)/(1-pi_pred)
+  H1 = d/pi_pred
+
+  # Estimate fluctuation parameter through maximum likelihood estimation
+  epsilon <- glm(y_tilde ~ -1 + H0 + H1 + offset(qlogis((d==1)*mu1_pred + (d==0)*mu0_pred)),
+                 family = binomial(link = 'logit')) %>%
+    tidy() %>%
+    pull(estimate)
+
+  # Targeted estimates of the potential outcomes
+  target_0 <- plogis(qlogis(mu0_pred + epsilon[1]*H0))
+  target_1 <- plogis(qlogis(mu1_pred + epsilon[2]*H1))
+
+  # Estimate ATE
+  ATE <- mean(target_1 - target_0)
+  return(denormalize(ATE, y))
+}
+```
+
+## Double/Debiased Machine Learning (DML)
+
+The most recently developed of the methods reviewed here, DML was proposed in an econometrics context [@chernozhukov_2018_double] and has since seen a flurry of development [@dukes_2022_doubly; @kennedy_2023_semiparametric; @semenova_2021_debiased; @chernozhukov_2022_long; @farbmacher_2022_causal; @jung_2021_estimating].
+The R package `DoubleML` [@bach_2021_doubleml] provides straightforward implementation of the method.
+
+DML is motivated by the need to handle problems with high-dimensional nuisance parameters, i.e.
+a large number of measured confounders.
+Flexible machine learning is appropriate for this task, but such methods suffer from regularization bias.
+DML removes this bias in a two-step procedure.
+First, it solves the auxiliary problem of estimating the treatment exposure model $E(D|X) = \pi(X)$.
+It then uses this model to remove bias: Neyman orthogonalization allows the creation of an orthogonalized regressor, essentially partialing out the effect of covariates $X$ from treatment $D$.
+The debiased $D$ is then used to estimate the conditional mean of the outcome $E(Y \mid X) = \mu(X)$, which can be used to calculate the estimand of interest.
+
+More formally, suppose we want to estimate $\delta$ in the following framework:
+$$y_i = \delta d_i + g_0(\mathbf x_i) + u_i,$$
+$$d_i = m_0(\mathbf x_i) + v_i.$$
+
+The idea is to estimate $g_0$ and $m_0$ separately, then use residual-on-residual regression to obtain an estimate of $\delta$, which we can designate $\hat \delta$.
+However this leaves a term in the asymptotic distribution of $\hat \delta$ that biases the estimate.
+To avoid this, DML uses sample splitting [@angrist_1995_splitsample].
+
+We randomly split the sample of $n$ observations into two sets, $I$ and $I^c$, each of size $n/2$.
+Using any prediction algorithm, we then estimate the response and treatment models using only set $I^c$:
+
+1) Estimate treatment model $\hat m_0$ in the equation $d_i = \hat m_0(\mathbf x_i) + \hat v_i, i \in I^c$.  
+2) Estimate the outcome model $\hat g_0$ in the equation $y_i =  \hat g_0(\mathbf x_i) + \hat u_i, i \in I^c$.
+
+Note that the estimation of the outcome does not consider treatment assignment $d_i$. This is a key difference between DML and AIPW or TMLE.
+
+Next, we use the estimated models to perform residual-on-residual regression *on the left out set* $I$ to obtain an estimate of $\delta$:
+$$\hat \delta(I^c, I) = \left(\sum_{i \in I} \hat v_i d_i \right)^{-1} 
+\sum_{i \in I} \hat v_i (y_i - \hat g_0 (\mathbf x_i)),$$
+
+where $\hat v_i = d_i - \hat m_0(\mathbf x_i)$.
+Using half the sample results in efficiency loss.
+To rectify this, we repeat the above procedure, switching the split sets.
+We then have $\delta(I^c, I)$ and $\delta(I, I^c)$.
+The cross-fitting DML estimator is:
+$$\widehat {ATE}_{DML} = \frac{\hat \delta (I^c, I) + \hat \delta (I, I^c)}{2}.$$
+R code to implement DML is shown below.
+Since DML involves sample splitting, this code is a little different from the above examples.
+We start with observed outcome values `y`, treatment assignment `d`, and covariate matrix `x`.
+First, a pre-processing function `dml_pre()` randomly splits the sample, outputting $I$ and $I^c$ sets of each of these variables.
+The second step predicts outcome and treatment probability for each half of the sample, using models fit to the other half.
+In the code chunk here, generalized random forests from the `grf` package are used to predict these, but any prediction algorithm can be used.
+Finally, a post-prediction function `dml_post()` performs the residual-on-residual regression for each half of the sample and finds the average of the two estimates to produce an ATE estimate.
+```{r dml-demo, eval = F, echo = T}
+# Pre-processing: sample splitting
+dml_pre <- function(y, d, x, seed = 1758){
+  set.seed(seed)
+
+  n <- length(y)
+  n_2 <- round(n/2)
+
+  # Split the sample
+  random_vec <- sample(1:n, n, replace = F)
+  I <- random_vec[1:n_2]
+  I_c <- random_vec[(n_2+1):n]
+
+  return(list(
+    y_I = y[I],
+    d_I = d[I],
+    x_I = x[I,],
+    y_I_c = y[I_c],
+    d_I_c = d[I_c],
+    x_I_c = x[I_c,]
+    ))
+}
+
+# Predictor function: in this case, generalized random forests
+grf_dml <- function(y_I, d_I, x_I, y_I_c, d_I_c, x_I_c){
+  # Train on the I_c sample, predict on the I sample
+  mu_mod1 <- grf::regression_forest(X = x_I_c, Y = y_I_c, tune.parameters = "all")
+  mu_pred1 <- predict(mu_mod1, newdata = x_I)$predictions
+
+  pi_mod1 <- grf::regression_forest(X = x_I_c, Y = d_I_c, tune.parameters = "all")
+  pi_pred1 <- predict(pi_mod1, newdata = x_I)$predictions
+
+  # Train on the I sample, predict on the I_c sample
+  mu_mod2 <- grf::regression_forest(X = x_I, Y = y_I, tune.parameters = "all")
+  mu_pred2 <- predict(mu_mod2, newdata = x_I_c)$predictions
+
+  pi_mod2 <- grf::regression_forest(X = x_I, Y = d_I, tune.parameters = "all")
+  pi_pred2 <- predict(pi_mod2, newdata = x_I_c)$predictions
+
+  return(list(
+    mu_pred1 = mu_pred1,
+    pi_pred1 = pi_pred1,
+    mu_pred2 = mu_pred2,
+    pi_pred2 = pi_pred2
+  ))
+}
+
+# Implement DML: takes outputs from pre_dml() and grf_dml()
+dml_post <- function(y_I, d_I, x_I, y_I_c, d_I_c, x_I_c,
+                     mu_pred1, pi_pred1, mu_pred2, pi_pred2){
+
+  # Residual-on-residual regression for each sample separately
+  v1 <- d_I - pi_pred1
+  delta1 <- (sum(v1 * d_I))^-1 * sum(v1 * (y_I - pi_pred1))
+
+  v2 <- d_I_c - pi_pred2
+  delta2 <- (sum(v2 * d_I_c))^-1 * sum(v2 * (y_I_c - pi_pred2))
+
+  # Average estimates from each sample
+  ate <- (delta1 + delta2)/2
+
+  return(ate)
+}
+
+dml_pre_out <- dml_pre(y = y, d = d, x = x)
+grf_dml_out <- do.call(grf_dml, dml_pre_out)
+dml_post_out <- do.call(dml_post, append(dml_pre_out, grf_dml_out))
+```
+
+## A simple demonstration using AIPW
+
+To demonstrate double robustness, this section presents one of the simpler double robust estimators, AIPW [@glynn_2010_introduction]. As shown above, we can write this estimator as follows:
+
+$$\begin{aligned}
+\widehat{ATE} = &\frac{1}{N} \sum_{i=1}^N \left( \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) \right) 
+- \frac{1}{N} \sum_{i=1}^N \left( \frac{(1-D_i)(Y_i - \hat \mu_0 (X_i))}{1-\hat \pi(X_i)} + \hat \mu_0(X_i) \right)
+\end{aligned}$$
+
+For each individual in the sample, this estimator calculates two quantities:
+
+- The treated potential outcome
+
+$$\hat Y_{1i} = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i)$$
+
+- The control potential outcome
+
+$$\hat Y_{0i} = \frac{(1-D_i)(Y_i - \hat \mu_0 (X_i))}{1-\hat \pi(X_i)} + \hat \mu_0(X_i)$$
+
+Let's focus on the treated model:
+
+$$\hat Y_{1i} = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i)$$
+
+First, assume that the outcome model $\mu_1(X_i)$ is *correctly* specified and the exposure model $\pi(X_i)$ is *incorreclty* specified.
+Let's also assume (for now) that we're dealing with a treated unit, i.e.
+$D_i = 1$.
+Then
+
+$$\hat \mu_1 (X_i) = Y_i$$
+
+and hence
+
+$$\hat Y_{1i} = \frac{D_i(0)}{\hat \pi (X_i)} + \hat \mu_1(X_i) = \hat \mu_1(X_i).$$
+
+So the model relies *only* on the outcome model.
+The incorrectly specified exposure model completely disappears from the equation.
+If we're dealing with a control unit ($D_i=0$), we get the same result:
+
+$$\hat Y_{1i} = \frac{0(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) = \hat \mu_1(X_i).$$
+
+Now, what if the *exposure* model $\pi(X_i)$ is correctly specified and the outcome model $\mu_1(X)$ is incorrect? First, we rewrite the estimator for the treated outcome:
+
+$$\begin{aligned}
+\hat Y_{1i}& = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) \\
+&= \frac{D_iY_i}{\hat \pi (X_i)} - \frac{D_i\hat \mu_1 (X_i)}{\hat \pi (X_i)} + \frac{\hat \pi (X_i)\hat \mu_1(X_i)}{\hat \pi (X_i)} \\
+& = \frac{D_iY_i}{\hat \pi (X_i)} - \left( \frac{D_i - \hat \pi(X_i)}{\hat \pi (X_i)}\right) \hat \mu_1(X_i). &&(*)
+\end{aligned}$$
+
+Since the exposure model is correclty specified, we have $D_i = \hat \pi(X_i)$ on average, so
+
+$$E[D_i - \hat \pi(X_i)] = 0.$$
+
+This means that the second term in equation $(*)$ is 0, so
+
+$$E[\hat Y_{1i}]= E \left [ \frac{D_iY_i}{\hat \pi (X_i)}\right].$$
+
+This shows that when the exposure model is correct, then the estimator depends *only* on the exposure model. We can make similar arguments for the control model $\hat Y_{0i}$.
+
+This demonstration shows that this estimator achieves double robustness: The estimator is robust to misspecification of either the exposure or the outcome model (but not both).
+
+# Methods
+
+These double robust methods have many similarities.
+How do the results they give compare?
+This section tests the performance of each in practice using two strategies.
+First, results are compared using simulated data from a causal inference competition (@dorie_2019_automated).
+The true treatment effect is known, so these simulations allow assessment of accuracy.
+Second, these methods are applied to data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW).
+The NSW randomly provided training to disadvantaged workers, allowing an experimental estimate of the effect of the intervention, and data assembled by @dehejia_1999_causal allows these experimental estimates to be compared to observational ones.
+
+The three double robust methods are compared to two sets of traditional methods used as benchmarks.
+First are one-model methods.
+The most classic method considered -- linear regression -- models only the response surface.
+Here it is estimated using ordinary least squares regression ("OLS"), entering each variable separately without any interactions or higher-order terms.
+Two other one-model methods model only the treatment assignment mechanism.
+Propensity score are estimated from logistic regression with each variable entered separately and without any higher order terms, then matched using the `MatchIt` package ("PSM").
+Finally, stabilized inverse probability weights [IPW, @austin_2015_moving, p.
+3663] are used for weighted OLS regression.
+These IPWs are estimated using each of the three under-the-hood estimation methods described below.
+
+The second set of traditional methods are two-model methods, which estimate separate models for treated and untreated units.
+In theory these could solve the misspecification problem that double robust methods are meant to solve, but they could still suffer from regularization bias.
+G-computation [@robins_1986_new; @hernan_2020_causal p.
+163; @snowden_2011_implementation] uses some estimation technique to predict outcomes under treatment and control for each unit in the dataset.
+The ATE estimate is the difference in the average prediction under treatment and the average prediction under control.
+The second two-model method is the Lin estimator [@lin_2013_agnostic].
+This method aims to solve issues with the bias induced by OLS regression in a randomization framework by interacting the treatment indicator with mean-centered covariates.
+
+Many of these methods allow the user to choose the underlying estimation method, results compare three techniques.
+First is using a logistic regression for the exposure model and an OLS regression for the outcome model.
+Second is generalized random forests [GRF, @athey_2019_generalized] using the `grf` R package, with separate models for exposure and outcome.
+The final technique is the SuperLearner (as promoted by the makers of TMLE) using the `SuperLearner` package, again with separate models for exposure and outcome.
+GLM, glmnet (lasso), and XGBoost models are considered for the SuperLearner.
+These three estimation techniques are used for each of the three double robust methods, for IPW, and for G-computation.
+
+For the simulations, results compare only point estimates from these methods.
+For evaluation of the experimental LaLonde data, I use bootstrapping with 100 samples to obtain estimates and standard errors.
+
+# Results
+
+```{r dorie-sim, eval = F}
+set.seed(185)
+
+# sims %>%
+#   lapply(function(x) append(x, list()))
+
+sim_list <- list()
+for(i in 1:20){ # up to 77
+  #sim_list_nest <- list()
+  for(j in 1:10){ # up to 100
+    print(paste0(i,',',j))
+    sim_list[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016,
+                                      i, j, extraInfo = T) %>% 
+      append(list(dataset = i, set = 'main'))
+  }
+}
+
+sim_linear <- list()
+for(i in c(1, 3)){
+  for(j in 1:100){ 
+    print(paste0(i,',',j))
+    sim_linear[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016, 
+                                      i, j, extraInfo = T) %>% 
+      append(list(dataset = i, set = 'linear'))
+  }
+}
+
+saveRDS(append(sim_list, sim_linear), here('files', 'sims.RDS'))
+```
+
+```{r large, eval = F}
+# dataset 7: polynomial     0.35    one-term exponential      0.75      high
+set.seed(185)
+
+sim_list <- list()
+
+for(j in c(2, 5, 10, 20)){ # up to 100
+  for(i in 1:20){ # up to 77
+  #sim_list_nest <- list()
+
+    print(paste0(i,',',j))
+
+    dataset <- aciccomp2016::input_2016 %>% 
+      slice(rep(1:n(), each = j))
+
+    sim_list[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(dataset, 7, i, extraInfo = T) %>% 
+      append(list(dataset = 7, set = 'large', size = j*4802))
+  }
+}
+
+saveRDS(sim_list, here('files', 'sims_large.RDS'))
+
+```
+
+```{r sims-small, eval = F}
+set.seed(185)
+
+sim_list <- list()
+for(j in c(150, 300, 600, 1200, 2400, 4802)){ 
+  for(i in 1:20){ 
+  #sim_list_nest <- list()
+
+    print(paste0(i,',',j))
+
+    sample_index <- sample(1:4802, j, replace = F)
+
+    sim_list[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016, 7, i, extraInfo = T) %>% 
+      append(list(dorie_dataset = 7, set = 'small', size = j))
+
+    for(name in names(sim_list[[paste0(i,',',j)]])[1:7]){
+      sim_list[[paste0(i,',',j)]][[name]] <- sim_list[[paste0(i,',',j)]][[name]][sample_index]
+    }
+
+    sim_list[[paste0(i,',',j)]]$x <- sim_list[[paste0(i,',',j)]]$x[sample_index,]
+  }
+}
+
+saveRDS(sim_list, here('files', 'sims_small.RDS'))
+```
+
+```{r sim-test, eval = F}
+data_test <- bind_rows(aciccomp2016::input_2016, aciccomp2016::input_2016)
+
+acs <- read_dta('/Users/nathan/Data/ACS/acs_2008_2021.dta')
+
+test <- aciccomp2016::dgp_2016(data_test, parameter_list, 1950, extraInfo = T)
+set.seed(185)
+test_acs <- aciccomp2016::dgp_2016(filter(acs, year == 2016) %>% drop_na() %>% sample_n(1e5), 
+                                   parameter_list, 1950, extraInfo = T)
+```
+
+```{r lm-sim, eval = F}
+lm_df <- lm_sim(sims)
+
+write_csv(lm_df, here('files', 'lm_df.csv'))
+
+lm_df %>%
+  group_by(set) %>%
+  summarize(ate_est = mean(ate), 
+            se = sd(ate))
+```
+
+```{r psm-sim, eval = F}
+psm_df <- psm_sim(sims)
+
+write_csv(psm_df, here('files', 'psm_df.csv'))
+```
+
+```{r pred-calc, eval = F}
+
+ols_logit_pred_list <- list()
+for(i in 1:length(sims)){
+  print(i)
+  dat <- sims[[i]]
+
+  start_time = Sys.time()
+
+  ols_logit_pred_list[[i]] <- ols_logit_pred(
+    y = dat$y,
+    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
+    x = dat$x) %>%
+    append(list(truth = mean(dat$y.1) - mean(dat$y.0),
+                comp_time = as.numeric(difftime(Sys.time(), start_time, units = 'secs'))))
+}
+saveRDS(ols_logit_pred_list, here('files/homemade', 'ols_logit_pred.RDS'))
+
+# tibble(ols_logit_pred_list[[i]]$y,
+#              ols_logit_pred_list[[i]]$mu1_pred, 
+#              ols_logit_pred_list[[i]]$mu0_pred,
+#              ols_logit_pred_list[[i]]$d,
+#              hist(ols_logit_pred_list[[12]]$pi_pred)
+#              )
+
+grf_pred_list <- list()
+for(i in 1:length(sims)){
+  print(i)
+  dat <- sims[[i]]
+
+  start_time = Sys.time()
+
+  grf_pred_list[[i]] <- grf_pred(
+    y = dat$y,
+    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
+    x = dat$x) %>%
+    append(list(truth = mean(dat$y.1) - mean(dat$y.0),
+                comp_time = as.numeric(difftime(Sys.time(), start_time, units = 'secs')),
+                dorie_dataset = sims[[i]]$dataset,
+                set = sims[[i]]$set,
+                size = sims[[i]]$size))
+}
+saveRDS(grf_pred_list, here('files/homemade', 'grf_pred.RDS'))
+
+superlearner_pred_list <- list() 
+for(i in 1:length(sims)){
+  print(i)
+  dat <- sims[[i]]
+
+  start_time = Sys.time()
+
+  superlearner_pred_list[[i]] <- superlearner_pred(
+    y = dat$y,
+    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
+    x = dat$x) %>%
+    append(list(truth = mean(dat$y.1) - mean(dat$y.0),
+                comp_time = as.numeric(difftime(Sys.time(), start_time, units = 'secs')),
+                dorie_dataset = sims[[i]]$dataset,
+                set = sims[[i]]$set,
+                size = sims[[i]]$size))
+}
+saveRDS(superlearner_pred_list, here('files/homemade', 'superlearner_pred.RDS'))
+
+```
+
+```{r ipw, eval = F}
+ols_logit_pred_list2 <- readRDS(here('files/homemade', 'ols_logit_pred.RDS'))
+grf_pred_list2 <- readRDS(here('files/homemade', 'grf_pred.RDS'))
+superlearner_pred_list2 <- readRDS(here('files/homemade', 'superlearner_pred.RDS'))
+
+ipw_out_list <- list()
+predictions <- list(ols_logit_pred_list2, grf_pred_list2, superlearner_pred_list2)
+pred_names <- c('logit', 'grf', 'superlearner')
+for(i in 1:length(sims)){
+  print(i)
+  for(j in 1:length(predictions)){
+
+    start_time <- Sys.time()
+
+    D <- sims[[i]]$z == 'trt'
+    PrD <- mean(D)
+    ps <- predictions[[j]][[i]]$pi_pred
+    ipw <- D*PrD/ps + (1-D)*(1-PrD)/(1-ps)
+
+    lm_out <- lm(sims[[i]]$y ~ D, weights=ipw) 
+    ate_ipw <- coefficients(lm_out)[[2]]
+
+    comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
+
+    ipw_out_list[[paste0(i, ',', j)]] <- data.frame(
+      dataset = i,
+      method = pred_names[[j]],
+      ate = ate_ipw, 
+      truth = predictions[[j]][[i]]$truth, 
+      comp_time = comp_time + predictions[[j]][[i]]$comp_time,
+      dorie_dataset = sims[[i]]$dataset,
+      set = sims[[i]]$set,
+      size = sims[[i]]$size)
+  }
+}
+
+write_csv(bind_rows(ipw_out_list), here('files', 'ipw.csv'))
+```
+
+```{r g-comp, eval = F}
+ols_logit_pred_list2 <- readRDS(here('files/homemade', 'ols_logit_pred.RDS'))
+grf_pred_list2 <- readRDS(here('files/homemade', 'grf_pred.RDS'))
+superlearner_pred_list2 <- readRDS(here('files/homemade', 'superlearner_pred.RDS'))
+
+gcomp_out_list <- list()
+predictions <- list(ols_logit_pred_list2, grf_pred_list2, superlearner_pred_list2)
+pred_names <- c('ols', 'grf', 'superlearner')
+for(i in 1:length(sims)){
+  print(i)
+  for(j in 1:length(predictions)){
+
+    start_time <- Sys.time()
+
+    gcomp_out <- with(predictions[[j]][[i]], mean(mu1_pred - mu0_pred))
+
+    comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
+
+    gcomp_out_list[[paste0(i, ',', j)]] <- data.frame(
+      dataset = i,
+      method = pred_names[[j]],
+      ate = gcomp_out, 
+      truth = predictions[[j]][[i]]$truth, 
+      comp_time = comp_time + predictions[[j]][[i]]$comp_time,
+      dorie_dataset = sims[[i]]$dataset,
+      set = sims[[i]]$set,
+      size = sims[[i]]$size)
+  }
+}
+
+write_csv(bind_rows(gcomp_out_list), here('files', 'gcomp.csv'))
+```
+
+```{r lin, eval = F}
+
+n <- length(sims)
+lin_list <- list()
+for(i in 1:n){
+  start_time <- Sys.time()
+
+  print(paste0(i, ' out of ', n))
+  sim_dat <- data.frame(y = sims[[i]]$y, 
+                        d = ifelse(sims[[i]]$z == 'trt', 1, 0), 
+                        sims[[i]]$x)
+
+  ate <- NA
+  tryCatch({
+    lm_out <- tidy(estimatr::lm_lin(y ~ d, 
+                                    covariates = as.formula(paste0('~ ', paste(names(sims[[i]]$x), collapse = ' + '))), 
+                                    data = sim_dat))
+    ate <- lm_out[[2,2]]
+
+    }, error=function(e){
+      cat("ERROR :",conditionMessage(e), "\n")
+      })
+
+  lin_list[[i]] <- data.frame(dataset = i,
+                             ate = ate,
+                             #se = lm_out[[2,3]],
+                             truth = mean(sims[[i]]$y.1) - mean(sims[[i]]$y.0),
+                             dorie_dataset = sims[[i]]$dataset,
+                             set = sims[[i]]$set,
+                             size = sims[[i]]$size,
+                             comp_time = as.numeric(difftime(Sys.time(), start_time, units = 'secs')))
+}
+
+write_csv(bind_rows(lin_list), here('files', 'lin.csv'))
+```
+
+```{r aipw, eval = F}
+
+aipw_calc2 <- function(mu1_pred, mu0_pred, pi_pred, d, y){
+  n <- length(mu1_pred)
+
+  # pi_pred <- case_when(
+  #   pi_pred < quantile(pi_pred, c(.025)) ~ as.numeric(quantile(pi_pred, c(.025))),
+  #   pi_pred > quantile(pi_pred, c(.975)) ~ as.numeric(quantile(pi_pred, c(.975))),
+  #   T ~ pi_pred)
+
+  # pi_pred <- case_when(
+  #   pi_pred < .01 ~ .01,
+  #   pi_pred > .99 ~ .99,
+  #   T ~ pi_pred)
+
+  ipw <- (d*y)/pi_pred - (1-d)*y/(1-pi_pred)
+  adjust <- (d-pi_pred)/(pi_pred*(1-pi_pred)) * (1-pi_pred)*mu1_pred + pi_pred*mu0_pred
+
+  ate <- (1/n) * sum(ipw - adjust)
+
+  return(ate)
+}
+
+aipw_out_list <- list()
+predictions <- list(ols_logit_pred_list2, grf_pred_list2, superlearner_pred_list2)
+pred_names <- c('ols_logit', 'grf', 'superlearner')
+for(i in 1:length(sims)){
+  print(i)
+  for(j in 1:length(predictions)){
+
+    start_time <- Sys.time()
+    aipw_out <- with(predictions[[j]][[i]], 
+                     aipw_calc(mu1_pred = mu1_pred, 
+                               mu0_pred = mu0_pred,
+                               pi_pred = pi_pred,
+                               d = d,
+                               y = y))
+    comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
+
+    aipw_out_list[[paste0(i, ',', j)]] <- data.frame(
+      dataset = i,
+      method = pred_names[[j]],
+      ate = aipw_out, 
+      truth = predictions[[j]][[i]]$truth, 
+      comp_time = comp_time + predictions[[j]][[i]]$comp_time,
+      dorie_dataset = sims[[i]]$dataset,
+      set = sims[[i]]$set,
+      size = sims[[i]]$size)
+  }
+}
+
+write_csv(bind_rows(aipw_out_list), here('files/homemade', 'aipw.csv'))
+
+aipw_out_list <- list()
+predictions <- list(ols_logit_pred_list2, grf_pred_list2, superlearner_pred_list2)
+pred_names <- c('ols_logit', 'grf', 'superlearner')
+for(i in 1:length(sims)){
+  print(i)
+  for(j in 1:length(predictions)){
+
+    start_time <- Sys.time()
+    aipw_out <- with(predictions[[j]][[i]], 
+                     aipw_calc_trunc(mu1_pred = mu1_pred, 
+                               mu0_pred = mu0_pred,
+                               pi_pred = pi_pred,
+                               d = d,
+                               y = y))
+    comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
+
+    aipw_out_list[[paste0(i, ',', j)]] <- data.frame(
+      dataset = i,
+      method = pred_names[[j]],
+      ate = aipw_out, 
+      truth = predictions[[j]][[i]]$truth, 
+      comp_time = comp_time + predictions[[j]][[i]]$comp_time,
+      dorie_dataset = sims[[i]]$dataset,
+      set = sims[[i]]$set,
+      size = sims[[i]]$size)
+  }
+}
+
+write_csv(bind_rows(aipw_out_list), here('files/homemade', 'aipw_trunc.csv'))
+
+```
+
+```{r tmle, eval = F}
+
+tmle_out_list <- list()
+predictions <- list(ols_logit_pred_list2, grf_pred_list2, superlearner_pred_list2)
+pred_names <- c('ols_logit', 'grf', 'superlearner')
+
+for(i in 1:length(sims)){
+  print(i)
+  for(j in 1:length(predictions)){
+    start_time <- Sys.time()
+    tryCatch({
+      tmle_out <- with(predictions[[j]][[i]], 
+                       tmle_calc(mu1_pred = normalize(mu1_pred, y), 
+                                 mu0_pred = normalize(mu0_pred, y),
+                                 pi_pred = pi_pred,
+                                 d = d,
+                                 y = normalize(y, y))
+                       )
+    }, error=function(e){
+      tmle_out <- NA
+      })
+    comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
+
+    tmle_out_list[[paste0(i, ',', j)]] <- data.frame(
+      dataset = i,
+      method = pred_names[[j]],
+      ate = denormalize(tmle_out, predictions[[j]][[i]]$y), 
+      truth = predictions[[j]][[i]]$truth, 
+      comp_time = comp_time + predictions[[j]][[i]]$comp_time,
+      fail = is.na(tmle_out),
+      dorie_dataset = sims[[i]]$dataset,
+      set = sims[[i]]$set,
+      size = sims[[i]]$size)
+  }
+}
+
+write_csv(bind_rows(tmle_out_list), here('files/homemade', 'tmle.csv'))
+
+# logit_logit_pred_list <- list()
+# 
+# for(i in 1:length(sim_linear)){
+#   print(i)
+#   dat <- sim_linear[[i]]
+#   
+#   logit_logit_pred_out <- logit_logit_pred(
+#     y = with(dat, (y - min(y)) / (max(y) - min(y))),
+#     d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
+#     x = dat$x
+#     )
+#   
+#   ate <- with(logit_logit_pred_out, 
+#               tmle_calc(mu1_pred = mu1_pred, 
+#                         mu0_pred = mu0_pred,
+#                         pi_pred = pi_pred,
+#                         d = d,
+#                         y = y)) 
+#   truth <- mean(dat$y.1) - mean(dat$y.0)
+# 
+#   logit_logit_pred_list[[i]] <-  data.frame(ate = ate * (max(dat$y)-min(dat$y)),
+#                                             truth = truth)
+# }
+# 
+# perform(bind_rows(logit_logit_pred_list), label = 'ols, logit, tmle')
+# 
+# 
+# #### 
+# 
+# grf_pred_list <- list()
+# 
+# for(i in 1:10){ #length(sim_linear)){
+#   print(i)
+#   dat <- sim_linear[[i]]
+#   
+#   grf_pred_out <- grf_pred(
+#     y = dat$y, # with(dat, (y - min(y)) / (max(y) - min(y))),
+#     d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
+#     x = dat$x
+#     )
+#   
+#   yt <- function(x, y){(x - min(y)) / (max(y) - min(y))}
+#   
+#   ate <- with(grf_pred_out, 
+#               tmle_calc(mu1_pred = yt(mu1_pred, dat$y), 
+#                         mu0_pred = yt(mu0_pred, dat$y),
+#                         pi_pred = pi_pred,
+#                         d = d,
+#                         y = yt(y, dat$y)))
+#   truth <- mean(dat$y.1) - mean(dat$y.0)
+#   
+#   grf_pred_list[[i]] <-  data.frame(ate = ate * (max(dat$y)-min(dat$y)),
+#                                             truth = truth)
+# }
+# 
+# perform(bind_rows(grf_pred_list), label = 'grf, tmle')
+
+# superlearner_pred_list <- list()
+# 
+# for(i in 1:length(sim_linear)){
+#   print(i)
+#   dat <- sim_linear[[i]]
+#   
+#   superlearner_pred_out <- superlearner_pred(
+#     y = with(dat, (y - min(y)) / (max(y) - min(y))),
+#     d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
+#     x = dat$x
+#     )
+#   
+#   ate <- with(superlearner_pred_out, 
+#               tmle_calc(mu1_pred = mu1_pred, 
+#                         mu0_pred = mu0_pred,
+#                         pi_pred = pi_pred,
+#                         d = d,
+#                         y = y))
+#   truth = mean(dat$y.1) - mean(dat$y.0)
+#   
+#   superlearner_pred_list[[i]] <- data.frame(ate = ate * (max(dat$y)-min(dat$y)),
+#                                             truth = truth)
+# }
+# 
+# perform(bind_rows(superlearner_pred_list), label = 'superlearner, tmle')
+```
+
+```{r dml, eval = F}
+
+## DML OLS logit
+
+ols_logit_dml_list <- list()
+
+set.seed(1285)
+for(i in 1:length(sims)){
+  print(i)
+  dat <- sims[[i]]
+
+  start_time <- Sys.time()
+  dml_pre_out <- dml_pre(dat$y,
+                       as.numeric(ifelse(dat$z == 'trt', 1, 0)),
+                       x = dat$x)
+
+  ols_logit_dml_out <- do.call(ols_logit_dml, dml_pre_out)
+
+  dml_post_out <- do.call(dml_post, append(dml_pre_out, ols_logit_dml_out))
+  comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
+
+  truth <- mean(dat$y.1) - mean(dat$y.0)
+
+  ols_logit_dml_list[[i]] <- data.frame(ate = dml_post_out, 
+                              truth = truth, 
+                              comp_time = comp_time,
+                              dataset = i,
+                              dorie_dataset = dat$dataset,
+                              set = dat$set,
+                              size = dat$size)
+}
+
+write_csv(bind_rows(ols_logit_dml_list), 
+          here('files/homemade', 'dml_ols_logit.csv'))
+
+# perform(bind_rows(ols_logit_dml_list), label = 'grf, dml')
+
+## GRF
+grf_dml_list <- list()
+
+set.seed(1285)
+for(i in 1:length(sims)){
+  print(i)
+  dat <- sims[[i]]
+
+  start_time <- Sys.time()
+
+  dml_pre_out <- dml_pre(dat$y,
+                       as.numeric(ifelse(dat$z == 'trt', 1, 0)),
+                       x = dat$x)
+  dml_post_out <- NA
+   tryCatch({
+      grf_dml_out <- do.call(grf_dml, dml_pre_out)
+
+      dml_post_out <- do.call(dml_post, append(dml_pre_out, grf_dml_out))
+      }, error=function(e){
+        cat("ERROR :",conditionMessage(e), "\n")
+        })
+
+  comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
+
+  truth <- mean(dat$y.1) - mean(dat$y.0)
+
+  grf_dml_list[[i]] <- data.frame(ate = dml_post_out, 
+                              truth = truth, 
+                              comp_time = comp_time,
+                              dataset = i,
+                              dorie_dataset = dat$dataset,
+                              set = dat$set,
+                              size = dat$size)
+}
+
+write_csv(bind_rows(grf_dml_list), 
+          here('files/homemade', 'dml_grf.csv'))
+
+# perform(bind_rows(grf_dml_list), label = 'grf, dml')
+
+## Superlearner
+superlearner_dml_list <- list()
+
+set.seed(1285)
+for(i in 1:length(sims)){
+  print(i)
+  dat <- sims[[i]]
+
+  start_time <- Sys.time()
+
+  dml_pre_out <- dml_pre(dat$y,
+                       as.numeric(ifelse(dat$z == 'trt', 1, 0)),
+                       x = dat$x)
+  dml_post_out <- NA
+   tryCatch({
+      superlearner_dml_out <- do.call(superlearner_dml, dml_pre_out)
+      dml_post_out <- do.call(dml_post, append(dml_pre_out, superlearner_dml_out ))
+      }, error=function(e){
+        cat("ERROR :",conditionMessage(e), "\n")
+        })
+
+  comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
+
+  truth <- mean(dat$y.1) - mean(dat$y.0)
+
+  superlearner_dml_list[[i]] <- data.frame(ate = dml_post_out, 
+                              truth = truth, 
+                              comp_time = comp_time,
+                              dataset = i,
+                              dorie_dataset = dat$dataset,
+                              set = dat$set,
+                              size = dat$size)
+}
+
+write_csv(bind_rows(superlearner_dml_list), 
+          here('files/homemade', 'dml_superlearner.csv'))
+
+#perform(bind_rows(superlearner_dml_list), label = 'superlearner, dml')
+
+```
+
+## Simluations with Dorie et al. (2019) Data
+
+In 2016, the Atlantic Causal Inference Conference hosted a competition for causal inference methods that adjust on observables.
+@dorie_2019_automated published the results of this competition, along with the data used in the competition.
+Below, I test double robust methods on the 20 data sets used for the "do-it-yourself" part of the competition.
+The data represent a hypothetical twins study investigating the impact of birth weight on IQ.
+The data have 4802 observations and 52 covariates.
+The authors of the study specify a different data generating process for the potential outcomes in each data set.
+In all cases, ignorability holds, but the authors vary the following:
+
+- degree of nonlinearity
+- percentage of treated
+- overlap for the treatment group
+- alignment (correspondence between the assignment mechanism and the response surface)
+- treatment effect heterogeneity
+- overall magnitude of the treatment effect
+
+### Main results
+
+The 20 data sets used here cover a range of these attributes; see the supplemental material from @dorie_2019_automated for details.
+I use 10 simulations of each data set, resulting in 200 data sets.
+I then calculate bias, percent bias (the estimator's bias as a percentage of its standard error), root mean squared error (rmse), and median absolute error (mae).
+I also present the number of datasets for which the method fails and the average computation time for each data set, in seconds.
+
+Results for the full range of simulations are shown in Table \@ref(tab:dorie-results) and Figure \@ref(fig:dorie-results-fig).
+Using AIPW as written above results in some wildly biased estimates for the ols_logit estimator, due to dividing by some very small propensity scores.
+Hence I present estimates from a trimmed AIPW estimator, where predicted exposure model values are set to 0.01 if they are less than 0.01 and to 0.99 if they are greater than 0.99.
+
+The lowest bias is achieved by AIPW with GRF, followed by propensity score matching and then OLS.
+The lowest root mean squared error is obtained by AIPW with GRF, followed by TMLE with GRF, and next by OLS regression.
+Results are similar if we consider percent bias or mean absolute error.
+DML does not perform particularly well and also has the highest computation times due to sample splitting.
+
+```{r dorie-results}
+
+lm_df <- read_csv(here('files', 'lm_df.csv')) %>%
+  mutate(method = 'ols')
+
+psm_df <- read_csv(here('files', 'psm_df.csv')) %>%
+  mutate(method = 'psm')
+
+lin_df <- read_csv(here('files', 'lin.csv')) %>%
+  mutate(method = 'lin')
+
+ipw_df <- read_csv(here('files', 'ipw.csv')) %>%
+  mutate(estimator = method,
+         method = 'ipw')
+
+gcomp_df <- read_csv(here('files', 'gcomp.csv')) %>%
+  mutate(estimator = method,
+         method = 'g-comp')
+
+aipw_df <- read_csv(here('files/homemade', 'aipw.csv')) %>%
+  mutate(estimator = method,
+         method = 'aipw')
+
+aipw_trunc_df <- read_csv(here('files/homemade', 'aipw_trunc.csv')) %>%
+  mutate(estimator = method,
+         method = 'aipw')
+
+tmle_df <- read_csv(here('files/homemade', 'tmle.csv')) %>%
+  # filter(fail == F) %>%
+  select(-fail) %>%
+  mutate(estimator = method,
+         method = 'tmle')
+
+dml_df <- bind_rows(
+  mutate(read_csv(here('files/homemade', 'dml_ols_logit.csv')), 
+         estimator = 'ols_logit',
+         method = 'dml',
+         dataset = row_number()),
+  mutate(read_csv(here('files/homemade', 'dml_grf.csv')), 
+         estimator = 'grf',
+         method = 'dml',
+         dataset = row_number()),
+  mutate(read_csv(here('files/homemade', 'dml_superlearner.csv')), 
+         estimator = 'superlearner',
+         method = 'dml',
+         dataset = row_number())
+) %>%
+  select(names(tmle_df))
+
+sim_results <- bind_rows(lm_df, psm_df, lin_df, ipw_df, gcomp_df, aipw_trunc_df, tmle_df, dml_df) %>%
+  mutate(estimator = factor(estimator, levels = c('ols_logit', 'ols', 'logit', 'grf', 'superlearner')),
+         method = factor(method, levels = c('ols', 'psm', 'lin', 'ipw', 'g-comp', 'aipw', 'tmle', 'dml'))) %>%
+  arrange(method, estimator) %>%
+  #mutate(estimator = ifelse(is.na(estimator), 'NA', estimator)) %>%
+  mutate(bias = ate - truth,
+         method_estimator = ifelse(is.na(estimator), as.character(method), paste0(method, ', ', estimator))) %>%
+  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator}))) 
+```
+
+```{r dorie-results-fig, fig.height = 6, fig.cap = 'Results of Monte Carlo simulations using the first 20 datasets from Dorie et al. (2019), 10 replications each.'}
+addline_format <- function(x,...){
+    gsub('\\s','\n',x)
+}
+
+sim_results %>% 
+  filter(set == 'main') %>%
+  mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
+  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator}))) %>%
+  #filter(method %in% c('ols', 'psm', 'aipw')) %>%
+  ggplot(aes(x = method_estimator, y = bias)) +
+  geom_jitter(alpha = .2, width = .3, aes(color = method)) +
+  geom_boxplot(alpha = .5, outlier.alpha = 0) +
+  geom_hline(yintercept = 0) +
+  #facet_wrap(~method, scales = 'free_x') +
+  labs(x = '', title = 'All datasets') +
+  theme(#axis.text.x=element_text(angle=-15), 
+        legend.position = 'none') +
+  scale_x_discrete(labels=function(x){sub(", ", "\n", x)})
+```
+
+### Linear DGPs
+
+Traditional methods may perform better when the data generating processes are linear.
+To test this, I use 100 simulations of each of the two datasets from @dorie_2019_automated with linear data generating processes (numbers 1 and 3) to show how these methods perform when the underlying models are linear.
+
+If we consider only the linear datasets (Table \@ref(tab:dorie-results-linear) and Figure \@ref(fig:dorie-results-linear-fig)), OLS obtains the lowest bias, followed by AIPW with GRF and then propensity score matching.
+The lowest root mean squared error is achieved by OLS, then AIPW with GRF, and then TMLE with GRF.
+Percent bias and mean absolute error show similar results.
+
+Overall, traditional methods perform surprisingly well in comparison with the double robust methods.
+Even in the full range of datasets -- which include highly nonlinear exposure and outcome data-generating processes -- OLS and propensity score matching obtain some of the smallest bias.
+Generalized random forests appear to be the best estimators for the double robust methods, though a SuperLearner than incorporates GRF has the potential to outperform GRF alone, at the expense of computation time.
+Notably, the method with the longest computation time -- DML with a SuperLearner -- takes over 2,000 times as along as OLS.
+
+```{r dorie-results-linear-fig, fig.height = 6, fig.cap = 'Results of Monte Carlo simulations using the two datasets from Dorie et al.
+(2019), with linear data generating processes, 100 replications each ("linear").'}
+sim_results %>% 
+  filter(set == 'linear') %>%
+  mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
+  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator}))) %>%
+  #filter(method %in% c('ols', 'psm', 'aipw')) %>%
+  ggplot(aes(x = method_estimator, y = bias)) +
+  geom_jitter(alpha = .2, width = .3, aes(color = method)) +
+  geom_boxplot(alpha = .5, outlier.alpha = 0) +
+  geom_hline(yintercept = 0) +
+  #facet_wrap(~method, scales = 'free_x') +
+  labs(x = '', title = 'Linear DGPs') +
+  theme(#axis.text.x=element_text(angle=-15), 
+        legend.position = 'none') +
+  scale_x_discrete(labels=function(x){sub(", ", "\n", x)})
+```
+
+### Do results vary by DGP?
+```{r vary}
+sim_results_dgp <- sim_results %>%
+  filter(set == 'main') %>%
+  # mutate(paramter_num = ceiling(dataset/10)) %>%
+  left_join(mutate(aciccomp2016::parameters_2016, dorie_dataset = row_number()))
+
+dgp_names <- c('Treatment assignment', 'Probability of treatment',
+               'Overlap of treatment', 'Response surface',
+               'Alignment (same terms for treatment and response)',
+               'Treatment effect heterogeneity')
+
+names(dgp_names) <- names(aciccomp2016::parameters_2016)
+
+for(name in colnames(aciccomp2016::parameters_2016[1])){
+  plot <- sim_results_dgp %>% 
+    mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
+    mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator}))) %>%
+    #filter(method %in% c('ols', 'psm', 'aipw')) %>%
+    ggplot(aes(x = method_estimator, y = bias)) +
+    geom_jitter(alpha = .2, width = .3, aes(color = method)) +
+    geom_boxplot(alpha = .5, outlier.alpha = 0) +
+    #facet_wrap(~method, scales = 'free_x') +
+    labs(x = '', title = dgp_names[name]) +
+    theme(#axis.text.x=element_text(angle=-15), 
+          legend.position = 'none') +
+    scale_x_discrete(labels=function(x){sub(", ", "\n", x)}) +
+    facet_wrap(vars(!!sym(name)), ncol = 1, scales = 'free')
+
+  print(plot)
+}
+```
+
+### Do results vary by sample size?
+
+The double robust methods reviewed here have been shown to have lower bias asymptotically.
+Is the issue with previous results simply that the sample size of the simulation data ($n$ = 4,802) is too small for double robust methods to outperform traditional methods?
+To test this, this section uses simulated datasets of varying sizes, from 150 to 96,040 (20 times the original sample size).
+These datasets are also derived from the @dorie_2019_automated `aciccomp2016` package, using parameter set 7, a fairly nonlinear DGP with high heterogeneity.
+For sample sizes less than 4,802, the sample is randomly drawn from a randomly generated 4,802-unit sample.
+For sample sizes greater than 4,802, the design matrix (but non the outcome variable) is duplicated, then fed into the `dgp_2016` function.
+This preserves covariate distributions but retains stochasticity in the outcome.
+
+Results are presented in Table \@ref(tab:dorie-results-size) and Figure \@ref(fig:dorie-size-fig).
+
+```{r dorie-size-fig, fig.height = 6, fig.cap = 'RMSE of Monte Carlo simulations using dataset 7 from Dorie et al. (2019) with varying sample sizes, 20 replications each'}
+addline_format <- function(x,...){
+    gsub('\\s','\n',x)
+}
+
+# sim_results %>%
+#   filter(set %in% c('small', 'large')) %>% 
+#   group_by(method_estimator, size) %>%
+#   summarize(bias = round(mean(ate - truth, na.rm = T), 3),
+#             percent_bias = bias/sd(ate, na.rm = T),
+#             rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
+#             mae = median(abs(ate - truth), na.rm = T),
+#             comp_time = sum(comp_time)/n(),
+#             fail_count = n() - sum(!is.na(ate))
+#               ) %>%
+#   mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
+#   mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator})),
+#          size = factor(size, levels = sort(unique({.$size})))) %>%
+#   ggplot(aes(x = size, y = rmse)) +
+#   geom_point() +
+#   facet_wrap(~method_estimator, ncol = 1, scales = 'free')
+
+# # text labels
+# sim_results %>%
+#   filter(set %in% c('small', 'large')) %>% 
+#   group_by(method, estimator, method_estimator, size) %>%
+#   summarize(bias = round(mean(ate - truth, na.rm = T), 3),
+#             percent_bias = bias/sd(ate, na.rm = T),
+#             rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
+#             mae = median(abs(ate - truth), na.rm = T),
+#             comp_time = sum(comp_time)/n(),
+#             fail_count = n() - sum(!is.na(ate))
+#               ) %>%
+#   mutate(estimator = if_else(is.na(estimator), 'NA', estimator)) %>%
+#   mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
+#   mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator})),
+#          size = factor(size, levels = sort(unique({.$size})))) %>%
+#   ggplot(aes(x = size, y = rmse, color = estimator, label= method)) +
+#   geom_text() +
+#   scale_y_continuous(trans='log10')
+
+sim_results %>%
+  filter(set %in% c('small', 'large')) %>%
+  group_by(method, estimator, method_estimator, size) %>%
+  summarize(bias = round(mean(ate - truth, na.rm = T), 3),
+            percent_bias = bias/sd(ate, na.rm = T),
+            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
+            mae = median(abs(ate - truth), na.rm = T),
+            comp_time = sum(comp_time)/n(),
+            fail_count = n() - sum(!is.na(ate))
+              ) %>%
+  group_by(method_estimator) %>%
+  mutate(min_size = min(size*bias/bias, na.rm = T)) %>%
+  ungroup() %>%
+  mutate(estimator = if_else(is.na(estimator), 'NA', estimator),
+         method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
+  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator})),
+         label_min = if_else(size == min_size, as.character(method_estimator), NA_character_),
+         label_max = if_else(size == max(as.numeric(size)), 
+                             as.character(method_estimator), NA_character_),
+         size = factor(size, levels = sort(unique({.$size})))) %>%
+  ggplot(aes(x = size, y = rmse, color = method, linetype = estimator, group = method_estimator)) +
+  geom_line() +
+  ggrepel::geom_text_repel(aes(label = label_min), nudge_x = -1, na.rm = T, segment.color = 'transparent') +
+  ggrepel::geom_text_repel(aes(label = label_max), nudge_x = 1, na.rm = T, segment.color = 'transparent') +
+  scale_y_continuous(trans='log10') +
+  theme(legend.position = 'none')
+```
+
 ## Comparisons using LaLonde NSW Data
 
-As another benchmark test, I use data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NWS), as provided by @dehejia_1999_causal.
-The NWS randomly provided training to disadvantaged workers, allowing an experimental estimate of the effect of the intervention.
-This study had `r nrow(filter(lalonde_exp, treat == T))` treated and `r nrow(filter(lalonde_exp, treat == F))` control participants
-
-LaLonde compared these experimental estimates to estimates comparing the treated group to samples drawn from the Panel Study of Income Dynamics (PSID) and Westat's Matched Current Population Survey-Social Security Administration File (CPS).
+As another test, I use data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW), as provided by @dehejia_1999_causal.
+Between March 1975 and July 1977, the NSW randomly provided training to disadvantaged workers.
+LaLonde used earnings in 1978 as the outcome of interest; comparing earnings in this year for treated and untreated workers allows an experimental estimate of the effect of the intervention.
+Restricting the sample to men, this study had `r nrow(filter(lalonde_exp, treat == T))` treated and `r nrow(filter(lalonde_exp, treat == F))` control participants.
+Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, and not having a high school degree.
+Following @dehejia_1999_causal, I add a variable indicating whether each respondent's earnings in 1975 was $0 -- i.e., they were unemployed.
+
+LaLonde compared these experimental estimates to control samples drawn from the Panel Study of Income Dynamics (PSID) and Westat's Matched Current Population Survey-Social Security Administration File (CPS).
 The PSID-1 sample (*n* = `r nrow(lalonde_psid1_controls)`) contains all male household heads under 55 who did not classify themselves as retired in 1975, and the PSID-3 sample (*n* = `r nrow(lalonde_psid3_controls)`) further restricts this to men who were not working in spring of 1976 or 1975.
-The CPS-1 sample (*n* = `r nrow(lalonde_cps1_controls)`) includes all CPS males under 55, and CPS-3 (*n* = `r nrow(lalonde_cps3_controls)`) restricts this two those who were not working in March 1976 whose income in 1975 was below the poverty level.
-Restricting these observational samples is meant to get closer to the population eligible for the NWS.
-
-Following @dehejia_1999_causal, I present results for the original samples analyzed by @lalonde_1986_evaluating, but I also include results using a subsample of the experimental group that has 1974 earnings data available (`r nrow(filter(lalonde_exp_74, treat == T))` treated and `r nrow(filter(lalonde_exp_74, treat == F))` control participants).
-
-I again compare the three double robust methods to a linear model fitted by OLS ("lm") and propensity score matching using logistic regression ("psm").
-Results are presented in Table \@ref(tab:lalonde).
-
-For the original NSW data, none of the methods perform especially well.
-For the PSID samples, none of the estimates have a positive sign, as in the experimental estimates.
-For CPS, TMLE is the only method that achieves a positive sign.
-
-Including 1974 earnings data allows much better estimates with the observational control groups.
-(Note that the restricted experimental sample has a greater experimental effect estimate than the full experimental sample.) For PSID-1, TMLE performs the best, while DML performs much worse than even OLS.
+The CPS-1 sample (*n* = `r nrow(lalonde_cps1_controls)`) includes all CPS males under 55, and CPS-3 (*n* = `r nrow(lalonde_cps3_controls)`) restricts this two those who were not working in March 1976 whose earnings in 1975 was below the poverty level.
+Restricting these observational samples gets closer to the group eligible for the NSW.
+
+Following @dehejia_1999_causal, I present results for the original samples analyzed by @lalonde_1986_evaluating, but I also include results using a subsample of the experimental group that has 1974 earnings data available (`r nrow(filter(lalonde_exp_74, treat == T))` treated and `r nrow(filter(lalonde_exp_74, treat == F))` control participants) and include this additional covariate, along with an indicator variable for no earnings in 1974.
+
+I again compare the three double robust methods to a linear model fitted by OLS ("ols") and propensity score matching using logistic regression ("psm").
+Results are presented in Table \@ref(tab:lalonde), Figure \@ref(fig:lalonde-combined), and Figure \@ref(fig:lalonde-combined-1974).
+
+The "experimental" column provides a baseline for the comparison, suggesting that the program resulted in an earnings gain of about \$700 to \$800.
+If selection on observables holds, then we should be able to recover these estimates from the non-experimental control groups.
+Most of the methods do not perform very well; the only ones to estimate a positive treatment effects are OLS for the PSID-3 sample and TMLE for the CPS samples, and these are still smaller than the experimental baselines.
+
+Including 1974 earnings data results in much better estimates with the observational control groups.
+For PSID-1, TMLE provides estimates closest to the experimental ones, while DML performs much worse than even OLS.
 For PSID-3, OLS and TMLE both perform well.
@@
 
+These results highlight the importance of selection on observables holding.
+Without including 1974 earnings as a covariate, it appears that selection on observables does not hold, as most methods provide highly inaccurate estimates with the wrong sign.
+Once 1974 earnings are included, all of the methods provide estimates much closer to the experimental values.
+PSM, AIPW, and TMLE all do fairly well, while OLS and DML are more unstable across samples.
+
+```{r lalonde-calc-homemade, eval = F}
+
+lalonde_func <- function(dataset, sample, include_74 = F){
+  set.seed(872)
+
+  if(include_74 == F){
+    lalonde_variables <- names(lalonde_exp)[3:9]
+    dataset <- bind_rows(filter(lalonde_exp, treat == 1), dataset)
+
+  } else {
+    lalonde_variables <- names(lalonde_exp_74)[3:10]
+    dataset <- bind_rows(filter(lalonde_exp_74, treat == 1), dataset)
+  }
+
+  dat <- list(y = dataset$re78,
+                z = ifelse(dataset$treat == 1, 'trt', 'ctl'),
+                x = dataset[,lalonde_variables])
+
+  out_list <- list()
+
+  out_list[['ols']] <- data.frame(
+      method = 'ols',
+      estimator = NA,
+      ate = lm_sim(list(dat))$est_df$ate)
+
+  out_list[['psm']] <- data.frame(
+      method = 'psm',
+      estimator = NA,
+      ate = lm_sim(list(dat))$est_df$ate)
+
+  ols_logit_pred_out <- ols_logit_pred(
+    y = dat$y,
+    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
+    x = dat$x)
+
+  grf_pred_out <- grf_pred(
+    y = dat$y,
+    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
+    x = dat$x)
+
+  superlearner_pred_out <- superlearner_pred(
+    y = dat$y,
+    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
+    x = dat$x)
+
+  predictions <- list(ols_logit_pred_out, grf_pred_out, superlearner_pred_out)
+  pred_names <- c('ols_logit', 'grf', 'superlearner')
+  for(j in 1:length(predictions)){
+    aipw_out <- with(predictions[[j]], 
+                     aipw_calc_trunc(mu1_pred = mu1_pred, 
+                               mu0_pred = mu0_pred,
+                               pi_pred = pi_pred,
+                               d = d,
+                               y = y))
+
+    out_list[[paste0('aipw', j)]] <- data.frame(
+      method = 'aipw',
+      estimator = pred_names[[j]],
+      ate = aipw_out)
+
+    tmle_out <- with(predictions[[j]], 
+                       tmle_calc(mu1_pred = normalize(mu1_pred, y), 
+                                 mu0_pred = normalize(mu0_pred, y),
+                                 pi_pred = pi_pred,
+                                 d = d,
+                                 y = normalize(y, y))
+                       )
+
+      out_list[[paste0('tmle', j)]] <- data.frame(
+        method = 'tmle',
+        estimator = pred_names[[j]],
+        ate =  denormalize(tmle_out, predictions[[j]]$y))
+  }
+
+  dml_pre_out <- dml_pre(dat$y,
+                         as.numeric(ifelse(dat$z == 'trt', 1, 0)),
+                         x = dat$x)
+  ols_logit_dml_out <- do.call(ols_logit_dml, dml_pre_out)
+  dml_post_out <- do.call(dml_post, append(dml_pre_out, ols_logit_dml_out))
+
+  out_list[['dml_ols_logit']] <- data.frame(method = 'dml',
+                                            estimator = 'ols_logit',
+                                            ate = dml_post_out)
+
+  dml_pre_out <- dml_pre(dat$y,
+                     as.numeric(ifelse(dat$z == 'trt', 1, 0)),
+                     x = dat$x)
+  grf_dml_out <- do.call(ols_logit_dml, dml_pre_out)
+  dml_post_out <- do.call(dml_post, append(dml_pre_out, grf_dml_out))
+
+  out_list[['dml_grf']] <- data.frame(method = 'dml',
+                                            estimator = 'grf',
+                                            ate = dml_post_out)
+
+  dml_pre_out <- dml_pre(dat$y,
+                     as.numeric(ifelse(dat$z == 'trt', 1, 0)),
+                     x = dat$x)
+  superlearner_dml_out <- do.call(ols_logit_dml, dml_pre_out)
+  dml_post_out <- do.call(dml_post, append(dml_pre_out, superlearner_dml_out))
+
+  out_list[['dml_superlearner']] <- data.frame(method = 'dml',
+                                            estimator = 'superlearner',
+                                            ate = dml_post_out)
+
+  bind_rows(out_list) %>%
+    mutate(sample = sample) %>%
+    return()
+}
+
+lalonde_func_out <- bind_rows(
+  lalonde_func(filter(lalonde_exp, treat == 0), sample = 'experimental'),
+  lalonde_func(lalonde_psid1_controls, 'PSID-1'),
+  lalonde_func(lalonde_psid3_controls, 'PSID-3'),
+  lalonde_func(lalonde_cps1_controls, 'CPS-1'),
+  lalonde_func(lalonde_cps1_controls, 'CPS-3'))
+
+  lalonde_func_out %>%
+    pivot_wider(names_from = 'sample', values_from = ate) %>%
+  mutate(estimator = factor(estimator, levels = c('ols_logit', 'grf', 'superlearner')),
+         method = factor(method, levels = c('ols', 'psm', 'aipw', 'aipw (trim)', 'tmle', 'dml'))) %>%
+  arrange(method, estimator) %>%
+  #write_csv(here('files/homemade', 'lalonde.csv'))
+
+bind_rows(
+  lalonde_func(filter(lalonde_exp_74, treat == 0), sample = 'experimental', T),
+  lalonde_func(lalonde_psid1_controls, 'PSID-1', T),
+  lalonde_func(lalonde_psid3_controls, 'PSID-3', T),
+  lalonde_func(lalonde_cps1_controls, 'CPS-1', T),
+  lalonde_func(lalonde_cps1_controls, 'CPS-3', T)) %>%
+    pivot_wider(names_from = 'sample', values_from = estimate) %>%
+  write_csv(here('files/homemade', 'lalonde_74.csv'))
+
+```
+
 ```{r lalonde-calc, eval = F}
+unemp_func <- function(x){
+  x %>%
+    as.data.frame() %>%
+    mutate(re74_0 = re74 == 0,
+         re75_0 = re75 == 0) 
+}
+
+lalonde_exp <- read_dta(here('data', 'nsw.dta')) %>%
+  as.data.frame() %>%
+  mutate(re75_0 = re75 == 0)
+lalonde_exp_74 <- read_dta(here('data', 'nsw_dw.dta')) %>%
+  unemp_func()
+lalonde_cps1_controls <- read_dta(here('data', 'cps_controls.dta')) %>%
+  unemp_func()
+lalonde_cps3_controls <- read_dta(here('data', 'cps_controls3.dta')) %>%
+  unemp_func()
+lalonde_psid1_controls <- read_dta(here('data', 'psid_controls.dta')) %>%
+  unemp_func()
+lalonde_psid3_controls <- read_dta(here('data', 'psid_controls3.dta')) %>%
+  unemp_func()
+
 lalonde_func <- function(dataset, sample, include_74 = F){
@@
     bind_rows() %>%
-    mutate(method = c('lm', 'psm', 'aipw', 'tmle', 'dml'),
+    mutate(method = c('ols', 'psm', 'aipw', 'tmle', 'dml'),
            sample = sample,
+           ate = round(d),
+           se = round(se),
            estimate = paste0(round(d), ' (', round(se), ')')) %>%
@@
   write_csv(here('files', 'lalonde_74.csv'))
-# 
-# lalonde_cps1 <- bind_rows(filter(lalonde_exp, treat == 1), lalonde_cps1_controls)
-# lalonde_cps3 <- bind_rows(filter(lalonde_exp, treat == 1), lalonde_cps3_controls)
-# 
-# lalonde_exp <- list(list(y = as.numeric(lalonde_exp$re78),
-#                 z = ifelse(lalonde_exp$treat == 1, 'trt', 'ctl'),
-#                 x = lalonde_exp[,lalonde_variables]))
-# lalonde_cps1 <- list(list(y = lalonde_cps1$re78,
-#                 z = ifelse(lalonde_cps1$treat == 1, 'trt', 'ctl'),
-#                 x = lalonde_cps1[,lalonde_variables]))
-# lalonde_cps3 <- list(list(y = lalonde_cps3$re78,
-#                 z = ifelse(lalonde_cps3$treat == 1, 'trt', 'ctl'),
-#                 x = lalonde_cps3[,lalonde_variables]))
-# 
-# 
-# set.seed(185)
-# lapply(list(
-#     lm_sim(lalonde_exp),
-#     lm_sim(lalonde_cps1),
-#     lm_sim(lalonde_cps3),
-#     psm_sim(lalonde_exp),
-#     psm_sim(lalonde_cps1),
-#     psm_sim(lalonde_cps3),
-#     aipw_sim(lalonde_exp),
-#     aipw_sim(lalonde_cps1),
-#     aipw_sim(lalonde_cps3),
-#     tmle_sim(lalonde_exp),
-#     tmle_sim(lalonde_cps1),
-#     tmle_sim(lalonde_cps3),
-#     dml_sim(lalonde_exp),
-#     dml_sim(lalonde_cps1),
-#     dml_sim(lalonde_cps3)), 
-#   bind_cols) %>% 
-#   bind_rows()  %>%
-#   mutate(method = rep(c('lm', 'psm', 'aipw', 'tmle', 'dml'), each = 3),
-#          sample = rep(c('experimental', 'CPS-1', 'CPS-3'), 5),
-#          estimate = paste0(round(d), ' (', round(se), ')')) %>%
-#   select(method, sample, estimate) %>%
-#   pivot_wider(names_from = 'sample', values_from = estimate) %>%
-#  write_csv(here('files', 'lalonde_74.csv'))
-
-# lalonde <- CBPS::LaLonde %>%
-#   filter(re74.miss == F) %>%
-#   mutate(re74_0 = re74 == 0,
-#          re75_0 = re75 == 0)
-# 
-# lalonde_exp <- filter(lalonde, exper == 1)
-# lalonde_exp <- list(list(y = lalonde_exp$re78,
-#                 z = ifelse(lalonde_exp$treat == 1, 'trt', 'ctl'),
-#                 x = select(lalonde_exp, age:re75, re74_0, re75_0)))
-# lalonde_psid <- filter(lalonde, (exper == 1 & treat == 1) | exper == 0)
-# lalonde_psid <- list(list(y = lalonde_psid$re78,
-#                 z = ifelse(lalonde_psid$treat == 1, 'trt', 'ctl'),
-#                 x = select(lalonde_psid, age:re75, re74_0, re75_0)))
-# 
-# 
-# lalonde_cps <- MatchIt::lalonde %>%
-#   mutate(re74_0 = re74 == 0,
-#          re75_0 = re75 == 0)
-# lalonde_cps <- list(list(y = lalonde_cps$re78,
-#                 z = ifelse(lalonde_cps$treat == 1, 'trt', 'ctl'),
-#                 x = select(lalonde_cps, age:re75, re74_0, re75_0)))
-# 
-# 
-# set.seed(185)
-# lapply(list(
-#     lm_sim(lalonde_exp),
-#     lm_sim(lalonde_psid),
-#     lm_sim(lalonde_cps),
-#     psm_sim(lalonde_exp),
-#     psm_sim(lalonde_psid),
-#     psm_sim(lalonde_cps),
-#     aipw_sim(lalonde_exp),
-#     aipw_sim(lalonde_psid),
-#     aipw_sim(lalonde_cps),
-#     tmle_sim(lalonde_exp),
-#     tmle_sim(lalonde_psid),
-#     tmle_sim(lalonde_cps),
-#     dml_sim(lalonde_exp),
-#     dml_sim(lalonde_psid),
-#     dml_sim(lalonde_cps)), 
-#   bind_cols) %>% 
-#   bind_rows()  %>%
-#   mutate(method = rep(c('lm', 'psm', 'aipw', 'tmle', 'dml'), each = 3),
-#          sample = rep(c('experimental', 'PSID', 'CPS'), 5),
-#          estimate = paste0(round(d), ' (', round(se), ')')) %>%
-#   select(method, sample, estimate) %>%
-#   pivot_wider(names_from = 'sample', values_from = estimate) %>%
-#   write_csv(here('files', 'lalonde.csv'))
-```
-
-```{r lalonde}
+```
+
+```{r lalonde, eval = F}
 bind_rows(
@@
                     # linesep = '',
-                    caption = 'ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups. Standard errors shown in parentheses.')
+                    caption = 'ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
+Standard errors shown in parentheses.
+Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
+The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnigns in 1974.')
 
@@
 
+```{r lalonde-combined, eval = F, fig.cap = 'ATE estimates and 95% confidence intervals for Lalonde NSW data (original sample) as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.'}
+lalonde_df <- bind_rows(
+  read_csv(here('files', 'lalonde.csv')) %>%
+    mutate(sample = 'Original LaLonde'),
+  read_csv(here('files', 'lalonde_74.csv')) %>%
+    mutate(sample = 'With 1974 earnings')) %>%
+  select(sample, method, everything()) %>%
+  pivot_longer(-c(sample, method)) %>%
+  separate_wider_delim(value, delim = '(', names = c('ate', 'se')) %>%
+  separate_wider_delim(se, delim = ')', names = c('se', 'blank')) %>%
+  mutate(ate = as.numeric(ate), 
+         se = as.numeric(se),
+         method = factor(method, levels = unique({.$method})),
+         name = factor(name, levels = unique({.$name})),
+         experimental = name == 'experimental') %>%
+  select(-blank)
+
+lalonde_df %>%
+  filter(sample == 'Original LaLonde') %>%
+  ggplot(aes(x = name, y = ate, color = experimental)) +
+  geom_pointrange(aes(ymin = ate - 1.96*se, ymax = ate + 1.96*se)) +
+  geom_hline(yintercept = 0) +
+  facet_wrap(~method, scales = 'free_x') +
+  theme(axis.text.x=element_text(angle=-15), 
+        legend.position = 'none') +
+  scale_color_manual(values = ucla_palette) +
+  labs(title = 'Original LaLonde Sample', x = '')   
+```
+
+```{r lalonde-combined-1974, eval = F, fig.cap = 'ATE estimates and 95% confidence intervals for Lalonde NSW data (with 1974 earnings) as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.'}
+lalonde_df %>%
+  filter(sample == 'With 1974 earnings') %>%
+  ggplot(aes(x = name, y = ate, color = experimental)) +
+  geom_pointrange(aes(ymin = ate - 1.96*se, ymax = ate + 1.96*se)) +
+  geom_hline(yintercept = 0) +
+  facet_wrap(~method, scales = 'free_x') +
+  theme(axis.text.x=element_text(angle=-15), 
+        legend.position = 'none') +
+  scale_color_manual(values = ucla_palette) +
+  labs(title = 'With 1974 earnings', x = '')
+```
+
+```{r lalonde-traditional}
+lalonde_results <- sim_results %>%
+  mutate(set = ifelse(set == 'lalondeCPS-3 74', 'lalonde CPS-3 74', set),
+         set = ifelse(set == 'lalondeCPS-3 original', 'lalonde CPS-3 original', set)) %>%
+  filter(str_detect(set, 'lalonde')) %>%
+  separate_wider_delim(set, delim = ' ', names = c('set', 'sample', 'include_74')) %>%
+  mutate(sample = factor(sample, levels = unique({.$sample})),
+         estimator = factor(estimator, levels = c('ols_logit', 'ols', 'logit', 'grf', 'superlearner')),
+         method = factor(method, levels = c('ols', 'psm', 'lin', 'ipw', 'g-comp', 'aipw', 'tmle', 'dml')))
+
+lalonde_results_df <- lalonde_results %>%
+  group_by(set, sample, include_74, method_estimator) %>%
+  summarize(estimate = mean(ate),
+            se = sd(ate)) %>%
+  ungroup() %>%
+  mutate(value = paste0(round(estimate), ' (', round(se), ')')) %>%
+  select(include_74, sample, method_estimator, value) %>%
+  pivot_wider(values_from = value, names_from = method_estimator) %>%
+  arrange(desc(include_74))
+
+lalonde_results_df %>%
+  select(include_74:`g-comp, superlearner`) %>%
+  kableExtra::kable(booktabs = T, 
+                    # digits = 3,
+                    # linesep = '',
+                    caption = 'Traditional methods: ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
+Standard errors shown in parentheses.
+Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
+The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnigns in 1974.')
+```
+
+```{r lalonde-dr}
+lalonde_results_df %>%
+  select(include_74, sample, `g-comp, superlearner`:`dml, superlearner`) %>%
+  kableExtra::kable(booktabs = T, 
+                    # digits = 3,
+                    # linesep = '',
+                    caption = 'Double robust methods: ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
+Standard errors shown in parentheses.
+Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
+The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnigns in 1974.')
+```
+
+# Conclusion
+
+This paper aimed to provide an introduction to and evaluation of double robust methods for covariate adjustment in causal inference.
+By comparing AIPW, TMLE, and DML to the more traditional statistical methods of OLS and PSM, it allows evaluation of whether these methods are worth the effort and (computational) time for social scientists to adopt them.
+
+Results are mixed.
+On the one hand, in the full range of simulated data, AIPW with GRF estimators achieves the lowest bias and root mean squared error.
+This is the simplest (and most computationally efficient) of the double robust methods, although GRF is computationally expensive.
+TMLE with GRF also does fairly well.
+But OLS and PSM have strong showings, in the top three smallest bias or root mean squared error.
+In the datasets with linear data-generating processes, OLS achieves the lowest bias and root mean squared error.
+
+In the experimental LaLonde data, OLS does not perform as strongly.
+Although it is one of the few methods to provide experimental estimates with the correct sign in the original LaLonde set of covariates, its estimates are highly unstable across samples.
+When 1974 earnings are used as a covariate, PSM, AIPW, and TMLE all perform fairly well, though TMLE comes out on top.
+
+Overall, these double robust methods do not show a clear advantage over simpler, more computationally efficient methods such as OLS and PSM.
+While they are useful for social scientists to understand, in most applications, OLS or PSM provide similar results.
+However, in certain circumstances these double robust methods may be a better choice.
+Especially when paired with a highly flexible estimator like GRF, these methods can be useful when the number of covariates is high or even exceeds the number of observations.
+If the researcher believes the data-generating process is highly nonlinear, they may also be a good a choice, at least as a sensitivity check.
+
+This paper has a number of limitations.
+First, it does not consider situations where ignorability does not hold.
+@hunermund_2023_double evaluate a case of this, where endogenous variables are included in the covariate space, showing this can result in biased estimates from DML.
+
+\newpage
+
 # References
+
+<div id="refs"></div>
+
+\newpage
+
+# (APPENDIX) Appendix {-}
+
+# Appendix
+
+```{r dorie-results-table}
+sim_results %>%
+  filter(set == 'main') %>%
+  group_by(estimator, method) %>%
+  summarize(bias = round(mean(ate - truth, na.rm = T), 3),
+            # var = round(var(ate, na.rm = T), 3),
+            percent_bias = bias/sd(ate, na.rm = T),
+            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
+            mae = median(abs(ate - truth), na.rm = T),
+            comp_time = sum(comp_time)/n(),
+            fail_count = n() - sum(!is.na(ate))
+              ) %>%
+  select(method, everything()) %>%
+  arrange(method, estimator) %>%
+  # mutate(bias = as.character(bias),
+  #        rmse = as.character(rmse)) %>%
+  # mutate(across(bias:comp_time, function(x){as.character(round(x, 3))})) %>%
+  kableExtra::kable(booktabs = T, 
+                    digits = 3,
+                    linesep = '',
+                    caption = 'Results of Monte Carlo simulations using the first 20 datasets from Dorie et al.
+(2019), 10 replications each.
+Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is average computation time measured in seconds for each dataset.') %>%
+  kable_styling(latex_options = c("hold_position"))
+```
+
+\newpage
+
+```{r dorie-results-linear}
+sim_results %>%
+  filter(set == 'linear') %>%
+  group_by(estimator, method) %>%
+  summarize(bias = round(mean(ate - truth, na.rm = T), 3),
+            percent_bias = bias/sd(ate, na.rm = T),
+            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
+            mae = median(abs(ate - truth), na.rm = T),
+            comp_time = sum(comp_time)/n(),
+            fail_count = n() - sum(!is.na(ate))
+              ) %>%
+  select(method, everything()) %>%
+  arrange(method, estimator) %>%
+  # mutate(across(bias:comp_time, function(x){as.character(round(x, 3))})) %>%
+  kableExtra::kable(booktabs = T, 
+                    digits = 3,
+                    linesep = '',
+                    caption = 'Results of Monte Carlo simulations using the two datasets from Dorie et al.
+(2019), with linear data generating processes, 100 replications each ("linear").
+Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is average computation time measured in seconds for each dataset.') %>%
+  kable_styling(latex_options = c("hold_position"))
+```
+
+\newpage
+
+```{r dorie-results-size}
+sim_results %>%
+  filter(set %in% c('small', 'large')) %>% 
+  group_by(estimator, method, size) %>%
+  summarize(bias = round(mean(ate - truth, na.rm = T), 3),
+            percent_bias = bias/sd(ate, na.rm = T),
+            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
+            mae = median(abs(ate - truth), na.rm = T),
+            comp_time = sum(comp_time)/n(),
+            fail_count = n() - sum(!is.na(ate))
+              ) %>%
+  select(method, everything()) %>%
+  arrange(method, estimator, size) %>%  
+  # mutate(bias = as.character(bias),
+  #        rmse = as.character(rmse)) %>%
+  # mutate(across(bias:comp_time, function(x){as.character(round(x, 3))})) %>%
+  kableExtra::kable(booktabs = T, 
+                    digits = 3,
+                    linesep = '',
+                    longtable = T,
+                    caption = 'Results of Monte Carlo simulations using dataset 7 from Dorie et al.
+(2019) with varying sample sizes, 20 replications each.
+Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is average computation time measured in seconds for each dataset.') %>%
+  kable_styling(latex_options = c("hold_position")) #'repeat_header')) 
+```

### 2024-03-11 draft/ms-adj-draft.Rmd
full draft for working groups

@@
     pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
-    latex_engine: xelatex
+    #latex_engine: xelatex
 always_allow_html: true
@@
 citeproc: no
-fontfamily: mathpazo
+#fontfamily: mathpazo
 #fontsize: 11pt
@@
 title: "Double Robust, Flexible Adjustment Methods for Causal Inference: An Overview and an Evaluation"
-# subtitle: "American Sociological Association Annual Meeting 2024"
-author:  Nathan I. Hoffmann, Department of Sociology, UCLA
+
+author:  Nathan I. Hoffmann, Departments of Sociology and Statistics, UCLA
 date: "`r format(Sys.time(), '%B %e, %Y')`"
@@
 It is also unclear whether these methods actually outperform more traditional methods in finite samples.
-This paper has two aims: It is a guide to some of the latest methods in double robust, flexible covariate adjustment for causal inference, and it compares these methods to more traditional statistical methods.
+This paper has two aims: It is a guide to some of the latest methods in double robust, flexible covariate adjustment for causal inference, and it compares these methods to more traditional statistical methods and flexible \"single robust\" methods.
 It does this by using both simulated data where the treatment effect estimate is known, and then using comparisons of experimental and observational data from the National Supported Work Demonstration.
-Methods covered include Augmented Inverse Probability Weighting, Targeted Maximum Likelihood Estimation, and Double/Debiased Machine Learning.
-Results suggest that these methods do not necessarily outperform OLS regression or matching on propensity score estimated by logistic regression, even in cases where the data generating process is not linear."
+Methods covered include Augmented Inverse Probability Weighting (AIPW), Targeted Maximum Likelihood Estimation (TMLE), and Double/Debiased Machine Learning (DML).
+Results suggest that some of these methods do outperform traditional methods in a wide range of simulations, but only slightly.
+In particular, the top performers are TMLE and AIPW in conjunction with flexible machine learning algorithms.
+But G-computation with the same flexible machine learning algorithms obtains almost identical results, and simple regression methods are nearly comparable in bias and are much more computationally efficient."
 
@@
 library(here)
+library(patchwork)
 library(haven)
@@
 
-```{r load-sims, eval = F}
-lalonde_bootstrap <- function(dataset, sample, include_74 = F, iter = 100){
-
-  lalonde_variables <- c('age', 'education', 'black', 'hispanic', 'married', 'nodegree', 're75', 're75_0')
-  if(include_74 == F){
-        dataset <- bind_rows(filter(lalonde_exp, treat == 1), dataset)
-
-      } else {
-        lalonde_variables <- c(lalonde_variables, 're74', 're74_0')
-        dataset <- bind_rows(filter(lalonde_exp_74, treat == 1), dataset)
-      }
-
-  bootstrap_list <- list()
-
-  for(i in 1:iter){
-    dataset_bootstrap <- sample_n(dataset, nrow(dataset), replace = T)
-
-    bootstrap_list[[i]] <- list(y = dataset_bootstrap$re78,
-                  z = ifelse(dataset_bootstrap$treat == 1, 'trt', 'ctl'),
-                  x = dataset_bootstrap[,lalonde_variables],
-                  y.1 = NA, y.0 = NA,
-                  dataset = i,
-                  set = sample,
-                  size = nrow(dataset_bootstrap))
-  }
-
-  return(bootstrap_list)
-}
-
-set.seed(1859)
-sims_lalonde <- c(
-  lalonde_bootstrap(filter(lalonde_exp, treat == 0), sample = 'lalonde experimental original'),
-  lalonde_bootstrap(lalonde_psid1_controls, 'lalonde PSID-1 original'),
-  lalonde_bootstrap(lalonde_psid3_controls, 'lalonde PSID-3 original'),
-  lalonde_bootstrap(lalonde_cps1_controls, 'lalonde CPS-1 original'),
-  lalonde_bootstrap(lalonde_cps1_controls, 'lalonde CPS-3 original'),
-  lalonde_bootstrap(filter(lalonde_exp_74, treat == 0), sample = 'lalonde experimental 74', include_74 = T),
-  lalonde_bootstrap(lalonde_psid1_controls, 'lalonde PSID-1 74', include_74 = T),
-  lalonde_bootstrap(lalonde_psid3_controls, 'lalonde PSID-3 74', include_74 = T),
-  lalonde_bootstrap(lalonde_cps1_controls, 'lalonde CPS-1 74', include_74 = T),
-  lalonde_bootstrap(lalonde_cps1_controls, 'lalonde CPS-3 74', include_74 = T))
-
-# sims <- readRDS(here('files', 'sims.RDS'))
-
-sims_main <- readRDS(here('files_main', 'sims.RDS'))
-sims_large <- readRDS(here('files_large', 'sims_large.RDS'))
-sims_small <- readRDS(here('files_small', 'sims_small.RDS'))
-
-sims <- sims_main %>% append(sims_small) %>% append(sims_large) %>% append(sims_lalonde)
-
-# sims <- sims %>% append(sims_large)
-
-# sims <- readRDS(here('files', 'sims_small.RDS'))
-
-# for(i in 1:length(sims_small)){
-#   # sims_large[[i]]$size <- nrow(sims_large[[i]]$x)
-#   sims_small[[i]]$dataset <- 7
-# }
-# saveRDS(sims_large, here('files_large', 'sims_large.RDS'))
-# 
-# 
-# sims_combined <- sims %>% append(sims_small) %>% append(sims_large)
-# 
-# index_df <- data.frame(dorie_dataset = sapply(sims_combined, function(x) x$dataset),
-#                        set = sapply(sims_combined, function(x) x$set),
-#                        size = sapply(sims_combined, function(x) x$size)) %>%
-#   mutate(dataset = c(1:length(sims), 1:length(sims_small), 1:length(sims_large)))
-# 
-# lm_df <- read_csv(here('files_main', 'lm_df.csv')) %>% 
-#   mutate(set = c(rep('main', 200), rep('linear', 200))) %>%
-#   bind_rows(read_csv(here('files_small', 'lm_df.csv')) %>% mutate(set = 'small')) %>%
-#   bind_rows(read_csv(here('files_large', 'lm_df.csv')) %>% mutate(set = 'large')) %>%
-#   left_join(index_df)
-# 
-# 
-# write_csv(lm_df, here('files', 'lm_df.csv'))
-# 
-# psm_df <- read_csv(here('files_main', 'psm_df.csv')) %>% 
-#   mutate(set = ifelse(dataset <= 200, 'main', 'linear')) %>%
-#   bind_rows(read_csv(here('files_small', 'psm_df.csv')) %>% mutate(set = 'small')) %>%
-#   bind_rows(read_csv(here('files_large', 'psm_df.csv')) %>% mutate(set = 'large')) %>%
-#   left_join(index_df)
-# 
-# write_csv(lm_df, here('files', 'psm_df.csv'))
-# 
-# 
-# aipw_df <- read_csv(here('files_main/homemade', 'aipw.csv')) %>% 
-#   mutate(set = ifelse(dataset <= 200, 'main', 'linear')) %>%
-#   bind_rows(read_csv(here('files_small/homemade', 'aipw.csv')) %>% mutate(set = 'small')) %>%
-#   bind_rows(read_csv(here('files_large/homemade', 'aipw.csv')) %>% mutate(set = 'large')) %>%
-#   left_join(index_df)
-# 
-# write_csv(aipw_df, here('files/homemade', 'aipw.csv'))
-# 
-# 
-# aipw_trunc_df <- read_csv(here('files_main/homemade', 'aipw_trunc.csv')) %>% 
-#   mutate(set = ifelse(dataset <= 200, 'main', 'linear')) %>%
-#   bind_rows(read_csv(here('files_small/homemade', 'aipw_trunc.csv')) %>% mutate(set = 'small')) %>%
-#   bind_rows(read_csv(here('files_large/homemade', 'aipw_trunc.csv')) %>% mutate(set = 'large')) %>%
-#   left_join(index_df)
-# 
-# write_csv(aipw_trunc_df, here('files/homemade', 'aipw_trunc.csv'))
-# 
-# tmle_df <- read_csv(here('files_main/homemade', 'tmle.csv')) %>% 
-#   mutate(set = ifelse(dataset <= 200, 'main', 'linear')) %>%
-#   bind_rows(read_csv(here('files_small/homemade', 'tmle.csv')) %>% mutate(set = 'small')) %>%
-#   bind_rows(read_csv(here('files_large/homemade', 'tmle.csv')) %>% mutate(set = 'large')) %>%
-#   left_join(index_df)
-# 
-# write_csv(tmle_df, here('files/homemade', 'tmle.csv'))
-# 
-# dml_ols_logit_df <- read_csv(here('files_main/homemade', 'dml_ols_logit.csv')) %>%
-#   mutate(dataset = 1:nrow(.)) %>%
-#   bind_rows(read_csv(here('files_small/homemade', 'dml_ols_logit.csv')) %>% 
-#               mutate(set = 'small',
-#                      dorie_dataset = 7,
-#                      dataset = row_number())) %>%
-#   bind_rows(read_csv(here('files_large/homemade', 'dml_ols_logit.csv')) %>% 
-#               mutate(set = 'large',
-#                      dorie_dataset = 7,
-#                      dataset = row_number())) %>%
-#   left_join(index_df) 
-# 
-# write_csv(dml_ols_logit_df, here('files/homemade', 'dml_ols_logit.csv'))
-# 
-# dml_grf_df <- read_csv(here('files_main/homemade', 'dml_grf.csv')) %>%
-#   mutate(dataset = 1:nrow(.)) %>%
-#   bind_rows(read_csv(here('files_small/homemade', 'dml_grf.csv')) %>% 
-#               mutate(set = 'small',
-#                      dorie_dataset = 7,
-#                      dataset = row_number())) %>%
-#   bind_rows(read_csv(here('files_large/homemade', 'dml_grf.csv')) %>% 
-#               mutate(set = 'large',
-#                      dorie_dataset = 7,
-#                      dataset = row_number())) %>%
-#   select(-dorie_dataset) %>%
-#   left_join(index_df)
-# 
-# write_csv(dml_grf_df, here('files/homemade', 'dml_grf.csv'))
-# 
-# 
-# dml_superlearner_df <- read_csv(here('files_main/homemade', 'dml_superlearner.csv')) %>%
-#   mutate(dataset = 1:nrow(.)) %>%
-#   bind_rows(read_csv(here('files_small/homemade', 'dml_superlearner.csv')) %>% 
-#               mutate(set = 'small',
-#                      dorie_dataset = 7,
-#                      dataset = row_number())) %>%
-#   bind_rows(read_csv(here('files_large/homemade', 'dml_superlearner.csv')) %>% 
-#               mutate(set = 'large',
-#                      dorie_dataset = 7,
-#                      dataset = row_number())) %>%
-#   select(-dorie_dataset) %>%
-#   left_join(index_df)
-# 
-# write_csv(dml_superlearner_df, here('files/homemade', 'dml_superlearner.csv'))
-
-# ols_logit_pred_combined <- readRDS(here('files_main/homemade', 'ols_logit_pred.RDS')) %>%
-#   append(readRDS(here('files_small/homemade', 'ols_logit_pred.RDS'))) %>%
-#   append(readRDS(here('files_large/homemade', 'ols_logit_pred.RDS')))
-# 
-# grf_pred_combined <- readRDS(here('files_main/homemade', 'grf_pred.RDS')) %>%
-#   append(readRDS(here('files_small/homemade', 'grf_pred.RDS'))) %>%
-#   append(readRDS(here('files_large/homemade', 'grf_pred.RDS')))
-# 
-# superlearner_pred_combined <- readRDS(here('files_main/homemade', 'superlearner_pred.RDS')) %>%
-#   append(readRDS(here('files_small/homemade', 'superlearner_pred.RDS'))) %>%
-#   append(readRDS(here('files_large/homemade', 'superlearner_pred.RDS')))
-# 
-# saveRDS(ols_logit_pred_combined, here('files/homemade', 'ols_logit_pred.RDS'))
-# saveRDS(grf_pred_combined, here('files/homemade', 'grf_pred.RDS'))
-# saveRDS(superlearner_pred_combined, here('files/homemade', 'superlearner_pred.RDS'))
-
-# dml_ols_logit <- read_csv(here('files_large/homemade', 'dml_ols_logit.csv')) 
-# 
-# dml_ols_logit %>%
-#   filter(set == 'main') %>%
-#   write_csv(here('files_main/homemade', 'dml_ols_logit.csv'))
-# 
-# dml_ols_logit %>%
-#   filter(set == 'large') %>%
-#   write_csv(here('files_large/homemade', 'dml_ols_logit.csv'))
-
-## add lalonde ####
-# read_csv(here('files_combined', 'lm_df.csv')) %>%
-#   bind_rows(read_csv(here('files_lalonde', 'lm_df.csv'))) %>%
-#   write_csv(here('files', 'lm_df.csv'))
-# 
-# 
-# read_csv(here('files_combined', 'psm_df.csv')) %>%
-#   bind_rows(read_csv(here('files_lalonde', 'psm_df.csv'))) %>%
-#   write_csv(here('files', 'psm_df.csv'))
-# 
-# read_csv(here('files_combined', 'lin.csv')) %>%
-#   bind_rows(read_csv(here('files_lalonde', 'lin.csv'))) %>%
-#   write_csv(here('files', 'lin.csv'))
-# 
-# read_csv(here('files_combined', 'gcomp.csv')) %>%
-#   bind_rows(read_csv(here('files_lalonde', 'gcomp.csv'))) %>%
-#   write_csv(here('files', 'gcomp.csv'))
-# 
-# read_csv(here('files_combined/homemade', 'aipw.csv')) %>%
-#   bind_rows(read_csv(here('files_lalonde/homemade', 'aipw.csv'))) %>%
-#   write_csv(here('files/homemade', 'aipw.csv'))
-# 
-# read_csv(here('files_combined/homemade', 'aipw_trunc.csv')) %>%
-#   bind_rows(read_csv(here('files_lalonde/homemade', 'aipw_trunc.csv'))) %>%
-#   write_csv(here('files/homemade', 'aipw_trunc.csv'))
-# 
-# read_csv(here('files_combined/homemade', 'tmle.csv')) %>%
-#   bind_rows(read_csv(here('files_lalonde/homemade', 'tmle.csv'))) %>%
-#   write_csv(here('files/homemade', 'tmle.csv'))
-# 
-# read_csv(here('files_combined/homemade', 'dml_ols_logit.csv')) %>%
-#   bind_rows(read_csv(here('files_lalonde/homemade', 'dml_ols_logit.csv'))) %>%
-#   write_csv(here('files/homemade', 'dml_ols_logit.csv'))
-# 
-# read_csv(here('files_combined/homemade', 'dml_grf.csv')) %>%
-#   bind_rows(read_csv(here('files_lalonde/homemade', 'dml_grf.csv'))) %>%
-#   write_csv(here('files/homemade', 'dml_grf.csv'))
-# 
-# read_csv(here('files_combined/homemade', 'dml_superlearner.csv')) %>%
-#   bind_rows(read_csv(here('files_lalonde/homemade', 'dml_superlearner.csv'))) %>% 
-#   write_csv(here('files/homemade', 'dml_superlearner.csv'))
-# 
-# 
-# readRDS(here('files_combined/homemade', 'ols_logit_pred.RDS')) %>%
-#   bind_rows(readRDS(here('files_lalonde/homemade', 'ols_logit_pred.RDS'))) %>%
-#   saveRDS(here('files/homemade', 'ols_logit_pred.RDS'))
-# 
-# readRDS(here('files_combined/homemade', 'grf_pred.RDS')) %>%
-#   bind_rows(readRDS(here('files_lalonde/homemade', 'grf_pred.RDS'))) %>%
-#   saveRDS(here('files/homemade', 'grf_pred.RDS'))
-# 
-# readRDS(here('files_combined/homemade', 'superlearner_pred.RDS')) %>%
-#   bind_rows(readRDS(here('files_lalonde/homemade', 'superlearner_pred.RDS'))) %>%
-#   saveRDS(here('files/homemade', 'superlearner_pred.RDS'))
-
-# dml_ols_logit_df <- read_csv(here('files_main/homemade', 'dml_ols_logit.csv')) %>%
-#   mutate(dataset = 1:nrow(.)) %>%
-#   bind_rows(read_csv(here('files_small/homemade', 'dml_ols_logit.csv')) %>% 
-#               mutate(set = 'small',
-#                      dorie_dataset = 7,
-#                      dataset = row_number())) %>%
-#   bind_rows(read_csv(here('files_large/homemade', 'dml_ols_logit.csv')) %>% 
-#               mutate(set = 'large',
-#                      dorie_dataset = 7,
-#                      dataset = row_number())) %>%
-#   left_join(index_df) 
-# 
-# write_csv(dml_ols_logit_df, here('files/homemade', 'dml_ols_logit.csv'))
-# 
-# dml_grf_df <- read_csv(here('files_main/homemade', 'dml_grf.csv')) %>%
-#   mutate(dataset = 1:nrow(.)) %>%
-#   bind_rows(read_csv(here('files_small/homemade', 'dml_grf.csv')) %>% 
-#               mutate(set = 'small',
-#                      dorie_dataset = 7,
-#                      dataset = row_number())) %>%
-#   bind_rows(read_csv(here('files_large/homemade', 'dml_grf.csv')) %>% 
-#               mutate(set = 'large',
-#                      dorie_dataset = 7,
-#                      dataset = row_number())) %>%
-#   select(-dorie_dataset) %>%
-#   left_join(index_df)
-# 
-# write_csv(dml_grf_df, here('files/homemade', 'dml_grf.csv'))
-# 
-# 
-# dml_superlearner_df <- read_csv(here('files_main/homemade', 'dml_superlearner.csv')) %>%
-#   mutate(dataset = 1:nrow(.)) %>%
-#   bind_rows(read_csv(here('files_small/homemade', 'dml_superlearner.csv')) %>% 
-#               mutate(set = 'small',
-#                      dorie_dataset = 7,
-#                      dataset = row_number())) %>%
-#   bind_rows(read_csv(here('files_large/homemade', 'dml_superlearner.csv')) %>% 
-#               mutate(set = 'large',
-#                      dorie_dataset = 7,
-#                      dataset = row_number())) %>%
-#   select(-dorie_dataset) %>%
-#   left_join(index_df)
-# 
-# write_csv(dml_superlearner_df, here('files/homemade', 'dml_superlearner.csv'))
-
-# ols_logit_pred_combined <- readRDS(here('files_main/homemade', 'ols_logit_pred.RDS')) %>%
-#   append(readRDS(here('files_small/homemade', 'ols_logit_pred.RDS'))) %>%
-#   append(readRDS(here('files_large/homemade', 'ols_logit_pred.RDS')))
-# 
-# grf_pred_combined <- readRDS(here('files_main/homemade', 'grf_pred.RDS')) %>%
-#   append(readRDS(here('files_small/homemade', 'grf_pred.RDS'))) %>%
-#   append(readRDS(here('files_large/homemade', 'grf_pred.RDS')))
-# 
-# superlearner_pred_combined <- readRDS(here('files_main/homemade', 'superlearner_pred.RDS')) %>%
-#   append(readRDS(here('files_small/homemade', 'superlearner_pred.RDS'))) %>%
-#   append(readRDS(here('files_large/homemade', 'superlearner_pred.RDS')))
-# 
-# saveRDS(ols_logit_pred_combined, here('files/homemade', 'ols_logit_pred.RDS'))
-# saveRDS(grf_pred_combined, here('files/homemade', 'grf_pred.RDS'))
-# saveRDS(superlearner_pred_combined, here('files/homemade', 'superlearner_pred.RDS'))
-
-# dml_ols_logit <- read_csv(here('files_large/homemade', 'dml_ols_logit.csv')) 
-# 
-# dml_ols_logit %>%
-#   filter(set == 'main') %>%
-#   write_csv(here('files_main/homemade', 'dml_ols_logit.csv'))
-# 
-# dml_ols_logit %>%
-#   filter(set == 'large') %>%
-#   write_csv(here('files_large/homemade', 'dml_ols_logit.csv'))
-
-```
-
-```{r sim-homemade, eval = F}
-sim_homemade <- function(n, m = NULL){
-  if(is.null(m)){
-    m <- round(n/100)
-  }
-
-  dat <- replicate(m, rnorm(n, 0, 5)) %>% 
-    as.data.frame() 
-  dat_original <- dat
-
-  # first make treatment indicator
-  dat <- data.frame(1, dat)
-  coefs <- rnorm(m+1, 0, 2)
-  d <- round(1/(1+exp(-as.matrix(dat) %*% as.matrix(coefs))))
-
-  dat <- data.frame(dat, d)
-
-  # Set treatment effect to 2
-  coefs <- c(rnorm(m+1, 0, 2), 2)
-  y <- as.matrix(dat) %*% as.matrix(coefs) + rnorm(1)
-
-  dat <- data.frame(dat, y)
-
-  dat_new <- dat_original
-
-  transformers <- rnorm(m, 0, 2)
-
-  for(i in 1:m){
-    dat_new[,i] <- dat_new[,i] * transformers[i]
-  }
-
-  # m/4 squared terms
-  dat_new <- dat_new %>% 
-    mutate(across(sample(1:m, m/4, replace = F), function(x) x^2))
-
-  # m/4 exponentiated 
-  dat_new <- dat_new %>% 
-    mutate(across(sample(1:m, m/4, replace = F), function(x) exp(x)))
-
-  # m/4 sin 
-  dat_new <- dat_new %>% 
-    mutate(across(sample(1:m, m/4, replace = F), function(x) sin(x)))
-
-  # m/2 2-way interactions
-  for(i in 1:round(m/2)){
-    index <- sample(1:m, 2, replace = F)
-    dat_new[, index[1]] <- dat_new[,index[1]] * dat_new[,index[2]]
-  }
-
-  # m/4 3-way interactions
-  for(i in 1:round(m/4)){
-    index <- sample(1:m, 3, replace = F)
-    dat_new[, index[1]] <- dat_new[,index[1]] * dat_new[,index[2]] * dat_new[,index[3]]
-  }
-
-  dat_final <- data.frame(dat_new, d = dat[,'d'], y = dat[,'y'])
-  return(dat_final)
-}
-
-# 500, 1000, 5000, 10k, 50k, 100k
-# Set m = 1% of n
-# 50 of each 
-# then set n = 5000 and m = 10, 50, 200, 1000
-set.seed(185)
-sim_homemade_list <- list()
-for(n in c(500, 1000, 5000, 1e3, 5e3, 1e5)){
-  print(paste0('n = ', n))
-  for(i in 1:50){
-    print(i)
-    sim_homemade_list[[paste0(n, i)]] <- sim_homemade(n) %>%
-      mutate(n = n, m  = n/100, dataset = i, simulation = 'n')
-  }
-}
-for(m in c(10, 50, 200, 500, 1000)){
-  print(paste0('m = ', m))
-  for(i in 1:50){
-    print(i)
-    sim_homemade_list[[paste0(n, i)]] <- sim_homemade(n = n, m = m) %>%
-      mutate(n = n, m  = m, dataset = i, simulation = 'm')
-  }
-}
-
-saveRDS(sim_homemade_list, here('files', 'sim_homemade.RDS'))
-
-```
-
-```{r github-datageneration, eval = F}
-# from https://github.com/QuantLet/DataGenerationForCausalInference
-
-### This generates the Simulation Data as a dataframe
-# by Daniel Jacob (daniel.jacob@hu-berlin.de)
-
-# Arguments to specify are: 
-# Y = Outcome (dependend variable). Either continuous or binary. 
-# N = Number of observations (real number)
-# k = Number of covariates (real number). At least 10 
-# random_d = treatment assignment: (Either T for random assignment or F for confounding on X)
-# theta = treatment effect: (Either real number for only one theta, or "binary" {0.1,0.3}, "con" for continuous values (0.1,0.3) or "big" for {1,0.4})
-# var = Size of the variance (Noise-level)
-
-#Required Packages
-if(!require("clusterGeneration")) install.packages("clusterGeneration"); library("clusterGeneration")
-if(!require("mvtnorm")) install.packages("mvtnorm"); library("mvtnorm")
-
-datagen <- function(N,y,k,random_d,theta,var) {
-
-  N = N
-  k = k
-  b = 1 / (1:k)
-  # = Generate covariance matrix of z = #
-  sigma <- genPositiveDefMat(k, "unifcorrmat")$Sigma
-  sigma <- cov2cor(sigma)
-
-  z <- rmvnorm(N, sigma = sigma) # = Generate z = #
-
-  ### Options for D (m_(X))
-  if (random_d == T) {
-    d <- rep(c(0, 1), length.out = N)
-  } else {
-    d_prop <- pnorm(z %*% b) # D is dependent on Za
-    d <- as.numeric(rbinom(N, prob = d_prop, size = 1))
-  }
-
-  ### Options for theta
-  if (theta == "con") {
-    theta_s <- as.vector(sin(z %*% b) ^ 2)
-    theta <-
-      (theta_s - min(theta_s)) * (0.3 - 0.1) / (max(theta_s) - min(theta_s)) +
-      0.1
-  } else if (theta == "binary") {
-    theta_low <-
-      rbinom(N, pnorm((z[, 6] * (z[, 1] %*% t(
-        z[, 5]
-      )) * z[, 2]) ^ 2), size = 1)
-    theta <-
-      ifelse(theta_low == 1, 0.3, 0.1)
-  } else if (theta == "big") {
-    theta_big <-
-      rbinom(N, pnorm((z[, 6] * (z[, 1] %*% t(
-        z[, 5]
-      )) * z[, 2]) ^ 2), size = 1)
-    theta <- ifelse(theta_big == 1, 1, 0.4)
-  }  else {
-    theta == theta
-  }
-
-  g <- as.vector(cos(z %*% b) ^ 2)
-
-  if(y=="binary") {
-    y1 <- theta * d + g 
-    y1.1 <- rbinom(N,prob=pnorm(scale(y1)),size=1)
-    y <- y1.1
-  } else {y <- theta * d + g + rnorm(N,0,var)}
-
-  data <- as.data.frame(y)
-  data <- cbind(data, theta, d, z)
-  colnames(data) <- c("y", "theta", "d", c(paste0("V", 1:k)))
-
-  return(data)
-}
-
-### Example
-dataset <- datagen(y="binary",N = 2000, k = 20, random_d = F, theta = "binary", var = 1)
-summary(dataset)
-str(dataset)
-
-glm(y ~ ., data = dataset, family = binomial(link = 'logit')) %>%
-  summary()
-```
-
-```{r trash, eval = F}
-dat_transform <- function(dat){
-  # first make treatment indicator
-  coefs <- runif(ncol(dat), -1, 1)
-
-  # m/4 squared terms
-  dat <- dat %>% 
-    mutate(across(sample(1:m, m/4, replace = F), function(x) x^2))
-
-  # m/4 exponentiated 
-  dat <- dat %>% 
-    mutate(across(sample(1:ncol(dat), m/4, replace = F), function(x) exp(x)))
-
-  # m/4 sin 
-  dat <- dat %>% 
-    mutate(across(sample(1:ncol(dat), m/4, replace = F), function(x) sin(x)))
-
-  # m/2 2-way interactions
-  dat <- bind_cols(dat,
-    replicate(m/2, {
-      index <- sample(1:m, 2, replace = F)
-      dat[,index[1]] * dat[,index[2]]
-      }, simplify = T))
-
-  # m/4 3-way interactions
-  dat <- bind_cols(dat,
-    replicate(m/4, {
-      index <- sample(1:m, 3, replace = F)
-      dat[,index[1]] * dat[,index[2]] * dat[,index[3]]
-      }, simplify = T))
-
-  coefs <- runif(ncol(dat), -1, 1)
-
-  y <- as.matrix(dat) %*% as.matrix(coefs)
-
-  return(y)
-}
-
-sim_homemade <- function(m, n){
-  m <- m-2
-  dat <- replicate(m, rnorm(n, 0, 5)) %>%
-    cbind(replicate(m/4, rbinom(n, 1, .5))) %>%
-    as.data.frame()
-  dat_original <- dat
-
-  # first make treatment indicator
-  dat <- data.frame(1, dat)
-  coefs <- rnorm(ncol(dat), 0, 2)
-  d <- round(1/(1+exp(-as.matrix(dat) %*% as.matrix(coefs))))
-
-  dat <- data.frame(dat, d)
-
-  # Set treatment effect to 2
-  coefs <- c(rnorm(m+1, 0, 2), 2)
-  y <- as.matrix(dat) %*% as.matrix(coefs) + rnorm(1)
-
-  dat <- data.frame(dat, y)
-
-  dat_new <- dat_original
-
-  transformers <- rnorm(m, 0, 2)
-
-  for(i in 1:m){
-    dat_new[,i] <- dat_new[,i] * transformers[i]
-  }
-
-  # m/4 squared terms
-  dat_new <- dat_new %>% 
-    mutate(across(sample(1:m, m/4, replace = F), function(x) x^2))
-
-  # m/4 exponentiated 
-  dat_new <- dat_new %>% 
-    mutate(across(sample(1:ncol(m), m/4, replace = F), function(x) exp(x)))
-
-  # m/4 sin 
-  dat_new <- dat_new %>% 
-    mutate(across(sample(1:ncol(m), m/4, replace = F), function(x) sin(x)))
-
-  # m/2 2-way interactions
-  for(i in 1:round(m/2)){
-    index <- sample(1:m, 2, replace = F)
-    dat_new[, index[1]] <- dat_new[,index[1]] * dat_new[,index[2]]
-  }
-
-  # m/4 3-way interactions
-  for(i in 1:round(m/4)){
-    index <- sample(1:m, 3, replace = F)
-    dat_new[, index[1]] <- dat_new[,index[1]] * dat_new[,index[2]] * dat_new[,index[3]]
-  }
-
-  dat_final <- data.frame(dat_new, d = dat[,'d'], y = dat[,'y'])
-  return(dat_final)
-}
-
-```
-
 ```{r functions}
@@
   pi_pred <- predict(pi_mod, type = 'response')
+
+  # pi_pred <-case_when(
+  #   pi_pred < .01 ~ .01,
+  #   pi_pred > .99 ~ .99,
+  #   T ~ pi_pred)
 
@@
 
-<!-- # Abstract -->
-
-<!-- This thesis aims to compare different advanced adjustment methods.
-It will compare Imben & Rubins propensity matching, stabilized IPWs, TMLE, double machine learning (Chernozhukov et al 2018), Ratkovic (2021), and BART.
--->
+```{r load-sims, eval = F}
+lalonde_bootstrap <- function(dataset, sample, include_74 = F, iter = 100){
+
+  lalonde_variables <- c('age', 'education', 'black', 'hispanic', 'married', 'nodegree', 're75', 're75_0')
+  if(include_74 == F){
+        dataset <- bind_rows(filter(lalonde_exp, treat == 1), dataset)
+
+      } else {
+        lalonde_variables <- c(lalonde_variables, 're74', 're74_0')
+        dataset <- bind_rows(filter(lalonde_exp_74, treat == 1), dataset)
+      }
+
+  bootstrap_list <- list()
+
+  for(i in 1:iter){
+    dataset_bootstrap <- sample_n(dataset, nrow(dataset), replace = T)
+
+    bootstrap_list[[i]] <- list(y = dataset_bootstrap$re78,
+                  z = ifelse(dataset_bootstrap$treat == 1, 'trt', 'ctl'),
+                  x = dataset_bootstrap[,lalonde_variables],
+                  y.1 = NA, y.0 = NA,
+                  dataset = i,
+                  set = sample,
+                  size = nrow(dataset_bootstrap))
+  }
+
+  return(bootstrap_list)
+}
+
+lalonde_setup <- function(dataset, sample, include_74 = F){
+
+  lalonde_variables <- c('age', 'education', 'black', 'hispanic', 'married', 'nodegree', 're75', 're75_0')
+  if(include_74 == F){
+        dataset <- bind_rows(filter(lalonde_exp, treat == 1), dataset)
+
+      } else {
+        lalonde_variables <- c(lalonde_variables, 're74', 're74_0')
+        dataset <- bind_rows(filter(lalonde_exp_74, treat == 1), dataset)
+      }
+
+    list(y = dataset$re78,
+                  z = ifelse(dataset$treat == 1, 'trt', 'ctl'),
+                  x = dataset[,lalonde_variables],
+                  y.1 = NA, y.0 = NA,
+                  dataset = i,
+                  set = sample,
+                  size = nrow(dataset)) %>%
+      return()
+}
+
+set.seed(1859)
+sims_lalonde <- c(
+  lalonde_bootstrap(filter(lalonde_exp, treat == 0), sample = 'lalonde experimental original'),
+  lalonde_bootstrap(lalonde_psid1_controls, 'lalonde PSID-1 original'),
+  lalonde_bootstrap(lalonde_psid3_controls, 'lalonde PSID-3 original'),
+  lalonde_bootstrap(lalonde_cps1_controls, 'lalonde CPS-1 original'),
+  lalonde_bootstrap(lalonde_cps1_controls, 'lalonde CPS-3 original'),
+  lalonde_bootstrap(filter(lalonde_exp_74, treat == 0), sample = 'lalonde experimental 74', include_74 = T),
+  lalonde_bootstrap(lalonde_psid1_controls, 'lalonde PSID-1 74', include_74 = T),
+  lalonde_bootstrap(lalonde_psid3_controls, 'lalonde PSID-3 74', include_74 = T),
+  lalonde_bootstrap(lalonde_cps1_controls, 'lalonde CPS-1 74', include_74 = T),
+  lalonde_bootstrap(lalonde_cps1_controls, 'lalonde CPS-3 74', include_74 = T))
+
+# sims <- readRDS(here('files', 'sims.RDS'))
+
+sims_main <- readRDS(here('files_main', 'sims.RDS'))
+sims_large <- readRDS(here('files_large', 'sims_large.RDS'))
+sims_small <- readRDS(here('files_small', 'sims_small.RDS'))
+
+sims <- sims_main %>% append(sims_small) %>% append(sims_large) %>% append(sims_lalonde)
+
+## Full lalonde
+# sims <- list(
+#   lalonde_setup(filter(lalonde_exp, treat == 0), sample = 'lalonde experimental original'),
+#   lalonde_setup(lalonde_psid1_controls, 'lalonde PSID-1 original'),
+#   lalonde_setup(lalonde_psid3_controls, 'lalonde PSID-3 original'),
+#   lalonde_setup(lalonde_cps1_controls, 'lalonde CPS-1 original'),
+#   lalonde_setup(lalonde_cps1_controls, 'lalonde CPS-3 original'),
+#   lalonde_setup(filter(lalonde_exp_74, treat == 0), sample = 'lalonde experimental 74', include_74 = T),
+#   lalonde_setup(lalonde_psid1_controls, 'lalonde PSID-1 74', include_74 = T),
+#   lalonde_setup(lalonde_psid3_controls, 'lalonde PSID-3 74', include_74 = T),
+#   lalonde_setup(lalonde_cps1_controls, 'lalonde CPS-1 74', include_74 = T),
+#   lalonde_setup(lalonde_cps1_controls, 'lalonde CPS-3 74', include_74 = T))
+
+# sims <- sims %>% append(sims_large)
+
+# sims <- readRDS(here('files', 'sims_small.RDS'))
+
+# for(i in 1:length(sims_small)){
+#   # sims_large[[i]]$size <- nrow(sims_large[[i]]$x)
+#   sims_small[[i]]$dataset <- 7
+# }
+# saveRDS(sims_large, here('files_large', 'sims_large.RDS'))
+# 
+# 
+# sims_combined <- sims %>% append(sims_small) %>% append(sims_large)
+# 
+# index_df <- data.frame(dorie_dataset = sapply(sims_combined, function(x) x$dataset),
+#                        set = sapply(sims_combined, function(x) x$set),
+#                        size = sapply(sims_combined, function(x) x$size)) %>%
+#   mutate(dataset = c(1:length(sims), 1:length(sims_small), 1:length(sims_large)))
+# 
+# lm_df <- read_csv(here('files_main', 'lm_df.csv')) %>% 
+#   mutate(set = c(rep('main', 200), rep('linear', 200))) %>%
+#   bind_rows(read_csv(here('files_small', 'lm_df.csv')) %>% mutate(set = 'small')) %>%
+#   bind_rows(read_csv(here('files_large', 'lm_df.csv')) %>% mutate(set = 'large')) %>%
+#   left_join(index_df)
+# 
+# 
+# write_csv(lm_df, here('files', 'lm_df.csv'))
+# 
+# psm_df <- read_csv(here('files_main', 'psm_df.csv')) %>% 
+#   mutate(set = ifelse(dataset <= 200, 'main', 'linear')) %>%
+#   bind_rows(read_csv(here('files_small', 'psm_df.csv')) %>% mutate(set = 'small')) %>%
+#   bind_rows(read_csv(here('files_large', 'psm_df.csv')) %>% mutate(set = 'large')) %>%
+#   left_join(index_df)
+# 
+# write_csv(lm_df, here('files', 'psm_df.csv'))
+# 
+# 
+# aipw_df <- read_csv(here('files_main/homemade', 'aipw.csv')) %>% 
+#   mutate(set = ifelse(dataset <= 200, 'main', 'linear')) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'aipw.csv')) %>% mutate(set = 'small')) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'aipw.csv')) %>% mutate(set = 'large')) %>%
+#   left_join(index_df)
+# 
+# write_csv(aipw_df, here('files/homemade', 'aipw.csv'))
+# 
+# 
+# aipw_trunc_df <- read_csv(here('files_main/homemade', 'aipw_trunc.csv')) %>% 
+#   mutate(set = ifelse(dataset <= 200, 'main', 'linear')) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'aipw_trunc.csv')) %>% mutate(set = 'small')) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'aipw_trunc.csv')) %>% mutate(set = 'large')) %>%
+#   left_join(index_df)
+# 
+# write_csv(aipw_trunc_df, here('files/homemade', 'aipw_trunc.csv'))
+# 
+# tmle_df <- read_csv(here('files_main/homemade', 'tmle.csv')) %>% 
+#   mutate(set = ifelse(dataset <= 200, 'main', 'linear')) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'tmle.csv')) %>% mutate(set = 'small')) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'tmle.csv')) %>% mutate(set = 'large')) %>%
+#   left_join(index_df)
+# 
+# write_csv(tmle_df, here('files/homemade', 'tmle.csv'))
+# 
+# dml_ols_logit_df <- read_csv(here('files_main/homemade', 'dml_ols_logit.csv')) %>%
+#   mutate(dataset = 1:nrow(.)) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'dml_ols_logit.csv')) %>% 
+#               mutate(set = 'small',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'dml_ols_logit.csv')) %>% 
+#               mutate(set = 'large',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   left_join(index_df) 
+# 
+# write_csv(dml_ols_logit_df, here('files/homemade', 'dml_ols_logit.csv'))
+# 
+# dml_grf_df <- read_csv(here('files_main/homemade', 'dml_grf.csv')) %>%
+#   mutate(dataset = 1:nrow(.)) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'dml_grf.csv')) %>% 
+#               mutate(set = 'small',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'dml_grf.csv')) %>% 
+#               mutate(set = 'large',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   select(-dorie_dataset) %>%
+#   left_join(index_df)
+# 
+# write_csv(dml_grf_df, here('files/homemade', 'dml_grf.csv'))
+# 
+# 
+# dml_superlearner_df <- read_csv(here('files_main/homemade', 'dml_superlearner.csv')) %>%
+#   mutate(dataset = 1:nrow(.)) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'dml_superlearner.csv')) %>% 
+#               mutate(set = 'small',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'dml_superlearner.csv')) %>% 
+#               mutate(set = 'large',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   select(-dorie_dataset) %>%
+#   left_join(index_df)
+# 
+# write_csv(dml_superlearner_df, here('files/homemade', 'dml_superlearner.csv'))
+
+# ols_logit_pred_combined <- readRDS(here('files_main/homemade', 'ols_logit_pred.RDS')) %>%
+#   append(readRDS(here('files_small/homemade', 'ols_logit_pred.RDS'))) %>%
+#   append(readRDS(here('files_large/homemade', 'ols_logit_pred.RDS')))
+# 
+# grf_pred_combined <- readRDS(here('files_main/homemade', 'grf_pred.RDS')) %>%
+#   append(readRDS(here('files_small/homemade', 'grf_pred.RDS'))) %>%
+#   append(readRDS(here('files_large/homemade', 'grf_pred.RDS')))
+# 
+# superlearner_pred_combined <- readRDS(here('files_main/homemade', 'superlearner_pred.RDS')) %>%
+#   append(readRDS(here('files_small/homemade', 'superlearner_pred.RDS'))) %>%
+#   append(readRDS(here('files_large/homemade', 'superlearner_pred.RDS')))
+# 
+# saveRDS(ols_logit_pred_combined, here('files/homemade', 'ols_logit_pred.RDS'))
+# saveRDS(grf_pred_combined, here('files/homemade', 'grf_pred.RDS'))
+# saveRDS(superlearner_pred_combined, here('files/homemade', 'superlearner_pred.RDS'))
+
+# dml_ols_logit <- read_csv(here('files_large/homemade', 'dml_ols_logit.csv')) 
+# 
+# dml_ols_logit %>%
+#   filter(set == 'main') %>%
+#   write_csv(here('files_main/homemade', 'dml_ols_logit.csv'))
+# 
+# dml_ols_logit %>%
+#   filter(set == 'large') %>%
+#   write_csv(here('files_large/homemade', 'dml_ols_logit.csv'))
+
+## add lalonde ####
+# read_csv(here('files_combined', 'lm_df.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde', 'lm_df.csv'))) %>%
+#   write_csv(here('files', 'lm_df.csv'))
+# 
+# 
+# read_csv(here('files_combined', 'psm_df.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde', 'psm_df.csv'))) %>%
+#   write_csv(here('files', 'psm_df.csv'))
+# 
+# read_csv(here('files_combined', 'lin.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde', 'lin.csv'))) %>%
+#   write_csv(here('files', 'lin.csv'))
+# 
+# read_csv(here('files_combined', 'gcomp.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde', 'gcomp.csv'))) %>%
+#   write_csv(here('files', 'gcomp.csv'))
+# 
+# read_csv(here('files_combined/homemade', 'aipw.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde/homemade', 'aipw.csv'))) %>%
+#   write_csv(here('files/homemade', 'aipw.csv'))
+# 
+# read_csv(here('files_combined/homemade', 'aipw_trunc.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde/homemade', 'aipw_trunc.csv'))) %>%
+#   write_csv(here('files/homemade', 'aipw_trunc.csv'))
+# 
+# read_csv(here('files_combined/homemade', 'tmle.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde/homemade', 'tmle.csv'))) %>%
+#   write_csv(here('files/homemade', 'tmle.csv'))
+# 
+# read_csv(here('files_combined/homemade', 'dml_ols_logit.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde/homemade', 'dml_ols_logit.csv'))) %>%
+#   write_csv(here('files/homemade', 'dml_ols_logit.csv'))
+# 
+# read_csv(here('files_combined/homemade', 'dml_grf.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde/homemade', 'dml_grf.csv'))) %>%
+#   write_csv(here('files/homemade', 'dml_grf.csv'))
+# 
+# read_csv(here('files_combined/homemade', 'dml_superlearner.csv')) %>%
+#   bind_rows(read_csv(here('files_lalonde/homemade', 'dml_superlearner.csv'))) %>%
+#   write_csv(here('files/homemade', 'dml_superlearner.csv'))
+# 
+# 
+# readRDS(here('files_combined/homemade', 'ols_logit_pred.RDS')) %>%
+#   append(readRDS(here('files_lalonde/homemade', 'ols_logit_pred.RDS'))) %>%
+#   saveRDS(here('files/homemade', 'ols_logit_pred.RDS'))
+# 
+# readRDS(here('files_combined/homemade', 'grf_pred.RDS')) %>%
+#   append(readRDS(here('files_lalonde/homemade', 'grf_pred.RDS'))) %>%
+#   saveRDS(here('files/homemade', 'grf_pred.RDS'))
+# 
+# readRDS(here('files_combined/homemade', 'superlearner_pred.RDS')) %>%
+#   append(readRDS(here('files_lalonde/homemade', 'superlearner_pred.RDS'))) %>%
+#   saveRDS(here('files/homemade', 'superlearner_pred.RDS'))
+
+# dml_ols_logit_df <- read_csv(here('files_main/homemade', 'dml_ols_logit.csv')) %>%
+#   mutate(dataset = 1:nrow(.)) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'dml_ols_logit.csv')) %>% 
+#               mutate(set = 'small',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'dml_ols_logit.csv')) %>% 
+#               mutate(set = 'large',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   left_join(index_df) 
+# 
+# write_csv(dml_ols_logit_df, here('files/homemade', 'dml_ols_logit.csv'))
+# 
+# dml_grf_df <- read_csv(here('files_main/homemade', 'dml_grf.csv')) %>%
+#   mutate(dataset = 1:nrow(.)) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'dml_grf.csv')) %>% 
+#               mutate(set = 'small',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'dml_grf.csv')) %>% 
+#               mutate(set = 'large',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   select(-dorie_dataset) %>%
+#   left_join(index_df)
+# 
+# write_csv(dml_grf_df, here('files/homemade', 'dml_grf.csv'))
+# 
+# 
+# dml_superlearner_df <- read_csv(here('files_main/homemade', 'dml_superlearner.csv')) %>%
+#   mutate(dataset = 1:nrow(.)) %>%
+#   bind_rows(read_csv(here('files_small/homemade', 'dml_superlearner.csv')) %>% 
+#               mutate(set = 'small',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   bind_rows(read_csv(here('files_large/homemade', 'dml_superlearner.csv')) %>% 
+#               mutate(set = 'large',
+#                      dorie_dataset = 7,
+#                      dataset = row_number())) %>%
+#   select(-dorie_dataset) %>%
+#   left_join(index_df)
+# 
+# write_csv(dml_superlearner_df, here('files/homemade', 'dml_superlearner.csv'))
+
+# ols_logit_pred_combined <- readRDS(here('files_main/homemade', 'ols_logit_pred.RDS')) %>%
+#   append(readRDS(here('files_small/homemade', 'ols_logit_pred.RDS'))) %>%
+#   append(readRDS(here('files_large/homemade', 'ols_logit_pred.RDS')))
+# 
+# grf_pred_combined <- readRDS(here('files_main/homemade', 'grf_pred.RDS')) %>%
+#   append(readRDS(here('files_small/homemade', 'grf_pred.RDS'))) %>%
+#   append(readRDS(here('files_large/homemade', 'grf_pred.RDS')))
+# 
+# superlearner_pred_combined <- readRDS(here('files_main/homemade', 'superlearner_pred.RDS')) %>%
+#   append(readRDS(here('files_small/homemade', 'superlearner_pred.RDS'))) %>%
+#   append(readRDS(here('files_large/homemade', 'superlearner_pred.RDS')))
+# 
+# saveRDS(ols_logit_pred_combined, here('files/homemade', 'ols_logit_pred.RDS'))
+# saveRDS(grf_pred_combined, here('files/homemade', 'grf_pred.RDS'))
+# saveRDS(superlearner_pred_combined, here('files/homemade', 'superlearner_pred.RDS'))
+
+# dml_ols_logit <- read_csv(here('files_large/homemade', 'dml_ols_logit.csv')) 
+# 
+# dml_ols_logit %>%
+#   filter(set == 'main') %>%
+#   write_csv(here('files_main/homemade', 'dml_ols_logit.csv'))
+# 
+# dml_ols_logit %>%
+#   filter(set == 'large') %>%
+#   write_csv(here('files_large/homemade', 'dml_ols_logit.csv'))
+
+```
 
@@
 
-Statistical methods for flexible covariate adjustment in causal inference have proliferated in recent years.
-These methods have a number of strengths over traditional regression methods: They make few functional form assumptions, can accommodate large numbers of covariates, and produce easily interpretable treatment effect estimates.
-Many of these methods also have a "double robust" property: They estimate one model for the treatment exposure and another for the outcome, and as long as at least one is correctly specified, then the treatment effect will be estimated consistently.
-Despite their apparent advantages, these methods remain underutilized by social scientists.
+In causal inference, misspecification of underlying models can bias estimates of treatment effects [@hernan_2020_causal; @morgan_2015_counterfactuals].
+There have been two important developments that attempt to overcome this.
+First, methodologists have developed machine learning methods that allow greater flexibility in estimation, adjusting for covariates in data-driven, complex ways [@balzer_2021_invited; @brand_2023_recent].
+The second development is double robust methods [@bang_2005_doubly; @kang_2007_demystifying], which estimate two models: one for treatment exposure and another for the outcome.
+These models are robust to misspecification of either one of these models.
+
+A number methods unifying these two developments have proliferated.
+These double robust methods for flexible covariate adjustment use machine learning methods to adapatively model the data generating processes.
+These models purportedly overcome the shortcomings of both traditional statistical methods and machine learning methods.
+Common statistical methods -- such as OLS regression and matching on propensity scores estimated from logistic regression -- have rigid functional form assumptions and fail to calculate stable estimates when the number of covariates is large relative to the number of observations.
+Machine learning methods, on the other hand, are often difficult to interpret.
+They can also suffer from overfitting, where the flexibility of the model becomes a weakness and predictions out-of-sample are poor, yet efforts to correct for overfitting can introduce regularization bias [@hastie_2009_elements].
+Double robust methods with machine learning dispose of the constricting functional form assumptions of common statistical methods, and they correct for the regularization bias of flexible machine learning methods.
+They can also accommodate large numbers of covariates and produce easily interpretable treatment effect estimates.
+Despite their apparent advantages, these methods remain rarely utilized by social scientists.
 Part of the barrier has been lack of familiarity with these methods.
 It has also been unclear how these methods compare, or whether such methods actually perform better than traditional methods in finite samples.
-<!-- And when researchers want to use an existing R package for these methods, the array of possible estimation methods and other options can be dizzying.   -->
 
@@
 First, it is a guide to some of the latest methods in double robust, flexible covariate adjustment for causal inference, explaining the methods to a social scientist audience.
-Second, it compares these methods to more traditional statistical methods using both simulations [@dorie_2019_automated] and the National Support for Work Demonstration (NSW) originally analyzed by @lalonde_1986_evaluating.
-
-Methods covered include Augmented Inverse Probability Weighting [AIPW, @glynn_2010_introduction], Targeted Maximum Likelihood Estimation [TMLE, @vanderlaan_2006_targeted], and Double or Debiased Machine Learning [DML, @chernozhukov_2018_double].
-This paper reviews the theory behind these methods as well as simple R implementations of them on simulations and real data.
-These methods are compared to two methods commonly used by social scientists: ordinary least squares (OLS) regression, and matching on propensity scores estimated from logistic regression (PSM).
+Methods covered include Augmented Inverse Probability Weighting (AIPW), Targeted Maximum Likelihood Estimation (TMLE), and Double or Debiased Machine Learning (DML).
+This paper reviews the theory behind these methods as well as simple R implementations.
+
+Second, this paper evaluates these methods.
+They are tested on simulations from @dorie_2019_automated, which cover a range of data-generating processes where ignorability holds -- i.e., there are no unmeasured confounders.
+They are then used to estimate experimental and observational effects from real-world data, the National Support for Work Demonstration (NSW) originally analyzed by @lalonde_1986_evaluating.
+In these evaluations, double robust methods are compared to "single robust" single robust methods.
+These include traditional or simpler statistical methods commonly used by social scientists: ordinary least squares (OLS) regression, matching on propensity scores estimated from logistic regression (PSM), and inverse probability weighting (IPW).
+They are also compared to two more flexible methods that may overcome the misspecification issues that double robust methods aim to overcome: G-computation and the Lin estimator [@lin_2013_agnostic].
+
+Results from simulations where ignorability holds show that some double robust methods outperform traditional statistical methods, but only slightly.
+AIPW and TMLE perform the best, at least when used in conjunction with flexible machine learning algorithms, while DML does slightly worse than traditional methods.
+G-computation with flexible machine learning performs as well as the lowest-error double robust methods.
+Despite their lower average error, the computation times of these flexible methods are high.
+With its still relatively low error and much faster computation time, OLS remains a sensible choice as an estimator, and the Lin estimator -- which is as quick as standard OLS regression -- performs only slightly worse than the best double robust methods.
+
+Results from the NSW study highlight the importance of ignorability.
+When observational samples are not comparable to the experimental sample, or when important covariates are not included, all methods -- double robust or traditional -- fail to recover experimental estimates.
+When appropriate covariates are included, most methods perform well.
+<!-- Exceptions include IPW, DML, and the Lin estimator (surprising given the simulation results), whose estimates tend to be less stable across samples.   -->
 
@@
 
-Although previous work has compared different methods for covariate adjustment, there has not yet been a thorough evaluation and comparison of the recent and popular double robust methods of AIPW, TMLE, and DML.
-@austin_2014_comparison compares methods for matching on the propensity score.
-@dorie_2019_automated report the results for the Atlantic Causal Inference Conference 2016 competition.
-Some of the methods used incorporate TMLE but not AIPW or DML.
-@cousineau_2022_estimating evaluates the performance of optimization-baseds methods for causal inference, but these do not include the double robust methods covered in the current paper.
-@kang_2007_demystifying provide an overview and evaluation of double robust methods in the context of missing data.
-The authors consider AIPW but not TMLE or DML.
-@chatton_2020_gcomputation compare four methods: G-computation, IPW, full matching, and TMLE.
-These authors only consider one double robust method, and their focus is on omitted variable bias rather than determining which method is the most useful.
-@knaus_2022_double reviews double robust methods in an econometrics setting but does not compare them to traditional statistical methods for covaraite adjustment.
+Although previous work has compared different methods for covariate adjustment, there has not yet been a thorough evaluation and comparison of the recent and popular double robust methods of AIPW, TMLE, and DML for a social scientist audience.
+
+Although some introductions to double robust methods exist, they do not discuss them in the context of covariate adjustment for causal inference, or their treatment is overly technical for a social scientist audience.
+For example, @kang_2007_demystifying provide an an excellent overview and evaluation of double robust methods, but in the context of missing data, and the authors consider AIPW but not TMLE or DML.
+@bang_2005_doubly introduce double robust models for both causal inference and missing data, but their treatment is rather technical, and they only discuss AIPW.
+
+Evaluations of double robust methods have focused on only one double robust method and compare to few traditional statistical methods.
+@dorie_2019_automated compare estimations from a number of different flexible methods, but these do not include AIPW or DML.
+@chatton_2020_gcomputation compare four methods -- G-computation, IPW, full matching, and TMLE -- but authors only consider one double robust method, and their focus is on omitted variable bias rather than determining which method is the most useful.
+@cousineau_2022_estimating evaluates the performance of optimization-based methods for causal inference, but these do not include the double robust methods covered in the current paper.
+@knaus_2022_double reviews double robust methods in an econometrics setting but does not compare them to traditional statistical methods for covariate adjustment.
+
+An evaluation of multiple double robust methods that compares them to traditional statistical methods as well as flexible "single robust" methods is needed to understand just how practically useful these methods are for a social science audience.
+This paper endeavors to do this and to provide a gentle introduction to these methods.
 
@@
 According to @bang_2005_doubly, double robust methods have their origins in missing data models.
-@robins_1994_estimation and @rotnitzky_1998_semiparametric developed augmented orthogonal inverse probability-weighted (AIPW) estimators in missing data models, and @scharfstein_1999_adjusting showed that AIPW was double robust and extended to causal inference (since causal inference is fundamentally a missing data problem).
+@robins_1994_estimation and @rotnitzky_1998_semiparametric developed augmented orthogonal inverse probability-weighted (AIPW) estimators in missing data models.
+Drawing on the fact that causal inference is fundamentally a missing data problem, @scharfstein_1999_adjusting showed that AIPW was double robust and extended to causal inference.
 
@@
 Arguably, double robust methods go back even further than this.
-The form of double robust methods is similar to residual-on-residual regression, which dates back to @frisch_1933_partial famous FWL theorem:
-
+The form of double robust methods is similar to residual-on-residual regression, which dates back to the Frisch-Waugh-Lowell (FWL) theorem [@frisch_1933_partial; @lovell_1963_seasonal]:
 $$\beta_D = \frac{\text{Cov}(\tilde Y_i, \tilde D_i)}{\text{Var}(\tilde D_i)}$$
-
 where $\tilde D_i$ is the residual part of $D_i$ after regressing it on $X_i$, and $\tilde Y_i$ is the residual part of $Y_i$ after regressing it on $X_i$.
 This formulation writes the regression coefficient as composed of an outcome model ($\tilde Y_i$) and exposure model ($\tilde D_i$), the two models used in double robust estimators.
+Of the methods considered in this paper, double machine learning (DML) makes this connection most explicit by using residual-on-residual regression as part of its estimation strategy.
 
 There are also links between double robust methods and matching with regression adjustment.
-This work goes back to at least @rubin_1973_use, who suggested that regression adjustment in matched data produces less biased estimates that either matching (exposure adjustment) or regression (outcome adjustment) do by themselves.
+This work goes back at least as far as @rubin_1973_use, who suggested that regression adjustment in matched data produces less biased estimates that either matching (exposure adjustment) or regression (outcome adjustment) do by themselves.
 
 Today, double robust methods abound [e.g.
-@ratkovic_2023_relaxing; @sloczynski_2018_general; @arkhangelsky_2021_doublerobust; @dukes_2022_doubly; @kennedy_2023_semiparametric].
-This paper focuses on three of the more popular or fundamental methods.
+@arkhangelsky_2021_doublerobust; @ratkovic_2023_relaxing; @sloczynski_2018_general; @dukes_2022_doubly; @kennedy_2023_semiparametric].
+Although double robust methods exist for instrumental variables [@okui_2012_doubly; @wang_2018_bounded], difference-in-differences [@santanna_2020_doubly], longitudinal data [@yu_2006_double; @tran_2019_double], and other causal applications, this paper focuses on three of the most popular and foundational methods for covariate adjustment in a cross-sectional setting.
 
 ## Aims of Double Robust Methods
-Double robust methods for covariate adjustment aim to overcome what many consider to be the downsides of both traditional statistical methods and flexible machine learning methods.
+Double robust methods for covariate adjustment aim to overcome what many consider to be the shortcomings of both traditional statistical methods and flexible machine learning methods.
 Statistical methods that are popular with social scientists -- such as OLS regression and matching on propensity scores from logistic regression -- have two main weaknesses that double robust methods address.
@@
 
-Double robust methods for covariate adjustment are also motivated by the idea that many older methods ignore information present in the data.
+Double robust methods attempt to overcome the downsides of both traditional and machine learning methods by incorporating flexible models into a framework that avoids overfitting and provides easily interpretable estimates.
+These methods are also motivated by the idea that many older methods ignore information present in the data.
 Methods tend to model either the outcome -- as in OLS regression and G-computation -- or only the treatment assignment -- as in propensity score matching or inverse probability weighting.
@@
 
-Double robust methods estimate two models:
-
-- an *outcome model*
-
-$$\mu_d(X_i) = E(Y_i \mid D_i = d, X_i)$$
-
-- and an *exposure model* (or treatment model or propensity score):
-
-$$\pi(X_i) = E(D_i \mid X_i)$$
-
-where $\mu_d(\cdot)$ is the model of control or treatment $D_i = d=\{0, 1\}$, $X_i$ is a vector of covariates for unit $i = 1, \ldots, N$ for treatment (1) and control (0), $Y_i$ is the outcome, and $\pi(\cdot)$ is the exposure model.
+Double robust methods estimate two models: an *outcome model*:
+\begin{equation}
+\mu_d(X_i) = E(Y_i \mid D_i = d, X_i)
+(\#eq:outcome)
+\end{equation}
+and an *exposure model* (or treatment or propensity score model):
+\begin{equation}
+\pi(X_i) = E(D_i \mid X_i),
+(\#eq:exposure)
+\end{equation}
+where $\mu_d(\cdot)$ is a model of the outcome, $D_i = d_i \in \{0, 1\}$ is the treatment assignment (where 0 is control and 1 is treated), $X_i$ is a vector of covariates for unit $i = 1, \ldots, N$, $Y_i$ is the outcome, and $\pi(\cdot)$ is a model of the exposure.
 The covariates included in $X_i$ can be different for the two models.
 
-An estimator is called "double robust" if it achieves consistent estimation of the ATE (or whatever estimand the researcher is interested in) as long as *at least one* of these two models is consistently estimated.
+The focus of this paper is on the average treatment effect (ATE), which under the potential outcomes framework [@rubin_1974_estimating] is defined as
+$$\tau = E[Y_i(1) - Y_i(0)]$$
+where $Y_i(1)$ and $Y_i(0)$ are the potential outcomes of $Y_i$ under treatment and control, respectively.
+An estimator is called "double robust" if it achieves consistent estimation of the ATE (or whatever estimand the researcher is interested in) as long as *at least one* of Equations \@ref(eq:outcome) or \@ref(eq:exposure) is consistently estimated.
 This means that the outcome model can be completely misspecified, but as long as the exposure model is correct, our estimation of the ATE will be consistent.
@@
 
+It is important to consider what is meant by a "correct" model [@keil_2018_resolving].
+These estimators are robust from a statistical standpoint, but not necessarily a causal identification one.
+The researcher must know which variables are possible confounders and to include them in the appropriate models, while not including colliders or mediators [@hunermund_2023_double].
+The simulations discussed in this paper assume conditional ignorability; rather than testing what happens when models are missing important covariates, it focuses on accurate specification of the functional form of the treatment and outcome models.
+
 ## Assumptions
 
-Most double robust methods require almost all of the standard assumptions necessary formost methods that depend on selection on observables.
-Although some double robust methods relax one or two of these, the six standard assumptions are:
-
-1. Consistency
-2. Positivity/overlap
-3. One version of treatment
-4. No interference
-5. IID observations
-6. Conditional ignorability: $\{Y_{i0}, Y_{i1}\} \perp \!\!\! \perp D_i \mid X_i$
-
+Most double robust methods require almost all of the standard assumptions necessary for most methods that depend on selection on observables.
+Although some double robust methods relax one or two of these, the methods discussed in this paper rely on six standard assumptions when estimating the ATE.
+
+1. Consistency: $Y_i(d) = Y_i \mid D_i = d$, i.e. under treatment (control), we observe the potential outcome under treatment (control).
+
+2. One version of treatment: All treated units receive the same version of treatment.
+
+3. No interference: $Y_i(D_i, D_j) = Y_i(D_i)$, i.e. the potential outcome for one unit depends only on its own treatment, not the value of other units' treatment.
+
+4.
+Positivity/overlap: $0 < \Pr(D = 1 \mid X=x) < 1$ for all values of $X$, i.e.
+there is non-zero probability of receiving treatment or control for every combination of covariates in the data.
+This means we can find at least one control unit to compare every treated unit to (and vice versa).
+
+5. Independent and identically distributed (IID) observations: In order to make population-level inference, the sample needs to be representative of the population.
+
+6. Conditional ignorability: $\{Y_{i0}, Y_{i1}\} \perp \!\!\! \perp D_i \mid X_i$, i.e. there are no unmeasured confounders.
+
+The first three assumptions are embedded in the potential outcomes notation.
+Assumptions 2 and 3, together, are also called the Stable Unit Treatment Value assumption [SUTVA, @rubin_1980_randomization].
 Special attention should be paid to Assumption 6: double robust methods will not work if we do not measure an important confounder that affects both treatment and exposure.
 But notably, the double robust methods covered in this tutorial make no functional form assumptions.
-These methods are designed to incorporate flexible machine learning algorithms to estimate both the outcome and exposure models, with regularization (often through cross-fitting) to avoid overfitting.
 
@@
 Each of the methods reviewed in this paper can be thought of as a collection of estimation techniques.
-Each involves a model for the outcome and another for the treatment exposure, but the ways these relate and are combined varies from method to method.
-Choice of estimation technique for these two models is left to the discretion of the user; often ensemble learning is recommended, but in practice simpler methods can also work well.
+Each involves a model for the outcome and another for the treatment exposure, but choice of estimation technique for these two models is left to the discretion of the user.
+The ways these estimated models relate and are combined into a final effect estimate vary between double robust methods.
 
@@
 Introductions to AIPW exist in the contexts of political science [@glynn_2010_introduction] and econometrics [@funk_2011_doubly].
-The `AIPW` R package provides a simple implementation of the method.
+The `AIPW` R package provides a simple implementation of the method [@zhong_2021_aipw].
 
@@
 
-Formally, the model can be written as the difference between an estimated outcome for treated units and the estimated outcome for untreated units (see the demonstration below):
+Formally, the model can be written as the difference between an estimated outcome for treated units and an estimated outcome for untreated units (see the demonstration below):
 
 $$\begin{aligned}
-\widehat{ATE}_{AIPW} = &\frac{1}{n} \sum_{i=1}^n \left( \frac{D_i(Y_i - \hat \mu_1 (\mathbf X_i))}{\hat \pi (\mathbf X_i)} + \hat \mu_1(\mathbf X_i) \right) 
+\hat \tau_{AIPW} = &\frac{1}{n} \sum_{i=1}^n \left( \frac{D_i(Y_i - \hat \mu_1 (\mathbf X_i))}{\hat \pi (\mathbf X_i)} + \hat \mu_1(\mathbf X_i) \right) 
 - \frac{1}{n} \sum_{i=1}^n \left( \frac{(1-D_i)(Y_i - \hat \mu_0 (\mathbf X_i))}{1-\hat \pi(\mathbf X_i)} + \hat \mu_0(\mathbf X_i) \right)
@@
 $$\begin{aligned}
-\widehat{ATE}_{AIPW} = & \frac{1}{n} \sum_{i=1}^n \left\{ \left[ \frac{D_i Y_i}{\hat \pi(\mathbf X_i)} - \frac{(1-D_i) Y_i}{ 1- \hat \pi(\mathbf X_i)} \right] - \frac{D_i - \hat \pi (\mathbf X_i)}{\hat \pi (\mathbf X_i)(1 - \hat pi (\mathbf X_i))} [(1- \hat \pi (\mathbf X_i)) \hat \mu_1(\mathbf X_i) + \hat \pi (\mathbf X_i) \hat \mu_0(\mathbf X_i)] \right\}
+\hat \tau_{AIPW} = & \frac{1}{n} \sum_{i=1}^n \left\{ \left[ \frac{D_i Y_i}{\hat \pi(\mathbf X_i)} - \frac{(1-D_i) Y_i}{ 1- \hat \pi(\mathbf X_i)} \right] - \frac{D_i - \hat \pi (\mathbf X_i)}{\hat \pi (\mathbf X_i)(1 - \hat pi (\mathbf X_i))} [(1- \hat \pi (\mathbf X_i)) \hat \mu_1(\mathbf X_i) + \hat \pi (\mathbf X_i) \hat \mu_0(\mathbf X_i)] \right\}.
 \end{aligned}$$
@@
 
-@vanderlaan_2006_targeted first proposed TMLE an extension and improvement of previous double robust methods, using a parametric framework and the efficient influence curve  [@hines_2022_demystifying] to obtain estimates and standard errors.
+Extending and improving previous double robust methods, @vanderlaan_2006_targeted first proposed TMLE using a parametric framework and the efficient influence curve [@hines_2022_demystifying] to obtain estimates and standard errors.
 Mark van der Laan has gone on to collaborate on both a gentle introduction [@gruber_2009_targeted], a textbook [@vanderlaan_2011_targeted], and an R package [@gruber_2012_tmle] for implementing the method.
@@
 It next estimates the exposure model.
-Although any estimation method can be used for these steps, the originators of the method suggest using a "super learner," i.e.
-ensemble learning with cross-validation [@laan_2007_super].
+Although any estimation method can be used for these steps, the originators of the method suggest using a "SuperLearner," i.e.
+ensemble learning with cross-validation [@vanderlaan_2007_super].
 Next, the exposure model is used to calculate a "clever covariate," which is similar to an IPW.
@@
 
-Formally, first generate estimates of $\mu_{d}(\mathbf X_i) = E(Y \mid D=d, \mathbf X_i)$ and $\pi(\mathbf X_i) = P(D=1 \mid \mathbf X_i)$. Then create the variable $H_{di}$ for targeting step:
-$$H_{di} = \frac{I(D_i = 1)}{\hat \pi (\mathbf X_i)} - \frac{I(D_i=0)}{1 - \hat \pi (\mathbf X_i)}$$
-
-Next, calculate the clever covariates for each individual in the data. These quantities are similar to inverse probability weights, with $H_{0i}$ for untreated and $H_{0i}$ for treated units:
+<!-- Then create the variable $H_{di}$ for targeting step: -->
+<!-- $$H_{di} = \frac{I(D_i = 1)}{\hat \pi (\mathbf X_i)} - \frac{I(D_i=0)}{1 - \hat \pi (\mathbf X_i)}.$$ -->
+
+Formally, first generate estimates of $\mu_{d}(\mathbf X_i) = E(Y \mid D=d, \mathbf X_i)$ and $\pi(\mathbf X_i) = P(D=1 \mid \mathbf X_i)$.
+Next, calculate the clever covariates for each individual in the data.
+These quantities are similar to inverse probability weights, with $H_{0i}$ for untreated and $H_{1i}$ for treated units:
 $$\begin{aligned}
-H_{0i}(D=0, \mathbf X_i) &= \frac{1-d_i}{1- \hat \pi (\mathbf X_i)}, &
-H_{1i}(D=1, \mathbf X_i) = \frac{d_i}{\hat \pi (\mathbf X_i)}.
+H_{0i}(D=0, \mathbf X = \mathbf x_i) &= \frac{1-d_i}{1- \hat \pi (\mathbf x_i)}, &
+H_{1i}(D=1, \mathbf X = \mathbf x_i) = \frac{d_i}{\hat \pi (\mathbf x_i)}.
 \end{aligned}$$
@@
 Here we are assuming that $Y$ is a dichotomous variable taking the values of 0 or 1; the method is extended to continuous outcomes simply by normalizing the value of $Y$ to fall between 0 and 1.
-Then generate updated ("targeted") estimates of potential outcomes:
+Then we generate updated ("targeted") estimates of potential outcomes:
 $$\begin{aligned}
-\hat \mu_0^*(\mathbf X_i) &= \text{expit}[\text{logit}(\hat \mu_0(\mathbf X_i)) + \hat \epsilon H_{0i}]\\
-\hat \mu_1^*(\mathbf X_i) &= \text{expit}[\text{logit}(\hat \mu_1(\mathbf X_i)) + \hat \epsilon H_{1i}]
+\hat \mu_0^*(\mathbf x_i) &= \text{expit}[\text{logit}(\hat \mu_0(\mathbf x_i)) + \hat \epsilon H_{0i}]\\
+\hat \mu_1^*(\mathbf x_i) &= \text{expit}[\text{logit}(\hat \mu_1(\mathbf x_i)) + \hat \epsilon H_{1i}]
 \end{aligned}$$
-
-Finally, estimate the parameter of interest -- in this case, the ATE:
-$$\widehat{ATE}_{TMLE} = \frac{1}{n} \sum_{i=1}^n [\hat \mu_1^*(\mathbf X_i) - \hat \mu_0^*(\mathbf X_i)]$$
+where $\text{expit}(\cdot)$ is the inverse logit function.
+
+Finally, we estimate the parameter of interest -- in this case, the ATE:
+$$\hat \tau_{TMLE} = \frac{1}{n} \sum_{i=1}^n [\hat \mu_1^*(\mathbf x_i) - \hat \mu_0^*(\mathbf x_i)]$$
 
 Here is R code to implement TMLE, again with predicted outcome values `mu1_pred` and `mu0_pred` and predicted probability of treatment `pi_pred`.
-Since the outcome is bounded and continuous, it is transformed to fall between 0 and 1 via $\tilde Y_{i} = Y_i - \min(Y)/(\max(Y)-\min(Y)$.
+Since the outcome is bounded and continuous, it is transformed to fall between 0 and 1 via $\tilde Y_{i} = [Y_i - \min(Y)]/[(\max(Y)-\min(Y)]$.
 ```{r tmle-demo, eval = F, echo = T}
@@
 tmle_calc <- function(mu1_pred, mu0_pred, pi_pred, d, y){
-  # Normalize outcome variable
+  # Normalize the outcome variable
   mu1_pred <- normalize(mu1_pred, y)
@@
 a large number of measured confounders.
-Flexible machine learning is appropriate for this task, but such methods suffer from regularization bias.
+Flexible machine learning is appropriate for this task, but such methods suffer from regularization bias, where efforts to control the overfitting of models can bias estimates.
 DML removes this bias in a two-step procedure.
-First, it solves the auxiliary problem of estimating the treatment exposure model $E(D|X) = \pi(X)$.
+First, it solves the auxiliary problem of estimating the treatment exposure model $E(D \mid X) = \pi(X)$.
 It then uses this model to remove bias: Neyman orthogonalization allows the creation of an orthogonalized regressor, essentially partialing out the effect of covariates $X$ from treatment $D$.
@@
 
-More formally, suppose we want to estimate $\delta$ in the following framework:
-$$y_i = \delta d_i + g_0(\mathbf x_i) + u_i,$$
+More formally, suppose we want to estimate $\tau$ in the following framework:
+$$y_i = \tau d_i + g_0(\mathbf x_i) + u_i,$$
 $$d_i = m_0(\mathbf x_i) + v_i.$$
 
-The idea is to estimate $g_0$ and $m_0$ separately, then use residual-on-residual regression to obtain an estimate of $\delta$, which we can designate $\hat \delta$.
-However this leaves a term in the asymptotic distribution of $\hat \delta$ that biases the estimate.
+The idea is to estimate $g_0$ and $m_0$ separately, then use residual-on-residual regression to obtain an estimate of $\tau$, which we can designate $\hat \tau$.
+However this leaves a term in the asymptotic distribution of $\hat \tau$ that biases the estimate.
 To avoid this, DML uses sample splitting [@angrist_1995_splitsample].
@@
 
-1) Estimate treatment model $\hat m_0$ in the equation $d_i = \hat m_0(\mathbf x_i) + \hat v_i, i \in I^c$.  
-2) Estimate the outcome model $\hat g_0$ in the equation $y_i =  \hat g_0(\mathbf x_i) + \hat u_i, i \in I^c$.
+1) Estimate treatment model $\hat m_0$ in the equation $d_i = \hat m_0(\mathbf x_i) + \hat v_i, \forall i \in I^c$.  
+2) Estimate the outcome model $\hat g_0$ in the equation $y_i =  \hat g_0(\mathbf x_i) + \hat u_i, \forall i \in I^c$.
 
@@
 
-Next, we use the estimated models to perform residual-on-residual regression *on the left out set* $I$ to obtain an estimate of $\delta$:
-$$\hat \delta(I^c, I) = \left(\sum_{i \in I} \hat v_i d_i \right)^{-1} 
+Next, we use the estimated models to perform residual-on-residual regression *on the left out set* $I$ to obtain an estimate of $\tau$:
+$$\hat \tau(I^c, I) = \left(\sum_{i \in I} \hat v_i d_i \right)^{-1} 
 \sum_{i \in I} \hat v_i (y_i - \hat g_0 (\mathbf x_i)),$$
-
 where $\hat v_i = d_i - \hat m_0(\mathbf x_i)$.
@@
 To rectify this, we repeat the above procedure, switching the split sets.
-We then have $\delta(I^c, I)$ and $\delta(I, I^c)$.
+We then have $\hat \tau(I^c, I)$ and $\hat \tau(I, I^c)$.
 The cross-fitting DML estimator is:
-$$\widehat {ATE}_{DML} = \frac{\hat \delta (I^c, I) + \hat \delta (I, I^c)}{2}.$$
+$$\hat \tau_{DML} = \frac{\hat \tau (I^c, I) + \hat \tau (I, I^c)}{2}.$$
+
 R code to implement DML is shown below.
@@
 First, a pre-processing function `dml_pre()` randomly splits the sample, outputting $I$ and $I^c$ sets of each of these variables.
-The second step predicts outcome and treatment probability for each half of the sample, using models fit to the other half.
+The second step predicts outcome values and treatment probabilities for each half of the sample, using models fit to the other half.
 In the code chunk here, generalized random forests from the `grf` package are used to predict these, but any prediction algorithm can be used.
@@
 
-To demonstrate double robustness, this section presents one of the simpler double robust estimators, AIPW [@glynn_2010_introduction]. As shown above, we can write this estimator as follows:
+To demonstrate double robustness, this section presents one of the simpler double robust estimators, AIPW. As shown above, we can write this estimator as follows:
 
 $$\begin{aligned}
-\widehat{ATE} = &\frac{1}{N} \sum_{i=1}^N \left( \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) \right) 
+\hat \tau = &\frac{1}{N} \sum_{i=1}^N \left( \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) \right) 
 - \frac{1}{N} \sum_{i=1}^N \left( \frac{(1-D_i)(Y_i - \hat \mu_0 (X_i))}{1-\hat \pi(X_i)} + \hat \mu_0(X_i) \right)
@@
 
-$$\hat Y_{1i} = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i)$$
+\begin{equation}
+\hat Y_{1i} = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i)
+(\#eq:treated-aipw)
+\end{equation}
 
@@
 
-$$\hat Y_{0i} = \frac{(1-D_i)(Y_i - \hat \mu_0 (X_i))}{1-\hat \pi(X_i)} + \hat \mu_0(X_i)$$
-
-Let's focus on the treated model:
-
-$$\hat Y_{1i} = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i)$$
-
-First, assume that the outcome model $\mu_1(X_i)$ is *correctly* specified and the exposure model $\pi(X_i)$ is *incorreclty* specified.
+\begin{equation}
+\hat Y_{0i} = \frac{(1-D_i)(Y_i - \hat \mu_0 (X_i))}{1-\hat \pi(X_i)} + \hat \mu_0(X_i)
+(\#eq:control-aipw)
+\end{equation}
+
+Let's focus on the treated model, Equation \@ref(eq:treated-aipw).
+First, assume that the outcome model $\mu_1(X_i)$ is *correctly* specified and the exposure model $\pi(X_i)$ is *incorrectly* specified.
 Let's also assume (for now) that we're dealing with a treated unit, i.e.
@@
 Then
-
-$$\hat \mu_1 (X_i) = Y_i$$
-
+$$E[\hat \mu_1 (X_i)] = E[Y_1 \mid X_i].$$
+This means that
+$$E[Y_i - \hat \mu_1(X_i)] = 0,$$
 and hence
-
-$$\hat Y_{1i} = \frac{D_i(0)}{\hat \pi (X_i)} + \hat \mu_1(X_i) = \hat \mu_1(X_i).$$
-
+$$E[\hat Y_{1i}] = 0 + \hat \mu_1(X_i) = \hat \mu_1(X_i).$$
 So the model relies *only* on the outcome model.
@@
 If we're dealing with a control unit ($D_i=0$), we get the same result:
-
 $$\hat Y_{1i} = \frac{0(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) = \hat \mu_1(X_i).$$
@@
 Now, what if the *exposure* model $\pi(X_i)$ is correctly specified and the outcome model $\mu_1(X)$ is incorrect? First, we rewrite the estimator for the treated outcome:
-
-$$\begin{aligned}
-\hat Y_{1i}& = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) \\
-&= \frac{D_iY_i}{\hat \pi (X_i)} - \frac{D_i\hat \mu_1 (X_i)}{\hat \pi (X_i)} + \frac{\hat \pi (X_i)\hat \mu_1(X_i)}{\hat \pi (X_i)} \\
-& = \frac{D_iY_i}{\hat \pi (X_i)} - \left( \frac{D_i - \hat \pi(X_i)}{\hat \pi (X_i)}\right) \hat \mu_1(X_i). &&(*)
-\end{aligned}$$
-
-Since the exposure model is correclty specified, we have $D_i = \hat \pi(X_i)$ on average, so
-
+\begin{align}
+\hat Y_{1i}& = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) \nonumber \\
+&= \frac{D_iY_i}{\hat \pi (X_i)} - \frac{D_i\hat \mu_1 (X_i)}{\hat \pi (X_i)} + \frac{\hat \pi (X_i)\hat \mu_1(X_i)}{\hat \pi (X_i)} \nonumber \\
+& = \frac{D_iY_i}{\hat \pi (X_i)} - \left( \frac{D_i - \hat \pi(X_i)}{\hat \pi (X_i)}\right) \hat \mu_1(X_i). 
+(\#eq:exposure-correct)
+\end{align}
+Since the exposure model is correctly specified, we have $D_i = \hat \pi(X_i)$ on average, so
 $$E[D_i - \hat \pi(X_i)] = 0.$$
-
-This means that the second term in equation $(*)$ is 0, so
-
+This means that the second term in Equation \@ref(eq:exposure-correct) is 0, so
 $$E[\hat Y_{1i}]= E \left [ \frac{D_iY_i}{\hat \pi (X_i)}\right].$$
-
-This shows that when the exposure model is correct, then the estimator depends *only* on the exposure model. We can make similar arguments for the control model $\hat Y_{0i}$.
+This shows that when the exposure model is correct, then the estimator depends *only* on the exposure model.
+We can make similar arguments for the control model for $\hat Y_{0i}$ in Equation \@ref(eq:control-aipw).
 
 This demonstration shows that this estimator achieves double robustness: The estimator is robust to misspecification of either the exposure or the outcome model (but not both).
-
-# Methods
+The other two double robust methods considered in this paper can be shown to have the same property, but proving so is more complicated.
+
+# Evaluation Strategy
 
@@
 This section tests the performance of each in practice using two strategies.
-First, results are compared using simulated data from a causal inference competition (@dorie_2019_automated).
-The true treatment effect is known, so these simulations allow assessment of accuracy.
+First, results are compared using simulated data from a causal inference competition [@dorie_2019_automated].
+The true treatment effect is known and all potential confounders are observed, so these simulations allow assessment of bias and related quantities.
 Second, these methods are applied to data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW).
-The NSW randomly provided training to disadvantaged workers, allowing an experimental estimate of the effect of the intervention, and data assembled by @dehejia_1999_causal allows these experimental estimates to be compared to observational ones.
-
-The three double robust methods are compared to two sets of traditional methods used as benchmarks.
+The NSW randomly provided training to disadvantaged workers, allowing an experimental estimate of the effect of the intervention, and data assembled by @dehejia_1999_causal compares these experimental estimates to observational ones.
+
+The three double robust methods are compared to two sets of traditional or "single robust" methods used as benchmarks.
+By "single robust," I mean methods that are not robust to any misspecification.
 First are one-model methods.
 The most classic method considered -- linear regression -- models only the response surface.
-Here it is estimated using ordinary least squares regression ("OLS"), entering each variable separately without any interactions or higher-order terms.
+It is estimated using ordinary least squares regression ("OLS"), entering each variable separately without any interactions or higher-order terms.
 Two other one-model methods model only the treatment assignment mechanism.
-Propensity score are estimated from logistic regression with each variable entered separately and without any higher order terms, then matched using the `MatchIt` package ("PSM").
+In propensity score matching (PSM), propensity scores are estimated from logistic regression with each variable entered separately and without any higher order terms, then matched using the `MatchIt` package.
 Finally, stabilized inverse probability weights [IPW, @austin_2015_moving, p.
 3663] are used for weighted OLS regression.
-These IPWs are estimated using each of the three under-the-hood estimation methods described below.
-
-The second set of traditional methods are two-model methods, which estimate separate models for treated and untreated units.
-In theory these could solve the misspecification problem that double robust methods are meant to solve, but they could still suffer from regularization bias.
-G-computation [@robins_1986_new; @hernan_2020_causal p.
-163; @snowden_2011_implementation] uses some estimation technique to predict outcomes under treatment and control for each unit in the dataset.
+These IPWs are estimated using propensity scores estimated by each of the three under-the-hood estimation techniques described below; extreme propensity scores are truncated so that they range from 0.01 to 0.99.
+
+The second set of single robust methods are two-model methods, which estimate separate models for treated and untreated units.
+In theory these could solve the misspecification problem that double robust methods are meant to solve, but they could still suffer from overfitting.
+G-computation [@robins_1986_new; @snowden_2011_implementation] uses some estimation technique to predict outcomes under treatment and control for each unit in the dataset.
 The ATE estimate is the difference in the average prediction under treatment and the average prediction under control.
@@
 This method aims to solve issues with the bias induced by OLS regression in a randomization framework by interacting the treatment indicator with mean-centered covariates.
-
-Many of these methods allow the user to choose the underlying estimation method, results compare three techniques.
-First is using a logistic regression for the exposure model and an OLS regression for the outcome model.
+@hazlett_2024_understanding show that this method is equivalent to estimating two separate OLS regression models for the treated and control units.
+
+Because many of these methods allow the user to choose the underlying estimation method, results compare three techniques.
+The first technique uses a logistic regression for the exposure model and an OLS regression for the outcome model.
 Second is generalized random forests [GRF, @athey_2019_generalized] using the `grf` R package, with separate models for exposure and outcome.
-The final technique is the SuperLearner (as promoted by the makers of TMLE) using the `SuperLearner` package, again with separate models for exposure and outcome.
-GLM, glmnet (lasso), and XGBoost models are considered for the SuperLearner.
-These three estimation techniques are used for each of the three double robust methods, for IPW, and for G-computation.
+The final technique is the SuperLearner (as promoted by the makers of TMLE) using the `SuperLearner` package [@polley_2023_superlearner], again with separate models for exposure and outcome.
+GLM, glmnet [a weighted average of lasso and ridge regression, @friedman_2021_package], and XGBoost [@chen_2016_xgboost] models are considered for the SuperLearner.
+These three estimation techniques are used for each of the three double robust methods and for IPW.
+GRF and SuperLearner are also used for G-computation (OLS predictions with G-computation return identical results to OLS regression coefficient estimates).
 
 For the simulations, results compare only point estimates from these methods.
-For evaluation of the experimental LaLonde data, I use bootstrapping with 100 samples to obtain estimates and standard errors.
-
-# Results
+For evaluation of the experimental LaLonde data, I use bootstrapping with 100 samples to obtain standard errors and confidence intervals.
+Using AIPW as written above results in some wildly biased estimates, due to dividing by some very small propensity scores.
+Hence I present estimates from a truncated AIPW estimator, where predicted exposure model values are set to 0.01 if they are less than 0.01 and to 0.99 if they are greater than 0.99.
 
@@
 
-lm_df %>%
-  group_by(set) %>%
-  summarize(ate_est = mean(ate), 
-            se = sd(ate))
+# lm_df %>%
+#   group_by(set) %>%
+#   summarize(ate_est = mean(ate), 
+#             se = sd(ate))
 ```
@@
 
+    y <- sims[[i]]$y
     D <- sims[[i]]$z == 'trt'
     PrD <- mean(D)
-    ps <- predictions[[j]][[i]]$pi_pred
-    ipw <- D*PrD/ps + (1-D)*(1-PrD)/(1-ps)
-
+    # ps <- predictions[[j]][[i]]$pi_pred
+    ps <- case_when(
+      predictions[[j]][[i]]$pi_pred < .01 ~ .01,
+      predictions[[j]][[i]]$pi_pred > .99 ~ .99,
+      T ~ predictions[[j]][[i]]$pi_pred)
+
+    # ate_ipw <- sum((D*y)/ps) / sum(D/ps) - sum(((1-D)*y)/(1-ps)) / sum(1-D/(1-ps))
+
+    # ate_ipw <- mean(y*(D==1*PrD)/ps - y*((D==0)*(1-PrD))/(1-ps))
+
+    ipw <- (D*PrD)/ps + ((1-D)*(1-PrD))/(1-ps)
     lm_out <- lm(sims[[i]]$y ~ D, weights=ipw)
@@
 ```{r g-comp, eval = F}
-ols_logit_pred_list2 <- readRDS(here('files/homemade', 'ols_logit_pred.RDS'))
 grf_pred_list2 <- readRDS(here('files/homemade', 'grf_pred.RDS'))
@@
 gcomp_out_list <- list()
-predictions <- list(ols_logit_pred_list2, grf_pred_list2, superlearner_pred_list2)
-pred_names <- c('ols', 'grf', 'superlearner')
+predictions <- list(grf_pred_list2, superlearner_pred_list2)
+pred_names <- c('grf', 'superlearner')
 for(i in 1:length(sims)){
@@
   ipw <- (d*y)/pi_pred - (1-d)*y/(1-pi_pred)
-  adjust <- (d-pi_pred)/(pi_pred*(1-pi_pred)) * (1-pi_pred)*mu1_pred + pi_pred*mu0_pred
+  adjust <- (d-pi_pred)/(pi_pred*(1-pi_pred)) * ((1-pi_pred)*mu1_pred + pi_pred*mu0_pred)
 
@@
   for(j in 1:length(predictions)){
+
+    # if(j == 1){
+    #   predictions[[j]][[i]]$pi_pred <- case_when(
+    #     predictions[[j]][[i]]$pi_pred < .01 ~ .01,
+    #     predictions[[j]][[i]]$pi_pred > .99 ~ .99,
+    #     T ~ predictions[[j]][[i]]$pi_pred)
+    #   }
 
@@
 
+    # if(j == 1){
+    #   predictions[[j]][[i]]$pi_pred <- case_when(
+    #     predictions[[j]][[i]]$pi_pred < .01 ~ .01,
+    #     predictions[[j]][[i]]$pi_pred > .99 ~ .99,
+    #     T ~ predictions[[j]][[i]]$pi_pred)
+    #   }
+
     start_time <- Sys.time()
@@
                                y = y))
+
     comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
@@
 pred_names <- c('ols_logit', 'grf', 'superlearner')
-
 for(i in 1:length(sims)){
@@
   for(j in 1:length(predictions)){
+
+    # if(j == 1){
+    #   predictions[[j]][[i]]$pi_pred <- case_when(
+    #     predictions[[j]][[i]]$pi_pred < .01 ~ .01,
+    #     predictions[[j]][[i]]$pi_pred > .99 ~ .99,
+    #     T ~ predictions[[j]][[i]]$pi_pred)
+    # }
+
     start_time <- Sys.time()
@@
 
+## DML OLS logit (truncated)
+# 
+# ols_logit_dml_list <- list()
+# 
+# set.seed(1285)
+# for(i in 1:length(sims)){
+#   print(i)
+#   dat <- sims[[i]]
+#   
+#   start_time <- Sys.time()
+#   dml_pre_out <- dml_pre(dat$y,
+#                        as.numeric(ifelse(dat$z == 'trt', 1, 0)),
+#                        x = dat$x)
+# 
+#   ols_logit_dml_out <- do.call(ols_logit_dml, dml_pre_out)
+#   
+#   ols_logit_dml_out$pi_pred1 <- case_when(
+#         ols_logit_dml_out$pi_pred1 < .01 ~ .01,
+#         ols_logit_dml_out$pi_pred1 > .99 ~ .99,
+#         T ~ ols_logit_dml_out$pi_pred1)
+# 
+#   ols_logit_dml_out$pi_pred2 <- case_when(
+#         ols_logit_dml_out$pi_pred2 < .01 ~ .01,
+#         ols_logit_dml_out$pi_pred2 > .99 ~ .99,
+#         T ~ ols_logit_dml_out$pi_pred2)
+#     
+#     
+#   
+#   dml_post_out <- do.call(dml_post, append(dml_pre_out, ols_logit_dml_out))
+#   comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
+#   
+#   truth <- mean(dat$y.1) - mean(dat$y.0)
+#    
+#   ols_logit_dml_list[[i]] <- data.frame(ate = dml_post_out, 
+#                               truth = truth, 
+#                               comp_time = comp_time,
+#                               dataset = i,
+#                               dorie_dataset = dat$dataset,
+#                               set = dat$set,
+#                               size = dat$size)
+# }
+# 
+# write_csv(bind_rows(ols_logit_dml_list), 
+#           here('files/homemade', 'dml_ols_logit_trunc.csv'))
+
 # perform(bind_rows(ols_logit_dml_list), label = 'grf, dml')
@@
 
-## Simluations with Dorie et al. (2019) Data
-
-In 2016, the Atlantic Causal Inference Conference hosted a competition for causal inference methods that adjust on observables.
-@dorie_2019_automated published the results of this competition, along with the data used in the competition.
-Below, I test double robust methods on the 20 data sets used for the "do-it-yourself" part of the competition.
-The data represent a hypothetical twins study investigating the impact of birth weight on IQ.
-The data have 4802 observations and 52 covariates.
-The authors of the study specify a different data generating process for the potential outcomes in each data set.
-In all cases, ignorability holds, but the authors vary the following:
-
-- degree of nonlinearity
-- percentage of treated
-- overlap for the treatment group
-- alignment (correspondence between the assignment mechanism and the response surface)
-- treatment effect heterogeneity
-- overall magnitude of the treatment effect
-
-### Main results
-
-The 20 data sets used here cover a range of these attributes; see the supplemental material from @dorie_2019_automated for details.
-I use 10 simulations of each data set, resulting in 200 data sets.
-I then calculate bias, percent bias (the estimator's bias as a percentage of its standard error), root mean squared error (rmse), and median absolute error (mae).
-I also present the number of datasets for which the method fails and the average computation time for each data set, in seconds.
-
-Results for the full range of simulations are shown in Table \@ref(tab:dorie-results) and Figure \@ref(fig:dorie-results-fig).
-Using AIPW as written above results in some wildly biased estimates for the ols_logit estimator, due to dividing by some very small propensity scores.
-Hence I present estimates from a trimmed AIPW estimator, where predicted exposure model values are set to 0.01 if they are less than 0.01 and to 0.99 if they are greater than 0.99.
-
-The lowest bias is achieved by AIPW with GRF, followed by propensity score matching and then OLS.
-The lowest root mean squared error is obtained by AIPW with GRF, followed by TMLE with GRF, and next by OLS regression.
-Results are similar if we consider percent bias or mean absolute error.
-DML does not perform particularly well and also has the highest computation times due to sample splitting.
-
-```{r dorie-results}
+# Simluations with Dorie et al. (2019) Data
+
+```{r results-load}
 
@@
   mutate(estimator = factor(estimator, levels = c('ols_logit', 'ols', 'logit', 'grf', 'superlearner')),
-         method = factor(method, levels = c('ols', 'psm', 'lin', 'ipw', 'g-comp', 'aipw', 'tmle', 'dml'))) %>%
+         method = factor(method, levels = c('ols', 'psm', 'ipw', 'g-comp', 'lin', 
+                                            'aipw', 'tmle', 'dml', 'aipw (original)'))) %>%
   arrange(method, estimator) %>%
@@
   mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator})))
-```
-
-```{r dorie-results-fig, fig.height = 6, fig.cap = 'Results of Monte Carlo simulations using the first 20 datasets from Dorie et al. (2019), 10 replications each.'}
+
+# write_csv(sim_results, here('files', 'lalonde_means.csv'))
+```
+
+In 2016, the Atlantic Causal Inference Conference hosted a competition for causal inference methods that adjust on observables.
+@dorie_2019_automated published the results of this competition, along with the data used in the competition.
+Below, I test double robust methods on the 20 data sets used for the "do-it-yourself" part of the competition.
+The data represent a hypothetical twins study investigating the impact of birth weight on IQ.
+The data have 4,802 observations and 52 covariates.
+The authors of the study specify a different data generating process for the potential outcomes in each data set.
+In all cases, ignorability holds (all potential confounders are observed), but the authors vary the following:
+
+- degree of nonlinearity
+- percentage of treated
+- overlap for the treatment group
+- alignment (correspondence in variables used to generate the assignment mechanism and the response surface)
+- treatment effect heterogeneity
+
+The true treatment effect also varies, but as a function of the other DGP characteristics.
+It has a mean of `r sim_results %>% filter(set == 'main') %>% summarize(round(mean(truth), 1))`, standard deviation of `r sim_results %>% filter(set == 'main') %>% summarize(round(sd(truth), 1))`, and range of `r sim_results %>% filter(set == 'main') %>% pull(truth) %>% min() %>% round(1)` to `r sim_results %>% filter(set == 'main') %>% pull(truth) %>% max() %>% round(1)`.
+
+## Main results
+
+The 20 data sets used here cover a range of these attributes; see the supplemental material from @dorie_2019_automated for details.
+I use 10 simulations of each data set, resulting in 200 data sets.
+I then calculate bias, percent bias (the estimator's bias as a percentage of its standard error), root mean squared error (rmse), and median absolute error (mae).
+I also present the number of datasets for which the method fails and the median computation time for each data set, in seconds.^[Simulations were run on a 2020 MacBook Pro laptop computer with a 2 GHz Quad-Core Intel Core i5 Processor and 16 GB of memory.] In the main text I present average bias and RMSE, while the appendix contains tables with full results (Table \@ref(tab:dorie-results-table)).
+
+Bias results for the full range of simulations are shown in Figure \@ref(fig:dorie-results-bias).
+Bias is quite low for many of the methods, however IPW (logit) and AIPW (OLS/logit) have high bias and variance, while TMLE (OLS/logit) has moderately high bias and variance.
+With an average true treatment effect of `r sim_results %>% filter(set == 'main') %>% summarize(round(mean(truth), 1))`, bias with absolute value greater than 1 is substantial.
+The traditional methods, however, achieve fairly low bias in general.
+
+Figure \@ref(fig:dorie-results-rmse) orders methods by RMSE and presents both bias and RMSE.
+The lowest RMSE is achieved by three of the methods using SuperLearner estimators (AIPW, TMLE, and G-computation) with values of about 0.35, followed closely by the same three methods using GRF, with values closer to 0.5.
+The computationally efficient Lin estimator does not do much worse, with an RMSE of 0.6, and OLS and PSM achieve acceptable RMSE of 0.7 to 0.9.
+Interestingly, DML with the computationally efficient OLS/logit estimators achieves lower RMSE than with GRF or SuperLearner (0.8 compared to 0.9 and 1.6, respectively).
+The only estimators with RMSE that exceed 2 are TMLE (OLS/logit) with 2.3, IPW (logit) with 8.1, and AIPW (OLS/logit) with 10.1.
+These methods all use logit models to estimate probability of treatment, and these high error rates are likely due to extreme values of these estimates.
+
+<!-- Overall, while the double robust methods of AIPW and TMLE achieve slightly lower RMSE than the more traditional, differences are quite small.
+OLS, PSM, and the Lin estimator all achieve fairly low RMSE and are computed in less than a second.
+Compare this to the lowest-RMSE method AIPW with SuperLearner, which takes an average of 130 seconds per simulation.
+-->
+
+Overall, traditional methods perform surprisingly well in comparison with the double robust methods, and flexible single robust methods may be as effective as double robust methods.
+Even in the full range of datasets -- which include highly nonlinear exposure and outcome data-generating processes -- OLS, propensity score matching, and the Lin estimator obtain some of the smallest bias and RMSE.
+While double robust methods achieve the lowest RMSE, the choice of underlying estimator appears more important than the choice of method.
+AIPW and TMLE both do well with a flexible underlying estimator, while DML does worse than OLS.
+Of the estimators considered, the SuperLearner (which considers GLM, glmnet, and XGBoost models) appears to be best for the double robust methods, with GRF following closely.
+G-computation does only a hair worse than these two double robust methods without explicitly accounting for regularization bias.
+Notably, the method with the longest computation time -- DML with a SuperLearner -- takes nearly 2,000 times as long as OLS (an average of 129 seconds per simulation compared to 0.061 seconds).
+
+```{r dorie-results-bias,  fig.cap = 'Bias of Monte Carlo simulations using the first 20 datasets from Dorie et al. (2019), 10 replications each.'}
 addline_format <- function(x,...){
@@
   #facet_wrap(~method, scales = 'free_x') +
-  labs(x = '', title = 'All datasets') +
-  theme(#axis.text.x=element_text(angle=-15), 
-        legend.position = 'none') +
-  scale_x_discrete(labels=function(x){sub(", ", "\n", x)})
-```
-
-### Linear DGPs
-
-Traditional methods may perform better when the data generating processes are linear.
-To test this, I use 100 simulations of each of the two datasets from @dorie_2019_automated with linear data generating processes (numbers 1 and 3) to show how these methods perform when the underlying models are linear.
-
-If we consider only the linear datasets (Table \@ref(tab:dorie-results-linear) and Figure \@ref(fig:dorie-results-linear-fig)), OLS obtains the lowest bias, followed by AIPW with GRF and then propensity score matching.
-The lowest root mean squared error is achieved by OLS, then AIPW with GRF, and then TMLE with GRF.
-Percent bias and mean absolute error show similar results.
-
-Overall, traditional methods perform surprisingly well in comparison with the double robust methods.
-Even in the full range of datasets -- which include highly nonlinear exposure and outcome data-generating processes -- OLS and propensity score matching obtain some of the smallest bias.
-Generalized random forests appear to be the best estimators for the double robust methods, though a SuperLearner than incorporates GRF has the potential to outperform GRF alone, at the expense of computation time.
-Notably, the method with the longest computation time -- DML with a SuperLearner -- takes over 2,000 times as along as OLS.
-
-```{r dorie-results-linear-fig, fig.height = 6, fig.cap = 'Results of Monte Carlo simulations using the two datasets from Dorie et al.
-(2019), with linear data generating processes, 100 replications each ("linear").'}
+  labs(x = '', title = 'Main datasets') +
+  scale_y_continuous(trans=ggallin::pseudolog10_trans, breaks = c(-30, -20, -10, -1, 0, 1, 10, 20, 30)) +
+  # scale_x_discrete(labels=function(x){sub(", ", "\n", x)}) +
+  theme(axis.text.x=element_text(angle=90, hjust=0.95,vjust=0.2),
+        legend.position = 'none')
+
+```
+
+```{r dorie-results-rmse, fig.cap = 'Root mean squared error and bias for Monte Carlo simulations using the first 20 datasets from Dorie et al.
+(2019), 10 replications each.
+Values greater in absolute value than 4 are plotted at 4 and labeled with their actual value.'}
+
+sim_results_plot <- sim_results %>%
+  filter(set == 'main') %>%
+  group_by(method_estimator) %>%
+  summarize(bias = mean(ate - truth, na.rm = T),
+            rmse = sqrt(mean((ate - truth)^2, na.rm = T))
+              ) %>%
+  arrange(rmse) %>%
+  mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
+  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator}))) %>%
+  pivot_longer(c(bias, rmse)) %>%
+    mutate(label = ifelse(abs(value) > 4, round(value), NA),
+         value = ifelse(abs(value) > 4, 4*value/abs(value), value))
+
+sim_results_plot %>%
+  #filter(method %in% c('ols', 'psm', 'aipw')) %>%
+  ggplot(aes(x = method_estimator, y = value, color = name, shape = name)) +
+  geom_point() +
+  # ggrepel::geom_text_repel(aes(label = label), show.legend = F) +
+  geom_text(aes(label = label), nudge_y = ifelse(sim_results_plot$label > 0, -.5, .5), show.legend = F) +
+  geom_hline(yintercept = 0) + 
+  #facet_wrap(~method, scales = 'free_x') +
+  labs(x = '', y = '', title = 'Main datasets') +
+  theme(axis.text.x=element_text(angle=90, hjust=0.95,vjust=0.2)) +
+  #scale_x_discrete(labels=function(x){sub(", ", "\n", x)}) +
+  #scale_y_continuous(trans=ggallin::pseudolog10_trans)
+  ylim(c(-4, 4))
+
+```
+
+## Linear DGPs
+
+Due to their functional form assumptions, traditional methods may perform better when the data generating processes are linear.
+To test this, I use 100 simulations of each of the two datasets from @dorie_2019_automated with linear data generating processes for both exposure and outcome (numbers 1 and 3).
+In these two datasets, the average true treatment effect is `r sim_results %>% filter(set == 'linear') %>% summarize(mean(truth))` with a standard deviation of `r sim_results %>% filter(set == 'linear') %>% summarize(sd(truth))`.
+
+Figure \@ref(fig:dorie-linear-bias) shows the bias from each simulation for each method (in the Appendix, Table \@ref(tab:dorie-linear-results) shows the full results).
+Similarly to the full set of simulations, bias is fairly low for most methods.
+IPW (logit) and AIPW (OLS/logit) again suffer from greater bias than other methods, though not to quite as extent as in the full range of simulations.
+Unsurprisingly, methods that assume linearity -- OLS, PSM, the Lin model -- achieve low bias and variance.
+IPW does less well than expected, even when treatment assignment is modeled with flexible GRF and SuperLearner.
+
+Figure \@ref(fig:dorie-linear-rmse) orders the methods by RMSE and presents both RMSE and bias.
+The methods achieving the lowest RMSE are again three of the SuperLearner methods (TMLE, AIPW, and G-computation) followed by the Lin estimator, DML (OLS/logit), and OLS.
+The only methods with RMSE above 1 are IPW (logit) and AIPW (OLS/logit), again likely due to unstable logit predictions.
+
+With these linear DGPs, there seems little reason to sacrifice computational efficiency for a very slight reduction in RMSE.
+The Lin estimator has an RMSE of 0.28 compared to the lowest-RMSE method, TMLE (SuperLearner), of 0.25, and computes in 0.15 seconds compared to the latter's 126 seconds.
+Even standard OLS has quite a low RMSE of 0.39.
+While DML performs better with the linear DGPs than the full range of simulations, it still obtains higher RMSE than at least certain AIPW and TMLE variants.
+Finally, G-computation again shows its strength, outperforming most other methods when it is estimated using a SuperLearner.
+
+```{r dorie-linear-bias,  fig.cap = 'Bias of Monte Carlo simulations using the two datasets from Dorie et al. (2019), with linear data generating processes, 100 replications each ("linear").'}
 sim_results %>% 
@@
   labs(x = '', title = 'Linear DGPs') +
-  theme(#axis.text.x=element_text(angle=-15), 
-        legend.position = 'none') +
-  scale_x_discrete(labels=function(x){sub(", ", "\n", x)})
-```
-
-### Do results vary by DGP?
-```{r vary}
+  scale_y_continuous(trans=ggallin::pseudolog10_trans, breaks = c(-20, -10, -5, -1, 0, 1, 5)) +
+  # scale_x_discrete(labels=function(x){sub(", ", "\n", x)}) +
+  theme(axis.text.x=element_text(angle=90, hjust=0.95,vjust=0.2),
+        legend.position = 'none') 
+```
+
+```{r dorie-linear-rmse,  fig.cap = 'Root mean squared error and bias for Monte Carlo simulations using the two datasets from Dorie et al.
+(2019), with linear data generating processes, 100 replications each ("linear").
+Values greater in absolute value than 4 are plotted at 4 and labeled with their actual value.'}
+
+sim_results_plot <- sim_results %>%
+  filter(set == 'linear') %>%
+  group_by(method_estimator) %>%
+  summarize(bias = mean(ate - truth, na.rm = T),
+            rmse = sqrt(mean((ate - truth)^2, na.rm = T))
+              ) %>%
+  arrange(rmse) %>%
+  mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
+  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator}))) %>%
+  pivot_longer(c(bias, rmse)) %>%
+  mutate(label = ifelse(abs(value) > 4, round(value), NA),
+         value = ifelse(abs(value) > 4, 4*value/abs(value), value))
+
+sim_results_plot %>%
+  #filter(method %in% c('ols', 'psm', 'aipw')) %>%
+  ggplot(aes(x = method_estimator, y = value, color = name, shape = name)) +
+  geom_point() +
+  # ggrepel::geom_text_repel(aes(label = label), show.legend = F) +
+  geom_text(aes(label = label), nudge_y = ifelse(sim_results_plot$label > 0, -.5, .5), show.legend = F) +
+  geom_hline(yintercept = 0) + 
+  #facet_wrap(~method, scales = 'free_x') +
+  labs(x = '', y = '', title = 'Linear DGPs') +
+  theme(axis.text.x=element_text(angle=90, hjust=0.95,vjust=0.2)) +
+  #scale_x_discrete(labels=function(x){sub(", ", "\n", x)}) +
+  #scale_y_continuous(trans=ggallin::pseudolog10_trans)
+  ylim(c(-4, 4))
+```
+
+## Do results vary by DGP?
+```{r vary-old, eval = F}
 sim_results_dgp <- sim_results %>%
@@
 }
-```
-
-### Do results vary by sample size?
-
-The double robust methods reviewed here have been shown to have lower bias asymptotically.
-Is the issue with previous results simply that the sample size of the simulation data ($n$ = 4,802) is too small for double robust methods to outperform traditional methods?
+
+```
+
+```{r vary-fig, eval = F}
+sim_results_dgp <- sim_results %>%
+  filter(set == 'main') %>%
+  # mutate(paramter_num = ceiling(dataset/10)) %>%
+  left_join(mutate(aciccomp2016::parameters_2016, dorie_dataset = row_number()))
+
+dgp_names <- c('Treatment assignment', 'Probability of treatment',
+               'Overlap of treatment', 'Response surface',
+               'Alignment (same terms for treatment and response)',
+               'Treatment effect heterogeneity')
+
+names(dgp_names) <- names(aciccomp2016::parameters_2016)
+
+for(name in colnames(aciccomp2016::parameters_2016[1])){
+
+  sim_results_plot <- sim_results_dgp %>%
+    group_by(!!sym(name), method_estimator) %>%
+    summarize(bias = round(mean(ate - truth, na.rm = T), 3),
+              rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3)
+                ) %>%
+    arrange(rmse) %>%
+    mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
+    mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator}))) %>%
+    pivot_longer(c(bias, rmse)) %>%
+    mutate(label = ifelse(abs(value) > 4, round(value), NA),
+           value = ifelse(abs(value) > 4, 4*value/abs(value), value))
+
+  sim_results_plot %>%
+    #filter(method %in% c('ols', 'psm', 'aipw')) %>%
+    ggplot(aes(x = method_estimator, y = value, color = name, shape = name)) +
+    geom_point() +
+    # ggrepel::geom_text_repel(aes(label = label), show.legend = F) +
+    geom_text(aes(label = label), nudge_y = ifelse(sim_results_plot$label > 0, -.5, .5), show.legend = F) +
+    geom_hline(yintercept = 0) + 
+    #facet_wrap(~method, scales = 'free_x') +
+    labs(x = '', y = '', title = dgp_names[name]) +
+    theme(axis.text.x=element_text(angle=90, hjust=0.95,vjust=0.2)) +
+    #scale_x_discrete(labels=function(x){sub(", ", "\n", x)}) +
+    #scale_y_continuous(trans=ggallin::pseudolog10_trans)
+    ylim(c(-4, 4)) +
+    facet_wrap(vars(!!sym(name)), ncol = 1, scales = 'free_x') %>%
+    print()
+
+}
+
+```
+
+```{r dgp}
+dgp_names <- c('Treat. assign.', 'Prob. of treat.',
+               'Overlap', 'Response surface',
+               'Alignment',
+               'Treat. heterogeneity')
+
+rename_vec <- names(aciccomp2016::parameters_2016)
+names(rename_vec) <- dgp_names
+
+sim_results_dgp <- sim_results %>%
+  filter(set == 'main') %>%
+  # mutate(paramter_num = ceiling(dataset/10)) %>%
+  left_join(mutate(aciccomp2016::parameters_2016, dorie_dataset = row_number())) %>%
+  rename(rename_vec) %>%
+  mutate(estimator = if_else(is.na(estimator), 'NA', estimator),
+         method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
+  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator})))
+
+dgp_list <- list()
+
+for(name in dgp_names){
+
+  dgp_list[[name]] <- sim_results_dgp %>%
+    group_by(!!sym(name), method_estimator) %>%
+    summarize(rmse = sqrt(mean((ate - truth)^2, na.rm = T))
+                ) %>%
+    ungroup() %>%
+    group_by(!!sym(name)) %>%
+    slice_min(rmse, n = 6) %>%
+    mutate(rank = c('Lowest RMSE', 'Second-lowest', 'Third-lowest', 
+                    'Fourth-lowest', 'Fifth-lowest', 'Sixth-lowest'),
+           `DGP parameter` = name) %>%
+    ungroup() %>%
+    mutate(rmse = round(rmse, 3),
+          value = paste(method_estimator, rmse, sep = ': '),
+          dgp_value = as.character(!!sym(name))) %>%
+    select(`DGP parameter`, dgp_value, value, rank) %>%
+    pivot_wider(names_from = rank)
+
+}
+
+bind_rows(dgp_list) %>%
+  select(-c(`Fourth-lowest`:`Sixth-lowest`)) %>%
+  kableExtra::kable(booktabs = T, 
+                    digits = 3,
+                    linesep = '',
+                    caption = 'Data generating process: Three lowest RMSE methods by DGP for Monte Carlo simulations using the first 20 datasets from Dorie et al. (2019), 10 replications each.')
+```
+
+```{r dgp-2}
+bind_rows(dgp_list) %>%
+  select(-c(`Lowest RMSE`:`Third-lowest`)) %>%
+  kableExtra::kable(booktabs = T, 
+                    digits = 3,
+                    linesep = '',
+                    caption = 'Data generating process: Fourth- to sixth-lowest RMSE methods by DGP for Monte Carlo simulations using the first 20 datasets from Dorie et al.
+(2019), 10 replications each.')
+
+```
+
+While the AIPW, TMLE, and G-computation with a SuperLearner may be the top performing methods overall, this does not mean that there are some data-generating processes (DGPs) where some other method may do better.
+Across the the 20 datasets, @dorie_2019_automated vary six DGP characteristics: degree of nonlinearity, the percentage treated, overlap for the treatment group, alignment (correspondence in variables used to generate the exposure and response models), and treatment effect heterogeneity.
+To test how the methods perform across different values of these characteristics, I begin with the 200 simulations from the 20 datasets used in the main results (Figures \@ref(fig:dorie-results-bias) and \@ref(fig:dorie-results-rmse), Table \@ref(tab:dorie-results-table)).
+I limit datasets to those generated by a particular value of a DGP characteristic, and I then calculate RMSE for each method for only these datasets.
+For example, alignment is 0 for datasets 8 and 16 (meaning there is 0 correlation between the terms included in the treatment and outcome models), so for this value of the DGP RMSE is calculated only for those two datasets.
+
+Tables \@ref(tab:dgp) and \@ref(tab:dgp-2) shows the six top-performing methods by lowest RMSE for each each value of the DGP characteristics.
+Across DGPs, the same methods dominate as in the full range of simulations: the SuperLearner with AIPW, TMLE, and G-compuation.
+In fact, these three methods take the top three spots for *every* DGP variation in the simulations.
+
+Table \@ref(tab:dgp-2) shows the fourth- to sixth-lowest RMSE methods for each DGP variation.
+GRF with AIPW, G-computation, and TMLE take most of these spots, but the Lin estimator and OLS appear a few times.
+
+Overall, there is little variation across different types of DGPs in which method performs the best.
+Flexible estimators take the top spots (though notably not those used with DML), and traditional methods do fairly well across the board.
+
+## Do results vary by sample size?
+
+In the above simulations, double robust methods have only slightly outperformed traditional methods.
+Is the issue with previous results simply that the sample size of the simulation data ($n = 4,802$) is too small for double robust methods to seriously outperform traditional methods?
+The double robust methods reviewed here have been shown to have lower bias asymptotically, so perhaps their superiority to traditional or single robust methods will be starker in larger samples.
 To test this, this section uses simulated datasets of varying sizes, from 150 to 96,040 (20 times the original sample size).
@@
 For sample sizes less than 4,802, the sample is randomly drawn from a randomly generated 4,802-unit sample.
-For sample sizes greater than 4,802, the design matrix (but non the outcome variable) is duplicated, then fed into the `dgp_2016` function.
+For sample sizes greater than 4,802, the design matrix (but not the outcome variable) is duplicated, then fed into the `dgp_2016` function.
 This preserves covariate distributions but retains stochasticity in the outcome.
 
-Results are presented in Table \@ref(tab:dorie-results-size) and Figure \@ref(fig:dorie-size-fig).
-
-```{r dorie-size-fig, fig.height = 6, fig.cap = 'RMSE of Monte Carlo simulations using dataset 7 from Dorie et al. (2019) with varying sample sizes, 20 replications each'}
+Table \@ref(tab:dorie-size) presents the four methods with the lowest RMSE for each sample size (Table \@ref(tab:dorie-results-size) in the Appendix presents full results).
+Again, AIPW, TMLE, and G-computation methods that incorporate the SuperLearner or GRF dominate.
+There are two exceptions: In the tiny sample of 150, IPW (SuperLearner) and IPW (GRF) figure into the best four methods.
+PSM is the best-performing method in samples of 1200, but it fails to estimate 17 of the 20 datasets.
+(With 58 covariates, some of the methods fail in smaller samples.)
+
+Figure \@ref(fig:dorie-size-fig) presents RMSE for all sample sizes for all methods.
+In the smallest samples, GRF and SuperLearner are able to provide estimates, while traditional methods fail.
+Beginning at 1,200 observations, all methods are able to provide estimates for all datasets, with the exception of PSM, which fails to calculate even in some large samples.
+For most methods, RMSE decreases nearly monotonically as sample size grows.
+Two exceptions are IPW (logit) and AIPW (OLS/logit), whose error is highest in the maximum sample of 96,040, likely due to extreme logit estimates.
+In addition, the rank order of methods is nearly constant across sample sizes.
+DML does not achieve lower RMSE than OLS, PSM, or the Lin estimator in most sample sizes, and methods using the SuperLearner or GRF perform the best across sample sizes.
+
+In sum, although methods incorporating SuperLearner or GRF do the best in most sample sizes, traditional methods still perform fairly well, achieving low RMSE once the sample size is large enough for them to stably compute.
+
+```{r dorie-size-fig-old, fig.height = 8, eval = F, fig.cap = 'RMSE of Monte Carlo simulations using dataset 7 from Dorie et al. (2019) with varying sample sizes, 20 replications each'}
 addline_format <- function(x,...){
@@
 
-sim_results %>%
+size_plot <- sim_results %>%
   filter(set %in% c('small', 'large')) %>%
@@
             mae = median(abs(ate - truth), na.rm = T),
-            comp_time = sum(comp_time)/n(),
+            comp_time = median(comp_time),
             fail_count = n() - sum(!is.na(ate))
@@
                              as.character(method_estimator), NA_character_),
-         size = factor(size, levels = sort(unique({.$size})))) %>%
+         size = factor(size, levels = sort(unique({.$size}))))
+
+text_size = 3
+
+(size_plot %>%
+  filter(method %in% c('ols', 'psm', 'ipw', 'g-comp', 'lin')) %>%
   ggplot(aes(x = size, y = rmse, color = method, linetype = estimator, group = method_estimator)) +
   geom_line() +
-  ggrepel::geom_text_repel(aes(label = label_min), nudge_x = -1, na.rm = T, segment.color = 'transparent') +
-  ggrepel::geom_text_repel(aes(label = label_max), nudge_x = 1, na.rm = T, segment.color = 'transparent') +
+  ggrepel::geom_text_repel(aes(label = label_min), nudge_x = -1, na.rm = T, 
+                           size = text_size, segment.color = 'transparent') +
+  ggrepel::geom_text_repel(aes(label = label_max), nudge_x = 1, na.rm = T, 
+                           size = text_size, segment.color = 'transparent') +
   scale_y_continuous(trans='log10') +
+  theme(legend.position = 'none')) /
+  (size_plot %>%
+    filter(method %in% c('aipw', 'tmle', 'dml')) %>%
+    ggplot(aes(x = size, y = rmse, color = method, linetype = estimator, group = method_estimator)) +
+    geom_line() +
+    ggrepel::geom_text_repel(aes(label = label_min), nudge_x = -1, na.rm = T, 
+                             size = text_size, segment.color = 'transparent') +
+    ggrepel::geom_text_repel(aes(label = label_max), nudge_x = 1, na.rm = T, 
+                             size = text_size, segment.color = 'transparent') +
+    scale_y_continuous(trans='log10') +
+    theme(legend.position = 'none'))
+```
+
+```{r dorie-size}
+# 
+# 
+# size_plot <- sim_results %>%
+#   filter(set %in% c('small', 'large')) %>%
+#   group_by(method, estimator, method_estimator, size) %>%
+#   summarize(rmse = sqrt(mean((ate - truth)^2, na.rm = T))) %>%
+#   group_by(method_estimator) %>%
+#   mutate(min_size = min(size*rmse/rmse, na.rm = T)) %>%
+#   ungroup() %>%
+#   mutate(estimator = if_else(is.na(estimator), 'NA', estimator),
+#          method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
+#   mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator})),
+#          label_min = if_else(size == min_size, as.character(method_estimator), NA_character_),
+#          label_max = if_else(size == max(as.numeric(size)), 
+#                              as.character(method_estimator), NA_character_),
+#          size = factor(size, levels = sort(unique({.$size}))))
+
+size_plot <- sim_results %>%
+  filter(set %in% c('small', 'large')) %>%
+  group_by(method, estimator, method_estimator, size) %>%
+  summarize(bias = round(mean(ate - truth, na.rm = T), 3),
+            percent_bias = bias/sd(ate, na.rm = T),
+            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
+            mae = median(abs(ate - truth), na.rm = T),
+            comp_time = median(comp_time),
+            fail_count = n() - sum(!is.na(ate))
+              ) %>%
+  group_by(method_estimator) %>%
+  mutate(min_size = min(size*bias/bias, na.rm = T)) %>%
+  ungroup() %>%
+  mutate(estimator = if_else(is.na(estimator), 'NA', estimator),
+         method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
+  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator})),
+         label_min = if_else(size == min_size, as.character(method_estimator), NA_character_),
+         label_max = if_else(size == max(as.numeric(size)), 
+                             as.character(method_estimator), NA_character_),
+         size = factor(size, levels = sort(unique({.$size}))))
+
+size_plot %>%
+  group_by(size) %>%
+  slice_min(rmse, n = 4) %>% 
+  # mutate(rank = paste('Rank', row_number())) %>%
+  mutate(rank = c('Lowest', 'Second-lowest', 'Third-lowest', 'Fourth-lowest')) %>%
+  ungroup() %>%
+  mutate(rmse = round(rmse, 3),
+         value = paste(method_estimator, rmse, sep = ': ')) %>%
+  select(size, value, rank) %>%
+  pivot_wider(names_from = rank) %>%
+  kableExtra::kable(booktabs = T, 
+                    digits = 3,
+                    linesep = '',
+                    caption = 'Sample size: Four lowest RMSE methods by sample size for Monte Carlo simulations using dataset 7 from Dorie et al. (2019), 20 replications each')
+
+```
+
+```{r dorie-size-fig, fig.height = 8, fig.cap = 'RMSE of Monte Carlo simulations using dataset 7 from Dorie et al. (2019) with varying sample sizes, 20 replications each'}
+
+text_size = 2.5
+
+# best_methods <- size_plot %>%
+#   group_by(size) %>%
+#   slice_min(rmse, n= 5) %>%
+#   pull(method_estimator) %>%
+#   unique()
+
+best_methods <- size_plot %>%
+  filter(size %in% c(300, 96040)) %>%
+  group_by(size) %>%
+  slice_min(rmse, n= 10) %>%
+  pull(method_estimator) %>%
+  unique()
+
+size_plot %>%
+  # filter(method_estimator %in% best_methods) %>%
+  ggplot(aes(x = size, y = rmse, color = method, linetype = estimator, group = method_estimator)) +
+  geom_line() +
+  ggrepel::geom_text_repel(aes(label = label_min), nudge_x = -1, na.rm = T, 
+                           size = text_size, segment.color = 'transparent') +
+  ggrepel::geom_text_repel(aes(label = label_max), nudge_x = 1, na.rm = T, 
+                           size = text_size, segment.color = 'transparent') +
+  scale_y_continuous(trans='log10', breaks = c(0.1, 0.5, 1, 10, 100)) +
   theme(legend.position = 'none')
@@
 
-## Comparisons using LaLonde NSW Data
-
-As another test, I use data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW), as provided by @dehejia_1999_causal.
+# LaLonde NSW Data
+
+```{r lalonde, fig.height = 8, fig.cap = 'ATE estimates and 95-percent bootstrap standard error confidence intervals for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
+Standard errors shown in parentheses.
+Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
+The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnings in 1974.'}
+# lalonde_means <- read_csv(here('files', 'lalonde_means.csv'))
+
+lalonde_results <- sim_results %>%
+  mutate(set = ifelse(set == 'lalondeCPS-3 74', 'lalonde CPS-3 74', set),
+         set = ifelse(set == 'lalondeCPS-3 original', 'lalonde CPS-3 original', set)) %>%
+  filter(str_detect(set, 'lalonde')) %>%
+  group_by(set, method_estimator, method, estimator) %>%
+  summarize(se = sd(ate),
+            ate = mean(ate)) %>%
+  ungroup() %>%
+  # left_join(select(lalonde_means, estimate = ate, method, estimator, set)) %>%
+  separate_wider_delim(set, delim = ' ', names = c('set', 'sample', 'include_74')) %>%
+  mutate(sample = str_replace(sample, 'experimental', 'Experimental'),
+         sample = factor(sample, levels = c('Experimental', 'CPS-1', 'CPS-3', 'PSID-1', 'PSID-3')),
+         # estimator = factor(estimator, levels = c('ols_logit', 'ols', 'logit', 'grf', 'superlearner')),
+         # method = factor(method, levels = c('ols', 'psm','ipw', 'g-comp', 'lin', 'aipw', 'tmle', 'dml')),
+         include_74 = ifelse(include_74 == '74', 'With 1974 earnings', 'Original LaLonde sample'),
+         lower = estimate - 1.96*se, 
+         upper = estimate + 1.96*se)
+
+            # lower = quantile(ate, .0275),
+            # upper = quantile(ate, .975))
+            # upper = estimate + 1.96*sd(ate),
+            # lower = estimate - 1.96*sd(ate))
+
+lalonde_results %>%
+  mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
+  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator}))) %>%
+  ggplot(aes(x = sample, y = estimate, color = include_74, shape = include_74)) +
+  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(width = .5), size = .3) +
+  geom_hline(yintercept = 0) +
+  facet_wrap(~method_estimator) +
+  labs(x = '', y = '') +
+  coord_cartesian(ylim = c(-5000, 5000)) +
+  theme(axis.text.x=element_text(angle=90, hjust=0.95,vjust=0.3),
+        legend.position = 'bottom') 
+```
+
+As another evaluation of these methods, I use data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW), as provided by @dehejia_1999_causal.
 Between March 1975 and July 1977, the NSW randomly provided training to disadvantaged workers.
@@
 LaLonde compared these experimental estimates to control samples drawn from the Panel Study of Income Dynamics (PSID) and Westat's Matched Current Population Survey-Social Security Administration File (CPS).
-The PSID-1 sample (*n* = `r nrow(lalonde_psid1_controls)`) contains all male household heads under 55 who did not classify themselves as retired in 1975, and the PSID-3 sample (*n* = `r nrow(lalonde_psid3_controls)`) further restricts this to men who were not working in spring of 1976 or 1975.
-The CPS-1 sample (*n* = `r nrow(lalonde_cps1_controls)`) includes all CPS males under 55, and CPS-3 (*n* = `r nrow(lalonde_cps3_controls)`) restricts this two those who were not working in March 1976 whose earnings in 1975 was below the poverty level.
+The PSID-1 sample (*n* = `r nrow(lalonde_psid1_controls)`) contains all male household heads under 55 who did not classify themselves as retired in 1975, and the PSID-3 sample (*n* = `r nrow(lalonde_psid3_controls)`) further restricts this to men who were not working in the spring of 1976 or 1975.
+The CPS-1 sample (*n* = `r nrow(lalonde_cps1_controls)`) includes all CPS males under 55, and CPS-3 (*n* = `r nrow(lalonde_cps3_controls)`) restricts this two those who were not working in March 1976 whose earnings in 1975 were below the poverty level.
 Restricting these observational samples gets closer to the group eligible for the NSW.
@@
 
-I again compare the three double robust methods to a linear model fitted by OLS ("ols") and propensity score matching using logistic regression ("psm").
-Results are presented in Table \@ref(tab:lalonde), Figure \@ref(fig:lalonde-combined), and Figure \@ref(fig:lalonde-combined-1974).
-
-The "experimental" column provides a baseline for the comparison, suggesting that the program resulted in an earnings gain of about \$700 to \$800.
-If selection on observables holds, then we should be able to recover these estimates from the non-experimental control groups.
-Most of the methods do not perform very well; the only ones to estimate a positive treatment effects are OLS for the PSID-3 sample and TMLE for the CPS samples, and these are still smaller than the experimental baselines.
+Results are presented in Figure \@ref(fig:lalonde), with a table in the Appendix (Table 
+\@ref(tab:lalonde-all)).
+Standard errors are based on 100 bootstrap samples.
+We first focus on the original LaLonde dataset, which did not include 1974 earnings.
+The "experimental" estimates provide a baseline for the comparison, suggesting that the program resulted in an earnings gain of about \$800.
+Some methods calculate widely different results for the experimental estimates, highlighting their instability.
+Echoing results from the simulations, methods that include logit models are particularly unstable.
+
+If selection on observables holds, then we should be able to recover experimental estimates from the non-experimental control groups.
+Most of the methods do not perform very well, estimating treatment effects with the wrong sign.
+The exception is in the PSID-3 sample, where 12 of the 17 methods estimate treatment effects with the correct (positive) sign.
+This sample is chosen to be closer to the experimental sample.
 
 Including 1974 earnings data results in much better estimates with the observational control groups.
-For PSID-1, TMLE provides estimates closest to the experimental ones, while DML performs much worse than even OLS.
-For PSID-3, OLS and TMLE both perform well.
-For CPS-1 and CPS-3, TMLE performs the best.
+OLS, PSM, G-computation (SuperLearner), AIPW (SuperLearner), TMLE (SuperLearner), and DML (OLS/logit) compute fairly stable estimates across the samples.
+On the other hand, the estimates produced by IPW (logit), IPW (GRF), IPW (SuperLearner), the Lin estimator, and DML (GRF) vary widely across samples.
 
@@
 Without including 1974 earnings as a covariate, it appears that selection on observables does not hold, as most methods provide highly inaccurate estimates with the wrong sign.
-Once 1974 earnings are included, all of the methods provide estimates much closer to the experimental values.
-PSM, AIPW, and TMLE all do fairly well, while OLS and DML are more unstable across samples.
-
-```{r lalonde-calc-homemade, eval = F}
-
-lalonde_func <- function(dataset, sample, include_74 = F){
-  set.seed(872)
-
-  if(include_74 == F){
-    lalonde_variables <- names(lalonde_exp)[3:9]
-    dataset <- bind_rows(filter(lalonde_exp, treat == 1), dataset)
-
-  } else {
-    lalonde_variables <- names(lalonde_exp_74)[3:10]
-    dataset <- bind_rows(filter(lalonde_exp_74, treat == 1), dataset)
-  }
-
-  dat <- list(y = dataset$re78,
-                z = ifelse(dataset$treat == 1, 'trt', 'ctl'),
-                x = dataset[,lalonde_variables])
-
-  out_list <- list()
-
-  out_list[['ols']] <- data.frame(
-      method = 'ols',
-      estimator = NA,
-      ate = lm_sim(list(dat))$est_df$ate)
-
-  out_list[['psm']] <- data.frame(
-      method = 'psm',
-      estimator = NA,
-      ate = lm_sim(list(dat))$est_df$ate)
-
-  ols_logit_pred_out <- ols_logit_pred(
-    y = dat$y,
-    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-    x = dat$x)
-
-  grf_pred_out <- grf_pred(
-    y = dat$y,
-    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-    x = dat$x)
-
-  superlearner_pred_out <- superlearner_pred(
-    y = dat$y,
-    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-    x = dat$x)
-
-  predictions <- list(ols_logit_pred_out, grf_pred_out, superlearner_pred_out)
-  pred_names <- c('ols_logit', 'grf', 'superlearner')
-  for(j in 1:length(predictions)){
-    aipw_out <- with(predictions[[j]], 
-                     aipw_calc_trunc(mu1_pred = mu1_pred, 
-                               mu0_pred = mu0_pred,
-                               pi_pred = pi_pred,
-                               d = d,
-                               y = y))
-
-    out_list[[paste0('aipw', j)]] <- data.frame(
-      method = 'aipw',
-      estimator = pred_names[[j]],
-      ate = aipw_out)
-
-    tmle_out <- with(predictions[[j]], 
-                       tmle_calc(mu1_pred = normalize(mu1_pred, y), 
-                                 mu0_pred = normalize(mu0_pred, y),
-                                 pi_pred = pi_pred,
-                                 d = d,
-                                 y = normalize(y, y))
-                       )
-
-      out_list[[paste0('tmle', j)]] <- data.frame(
-        method = 'tmle',
-        estimator = pred_names[[j]],
-        ate =  denormalize(tmle_out, predictions[[j]]$y))
-  }
-
-  dml_pre_out <- dml_pre(dat$y,
-                         as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-                         x = dat$x)
-  ols_logit_dml_out <- do.call(ols_logit_dml, dml_pre_out)
-  dml_post_out <- do.call(dml_post, append(dml_pre_out, ols_logit_dml_out))
-
-  out_list[['dml_ols_logit']] <- data.frame(method = 'dml',
-                                            estimator = 'ols_logit',
-                                            ate = dml_post_out)
-
-  dml_pre_out <- dml_pre(dat$y,
-                     as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-                     x = dat$x)
-  grf_dml_out <- do.call(ols_logit_dml, dml_pre_out)
-  dml_post_out <- do.call(dml_post, append(dml_pre_out, grf_dml_out))
-
-  out_list[['dml_grf']] <- data.frame(method = 'dml',
-                                            estimator = 'grf',
-                                            ate = dml_post_out)
-
-  dml_pre_out <- dml_pre(dat$y,
-                     as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-                     x = dat$x)
-  superlearner_dml_out <- do.call(ols_logit_dml, dml_pre_out)
-  dml_post_out <- do.call(dml_post, append(dml_pre_out, superlearner_dml_out))
-
-  out_list[['dml_superlearner']] <- data.frame(method = 'dml',
-                                            estimator = 'superlearner',
-                                            ate = dml_post_out)
-
-  bind_rows(out_list) %>%
-    mutate(sample = sample) %>%
-    return()
-}
-
-lalonde_func_out <- bind_rows(
-  lalonde_func(filter(lalonde_exp, treat == 0), sample = 'experimental'),
-  lalonde_func(lalonde_psid1_controls, 'PSID-1'),
-  lalonde_func(lalonde_psid3_controls, 'PSID-3'),
-  lalonde_func(lalonde_cps1_controls, 'CPS-1'),
-  lalonde_func(lalonde_cps1_controls, 'CPS-3'))
-
-  lalonde_func_out %>%
-    pivot_wider(names_from = 'sample', values_from = ate) %>%
-  mutate(estimator = factor(estimator, levels = c('ols_logit', 'grf', 'superlearner')),
-         method = factor(method, levels = c('ols', 'psm', 'aipw', 'aipw (trim)', 'tmle', 'dml'))) %>%
-  arrange(method, estimator) %>%
-  #write_csv(here('files/homemade', 'lalonde.csv'))
-
-bind_rows(
-  lalonde_func(filter(lalonde_exp_74, treat == 0), sample = 'experimental', T),
-  lalonde_func(lalonde_psid1_controls, 'PSID-1', T),
-  lalonde_func(lalonde_psid3_controls, 'PSID-3', T),
-  lalonde_func(lalonde_cps1_controls, 'CPS-1', T),
-  lalonde_func(lalonde_cps1_controls, 'CPS-3', T)) %>%
-    pivot_wider(names_from = 'sample', values_from = estimate) %>%
-  write_csv(here('files/homemade', 'lalonde_74.csv'))
-
-```
-
-```{r lalonde-calc, eval = F}
-unemp_func <- function(x){
-  x %>%
-    as.data.frame() %>%
-    mutate(re74_0 = re74 == 0,
-         re75_0 = re75 == 0) 
-}
-
-lalonde_exp <- read_dta(here('data', 'nsw.dta')) %>%
-  as.data.frame() %>%
-  mutate(re75_0 = re75 == 0)
-lalonde_exp_74 <- read_dta(here('data', 'nsw_dw.dta')) %>%
-  unemp_func()
-lalonde_cps1_controls <- read_dta(here('data', 'cps_controls.dta')) %>%
-  unemp_func()
-lalonde_cps3_controls <- read_dta(here('data', 'cps_controls3.dta')) %>%
-  unemp_func()
-lalonde_psid1_controls <- read_dta(here('data', 'psid_controls.dta')) %>%
-  unemp_func()
-lalonde_psid3_controls <- read_dta(here('data', 'psid_controls3.dta')) %>%
-  unemp_func()
-
-lalonde_func <- function(dataset, sample, include_74 = F){
-  set.seed(872)
-
-  if(include_74 == F){
-    lalonde_variables <- names(lalonde_exp)[3:9]
-    dataset <- bind_rows(filter(lalonde_exp, treat == 1), dataset)
-
-  } else {
-    lalonde_variables <- names(lalonde_exp_74)[3:10]
-    dataset <- bind_rows(filter(lalonde_exp_74, treat == 1), dataset)
-  }
-
-  dataset <- list(list(y = dataset$re78,
-                z = ifelse(dataset$treat == 1, 'trt', 'ctl'),
-                x = dataset[,lalonde_variables]))
-
-  lapply(list(
-    lm_sim(dataset),
-    psm_sim(dataset),
-    aipw_sim(dataset),
-    tmle_sim(dataset),
-    dml_sim(dataset)),
-  bind_cols) %>%
-    bind_rows() %>%
-    mutate(method = c('ols', 'psm', 'aipw', 'tmle', 'dml'),
-           sample = sample,
-           ate = round(d),
-           se = round(se),
-           estimate = paste0(round(d), ' (', round(se), ')')) %>%
-    select(method, sample, estimate) 
-}
-
-bind_rows(
-  lalonde_func(filter(lalonde_exp, treat == 0), sample = 'experimental'),
-  lalonde_func(lalonde_psid1_controls, 'PSID-1'),
-  lalonde_func(lalonde_psid3_controls, 'PSID-3'),
-  lalonde_func(lalonde_cps1_controls, 'CPS-1'),
-  lalonde_func(lalonde_cps1_controls, 'CPS-3')) %>%
-    pivot_wider(names_from = 'sample', values_from = estimate) %>%
-  write_csv(here('files', 'lalonde.csv'))
-
-bind_rows(
-  lalonde_func(filter(lalonde_exp_74, treat == 0), sample = 'experimental', T),
-  lalonde_func(lalonde_psid1_controls, 'PSID-1', T),
-  lalonde_func(lalonde_psid3_controls, 'PSID-3', T),
-  lalonde_func(lalonde_cps1_controls, 'CPS-1', T),
-  lalonde_func(lalonde_cps1_controls, 'CPS-3', T)) %>%
-    pivot_wider(names_from = 'sample', values_from = estimate) %>%
-  write_csv(here('files', 'lalonde_74.csv'))
-```
-
-```{r lalonde, eval = F}
-bind_rows(
-  read_csv(here('files', 'lalonde.csv')) %>%
-    mutate(sample = 'Original LaLonde'),
-  read_csv(here('files', 'lalonde_74.csv')) %>%
-    mutate(sample = 'With 1974 earnings')) %>%
-  select(sample, method, everything()) %>%
-  kableExtra::kable(booktabs = T, 
-                    # digits = 3,
-                    # linesep = '',
-                    caption = 'ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
-Standard errors shown in parentheses.
-Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
-The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnigns in 1974.')
-
-# bind_rows(
-#   read_csv(here('files', 'lalonde.csv')) %>%
-#     mutate(sample = 'LaLonde'),
-#   read_csv(here('files', 'lalonde_74.csv')) %>%
-#     mutate(sample = 'DW (with 1974 earnings)')) %>%
-#   select(sample, everything()) %>%
-#   kableExtra::kable(booktabs = T, 
-#                     # digits = 3,
-#                     linesep = '',
-#                     caption = 'ATE estimates for Lalonde NSW data from Dehejia and Wahba (1999), with PSID ')
-
-# lalonde_exp_df <- filter(lalonde, exper == 1)
-# fit <- CBPS::CBPS(treat ~ age + educ + re75 + re74 + 
-# 			I(re75==0) + I(re74==0), 
-# 			data = lalonde_exp_df, ATT = TRUE)
-# summary(fit)
-# m.out <- MatchIt::matchit(treat ~ fitted(fit), method = "nearest", 
-# 				 data = lalonde_exp_df, replace = TRUE)
-# lm(re78 ~ treat + age + educ + re75 + re74, MatchIt::match.data(m.out), weights = weights) %>%
-#   tidy()
-# 
-# 
-# lalonde_psid_df <- filter(lalonde, (exper == 1 & treat == 1) | exper == 0)
-# fit <- CBPS::CBPS(treat ~ age + educ + re75 + re74 + 
-# 			I(re75==0) + I(re74==0), 
-# 			data = lalonde_psid_df, ATT = TRUE)
-# m.out <- MatchIt::matchit(treat ~ fitted(fit), method = "nearest", 
-# 				 data = lalonde_psid_df, replace = TRUE)
-# lm(re78 ~ treat + age + educ + re75 + re74, MatchIt::match.data(m.out), weights = weights) %>%
-#   tidy()
-```
-
-```{r lalonde-combined, eval = F, fig.cap = 'ATE estimates and 95% confidence intervals for Lalonde NSW data (original sample) as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.'}
-lalonde_df <- bind_rows(
-  read_csv(here('files', 'lalonde.csv')) %>%
-    mutate(sample = 'Original LaLonde'),
-  read_csv(here('files', 'lalonde_74.csv')) %>%
-    mutate(sample = 'With 1974 earnings')) %>%
-  select(sample, method, everything()) %>%
-  pivot_longer(-c(sample, method)) %>%
-  separate_wider_delim(value, delim = '(', names = c('ate', 'se')) %>%
-  separate_wider_delim(se, delim = ')', names = c('se', 'blank')) %>%
-  mutate(ate = as.numeric(ate), 
-         se = as.numeric(se),
-         method = factor(method, levels = unique({.$method})),
-         name = factor(name, levels = unique({.$name})),
-         experimental = name == 'experimental') %>%
-  select(-blank)
-
-lalonde_df %>%
-  filter(sample == 'Original LaLonde') %>%
-  ggplot(aes(x = name, y = ate, color = experimental)) +
-  geom_pointrange(aes(ymin = ate - 1.96*se, ymax = ate + 1.96*se)) +
-  geom_hline(yintercept = 0) +
-  facet_wrap(~method, scales = 'free_x') +
-  theme(axis.text.x=element_text(angle=-15), 
-        legend.position = 'none') +
-  scale_color_manual(values = ucla_palette) +
-  labs(title = 'Original LaLonde Sample', x = '')   
-```
-
-```{r lalonde-combined-1974, eval = F, fig.cap = 'ATE estimates and 95% confidence intervals for Lalonde NSW data (with 1974 earnings) as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.'}
-lalonde_df %>%
-  filter(sample == 'With 1974 earnings') %>%
-  ggplot(aes(x = name, y = ate, color = experimental)) +
-  geom_pointrange(aes(ymin = ate - 1.96*se, ymax = ate + 1.96*se)) +
-  geom_hline(yintercept = 0) +
-  facet_wrap(~method, scales = 'free_x') +
-  theme(axis.text.x=element_text(angle=-15), 
-        legend.position = 'none') +
-  scale_color_manual(values = ucla_palette) +
-  labs(title = 'With 1974 earnings', x = '')
-```
-
-```{r lalonde-traditional}
-lalonde_results <- sim_results %>%
-  mutate(set = ifelse(set == 'lalondeCPS-3 74', 'lalonde CPS-3 74', set),
-         set = ifelse(set == 'lalondeCPS-3 original', 'lalonde CPS-3 original', set)) %>%
-  filter(str_detect(set, 'lalonde')) %>%
-  separate_wider_delim(set, delim = ' ', names = c('set', 'sample', 'include_74')) %>%
-  mutate(sample = factor(sample, levels = unique({.$sample})),
-         estimator = factor(estimator, levels = c('ols_logit', 'ols', 'logit', 'grf', 'superlearner')),
-         method = factor(method, levels = c('ols', 'psm', 'lin', 'ipw', 'g-comp', 'aipw', 'tmle', 'dml')))
-
-lalonde_results_df <- lalonde_results %>%
-  group_by(set, sample, include_74, method_estimator) %>%
-  summarize(estimate = mean(ate),
-            se = sd(ate)) %>%
-  ungroup() %>%
-  mutate(value = paste0(round(estimate), ' (', round(se), ')')) %>%
-  select(include_74, sample, method_estimator, value) %>%
-  pivot_wider(values_from = value, names_from = method_estimator) %>%
-  arrange(desc(include_74))
-
-lalonde_results_df %>%
-  select(include_74:`g-comp, superlearner`) %>%
-  kableExtra::kable(booktabs = T, 
-                    # digits = 3,
-                    # linesep = '',
-                    caption = 'Traditional methods: ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
-Standard errors shown in parentheses.
-Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
-The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnigns in 1974.')
-```
-
-```{r lalonde-dr}
-lalonde_results_df %>%
-  select(include_74, sample, `g-comp, superlearner`:`dml, superlearner`) %>%
-  kableExtra::kable(booktabs = T, 
-                    # digits = 3,
-                    # linesep = '',
-                    caption = 'Double robust methods: ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
-Standard errors shown in parentheses.
-Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
-The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnigns in 1974.')
-```
+Once 1974 earnings are included, most of the methods provide estimates much closer to the experimental values.
 
@@
 
-This paper aimed to provide an introduction to and evaluation of double robust methods for covariate adjustment in causal inference.
-By comparing AIPW, TMLE, and DML to the more traditional statistical methods of OLS and PSM, it allows evaluation of whether these methods are worth the effort and (computational) time for social scientists to adopt them.
-
-Results are mixed.
-On the one hand, in the full range of simulated data, AIPW with GRF estimators achieves the lowest bias and root mean squared error.
-This is the simplest (and most computationally efficient) of the double robust methods, although GRF is computationally expensive.
-TMLE with GRF also does fairly well.
-But OLS and PSM have strong showings, in the top three smallest bias or root mean squared error.
-In the datasets with linear data-generating processes, OLS achieves the lowest bias and root mean squared error.
-
-In the experimental LaLonde data, OLS does not perform as strongly.
-Although it is one of the few methods to provide experimental estimates with the correct sign in the original LaLonde set of covariates, its estimates are highly unstable across samples.
-When 1974 earnings are used as a covariate, PSM, AIPW, and TMLE all perform fairly well, though TMLE comes out on top.
-
-Overall, these double robust methods do not show a clear advantage over simpler, more computationally efficient methods such as OLS and PSM.
-While they are useful for social scientists to understand, in most applications, OLS or PSM provide similar results.
+This paper aims to provide an introduction to and evaluation of double robust methods for covariate adjustment in causal inference.
+By comparing AIPW, TMLE, and DML to more traditional statistical methods such as OLS and PSM as well as flexible "single robust" methods such as G-computation and the Lin estimator, it allows evaluation of whether these methods are worth the effort and (computational) time for social scientists to adopt them.
+
+Results are nuanced.
+In the full range of simulated data, AIPW and TMLE with a SuperLearner or GRF are able to obtain smaller RMSE than OLS or PSM.
+However these differences are quite small, and G-computation with the same flexible machine learning methods performs just as well as the double robust methods.
+DML does not perform as well as AIPW or TMLE.
+The Lin estimator performs slightly better than OLS or PSM, without any increase in computation time.
+Methods relying on logit models to estimate probability weights have the most error; researchers should use these methods with caution.
+
+Methods that come out on top in the full range of simulations also tend to do the best regardless of the data generating process, though the Lin estimator and OLS rise in the rankings when the true treatment and outcome models are linear.
+AIPW, TMLE, and G-computation with a SuperLearner or GRF perform the best, followed closely by the Lin estimator, OLS, and PSM.
+As sample size varies, the same rank order generally holds, though traditional methods are unable to produce estimates in small samples when there are many covariates, while the double robust methods are able to do so.
+
+Results from the experimental LaLonde data are more difficult to interpret.
+The sample appears much more important than the choice of method.
+In the original LaLonde data, most methods fail to estimate treatment effects in the observational data with the same sign as the experimental estimate.
+The exception is the PSID-3 sample, which includes only men who were not working in the spring of 1976 or 1975 and is thus more comparable to the individuals were recruited to the NSW study.
+When 1974 earnings are included as a covariate, many of the methods provide estimates across samples that are close to the experimental estimates.
+OLS, PSM, G-computation (SuperLearner), AIPW (SuperLearner), TMLE (SuperLearner), and DML (OLS/logit) appear the most reliable, while IPW (logit), IPW (GRF), IPW (SuperLearner), the Lin estimator, and DML (GRF) prove unstable.
+It is surprising that the Lin estimator provides unstable results in the NSW data, while it is among the lowest-RMSE methods in the simulation study.
+This highlights the complexity of doing causal inference with observational data where ignorability may not hold.
+
+This paper has a number of limitations.
+First, although it considers some of the most popular double robust, machine learning, traditional, and single robust methods, there are many methods that it could not evaluate.
+Second, although the simulations are meant to cover a wide range of data generating processes, they only consider continuous outcomes and binary treatments; simulations with binary or categorical outcomes and continuous or multi-armed treatments may yield different results.
+Finally, the simulations in this paper do not consider situations where ignorability does not hold.
+In particular, it does not evaluate situations where causal identification is misspecified [@keil_2018_resolving].
+Future research should assess violations of this and other assumptions underlying these methods.
+
+In conclusion, if researchers want small gains in accuracy, they may opt for AIPW, TMLE, or G-computation with a flexible machine learning algorithm.
+But these methods are computationally costly, taking over two minutes per dataset of 4,802 observations and 52 covariates, while OLS, PSM, and the Lin estimator each take a fraction of a second.
+While double robust methods are useful for social scientists to understand, in most applications, OLS or PSM provide similar results.
 However, in certain circumstances these double robust methods may be a better choice.
-Especially when paired with a highly flexible estimator like GRF, these methods can be useful when the number of covariates is high or even exceeds the number of observations.
-If the researcher believes the data-generating process is highly nonlinear, they may also be a good a choice, at least as a sensitivity check.
-
-This paper has a number of limitations.
-First, it does not consider situations where ignorability does not hold.
-@hunermund_2023_double evaluate a case of this, where endogenous variables are included in the covariate space, showing this can result in biased estimates from DML.
+Especially when paired with a highly flexible estimator like a SuperLearner or GRF, these methods may be slightly more accurate, and they can be useful when the number of covariates is high or even exceeds the number of observations.
+They can also be useful as a sensitivity check; if researchers obtain similar estimates across traditional and double robust methods, they can be more confident in the reliability of their estimates.
 
@@
 sim_results %>%
+  # bind_rows(mutate(aipw_df, method = as.factor('aipw (original)'))) %>%
   filter(set == 'main') %>%
@@
                     linesep = '',
-                    caption = 'Results of Monte Carlo simulations using the first 20 datasets from Dorie et al.
+                    caption = 'Main datasets: Results of Monte Carlo simulations using the first 20 datasets from Dorie et al.
 (2019), 10 replications each.
-Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is average computation time measured in seconds for each dataset.') %>%
+Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is median computation time measured in seconds for each dataset.') %>%
   kable_styling(latex_options = c("hold_position"))
@@
 
-```{r dorie-results-linear}
+```{r dorie-linear-results}
 sim_results %>%
   filter(set == 'linear') %>%
+  # bind_rows(mutate(aipw_df, method = as.factor('aipw (original)'))) %>%
   group_by(estimator, method) %>%
@@
                     linesep = '',
-                    caption = 'Results of Monte Carlo simulations using the two datasets from Dorie et al.
+                    caption = 'Linear datasets: Results of Monte Carlo simulations using the two datasets from Dorie et al.
 (2019), with linear data generating processes, 100 replications each ("linear").
-Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is average computation time measured in seconds for each dataset.') %>%
+Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is median computation time measured in seconds for each dataset.') %>%
   kable_styling(latex_options = c("hold_position"))
@@
                     longtable = T,
-                    caption = 'Results of Monte Carlo simulations using dataset 7 from Dorie et al.
+                    caption = 'Sample size: Results of Monte Carlo simulations using dataset 7 from Dorie et al.
 (2019) with varying sample sizes, 20 replications each.
-Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is average computation time measured in seconds for each dataset.') %>%
+Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is median computation time measured in seconds for each dataset.') %>%
   kable_styling(latex_options = c("hold_position")) #'repeat_header')) 
 ```
+
+\newpage
+
+```{r lalonde-all}
+# lalonde_results <- sim_results %>%
+#   mutate(set = ifelse(set == 'lalondeCPS-3 74', 'lalonde CPS-3 74', set),
+#          set = ifelse(set == 'lalondeCPS-3 original', 'lalonde CPS-3 original', set)) %>%
+#   filter(str_detect(set, 'lalonde')) %>%
+#   separate_wider_delim(set, delim = ' ', names = c('set', 'sample', 'include_74')) %>%
+#   mutate(sample = factor(sample, levels = unique({.$sample})),
+#          include_74 = ifelse(include_74 == 'original', 'No', "Yes"))
+
+lalonde_results %>%
+  mutate(include_74 = ifelse(include_74 == 'With 1974 earnings', 'Yes', 'No')) %>%
+  # group_by(set, sample, include_74, method_estimator) %>%
+  # summarize(estimate = mean(ate),
+  #           se = sd(ate)) %>%
+  # ungroup() %>%
+  mutate(value = paste0(round(estimate), ' (', round(se), ')')) %>%
+  select(`'74 earnings?` = include_74, Sample = sample, Method = method_estimator, value) %>%
+  arrange(Sample) %>%
+  pivot_wider(values_from = value, names_from = Sample) %>%
+  arrange(`'74 earnings?`, Method) %>%
+  mutate(Method = str_replace(Method, 'superlearner', 'superl.')) %>%
+  kableExtra::kable(booktabs = T, 
+                    # digits = 3,
+                    linesep = '',
+                    caption = 'ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
+Bootstrap standard errors shown in parentheses.
+Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
+The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnings in 1974.') %>%
+  kable_styling(latex_options = c("hold_position")) 
+```
+
+```{r lalonde-traditional, eval = F}
+lalonde_results <- sim_results %>%
+  mutate(set = ifelse(set == 'lalondeCPS-3 74', 'lalonde CPS-3 74', set),
+         set = ifelse(set == 'lalondeCPS-3 original', 'lalonde CPS-3 original', set)) %>%
+  filter(str_detect(set, 'lalonde')) %>%
+  separate_wider_delim(set, delim = ' ', names = c('set', 'sample', 'include_74')) %>%
+  mutate(sample = factor(sample, levels = unique({.$sample})),
+         estimator = factor(estimator, levels = c('ols_logit', 'ols', 'logit', 'grf', 'superlearner')),
+         method = factor(method, levels = c('ols', 'psm','ipw', 'g-comp', 'lin', 'aipw', 'tmle', 'dml')))
+
+lalonde_results_df <- lalonde_results %>%
+  group_by(set, sample, include_74, method_estimator) %>%
+  summarize(estimate = mean(ate),
+            se = sd(ate)) %>%
+  ungroup() %>%
+  mutate(value = paste0(round(estimate), ' (', round(se), ')')) %>%
+  select(include_74, sample, method_estimator, value) %>%
+  pivot_wider(values_from = value, names_from = method_estimator) %>%
+  arrange(desc(include_74))
+
+lalonde_results_df %>%
+  select(include_74:`lin`) %>%
+  kableExtra::kable(booktabs = T, 
+                    # digits = 3,
+                    # linesep = '',
+                    caption = 'Traditional methods: ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
+Bootstrap standard errors shown in parentheses.
+Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
+The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnings in 1974.') %>%
+  kable_styling(latex_options = c("hold_position")) 
+```
+
+```{r lalonde-dr, eval = F}
+lalonde_results_df %>%
+  select(include_74, sample, `aipw, ols_logit`:`dml, superlearner`) %>%
+  kableExtra::kable(booktabs = T, 
+                    # digits = 3,
+                    # linesep = '',
+                    caption = 'Double robust methods: ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
+Bootstrap standard errors shown in parentheses.
+Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
+The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnings in 1974.') %>%
+  kable_styling(latex_options = c("hold_position")) 
+```

### 2024-07-02 draft/ms-adj-draft.Rmd
filed version

@@
     toc: no
-    number_sections: yes
+    keep_tex: true
+    number_sections: no
     pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
@@
 #fontfamily: mathpazo
-#fontsize: 11pt
+# fontsize: 12pt
 # geometry: margin=.6in
@@
 date: "`r format(Sys.time(), '%B %e, %Y')`"
+
+thanks: "I deeply thank  my committee -- Chad Hazlett, Onyebuchi A.
+Arah, Jennie E.
+Brand -- for their extensive suggestions and advice on previous drafts.
+I would also like to thank the members of UCLA's Practical Causal Inference Lab, UCLA's Social Inequality Data Science Lab, participants of the 2023 American Sociological Association's Annual Meeting, and participants of the 2024 All-UC Demography Conference for their feedback on previous versions of this paper."
 
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T)
+knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T, dev = c('pdf', 'png'), fig.retina = 3)
 options("yaml.eval.expr" = TRUE)
@@
 
-  epsilon <- glm(y ~ -1 + H0 + H1 + offset(qlogis((d==1)*mu1_pred + (d==0)*mu0_pred)),
+  epsilon <- glm(y ~ -1 + H0 + H1 + offset(qlogis((d==1)*mu1_pred 
+                    + (d==0)*mu0_pred)),
                  family = binomial(link = 'logit')) %>%
@@
 
-In causal inference, misspecification of underlying models can bias estimates of treatment effects [@hernan_2020_causal; @morgan_2015_counterfactuals].
+In causal inference, functional form misspecification of underlying models can bias estimates of treatment effects [@hernan_2020_causal; @morgan_2015_counterfactuals].
 There have been two important developments that attempt to overcome this.
@@
 The second development is double robust methods [@bang_2005_doubly; @kang_2007_demystifying], which estimate two models: one for treatment exposure and another for the outcome.
-These models are robust to misspecification of either one of these models.
+These models are robust to misspecification of either one of these "nuisance" models.
 
 A number methods unifying these two developments have proliferated.
-These double robust methods for flexible covariate adjustment use machine learning methods to adapatively model the data generating processes.
+These double robust methods for flexible covariate adjustment use machine learning methods to adapatively model the data generating processes at play.
 These models purportedly overcome the shortcomings of both traditional statistical methods and machine learning methods.
@@
 They are then used to estimate experimental and observational effects from real-world data, the National Support for Work Demonstration (NSW) originally analyzed by @lalonde_1986_evaluating.
-In these evaluations, double robust methods are compared to "single robust" single robust methods.
+In these evaluations, double robust methods are compared to "single robust" methods (i.e., ones with one nuisance model).
 These include traditional or simpler statistical methods commonly used by social scientists: ordinary least squares (OLS) regression, matching on propensity scores estimated from logistic regression (PSM), and inverse probability weighting (IPW).
@@
 
-Although previous work has compared different methods for covariate adjustment, there has not yet been a thorough evaluation and comparison of the recent and popular double robust methods of AIPW, TMLE, and DML for a social scientist audience.
+Although previous work has compared different methods for covariate adjustment, there has not yet been a thorough comparison and evaluation of the recent and popular double robust methods of AIPW, TMLE, and DML for a social scientist audience.
 
@@
 @bang_2005_doubly introduce double robust models for both causal inference and missing data, but their treatment is rather technical, and they only discuss AIPW.
-
-Evaluations of double robust methods have focused on only one double robust method and compare to few traditional statistical methods.
+@lundberg_2022_researcher provide brief schematic overviews of double robust methods for a social scientist audience, but they do not evaluate these methods.
+
+Existing evaluations of double robust methods have focused on only one double robust method and compared it to few traditional statistical methods.
 @dorie_2019_automated compare estimations from a number of different flexible methods, but these do not include AIPW or DML.
@@
 @cousineau_2022_estimating evaluates the performance of optimization-based methods for causal inference, but these do not include the double robust methods covered in the current paper.
-@knaus_2022_double reviews double robust methods in an econometrics setting but does not compare them to traditional statistical methods for covariate adjustment.
+@knaus_2022_double reviews DML-based methods in an econometrics setting but does not compare them to traditional statistical methods for covariate adjustment.
 
 An evaluation of multiple double robust methods that compares them to traditional statistical methods as well as flexible "single robust" methods is needed to understand just how practically useful these methods are for a social science audience.
-This paper endeavors to do this and to provide a gentle introduction to these methods.
+This paper does this as well as provides a gentle introduction to these methods.
 
@@
 ## Aims of Double Robust Methods
-Double robust methods for covariate adjustment aim to overcome what many consider to be the shortcomings of both traditional statistical methods and flexible machine learning methods.
+Double robust methods for covariate adjustment aim to overcome what many consider to be the shortcomings of both traditional statistical methods and flexible machine learning methods [@diaz_2020_machine].
 Statistical methods that are popular with social scientists -- such as OLS regression and matching on propensity scores from logistic regression -- have two main weaknesses that double robust methods address.
@@
 In the presence of highly nonlinear data generating processes, they may provide biased estimates.
-Second, these methods cannot handle large numbers of covariates relative to sample size.
+Second, these methods cannot handle large numbers of covariates relative to sample size, i.e.
+sparsity.
 While some machine learning methods can produce estimates even when the number of covariates exceeds the number of observations (such as lasso), OLS fails in this case due to the $X^\top X$ matrix not being of full rank and hence not invertible.
@@
 First, naive application of these methods can result in overfitting, with predictive accuracy maximized in sample but treatment effect estimation being biased.
+When regularization is used to correct for overfitting, "regularization bias" can result.
 Furthermore, results of these machine learning methods can be difficult to interpret without further processing.
@@
 
-Double robust methods attempt to overcome the downsides of both traditional and machine learning methods by incorporating flexible models into a framework that avoids overfitting and provides easily interpretable estimates.
+Double robust methods attempt to overcome the downsides of both traditional and machine learning methods by incorporating flexible models into a framework that avoids overfitting and regularization bias and provides easily interpretable estimates.
 These methods are also motivated by the idea that many older methods ignore information present in the data.
-Methods tend to model either the outcome -- as in OLS regression and G-computation -- or only the treatment assignment -- as in propensity score matching or inverse probability weighting.
+Methods tend to model either only the outcome -- as in OLS regression and G-computation -- or only the treatment assignment -- as in propensity score matching or inverse probability weighting.
 Double robust methods, on the other hand, model both of these.
@@
 The focus of this paper is on the average treatment effect (ATE), which under the potential outcomes framework [@rubin_1974_estimating] is defined as
-$$\tau = E[Y_i(1) - Y_i(0)]$$
+$$\tau = E[Y_i(1) - Y_i(0)],$$
 where $Y_i(1)$ and $Y_i(0)$ are the potential outcomes of $Y_i$ under treatment and control, respectively.
@@
 
-It is important to consider what is meant by a "correct" model [@keil_2018_resolving].
+It is important to consider what is meant by a "correct" model specification [@keil_2018_resolving].
 These estimators are robust from a statistical standpoint, but not necessarily a causal identification one.
@@
 Extending and improving previous double robust methods, @vanderlaan_2006_targeted first proposed TMLE using a parametric framework and the efficient influence curve [@hines_2022_demystifying] to obtain estimates and standard errors.
-Mark van der Laan has gone on to collaborate on both a gentle introduction [@gruber_2009_targeted], a textbook [@vanderlaan_2011_targeted], and an R package [@gruber_2012_tmle] for implementing the method.
+Mark van der Laan has gone on to collaborate on both a gentle introduction [@gruber_2009_targeted], two textbooks [@vanderlaan_2011_targeted; @vanderlaan_2018_targeted], and an R package [@gruber_2012_tmle] for implementing the method.
 @schuler_2017_targeted and @luque-fernandez_2018_targeted provide introductions for epidemiologists.
@@
 
-More formally, suppose we want to estimate $\tau$ in the following framework:
+More formally, suppose we want to estimate $\tau$ in the following framework:^[Note that this basic DML setup assumes a partially linear model and targets the ATE.
+If we are interested in the CATE and heterogeneous effects, Chernozhukov et al.
+[-@chernozhukov_2018_double, p.
+C35] present an alternative score function that closely resembles AIPW.
+See also @jacob_2021_cate and @nie_2021_quasioracle.]
 $$y_i = \tau d_i + g_0(\mathbf x_i) + u_i,$$
@@
 
-The idea is to estimate $g_0$ and $m_0$ separately, then use residual-on-residual regression to obtain an estimate of $\tau$, which we can designate $\hat \tau$.
-However this leaves a term in the asymptotic distribution of $\hat \tau$ that biases the estimate.
+The idea is to estimate $g_0$ and $m_0$ separately, then use an orthogonalized or debiased score function -- here, residual-on-residual regression -- to obtain an estimate of $\tau$, which we can designate $\hat \tau$.
+However, this leaves a term in the asymptotic distribution of $\hat \tau$ that biases the estimate.
 To avoid this, DML uses sample splitting [@angrist_1995_splitsample].
 
-We randomly split the sample of $n$ observations into two sets, $I$ and $I^c$, each of size $n/2$.
-Using any prediction algorithm, we then estimate the response and treatment models using only set $I^c$:
+We randomly split the sample of $n$ observations into two sets, $I$ and $I^c$, each of size $n/2$.^[In practice, we can split the sample into any number of folds, and more than two sets might be better.] Using any prediction algorithm, we then estimate the response and treatment models using only set $I^c$:
 
@@
 
-Note that the estimation of the outcome does not consider treatment assignment $d_i$. This is a key difference between DML and AIPW or TMLE.
+<!-- Note that, in this setup, the estimation of the outcome does not consider treatment assignment $d_i$. This is a key difference between DML and AIPW or TMLE.   -->
 
@@
 
-The three double robust methods are compared to two sets of traditional or "single robust" methods used as benchmarks.
+```{r methods-overview}
+
+read_csv(here('files/methods.csv')) %>%
+  huxtable::hux() %>%
+  huxtable::theme_article() %>%
+  huxtable::set_width(1) %>%
+  # huxtable::set_all_padding(0) %>%
+  # huxtable::set_latex_float('h!') %>%
+  huxtable::set_caption('Double and single robust methods used for evaluation')
+
+  # pander::pander(split.cell = 15, split.table = Inf, 
+  #                justify = 'left',
+  #                caption = 'Double and single robust methods used for evaluation',
+  #                label = 'methods-overview') 
+  # kable(booktabs = T, linesep = '', caption = 'Double and single robust methods used for evaluation') %>%
+  # kable_styling(latex_options = c("hold_position"))
+
+```
+
+The three double robust methods are compared to two sets of traditional or "single robust" methods used as benchmarks (see Table \@ref(tab:methods-overview) for an overview of all methods used).
 By "single robust," I mean methods that are not robust to any misspecification.
@@
 
+ggsave(here('draft/figures', 'dorie-results-bias.png'), width = 7,  height = 5.5, dpi = 600)
 ```
@@
 
+ggsave(here('draft/figures', 'dorie-results-rmse.png'), width = 7,  height = 5.5, dpi = 600)
 ```
@@
         legend.position = 'none')
+
+ggsave(here('draft/figures', 'dorie-linear-bias.png'), width = 7,  height = 5.5, dpi = 600)
 ```
@@
   ylim(c(-4, 4))
+
+ggsave(here('draft/figures', 'dorie-linear-rmse.png'), width = 7,  height = 5.5, dpi = 600)
 ```
@@
 While the AIPW, TMLE, and G-computation with a SuperLearner may be the top performing methods overall, this does not mean that there are some data-generating processes (DGPs) where some other method may do better.
-Across the the 20 datasets, @dorie_2019_automated vary six DGP characteristics: degree of nonlinearity, the percentage treated, overlap for the treatment group, alignment (correspondence in variables used to generate the exposure and response models), and treatment effect heterogeneity.
+Across the the 20 datasets, @dorie_2019_automated vary five DGP characteristics: degree of nonlinearity, the percentage treated, overlap for the treatment group, alignment (correspondence in variables used to generate the exposure and response models), and treatment effect heterogeneity.
 To test how the methods perform across different values of these characteristics, I begin with the 200 simulations from the 20 datasets used in the main results (Figures \@ref(fig:dorie-results-bias) and \@ref(fig:dorie-results-rmse), Table \@ref(tab:dorie-results-table)).
@@
   summarize(se = sd(ate),
-            ate = mean(ate)) %>%
+            estimate = mean(ate)) %>%
   ungroup() %>%
@@
   theme(axis.text.x=element_text(angle=90, hjust=0.95,vjust=0.3),
-        legend.position = 'bottom') 
+        legend.position = 'bottom')  +
+  labs(title = 'Results for Lalonde NSW data, with CPS and PSID comparison groups')
+
+ggsave(here('draft/figures', 'lalonde.png'), width = 18,  height = 8, dpi = 1200)
 ```
@@
 However these differences are quite small, and G-computation with the same flexible machine learning methods performs just as well as the double robust methods.
-DML does not perform as well as AIPW or TMLE.
+DML does not perform as well as AIPW or TMLE (however, a version of DML that allows for heterogeneous effects might perform better; see Chernozhukov et al.
+[-@chernozhukov_2018_double, p.
+C35]).
 The Lin estimator performs slightly better than OLS or PSM, without any increase in computation time.
-Methods relying on logit models to estimate probability weights have the most error; researchers should use these methods with caution.
+Methods relying on logit models to estimate propensity weights have the most error; researchers should use these methods with caution.
 
@@
 This paper has a number of limitations.
-First, although it considers some of the most popular double robust, machine learning, traditional, and single robust methods, there are many methods that it could not evaluate.
+First, although it considers some of the most popular double robust, machine learning, traditional, and single robust methods, there are many methods that it could not evaluate, including variations and extensions of the three methods.
 Second, although the simulations are meant to cover a wide range of data generating processes, they only consider continuous outcomes and binary treatments; simulations with binary or categorical outcomes and continuous or multi-armed treatments may yield different results.
-Finally, the simulations in this paper do not consider situations where ignorability does not hold.
+Finally, in considering only functional form misspecification, the simulations in this paper do not consider situations where ignorability does not hold.
 In particular, it does not evaluate situations where causal identification is misspecified [@keil_2018_resolving].
@@
 Especially when paired with a highly flexible estimator like a SuperLearner or GRF, these methods may be slightly more accurate, and they can be useful when the number of covariates is high or even exceeds the number of observations.
+In longitudinal settings with time-varying confounders, they may be more useful [@tran_2019_double].
 They can also be useful as a sensitivity check; if researchers obtain similar estimates across traditional and double robust methods, they can be more confident in the reliability of their estimates.
@@
   kable_styling(latex_options = c("hold_position")) 
-```
+`

### 2024-07-23 draft/ms-adj-asa.Rmd
before taking out lalonde

---
output:
  # bookdown::word_document2:
    # reference_docx: "word-template.docx"
  bookdown::pdf_document2:
    toc: no
    number_sections: no
    pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
    latex_engine: xelatex
always_allow_html: true
header-includes:
  #- \usepackage{setspace}\doublespace
  # - \usepackage[nolists, fighead, tabhead]{endfloat}
  # - \usepackage{endnotes}
  # - \let\footnote=\endnote
#- \setlength{\headheight}{14.5pt}
#- \setlength{\headheight}{13.6pt}
# - \usepackage{fancyhdr}
# - \pagestyle{fancy}
# - \lhead{N.I. Hoffmann}
# - \rhead{`r format(Sys.time(), '%B %e, %Y')`}
# - \newcommand{\beginsupplement}{\setcounter{table}{0}  
# \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} 
# \renewcommand{\thefigure}{A\arabic{figure}}}

editor_options: 
  chunk_output_type: console

citeproc: no
fontfamily: mathpazo
#fontsize: 11pt
# geometry: margin=.6in
indent: yes
link-citations: yes
linkcolor: blue
lang: 'en-US'

bibliography: "/Users/nathan/Documents/My Library.bib" 
# bibliography: "My Library.bib"  
csl: apa.csl
# csl: american-sociological-association.csl

title: "Demystifying Double Robust, Flexible Adjustment Methods for Causal Inference"
#subtitle: "PAA 2023"
author:  Nathan I. Hoffmann
#   | Department of Sociology, UCLA
date: "`r format(Sys.time(), '%B %e, %Y')`"

abstract: "Double robust methods for flexible covariate adjustment in causal inference have proliferated in recent years. Despite their apparent advantages, these methods remain underutilized by social scientists. It is also unclear whether these methods actually outperform more traditional methods in finite samples. This paper has two aims: It is a guide to some of the latest methods in double robust, flexible covariate adjustment for causal inference, and it compares these methods to more traditional statistical methods. It does this by using both simulated data where the treatment effect estimate is known, and then using comparisons of experimental and observational data from the National Supported Work Demonstration. Methods covered include Augmented Inverse Propensity Weighting, Targeted Maximum Likelihood Estimation, and Double/Debiased Machine Learning. Results suggest that these methods do not necessarily outperform OLS regression or matching on propensity score estimated by logistic regression, even in cases where the data generating process is not linear."

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T)
options("yaml.eval.expr" = TRUE)

library(SuperLearner)
library(broom)
library(knitr)
library(here)
library(haven)
library(tidyverse)

knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})

options("yaml.eval.expr" = TRUE, scipen = 3, digits = 2)

uclablue = '#2774AE'
gray = '#808080'
black = '#000000'
ucla_palette = c(black, uclablue, gray)

# theme_set(theme_cowplot(font_family = 'Palatino') + 
theme_set(theme_classic(base_family = 'Palatino') + 
      theme(legend.title=element_blank(), 
         panel.grid.major.y = element_line('grey80'),
         legend.background = element_rect(fill = alpha("white", 0.5))
         ))
ggplot <- function(...) ggplot2::ggplot(...) + 
  scale_color_brewer(palette="Dark2") +
  scale_fill_brewer(palette="Dark2")

kable <- function(...) knitr::kable(..., format.args = list(big.mark = ","))
```

```{r load}
sims <- readRDS(here('files', 'sims.RDS'))

unemp_func <- function(x){
  x %>%
    as.data.frame() %>%
    mutate(re74_0 = re74 == 0,
         re75_0 = re75 == 0) 
}

lalonde_exp <- read_dta(here('data', 'nsw.dta')) %>%
  as.data.frame() %>%
  mutate(re75_0 = re75 == 0)
lalonde_exp_74 <- read_dta(here('data', 'nsw_dw.dta')) %>%
  unemp_func()
lalonde_cps1_controls <- read_dta(here('data', 'cps_controls.dta')) %>%
  unemp_func()
lalonde_cps3_controls <- read_dta(here('data', 'cps_controls3.dta')) %>%
  unemp_func()
lalonde_psid1_controls <- read_dta(here('data', 'psid_controls.dta')) %>%
  unemp_func()
lalonde_psid3_controls <- read_dta(here('data', 'psid_controls3.dta')) %>%
  unemp_func()
```

```{r functions}
## Pred functions ####
ols_logit_pred <- function(y, d, x){
  if('factor' %in% unlist(lapply(x, class))){
    x <- fastDummies::dummy_cols(x, remove_first_dummy = T, remove_selected_columns = T) 
  }

  mu_mod <- lm(y ~  d + ., data.frame(y, d, x))
  mu1_pred <- predict(mu_mod, newdata = data.frame(y, d = 1, x))
  mu0_pred <- predict(mu_mod, newdata = data.frame(y, d = 0, x))

  pi_mod <- glm(d ~ ., data.frame(y, x), family = binomial(link = 'logit'))
  pi_pred <- predict(pi_mod, type = 'response')

  return(
    list(
      mu1_pred = mu1_pred, 
      mu0_pred = mu0_pred, 
      pi_pred = pi_pred,
      d = d,
      y = y
    ))
}

grf_pred <- function(y, d, x){
  if('factor' %in% unlist(lapply(x, class))){
    x <- fastDummies::dummy_cols(x, remove_first_dummy = T, remove_selected_columns = T) 
  }

  forest_mu <- grf::regression_forest(X = data.frame(d, x), Y = y, 
                                 tune.parameters = "all")
  mu0_pred <- predict(forest_mu, newdata = data.frame(d = 0, x))$predictions
  mu1_pred <- predict(forest_mu, newdata = data.frame(d = 1, x))$predictions

  forest_pi <- grf::regression_forest(X = x, Y = d, tune.parameters = "all")
  pi_pred <- predict(forest_pi, newdata = x)$predictions

  return(
    list(
      mu1_pred = mu1_pred, 
      mu0_pred = mu0_pred, 
      pi_pred = pi_pred,
      d = d,
      y = y
    ))
}

superlearner_pred <- function(y, d, x, folds = 5, seed = 158){
  if('factor' %in% unlist(lapply(x, class))){
    x <- fastDummies::dummy_cols(x, remove_first_dummy = T, remove_selected_columns = T) 
  }

  set.seed(seed)
  mu_fit <- SuperLearner(
    Y = y,
    X = data.frame(d, x),
    cvControl = list(V = folds),
    SL.library=c("SL.glm", 
                 "SL.glmnet", 
                 "SL.xgboost"),
    method="method.CC_nloglik", 
    family="gaussian"
  )

  pi_fit <- SuperLearner(
    Y = d,
    X = x,
    cvControl = list(V = folds),
    SL.library=c("SL.glm", 
                 "SL.glmnet", 
                 "SL.xgboost"),
    method="method.CC_nloglik", 
    family="gaussian"
  )

  return(list(
    mu0_pred = predict(mu_fit, newdata = data.frame(d = 0, x), type = 'response')$pred,
    mu1_pred = predict(mu_fit, newdata = data.frame(d = 1, x), type = 'response')$pred,
    pi_pred = predict(pi_fit, type = 'response')$pred,
    d = d,
    y = y))
}

## Methods ####

lm_sim <- function(dat){
  start_time <- Sys.time()
  n <- length(dat)
  lm_list <- list()
  for(i in 1:n){
    print(paste0(i, ' out of ', n))
    sim_dat <- data.frame(y = dat[[i]]$y, 
                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
                          dat[[i]]$x)

    tryCatch({
      lm_out <- tidy(lm(y ~ d + ., sim_dat))
      lm_list[[i]] <- data.frame(dataset = i,
                                 ate = lm_out[[2,2]],
                                 #se = lm_out[[2,3]],
                                 truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))
      }, error=function(e){
        cat("ERROR :",conditionMessage(e), "\n")
        })

  }

  fail_count <- sum(sapply(lm_list, function(x) is.null(x)))
  # in case last few are errors
  fail_count <- ifelse(length(lm_list) == n, fail_count, fail_count + (n - length(lm_list)))

  end_time <- Sys.time()

  return(list(
    est_df = bind_rows(lm_list),
    fail_count = fail_count,
    comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
    )
}

psm_sim <- function(dat){
  start_time <- Sys.time()
  n <- length(dat)
  psm_list <- list()
  for(i in 1:n){
    print(paste0(i, ' out of ', n))
    sim_dat <- data.frame(y = dat[[i]]$y, 
                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
                          dat[[i]]$x)

    form <- as.formula(paste0('d ~ ', paste(names(dat[[i]]$x), collapse = '+')))
    match_out <- MatchIt::matchit(form,
                           data = sim_dat,
                           method = 'nearest',
                           distance = 'glm')

    # match_data <- MatchIt::match.data(match_out) 
    # apply(match_data, 1, unique)
    form2 <- as.formula(paste0('y ~ d + ', paste(names(dat[[i]]$x), collapse = '+')))

  tryCatch({
    psm_out <- lm(form2, 
                  MatchIt::match.data(match_out), 
                  weights = weights) %>%
      tidy()
    psm_list[[i]] <- data.frame(dataset = i,
                                ate = psm_out[[2,2]],
                                # se = psm_out[[2,3]],
                                truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))

  }, error=function(e){
    cat("ERROR :",conditionMessage(e), "\n")
    })

  }

  fail_count <- sum(sapply(psm_list, function(x) is.null(x)))
  # in case last few are errors
  fail_count <- ifelse(length(psm_list) == n, fail_count, fail_count + (n - length(psm_list)))

  end_time <- Sys.time()

  return(list(
    est_df = bind_rows(psm_list),
    fail_count = fail_count,
    comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
  )
}

aipw_calc <- function(mu1_pred, mu0_pred, pi_pred, d, y){
  n <- length(mu1_pred)

  y1_pred <- (d*(y-mu1_pred))/pi_pred + mu1_pred
  y0_pred <- ((1-d)*(y-mu0_pred))/(1-pi_pred) + mu0_pred

  ate <- (1/n)*(sum(y1_pred)) - (1/n)*sum(y0_pred)

  return(ate)
}

aipw_calc_trunc <- function(mu1_pred, mu0_pred, pi_pred, d, y){
  n <- length(mu1_pred)

  pi_pred <- case_when(
    pi_pred < .01 ~ .01,
    pi_pred > .99 ~ .99,
    T ~ pi_pred)

  y1_pred <- (d*(y-mu1_pred))/pi_pred + mu1_pred
  y0_pred <- ((1-d)*(y-mu0_pred))/(1-pi_pred) + mu0_pred

  ate <- (1/n)*(sum(y1_pred)) - (1/n)*sum(y0_pred)

  return(ate)
}

tmle_calc <- function(mu1_pred, mu0_pred, pi_pred, d, y){
  n <- length(y)
  # H <- (d == 1)/pi_pred - (d==0)/(1-pi_pred)
  H0 = (1-d)/(1-pi_pred)
  H1 = d/pi_pred

  epsilon <- glm(y ~ -1 + H0 + H1 + offset(qlogis((d==1)*mu1_pred + (d==0)*mu0_pred)),
                 family = binomial(link = 'logit')) %>%
    tidy() %>%
    pull(estimate)

  H_0 = (1-d)/(1-pi_pred)
  H_1 = d/pi_pred

  target_0 <- plogis(qlogis(mu0_pred + epsilon[1]*H_0))
  target_1 <- plogis(qlogis(mu1_pred + epsilon[2]*H_1))

  ATE <- mean((target_1 - target_0), na.rm = T)
  return(ATE)
}

dml_pre <- function(y, d, x){
  if('factor' %in% unlist(lapply(x, class))){
    x <- fastDummies::dummy_cols(x, remove_first_dummy = T, remove_selected_columns = T) 
  }

  n <- length(y)
  n_2 <- n/2
  n_2_1 = ifelse(round(n_2) == n_2, n_2, round(n_2))
  n_2_2 = ifelse(round(n_2) == n_2, n_2, round(n_2)+1)

  # split the sample
  random_vec <- sample(1:n, n)
  I <- random_vec[1:n_2_1]
  I_c <- random_vec[(n_2_1+1):n]

  return(list(
    y_I = y[I_c],
    d_I = d[I_c],
    x_I = x[I_c,],
        y_I_c = y[I_c],
    d_I_c = d[I_c],
    x_I_c = x[I_c,]
    ))
}

dml_post <- function(y_I, d_I, x_I = NULL, y_I_c, d_I_c, x_I_c = NULL,
                     mu_pred1, pi_pred1, mu_pred2, pi_pred2){

  v1 <- d_I - pi_pred1
  delta1 <- (sum(v1 * d_I))^-1 * sum(v1 * (y_I - pi_pred1))

  v2 <- d_I_c - pi_pred2
  delta2 <- (sum(v2 * d_I_c))^-1 * sum(v2 * (y_I_c - pi_pred2))

  ate <- (delta1 + delta2)/2

  return(ate)
}

## Predictor functions
ols_logit_dml <- function(y_I, d_I, x_I, y_I_c, d_I_c, x_I_c){
  mu_mod1 <- lm(y ~ ., data.frame(y = y_I_c, x_I_c))
  mu_pred1 <- predict(mu_mod1, newdata = data.frame(y = y_I, x_I))

  pi_mod1 <- glm(d ~ ., data.frame(d = d_I_c, x_I_c), 
                family = binomial(link = 'logit'))
  pi_pred1 <- predict(pi_mod1, 
                     newdata = data.frame(d = d_I, x_I), 
                     type = 'response')

  mu_mod2 <- lm(y ~ ., data.frame(y = y_I, x_I))
  mu_pred2 <- predict(mu_mod2, newdata = data.frame(y = y_I_c, x_I_c))

  pi_mod2 <- glm(d ~ ., data.frame(d = d_I, x_I), 
                family = binomial(link = 'logit'))
  pi_pred2 <- predict(pi_mod2, 
                     newdata = data.frame(d = d_I_c, x_I_c), 
                     type = 'response')

  return(list(
    mu_pred1 = mu_pred1,
    pi_pred1 = pi_pred1,
    mu_pred2 = mu_pred2,
    pi_pred2 = pi_pred2
  ))
}

grf_dml <- function(y_I, d_I, x_I, y_I_c, d_I_c, x_I_c){
  mu_mod1 <- grf::regression_forest(X = x_I_c, Y = y_I_c, 
                                       tune.parameters = "all")
  mu1_pred1 <- predict(mu_mod1, newdata = x_I)$predictions

  pi_mod1 <- grf::regression_forest(X = x_I_c, Y = d_I_c, tune.parameters = "all")
  pi_pred1 <- predict(pi_mod1, newdata = x_I)$predictions

  mu_mod2 <- grf::regression_forest(X = x_I, Y = y_I, 
                                       tune.parameters = "all")
  mu1_pred2 <- predict(mu_mod1, newdata = x_I_c)$predictions

  pi_mod2 <- grf::regression_forest(X = x_I, Y = d_I, tune.parameters = "all")
  pi_pred2 <- predict(pi_mod1, newdata = x_I_c)$predictions

  return(list(
    mu_pred1 = mu_pred1,
    pi_pred1 = pi_pred1,
    mu_pred2 = mu_pred2,
    pi_pred2 = pi_pred2
  ))
}

superlearner_dml <- function(y_I, d_I, x_I, y_I_c, d_I_c, x_I_c,
                             folds = 5){

  mu_mod1 <- SuperLearner(
    Y = y_I_c,
    X = x_I_c,
    cvControl = list(V = folds),
    SL.library=c("SL.glm", 
                 "SL.glmnet", 
                 "SL.xgboost"),
    method="method.CC_nloglik", 
    family="gaussian"
  )

  pi_mod1 <- SuperLearner(
    Y = d_I_c,
    X = x_I_c,
    cvControl = list(V = folds),
    SL.library=c("SL.glm", 
                 "SL.glmnet", 
                 "SL.xgboost"),
    method="method.CC_nloglik", 
    family="gaussian"
  )

  mu_pred1 <- predict(mu_mod1, newdata = x_I, type = 'response')$pred
  pi_pred1 <- predict(mu_mod1, newdata = x_I, type = 'response')$pred

  mu_mod2 <- SuperLearner(
    Y = y_I,
    X = x_I,
    cvControl = list(V = folds),
    SL.library=c("SL.glm", 
                 "SL.glmnet", 
                 "SL.xgboost"),
    method="method.CC_nloglik", 
    family="gaussian"
  )

  pi_mod2 <- SuperLearner(
    Y = d_I,
    X = x_I,
    cvControl = list(V = folds),
    SL.library=c("SL.glm", 
                 "SL.glmnet", 
                 "SL.xgboost"),
    method="method.CC_nloglik", 
    family="gaussian"
  )

  mu_pred2 <- predict(mu_mod2, newdata = x_I_c, type = 'response')$pred
  pi_pred2 <- predict(mu_mod2, newdata = x_I_c, type = 'response')$pred

  return(list(
    mu_pred1 = mu_pred1,
    pi_pred1 = pi_pred1,
    mu_pred2 = mu_pred2,
    pi_pred2 = pi_pred2
  ))
}

## Functions using double robust packages ####
aipw_sim <- function(dat, seed = 185){

  start_time <- Sys.time()

  set.seed(seed)
  n <- length(dat)
  aipw_list <- list()
  # fail_count <- 0

  for(i in 1:n){
    print(paste0(i, ' out of ', n))
    sim_dat <- data.frame(y = dat[[i]]$y, 
                          d = as.numeric(ifelse(dat[[i]]$z == 'trt', 1, 0)), 
                          dat[[i]]$x)

    tryCatch({
      sim_dat <- sim_dat %>%
        fastDummies::dummy_cols(remove_first_dummy = T, remove_selected_columns = T) 
      }, error=function(e){
      })

    tryCatch({
      forest <- grf::causal_forest(X = select(sim_dat, 3:length(names(sim_dat))), 
                                   Y = sim_dat$y, 
                                   W = sim_dat$d)
      # forest <- grf::causal_forest(X = select(sim_dat, starts_with('x')), 
      #                              Y = sim_dat$y, W = sim_dat$d)

      aipw_out <- grf::average_treatment_effect(forest, target.sample = 'treated', method = 'AIPW')

      aipw_list[[i]] <- data.frame(d = aipw_out[[1]],
                                   se = aipw_out[[2]],
                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))

  }, error=function(e){
    cat("ERROR :",conditionMessage(e), "\n")
    })
  }

  fail_count <- sum(sapply(aipw_list, function(x) is.null(x)))
  # in case last few are errors
  fail_count <- ifelse(length(aipw_list) == n, fail_count, fail_count + (n - length(aipw_list)))

  end_time <- Sys.time()

  return(list(
      est_df = bind_rows(aipw_list),
      fail_count = fail_count,
      comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
  )
}

tmle_sim <- function(dat, seed = 185){
  start_time <- Sys.time()

  set.seed(seed)
  n <- length(dat)
  tmle_list <- list()
  # fail_count <- 0

  for(i in 1:n){
    print(paste0(i, ' out of ', n))
    sim_dat <- data.frame(y = dat[[i]]$y, 
                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
                          dat[[i]]$x)

    tryCatch({
      sim_dat <- sim_dat %>%
        fastDummies::dummy_cols(remove_first_dummy = T, remove_selected_columns = T) 
      }, error=function(e){
      })

    tryCatch({
      forest <- grf::causal_forest(X = select(sim_dat, 3:length(names(sim_dat))), 
                                   Y = sim_dat$y, W = sim_dat$d)
      # forest <- grf::causal_forest(X = select(sim_dat, starts_with('x')), 
      #   Y = sim_dat$y, W = sim_dat$d)

      tmle_out <- grf::average_treatment_effect(forest, target.sample = 'treated', method = 'TMLE')

      tmle_list[[i]] <- data.frame(d = tmle_out[[1]],
                                   se = tmle_out[[2]],
                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))

  }, error=function(e){
    cat("ERROR :",conditionMessage(e), "\n")
    })
  }

  fail_count <- sum(sapply(tmle_list, function(x) is.null(x)))
  # in case last few are errors
  fail_count <- ifelse(length(tmle_list) == n, fail_count, fail_count + (n - length(tmle_list)))

  end_time <- Sys.time()

 return(list(
      est_df = bind_rows(tmle_list),
      fail_count = fail_count,
      comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
  )
}

dml_sim <- function(dat, seed = 185){
  library(mlr3)
  library(mlr3learners)

  start_time <- Sys.time()

  set.seed(seed)

  n <- length(dat)

  dml_list <- list()

  for(i in 1:n){
    print(paste0(i, ' out of ', n))
    sim_dat <- data.frame(y = dat[[i]]$y, 
                          d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
                          dat[[i]]$x)

    lgr::get_logger("mlr3")$set_threshold("warn")

    learner = lrn("regr.ranger", num.trees=500, 
                  max.depth=5, min.node.size=2)
    ml_l = learner$clone()
    ml_m = learner$clone()

    tryCatch({
      dml_out <- DoubleML::DoubleMLPLR$new(
        DoubleML::DoubleMLData$new(sim_dat,
                                 y_col = 'y',
                                 d_cols = 'd',
                                 x_cols = names(dat[[i]]$x)), 
        ml_l=ml_l, ml_m=ml_m)

      dml_out$fit()
      dml_list[[i]] <- data.frame(d = dml_out$all_coef[[1,1]],
                                  se = dml_out$all_se[[1,1]],
                               truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))

  }, error=function(e){
    cat("ERROR :",conditionMessage(e), "\n")
    })
  }

  fail_count <- sum(sapply(dml_list, function(x) is.null(x)))
  # in case last few are errors
  fail_count <- ifelse(length(dml_list) == n, fail_count, fail_count + (n - length(dml_list)))

  end_time <- Sys.time()

  return(list(
      est_df = bind_rows(dml_list),
      fail_count = fail_count,
      comp_time = as.numeric(difftime(end_time, start_time, units = 'secs'))/(n-fail_count))
      )
}

## Other functions ####
normalize <- function(x, y){(x - min(y)) / (max(y) - min(y))}
denormalize <- function(x, y){x * (max(y) - min(y))}
perform <- function(est_df, label){
  est_df %>%
    # mutate(d = d/truth,
    #        truth = 1) %>%
    summarize(bias = mean(d - truth),
              percent_bias = bias/sd(d),
              rmse = sqrt(mean((ate - truth)^2)),
              mae = median(abs(d - truth)),
              fail_count = first(fail_count),
              comp_time = first(comp_time)) %>%
    mutate(label = label,
           n = nrow(est_df) + fail_count) %>%
    select(label, everything()) %>%
    return()
}
```

<!-- # Abstract -->

<!-- This thesis aims to compare different advanced adjustment methods. It will compare Imben & Rubins propensity matching, stabilized IPWs, TMLE, double machine learning (Chernozhukov et al 2018), Ratkovic (2021), and BART. -->

# Introduction

Statistical methods for flexible covariate adjustment in causal inference have proliferated in recent years. These methods have a number of strengths over traditional regression methods: They make few functional form assumptions, can accommodate large numbers of covariates, and produce easily interpretable treatment effect estimates. Many of these methods also have a "double robust" property: They estimate one model for the treatment exposure and another for the outcome, and as long as at least one is correctly specified, then the treatment effect will be estimated consistently. Despite their apparent advantages, these methods remain underutilized by social scientists. Part of the barrier has been lack of familiarity with these methods. It has also been unclear how these methods compare, or whether such methods actually perform better than traditional methods in finite samples. 
<!-- And when researchers want to use an existing R package for these methods, the array of possible estimation methods and other options can be dizzying.   -->

This paper makes advances on these fronts. First, it is a guide to some of the latest methods in double robust, flexible covariate adjustment for causal inference, explaining the methods to a social scientist audience. Second, it compares these methods to more traditional statistical methods using both simulations [@dorie_2019_automated] and the National Support for Work Demonstration (NSW) originally analyzed by @lalonde_1986_evaluating.

Methods covered include Targeted Maximum Likelihood Estimation [TMLE, @vanderlaan_2006_targeted], Double or Debiased Machine Learning [DML, @chernozhukov_2018_double], and Augmented Inverse Propensity Weighting [AIPW, @glynn_2010_introduction]. This paper reviews the theory behind these methods as well as simple R implementations of them on simulations and real data. These methods are compared to two methods commonly used by social scientists: ordinary least squares (OLS) regression, and matching on propensity scores estimated from logistic regression (PSM).

# Conceptual Overview

Double robust methods estimate two models:

- an *outcome model*

$$\mu_d(X_i) = E(Y_i \mid D_i = d, X_i)$$

- and an *exposure model* (or treatment model or propensity score):

$$\pi(X_i) = E(D_i \mid X_i)$$

where $\mu_d(\cdot)$ is the model of control or treatment $D_i = d=\{0, 1\}$, $X_i$ is a vector of covariates for unit $i = 1, \ldots, N$ for treatment (1) and control (0), $Y_i$ is the outcome, and $\pi(\cdot)$ is the exposure model. The covariates included in $X_i$ can be different for the two models.

An estimator is called "double robust" if it achieves consistent estimation of the ATE (or whatever estimand the researcher is interested in) as long as *at least one* of these two models is consistently estimated. This means that the outcome model can be completely misspecified, but as long as the exposure model is correct, our estimation of the ATE will be consistent. This also means that the exposure model can be completely wrong, as along as the outcome model is correct.

## Origins of Doubly Robust Methods

According to @bang_2005_doubly, double robust methods have their origins in missing data models. @robins_1994_estimation and @rotnitzky_1998_semiparametric developed augmented orthogonal inverse probability-weighted (AIPW) estimators in missing data models, and @scharfstein_1999_adjusting showed that AIPW was double robust and extended to causal inference.

But @kang_2007_demystifying argue that double robust methods are older. They cite work by @cassel_1976_results, who proposed “generalized regression estimators” for population means from surveys where sampling weights must be estimated. Arguably, double robust methods go back even further than this. The form of double robust methods is similar to residual-on-residual regression, which dates back to @frisch_1933_partial famous FWL theorem:

$$\beta_D = \frac{\text{Cov}(\tilde Y_i, \tilde D_i)}{\text{Var}(\tilde D_i)}$$

where $\tilde D_i$ is the residual part of $D_i$ after regressing it on $X_i$, and $\tilde Y_i$ is the residual part of $Y_i$ after regressing it on $X_i$. This formulation writes the regression coefficient as composed of an outcome model ($\tilde Y_i$) and exposure model ($\tilde D_i$), the two models used in double robust estimators.

There are also links between double robust methods and matching with regression adjustment. This work goes back to at least @rubin_1973_use, who suggested that regression adjustment in matched data produces less biased estimates that either matching (exposure adjustment) or regression (outcome adjustment) do by themselves.

## Assumptions

Most double robust methods require almost all of the standard assumptions necessary formost methods that depend on selection on observables. Although some double robust methods relax one or two of these, the six standard assumptions are:

1. Consistency
2. Positivity/overlap
3. One version of treatment
4. No interference
5. IID observations
6. Conditional ignorability: $\{Y_{i0}, Y_{i1}\} \perp \!\!\! \perp D_i \mid X_i$

Special attention should be paid to Assumption 6: double robust methods will not work if we do not measure an important confounder that affects both treatment and exposure. But notably, the double robust methods covered in this tutorial make no functional form assumptions. These methods are designed to incorporate flexible machine learning algorithms to estimate both the outcome and exposure models, with regularization (often through cross-fitting) to avoid overfitting.

# Overview of Techniques  
Each of the methods reviewed in this paper can be thought of as a collection of estimation techniques. Each involves a model for the outcome and another for the treatment exposure, but the ways these relate and are combined varies from method to method. Choice of estimation technique for these two models is left to the discretion of the user; often ensemble learning is recommended, but in practice simpler methods can also work well.

## Augmented Inverse Propensity Weighting (AIPW)

The oldest of these modern methods, AIPW arose in the context of missing data imputation. The method simply combines estimates from a model for the treatment exposure, $\pi(X)$, and a model for the outcome, $\mu(X)$. The name comes from the close similarity to inverse propensity weights (IPW), but whereas IPW only weights for propensity of treatment, AIPW "augments" these weights with an estimate of the response surface as well.

Formally, the model can be written as the difference between an estimated outcome for treated units and the estimated outcome for untreated units (see the demonstration below):

$$\begin{aligned}
\widehat{ATE}_{AIPW} = &\frac{1}{n} \sum_{i=1}^n \left( \frac{D_i(Y_i - \hat \mu_1 (\mathbf X_i))}{\hat \pi (\mathbf X_i)} + \hat \mu_1(\mathbf X_i) \right) 
- \frac{1}{n} \sum_{i=1}^n \left( \frac{(1-D_i)(Y_i - \hat \mu_0 (\mathbf X_i))}{1-\hat \pi(\mathbf X_i)} + \hat \mu_0(\mathbf X_i) \right)
\end{aligned}$$

@glynn_2010_introduction provide an alternate formula, where the basic inverse probability weight (IPW) estimator (which incorporates only the exposure model $\hat \pi$) is corrected using a weighted average of two outcome regression estimates: 
$$\begin{aligned}
\widehat{ATE}_{AIPW} = & \frac{1}{n} \sum_{i=1}^n \left\{ \left[ \frac{D_i Y_i}{\hat \pi(\mathbf X_i)} - \frac{(1-D_i) Y_i}{ 1- \hat \pi(\mathbf X_i)} \right] - \frac{D_i - \hat \pi (\mathbf X_i)}{\hat \pi (\mathbf X_i)(1 - \hat pi (\mathbf X_i))} [(1- \hat \pi (\mathbf X_i)) \hat \mu_1(\mathbf X_i) + \hat \pi (\mathbf X_i) \hat \mu_0(\mathbf X_i)] \right\}
\end{aligned}$$

## Targeted Maximum Likelihood Estimation (TMLE)

TMLE begins by estimating the relevant part of the data-generating distribution $P(Y)$, i.e. the conditional density $Q = P(Y \mid X)$. It next estimates the exposure model. Although any estimation method can be used for these steps, the originators of the method suggest using a "super learner," i.e. ensemble learning with cross-validation. Next, the exposure model is used to calculate a "clever covariate," which is similar to an IPW. The coefficient for this clever covariate is estimated using maximum likelihood -- whence the "MLE" in "TMLE." Finally, the estimate of $Q$ is updated in a function involving the clever covariate. This process can be iterated, but usually one iteration is enough. The estimate of the distribution $Q$ can be used to calculate the estimand of interest.

Formulaly, first generate estimates of $\mu_{d}(\mathbf X_i) = E(Y \mid D=d, \mathbf X_i)$ and $\pi(\mathbf X_i) = P(D=1 \mid \mathbf X_i)$. Then create variable for targeting step:
$$H_{di} = \frac{I(D_i = 1)}{\hat \pi (\mathbf X_i)} - \frac{I(D_i=0)}{1 - \hat \pi (\mathbf X_i)}$$

Next, calculate the clever covariates for each individual in the data. These quantities are similar to inverse probability weights:
$$\begin{aligned}
H_{1i}(D=1, \mathbf X_i) &= \frac{d_i}{\hat \pi (\mathbf X_i)}, &
H_{0i}(D=0, \mathbf X_i) = \frac{1-d_i}{1- \hat \pi (\mathbf X_i)}.
\end{aligned}$$

Then estimate fluctuation parameters $\epsilon = (\epsilon_0, \epsilon_1)$ through maximum likelihood of the following logistic regression with fixed intercept $\text{logit}(\mu_{di})$: 
<!-- $$E(Y=1 \mid D, \mathbf X) = \text{logit}(\mu_{di}) + \epsilon H_{di}$$ -->
$$\text{logit}[E(Y=1 \mid D, \mathbf X)] = \text{logit}(\hat \mu_{di}) + \epsilon_0 H_{0i} + \epsilon_1 H_{1i}$$

Then generate updated ("targeted") estimates of potential outcomes:
$$\begin{aligned}
\hat \mu_1^*(\mathbf X_i) &= \text{expit}[\text{logit}(\hat \mu_1(\mathbf X_i)) + \hat \epsilon H_{1i}]\\
\hat \mu_0^*(\mathbf X_i) &= \text{expit}[\text{logit}(\hat \mu_0(\mathbf X_i)) + \hat \epsilon H_{0i}]
\end{aligned}$$

Finally, estimate targeted parameter (ATE):
$$\widehat{ATE}_{TMLE} = \frac{1}{n} \sum_{i=1}^n [\hat \mu_1^*(\mathbf X_i) - \hat \mu_1^*(\mathbf X_i)]$$

## Double or Debiased Machine Learning* (DML)

The most recent of the methods reviewed here, DML is motivated by the need to handle problems with high-dimensional nuisance parameters, i.e. a large number of measured confounders. Flexible machine learning is appropriate for this task, but such methods suffer from regularization bias. DML removes this bias in a two-step procedure. First, it solves the auxiliary problem of estimating the treatment exposure model $E(D|X) =  \pi(X)$. It then uses this model to remove bias: Neyman orthogonalization allows the creation of an orthogonalized regressor, essentially partialing out the effect of covariates $X$ from treatment $D$. The debiased $D$ is then used to estimate the conditional mean of the outcome $E(Y\mid X) = \mu(X)$, which can be used to calculate the estimand of interest.

We can motivate this as follows. Suppose we want to estimate $\delta$ in the following framework:
$$y_i = \delta d_i + g_0(\mathbf x_i) + u_i,$$
$$d_i = m_0(\mathbf x_i) + v_i.$$

The idea is to estimate $g_0$ and $m_0$ separately, then use residual-on-residual regression to obtain an estimate of $\delta$. However this leaves a term in the asymptotic distribution of $\hat \delta$ that biases the estimate. To avoid this, DML uses sample splitting.

We randomly split the sample of $n$ observations into two sets, $I$ and $I^c$, each of size $n/2$. We then estimate the response and treatment models using only set $I^c$:

1) Estimate $d_i = \hat m_0(\mathbf x_i) + \hat v_i, i \in I^c$.  
2) Estimate $y_i =  \hat g_0(\mathbf x_i) + \hat u_i, i \in I^c$, without using $d_i$.

Next, we use the estimated models to perform residual-on-residual regression *on the left out set* $I$ to obtain an estimate of $\delta$:
$$\hat \delta(I^c, I) = \left(\sum_{i \in I} \hat v_i d_i \right)^{-1} 
\sum_{i \in I} \hat v_i (y_i - \hat g_0 (\mathbf x_i)).$$

Using half the sample results in efficiency loss. To rectify this, we repeat the above procedure, switching the split sets. We then have $\delta(I^c, I)$ and $\delta(I, I^c)$. The cross-fitting DML estimator is:
$$\widehat {ATE}_{DML} = \frac{\hat \delta (I^c, I) + \hat \delta (I, I^c)}{2}.$$

## A simple demonstration using AIPW

To demonstrate double robustness, this section presents one of the simpler double robust estimators, AIPW [@glynn_2010_introduction]. As shown above, we can write this estimator as follows:

$$\begin{aligned}
\widehat{ATE} = &\frac{1}{N} \sum_{i=1}^N \left( \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) \right) 
- \frac{1}{N} \sum_{i=1}^N \left( \frac{(1-D_i)(Y_i - \hat \mu_0 (X_i))}{1-\hat \pi(X_i)} + \hat \mu_0(X_i) \right)
\end{aligned}$$

For each individual in the sample, this estimator calculates two quantities:

- The treated potential outcome

$$\hat Y_{1i} = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i)$$

- The control potential outcome

$$\hat Y_{0i} = \frac{(1-D_i)(Y_i - \hat \mu_0 (X_i))}{1-\hat \pi(X_i)} + \hat \mu_0(X_i)$$

Let's focus on the treated model:

$$\hat Y_{1i} = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i)$$

First, assume that the outcome model $\mu_1(X_i)$ is *correctly* specified and the exposure model $\pi(X_i)$ is *incorreclty* specified. Let's also assume (for now) that we're dealing with a treated unit, i.e. $D_i = 1$. Then

$$\hat \mu_1 (X_i) = Y_i$$

and hence

$$\hat Y_{1i} = \frac{D_i(0)}{\hat \pi (X_i)} + \hat \mu_1(X_i) = \hat \mu_1(X_i).$$

So the model relies *only* on the outcome model. The incorrectly specified exposure model completely disappears from the equation. If we're dealing with a control unit ($D_i=0$), we get the same result:

$$\hat Y_{1i} = \frac{0(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) = \hat \mu_1(X_i).$$

Now, what if the *exposure* model $\pi(X_i)$ is correctly specified and the outcome model $\mu_1(X)$ is incorrect? First, we rewrite the estimator for the treated outcome:

$$\begin{aligned}
\hat Y_{1i}& = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) \\
&= \frac{D_iY_i}{\hat \pi (X_i)} - \frac{D_i\hat \mu_1 (X_i)}{\hat \pi (X_i)} + \frac{\hat \pi (X_i)\hat \mu_1(X_i)}{\hat \pi (X_i)} \\
& = \frac{D_iY_i}{\hat \pi (X_i)} - \left( \frac{D_i - \hat \pi(X_i)}{\hat \pi (X_i)}\right) \hat \mu_1(X_i). &&(*)
\end{aligned}$$

Since the exposure model is correclty specified, we have $D_i = \hat \pi(X_i)$ on average, so

$$E[D_i - \hat \pi(X_i)] = 0.$$

This means that the second term in equation $(*)$ is 0, so

$$E[\hat Y_{1i}]= E \left [ \frac{D_iY_i}{\hat \pi (X_i)}\right].$$

This shows that when the exposure model is correct, then the estimator depends *only* on the exposure model. We can make similar arguments for the control model $\hat Y_{0i}$.

This demonstration shows that this estimator achieves double robustness: the estimator is robust to misspecification of either the exposure or the outcome model (but not both).

# Methods

These methods have many similarities. How do the results they give compare? This section tests the performance of each in practice using two methods. First, results are compared using simulated data from a causal inference competition (@dorie_2019_automated). The true treatment effect is known, so these simulations allow assessment of accuracy. Second, these methods are applied to data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW). The NSW randomly provided training to disadvantaged workers, allowing an experimental estimate of the effect of the intervention, and data assembled by @dehejia_1999_causal allows these experimental estimates to be compared to observational ones.

The three double robust methods are compared to two traditional estimation methods used as benchmarks: linear regression estimated using ordinary least squares regression ("OLS") and propensity-score matching with scores estimated from logistic regression using the `MatchIt` package ("PSM").

Double robust can use a variety of techniques to estimate the underlying treatment and outcome models. The simulation results below compare three estimation techniques. First is using a logistic regression for the exposure model and an OLS regression for the outcome model. Second is generalized random forests [GRF, @athey_2019_generalized] using the `grf` R package, with separate models for exposure and outcome. The final technique is the SuperLearner (as promoted by the makers of TMLE) using the `SuperLearner` package, again with separate models for exposure and outcome. GLM, glmnet (lasso), and XGBoost models are considered for the SuperLearner.

For the simulations, I have coded original functions to to implement the three double robust methods. This allows the use of the same exposure and outcome models' predictions in implementing these methods, permitting maximum comparability. However, the evaluation of the simulations only considers point estimates and not standard errors. For evaluation of the experimental LaLonde data, I use availabel R packages that calculate standard errors, using generalized random forests as the estimation technique. The augmented inverse propensity weighted estimator and targeted maximum likelihood estimation use the `grf` package, and double/debiased machine learning uses `DoubleML` and `mlr3` packages.

# Results

## Simluations with Dorie et al. (2019) Data

In 2016, the Atlantic Causal Inference Conference hosted a competition for causal inference methods that adjust on observables. @dorie_2019_automated published the results of this competition, along with the data used in the competition. Below, I test double robust methods on the 20 data sets used for the "do-it-yourself" part of the competition. The data represent a hypothetical twins study investigating the impact of birth weight on IQ. The data have 4802 observations and 52 covariates. The authors of the study specify a different data generating process for the potential outcomes in each data set. In all cases, ignorability holds, but the authors vary the following:

- degree of nonlinearity
- percentage of treated
- overlap for the treatment group
- alignment (correspondence between the assignment mechanism and the response surface)
- treatment effect heterogeneity
- overall magnitude of the treatment effect

The 20 data sets used here cover a range of these attributes; see the supplemental material from @dorie_2019_automated for details. I use 10 simulations of each data set, resulting in 200 data sets. I also use 100 simulations of each of the two datasets with linear data generating processes (numbers 1 and 3) to show how these methods perform when the underlying models are linear. I then calculate bias, percent bias (the estimator's bias as a percentage of its standard error), root mean squared error (rmse), and median absolute error (mae). I also present the number of datasets for which the method fails and the average computation time for each data set, in seconds.

Results for the full range of simulations are shown in Table \@ref(tab:dorie-results). Using AIPW as written above results in some wildly biased estimates for the ols_logit estimator, due to dividing by some very small propensity scores. Hence I present estimates from a trimmed AIPW estimator, where predicted exposure model values are set to 0.01 if they are less than 0.01 and to 0.99 if they are greater than 0.99.

The lowest bias is achieved by AIPW with GRF, followed by propensity score matching and then OLS. The lowest root mean squared error is obtained by AIPW with GRF, followed by TMLE with GRF, and next by OLS regression. Results are similar if we consider percent bias or mean absolute error. DML does not perform particularly well and also has the highest computation times due to sample splitting.

If we consider only the linear datasets (Table \@ref(tab:dorie-results-linear)), OLS obtains the lowest bias, followed by AIPW with GRF and then propensity score matching. The lowest root mean squared error is achieved by OLS, then AIPW with GRF, and then TMLE with GRF. Percent bias and mean absolute error show similar results.

Overall, traditional methods perform surprisingly well in comparison with the double robust methods. Even in the full range of datasets -- which include highly nonlinear exposure and outcome data-generating processes -- OLS and propensity score matching obtain some of the smallest bias. Generalized random forests appear to be the best estimators for the double robust methods, though a SuperLearner than incorporates GRF has the potential to outperform GRF alone, at the expense of computation time. Notably, the method with the longest computation time -- DML with a SuperLearner -- takes over 2,000 times as along as OLS.

```{r dorie-sim, eval = F}
set.seed(185)

sim_list <- list()
for(i in 1:20){ # up to 77
  #sim_list_nest <- list()
  for(j in 1:10){ # up to 100
    print(paste0(i,',',j))
    sim_list[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016,
                                      i, j, extraInfo = T)
  }
}

sim_linear <- list()
for(i in c(1, 3)){
  for(j in 1:100){ 
    print(paste0(i,',',j))
    sim_linear[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016, 
                                      i, j, extraInfo = T)
  }
}

saveRDS(append(sim_list, sim_linear), here('files', 'sims.RDS'))
```

```{r lm-sim, eval = F}

lm_sim_out <- lm_sim(sims)

lm_df <- lm_sim_out$est_df %>%
  mutate(fail_count = lm_sim_out$fail_count,
         comp_time = lm_sim_out$comp_time)

write_csv(lm_df, here('files', 'lm_df.csv'))

```

```{r psm-sim, eval = F}
psm_sim_out <- psm_sim(sims)

psm_df <- psm_sim_out$est_df %>%
  mutate(fail_count = psm_sim_out$fail_count,
         comp_time = psm_sim_out$comp_time)

write_csv(psm_df, here('files', 'psm_df.csv'))
```

```{r pred-calc, eval = F}

ols_logit_pred_list <- list()
for(i in 1:length(sims)){
  print(i)
  dat <- sims[[i]]

  start_time = Sys.time()

  ols_logit_pred_list[[i]] <- ols_logit_pred(
    y = dat$y,
    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
    x = dat$x) %>%
    append(list(truth = mean(dat$y.1) - mean(dat$y.0),
                comp_time = as.numeric(difftime(Sys.time(), start_time, units = 'secs'))))
}
saveRDS(ols_logit_pred_list, here('files/homemade/', 'ols_logit_pred.RDS'))

# tibble(ols_logit_pred_list[[i]]$y,
#              ols_logit_pred_list[[i]]$mu1_pred, 
#              ols_logit_pred_list[[i]]$mu0_pred,
#              ols_logit_pred_list[[i]]$d,
#              hist(ols_logit_pred_list[[12]]$pi_pred)
#              )

grf_pred_list <- list()
for(i in 1:length(sims)){
  print(i)
  dat <- sims[[i]]

  start_time = Sys.time()

  grf_pred_list[[i]] <- grf_pred(
    y = dat$y,
    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
    x = dat$x) %>%
    append(list(truth = mean(dat$y.1) - mean(dat$y.0),
                comp_time = as.numeric(difftime(Sys.time(), start_time, units = 'secs'))))
}
saveRDS(grf_pred_list, here('files/homemade/', 'grf_pred.RDS'))

superlearner_pred_list <- list() 
for(i in 1:length(sims)){
  print(i)
  dat <- sims[[i]]

  start_time = Sys.time()

  superlearner_pred_list[[i]] <- superlearner_pred(
    y = dat$y,
    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
    x = dat$x) %>%
    append(list(truth = mean(dat$y.1) - mean(dat$y.0),
                comp_time = as.numeric(difftime(Sys.time(), start_time, units = 'secs'))))
}
saveRDS(superlearner_pred_list, here('files/homemade/', 'superlearner_pred.RDS'))

```

```{r aipw, eval = F}

aipw_calc2 <- function(mu1_pred, mu0_pred, pi_pred, d, y){
  n <- length(mu1_pred)

  # pi_pred <- case_when(
  #   pi_pred < quantile(pi_pred, c(.025)) ~ as.numeric(quantile(pi_pred, c(.025))),
  #   pi_pred > quantile(pi_pred, c(.975)) ~ as.numeric(quantile(pi_pred, c(.975))),
  #   T ~ pi_pred)

  # pi_pred <- case_when(
  #   pi_pred < .01 ~ .01,
  #   pi_pred > .99 ~ .99,
  #   T ~ pi_pred)

  ipw <- (d*y)/pi_pred - (1-d)*y/(1-pi_pred)
  adjust <- (d-pi_pred)/(pi_pred*(1-pi_pred)) * (1-pi_pred)*mu1_pred + pi_pred*mu0_pred

  ate <- (1/n) * sum(ipw - adjust)

  return(ate)
}

aipw_out_list <- list()
predictions <- list(ols_logit_pred_list2, grf_pred_list2, superlearner_pred_list2)
pred_names <- c('ols_logit', 'grf', 'superlearner')
for(i in 1:length(sims)){
  print(i)
  for(j in 1:length(predictions)){

    start_time <- Sys.time()
    aipw_out <- with(predictions[[j]][[i]], 
                     aipw_calc(mu1_pred = mu1_pred, 
                               mu0_pred = mu0_pred,
                               pi_pred = pi_pred,
                               d = d,
                               y = y))
    comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))

    aipw_out_list[[paste0(i, ',', j)]] <- data.frame(
      dataset = i,
      method = pred_names[[j]],
      ate = aipw_out, 
      truth = predictions[[j]][[i]]$truth, 
      comp_time = comp_time + predictions[[j]][[i]]$comp_time)
  }
}

write_csv(bind_rows(aipw_out_list), here('files/homemade/', 'aipw.csv'))

aipw_out_list <- list()
predictions <- list(ols_logit_pred_list2, grf_pred_list2, superlearner_pred_list2)
pred_names <- c('ols_logit', 'grf', 'superlearner')
for(i in 1:length(sims)){
  print(i)
  for(j in 1:length(predictions)){

    start_time <- Sys.time()
    aipw_out <- with(predictions[[j]][[i]], 
                     aipw_calc_trunc(mu1_pred = mu1_pred, 
                               mu0_pred = mu0_pred,
                               pi_pred = pi_pred,
                               d = d,
                               y = y))
    comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))

    aipw_out_list[[paste0(i, ',', j)]] <- data.frame(
      dataset = i,
      method = pred_names[[j]],
      ate = aipw_out, 
      truth = predictions[[j]][[i]]$truth, 
      comp_time = comp_time + predictions[[j]][[i]]$comp_time)
  }
}

write_csv(bind_rows(aipw_out_list), here('files/homemade/', 'aipw_trunc.csv'))

```

```{r tmle, eval = F}

tmle_out_list <- list()
predictions <- list(ols_logit_pred_list2, grf_pred_list2, superlearner_pred_list2)
pred_names <- c('ols_logit', 'grf', 'superlearner')

for(i in 1:length(sims)){
  print(i)
  for(j in 1:length(predictions)){
    start_time <- Sys.time()
    tryCatch({
      tmle_out <- with(predictions[[j]][[i]], 
                       tmle_calc(mu1_pred = normalize(mu1_pred, y), 
                                 mu0_pred = normalize(mu0_pred, y),
                                 pi_pred = pi_pred,
                                 d = d,
                                 y = normalize(y, y))
                       )
    }, error=function(e){
      tmle_out <- NA
      })
    comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))

    tmle_out_list[[paste0(i, ',', j)]] <- data.frame(
      dataset = i,
      method = pred_names[[j]],
      ate = denormalize(tmle_out, predictions[[j]][[i]]$y), 
      truth = predictions[[j]][[i]]$truth, 
      comp_time = comp_time + predictions[[j]][[i]]$comp_time,
      fail = is.na(tmle_out))
  }
}

write_csv(bind_rows(tmle_out_list), here('files/homemade/', 'tmle.csv'))

# logit_logit_pred_list <- list()
# 
# for(i in 1:length(sim_linear)){
#   print(i)
#   dat <- sim_linear[[i]]
#   
#   logit_logit_pred_out <- logit_logit_pred(
#     y = with(dat, (y - min(y)) / (max(y) - min(y))),
#     d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
#     x = dat$x
#     )
#   
#   ate <- with(logit_logit_pred_out, 
#               tmle_calc(mu1_pred = mu1_pred, 
#                         mu0_pred = mu0_pred,
#                         pi_pred = pi_pred,
#                         d = d,
#                         y = y)) 
#   truth <- mean(dat$y.1) - mean(dat$y.0)
# 
#   logit_logit_pred_list[[i]] <-  data.frame(ate = ate * (max(dat$y)-min(dat$y)),
#                                             truth = truth)
# }
# 
# perform(bind_rows(logit_logit_pred_list), label = 'ols, logit, tmle')
# 
# 
# #### 
# 
# grf_pred_list <- list()
# 
# for(i in 1:10){ #length(sim_linear)){
#   print(i)
#   dat <- sim_linear[[i]]
#   
#   grf_pred_out <- grf_pred(
#     y = dat$y, # with(dat, (y - min(y)) / (max(y) - min(y))),
#     d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
#     x = dat$x
#     )
#   
#   yt <- function(x, y){(x - min(y)) / (max(y) - min(y))}
#   
#   ate <- with(grf_pred_out, 
#               tmle_calc(mu1_pred = yt(mu1_pred, dat$y), 
#                         mu0_pred = yt(mu0_pred, dat$y),
#                         pi_pred = pi_pred,
#                         d = d,
#                         y = yt(y, dat$y)))
#   truth <- mean(dat$y.1) - mean(dat$y.0)
#   
#   grf_pred_list[[i]] <-  data.frame(ate = ate * (max(dat$y)-min(dat$y)),
#                                             truth = truth)
# }
# 
# perform(bind_rows(grf_pred_list), label = 'grf, tmle')

# superlearner_pred_list <- list()
# 
# for(i in 1:length(sim_linear)){
#   print(i)
#   dat <- sim_linear[[i]]
#   
#   superlearner_pred_out <- superlearner_pred(
#     y = with(dat, (y - min(y)) / (max(y) - min(y))),
#     d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
#     x = dat$x
#     )
#   
#   ate <- with(superlearner_pred_out, 
#               tmle_calc(mu1_pred = mu1_pred, 
#                         mu0_pred = mu0_pred,
#                         pi_pred = pi_pred,
#                         d = d,
#                         y = y))
#   truth = mean(dat$y.1) - mean(dat$y.0)
#   
#   superlearner_pred_list[[i]] <- data.frame(ate = ate * (max(dat$y)-min(dat$y)),
#                                             truth = truth)
# }
# 
# perform(bind_rows(superlearner_pred_list), label = 'superlearner, tmle')
```

```{r dml, eval = F}

## DML OLS logit

ols_logit_dml_list <- list()

set.seed(1285)
for(i in 1:length(sims)){
  print(i)
  dat <- sims[[i]]

  start_time <- Sys.time()
  dml_pre_out <- dml_pre(dat$y,
                       as.numeric(ifelse(dat$z == 'trt', 1, 0)),
                       x = dat$x)

  ols_logit_dml_out <- do.call(ols_logit_dml, dml_pre_out)

  dml_post_out <- do.call(dml_post, append(dml_pre_out, ols_logit_dml_out))
  comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))

  truth <- mean(dat$y.1) - mean(dat$y.0)

  ols_logit_dml_list[[i]] <- data.frame(ate = dml_post_out, 
                              truth = truth, 
                              comp_time = comp_time)
}

write_csv(bind_rows(ols_logit_dml_list), 
          here('files/homemade/', 'dml_ols_logit.csv'))

# perform(bind_rows(ols_logit_dml_list), label = 'grf, dml')

## GRF
grf_dml_list <- list()

set.seed(1285)
for(i in 1:length(sims)){
  print(i)
  dat <- sims[[i]]

  start_time <- Sys.time()

  dml_pre_out <- dml_pre(dat$y,
                       as.numeric(ifelse(dat$z == 'trt', 1, 0)),
                       x = dat$x)

  grf_dml_out <- do.call(grf_dml, dml_pre_out)

  dml_post_out <- do.call(dml_post, append(dml_pre_out, ols_logit_dml_out))

  comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))

  truth <- mean(dat$y.1) - mean(dat$y.0)

  grf_dml_list[[i]] <- data.frame(ate = dml_post_out, 
                              truth = truth, 
                              comp_time = comp_time)
}

write_csv(bind_rows(grf_dml_list), 
          here('files/homemade/', 'dml_grf.csv'))

# perform(bind_rows(grf_dml_list), label = 'grf, dml')

## Superlearner
superlearner_dml_list <- list()

set.seed(1285)
for(i in 1:length(sims)){
  print(i)
  dat <- sims[[i]]

  start_time <- Sys.time()

  dml_pre_out <- dml_pre(dat$y,
                       as.numeric(ifelse(dat$z == 'trt', 1, 0)),
                       x = dat$x)

  superlearner_dml_out <- do.call(superlearner_dml, dml_pre_out)

  dml_post_out <- do.call(dml_post, append(dml_pre_out, ols_logit_dml_out))

  comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))

  truth <- mean(dat$y.1) - mean(dat$y.0)

  superlearner_dml_list[[i]] <- data.frame(ate = dml_post_out, 
                              truth = truth, 
                              comp_time = comp_time)
}

write_csv(bind_rows(superlearner_dml_list), 
          here('files/homemade/', 'dml_superlearner.csv'))

#perform(bind_rows(superlearner_dml_list), label = 'superlearner, dml')

```

```{r dorie-results}

lm_df <- read_csv(here('files', 'lm_df.csv')) %>%
  mutate(method = 'ols')

psm_df <- read_csv(here('files', 'psm_df.csv')) %>%
  mutate(method = 'psm')

aipw_df <- read_csv(here('files/homemade', 'aipw.csv')) %>%
  mutate(estimator = method,
         method = 'aipw')

aipw_trunc_df <- read_csv(here('files/homemade', 'aipw_trunc.csv')) %>%
  mutate(estimator = method,
         method = 'aipw (trim)')

tmle_df <- read_csv(here('files/homemade', 'tmle.csv')) %>%
  filter(fail == F) %>%
  select(-fail) %>%
  mutate(estimator = method,
         method = 'tmle')

dml_df <- bind_rows(
  mutate(read_csv(here('files/homemade', 'dml_ols_logit.csv')), 
         estimator = 'ols_logit',
         method = 'dml',
         dataset = row_number()),
  mutate(read_csv(here('files/homemade', 'dml_grf.csv')), 
         estimator = 'grf',
         method = 'dml',
         dataset = row_number()),
  mutate(read_csv(here('files/homemade', 'dml_superlearner.csv')), 
         estimator = 'superlearner',
         method = 'dml',
         dataset = row_number())
) %>%
  select(dataset, estimator, ate, truth, comp_time, method)

bind_rows(lm_df, psm_df, aipw_trunc_df, tmle_df, dml_df) %>%
  mutate(estimator = factor(estimator, levels = c('ols_logit', 'grf', 'superlearner')),
         method = factor(method, levels = c('ols', 'psm', 'aipw', 'aipw (trim)', 'tmle', 'dml'))) %>%
  filter(dataset <= 200) %>%
  group_by(estimator, method) %>%
  summarize(bias = round(mean(ate - truth), 3),
              percent_bias = bias/sd(ate),
              rmse = round(sqrt(mean((ate - truth)^2)), 3),
              mae = median(abs(ate - truth)),
              comp_time = sum(comp_time)/n()
              ) %>%
  select(method, everything()) %>%
  arrange(method, estimator) %>%
  # mutate(bias = as.character(bias),
  #        rmse = as.character(rmse)) %>%
  # mutate(across(bias:comp_time, function(x){as.character(round(x, 3))})) %>%
  kableExtra::kable(booktabs = T, 
                    digits = 3,
                    linesep = '',
                    caption = 'Results of Monte Carlo simulations using the first 20 datasets from Dorie et al. (2019), 10 replications each. Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is average computation time measured in seconds for each dataset.')
```

```{r dorie-results-linear}
bind_rows(lm_df, psm_df, aipw_trunc_df, tmle_df, dml_df) %>%
  mutate(estimator = factor(estimator, levels = c('ols_logit', 'grf', 'superlearner')),
         method = factor(method, levels = c('ols', 'psm', 'aipw', 'aipw (trim)', 'tmle', 'dml'))) %>%
  filter(dataset > 200) %>%
  group_by(estimator, method) %>%
  summarize(bias = round(mean(ate - truth), 3),
              percent_bias = bias/sd(ate),
              rmse = round(sqrt(mean((ate - truth)^2)), 3),
              mae = median(abs(ate - truth)),
              comp_time = sum(comp_time)/n()
              ) %>%
  select(method, everything()) %>%
  arrange(method, estimator) %>%
  mutate(bias = as.character(bias),
         rmse = as.character(rmse)) %>%
  # mutate(across(bias:comp_time, function(x){as.character(round(x, 3))})) %>%
  kableExtra::kable(booktabs = T, 
                    digits = 3,
                    linesep = '',
                    caption = 'Results of Monte Carlo simulations using the two datasets from Dorie et al. (2019), with linear data generating processes, 100 replications each ("linear"). Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is average computation time measured in seconds for each dataset.')
```

## Comparisons using LaLonde NSW Data

As another test, I use data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW), as provided by @dehejia_1999_causal. Between March 1975 and July 1977, the NSW randomly provided training to disadvantaged workers. LaLonde used earnings in 1978 as the outcome of interest; comparing earnings in this year for treated and untreated workers allows an experimental estimate of the effect of the intervention. Restricting the sample to men, this study had `r nrow(filter(lalonde_exp, treat == T))` treated and `r nrow(filter(lalonde_exp, treat == F))` control participants. Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, and not having a high school degree. Following @dehejia_1999_causal, I add a variable indicating whether each respondent's earnings in 1975 was $0 -- i.e., they were unemployed.

LaLonde compared these experimental estimates to control samples drawn from the Panel Study of Income Dynamics (PSID) and Westat's Matched Current Population Survey-Social Security Administration File (CPS). The PSID-1 sample (*n* = `r nrow(lalonde_psid1_controls)`) contains all male household heads under 55 who did not classify themselves as retired in 1975, and the PSID-3 sample (*n* = `r nrow(lalonde_psid3_controls)`) further restricts this to men who were not working in spring of 1975 or 1976. The CPS-1 sample (*n* = `r nrow(lalonde_cps1_controls)`) includes all CPS males under 55, and CPS-3 (*n* = `r nrow(lalonde_cps3_controls)`) restricts this to those who were not working in March 1976 whose earnings in 1975 was below the poverty level. Restricting these observational samples gets closer to the group eligible for the NSW.

Following @dehejia_1999_causal, I present results for the original samples analyzed by @lalonde_1986_evaluating, but I also include results using a subsample of the experimental group that has 1974 earnings data available (`r nrow(filter(lalonde_exp_74, treat == T))` treated and `r nrow(filter(lalonde_exp_74, treat == F))` control participants) and include this additional covariate, along with an indicator variable for no earnings in 1974.

I again compare the three double robust methods to a linear model fitted by OLS ("ols") and propensity score matching using logistic regression ("psm"). Results are presented in Table \@ref(tab:lalonde).

The "experimental" column provides a baseline for the comparison, suggesting that the program resulted in an earnings gain of about \$700 to \$800. If selection on observables holds, then we should be able to recover these estimates from the non-experimental control groups. Most of the methods do not perform very well; the only ones to estimate a positive treatment effects are OLS for the PSID-3 sample and TMLE for the CPS samples, and these are still smaller than the experimental baselines.

Including 1974 earnings data results in much better estimates with the observational control groups. For PSID-1, TMLE provides estimates closest to the experimental ones, while DML performs much worse than even OLS. For PSID-3, OLS and TMLE both perform well. For CPS-1 and CPS-3, TMLE performs the best.

These results highlight the importance of selection on observables holding. Without including 1974 earnings as a covariate, it appears that selection on observables does not hold, as most methods provide highly inaccurate estimates with the wrong sign. Once 1974 earnings are included, all of the methods provide estimates much closer to the experimental values. PSM, AIPW, and TMLE all do fairly well, while OLS and DML are more unstable across samples.

```{r lalonde-calc-homemade, eval = F}

lalonde_func <- function(dataset, sample, include_74 = F){
  set.seed(872)

  if(include_74 == F){
    lalonde_variables <- names(lalonde_exp)[3:9]
    dataset <- bind_rows(filter(lalonde_exp, treat == 1), dataset)

  } else {
    lalonde_variables <- names(lalonde_exp_74)[3:10]
    dataset <- bind_rows(filter(lalonde_exp_74, treat == 1), dataset)
  }

  dat <- list(y = dataset$re78,
                z = ifelse(dataset$treat == 1, 'trt', 'ctl'),
                x = dataset[,lalonde_variables])

  out_list <- list()

  out_list[['ols']] <- data.frame(
      method = 'ols',
      estimator = NA,
      ate = lm_sim(list(dat))$est_df$ate)

  out_list[['psm']] <- data.frame(
      method = 'psm',
      estimator = NA,
      ate = lm_sim(list(dat))$est_df$ate)

  ols_logit_pred_out <- ols_logit_pred(
    y = dat$y,
    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
    x = dat$x)

  grf_pred_out <- grf_pred(
    y = dat$y,
    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
    x = dat$x)

  superlearner_pred_out <- superlearner_pred(
    y = dat$y,
    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
    x = dat$x)

  predictions <- list(ols_logit_pred_out, grf_pred_out, superlearner_pred_out)
  pred_names <- c('ols_logit', 'grf', 'superlearner')
  for(j in 1:length(predictions)){
    aipw_out <- with(predictions[[j]], 
                     aipw_calc_trunc(mu1_pred = mu1_pred, 
                               mu0_pred = mu0_pred,
                               pi_pred = pi_pred,
                               d = d,
                               y = y))

    out_list[[paste0('aipw', j)]] <- data.frame(
      method = 'aipw',
      estimator = pred_names[[j]],
      ate = aipw_out)

    tmle_out <- with(predictions[[j]], 
                       tmle_calc(mu1_pred = normalize(mu1_pred, y), 
                                 mu0_pred = normalize(mu0_pred, y),
                                 pi_pred = pi_pred,
                                 d = d,
                                 y = normalize(y, y))
                       )

      out_list[[paste0('tmle', j)]] <- data.frame(
        method = 'tmle',
        estimator = pred_names[[j]],
        ate =  denormalize(tmle_out, predictions[[j]]$y))
  }

  dml_pre_out <- dml_pre(dat$y,
                         as.numeric(ifelse(dat$z == 'trt', 1, 0)),
                         x = dat$x)
  ols_logit_dml_out <- do.call(ols_logit_dml, dml_pre_out)
  dml_post_out <- do.call(dml_post, append(dml_pre_out, ols_logit_dml_out))

  out_list[['dml_ols_logit']] <- data.frame(method = 'dml',
                                            estimator = 'ols_logit',
                                            ate = dml_post_out)

  dml_pre_out <- dml_pre(dat$y,
                     as.numeric(ifelse(dat$z == 'trt', 1, 0)),
                     x = dat$x)
  grf_dml_out <- do.call(ols_logit_dml, dml_pre_out)
  dml_post_out <- do.call(dml_post, append(dml_pre_out, grf_dml_out))

  out_list[['dml_grf']] <- data.frame(method = 'dml',
                                            estimator = 'grf',
                                            ate = dml_post_out)

  dml_pre_out <- dml_pre(dat$y,
                     as.numeric(ifelse(dat$z == 'trt', 1, 0)),
                     x = dat$x)
  superlearner_dml_out <- do.call(ols_logit_dml, dml_pre_out)
  dml_post_out <- do.call(dml_post, append(dml_pre_out, superlearner_dml_out))

  out_list[['dml_superlearner']] <- data.frame(method = 'dml',
                                            estimator = 'superlearner',
                                            ate = dml_post_out)

  bind_rows(out_list) %>%
    mutate(sample = sample) %>%
    return()
}

lalonde_func_out <- bind_rows(
  lalonde_func(filter(lalonde_exp, treat == 0), sample = 'experimental'),
  lalonde_func(lalonde_psid1_controls, 'PSID-1'),
  lalonde_func(lalonde_psid3_controls, 'PSID-3'),
  lalonde_func(lalonde_cps1_controls, 'CPS-1'),
  lalonde_func(lalonde_cps1_controls, 'CPS-3'))

  lalonde_func_out %>%
    pivot_wider(names_from = 'sample', values_from = ate) %>%
  mutate(estimator = factor(estimator, levels = c('ols_logit', 'grf', 'superlearner')),
         method = factor(method, levels = c('ols', 'psm', 'aipw', 'aipw (trim)', 'tmle', 'dml'))) %>%
  arrange(method, estimator) %>%
  #write_csv(here('files/homemade', 'lalonde.csv'))

bind_rows(
  lalonde_func(filter(lalonde_exp_74, treat == 0), sample = 'experimental', T),
  lalonde_func(lalonde_psid1_controls, 'PSID-1', T),
  lalonde_func(lalonde_psid3_controls, 'PSID-3', T),
  lalonde_func(lalonde_cps1_controls, 'CPS-1', T),
  lalonde_func(lalonde_cps1_controls, 'CPS-3', T)) %>%
    pivot_wider(names_from = 'sample', values_from = estimate) %>%
  write_csv(here('files/homemade', 'lalonde_74.csv'))

```

```{r lalonde-calc, eval = F}
unemp_func <- function(x){
  x %>%
    as.data.frame() %>%
    mutate(re74_0 = re74 == 0,
         re75_0 = re75 == 0) 
}

lalonde_exp <- read_dta(here('data', 'nsw.dta')) %>%
  as.data.frame() %>%
  mutate(re75_0 = re75 == 0)
lalonde_exp_74 <- read_dta(here('data', 'nsw_dw.dta')) %>%
  unemp_func()
lalonde_cps1_controls <- read_dta(here('data', 'cps_controls.dta')) %>%
  unemp_func()
lalonde_cps3_controls <- read_dta(here('data', 'cps_controls3.dta')) %>%
  unemp_func()
lalonde_psid1_controls <- read_dta(here('data', 'psid_controls.dta')) %>%
  unemp_func()
lalonde_psid3_controls <- read_dta(here('data', 'psid_controls3.dta')) %>%
  unemp_func()

lalonde_func <- function(dataset, sample, include_74 = F){
  set.seed(872)

  if(include_74 == F){
    lalonde_variables <- names(lalonde_exp)[3:9]
    dataset <- bind_rows(filter(lalonde_exp, treat == 1), dataset)

  } else {
    lalonde_variables <- names(lalonde_exp_74)[3:10]
    dataset <- bind_rows(filter(lalonde_exp_74, treat == 1), dataset)
  }

  dataset <- list(list(y = dataset$re78,
                z = ifelse(dataset$treat == 1, 'trt', 'ctl'),
                x = dataset[,lalonde_variables]))

  lapply(list(
    lm_sim(dataset),
    psm_sim(dataset),
    aipw_sim(dataset),
    tmle_sim(dataset),
    dml_sim(dataset)),
  bind_cols) %>%
    bind_rows() %>%
    mutate(method = c('ols', 'psm', 'aipw', 'tmle', 'dml'),
           sample = sample,
           ate = round(d),
           se = round(se),
           estimate = paste0(round(d), ' (', round(se), ')')) %>%
    select(method, sample, estimate) 
}

bind_rows(
  lalonde_func(filter(lalonde_exp, treat == 0), sample = 'experimental'),
  lalonde_func(lalonde_psid1_controls, 'PSID-1'),
  lalonde_func(lalonde_psid3_controls, 'PSID-3'),
  lalonde_func(lalonde_cps1_controls, 'CPS-1'),
  lalonde_func(lalonde_cps1_controls, 'CPS-3')) %>%
    pivot_wider(names_from = 'sample', values_from = estimate) %>%
  write_csv(here('files', 'lalonde.csv'))

bind_rows(
  lalonde_func(filter(lalonde_exp_74, treat == 0), sample = 'experimental', T),
  lalonde_func(lalonde_psid1_controls, 'PSID-1', T),
  lalonde_func(lalonde_psid3_controls, 'PSID-3', T),
  lalonde_func(lalonde_cps1_controls, 'CPS-1', T),
  lalonde_func(lalonde_cps1_controls, 'CPS-3', T)) %>%
    pivot_wider(names_from = 'sample', values_from = estimate) %>%
  write_csv(here('files', 'lalonde_74.csv'))
```

```{r lalonde}
bind_rows(
  read_csv(here('files', 'lalonde.csv')) %>%
    mutate(sample = 'Original LaLonde'),
  read_csv(here('files', 'lalonde_74.csv')) %>%
    mutate(sample = 'With 1974 earnings')) %>%
  select(sample, method, everything()) %>%
  kableExtra::kable(booktabs = T, 
                    # digits = 3,
                    # linesep = '',
                    caption = 'ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups. Standard errors shown in parentheses. Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975. The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnigns in 1974.')

# bind_rows(
#   read_csv(here('files', 'lalonde.csv')) %>%
#     mutate(sample = 'LaLonde'),
#   read_csv(here('files', 'lalonde_74.csv')) %>%
#     mutate(sample = 'DW (with 1974 earnings)')) %>%
#   select(sample, everything()) %>%
#   kableExtra::kable(booktabs = T, 
#                     # digits = 3,
#                     linesep = '',
#                     caption = 'ATE estimates for Lalonde NSW data from Dehejia and Wahba (1999), with PSID ')

# lalonde_exp_df <- filter(lalonde, exper == 1)
# fit <- CBPS::CBPS(treat ~ age + educ + re75 + re74 + 
# 			I(re75==0) + I(re74==0), 
# 			data = lalonde_exp_df, ATT = TRUE)
# summary(fit)
# m.out <- MatchIt::matchit(treat ~ fitted(fit), method = "nearest", 
# 				 data = lalonde_exp_df, replace = TRUE)
# lm(re78 ~ treat + age + educ + re75 + re74, MatchIt::match.data(m.out), weights = weights) %>%
#   tidy()
# 
# 
# lalonde_psid_df <- filter(lalonde, (exper == 1 & treat == 1) | exper == 0)
# fit <- CBPS::CBPS(treat ~ age + educ + re75 + re74 + 
# 			I(re75==0) + I(re74==0), 
# 			data = lalonde_psid_df, ATT = TRUE)
# m.out <- MatchIt::matchit(treat ~ fitted(fit), method = "nearest", 
# 				 data = lalonde_psid_df, replace = TRUE)
# lm(re78 ~ treat + age + educ + re75 + re74, MatchIt::match.data(m.out), weights = weights) %>%
#   tidy()
```

# Conclusion

This paper aimed to provide an introduction to and evaluation of double robust methods for covariate adjustment in causal inference. By comparing AIPW, TMLE, and DML to the more traditional statistical methods of OLS and PSM, it allows evaluation of whether these methods are worth the effort and (computational) time for social scientists to adopt them.

Results are mixed. On the one hand, in the full range of simulated data, AIPW with GRF estimators achieves the lowest bias and root mean squared error. This is the simplest (and most computationally efficient) of the double robust methods, although GRF is computationally expensive. TMLE with GRF also does fairly well. But OLS and PSM have strong showings, in the top three smallest bias or root mean squared error. In the datasets with linear data-generating processes, OLS achieves the lowest bias and root mean squared error.

In the experimental LaLonde data, OLS does not perform as strongly. Although it is one of the few methods to provide experimental estimates with the correct sign in the original LaLonde set of covariates, its estimates are highly unstable across samples. When 1974 earnings are used as a covariate, PSM, AIPW, and TMLE all perform fairly well, though TMLE comes out on top.

Overall, these double robust methods do not show a clear advantage over simpler, more computationally efficient methods such as OLS and PSM. While they are useful for social scientists to understand, in most applications, OLS or PSM provide similar results. However, in certain circumstances these double robust methods may be a better choice. Especially when paired with a highly flexible estimator like GRF, these methods can be useful when the number of covariates is high or even exceeds the number of observations. If the researcher believes the data-generating process is highly nonlinear, they may also be a good a choice, at least as a sensitivity check.

\newpage

# References

### 2024-07-29 draft/ms-adj-appendix.Rmd
replications

--- 2024-01-25 draft/ms-adj-draft.Rmd
@@
   bookdown::pdf_document2:
-    toc: no
+    toc: yes
+    keep_tex: true
     number_sections: yes
     pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
-    latex_engine: xelatex
+    #latex_engine: xelatex
 always_allow_html: true
@@
   - \rhead{`r format(Sys.time(), '%B %e, %Y')`}
+  - \counterwithin{figure}{section}
+  - \counterwithin{table}{section}
 # - \newcommand{\beginsupplement}{\setcounter{table}{0}  
@@
 citeproc: no
-fontfamily: mathpazo
-#fontsize: 11pt
+#fontfamily: mathpazo
+# fontsize: 12pt
 # geometry: margin=.6in
@@
 
-title: "Double Robust, Flexible Adjustment Methods for Causal Inference: An Overview and an Evaluation"
-# subtitle: "American Sociological Association Annual Meeting 2024"
-author:  Nathan I. Hoffmann, Department of Sociology, UCLA
+title: "Online Appendix"
+subtitle: "Double Robust, Flexible Adjustment Methods for Causal Inference: An Overview and an Evaluation"
+
+author:  Nathan I. Hoffmann, Departments of Sociology and Statistics, UCLA
 date: "`r format(Sys.time(), '%B %e, %Y')`"
 
-abstract: "Double robust methods for flexible covariate adjustment in causal inference have proliferated in recent years.
-Despite their apparent advantages, these methods remain underutilized by social scientists.
-It is also unclear whether these methods actually outperform more traditional methods in finite samples.
-This paper has two aims: It is a guide to some of the latest methods in double robust, flexible covariate adjustment for causal inference, and it compares these methods to more traditional statistical methods.
-It does this by using both simulated data where the treatment effect estimate is known, and then using comparisons of experimental and observational data from the National Supported Work Demonstration.
-Methods covered include Augmented Inverse Probability Weighting, Targeted Maximum Likelihood Estimation, and Double/Debiased Machine Learning.
-Results suggest that these methods do not necessarily outperform OLS regression or matching on propensity score estimated by logistic regression, even in cases where the data generating process is not linear."
-
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T)
+knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T, dev = c('pdf', 'png'), fig.retina = 3, ft.latex.float = 'float')
 options("yaml.eval.expr" = TRUE)
@@
 }
-```
-
-<!-- # Abstract -->
-
-<!-- This thesis aims to compare different advanced adjustment methods.
-It will compare Imben & Rubins propensity matching, stabilized IPWs, TMLE, double machine learning (Chernozhukov et al 2018), Ratkovic (2021), and BART.
--->
-
-# Introduction
-
-Statistical methods for flexible covariate adjustment in causal inference have proliferated in recent years.
-These methods have a number of strengths over traditional regression methods: They make few functional form assumptions, can accommodate large numbers of covariates, and produce easily interpretable treatment effect estimates.
-Many of these methods also have a "double robust" property: They estimate one model for the treatment exposure and another for the outcome, and as long as at least one is correctly specified, then the treatment effect will be estimated consistently.
-Despite their apparent advantages, these methods remain underutilized by social scientists.
-Part of the barrier has been lack of familiarity with these methods.
-It has also been unclear how these methods compare, or whether such methods actually perform better than traditional methods in finite samples.
-<!-- And when researchers want to use an existing R package for these methods, the array of possible estimation methods and other options can be dizzying.   -->
-
-This paper makes advances on these fronts.
-First, it is a guide to some of the latest methods in double robust, flexible covariate adjustment for causal inference, explaining the methods to a social scientist audience.
-Second, it compares these methods to more traditional statistical methods using both simulations [@dorie_2019_automated] and the National Support for Work Demonstration (NSW) originally analyzed by @lalonde_1986_evaluating.
-
-Methods covered include Augmented Inverse Probability Weighting [AIPW, @glynn_2010_introduction], Targeted Maximum Likelihood Estimation [TMLE, @vanderlaan_2006_targeted], and Double or Debiased Machine Learning [DML, @chernozhukov_2018_double].
-This paper reviews the theory behind these methods as well as simple R implementations of them on simulations and real data.
-These methods are compared to two methods commonly used by social scientists: ordinary least squares (OLS) regression, and matching on propensity scores estimated from logistic regression (PSM).
-
-# Motivation
-
-## Literature Review
-
-Although previous work has compared different methods for covariate adjustment, there has not yet been a thorough evaluation and comparison of the recent and popular double robust methods of AIPW, TMLE, and DML.
-@austin_2014_comparison compares methods for matching on the propensity score.
-@dorie_2019_automated report the results for the Atlantic Causal Inference Conference 2016 competition.
-Some of the methods used incorporate TMLE but not AIPW or DML.
-@cousineau_2022_estimating evaluates the performance of optimization-baseds methods for causal inference, but these do not include the double robust methods covered in the current paper.
-@kang_2007_demystifying provide an overview and evaluation of double robust methods in the context of missing data.
-The authors consider AIPW but not TMLE or DML.
-@chatton_2020_gcomputation compare four methods: G-computation, IPW, full matching, and TMLE.
-These authors only consider one double robust method, and their focus is on omitted variable bias rather than determining which method is the most useful.
-@knaus_2022_double reviews double robust methods in an econometrics setting but does not compare them to traditional statistical methods for covaraite adjustment.
-
-## Historical Overview
-
-According to @bang_2005_doubly, double robust methods have their origins in missing data models.
-@robins_1994_estimation and @rotnitzky_1998_semiparametric developed augmented orthogonal inverse probability-weighted (AIPW) estimators in missing data models, and @scharfstein_1999_adjusting showed that AIPW was double robust and extended to causal inference (since causal inference is fundamentally a missing data problem).
-
-But @kang_2007_demystifying argue that double robust methods are older.
-They cite work by @cassel_1976_results, who proposed “generalized regression estimators” for population means from surveys where sampling weights must be estimated.
-Arguably, double robust methods go back even further than this.
-The form of double robust methods is similar to residual-on-residual regression, which dates back to @frisch_1933_partial famous FWL theorem:
-
-$$\beta_D = \frac{\text{Cov}(\tilde Y_i, \tilde D_i)}{\text{Var}(\tilde D_i)}$$
-
-where $\tilde D_i$ is the residual part of $D_i$ after regressing it on $X_i$, and $\tilde Y_i$ is the residual part of $Y_i$ after regressing it on $X_i$.
-This formulation writes the regression coefficient as composed of an outcome model ($\tilde Y_i$) and exposure model ($\tilde D_i$), the two models used in double robust estimators.
-
-There are also links between double robust methods and matching with regression adjustment.
-This work goes back to at least @rubin_1973_use, who suggested that regression adjustment in matched data produces less biased estimates that either matching (exposure adjustment) or regression (outcome adjustment) do by themselves.
-
-Today, double robust methods abound [e.g.
-@ratkovic_2023_relaxing; @sloczynski_2018_general; @arkhangelsky_2021_doublerobust; @dukes_2022_doubly; @kennedy_2023_semiparametric].
-This paper focuses on three of the more popular or fundamental methods.
-
-## Aims of Double Robust Methods
-Double robust methods for covariate adjustment aim to overcome what many consider to be the downsides of both traditional statistical methods and flexible machine learning methods.
-Statistical methods that are popular with social scientists -- such as OLS regression and matching on propensity scores from logistic regression -- have two main weaknesses that double robust methods address.
-First, they assume simple (linear or transformed linear) functional forms.
-In the presence of highly nonlinear data generating processes, they may provide biased estimates.
-Second, these methods cannot handle large numbers of covariates relative to sample size.
-While some machine learning methods can produce estimates even when the number of covariates exceeds the number of observations (such as lasso), OLS fails in this case due to the $X^\top X$ matrix not being of full rank and hence not invertible.
-In cases with many covariates, but not more than the number of observations, estimation is unstable with many traditional statistical methods.
-
-Flexible machine learning methods also have their drawbacks.
-First, naive application of these methods can result in overfitting, with predictive accuracy maximized in sample but treatment effect estimation being biased.
-Furthermore, results of these machine learning methods can be difficult to interpret without further processing.
-Machine learning methods have often been developed with a focus on prediction rather than on producing treatment effect point estimates.
-
-Double robust methods for covariate adjustment are also motivated by the idea that many older methods ignore information present in the data.
-Methods tend to model either the outcome -- as in OLS regression and G-computation -- or only the treatment assignment -- as in propensity score matching or inverse probability weighting.
-Double robust methods, on the other hand, model both of these.
-
-# Conceptual Overview
-
-Double robust methods estimate two models:
-
-- an *outcome model*
-
-$$\mu_d(X_i) = E(Y_i \mid D_i = d, X_i)$$
-
-- and an *exposure model* (or treatment model or propensity score):
-
-$$\pi(X_i) = E(D_i \mid X_i)$$
-
-where $\mu_d(\cdot)$ is the model of control or treatment $D_i = d=\{0, 1\}$, $X_i$ is a vector of covariates for unit $i = 1, \ldots, N$ for treatment (1) and control (0), $Y_i$ is the outcome, and $\pi(\cdot)$ is the exposure model.
-The covariates included in $X_i$ can be different for the two models.
-
-An estimator is called "double robust" if it achieves consistent estimation of the ATE (or whatever estimand the researcher is interested in) as long as *at least one* of these two models is consistently estimated.
-This means that the outcome model can be completely misspecified, but as long as the exposure model is correct, our estimation of the ATE will be consistent.
-This also means that the exposure model can be completely wrong, as along as the outcome model is correct.
-
-## Assumptions
-
-Most double robust methods require almost all of the standard assumptions necessary formost methods that depend on selection on observables.
-Although some double robust methods relax one or two of these, the six standard assumptions are:
-
-1. Consistency
-2. Positivity/overlap
-3. One version of treatment
-4. No interference
-5. IID observations
-6. Conditional ignorability: $\{Y_{i0}, Y_{i1}\} \perp \!\!\! \perp D_i \mid X_i$
-
-Special attention should be paid to Assumption 6: double robust methods will not work if we do not measure an important confounder that affects both treatment and exposure.
-But notably, the double robust methods covered in this tutorial make no functional form assumptions.
-These methods are designed to incorporate flexible machine learning algorithms to estimate both the outcome and exposure models, with regularization (often through cross-fitting) to avoid overfitting.
-
-# Overview of Techniques  
-Each of the methods reviewed in this paper can be thought of as a collection of estimation techniques.
-Each involves a model for the outcome and another for the treatment exposure, but the ways these relate and are combined varies from method to method.
-Choice of estimation technique for these two models is left to the discretion of the user; often ensemble learning is recommended, but in practice simpler methods can also work well.
-
-## Augmented Inverse Probability Weighting (AIPW)
-
-The oldest of these modern methods, AIPW arose in the context of missing data imputation [@robins_1994_estimation].
-@scharfstein_1999_adjusting showed that AIPW was double robust and extended to causal inference.
-Introductions to AIPW exist in the contexts of political science [@glynn_2010_introduction] and econometrics [@funk_2011_doubly].
-The `AIPW` R package provides a simple implementation of the method.
-
-AIPW combines estimates from a model for the treatment exposure, $\pi(X)$, and a model for the outcome, $\mu(X)$.
-The name comes from the close similarity to inverse probability weights (IPW), but whereas IPW only weights for probability of treatment, AIPW "augments" these weights with an estimate of the response surface.
-
-Formally, the model can be written as the difference between an estimated outcome for treated units and the estimated outcome for untreated units (see the demonstration below):
-
-$$\begin{aligned}
-\widehat{ATE}_{AIPW} = &\frac{1}{n} \sum_{i=1}^n \left( \frac{D_i(Y_i - \hat \mu_1 (\mathbf X_i))}{\hat \pi (\mathbf X_i)} + \hat \mu_1(\mathbf X_i) \right) 
-- \frac{1}{n} \sum_{i=1}^n \left( \frac{(1-D_i)(Y_i - \hat \mu_0 (\mathbf X_i))}{1-\hat \pi(\mathbf X_i)} + \hat \mu_0(\mathbf X_i) \right)
-\end{aligned}$$
-
-In practice, AIPW weights may be very small or very large, a problem that inverse probability weights also suffer from.
-This can make AIPW prone to high variance.
-To remedy this, the predicted probabilities of treatment are often truncated, setting extremely small or large weights to some less extreme value [as in the `AIPW` R package, @zhong_2021_aipw].
-
-Below is R code to implement AIPW with truncation of extreme weights.
-As with all of the double robust methods reviewed here, we begin with predicted values (such as from a machine learning algorithm) for the outcome for treated units `mu1_pred` and untreated units `mu0_pred` as well as predicted values for treatment assignment probability `pi_pred`.
-We also have `d`, the vector of actual treatment assignments, and `y`, the observed outcome values.
-
-```{r aipw-demo, eval = F, echo = T}
-require(tidyverse)
-
-aipw_calc <- function(mu1_pred, mu0_pred, pi_pred, d, y){
-  n <- length(mu1_pred)
-
-  # Truncate extreme values of the weights
-  pi_pred <- case_when(
-    pi_pred < .01 ~ .01,
-    pi_pred > .99 ~ .99,
-    T ~ pi_pred)
-
-  # Calculate the predicted outcome value for treated units
-  y1_pred <- (d*(y-mu1_pred))/pi_pred + mu1_pred
-  # Calculate the predicted outcome value for untreated units
-  y0_pred <- ((1-d)*(y-mu0_pred))/(1-pi_pred) + mu0_pred
-
-  # Calculate the ATE
-  ate <- (1/n)*(sum(y1_pred)) - (1/n)*sum(y0_pred)
-
-  return(ate)
-}
-```
-
-@glynn_2010_introduction provide an alternate but equivalent formula, where the basic inverse probability weight (IPW) estimator (which incorporates only the exposure model $\hat \pi$) is corrected using a weighted average of two outcome regression estimates:
-$$\begin{aligned}
-\widehat{ATE}_{AIPW} = & \frac{1}{n} \sum_{i=1}^n \left\{ \left[ \frac{D_i Y_i}{\hat \pi(\mathbf X_i)} - \frac{(1-D_i) Y_i}{ 1- \hat \pi(\mathbf X_i)} \right] - \frac{D_i - \hat \pi (\mathbf X_i)}{\hat \pi (\mathbf X_i)(1 - \hat pi (\mathbf X_i))} [(1- \hat \pi (\mathbf X_i)) \hat \mu_1(\mathbf X_i) + \hat \pi (\mathbf X_i) \hat \mu_0(\mathbf X_i)] \right\}
-\end{aligned}$$
-
-## Targeted Maximum Likelihood Estimation (TMLE)
-
-@vanderlaan_2006_targeted first proposed TMLE an extension and improvement of previous double robust methods, using a parametric framework and the efficient influence curve  [@hines_2022_demystifying] to obtain estimates and standard errors.
-Mark van der Laan has gone on to collaborate on both a gentle introduction [@gruber_2009_targeted], a textbook [@vanderlaan_2011_targeted], and an R package [@gruber_2012_tmle] for implementing the method.
-@schuler_2017_targeted and @luque-fernandez_2018_targeted provide introductions for epidemiologists.
-
-TMLE begins by estimating the relevant part of the data-generating distribution $P(Y)$, i.e.
-the conditional density $Q = P(Y \mid X)$.
-It next estimates the exposure model.
-Although any estimation method can be used for these steps, the originators of the method suggest using a "super learner," i.e.
-ensemble learning with cross-validation [@laan_2007_super].
-Next, the exposure model is used to calculate a "clever covariate," which is similar to an IPW.
-The coefficient for this clever covariate is estimated using maximum likelihood -- whence the "MLE" in "TMLE." Finally, the estimate of $Q$ is updated in a function involving the clever covariate.
-This process can be iterated, but usually one iteration is enough.
-The estimate of the distribution $Q$ can be used to calculate the estimand of interest.
-
-Formally, first generate estimates of $\mu_{d}(\mathbf X_i) = E(Y \mid D=d, \mathbf X_i)$ and $\pi(\mathbf X_i) = P(D=1 \mid \mathbf X_i)$. Then create the variable $H_{di}$ for targeting step:
-$$H_{di} = \frac{I(D_i = 1)}{\hat \pi (\mathbf X_i)} - \frac{I(D_i=0)}{1 - \hat \pi (\mathbf X_i)}$$
-
-Next, calculate the clever covariates for each individual in the data. These quantities are similar to inverse probability weights, with $H_{0i}$ for untreated and $H_{0i}$ for treated units:
-$$\begin{aligned}
-H_{0i}(D=0, \mathbf X_i) &= \frac{1-d_i}{1- \hat \pi (\mathbf X_i)}, &
-H_{1i}(D=1, \mathbf X_i) = \frac{d_i}{\hat \pi (\mathbf X_i)}.
-\end{aligned}$$
-
-In the next step, we estimate fluctuation parameters $\epsilon = (\epsilon_0, \epsilon_1)$ through maximum likelihood of the following logistic regression with fixed intercept $\text{logit}(\mu_{di})$:
-<!-- $$E(Y=1 \mid D, \mathbf X) = \text{logit}(\mu_{di}) + \epsilon H_{di}$$ -->
-$$\text{logit}[E(Y=1 \mid D, \mathbf X)] = \text{logit}(\hat \mu_{di}) + \epsilon_0 H_{0i} + \epsilon_1 H_{1i}$$
-
-Here we are assuming that $Y$ is a dichotomous variable taking the values of 0 or 1; the method is extended to continuous outcomes simply by normalizing the value of $Y$ to fall between 0 and 1.
-Then generate updated ("targeted") estimates of potential outcomes:
-$$\begin{aligned}
-\hat \mu_0^*(\mathbf X_i) &= \text{expit}[\text{logit}(\hat \mu_0(\mathbf X_i)) + \hat \epsilon H_{0i}]\\
-\hat \mu_1^*(\mathbf X_i) &= \text{expit}[\text{logit}(\hat \mu_1(\mathbf X_i)) + \hat \epsilon H_{1i}]
-\end{aligned}$$
-
-Finally, estimate the parameter of interest -- in this case, the ATE:
-$$\widehat{ATE}_{TMLE} = \frac{1}{n} \sum_{i=1}^n [\hat \mu_1^*(\mathbf X_i) - \hat \mu_0^*(\mathbf X_i)]$$
-
-Here is R code to implement TMLE, again with predicted outcome values `mu1_pred` and `mu0_pred` and predicted probability of treatment `pi_pred`.
-Since the outcome is bounded and continuous, it is transformed to fall between 0 and 1 via $\tilde Y_{i} = Y_i - \min(Y)/(\max(Y)-\min(Y)$.
-```{r tmle-demo, eval = F, echo = T}
-# Functions for normalization and de-normalization
-normalize <- function(x, y){(x - min(y)) / (max(y) - min(y))}
-denormalize <- function(x, y){x * (max(y) - min(y))}
-
-tmle_calc <- function(mu1_pred, mu0_pred, pi_pred, d, y){
-  # Normalize outcome variable
-  mu1_pred <- normalize(mu1_pred, y)
-  mu0_pred <- normalize(mu0_pred, y)
-  y_tilde <- normalize(y, y))
-
-  n <- length(y)
-
-  # Calculate clever covariates
-  H0 = (1-d)/(1-pi_pred)
-  H1 = d/pi_pred
-
-  # Estimate fluctuation parameter through maximum likelihood estimation
-  epsilon <- glm(y_tilde ~ -1 + H0 + H1 + offset(qlogis((d==1)*mu1_pred + (d==0)*mu0_pred)),
-                 family = binomial(link = 'logit')) %>%
-    tidy() %>%
-    pull(estimate)
-
-  # Targeted estimates of the potential outcomes
-  target_0 <- plogis(qlogis(mu0_pred + epsilon[1]*H0))
-  target_1 <- plogis(qlogis(mu1_pred + epsilon[2]*H1))
-
-  # Estimate ATE
-  ATE <- mean(target_1 - target_0)
-  return(denormalize(ATE, y))
-}
-```
-
-## Double/Debiased Machine Learning (DML)
-
-The most recently developed of the methods reviewed here, DML was proposed in an econometrics context [@chernozhukov_2018_double] and has since seen a flurry of development [@dukes_2022_doubly; @kennedy_2023_semiparametric; @semenova_2021_debiased; @chernozhukov_2022_long; @farbmacher_2022_causal; @jung_2021_estimating].
-The R package `DoubleML` [@bach_2021_doubleml] provides straightforward implementation of the method.
-
-DML is motivated by the need to handle problems with high-dimensional nuisance parameters, i.e.
-a large number of measured confounders.
-Flexible machine learning is appropriate for this task, but such methods suffer from regularization bias.
-DML removes this bias in a two-step procedure.
-First, it solves the auxiliary problem of estimating the treatment exposure model $E(D|X) = \pi(X)$.
-It then uses this model to remove bias: Neyman orthogonalization allows the creation of an orthogonalized regressor, essentially partialing out the effect of covariates $X$ from treatment $D$.
-The debiased $D$ is then used to estimate the conditional mean of the outcome $E(Y \mid X) = \mu(X)$, which can be used to calculate the estimand of interest.
-
-More formally, suppose we want to estimate $\delta$ in the following framework:
-$$y_i = \delta d_i + g_0(\mathbf x_i) + u_i,$$
-$$d_i = m_0(\mathbf x_i) + v_i.$$
-
-The idea is to estimate $g_0$ and $m_0$ separately, then use residual-on-residual regression to obtain an estimate of $\delta$, which we can designate $\hat \delta$.
-However this leaves a term in the asymptotic distribution of $\hat \delta$ that biases the estimate.
-To avoid this, DML uses sample splitting [@angrist_1995_splitsample].
-
-We randomly split the sample of $n$ observations into two sets, $I$ and $I^c$, each of size $n/2$.
-Using any prediction algorithm, we then estimate the response and treatment models using only set $I^c$:
-
-1) Estimate treatment model $\hat m_0$ in the equation $d_i = \hat m_0(\mathbf x_i) + \hat v_i, i \in I^c$.  
-2) Estimate the outcome model $\hat g_0$ in the equation $y_i =  \hat g_0(\mathbf x_i) + \hat u_i, i \in I^c$.
-
-Note that the estimation of the outcome does not consider treatment assignment $d_i$. This is a key difference between DML and AIPW or TMLE.
-
-Next, we use the estimated models to perform residual-on-residual regression *on the left out set* $I$ to obtain an estimate of $\delta$:
-$$\hat \delta(I^c, I) = \left(\sum_{i \in I} \hat v_i d_i \right)^{-1} 
-\sum_{i \in I} \hat v_i (y_i - \hat g_0 (\mathbf x_i)),$$
-
-where $\hat v_i = d_i - \hat m_0(\mathbf x_i)$.
-Using half the sample results in efficiency loss.
-To rectify this, we repeat the above procedure, switching the split sets.
-We then have $\delta(I^c, I)$ and $\delta(I, I^c)$.
-The cross-fitting DML estimator is:
-$$\widehat {ATE}_{DML} = \frac{\hat \delta (I^c, I) + \hat \delta (I, I^c)}{2}.$$
-R code to implement DML is shown below.
-Since DML involves sample splitting, this code is a little different from the above examples.
-We start with observed outcome values `y`, treatment assignment `d`, and covariate matrix `x`.
-First, a pre-processing function `dml_pre()` randomly splits the sample, outputting $I$ and $I^c$ sets of each of these variables.
-The second step predicts outcome and treatment probability for each half of the sample, using models fit to the other half.
-In the code chunk here, generalized random forests from the `grf` package are used to predict these, but any prediction algorithm can be used.
-Finally, a post-prediction function `dml_post()` performs the residual-on-residual regression for each half of the sample and finds the average of the two estimates to produce an ATE estimate.
-```{r dml-demo, eval = F, echo = T}
-# Pre-processing: sample splitting
-dml_pre <- function(y, d, x, seed = 1758){
+
+model_matrix <- function(...){
+  options(na.action='na.pass')
+  matrix_out <- model.matrix(...)
+  options(na.action = 'na.omit')
+  return(matrix_out)
+}
+
+compare_tbl <- function(model_list, treatment){
+  out_list <- list()
+  k <- 1
+  for(model_set in model_list){
+    names(model_set[[2]]) <- c('estimate', 'std.error')
+
+    out_list[[k]] <- tidy(model_set[[1]]) %>%
+      filter(term == treatment) %>%
+      bind_rows(bind_rows(model_set[[2]])) %>%
+      bind_rows(model_set[[3]]) %>%
+      mutate(term = c('Original', 'AIPW (GRF)', 'DML (SuperLearner)'), p.value = p_val(estimate, std.error))
+
+    k <- k+1
+  }
+  return(out_list)
+}
+
+dml_grf <- function(outcome, treatment, covariates, clustervar = NULL, dataset, 
+                    fe = T, target = 'treated', paper, model, drop_na_grf = F, seed = 123){
   set.seed(seed)
 
-  n <- length(y)
-  n_2 <- round(n/2)
-
-  # Split the sample
-  random_vec <- sample(1:n, n, replace = F)
-  I <- random_vec[1:n_2]
-  I_c <- random_vec[(n_2+1):n]
-
-  return(list(
-    y_I = y[I],
-    d_I = d[I],
-    x_I = x[I,],
-    y_I_c = y[I_c],
-    d_I_c = d[I_c],
-    x_I_c = x[I_c,]
-    ))
-}
-
-# Predictor function: in this case, generalized random forests
-grf_dml <- function(y_I, d_I, x_I, y_I_c, d_I_c, x_I_c){
-  # Train on the I_c sample, predict on the I sample
-  mu_mod1 <- grf::regression_forest(X = x_I_c, Y = y_I_c, tune.parameters = "all")
-  mu_pred1 <- predict(mu_mod1, newdata = x_I)$predictions
-
-  pi_mod1 <- grf::regression_forest(X = x_I_c, Y = d_I_c, tune.parameters = "all")
-  pi_pred1 <- predict(pi_mod1, newdata = x_I)$predictions
-
-  # Train on the I sample, predict on the I_c sample
-  mu_mod2 <- grf::regression_forest(X = x_I, Y = y_I, tune.parameters = "all")
-  mu_pred2 <- predict(mu_mod2, newdata = x_I_c)$predictions
-
-  pi_mod2 <- grf::regression_forest(X = x_I, Y = d_I, tune.parameters = "all")
-  pi_pred2 <- predict(pi_mod2, newdata = x_I_c)$predictions
-
-  return(list(
-    mu_pred1 = mu_pred1,
-    pi_pred1 = pi_pred1,
-    mu_pred2 = mu_pred2,
-    pi_pred2 = pi_pred2
-  ))
-}
-
-# Implement DML: takes outputs from pre_dml() and grf_dml()
-dml_post <- function(y_I, d_I, x_I, y_I_c, d_I_c, x_I_c,
-                     mu_pred1, pi_pred1, mu_pred2, pi_pred2){
-
-  # Residual-on-residual regression for each sample separately
-  v1 <- d_I - pi_pred1
-  delta1 <- (sum(v1 * d_I))^-1 * sum(v1 * (y_I - pi_pred1))
-
-  v2 <- d_I_c - pi_pred2
-  delta2 <- (sum(v2 * d_I_c))^-1 * sum(v2 * (y_I_c - pi_pred2))
-
-  # Average estimates from each sample
-  ate <- (delta1 + delta2)/2
-
-  return(ate)
-}
-
-dml_pre_out <- dml_pre(y = y, d = d, x = x)
-grf_dml_out <- do.call(grf_dml, dml_pre_out)
-dml_post_out <- do.call(dml_post, append(dml_pre_out, grf_dml_out))
-```
-
-## A simple demonstration using AIPW
-
-To demonstrate double robustness, this section presents one of the simpler double robust estimators, AIPW [@glynn_2010_introduction]. As shown above, we can write this estimator as follows:
-
-$$\begin{aligned}
-\widehat{ATE} = &\frac{1}{N} \sum_{i=1}^N \left( \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) \right) 
-- \frac{1}{N} \sum_{i=1}^N \left( \frac{(1-D_i)(Y_i - \hat \mu_0 (X_i))}{1-\hat \pi(X_i)} + \hat \mu_0(X_i) \right)
-\end{aligned}$$
-
-For each individual in the sample, this estimator calculates two quantities:
-
-- The treated potential outcome
-
-$$\hat Y_{1i} = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i)$$
-
-- The control potential outcome
-
-$$\hat Y_{0i} = \frac{(1-D_i)(Y_i - \hat \mu_0 (X_i))}{1-\hat \pi(X_i)} + \hat \mu_0(X_i)$$
-
-Let's focus on the treated model:
-
-$$\hat Y_{1i} = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i)$$
-
-First, assume that the outcome model $\mu_1(X_i)$ is *correctly* specified and the exposure model $\pi(X_i)$ is *incorreclty* specified.
-Let's also assume (for now) that we're dealing with a treated unit, i.e.
-$D_i = 1$.
-Then
-
-$$\hat \mu_1 (X_i) = Y_i$$
-
-and hence
-
-$$\hat Y_{1i} = \frac{D_i(0)}{\hat \pi (X_i)} + \hat \mu_1(X_i) = \hat \mu_1(X_i).$$
-
-So the model relies *only* on the outcome model.
-The incorrectly specified exposure model completely disappears from the equation.
-If we're dealing with a control unit ($D_i=0$), we get the same result:
-
-$$\hat Y_{1i} = \frac{0(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) = \hat \mu_1(X_i).$$
-
-Now, what if the *exposure* model $\pi(X_i)$ is correctly specified and the outcome model $\mu_1(X)$ is incorrect? First, we rewrite the estimator for the treated outcome:
-
-$$\begin{aligned}
-\hat Y_{1i}& = \frac{D_i(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) \\
-&= \frac{D_iY_i}{\hat \pi (X_i)} - \frac{D_i\hat \mu_1 (X_i)}{\hat \pi (X_i)} + \frac{\hat \pi (X_i)\hat \mu_1(X_i)}{\hat \pi (X_i)} \\
-& = \frac{D_iY_i}{\hat \pi (X_i)} - \left( \frac{D_i - \hat \pi(X_i)}{\hat \pi (X_i)}\right) \hat \mu_1(X_i). &&(*)
-\end{aligned}$$
-
-Since the exposure model is correclty specified, we have $D_i = \hat \pi(X_i)$ on average, so
-
-$$E[D_i - \hat \pi(X_i)] = 0.$$
-
-This means that the second term in equation $(*)$ is 0, so
-
-$$E[\hat Y_{1i}]= E \left [ \frac{D_iY_i}{\hat \pi (X_i)}\right].$$
-
-This shows that when the exposure model is correct, then the estimator depends *only* on the exposure model. We can make similar arguments for the control model $\hat Y_{0i}$.
-
-This demonstration shows that this estimator achieves double robustness: The estimator is robust to misspecification of either the exposure or the outcome model (but not both).
-
-# Methods
-
-These double robust methods have many similarities.
-How do the results they give compare?
-This section tests the performance of each in practice using two strategies.
-First, results are compared using simulated data from a causal inference competition (@dorie_2019_automated).
-The true treatment effect is known, so these simulations allow assessment of accuracy.
-Second, these methods are applied to data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW).
-The NSW randomly provided training to disadvantaged workers, allowing an experimental estimate of the effect of the intervention, and data assembled by @dehejia_1999_causal allows these experimental estimates to be compared to observational ones.
-
-The three double robust methods are compared to two sets of traditional methods used as benchmarks.
-First are one-model methods.
-The most classic method considered -- linear regression -- models only the response surface.
-Here it is estimated using ordinary least squares regression ("OLS"), entering each variable separately without any interactions or higher-order terms.
-Two other one-model methods model only the treatment assignment mechanism.
-Propensity score are estimated from logistic regression with each variable entered separately and without any higher order terms, then matched using the `MatchIt` package ("PSM").
-Finally, stabilized inverse probability weights [IPW, @austin_2015_moving, p.
-3663] are used for weighted OLS regression.
-These IPWs are estimated using each of the three under-the-hood estimation methods described below.
-
-The second set of traditional methods are two-model methods, which estimate separate models for treated and untreated units.
-In theory these could solve the misspecification problem that double robust methods are meant to solve, but they could still suffer from regularization bias.
-G-computation [@robins_1986_new; @hernan_2020_causal p.
-163; @snowden_2011_implementation] uses some estimation technique to predict outcomes under treatment and control for each unit in the dataset.
-The ATE estimate is the difference in the average prediction under treatment and the average prediction under control.
-The second two-model method is the Lin estimator [@lin_2013_agnostic].
-This method aims to solve issues with the bias induced by OLS regression in a randomization framework by interacting the treatment indicator with mean-centered covariates.
-
-Many of these methods allow the user to choose the underlying estimation method, results compare three techniques.
-First is using a logistic regression for the exposure model and an OLS regression for the outcome model.
-Second is generalized random forests [GRF, @athey_2019_generalized] using the `grf` R package, with separate models for exposure and outcome.
-The final technique is the SuperLearner (as promoted by the makers of TMLE) using the `SuperLearner` package, again with separate models for exposure and outcome.
-GLM, glmnet (lasso), and XGBoost models are considered for the SuperLearner.
-These three estimation techniques are used for each of the three double robust methods, for IPW, and for G-computation.
-
-For the simulations, results compare only point estimates from these methods.
-For evaluation of the experimental LaLonde data, I use bootstrapping with 100 samples to obtain estimates and standard errors.
-
-# Results
-
-```{r dorie-sim, eval = F}
-set.seed(185)
-
-# sims %>%
-#   lapply(function(x) append(x, list()))
-
-sim_list <- list()
-for(i in 1:20){ # up to 77
-  #sim_list_nest <- list()
-  for(j in 1:10){ # up to 100
-    print(paste0(i,',',j))
-    sim_list[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016,
-                                      i, j, extraInfo = T) %>% 
-      append(list(dataset = i, set = 'main'))
-  }
-}
-
-sim_linear <- list()
-for(i in c(1, 3)){
-  for(j in 1:100){ 
-    print(paste0(i,',',j))
-    sim_linear[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016, 
-                                      i, j, extraInfo = T) %>% 
-      append(list(dataset = i, set = 'linear'))
-  }
-}
-
-saveRDS(append(sim_list, sim_linear), here('files', 'sims.RDS'))
-```
-
-```{r large, eval = F}
-# dataset 7: polynomial     0.35    one-term exponential      0.75      high
-set.seed(185)
-
-sim_list <- list()
-
-for(j in c(2, 5, 10, 20)){ # up to 100
-  for(i in 1:20){ # up to 77
-  #sim_list_nest <- list()
-
-    print(paste0(i,',',j))
-
-    dataset <- aciccomp2016::input_2016 %>% 
-      slice(rep(1:n(), each = j))
-
-    sim_list[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(dataset, 7, i, extraInfo = T) %>% 
-      append(list(dataset = 7, set = 'large', size = j*4802))
-  }
-}
-
-saveRDS(sim_list, here('files', 'sims_large.RDS'))
-
-```
-
-```{r sims-small, eval = F}
-set.seed(185)
-
-sim_list <- list()
-for(j in c(150, 300, 600, 1200, 2400, 4802)){ 
-  for(i in 1:20){ 
-  #sim_list_nest <- list()
-
-    print(paste0(i,',',j))
-
-    sample_index <- sample(1:4802, j, replace = F)
-
-    sim_list[[paste0(i,',',j)]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016, 7, i, extraInfo = T) %>% 
-      append(list(dorie_dataset = 7, set = 'small', size = j))
-
-    for(name in names(sim_list[[paste0(i,',',j)]])[1:7]){
-      sim_list[[paste0(i,',',j)]][[name]] <- sim_list[[paste0(i,',',j)]][[name]][sample_index]
-    }
-
-    sim_list[[paste0(i,',',j)]]$x <- sim_list[[paste0(i,',',j)]]$x[sample_index,]
-  }
-}
-
-saveRDS(sim_list, here('files', 'sims_small.RDS'))
-```
-
-```{r sim-test, eval = F}
-data_test <- bind_rows(aciccomp2016::input_2016, aciccomp2016::input_2016)
-
-acs <- read_dta('/Users/nathan/Data/ACS/acs_2008_2021.dta')
-
-test <- aciccomp2016::dgp_2016(data_test, parameter_list, 1950, extraInfo = T)
-set.seed(185)
-test_acs <- aciccomp2016::dgp_2016(filter(acs, year == 2016) %>% drop_na() %>% sample_n(1e5), 
-                                   parameter_list, 1950, extraInfo = T)
-```
-
-```{r lm-sim, eval = F}
-lm_df <- lm_sim(sims)
-
-write_csv(lm_df, here('files', 'lm_df.csv'))
-
-lm_df %>%
-  group_by(set) %>%
-  summarize(ate_est = mean(ate), 
-            se = sd(ate))
-```
-
-```{r psm-sim, eval = F}
-psm_df <- psm_sim(sims)
-
-write_csv(psm_df, here('files', 'psm_df.csv'))
-```
-
-```{r pred-calc, eval = F}
-
-ols_logit_pred_list <- list()
-for(i in 1:length(sims)){
-  print(i)
-  dat <- sims[[i]]
-
-  start_time = Sys.time()
-
-  ols_logit_pred_list[[i]] <- ols_logit_pred(
-    y = dat$y,
-    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-    x = dat$x) %>%
-    append(list(truth = mean(dat$y.1) - mean(dat$y.0),
-                comp_time = as.numeric(difftime(Sys.time(), start_time, units = 'secs'))))
-}
-saveRDS(ols_logit_pred_list, here('files/homemade', 'ols_logit_pred.RDS'))
-
-# tibble(ols_logit_pred_list[[i]]$y,
-#              ols_logit_pred_list[[i]]$mu1_pred, 
-#              ols_logit_pred_list[[i]]$mu0_pred,
-#              ols_logit_pred_list[[i]]$d,
-#              hist(ols_logit_pred_list[[12]]$pi_pred)
-#              )
-
-grf_pred_list <- list()
-for(i in 1:length(sims)){
-  print(i)
-  dat <- sims[[i]]
-
-  start_time = Sys.time()
-
-  grf_pred_list[[i]] <- grf_pred(
-    y = dat$y,
-    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-    x = dat$x) %>%
-    append(list(truth = mean(dat$y.1) - mean(dat$y.0),
-                comp_time = as.numeric(difftime(Sys.time(), start_time, units = 'secs')),
-                dorie_dataset = sims[[i]]$dataset,
-                set = sims[[i]]$set,
-                size = sims[[i]]$size))
-}
-saveRDS(grf_pred_list, here('files/homemade', 'grf_pred.RDS'))
-
-superlearner_pred_list <- list() 
-for(i in 1:length(sims)){
-  print(i)
-  dat <- sims[[i]]
-
-  start_time = Sys.time()
-
-  superlearner_pred_list[[i]] <- superlearner_pred(
-    y = dat$y,
-    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-    x = dat$x) %>%
-    append(list(truth = mean(dat$y.1) - mean(dat$y.0),
-                comp_time = as.numeric(difftime(Sys.time(), start_time, units = 'secs')),
-                dorie_dataset = sims[[i]]$dataset,
-                set = sims[[i]]$set,
-                size = sims[[i]]$size))
-}
-saveRDS(superlearner_pred_list, here('files/homemade', 'superlearner_pred.RDS'))
-
-```
-
-```{r ipw, eval = F}
-ols_logit_pred_list2 <- readRDS(here('files/homemade', 'ols_logit_pred.RDS'))
-grf_pred_list2 <- readRDS(here('files/homemade', 'grf_pred.RDS'))
-superlearner_pred_list2 <- readRDS(here('files/homemade', 'superlearner_pred.RDS'))
-
-ipw_out_list <- list()
-predictions <- list(ols_logit_pred_list2, grf_pred_list2, superlearner_pred_list2)
-pred_names <- c('logit', 'grf', 'superlearner')
-for(i in 1:length(sims)){
-  print(i)
-  for(j in 1:length(predictions)){
-
-    start_time <- Sys.time()
-
-    D <- sims[[i]]$z == 'trt'
-    PrD <- mean(D)
-    ps <- predictions[[j]][[i]]$pi_pred
-    ipw <- D*PrD/ps + (1-D)*(1-PrD)/(1-ps)
-
-    lm_out <- lm(sims[[i]]$y ~ D, weights=ipw) 
-    ate_ipw <- coefficients(lm_out)[[2]]
-
-    comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
-
-    ipw_out_list[[paste0(i, ',', j)]] <- data.frame(
-      dataset = i,
-      method = pred_names[[j]],
-      ate = ate_ipw, 
-      truth = predictions[[j]][[i]]$truth, 
-      comp_time = comp_time + predictions[[j]][[i]]$comp_time,
-      dorie_dataset = sims[[i]]$dataset,
-      set = sims[[i]]$set,
-      size = sims[[i]]$size)
-  }
-}
-
-write_csv(bind_rows(ipw_out_list), here('files', 'ipw.csv'))
-```
-
-```{r g-comp, eval = F}
-ols_logit_pred_list2 <- readRDS(here('files/homemade', 'ols_logit_pred.RDS'))
-grf_pred_list2 <- readRDS(here('files/homemade', 'grf_pred.RDS'))
-superlearner_pred_list2 <- readRDS(here('files/homemade', 'superlearner_pred.RDS'))
-
-gcomp_out_list <- list()
-predictions <- list(ols_logit_pred_list2, grf_pred_list2, superlearner_pred_list2)
-pred_names <- c('ols', 'grf', 'superlearner')
-for(i in 1:length(sims)){
-  print(i)
-  for(j in 1:length(predictions)){
-
-    start_time <- Sys.time()
-
-    gcomp_out <- with(predictions[[j]][[i]], mean(mu1_pred - mu0_pred))
-
-    comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
-
-    gcomp_out_list[[paste0(i, ',', j)]] <- data.frame(
-      dataset = i,
-      method = pred_names[[j]],
-      ate = gcomp_out, 
-      truth = predictions[[j]][[i]]$truth, 
-      comp_time = comp_time + predictions[[j]][[i]]$comp_time,
-      dorie_dataset = sims[[i]]$dataset,
-      set = sims[[i]]$set,
-      size = sims[[i]]$size)
-  }
-}
-
-write_csv(bind_rows(gcomp_out_list), here('files', 'gcomp.csv'))
-```
-
-```{r lin, eval = F}
-
-n <- length(sims)
-lin_list <- list()
-for(i in 1:n){
-  start_time <- Sys.time()
-
-  print(paste0(i, ' out of ', n))
-  sim_dat <- data.frame(y = sims[[i]]$y, 
-                        d = ifelse(sims[[i]]$z == 'trt', 1, 0), 
-                        sims[[i]]$x)
-
-  ate <- NA
-  tryCatch({
-    lm_out <- tidy(estimatr::lm_lin(y ~ d, 
-                                    covariates = as.formula(paste0('~ ', paste(names(sims[[i]]$x), collapse = ' + '))), 
-                                    data = sim_dat))
-    ate <- lm_out[[2,2]]
-
-    }, error=function(e){
-      cat("ERROR :",conditionMessage(e), "\n")
-      })
-
-  lin_list[[i]] <- data.frame(dataset = i,
-                             ate = ate,
-                             #se = lm_out[[2,3]],
-                             truth = mean(sims[[i]]$y.1) - mean(sims[[i]]$y.0),
-                             dorie_dataset = sims[[i]]$dataset,
-                             set = sims[[i]]$set,
-                             size = sims[[i]]$size,
-                             comp_time = as.numeric(difftime(Sys.time(), start_time, units = 'secs')))
-}
-
-write_csv(bind_rows(lin_list), here('files', 'lin.csv'))
-```
-
-```{r aipw, eval = F}
-
-aipw_calc2 <- function(mu1_pred, mu0_pred, pi_pred, d, y){
-  n <- length(mu1_pred)
-
-  # pi_pred <- case_when(
-  #   pi_pred < quantile(pi_pred, c(.025)) ~ as.numeric(quantile(pi_pred, c(.025))),
-  #   pi_pred > quantile(pi_pred, c(.975)) ~ as.numeric(quantile(pi_pred, c(.975))),
-  #   T ~ pi_pred)
-
-  # pi_pred <- case_when(
-  #   pi_pred < .01 ~ .01,
-  #   pi_pred > .99 ~ .99,
-  #   T ~ pi_pred)
-
-  ipw <- (d*y)/pi_pred - (1-d)*y/(1-pi_pred)
-  adjust <- (d-pi_pred)/(pi_pred*(1-pi_pred)) * (1-pi_pred)*mu1_pred + pi_pred*mu0_pred
-
-  ate <- (1/n) * sum(ipw - adjust)
-
-  return(ate)
-}
-
-aipw_out_list <- list()
-predictions <- list(ols_logit_pred_list2, grf_pred_list2, superlearner_pred_list2)
-pred_names <- c('ols_logit', 'grf', 'superlearner')
-for(i in 1:length(sims)){
-  print(i)
-  for(j in 1:length(predictions)){
-
-    start_time <- Sys.time()
-    aipw_out <- with(predictions[[j]][[i]], 
-                     aipw_calc(mu1_pred = mu1_pred, 
-                               mu0_pred = mu0_pred,
-                               pi_pred = pi_pred,
-                               d = d,
-                               y = y))
-    comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
-
-    aipw_out_list[[paste0(i, ',', j)]] <- data.frame(
-      dataset = i,
-      method = pred_names[[j]],
-      ate = aipw_out, 
-      truth = predictions[[j]][[i]]$truth, 
-      comp_time = comp_time + predictions[[j]][[i]]$comp_time,
-      dorie_dataset = sims[[i]]$dataset,
-      set = sims[[i]]$set,
-      size = sims[[i]]$size)
-  }
-}
-
-write_csv(bind_rows(aipw_out_list), here('files/homemade', 'aipw.csv'))
-
-aipw_out_list <- list()
-predictions <- list(ols_logit_pred_list2, grf_pred_list2, superlearner_pred_list2)
-pred_names <- c('ols_logit', 'grf', 'superlearner')
-for(i in 1:length(sims)){
-  print(i)
-  for(j in 1:length(predictions)){
-
-    start_time <- Sys.time()
-    aipw_out <- with(predictions[[j]][[i]], 
-                     aipw_calc_trunc(mu1_pred = mu1_pred, 
-                               mu0_pred = mu0_pred,
-                               pi_pred = pi_pred,
-                               d = d,
-                               y = y))
-    comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
-
-    aipw_out_list[[paste0(i, ',', j)]] <- data.frame(
-      dataset = i,
-      method = pred_names[[j]],
-      ate = aipw_out, 
-      truth = predictions[[j]][[i]]$truth, 
-      comp_time = comp_time + predictions[[j]][[i]]$comp_time,
-      dorie_dataset = sims[[i]]$dataset,
-      set = sims[[i]]$set,
-      size = sims[[i]]$size)
-  }
-}
-
-write_csv(bind_rows(aipw_out_list), here('files/homemade', 'aipw_trunc.csv'))
-
-```
-
-```{r tmle, eval = F}
-
-tmle_out_list <- list()
-predictions <- list(ols_logit_pred_list2, grf_pred_list2, superlearner_pred_list2)
-pred_names <- c('ols_logit', 'grf', 'superlearner')
-
-for(i in 1:length(sims)){
-  print(i)
-  for(j in 1:length(predictions)){
-    start_time <- Sys.time()
-    tryCatch({
-      tmle_out <- with(predictions[[j]][[i]], 
-                       tmle_calc(mu1_pred = normalize(mu1_pred, y), 
-                                 mu0_pred = normalize(mu0_pred, y),
-                                 pi_pred = pi_pred,
-                                 d = d,
-                                 y = normalize(y, y))
-                       )
-    }, error=function(e){
-      tmle_out <- NA
-      })
-    comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
-
-    tmle_out_list[[paste0(i, ',', j)]] <- data.frame(
-      dataset = i,
-      method = pred_names[[j]],
-      ate = denormalize(tmle_out, predictions[[j]][[i]]$y), 
-      truth = predictions[[j]][[i]]$truth, 
-      comp_time = comp_time + predictions[[j]][[i]]$comp_time,
-      fail = is.na(tmle_out),
-      dorie_dataset = sims[[i]]$dataset,
-      set = sims[[i]]$set,
-      size = sims[[i]]$size)
-  }
-}
-
-write_csv(bind_rows(tmle_out_list), here('files/homemade', 'tmle.csv'))
-
-# logit_logit_pred_list <- list()
+  dataset <- filter(dataset, !is.na(!!sym(outcome))) %>%
+    select(all_of(c(treatment, outcome, covariates, clustervar)))
+
+  if(drop_na_grf == T){
+    dataset <- dataset %>%
+      drop_na()
+  }
+
+  y <- as.numeric(dataset[[outcome]])
+  X <- model_matrix(~., select(dataset, all_of(covariates)))[,]
+  d <- as.numeric(dataset[[treatment]])
+
+  grf_model <- grf::causal_forest(X = X, Y = y, W = d, seed = 123,
+                        clusters = dataset[[clustervar]])
+
+  grf_out <- grf::average_treatment_effect(grf_model, target.sample = target)
+
+  dataset_drop_na <- as.data.frame(model_matrix(~., dataset)[,]) %>%
+    # remove annoying characters
+    rename_with(., ~ gsub("'", "", iconv(.x, from = "UTF-8", to='ASCII//TRANSLIT'))) %>%
+    rename_with(., ~ gsub("\\[|\\]|\\/|\\*|\\)|\\(", "", .x)) %>%
+    rename_with(., ~ gsub(" ", "", .x)) %>%
+    # drop missing
+    drop_na() %>%
+    # remove uninformative columns
+    select(where(~n_distinct(.) > 1)) 
+  dataset_drop_na <- dataset_drop_na %>%
+    left_join(dataset_drop_na %>%
+                group_by(!!sym(clustervar)) %>%
+                summarize(across(everything(), mean, .names = 'mean_{.col}')) %>%
+                ungroup()) %>%
+    mutate(intercept = 1)
+  # covariates_design <- dataset_drop_na %>% 
+  #   select(select(-c(treatment, outcome, clustervar))) %>%
+  #   names() %>%
+  #   append('intercept', after = 0)
+  covariates_design <- names(dataset_drop_na)[!(names(dataset_drop_na) %in% c(treatment, outcome, clustervar)) &
+                                                !str_detect(names(dataset_drop_na),  'mean_')]
+
+  # dataset_drop_na$cov_mean <- dataset_drop_na %>%
+  #   select(all_of(covariates_design)) %>%
+  #   mutate_all(scale) %>%
+  #   apply(1, mean)
+
+  # dml_dataframe <- as.data.frame(cbind(y, d, 
+  #                                      d_bar = dataset_drop_na[[paste0('mean_', treatment)]],
+  #                                      as_tibble(X)[,-1], 
+  #                                      as_tibble(mean_X)[,-1], 
+  #                                      cluster = dataset_drop_na[[clustervar]]))
+
+  graph_ensemble_regr = gunion(list(
+      po("learner", lrn("regr.cv_glmnet", s = "lambda.min")),
+      po("learner", lrn('regr.xgboost', max_depth = 4)),
+      po("learner", lrn("regr.glm"))
+    )) %>>%
+      po("regravg", 3)
+
+  ensemble_pipe_regr = as_learner(graph_ensemble_regr)
+
+  # DML
+  set.seed(seed)
+  dml_data <- double_ml_data_from_data_frame(dataset_drop_na,
+                                             x_cols = covariates_design,
+                                             y_col = outcome,
+                                             d_cols = treatment,
+                                             cluster_cols = clustervar)
+
+  # y <- as.numeric(dataset_drop_na[[outcome]])
+  # # X <- select(dataset_drop_na, covariates_design)
+  # X <- model_matrix(~., select(dataset_drop_na, all_of(covariates)))[,]
+  # # mean_X <- model_matrix(~., select(dataset_drop_na, all_of(paste0('mean_', covariates))))[,]
+  # d <- as.numeric(dataset_drop_na[[treatment]])
   # 
-# for(i in 1:length(sim_linear)){
-#   print(i)
-#   dat <- sim_linear[[i]]
-#   
-#   logit_logit_pred_out <- logit_logit_pred(
-#     y = with(dat, (y - min(y)) / (max(y) - min(y))),
-#     d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-#     x = dat$x
-#     )
-#   
-#   ate <- with(logit_logit_pred_out, 
-#               tmle_calc(mu1_pred = mu1_pred, 
-#                         mu0_pred = mu0_pred,
-#                         pi_pred = pi_pred,
-#                         d = d,
-#                         y = y)) 
-#   truth <- mean(dat$y.1) - mean(dat$y.0)
-# 
-#   logit_logit_pred_list[[i]] <-  data.frame(ate = ate * (max(dat$y)-min(dat$y)),
-#                                             truth = truth)
-# }
-# 
-# perform(bind_rows(logit_logit_pred_list), label = 'ols, logit, tmle')
-# 
-# 
-# #### 
-# 
-# grf_pred_list <- list()
-# 
-# for(i in 1:10){ #length(sim_linear)){
-#   print(i)
-#   dat <- sim_linear[[i]]
-#   
-#   grf_pred_out <- grf_pred(
-#     y = dat$y, # with(dat, (y - min(y)) / (max(y) - min(y))),
-#     d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-#     x = dat$x
-#     )
-#   
-#   yt <- function(x, y){(x - min(y)) / (max(y) - min(y))}
-#   
-#   ate <- with(grf_pred_out, 
-#               tmle_calc(mu1_pred = yt(mu1_pred, dat$y), 
-#                         mu0_pred = yt(mu0_pred, dat$y),
-#                         pi_pred = pi_pred,
-#                         d = d,
-#                         y = yt(y, dat$y)))
-#   truth <- mean(dat$y.1) - mean(dat$y.0)
-#   
-#   grf_pred_list[[i]] <-  data.frame(ate = ate * (max(dat$y)-min(dat$y)),
-#                                             truth = truth)
-# }
-# 
-# perform(bind_rows(grf_pred_list), label = 'grf, tmle')
-
-# superlearner_pred_list <- list()
-# 
-# for(i in 1:length(sim_linear)){
-#   print(i)
-#   dat <- sim_linear[[i]]
-#   
-#   superlearner_pred_out <- superlearner_pred(
-#     y = with(dat, (y - min(y)) / (max(y) - min(y))),
-#     d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-#     x = dat$x
-#     )
-#   
-#   ate <- with(superlearner_pred_out, 
-#               tmle_calc(mu1_pred = mu1_pred, 
-#                         mu0_pred = mu0_pred,
-#                         pi_pred = pi_pred,
-#                         d = d,
-#                         y = y))
-#   truth = mean(dat$y.1) - mean(dat$y.0)
-#   
-#   superlearner_pred_list[[i]] <- data.frame(ate = ate * (max(dat$y)-min(dat$y)),
-#                                             truth = truth)
-# }
-# 
-# perform(bind_rows(superlearner_pred_list), label = 'superlearner, tmle')
-```
-
-```{r dml, eval = F}
-
-## DML OLS logit
-
-ols_logit_dml_list <- list()
-
-set.seed(1285)
-for(i in 1:length(sims)){
-  print(i)
-  dat <- sims[[i]]
-
-  start_time <- Sys.time()
-  dml_pre_out <- dml_pre(dat$y,
-                       as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-                       x = dat$x)
-
-  ols_logit_dml_out <- do.call(ols_logit_dml, dml_pre_out)
-
-  dml_post_out <- do.call(dml_post, append(dml_pre_out, ols_logit_dml_out))
-  comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
-
-  truth <- mean(dat$y.1) - mean(dat$y.0)
-
-  ols_logit_dml_list[[i]] <- data.frame(ate = dml_post_out, 
-                              truth = truth, 
-                              comp_time = comp_time,
-                              dataset = i,
-                              dorie_dataset = dat$dataset,
-                              set = dat$set,
-                              size = dat$size)
-}
-
-write_csv(bind_rows(ols_logit_dml_list), 
-          here('files/homemade', 'dml_ols_logit.csv'))
-
-# perform(bind_rows(ols_logit_dml_list), label = 'grf, dml')
-
-## GRF
-grf_dml_list <- list()
-
-set.seed(1285)
-for(i in 1:length(sims)){
-  print(i)
-  dat <- sims[[i]]
-
-  start_time <- Sys.time()
-
-  dml_pre_out <- dml_pre(dat$y,
-                       as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-                       x = dat$x)
-  dml_post_out <- NA
-   tryCatch({
-      grf_dml_out <- do.call(grf_dml, dml_pre_out)
-
-      dml_post_out <- do.call(dml_post, append(dml_pre_out, grf_dml_out))
-      }, error=function(e){
-        cat("ERROR :",conditionMessage(e), "\n")
-        })
-
-  comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
-
-  truth <- mean(dat$y.1) - mean(dat$y.0)
-
-  grf_dml_list[[i]] <- data.frame(ate = dml_post_out, 
-                              truth = truth, 
-                              comp_time = comp_time,
-                              dataset = i,
-                              dorie_dataset = dat$dataset,
-                              set = dat$set,
-                              size = dat$size)
-}
-
-write_csv(bind_rows(grf_dml_list), 
-          here('files/homemade', 'dml_grf.csv'))
-
-# perform(bind_rows(grf_dml_list), label = 'grf, dml')
-
-## Superlearner
-superlearner_dml_list <- list()
-
-set.seed(1285)
-for(i in 1:length(sims)){
-  print(i)
-  dat <- sims[[i]]
-
-  start_time <- Sys.time()
-
-  dml_pre_out <- dml_pre(dat$y,
-                       as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-                       x = dat$x)
-  dml_post_out <- NA
-   tryCatch({
-      superlearner_dml_out <- do.call(superlearner_dml, dml_pre_out)
-      dml_post_out <- do.call(dml_post, append(dml_pre_out, superlearner_dml_out ))
-      }, error=function(e){
-        cat("ERROR :",conditionMessage(e), "\n")
-        })
-
-  comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
-
-  truth <- mean(dat$y.1) - mean(dat$y.0)
-
-  superlearner_dml_list[[i]] <- data.frame(ate = dml_post_out, 
-                              truth = truth, 
-                              comp_time = comp_time,
-                              dataset = i,
-                              dorie_dataset = dat$dataset,
-                              set = dat$set,
-                              size = dat$size)
-}
-
-write_csv(bind_rows(superlearner_dml_list), 
-          here('files/homemade', 'dml_superlearner.csv'))
-
-#perform(bind_rows(superlearner_dml_list), label = 'superlearner, dml')
-
-```
-
-## Simluations with Dorie et al. (2019) Data
-
-In 2016, the Atlantic Causal Inference Conference hosted a competition for causal inference methods that adjust on observables.
-@dorie_2019_automated published the results of this competition, along with the data used in the competition.
-Below, I test double robust methods on the 20 data sets used for the "do-it-yourself" part of the competition.
-The data represent a hypothetical twins study investigating the impact of birth weight on IQ.
-The data have 4802 observations and 52 covariates.
-The authors of the study specify a different data generating process for the potential outcomes in each data set.
-In all cases, ignorability holds, but the authors vary the following:
-
-- degree of nonlinearity
-- percentage of treated
-- overlap for the treatment group
-- alignment (correspondence between the assignment mechanism and the response surface)
-- treatment effect heterogeneity
-- overall magnitude of the treatment effect
-
-### Main results
-
-The 20 data sets used here cover a range of these attributes; see the supplemental material from @dorie_2019_automated for details.
-I use 10 simulations of each data set, resulting in 200 data sets.
-I then calculate bias, percent bias (the estimator's bias as a percentage of its standard error), root mean squared error (rmse), and median absolute error (mae).
-I also present the number of datasets for which the method fails and the average computation time for each data set, in seconds.
-
-Results for the full range of simulations are shown in Table \@ref(tab:dorie-results) and Figure \@ref(fig:dorie-results-fig).
-Using AIPW as written above results in some wildly biased estimates for the ols_logit estimator, due to dividing by some very small propensity scores.
-Hence I present estimates from a trimmed AIPW estimator, where predicted exposure model values are set to 0.01 if they are less than 0.01 and to 0.99 if they are greater than 0.99.
-
-The lowest bias is achieved by AIPW with GRF, followed by propensity score matching and then OLS.
-The lowest root mean squared error is obtained by AIPW with GRF, followed by TMLE with GRF, and next by OLS regression.
-Results are similar if we consider percent bias or mean absolute error.
-DML does not perform particularly well and also has the highest computation times due to sample splitting.
-
-```{r dorie-results}
+  # dml_data <- double_ml_data_from_matrix(X = X, y = y, d = d, 
+  #                                        cluster_vars = dataset_drop_na[[clustervar]])
+
+  # dml_data <- double_ml_data_from_matrix(X = select(dataset_drop_na, all_of(covariates_design)),
+  #                                            y = dataset_drop_na[,outcome],
+  #                                            d = dataset_drop_na[,treatment],
+  #                                            cluster_vars = dataset_drop_na[,clustervar])
+  obj_dml_plr_sim_pipe_ensemble = DoubleMLPLR$new(dml_data,
+                                                  ml_l = ensemble_pipe_regr,
+                                                  ml_m = ensemble_pipe_regr)
+  obj_dml_plr_sim_pipe_ensemble$fit() 
+  dml_out <- data.frame(estimate = obj_dml_plr_sim_pipe_ensemble$coef,
+                         std.error = obj_dml_plr_sim_pipe_ensemble$se)
+
+  if(fe == T){
+    # DML CRE
+    set.seed(seed)  
+    dml_data_cre <- XTDML::dml_cre_data_from_data_frame(dataset_drop_na,
+                                                 x_cols = covariates_design,
+                                                 y_col = outcome,
+                                                 d_cols = treatment,
+                                                 xbar_cols = paste0('mean_', covariates_design[-length(covariates_design)]),
+                                                 dbar_cols = paste0('mean_', treatment),
+                                                 cluster_cols = clustervar)  
+    obj_dml_cre = XTDML::dml_cre_plr$new(dml_data_cre,
+                                         ml_l = ensemble_pipe_regr,
+                                         ml_m = ensemble_pipe_regr)
+
+    obj_dml_cre$fit()
+    dml_cre_out <- data.frame(estimate = obj_dml_cre$coef_theta,
+                           std.error = obj_dml_cre$se_theta)
+
+  # DML WG-CRE
+  require(parameters)
+  set.seed(seed)  
+  dml_data_wg_cre <- XTDML::dml_hybrid_data_from_data_frame(dataset_drop_na,
+                                               x_cols = covariates_design,
+                                               y_col = outcome,
+                                               d_cols = treatment,
+                                               xbar_cols = paste0('mean_', covariates_design[-length(covariates_design)]),
+                                               dbar_cols = paste0('mean_', treatment),
+                                               cluster_cols = clustervar)  
+  obj_dml_wg_cre = XTDML::dml_hybrid_plr$new(dml_data_wg_cre,
+                                       ml_l = ensemble_pipe_regr,
+                                       ml_m = ensemble_pipe_regr)
+
+  obj_dml_wg_cre$fit()
+  dml_wg_cre_out <- data.frame(estimate = obj_dml_wg_cre$coef_theta,
+                         std.error = obj_dml_wg_cre$se_theta)
+  } else {
+    dml_cre_out <- data.frame(estimate = NA,
+                           std.error = NA)
+    dml_wg_cre_out <- data.frame(estimate = NA,
+                         std.error = NA)
+  }
+
+  return(list(grf = grf_out, 
+              dml = dml_out,
+              dml_cre = dml_cre_out,
+              dml_wg_cre = dml_wg_cre_out))
+}
+```
+
+```{r results-load}
 
@@
 
-sim_results <- bind_rows(lm_df, psm_df, lin_df, ipw_df, gcomp_df, aipw_trunc_df, tmle_df, dml_df) %>%
-  mutate(estimator = factor(estimator, levels = c('ols_logit', 'ols', 'logit', 'grf', 'superlearner')),
-         method = factor(method, levels = c('ols', 'psm', 'lin', 'ipw', 'g-comp', 'aipw', 'tmle', 'dml'))) %>%
+aipw_package_df <- read_csv(here('files/homemade', 'aipw_package.csv')) %>%
+  mutate(estimator = 'grf (pack.)',
+         method = 'aipw')
+
+dml_package_df <- read_csv(here('files/homemade', 'dml_package.csv')) %>%
+  mutate(estimator = 'superlearner (pack.)',
+         method = 'dml')
+
+sim_results <- bind_rows(lm_df, psm_df, lin_df, ipw_df, gcomp_df, aipw_trunc_df, tmle_df, dml_df, aipw_package_df, dml_package_df) %>%
+  mutate(estimator = factor(estimator, levels = c('ols_logit', 'ols', 'logit', 
+          'grf', 'grf (pack.)', 'superlearner', 'superlearner (pack.)')),
+         method = factor(method, levels = c('ols', 'psm', 'ipw', 'g-comp', 'lin', 
+                                            'aipw', 'tmle', 'dml'))) %>%
   arrange(method, estimator) %>%
@@
   mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator})))
-```
-
-```{r dorie-results-fig, fig.height = 6, fig.cap = 'Results of Monte Carlo simulations using the first 20 datasets from Dorie et al. (2019), 10 replications each.'}
-addline_format <- function(x,...){
-    gsub('\\s','\n',x)
-}
-
-sim_results %>% 
-  filter(set == 'main') %>%
-  mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
-  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator}))) %>%
-  #filter(method %in% c('ols', 'psm', 'aipw')) %>%
-  ggplot(aes(x = method_estimator, y = bias)) +
-  geom_jitter(alpha = .2, width = .3, aes(color = method)) +
-  geom_boxplot(alpha = .5, outlier.alpha = 0) +
-  geom_hline(yintercept = 0) +
-  #facet_wrap(~method, scales = 'free_x') +
-  labs(x = '', title = 'All datasets') +
-  theme(#axis.text.x=element_text(angle=-15), 
-        legend.position = 'none') +
-  scale_x_discrete(labels=function(x){sub(", ", "\n", x)})
-```
-
-### Linear DGPs
-
-Traditional methods may perform better when the data generating processes are linear.
-To test this, I use 100 simulations of each of the two datasets from @dorie_2019_automated with linear data generating processes (numbers 1 and 3) to show how these methods perform when the underlying models are linear.
-
-If we consider only the linear datasets (Table \@ref(tab:dorie-results-linear) and Figure \@ref(fig:dorie-results-linear-fig)), OLS obtains the lowest bias, followed by AIPW with GRF and then propensity score matching.
-The lowest root mean squared error is achieved by OLS, then AIPW with GRF, and then TMLE with GRF.
-Percent bias and mean absolute error show similar results.
-
-Overall, traditional methods perform surprisingly well in comparison with the double robust methods.
-Even in the full range of datasets -- which include highly nonlinear exposure and outcome data-generating processes -- OLS and propensity score matching obtain some of the smallest bias.
-Generalized random forests appear to be the best estimators for the double robust methods, though a SuperLearner than incorporates GRF has the potential to outperform GRF alone, at the expense of computation time.
-Notably, the method with the longest computation time -- DML with a SuperLearner -- takes over 2,000 times as along as OLS.
-
-```{r dorie-results-linear-fig, fig.height = 6, fig.cap = 'Results of Monte Carlo simulations using the two datasets from Dorie et al.
-(2019), with linear data generating processes, 100 replications each ("linear").'}
-sim_results %>% 
-  filter(set == 'linear') %>%
-  mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
-  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator}))) %>%
-  #filter(method %in% c('ols', 'psm', 'aipw')) %>%
-  ggplot(aes(x = method_estimator, y = bias)) +
-  geom_jitter(alpha = .2, width = .3, aes(color = method)) +
-  geom_boxplot(alpha = .5, outlier.alpha = 0) +
-  geom_hline(yintercept = 0) +
-  #facet_wrap(~method, scales = 'free_x') +
-  labs(x = '', title = 'Linear DGPs') +
-  theme(#axis.text.x=element_text(angle=-15), 
-        legend.position = 'none') +
-  scale_x_discrete(labels=function(x){sub(", ", "\n", x)})
-```
-
-### Do results vary by DGP?
-```{r vary}
-sim_results_dgp <- sim_results %>%
-  filter(set == 'main') %>%
-  # mutate(paramter_num = ceiling(dataset/10)) %>%
-  left_join(mutate(aciccomp2016::parameters_2016, dorie_dataset = row_number()))
-
-dgp_names <- c('Treatment assignment', 'Probability of treatment',
-               'Overlap of treatment', 'Response surface',
-               'Alignment (same terms for treatment and response)',
-               'Treatment effect heterogeneity')
-
-names(dgp_names) <- names(aciccomp2016::parameters_2016)
-
-for(name in colnames(aciccomp2016::parameters_2016[1])){
-  plot <- sim_results_dgp %>% 
-    mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
-    mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator}))) %>%
-    #filter(method %in% c('ols', 'psm', 'aipw')) %>%
-    ggplot(aes(x = method_estimator, y = bias)) +
-    geom_jitter(alpha = .2, width = .3, aes(color = method)) +
-    geom_boxplot(alpha = .5, outlier.alpha = 0) +
-    #facet_wrap(~method, scales = 'free_x') +
-    labs(x = '', title = dgp_names[name]) +
-    theme(#axis.text.x=element_text(angle=-15), 
-          legend.position = 'none') +
-    scale_x_discrete(labels=function(x){sub(", ", "\n", x)}) +
-    facet_wrap(vars(!!sym(name)), ncol = 1, scales = 'free')
-
-  print(plot)
-}
-```
-
-### Do results vary by sample size?
-
-The double robust methods reviewed here have been shown to have lower bias asymptotically.
-Is the issue with previous results simply that the sample size of the simulation data ($n$ = 4,802) is too small for double robust methods to outperform traditional methods?
-To test this, this section uses simulated datasets of varying sizes, from 150 to 96,040 (20 times the original sample size).
-These datasets are also derived from the @dorie_2019_automated `aciccomp2016` package, using parameter set 7, a fairly nonlinear DGP with high heterogeneity.
-For sample sizes less than 4,802, the sample is randomly drawn from a randomly generated 4,802-unit sample.
-For sample sizes greater than 4,802, the design matrix (but non the outcome variable) is duplicated, then fed into the `dgp_2016` function.
-This preserves covariate distributions but retains stochasticity in the outcome.
-
-Results are presented in Table \@ref(tab:dorie-results-size) and Figure \@ref(fig:dorie-size-fig).
-
-```{r dorie-size-fig, fig.height = 6, fig.cap = 'RMSE of Monte Carlo simulations using dataset 7 from Dorie et al. (2019) with varying sample sizes, 20 replications each'}
-addline_format <- function(x,...){
-    gsub('\\s','\n',x)
-}
-
-# sim_results %>%
-#   filter(set %in% c('small', 'large')) %>% 
-#   group_by(method_estimator, size) %>%
-#   summarize(bias = round(mean(ate - truth, na.rm = T), 3),
-#             percent_bias = bias/sd(ate, na.rm = T),
-#             rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
-#             mae = median(abs(ate - truth), na.rm = T),
-#             comp_time = sum(comp_time)/n(),
-#             fail_count = n() - sum(!is.na(ate))
-#               ) %>%
-#   mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
-#   mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator})),
-#          size = factor(size, levels = sort(unique({.$size})))) %>%
-#   ggplot(aes(x = size, y = rmse)) +
-#   geom_point() +
-#   facet_wrap(~method_estimator, ncol = 1, scales = 'free')
-
-# # text labels
-# sim_results %>%
-#   filter(set %in% c('small', 'large')) %>% 
-#   group_by(method, estimator, method_estimator, size) %>%
-#   summarize(bias = round(mean(ate - truth, na.rm = T), 3),
-#             percent_bias = bias/sd(ate, na.rm = T),
-#             rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
-#             mae = median(abs(ate - truth), na.rm = T),
-#             comp_time = sum(comp_time)/n(),
-#             fail_count = n() - sum(!is.na(ate))
-#               ) %>%
-#   mutate(estimator = if_else(is.na(estimator), 'NA', estimator)) %>%
-#   mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
-#   mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator})),
-#          size = factor(size, levels = sort(unique({.$size})))) %>%
-#   ggplot(aes(x = size, y = rmse, color = estimator, label= method)) +
-#   geom_text() +
-#   scale_y_continuous(trans='log10')
-
-sim_results %>%
-  filter(set %in% c('small', 'large')) %>%
-  group_by(method, estimator, method_estimator, size) %>%
-  summarize(bias = round(mean(ate - truth, na.rm = T), 3),
-            percent_bias = bias/sd(ate, na.rm = T),
-            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
-            mae = median(abs(ate - truth), na.rm = T),
-            comp_time = sum(comp_time)/n(),
-            fail_count = n() - sum(!is.na(ate))
-              ) %>%
-  group_by(method_estimator) %>%
-  mutate(min_size = min(size*bias/bias, na.rm = T)) %>%
-  ungroup() %>%
-  mutate(estimator = if_else(is.na(estimator), 'NA', estimator),
-         method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
-  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator})),
-         label_min = if_else(size == min_size, as.character(method_estimator), NA_character_),
-         label_max = if_else(size == max(as.numeric(size)), 
-                             as.character(method_estimator), NA_character_),
-         size = factor(size, levels = sort(unique({.$size})))) %>%
-  ggplot(aes(x = size, y = rmse, color = method, linetype = estimator, group = method_estimator)) +
-  geom_line() +
-  ggrepel::geom_text_repel(aes(label = label_min), nudge_x = -1, na.rm = T, segment.color = 'transparent') +
-  ggrepel::geom_text_repel(aes(label = label_max), nudge_x = 1, na.rm = T, segment.color = 'transparent') +
-  scale_y_continuous(trans='log10') +
-  theme(legend.position = 'none')
-```
-
-## Comparisons using LaLonde NSW Data
-
-As another test, I use data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW), as provided by @dehejia_1999_causal.
-Between March 1975 and July 1977, the NSW randomly provided training to disadvantaged workers.
-LaLonde used earnings in 1978 as the outcome of interest; comparing earnings in this year for treated and untreated workers allows an experimental estimate of the effect of the intervention.
-Restricting the sample to men, this study had `r nrow(filter(lalonde_exp, treat == T))` treated and `r nrow(filter(lalonde_exp, treat == F))` control participants.
-Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, and not having a high school degree.
-Following @dehejia_1999_causal, I add a variable indicating whether each respondent's earnings in 1975 was $0 -- i.e., they were unemployed.
-
-LaLonde compared these experimental estimates to control samples drawn from the Panel Study of Income Dynamics (PSID) and Westat's Matched Current Population Survey-Social Security Administration File (CPS).
-The PSID-1 sample (*n* = `r nrow(lalonde_psid1_controls)`) contains all male household heads under 55 who did not classify themselves as retired in 1975, and the PSID-3 sample (*n* = `r nrow(lalonde_psid3_controls)`) further restricts this to men who were not working in spring of 1976 or 1975.
-The CPS-1 sample (*n* = `r nrow(lalonde_cps1_controls)`) includes all CPS males under 55, and CPS-3 (*n* = `r nrow(lalonde_cps3_controls)`) restricts this two those who were not working in March 1976 whose earnings in 1975 was below the poverty level.
-Restricting these observational samples gets closer to the group eligible for the NSW.
-
-Following @dehejia_1999_causal, I present results for the original samples analyzed by @lalonde_1986_evaluating, but I also include results using a subsample of the experimental group that has 1974 earnings data available (`r nrow(filter(lalonde_exp_74, treat == T))` treated and `r nrow(filter(lalonde_exp_74, treat == F))` control participants) and include this additional covariate, along with an indicator variable for no earnings in 1974.
-
-I again compare the three double robust methods to a linear model fitted by OLS ("ols") and propensity score matching using logistic regression ("psm").
-Results are presented in Table \@ref(tab:lalonde), Figure \@ref(fig:lalonde-combined), and Figure \@ref(fig:lalonde-combined-1974).
-
-The "experimental" column provides a baseline for the comparison, suggesting that the program resulted in an earnings gain of about \$700 to \$800.
-If selection on observables holds, then we should be able to recover these estimates from the non-experimental control groups.
-Most of the methods do not perform very well; the only ones to estimate a positive treatment effects are OLS for the PSID-3 sample and TMLE for the CPS samples, and these are still smaller than the experimental baselines.
-
-Including 1974 earnings data results in much better estimates with the observational control groups.
-For PSID-1, TMLE provides estimates closest to the experimental ones, while DML performs much worse than even OLS.
-For PSID-3, OLS and TMLE both perform well.
-For CPS-1 and CPS-3, TMLE performs the best.
-
-These results highlight the importance of selection on observables holding.
-Without including 1974 earnings as a covariate, it appears that selection on observables does not hold, as most methods provide highly inaccurate estimates with the wrong sign.
-Once 1974 earnings are included, all of the methods provide estimates much closer to the experimental values.
-PSM, AIPW, and TMLE all do fairly well, while OLS and DML are more unstable across samples.
-
-```{r lalonde-calc-homemade, eval = F}
-
-lalonde_func <- function(dataset, sample, include_74 = F){
-  set.seed(872)
-
-  if(include_74 == F){
-    lalonde_variables <- names(lalonde_exp)[3:9]
-    dataset <- bind_rows(filter(lalonde_exp, treat == 1), dataset)
-
-  } else {
-    lalonde_variables <- names(lalonde_exp_74)[3:10]
-    dataset <- bind_rows(filter(lalonde_exp_74, treat == 1), dataset)
-  }
-
-  dat <- list(y = dataset$re78,
-                z = ifelse(dataset$treat == 1, 'trt', 'ctl'),
-                x = dataset[,lalonde_variables])
-
-  out_list <- list()
-
-  out_list[['ols']] <- data.frame(
-      method = 'ols',
-      estimator = NA,
-      ate = lm_sim(list(dat))$est_df$ate)
-
-  out_list[['psm']] <- data.frame(
-      method = 'psm',
-      estimator = NA,
-      ate = lm_sim(list(dat))$est_df$ate)
-
-  ols_logit_pred_out <- ols_logit_pred(
-    y = dat$y,
-    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-    x = dat$x)
-
-  grf_pred_out <- grf_pred(
-    y = dat$y,
-    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-    x = dat$x)
-
-  superlearner_pred_out <- superlearner_pred(
-    y = dat$y,
-    d = as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-    x = dat$x)
-
-  predictions <- list(ols_logit_pred_out, grf_pred_out, superlearner_pred_out)
-  pred_names <- c('ols_logit', 'grf', 'superlearner')
-  for(j in 1:length(predictions)){
-    aipw_out <- with(predictions[[j]], 
-                     aipw_calc_trunc(mu1_pred = mu1_pred, 
-                               mu0_pred = mu0_pred,
-                               pi_pred = pi_pred,
-                               d = d,
-                               y = y))
-
-    out_list[[paste0('aipw', j)]] <- data.frame(
-      method = 'aipw',
-      estimator = pred_names[[j]],
-      ate = aipw_out)
-
-    tmle_out <- with(predictions[[j]], 
-                       tmle_calc(mu1_pred = normalize(mu1_pred, y), 
-                                 mu0_pred = normalize(mu0_pred, y),
-                                 pi_pred = pi_pred,
-                                 d = d,
-                                 y = normalize(y, y))
-                       )
-
-      out_list[[paste0('tmle', j)]] <- data.frame(
-        method = 'tmle',
-        estimator = pred_names[[j]],
-        ate =  denormalize(tmle_out, predictions[[j]]$y))
-  }
-
-  dml_pre_out <- dml_pre(dat$y,
-                         as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-                         x = dat$x)
-  ols_logit_dml_out <- do.call(ols_logit_dml, dml_pre_out)
-  dml_post_out <- do.call(dml_post, append(dml_pre_out, ols_logit_dml_out))
-
-  out_list[['dml_ols_logit']] <- data.frame(method = 'dml',
-                                            estimator = 'ols_logit',
-                                            ate = dml_post_out)
-
-  dml_pre_out <- dml_pre(dat$y,
-                     as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-                     x = dat$x)
-  grf_dml_out <- do.call(ols_logit_dml, dml_pre_out)
-  dml_post_out <- do.call(dml_post, append(dml_pre_out, grf_dml_out))
-
-  out_list[['dml_grf']] <- data.frame(method = 'dml',
-                                            estimator = 'grf',
-                                            ate = dml_post_out)
-
-  dml_pre_out <- dml_pre(dat$y,
-                     as.numeric(ifelse(dat$z == 'trt', 1, 0)),
-                     x = dat$x)
-  superlearner_dml_out <- do.call(ols_logit_dml, dml_pre_out)
-  dml_post_out <- do.call(dml_post, append(dml_pre_out, superlearner_dml_out))
-
-  out_list[['dml_superlearner']] <- data.frame(method = 'dml',
-                                            estimator = 'superlearner',
-                                            ate = dml_post_out)
-
-  bind_rows(out_list) %>%
-    mutate(sample = sample) %>%
-    return()
-}
-
-lalonde_func_out <- bind_rows(
-  lalonde_func(filter(lalonde_exp, treat == 0), sample = 'experimental'),
-  lalonde_func(lalonde_psid1_controls, 'PSID-1'),
-  lalonde_func(lalonde_psid3_controls, 'PSID-3'),
-  lalonde_func(lalonde_cps1_controls, 'CPS-1'),
-  lalonde_func(lalonde_cps1_controls, 'CPS-3'))
-
-  lalonde_func_out %>%
-    pivot_wider(names_from = 'sample', values_from = ate) %>%
-  mutate(estimator = factor(estimator, levels = c('ols_logit', 'grf', 'superlearner')),
-         method = factor(method, levels = c('ols', 'psm', 'aipw', 'aipw (trim)', 'tmle', 'dml'))) %>%
-  arrange(method, estimator) %>%
-  #write_csv(here('files/homemade', 'lalonde.csv'))
-
-bind_rows(
-  lalonde_func(filter(lalonde_exp_74, treat == 0), sample = 'experimental', T),
-  lalonde_func(lalonde_psid1_controls, 'PSID-1', T),
-  lalonde_func(lalonde_psid3_controls, 'PSID-3', T),
-  lalonde_func(lalonde_cps1_controls, 'CPS-1', T),
-  lalonde_func(lalonde_cps1_controls, 'CPS-3', T)) %>%
-    pivot_wider(names_from = 'sample', values_from = estimate) %>%
-  write_csv(here('files/homemade', 'lalonde_74.csv'))
-
-```
-
-```{r lalonde-calc, eval = F}
+
+# write_csv(sim_results, here('files', 'lalonde_means.csv'))
+```
+
+# (APPENDIX) Appendix {-}
+
+\newpage
+
+# LaLonde NSW Data
+
+```{r lalonde-packages, eval = F}
+library(grf)
+library(DoubleML)
+library(mlr3)
+library(mlr3pipelines)
+library(mlr3learners)
+library(mlr3extralearners)
+
+dml_grf_att <- function(outcome, treatment, covariates, dataset, 
+                    paper, model,  seed = 123){
+  set.seed(seed)
+
+  dataset <- filter(dataset, !is.na(!!sym(outcome))) %>%
+    select(all_of(c(treatment, outcome, covariates)))
+
+  y <- as.numeric(dataset[[outcome]])
+  X <- model_matrix(~., select(dataset, all_of(covariates)))[,]
+  d <- as.numeric(dataset[[treatment]])
+
+  grf_model <- grf::causal_forest(X = X, Y = y, W = d, seed = 123)
+
+  grf_out <- grf::average_treatment_effect(grf_model, target.sample = 'treated')
+
+  # dataset_drop_na$cov_mean <- dataset_drop_na %>%
+  #   select(all_of(covariates_design)) %>%
+  #   mutate_all(scale) %>%
+  #   apply(1, mean)
+
+  # dml_dataframe <- as.data.frame(cbind(y, d, 
+  #                                      d_bar = dataset_drop_na[[paste0('mean_', treatment)]],
+  #                                      as_tibble(X)[,-1], 
+  #                                      as_tibble(mean_X)[,-1], 
+  #                                      cluster = dataset_drop_na[[clustervar]]))
+
+  graph_ensemble_regr = gunion(list(
+      po("learner", lrn("regr.cv_glmnet", s = "lambda.min")),
+      po("learner", lrn('regr.xgboost', max_depth = 4)),
+      po("learner", lrn("regr.glm"))
+    )) %>>%
+      po("regravg", 3)
+
+  ensemble_pipe_regr = as_learner(graph_ensemble_regr)
+
+  # DML
+  set.seed(seed)
+  dml_data <- double_ml_data_from_data_frame(dataset,
+                                             x_cols = covariates,
+                                             y_col = outcome,
+                                             d_cols = treatment)
+
+  # y <- as.numeric(dataset_drop_na[[outcome]])
+  # # X <- select(dataset_drop_na, covariates_design)
+  # X <- model_matrix(~., select(dataset_drop_na, all_of(covariates)))[,]
+  # # mean_X <- model_matrix(~., select(dataset_drop_na, all_of(paste0('mean_', covariates))))[,]
+  # d <- as.numeric(dataset_drop_na[[treatment]])
+  # 
+  # dml_data <- double_ml_data_from_matrix(X = X, y = y, d = d, 
+  #                                        cluster_vars = dataset_drop_na[[clustervar]])
+
+  # dml_data <- double_ml_data_from_matrix(X = select(dataset_drop_na, all_of(covariates_design)),
+  #                                            y = dataset_drop_na[,outcome],
+  #                                            d = dataset_drop_na[,treatment],
+  #                                            cluster_vars = dataset_drop_na[,clustervar])
+  obj_dml_plr_sim_pipe_ensemble = DoubleML::DoubleMLIRM(dml_data, score = 'ATTE',
+                                                  ml_l = ensemble_pipe_regr,
+                                                  ml_m = ensemble_pipe_regr)
+  obj_dml_plr_sim_pipe_ensemble$fit() 
+  dml_out <- data.frame(estimate = obj_dml_plr_sim_pipe_ensemble$coef,
+                         std.error = obj_dml_plr_sim_pipe_ensemble$se)
+
+  return(list(grf = grf_out, 
+              dml = dml_out))
+}
+
 unemp_func <- function(x){
@@
 
-lalonde_func <- function(dataset, sample, include_74 = F){
-  set.seed(872)
-
-  if(include_74 == F){
-    lalonde_variables <- names(lalonde_exp)[3:9]
-    dataset <- bind_rows(filter(lalonde_exp, treat == 1), dataset)
-
-  } else {
-    lalonde_variables <- names(lalonde_exp_74)[3:10]
-    dataset <- bind_rows(filter(lalonde_exp_74, treat == 1), dataset)
-  }
-
-  dataset <- list(list(y = dataset$re78,
-                z = ifelse(dataset$treat == 1, 'trt', 'ctl'),
-                x = dataset[,lalonde_variables]))
-
-  lapply(list(
-    lm_sim(dataset),
-    psm_sim(dataset),
-    aipw_sim(dataset),
-    tmle_sim(dataset),
-    dml_sim(dataset)),
-  bind_cols) %>%
-    bind_rows() %>%
-    mutate(method = c('ols', 'psm', 'aipw', 'tmle', 'dml'),
-           sample = sample,
-           ate = round(d),
-           se = round(se),
-           estimate = paste0(round(d), ' (', round(se), ')')) %>%
-    select(method, sample, estimate) 
-}
-
-bind_rows(
-  lalonde_func(filter(lalonde_exp, treat == 0), sample = 'experimental'),
-  lalonde_func(lalonde_psid1_controls, 'PSID-1'),
-  lalonde_func(lalonde_psid3_controls, 'PSID-3'),
-  lalonde_func(lalonde_cps1_controls, 'CPS-1'),
-  lalonde_func(lalonde_cps1_controls, 'CPS-3')) %>%
-    pivot_wider(names_from = 'sample', values_from = estimate) %>%
-  write_csv(here('files', 'lalonde.csv'))
-
-bind_rows(
-  lalonde_func(filter(lalonde_exp_74, treat == 0), sample = 'experimental', T),
-  lalonde_func(lalonde_psid1_controls, 'PSID-1', T),
-  lalonde_func(lalonde_psid3_controls, 'PSID-3', T),
-  lalonde_func(lalonde_cps1_controls, 'CPS-1', T),
-  lalonde_func(lalonde_cps1_controls, 'CPS-3', T)) %>%
-    pivot_wider(names_from = 'sample', values_from = estimate) %>%
-  write_csv(here('files', 'lalonde_74.csv'))
-```
-
-```{r lalonde, eval = F}
-bind_rows(
-  read_csv(here('files', 'lalonde.csv')) %>%
-    mutate(sample = 'Original LaLonde'),
-  read_csv(here('files', 'lalonde_74.csv')) %>%
-    mutate(sample = 'With 1974 earnings')) %>%
-  select(sample, method, everything()) %>%
+lalonde_exp_models <- dml_grf_att(outcome = 're78', 
+        treatment = 'treat', 
+        covariates = c('age', 'education', 'black', 'hispanic', 'married', 'nodegree', 're75', 're75_0'),
+        dataset = lalonde_exp,
+        paper = 'NSW',
+        model = 'experimental')
+
+```
+
+```{r lalonde, fig.height = 8, fig.cap = 'ATE estimates and 95-percent bootstrap standard error confidence intervals for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
+Standard errors shown in parentheses.
+Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
+The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnings in 1974.'}
+# lalonde_means <- read_csv(here('files', 'lalonde_means.csv'))
+
+lalonde_results <- sim_results %>%
+  mutate(set = ifelse(set == 'lalondeCPS-3 74', 'lalonde CPS-3 74', set),
+         set = ifelse(set == 'lalondeCPS-3 original', 'lalonde CPS-3 original', set)) %>%
+  filter(str_detect(set, 'lalonde')) %>%
+  # filter(str_detect(set, 'experimental') | str_detect(set, 'PSID-3')) %>%
+  group_by(set, method_estimator, method, estimator) %>%
+  summarize(se = sd(ate),
+            estimate = mean(ate)) %>%
+  ungroup() %>%
+  # left_join(select(lalonde_means, estimate = ate, method, estimator, set)) %>%
+  separate_wider_delim(set, delim = ' ', names = c('set', 'sample', 'include_74')) %>%
+  mutate(sample = str_replace(sample, 'experimental', 'Experimental'),
+         sample = factor(sample, levels = c('Experimental', 'CPS-1', 'CPS-3', 'PSID-1', 'PSID-3')),
+         # estimator = factor(estimator, levels = c('ols_logit', 'ols', 'logit', 'grf', 'superlearner')),
+         # method = factor(method, levels = c('ols', 'psm','ipw', 'g-comp', 'lin', 'aipw', 'tmle', 'dml')),
+         include_74 = ifelse(include_74 == '74', 'With 1974 earnings', 'Original LaLonde sample'),
+         lower = estimate - 1.96*se, 
+         upper = estimate + 1.96*se)
+
+            # lower = quantile(ate, .0275),
+            # upper = quantile(ate, .975))
+            # upper = estimate + 1.96*sd(ate),
+            # lower = estimate - 1.96*sd(ate))
+
+lalonde_results %>%
+  mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
+  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator}))) %>%
+  ggplot(aes(x = sample, y = estimate, color = include_74, shape = include_74)) +
+  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(width = .5), size = .3) +
+  geom_hline(yintercept = 0) +
+  facet_wrap(~method_estimator) +
+  labs(x = '', y = '') +
+  coord_cartesian(ylim = c(-5000, 5000)) +
+  theme(axis.text.x=element_text(angle=90, hjust=0.95,vjust=0.3),
+        legend.position = 'bottom')  +
+  labs(title = 'Results for Lalonde NSW data, with CPS and PSID comparison groups')
+
+ggsave(here('draft/figures', 'lalonde.png'), width = 18,  height = 8, dpi = 1200)
+```
+
+As another evaluation of these methods, I use data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW), as provided by @dehejia_1999_causal.
+Between March 1975 and July 1977, the NSW randomly provided training to disadvantaged workers.
+LaLonde used earnings in 1978 as the outcome of interest; comparing earnings in this year for treated and untreated workers allows an experimental estimate of the effect of the intervention.
+Restricting the sample to men, this study had `r nrow(filter(lalonde_exp, treat == T))` treated and `r nrow(filter(lalonde_exp, treat == F))` control participants.
+Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, and not having a high school degree.
+Following @dehejia_1999_causal, I add a variable indicating whether each respondent's earnings in 1975 was $0 -- i.e., they were unemployed.
+
+LaLonde compared these experimental estimates to control samples drawn from the Panel Study of Income Dynamics (PSID) and Westat's Matched Current Population Survey-Social Security Administration File (CPS).
+The PSID-1 sample (*n* = `r nrow(lalonde_psid1_controls)`) contains all male household heads under 55 who did not classify themselves as retired in 1975, and the PSID-3 sample (*n* = `r nrow(lalonde_psid3_controls)`) further restricts this to men who were not working in the spring of 1976 or 1975.
+The CPS-1 sample (*n* = `r nrow(lalonde_cps1_controls)`) includes all CPS males under 55, and CPS-3 (*n* = `r nrow(lalonde_cps3_controls)`) restricts this two those who were not working in March 1976 whose earnings in 1975 were below the poverty level.
+Restricting these observational samples gets closer to the group eligible for the NSW.
+
+Following @dehejia_1999_causal, I present results for the original samples analyzed by @lalonde_1986_evaluating, but I also include results using a subsample of the experimental group that has 1974 earnings data available (`r nrow(filter(lalonde_exp_74, treat == T))` treated and `r nrow(filter(lalonde_exp_74, treat == F))` control participants) and include this additional covariate, along with an indicator variable for no earnings in 1974.
+
+Results are presented in Figure \@ref(fig:lalonde), with a table in the Appendix (Table 
+\@ref(tab:lalonde-all)).
+Standard errors are based on 100 bootstrap samples.
+We first focus on the original LaLonde dataset, which did not include 1974 earnings.
+The "experimental" estimates provide a baseline for the comparison, suggesting that the program resulted in an earnings gain of about \$800.
+Some methods calculate widely different results for the experimental estimates, highlighting their instability.
+Echoing results from the simulations, methods that include logit models are particularly unstable.
+
+If selection on observables holds, then we should be able to recover experimental estimates from the non-experimental control groups.
+Most of the methods do not perform very well, estimating treatment effects with the wrong sign.
+The exception is in the PSID-3 sample, where 12 of the 17 methods estimate treatment effects with the correct (positive) sign.
+This sample is chosen to be closer to the experimental sample.
+
+Including 1974 earnings data results in much better estimates with the observational control groups.
+OLS, PSM, G-computation (SuperLearner), AIPW (SuperLearner), TMLE (SuperLearner), and DML (OLS/logit) compute fairly stable estimates across the samples.
+On the other hand, the estimates produced by IPW (logit), IPW (GRF), IPW (SuperLearner), the Lin estimator, and DML (GRF) vary widely across samples.
+
+These results highlight the importance of selection on observables holding.
+Without including 1974 earnings as a covariate, it appears that selection on observables does not hold, as most methods provide highly inaccurate estimates with the wrong sign.
+Once 1974 earnings are included, most of the methods provide estimates much closer to the experimental values.
+
+\newpage
+
+```{r lalonde-all}
+# lalonde_results <- sim_results %>%
+#   mutate(set = ifelse(set == 'lalondeCPS-3 74', 'lalonde CPS-3 74', set),
+#          set = ifelse(set == 'lalondeCPS-3 original', 'lalonde CPS-3 original', set)) %>%
+#   filter(str_detect(set, 'lalonde')) %>%
+#   separate_wider_delim(set, delim = ' ', names = c('set', 'sample', 'include_74')) %>%
+#   mutate(sample = factor(sample, levels = unique({.$sample})),
+#          include_74 = ifelse(include_74 == 'original', 'No', "Yes"))
+
+lalonde_results %>%
+  mutate(include_74 = ifelse(include_74 == 'With 1974 earnings', 'Yes', 'No')) %>%
+  # group_by(set, sample, include_74, method_estimator) %>%
+  # summarize(estimate = mean(ate),
+  #           se = sd(ate)) %>%
+  # ungroup() %>%
+  mutate(value = paste0(round(estimate), ' (', round(se), ')')) %>%
+  select(`'74 earnings?` = include_74, Sample = sample, Method = method_estimator, value) %>%
+  arrange(Sample) %>%
+  pivot_wider(values_from = value, names_from = Sample) %>%
+  arrange(`'74 earnings?`, Method) %>%
+  mutate(Method = str_replace(Method, 'superlearner', 'superl.')) %>%
   kableExtra::kable(booktabs = T, 
                     # digits = 3,
-                    # linesep = '',
+                    linesep = '',
                     caption = 'ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
-Standard errors shown in parentheses.
+Bootstrap standard errors shown in parentheses.
 Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
-The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnigns in 1974.')
-
-# bind_rows(
-#   read_csv(here('files', 'lalonde.csv')) %>%
-#     mutate(sample = 'LaLonde'),
-#   read_csv(here('files', 'lalonde_74.csv')) %>%
-#     mutate(sample = 'DW (with 1974 earnings)')) %>%
-#   select(sample, everything()) %>%
-#   kableExtra::kable(booktabs = T, 
-#                     # digits = 3,
-#                     linesep = '',
-#                     caption = 'ATE estimates for Lalonde NSW data from Dehejia and Wahba (1999), with PSID ')
-
-# lalonde_exp_df <- filter(lalonde, exper == 1)
-# fit <- CBPS::CBPS(treat ~ age + educ + re75 + re74 + 
-# 			I(re75==0) + I(re74==0), 
-# 			data = lalonde_exp_df, ATT = TRUE)
-# summary(fit)
-# m.out <- MatchIt::matchit(treat ~ fitted(fit), method = "nearest", 
-# 				 data = lalonde_exp_df, replace = TRUE)
-# lm(re78 ~ treat + age + educ + re75 + re74, MatchIt::match.data(m.out), weights = weights) %>%
-#   tidy()
-# 
-# 
-# lalonde_psid_df <- filter(lalonde, (exper == 1 & treat == 1) | exper == 0)
-# fit <- CBPS::CBPS(treat ~ age + educ + re75 + re74 + 
-# 			I(re75==0) + I(re74==0), 
-# 			data = lalonde_psid_df, ATT = TRUE)
-# m.out <- MatchIt::matchit(treat ~ fitted(fit), method = "nearest", 
-# 				 data = lalonde_psid_df, replace = TRUE)
-# lm(re78 ~ treat + age + educ + re75 + re74, MatchIt::match.data(m.out), weights = weights) %>%
-#   tidy()
-```
-
-```{r lalonde-combined, eval = F, fig.cap = 'ATE estimates and 95% confidence intervals for Lalonde NSW data (original sample) as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.'}
-lalonde_df <- bind_rows(
-  read_csv(here('files', 'lalonde.csv')) %>%
-    mutate(sample = 'Original LaLonde'),
-  read_csv(here('files', 'lalonde_74.csv')) %>%
-    mutate(sample = 'With 1974 earnings')) %>%
-  select(sample, method, everything()) %>%
-  pivot_longer(-c(sample, method)) %>%
-  separate_wider_delim(value, delim = '(', names = c('ate', 'se')) %>%
-  separate_wider_delim(se, delim = ')', names = c('se', 'blank')) %>%
-  mutate(ate = as.numeric(ate), 
-         se = as.numeric(se),
-         method = factor(method, levels = unique({.$method})),
-         name = factor(name, levels = unique({.$name})),
-         experimental = name == 'experimental') %>%
-  select(-blank)
-
-lalonde_df %>%
-  filter(sample == 'Original LaLonde') %>%
-  ggplot(aes(x = name, y = ate, color = experimental)) +
-  geom_pointrange(aes(ymin = ate - 1.96*se, ymax = ate + 1.96*se)) +
-  geom_hline(yintercept = 0) +
-  facet_wrap(~method, scales = 'free_x') +
-  theme(axis.text.x=element_text(angle=-15), 
-        legend.position = 'none') +
-  scale_color_manual(values = ucla_palette) +
-  labs(title = 'Original LaLonde Sample', x = '')   
-```
-
-```{r lalonde-combined-1974, eval = F, fig.cap = 'ATE estimates and 95% confidence intervals for Lalonde NSW data (with 1974 earnings) as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.'}
-lalonde_df %>%
-  filter(sample == 'With 1974 earnings') %>%
-  ggplot(aes(x = name, y = ate, color = experimental)) +
-  geom_pointrange(aes(ymin = ate - 1.96*se, ymax = ate + 1.96*se)) +
-  geom_hline(yintercept = 0) +
-  facet_wrap(~method, scales = 'free_x') +
-  theme(axis.text.x=element_text(angle=-15), 
-        legend.position = 'none') +
-  scale_color_manual(values = ucla_palette) +
-  labs(title = 'With 1974 earnings', x = '')
-```
-
-```{r lalonde-traditional}
+The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnings in 1974.') %>%
+  kable_styling(latex_options = c("hold_position")) 
+```
+
+```{r lalonde-traditional, eval = F}
 lalonde_results <- sim_results %>%
@@
          estimator = factor(estimator, levels = c('ols_logit', 'ols', 'logit', 'grf', 'superlearner')),
-         method = factor(method, levels = c('ols', 'psm', 'lin', 'ipw', 'g-comp', 'aipw', 'tmle', 'dml')))
+         method = factor(method, levels = c('ols', 'psm','ipw', 'g-comp', 'lin', 'aipw', 'tmle', 'dml')))
 
@@
 lalonde_results_df %>%
-  select(include_74:`g-comp, superlearner`) %>%
+  select(include_74:`lin`) %>%
   kableExtra::kable(booktabs = T, 
@@
                     caption = 'Traditional methods: ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
-Standard errors shown in parentheses.
+Bootstrap standard errors shown in parentheses.
 Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
-The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnigns in 1974.')
-```
-
-```{r lalonde-dr}
-lalonde_results_df %>%
-  select(include_74, sample, `g-comp, superlearner`:`dml, superlearner`) %>%
-  kableExtra::kable(booktabs = T, 
-                    # digits = 3,
-                    # linesep = '',
-                    caption = 'Double robust methods: ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
-Standard errors shown in parentheses.
-Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
-The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnigns in 1974.')
-```
-
-# Conclusion
-
-This paper aimed to provide an introduction to and evaluation of double robust methods for covariate adjustment in causal inference.
-By comparing AIPW, TMLE, and DML to the more traditional statistical methods of OLS and PSM, it allows evaluation of whether these methods are worth the effort and (computational) time for social scientists to adopt them.
-
-Results are mixed.
-On the one hand, in the full range of simulated data, AIPW with GRF estimators achieves the lowest bias and root mean squared error.
-This is the simplest (and most computationally efficient) of the double robust methods, although GRF is computationally expensive.
-TMLE with GRF also does fairly well.
-But OLS and PSM have strong showings, in the top three smallest bias or root mean squared error.
-In the datasets with linear data-generating processes, OLS achieves the lowest bias and root mean squared error.
-
-In the experimental LaLonde data, OLS does not perform as strongly.
-Although it is one of the few methods to provide experimental estimates with the correct sign in the original LaLonde set of covariates, its estimates are highly unstable across samples.
-When 1974 earnings are used as a covariate, PSM, AIPW, and TMLE all perform fairly well, though TMLE comes out on top.
-
-Overall, these double robust methods do not show a clear advantage over simpler, more computationally efficient methods such as OLS and PSM.
-While they are useful for social scientists to understand, in most applications, OLS or PSM provide similar results.
-However, in certain circumstances these double robust methods may be a better choice.
-Especially when paired with a highly flexible estimator like GRF, these methods can be useful when the number of covariates is high or even exceeds the number of observations.
-If the researcher believes the data-generating process is highly nonlinear, they may also be a good a choice, at least as a sensitivity check.
-
-This paper has a number of limitations.
-First, it does not consider situations where ignorability does not hold.
-@hunermund_2023_double evaluate a case of this, where endogenous variables are included in the covariate space, showing this can result in biased estimates from DML.
+The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnings in 1974.') %>%
+  kable_styling(latex_options = c("hold_position")) 
+```
 
@@
 
-# References
-
-<div id="refs"></div>
+# Replications with Fixed Effects
+
+The tables below provide estimates from the ASR replications presented in the main text, but with the addition of two other models.
+These implement methods proposed by @clarke_2024_double that incorporate individual or group fixed effects into DML.
+The authors' package, `XTDML`, builds on the `DoubleML` package.
+I use two of their procedures.
+First, correlated random effects (CRE) models explicitly models the correlation between the group-level components in both the treatment and outcome models.
+Second, the authors' "hybrid" model combines CRE with a within-group estimator that partials out group means from all variables, similar to the function of fixed effects in OLS.
+
+```{r rep-aksoy}
+readRDS(here('replication', 'aksoy_rep.RDS')) %>%
+  huxtable::huxreg(statistics = NA,
+                   note = '{stars}.
+Covariates include GDP growth, population, turnout, number of parliamentary seats in province in Model 2 and 3; Models 3 also adjusts for the lagged value of the dependent variable (i.e., one election lagged Islamic votes); cluster robust standard errors are in parentheses.
+The AIPW (GRF) model does not drop incomplete observations.') %>%
+  huxtable::insert_row(c('Covariates', 'No', rep('Yes', 2)), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Lagged dependent variable', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Election year fixed effects', 'Yes', 'Yes', 'Yes'), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Province fixed effects', 'Yes', 'Yes', 'Yes'), after = nrow(.) - 1) %>%
+  huxtable::set_top_border((nrow(.)-4):(nrow(.)-1), value = 0) %>%
+  huxtable::set_top_border((nrow(.)-4), 2:4) %>%
+  huxtable::set_caption('Replication of Aksoy et al.
+(2022) Table 2, models for outcome of Islamic Votes: "Effect of Fasting Hours (Daylength) during Ramadan on Various Outcome Variables Based on Regression Models That Include Fixed Effects for Provinces and Election Years"') %>%
+  huxtable::set_width(.8) %>%
+  huxtable::set_all_padding(0) %>%
+  huxtable::set_latex_float('h!')
+
+# read_rds(here('replication', 'aksoy_tab.RDS')) %>%
+#   huxtable::as_flextable() %>%
+#   flextable::hline(7:8, 1:4, border = officer::fp_border(width = 0)) %>%
+#   flextable::hline(7, 2:4) %>%
+#   flextable::hline(9) %>%
+#   flextable::set_caption('Replication of Aksoy et al.
+(2022) Table 2, models for outcome of Islamic Votes: "Effect of Fasting Hours (Daylength) during Ramadan on Various Outcome Variables Based on Regression Models That Include Fixed Effects for Provinces and Election Years"')
+```
 
@@
 
-# (APPENDIX) Appendix {-}
-
-# Appendix
+```{r rep-biegert}
+readRDS(here('replication', 'biegert_rep.RDS')) %>%
+  huxtable::huxreg(statistics = NA,
+                   note = '{stars}.
+With no control variables, Model 1 could not be estimated using DML with a SuperLearner.
+Model 2 adjusts for year (fixed effects in original model), height (cm), position, age at league entry, being Black, and NBA tenure.
+Model 3 adds controls for the previous year\'s average points per 36 minutes, average assists per 36 minutes, average rebounds per 36 minutes, minutes played, whether the team reached playoffs, the team\'s win percentage, and whether it was a big market team.
+Model 4 adds controls for current average points, average assists, and average rebounds per 36 minutes.
+Model 5 additionally controls for current minutes played, whether the team reaches the playoffs, the team win percentage, and whether it is a big market team.
+Model 6 adds controls for cumulative all-star nominations, average points per 36 minutes, average assists per 36 minutes, average rebounds per 36 minutes, minutes played, team reached playoffs rate, team win percentage, and big market team rate.
+Player clustered standard errors are in parentheses.
+None of the original models include player fixed effects.
+The AIPW (GRF) model does not drop incomplete observations.') %>%
+  huxtable::insert_row(c('Baseline confounders', 'No', rep('Yes', 5)), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Prior situation + performance', rep('No', 2), rep('Yes', 4)), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Current performance', rep('No', 3), rep('Yes', 3)), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Current situation', rep('No', 4), rep('Yes', 2)), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Cumul. AS + cumul. mediators', rep('No', 5), 'Yes'), after = nrow(.) - 1) %>%
+  huxtable::set_top_border((nrow(.)-5):(nrow(.)-1), value = 0) %>%
+  huxtable::set_top_border((nrow(.)-5), 2:7) %>%
+  huxtable::set_caption('Replication of Biegert et al. (2023) Table 3: "Average Marginal Effects from Logistic Regression Models of All-Star Nomination"') %>%
+  huxtable::set_width(1) %>%
+  huxtable::set_all_padding(0) %>%
+  huxtable::set_latex_float('h!')
+
+# read_rds(here('replication', 'biegert_tab.RDS')) %>%
+#   huxtable::as_flextable() %>%
+#   flextable::hline(7:11, 1:7, border = officer::fp_border(width = 0)) %>%
+#   flextable::hline(7, 2:7) %>%
+#   flextable::padding(padding = 0, part = "all") %>% 
+#   flextable::autofit() %>%
+#   flextable::hline(12) %>%
+#   flextable::set_caption('Replication of Biegert et al. (2023) Table 3: "Average Marginal Effects from Logistic Regression Models of All-Star Nomination"')
+```
+
+\newpage
+
+```{r rep-nussio-ind}
+readRDS(here('replication', 'nussio_ind_rep.RDS')) %>%
+  huxtable::huxreg(statistics = NA,
+                   note = "{stars}.
+Models estimate the effect of the log number of names that respondents know in their colonia (neighborhood) on whether they had ever participate in a lynching.
+Model 1 controls for the extent to which people trust others living in their neighborhood.
+Model 2 adds controls for education, age, female, number of light bulbs, and unemployment.
+Model 3 additionally controls for employment, being Catholic or non-religious, whether someone has participated in a fight, whether parents live in the colonia, trust in government, garbage on the street, and residential street block.
+Colonia clustered standard errors are in parentheses.
+Model 4 adds colonia fixed effects.
+The AIPW (GRF) model does not drop incomplete observations.") %>%
+  huxtable::insert_row(c('Colonia FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>%
+  huxtable::set_top_border((nrow(.)-2):(nrow(.)-1), value = 0) %>%
+  huxtable::set_top_border((nrow(.)-2), 2:5) %>%
+  huxtable::set_caption('Replication of Nussio (2024) Table 2: "Individual-Level Analysis: Community Ties and Lynching Participation"') %>%
+  huxtable::set_width(.8) %>%
+  huxtable::set_all_padding(0) %>%
+  huxtable::set_latex_float('h!')
+
+# read_rds(here('replication', 'nussio_ind_tab.RDS')) %>%
+#   huxtable::as_flextable() %>%
+#   flextable::hline(7:8, 1:5, border = officer::fp_border(width = 0)) %>%
+#   flextable::hline(7, 2:5) %>%
+#   flextable::hline(9) %>%
+#   flextable::set_caption('Replication of Nussio (2024) Table 2: "Individual-Level Analysis: Community Ties and Lynching Participation"')
+```
+
+\newpage
+
+```{r rep-nussio-ag}
+readRDS(here('replication', 'nussio_ag_rep.RDS')) %>%
+  huxtable::huxreg(statistics = NA,
+                   note = "{stars}.
+Models estimate the effect of neighborly cooperation -- operationalized by the proportion of respondents who think that most neighbors help each other in problems related to electric lighting -- on the log municipal lynching rate.
+Model 1 adds controls for the proportion of respondents in a municipality that trust their neighbors.
+Model controls for population, area in square kilometers, poverty rate, Gini coefficient, share indigenous people, non-religious population, homicide rate, and robbery rate.
+Model 3 adds controls for household victimization and trust in army.
+Model 4 adds estado (state) fixed effects.
+Municipality clustered standard errors are in paratheses.
+The AIPW (GRF) model does not drop incomplete observations.") %>%
+  huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Estado FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Estado clustered SE', 'Yes', 'Yes', 'Yes', 'No'), after = nrow(.) - 1) %>%
+  huxtable::set_top_border((nrow(.)-3):(nrow(.)-1), value = 0) %>%
+  huxtable::set_top_border((nrow(.)-3), 2:5) %>%
+  huxtable::set_caption('Replication of Nussio (2024) Table 4: "Aggregate-Level Analysis: Community Ties and Lynching Rate"') %>%
+  huxtable::set_width(.8) %>%
+  huxtable::set_all_padding(0) %>%
+  huxtable::set_latex_float('h!')
+
+# read_rds(here('replication', 'nussio_ag_tab.RDS')) %>%
+#   huxtable::as_flextable() %>%
+#   flextable::hline(7:9, 1:5, border = officer::fp_border(width = 0)) %>%
+#   flextable::hline(7, 2:5) %>%
+#   flextable::hline(10) %>%
+#   flextable::set_caption('Replication of Nussio (2024) Table 4: "Aggregate-Level Analysis: Community Ties and Lynching Rate"')
+```
+
+\newpage
+
+```{r rep-nussio-ne}
+readRDS(here('replication', 'nussio_ne_rep.RDS')) %>%
+  huxtable::huxreg(statistics = NA,
+                   note = "{stars}.
+Models estimate the effect of the Puebla earthquake on September 19, 2017, on the number of lynching events.
+Data is a panel of Mexican municipalities from 2000 to 2020.
+Specific independent variables include having an earthquake within 250 km (Models 1 and 2) or having earthquake damage (Models 3 and 4), each interacted with a post-2017 indicator variable.
+Municipality clustered standard errors are in parentheses.
+The original models include two-way fixed effects for year and municipality.
+Model 2 and 4 additionally control for homicides, robberies, kidnappings, and infant mortality.
+Machine learning models control for year.
+All models drop incomplete observations; Models 1, and 3 have 51,597 observations, while Models 2, and 4 have 17,225 observations.
+Due to complications with continuous treatment effects, I do not present the original Models 5 and 6, where the independent variable was distance from the earthquake.") %>%
+  huxtable::insert_row(c('Control variables', 'No', 'Yes', 'No', 'Yes'), 
+                       after = nrow(.) - 1) %>%
+  huxtable::set_top_border((nrow(.)-1):(nrow(.)-1), value = 0) %>%
+  huxtable::set_top_border((nrow(.)-1), 2:5) %>%
+  huxtable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"') %>%
+  huxtable::set_width(.8) %>%
+  huxtable::set_all_padding(0) %>%
+  huxtable::set_latex_float('h!')
+
+# Final table
+# huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1),
+#                                   list(m2, grf_out2, dml_out2),
+#                                   list(m3, grf_out3, dml_out3),
+#                                   list(m4, grf_out4, dml_out4),
+#                                   list(m5, grf_out5, dml_out5),
+#                                   list(m6, grf_out6, dml_out6)),
+#                              tidy = F),
+#                  statistics = NA) %>%
+#   huxtable::insert_row(c('Control variables', 'No', 'Yes', 'No', 'Yes', 'No', 'Yes'), 
+#                        after = nrow(.) - 1) %>%
+#   huxtable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"') %>%
+
+# read_rds(here('replication', 'nussio_ne_tab.RDS')) %>%
+#   huxtable::as_flextable() %>%
+#   flextable::hline(7, 1:7, border = officer::fp_border(width = 0)) %>%
+#   flextable::hline(7, 2:7) %>%
+#   flextable::hline(8) %>%
+#   flextable::padding(padding = 0, part = "all") %>% 
+#   flextable::autofit() %>%
+#   flextable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"')
+```
+
+\newpage
+
+# Tables of Results
 
@@
                     longtable = T,
-                    caption = 'Results of Monte Carlo simulations using dataset 7 from Dorie et al.
+                    caption = 'Sample size: Results of Monte Carlo simulations using dataset 7 from Dorie et al.
 (2019) with varying sample sizes, 20 replications each.
-Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is average computation time measured in seconds for each dataset.') %>%
+Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is median computation time measured in seconds for each dataset.') %>%
   kable_styling(latex_options = c("hold_position")) #'repeat_header')) 
 ```
+
+\newpage
+
+# References
+
+<div id="refs"></div>

### 2024-07-29 draft/ms-adj-draft.Rmd
replications

@@
     keep_tex: true
-    number_sections: no
+    number_sections: yes
     pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T, dev = c('pdf', 'png'), fig.retina = 3)
+knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T, dev = c('pdf', 'png'), fig.retina = 3, ft.latex.float = 'float')
 options("yaml.eval.expr" = TRUE)
@@
 }
+
+model_matrix <- function(...){
+  options(na.action='na.pass')
+  matrix_out <- model.matrix(...)
+  options(na.action = 'na.omit')
+  return(matrix_out)
+}
+
+p_val <- function(estimate, std.error){
+  z <- estimate / std.error
+  2*(1 - pnorm(abs(as.numeric(z))))
+}
+
+compare_tbl <- function(model_list, treatment, tidy = T){
+  out_list <- list()
+  k <- 1
+  for(model_set in model_list){
+    names(model_set$grf) <- c('estimate', 'std.error')
+
+    if(tidy == T){
+    original_model <- tidy(model_set$original) %>%
+      filter(term == treatment)
+    } else{
+      original_model <- model_set$original
+    }
+
+    out_list[[k]] <- original_model %>%
+      bind_rows(bind_rows(model_set$grf)) %>%
+      bind_rows(model_set$dml) %>%
+      bind_rows(model_set$dml_cre) %>%
+      bind_rows(model_set$dml_wg_cre) %>%
+      mutate(term = c('Original', 'AIPW (GRF)', 'DML (SuperLearner)', 
+                      'DML (SuperLearner), CRE FE', 'DML (SuperLearner), hybrid FE'), 
+             p.value = p_val(estimate, std.error)) %>%
+      remove_rownames() %>%
+      tibble()
+
+    k <- k+1
+  }
+  return(out_list)
+}
+
+# compare_tbl_notidy <- function(model_list){
+#   out_list <- list()
+#   k <- 1
+#   for(model_set in model_list){
+#     names(model_set[[2]]) <- c('estimate', 'std.error')
+#     
+#     
+#     out_list[[k]] <- model_set[[1]] %>%
+#       bind_rows(bind_rows(model_set[[2]])) %>%
+#       bind_rows(model_set[[3]]) %>%
+#       mutate(term = c('Original', 'AIPW (GRF)', 'DML (SuperLearner)'), p.value = p_val(estimate, std.error)) %>%
+#       tibble()
+#     
+#     k <- k+1
+#   }
+#   return(out_list)
+# }
+
+dml_grf <- function(outcome, treatment, covariates, clustervar = NULL, dataset, 
+                    fe = T, target = 'treated', paper, model, drop_na_grf = F, seed = 123){
+  set.seed(seed)
+
+  dataset <- filter(dataset, !is.na(!!sym(outcome))) %>%
+    select(all_of(c(treatment, outcome, covariates, clustervar)))
+
+  if(drop_na_grf == T){
+    dataset <- dataset %>%
+      drop_na()
+  }
+
+  y <- as.numeric(dataset[[outcome]])
+  X <- model_matrix(~., select(dataset, all_of(covariates)))[,]
+  d <- as.numeric(dataset[[treatment]])
+
+  grf_model <- grf::causal_forest(X = X, Y = y, W = d, seed = 123,
+                        clusters = dataset[[clustervar]])
+
+  grf_out <- grf::average_treatment_effect(grf_model, target.sample = target)
+
+  dataset_drop_na <- as.data.frame(model_matrix(~., dataset)[,]) %>%
+    # remove annoying characters
+    rename_with(., ~ gsub("'", "", iconv(.x, from = "UTF-8", to='ASCII//TRANSLIT'))) %>%
+    rename_with(., ~ gsub("\\[|\\]|\\/|\\*|\\)|\\(", "", .x)) %>%
+    rename_with(., ~ gsub(" ", "", .x)) %>%
+    # drop missing
+    drop_na() %>%
+    # remove uninformative columns
+    select(where(~n_distinct(.) > 1)) 
+  dataset_drop_na <- dataset_drop_na %>%
+    left_join(dataset_drop_na %>%
+                group_by(!!sym(clustervar)) %>%
+                summarize(across(everything(), mean, .names = 'mean_{.col}')) %>%
+                ungroup()) %>%
+    mutate(intercept = 1)
+  # covariates_design <- dataset_drop_na %>% 
+  #   select(select(-c(treatment, outcome, clustervar))) %>%
+  #   names() %>%
+  #   append('intercept', after = 0)
+  covariates_design <- names(dataset_drop_na)[!(names(dataset_drop_na) %in% c(treatment, outcome, clustervar)) &
+                                                !str_detect(names(dataset_drop_na),  'mean_')]
+
+  # dataset_drop_na$cov_mean <- dataset_drop_na %>%
+  #   select(all_of(covariates_design)) %>%
+  #   mutate_all(scale) %>%
+  #   apply(1, mean)
+
+  # dml_dataframe <- as.data.frame(cbind(y, d, 
+  #                                      d_bar = dataset_drop_na[[paste0('mean_', treatment)]],
+  #                                      as_tibble(X)[,-1], 
+  #                                      as_tibble(mean_X)[,-1], 
+  #                                      cluster = dataset_drop_na[[clustervar]]))
+
+  graph_ensemble_regr = gunion(list(
+      po("learner", lrn("regr.cv_glmnet", s = "lambda.min")),
+      po("learner", lrn('regr.xgboost', max_depth = 4)),
+      po("learner", lrn("regr.glm"))
+    )) %>>%
+      po("regravg", 3)
+
+  ensemble_pipe_regr = as_learner(graph_ensemble_regr)
+
+  # DML
+  set.seed(seed)
+  dml_data <- double_ml_data_from_data_frame(dataset_drop_na,
+                                             x_cols = covariates_design,
+                                             y_col = outcome,
+                                             d_cols = treatment,
+                                             cluster_cols = clustervar)
+
+  # y <- as.numeric(dataset_drop_na[[outcome]])
+  # # X <- select(dataset_drop_na, covariates_design)
+  # X <- model_matrix(~., select(dataset_drop_na, all_of(covariates)))[,]
+  # # mean_X <- model_matrix(~., select(dataset_drop_na, all_of(paste0('mean_', covariates))))[,]
+  # d <- as.numeric(dataset_drop_na[[treatment]])
+  # 
+  # dml_data <- double_ml_data_from_matrix(X = X, y = y, d = d, 
+  #                                        cluster_vars = dataset_drop_na[[clustervar]])
+
+  # dml_data <- double_ml_data_from_matrix(X = select(dataset_drop_na, all_of(covariates_design)),
+  #                                            y = dataset_drop_na[,outcome],
+  #                                            d = dataset_drop_na[,treatment],
+  #                                            cluster_vars = dataset_drop_na[,clustervar])
+  obj_dml_plr_sim_pipe_ensemble = DoubleMLPLR$new(dml_data,
+                                                  ml_l = ensemble_pipe_regr,
+                                                  ml_m = ensemble_pipe_regr)
+  obj_dml_plr_sim_pipe_ensemble$fit() 
+  dml_out <- data.frame(estimate = obj_dml_plr_sim_pipe_ensemble$coef,
+                         std.error = obj_dml_plr_sim_pipe_ensemble$se)
+
+  if(fe == T){
+    # DML CRE
+    set.seed(seed)  
+    dml_data_cre <- XTDML::dml_cre_data_from_data_frame(dataset_drop_na,
+                                                 x_cols = covariates_design,
+                                                 y_col = outcome,
+                                                 d_cols = treatment,
+                                                 xbar_cols = paste0('mean_', covariates_design[-length(covariates_design)]),
+                                                 dbar_cols = paste0('mean_', treatment),
+                                                 cluster_cols = clustervar)  
+    obj_dml_cre = XTDML::dml_cre_plr$new(dml_data_cre,
+                                         ml_l = ensemble_pipe_regr,
+                                         ml_m = ensemble_pipe_regr)
+
+    obj_dml_cre$fit()
+    dml_cre_out <- data.frame(estimate = obj_dml_cre$coef_theta,
+                           std.error = obj_dml_cre$se_theta)
+
+  # DML WG-CRE
+  require(parameters)
+  set.seed(seed)  
+  dml_data_wg_cre <- XTDML::dml_hybrid_data_from_data_frame(dataset_drop_na,
+                                               x_cols = covariates_design,
+                                               y_col = outcome,
+                                               d_cols = treatment,
+                                               xbar_cols = paste0('mean_', covariates_design[-length(covariates_design)]),
+                                               dbar_cols = paste0('mean_', treatment),
+                                               cluster_cols = clustervar)  
+  obj_dml_wg_cre = XTDML::dml_hybrid_plr$new(dml_data_wg_cre,
+                                       ml_l = ensemble_pipe_regr,
+                                       ml_m = ensemble_pipe_regr)
+
+  obj_dml_wg_cre$fit()
+  dml_wg_cre_out <- data.frame(estimate = obj_dml_wg_cre$coef_theta,
+                         std.error = obj_dml_wg_cre$se_theta)
+  } else {
+    dml_cre_out <- data.frame(estimate = NA,
+                           std.error = NA)
+    dml_wg_cre_out <- data.frame(estimate = NA,
+                         std.error = NA)
+  }
+
+  return(list(grf = grf_out, 
+              dml = dml_out,
+              dml_cre = dml_cre_out,
+              dml_wg_cre = dml_wg_cre_out))
+}
+
 ```
@@
 They are tested on simulations from @dorie_2019_automated, which cover a range of data-generating processes where ignorability holds -- i.e., there are no unmeasured confounders.
-They are then used to estimate experimental and observational effects from real-world data, the National Support for Work Demonstration (NSW) originally analyzed by @lalonde_1986_evaluating.
+In the Online Appendix, I also estimate experimental and observational effects from the National Support for Work Demonstration (NSW) originally analyzed by @lalonde_1986_evaluating.
 In these evaluations, double robust methods are compared to "single robust" methods (i.e., ones with one nuisance model).
@@
 They are also compared to two more flexible methods that may overcome the misspecification issues that double robust methods aim to overcome: G-computation and the Lin estimator [@lin_2013_agnostic].
+Lastly, I use two of the double robust methods to replicate analyses from three recent *American Sociological Review* (ASR) papers that use OLS or logistic regression to estimate causal effects.
 
@@
 When appropriate covariates are included, most methods perform well.
+
+In the *ASR* replications, double robust methods provide similar coefficients for most, but not all, of the analyses.
+In some cases, significance is lost, and in a minority of cases the coefficient sign changes.
+These replications highlight the importance of testing the robustness of quantitative results by comparing multiple methods and estimators.
 <!-- Exceptions include IPW, DML, and the Lin estimator (surprising given the simulation results), whose estimates tend to be less stable across samples.   -->
@@
 # Overview of Techniques  
-Each of the methods reviewed in this paper can be thought of as a collection of estimation techniques.
-Each involves a model for the outcome and another for the treatment exposure, but choice of estimation technique for these two models is left to the discretion of the user.
-The ways these estimated models relate and are combined into a final effect estimate vary between double robust methods.
+Each of the methods reviewed in this paper can be used with a variety of estimation techniques, including both traditional statistical methods and flexible machine learning methods.
+Each involves a model for the outcome and another for the treatment exposure, but choice of estimator for these two models is left to the discretion of the user.
+Double robust methods are distinct in the ways these estimated models relate and are combined into a final estimate of the desired estimand.
+
+This section provides some intuition for the mathematical theory behind each method and contains R code to simply implement these methods.
+This is the code used to evaluate these methods later in this paper, and it represents basic implementations of these methods.
+However, for researchers wishing to put these methods into practice, using a dedicated R packages for each method is probably a better idea.
+These packages have many flexible options, such as accounting for complex survey design, targeting estimands besides the ATE, and integrating with a variety of estimation techniques.
+In the Online Appendix, Table \@ref(tab:packages) suggests packages for each method.
 
@@
 
-More formally, suppose we want to estimate $\tau$ in the following framework:^[Note that this basic DML setup assumes a partially linear model and targets the ATE.
+More formally, suppose we want to estimate $\tau$ in the following framework:^[Note that this basic DML setup -- presented in the introduction of @chernozhukov_2018_double -- assumes a partially linear model and targets the ATE.
 If we are interested in the CATE and heterogeneous effects, Chernozhukov et al.
@@
 C35] present an alternative score function that closely resembles AIPW.
+In this case, DML and AIPW are identical, except DML also includes sample splitting, accounting for the regularization bias that flexible machine learning estimators may induce.
 See also @jacob_2021_cate and @nie_2021_quasioracle.]
@@
   # huxtable::set_latex_float('h!') %>%
-  huxtable::set_caption('Double and single robust methods used for evaluation')
+  huxtable::set_caption('Double and single robust methods used for evaluation. The super learner estimator is an ensemble learning method relying on GLM, glmnet, and XGBoost.')
 
@@
 
-Because many of these methods allow the user to choose the underlying estimation method, results compare three techniques.
-The first technique uses a logistic regression for the exposure model and an OLS regression for the outcome model.
+Because many of these methods allow the user to choose the underlying estimation method, results compare three estimators The first estimator uses a logistic regression for the exposure model and an OLS regression for the outcome model.
 Second is generalized random forests [GRF, @athey_2019_generalized] using the `grf` R package, with separate models for exposure and outcome.
-The final technique is the SuperLearner (as promoted by the makers of TMLE) using the `SuperLearner` package [@polley_2023_superlearner], again with separate models for exposure and outcome.
-GLM, glmnet [a weighted average of lasso and ridge regression, @friedman_2021_package], and XGBoost [@chen_2016_xgboost] models are considered for the SuperLearner.
+The final estimator is the SuperLearner (as promoted by the makers of TMLE) using the `SuperLearner` package [@polley_2023_superlearner], again with separate models for exposure and outcome.
+GLM, glmnet [a weighted average of lasso and ridge regression, @friedman_2021_package], and XGBoost with a maximum tree depth of 4 [@chen_2016_xgboost] are the models considered for the SuperLearner.
 These three estimation techniques are used for each of the three double robust methods and for IPW.
@@
 For evaluation of the experimental LaLonde data, I use bootstrapping with 100 samples to obtain standard errors and confidence intervals.
-Using AIPW as written above results in some wildly biased estimates, due to dividing by some very small propensity scores.
-Hence I present estimates from a truncated AIPW estimator, where predicted exposure model values are set to 0.01 if they are less than 0.01 and to 0.99 if they are greater than 0.99.
+I use the code shown above for AIPW, TMLE, and DML, and I also compare results for two ready-made double robust packages.
+These include `grf` [@tibshirani_2024_grf], which implements AIPW with generalized random forests, and `DoubleML` [@bach_2024_doubleml], which I use to implement a partially linear DML model with a SuperLearner using GLM, glmnet, and XGBoost.
 
@@
 #perform(bind_rows(superlearner_dml_list), label = 'superlearner, dml')
+
+```
+
+```{r aipw-package, eval = F}
+aipw_package_list <- list()
+
+set.seed(1285)
+for(i in 1:length(sims)){
+  print(paste0(i, ' out of ', length(sims)))
+  dat <- sims[[i]]
+
+  start_time <- Sys.time()
+
+  y <- dat$y
+  d <- as.numeric(ifelse(dat$z == 'trt', 1, 0))
+  x <- model_matrix(~., dat$x)[,]
+
+  grf_model <- grf::causal_forest(X = x, Y = y, W = d)                        
+  grf_out <- grf::average_treatment_effect(grf_model, target.sample = 'all', method = 'AIPW', seed = 123)
+
+  comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
+
+  truth <- mean(dat$y.1) - mean(dat$y.0)
+
+  aipw_package_list[[i]] <- data.frame(ate = grf_out[['estimate']], 
+                              truth = truth, 
+                              comp_time = comp_time,
+                              dataset = i,
+                              dorie_dataset = dat$dataset,
+                              set = dat$set,
+                              size = dat$size)
+
+  if(i %% 100 == 0){
+    write_csv(bind_rows(aipw_package_list), 
+          here('files/homemade', 'aipw_package.csv'))
+  }
+
+}
+
+write_csv(bind_rows(aipw_package_list), 
+          here('files/homemade', 'aipw_package.csv'))
+
+```
+
+```{r dml-package, eval = F}
+library(DoubleML)
+library(mlr3)
+library(mlr3pipelines)
+library(mlr3learners)
+library(mlr3extralearners)
+
+dml_package_list <- list()
+
+set.seed(1285)
+for(i in 1:length(sims)){
+  print(paste0(i, ' out of ', length(sims)))
+  dat <- sims[[i]]
+
+  start_time <- Sys.time()
+
+  dml_data <- double_ml_data_from_matrix(X = model_matrix(~., dat$x)[,],
+           y = dat$y,
+           d = as.numeric(ifelse(dat$z == 'trt', 1, 0)))
+
+  graph_ensemble_regr = gunion(list(
+      po("learner", lrn("regr.cv_glmnet", s = "lambda.min")),
+      po("learner", lrn('regr.xgboost', max_depth = 4)),
+      po("learner", lrn("regr.glm"))
+    )) %>>%
+      po("regravg", 3)
+
+  ensemble_pipe_regr = as_learner(graph_ensemble_regr)
+  set.seed(123)
+  obj_dml_plr_sim_pipe_ensemble = DoubleMLPLR$new(dml_data,
+                                                  ml_l = ensemble_pipe_regr,
+                                                  ml_m = ensemble_pipe_regr)
+  obj_dml_plr_sim_pipe_ensemble$fit()
+
+  comp_time <- as.numeric(difftime(Sys.time(), start_time, units = 'secs'))
+
+  truth <- mean(dat$y.1) - mean(dat$y.0)
+
+  dml_package_list[[i]] <- data.frame(ate = as.vector(obj_dml_plr_sim_pipe_ensemble$coef), 
+                              truth = truth, 
+                              comp_time = comp_time,
+                              dataset = i,
+                              dorie_dataset = dat$dataset,
+                              set = dat$set,
+                              size = dat$size)
+
+  if(i %% 100 == 0){
+    write_csv(bind_rows(dml_package_list), 
+          here('files/homemade', 'dml_package.csv'))
+  }
+
+}
+
+write_csv(bind_rows(dml_package_list), 
+          here('files/homemade', 'dml_package.csv'))
 
@@
 
+# aipw_package_df <- read_csv(here('files/homemade', 'aipw_package.csv')) %>%
+#   mutate(estimator = 'grf (package)',
+#          method = 'aipw')
+# 
+# dml_package_df <- read_csv(here('files/homemade', 'dml_package.csv')) %>%
+#   mutate(estimator = 'superlearner (package)',
+#          method = 'dml')
+
 sim_results <- bind_rows(lm_df, psm_df, lin_df, ipw_df, gcomp_df, aipw_trunc_df, tmle_df, dml_df) %>%
-  mutate(estimator = factor(estimator, levels = c('ols_logit', 'ols', 'logit', 'grf', 'superlearner')),
+  mutate(estimator = factor(estimator, levels = c('ols_logit', 'ols', 'logit', 
+          'grf', 'grf (package)', 'superlearner', 'superlearner (package)')),
          method = factor(method, levels = c('ols', 'psm', 'ipw', 'g-comp', 'lin', 
-                                            'aipw', 'tmle', 'dml', 'aipw (original)'))) %>%
+                                            'aipw', 'tmle', 'dml', 'aipw (original)', 'aipw (package)'))) %>%
   arrange(method, estimator) %>%
@@
 I then calculate bias, percent bias (the estimator's bias as a percentage of its standard error), root mean squared error (rmse), and median absolute error (mae).
-I also present the number of datasets for which the method fails and the median computation time for each data set, in seconds.^[Simulations were run on a 2020 MacBook Pro laptop computer with a 2 GHz Quad-Core Intel Core i5 Processor and 16 GB of memory.] In the main text I present average bias and RMSE, while the appendix contains tables with full results (Table \@ref(tab:dorie-results-table)).
+I also present the number of datasets for which the method fails and the median computation time for each data set, in seconds.^[Simulations were run on a 2020 MacBook Pro laptop computer with a 2 GHz Quad-Core Intel Core i5 Processor and 16 GB of memory.] In the main text I present average bias and RMSE, while the Online Appendix contains tables with full results.
 
@@
 
-Figure \@ref(fig:dorie-linear-bias) shows the bias from each simulation for each method (in the Appendix, Table \@ref(tab:dorie-linear-results) shows the full results).
+Figure \@ref(fig:dorie-linear-bias) shows the bias from each simulation for each method (table in the Online Appendix).
 Similarly to the full set of simulations, bias is fairly low for most methods.
@@
 Across the the 20 datasets, @dorie_2019_automated vary five DGP characteristics: degree of nonlinearity, the percentage treated, overlap for the treatment group, alignment (correspondence in variables used to generate the exposure and response models), and treatment effect heterogeneity.
-To test how the methods perform across different values of these characteristics, I begin with the 200 simulations from the 20 datasets used in the main results (Figures \@ref(fig:dorie-results-bias) and \@ref(fig:dorie-results-rmse), Table \@ref(tab:dorie-results-table)).
+To test how the methods perform across different values of these characteristics, I begin with the 200 simulations from the 20 datasets used in the main results (Figures \@ref(fig:dorie-results-bias) and \@ref(fig:dorie-results-rmse)).
 I limit datasets to those generated by a particular value of a DGP characteristic, and I then calculate RMSE for each method for only these datasets.
@@
 Tables \@ref(tab:dgp) and \@ref(tab:dgp-2) shows the six top-performing methods by lowest RMSE for each each value of the DGP characteristics.
-Across DGPs, the same methods dominate as in the full range of simulations: the SuperLearner with AIPW, TMLE, and G-compuation.
+Across DGPs, the same methods dominate as in the full range of simulations: the SuperLearner with AIPW, TMLE, and G-computation.
 In fact, these three methods take the top three spots for *every* DGP variation in the simulations.
@@
 
-Table \@ref(tab:dorie-size) presents the four methods with the lowest RMSE for each sample size (Table \@ref(tab:dorie-results-size) in the Appendix presents full results).
+Table \@ref(tab:dorie-size) presents the four methods with the lowest RMSE for each sample size (the Online Appendix presents a table with full results).
 Again, AIPW, TMLE, and G-computation methods that incorporate the SuperLearner or GRF dominate.
@@
   scale_y_continuous(trans='log10', breaks = c(0.1, 0.5, 1, 10, 100)) +
-  theme(legend.position = 'none') 
-```
+  theme(legend.position = 'none') +
+  labs(x = 'Size (n)')
+```
+
+# Replications
+
+```{r aksoy, eval = F}
+aksoy <- read_dta(here('replication', 'aksoy.dta')) %>%
+  mutate(cid_num = as.integer(factor(cid))) %>%
+  as_factor()
+
+# first three models from table 2
+
+m1 <- lm(ISL ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` + 
+     `_Y66` + `_Y70` + `_Y71` + dlen + cid,
+   data = filter(aksoy, electyr == T)) # %>%
+  # tidy() %>%
+  # filter(!str_detect(term, 'cid'), !str_detect(term, '_Y'))
+
+m2 <- lm(ISL ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` + 
+     `_Y66` + `_Y70` + `_Y71` + dlen + cid + gdp_g + t + m + pop,
+   data = aksoy) 
+  # tidy() %>%
+  # filter(!str_detect(term, 'cid'), !str_detect(term, '_Y'))
+
+m3 <- lm(ISL ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` + 
+     `_Y66` + `_Y70` + `_Y71` + dlen + cid + gdp_g + t + m + pop + l_ISL,
+   data = aksoy) 
+  # tidy() %>%
+  # filter(!str_detect(term, 'cid'), !str_detect(term, '_Y'))
+
+aksoy_drop_na_y <- filter(aksoy, !is.na(ISL))
+
+m1_grf_dml <- dml_grf(outcome = 'ISL', 
+        treatment = 'dlen', 
+        covariates = c('year'), 
+        clustervar = 'cid_num',
+        dataset = aksoy,
+        target = 'all')
+
+m2_grf_dml <- dml_grf(outcome = 'ISL', 
+        treatment = 'dlen', 
+        covariates = c('year', 'gdp_g', 't', 'm', 'pop'), 
+        clustervar = 'cid_num',
+        dataset = aksoy,
+        target = 'all')
+
+m3_grf_dml <- dml_grf(outcome = 'ISL', 
+        treatment = 'dlen', 
+        covariates = c('year', 'gdp_g', 't', 'm', 'pop', 'l_ISL'), 
+        clustervar = 'cid_num',
+        dataset = aksoy,
+        target = 'all')
+
+m1 <- data.frame(estimate = 7.159, std.error = 2.539)
+m2 <- data.frame(estimate = 7.349, std.error = 2.491)
+m3 <- data.frame(estimate = 5.317, std.error = 1.855)
+
+compare_tbl(list(append(list(original = m1), m1_grf_dml), 
+                                  append(list(original = m2), m2_grf_dml), 
+                                  append(list(original = m3), m3_grf_dml)),
+                             tidy = F) %>%
+  write_rds(here('replication', 'aksoy_rep.RDS'))
+
+# huxtable::huxreg(compare_tbl(list(append(list(original = m1), m1_grf_dml), 
+#                                   append(list(original = m2), m2_grf_dml), 
+#                                   append(list(original = m3), m3_grf_dml)),
+#                              tidy = F),
+#                  statistics = NA) %>%
+#   huxtable::insert_row(c('Covariates', 'No', rep('Yes', 2)), after = nrow(.) - 1) %>%
+#   huxtable::insert_row(c('Lagged dependent variable', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
+#   huxtable::set_caption('Replication of aksoy et al.
+(2022) Table 2, models for outcome of Islamic Votes: "Effect of Fasting Hours (Daylength) during Ramadan on Various Outcome Variables Based on Regression Models That Include Fixed Effects for Provinces and Election Years"') %>%
+#   write_rds(here('replication', 'aksoy_tab.RDS'))
+# 
+# read_rds(here('replication', 'aksoy_rep.RDS')) %>%
+#   huxtable::huxreg()
+
+```
+
+```{r biegert, eval = F}
+# Table 3
+
+biegert <- read_dta(here('replication', 'biegert.dta')) %>%
+  filter(sampleC == 1) %>%
+  mutate(year_num = as.numeric(year),
+         allstar_y_num = as.numeric(allstar_y),
+         allstar_x_num = as.numeric(allstar_x),
+    across(c(allstar_y, allstar_x, year), as.factor),
+    player_id_num = as.integer(factor(player_id))) %>%
+  as_factor()
+
+m1 <- glm(allstar_y ~ allstar_x, 
+          data = filter(biegert, sampleC == 1), family = 'binomial') %>%
+  margins::margins(variables = 'allstar_x', 
+                   vcov = sandwich::vcovCL(., cluster = ~player_id))
+
+m2 <- glm(allstar_y ~ allstar_x + height + pos + age_0 + age_0_2 + Black + time + time_2 + year, 
+          data = filter(biegert, sampleC == 1),
+          family = binomial(link = 'logit')) %>%
+  margins::margins(variables = 'allstar_x', 
+                   vcov = sandwich::vcovCL(., cluster = ~player_id))
+
+m3 <- glm(allstar_y ~ allstar_x + height + pos + age_0 + age_0_2 + Black + time + time_2 + year +
+            pts_sdt_nd + ast_sdt_nd + trb_sdt_nd + min_played_nd +  playoffs_nd + win_nd + bigm_nd, 
+          data = filter(biegert, sampleC == 1),
+          family = binomial(link = 'logit')) %>%
+  margins::margins(variables = 'allstar_x', 
+                   vcov = sandwich::vcovCL(., cluster = ~player_id))
+
+m4 <- glm(allstar_y ~ allstar_x + height + pos + age_0 + age_0_2 + Black + time + time_2 + year +
+            pts_sdt_nd + ast_sdt_nd + trb_sdt_nd + min_played_nd +  playoffs_nd + win_nd + bigm_nd +
+            pts_sdt_t + ast_sdt_t + trb_sdt_t, 
+          data = filter(biegert, sampleC == 1),
+          family = binomial(link = 'logit')) %>%
+  margins::margins(variables = 'allstar_x', 
+                   vcov = sandwich::vcovCL(., cluster = ~player_id))
+
+m5 <- glm(allstar_y ~ allstar_x + height + pos + age_0 + age_0_2 + Black + time + time_2 + year +
+            pts_sdt_nd + ast_sdt_nd + trb_sdt_nd + min_played_nd +  playoffs_nd + win_nd + bigm_nd +
+            pts_sdt_t + ast_sdt_t + trb_sdt_t +
+            min_played_t + playoffs_t + win_t + bigm_t, 
+          data = filter(biegert, sampleC == 1),
+          family = binomial(link = 'logit')) %>%
+  margins::margins(variables = 'allstar_x', 
+                   vcov = sandwich::vcovCL(., cluster = ~player_id))
+
+m6 <- glm(allstar_y ~ allstar_x + allstar_hi + height + pos + age_0 + age_0_2 + Black + time + time_2 + year +
+            pts_sdt_nd + ast_sdt_nd + trb_sdt_nd + min_played_nd +  playoffs_nd + win_nd + bigm_nd +
+            pts_sdt_t + ast_sdt_t + trb_sdt_t +
+            min_played_t + playoffs_t + win_t + bigm_t +
+            pts_sdt_hi + ast_sdt_hi + trb_sdt_hi + min_played_hi + playoffs_hi + win_hi + bigm_hi, 
+          data = filter(biegert, sampleC == 1),
+          family = binomial(link = 'logit')) %>%
+  margins::margins(variables = 'allstar_x', 
+                   vcov = sandwich::vcovCL(., cluster = ~player_id))
+
+# M1 
+set.seed(123)
+Y <- as.numeric(biegert[['allstar_y']])
+X <- data.frame(var = rep(NA_integer_, length(Y)))
+W <- as.numeric(biegert[['allstar_x']])
+
+grf_model1 <- grf::causal_forest(X = X, Y = Y, W = W, seed = 123,
+                      clusters = biegert$player_id_num
+                      )
+
+grf_out1 <- grf::average_treatment_effect(grf_model1, target.sample = 'all')
+
+dml_out1 <- data.frame(estimate = NA,
+                       std.error = NA)
+dml_cre_out1 <- dml_out1
+dml_hybrid_out1 <- dml_out1
+
+# M2
+m2_grf_dml <- dml_grf(outcome = 'allstar_y_num', 
+        treatment = 'allstar_x_num', 
+        covariates = c('height', 'pos', 'age_0', 'Black', 'time', 'year_num'), 
+        clustervar = 'player_id_num',
+        dataset = biegert,
+        target = 'all')
+
+# M3 
+m3_grf_dml <- dml_grf(outcome = 'allstar_y_num', 
+        treatment = 'allstar_x_num', 
+        covariates = c('height', 'pos', 'age_0', 'Black', 'time', 'year_num',
+                       'pts_sdt_nd', 'ast_sdt_nd', 'trb_sdt_nd', 'min_played_nd',  'playoffs_nd', 'win_nd', 'bigm_nd'), 
+        clustervar = 'player_id_num',
+        dataset = biegert,
+        target = 'all')
+
+# M4
+m4_grf_dml <- dml_grf(outcome = 'allstar_y_num', 
+        treatment = 'allstar_x_num', 
+        covariates = c('height', 'pos', 'age_0', 'Black', 'time', 'year_num',
+                       'pts_sdt_nd', 'ast_sdt_nd', 'trb_sdt_nd', 'min_played_nd',  'playoffs_nd', 'win_nd', 'bigm_nd',
+                       'pts_sdt_t', 'ast_sdt_t', 'trb_sdt_t'), 
+        clustervar = 'player_id_num',
+        dataset = biegert,
+        target = 'all')
+
+# M5
+m5_grf_dml <- dml_grf(outcome = 'allstar_y_num', 
+        treatment = 'allstar_x_num', 
+        covariates = c('height', 'pos', 'age_0', 'Black', 'time', 'year_num',
+                       'pts_sdt_nd', 'ast_sdt_nd', 'trb_sdt_nd', 'min_played_nd',  'playoffs_nd', 'win_nd', 'bigm_nd',
+                       'pts_sdt_t', 'ast_sdt_t', 'trb_sdt_t',
+                       'min_played_t', 'playoffs_t', 'win_t', 'bigm_t'), 
+        clustervar = 'player_id_num',
+        dataset = biegert,
+        target = 'all')
+
+# # M6
+# m6_grf_dml <- dml_grf(outcome = 'allstar_y_num', 
+#         treatment = 'allstar_x_num', 
+#         covariates = c('height', 'pos', 'age_0', 'Black', 'time', 'year_num',
+#                        'pts_sdt_nd', 'ast_sdt_nd', 'trb_sdt_nd', 'min_played_nd',  'playoffs_nd', 'win_nd', 'bigm_nd',
+#                        'pts_sdt_t', 'ast_sdt_t', 'trb_sdt_t',
+#                        'min_played_t', 'playoffs_t', 'win_t', 'bigm_t',
+#                        'pts_sdt_hi', 'ast_sdt_hi', 'trb_sdt_hi', 'min_played_hi', 'playoffs_hi', 'win_hi', 'bigm_hi'), 
+#         clustervar = 'player_id_num',
+#         dataset = biegert,
+#         target = 'all')
+
+out_empty <- grf_out1
+out_empty$estimate <- NA
+out_empty$std.err <-
+
+compare_tbl(model_list = list(
+                 list(original = m1, grf = grf_out1, dml = dml_out1, dml_cre = dml_cre_out1, dml_wg_cre = dml_hybrid_out1), 
+                 append(list(original = m2), m2_grf_dml), 
+                 append(list(original = m3), m3_grf_dml),
+                 append(list(original = m4), m4_grf_dml),
+                 append(list(original = m5), m5_grf_dml),
+            treatment = 'allstar_x1',
+            tidy = T) %>%
+  write_rds(here('replication', 'biegert_rep.RDS'))
+
+# Final table
+# huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1),
+#                                   list(m2, grf_out2, dml_out2),
+#                                   list(m3, grf_out3, dml_out3),
+#                                   list(m4, grf_out4, dml_out4),
+#                                   list(m5, grf_out5, dml_out5),
+#                                   list(m6, grf_out6, dml_out6)),
+#                              treatment = 'allstar_x1'),
+#                  statistics = NA) %>%
+#   huxtable::insert_row(c('Baseline confounders', 'No', rep('Yes', 5)), after = nrow(.) - 1) %>%
+#   huxtable::insert_row(c('Prior situation + performance', rep('No', 2), rep('Yes', 4)), after = nrow(.) - 1) %>%
+#   huxtable::insert_row(c('Current performance', rep('No', 3), rep('Yes', 3)), after = nrow(.) - 1) %>%
+#   huxtable::insert_row(c('Current situation', rep('No', 4), rep('Yes', 2)), after = nrow(.) - 1) %>%
+#   huxtable::insert_row(c('Cumul. AS + cumul. mediators', rep('No', 5), 'Yes'), after = nrow(.) - 1) %>%
+#   huxtable::set_caption('Replication of Biegert et al. (2023) Table 3: "Average Marginal Effects from Logistic Regression Models of All-Star Nomination"') %>%
+#   write_rds(here('replication', 'biegert_tab.RDS'))
+# 
+# read_rds(here('replication', 'biegert_tab.RDS'))
+
+```
+
+```{r nussio-ind, eval = F}
+nussio_ind <- read_dta(here('replication/nussio_2024', 'Mexico City Individual data.dta')) %>%
+  filter(if_all(c(PARP, lognombre), ~!is.na(.x))) %>%
+  mutate(across(c(PARP, IT1, ED, BASURA), as.numeric),
+         cve_col_num = as.numeric(factor(cve_col))) %>%
+  as_factor()
+
+## Table 2 #### (individual analysis)
+
+m1 <- lm(PARP ~ lognombre + IT1, 
+         nussio_ind) %>%
+  lmtest::coeftest(., vcov = sandwich::vcovCL(., ~cve_col))
+
+m2 <- lm(PARP ~ lognombre + IT1 + 
+           ED + age + female + INGi + unemployed, 
+         nussio_ind) %>%
+  lmtest::coeftest(., vcov = sandwich::vcovCL(., ~cve_col))
+
+m3 <- lm(PARP ~ lognombre + IT1 + 
+           ED + age + female + INGi + unemployed +
+           HER + catholic + nonreligious + working + BASURA + RESS + 
+           PELEA  + PADRES + index_trustgov, 
+         nussio_ind) %>%
+  lmtest::coeftest(., vcov = sandwich::vcovCL(., ~cve_col))
+
+m4 <- lm(PARP ~ lognombre + IT1 + 
+           ED + age + female + INGi + unemployed +
+           HER + catholic + nonreligious + working + BASURA + RESS + 
+           PELEA  + PADRES + index_trustgov +
+           col, nussio_ind) %>%
+  lmtest::coeftest(., vcov = sandwich::vcovCL(., ~cve_col)) 
+  # tidy() %>%
+  # filter(!(str_detect(term, 'col')))
+
+# M1 
+m1_grf_dml <- dml_grf(outcome = 'PARP', 
+        treatment = 'lognombre', 
+        covariates = c('IT1'), 
+        clustervar = 'cve_col_num',
+        dataset = nussio_ind,
+        target = 'all')
+
+# M2 
+m2_grf_dml <- dml_grf(outcome = 'PARP', 
+        treatment = 'lognombre', 
+        covariates = c('IT1', 'ED', 'age', 'female', 'INGi', 'unemployed'), 
+        clustervar = 'cve_col_num',
+        dataset = nussio_ind,
+        target = 'all')
+
+# M3 & M4 (M4 has fixed effects)
+m3_grf_dml <- dml_grf(outcome = 'PARP', 
+        treatment = 'lognombre', 
+        covariates = c('IT1', 'ED', 'age', 'female', 'INGi', 'unemployed',
+                       'HER', 'catholic', 'nonreligious', 'working', 'BASURA', 'RESS', 
+                       'PELEA' , 'PADRES', 'index_trustgov'), 
+        clustervar = 'cve_col_num',
+        dataset = nussio_ind,
+        target = 'all')
+
+m4_grf_dml <- m3_grf_dml
+
+compare_tbl(model_list = list(append(list(original = m1), m1_grf_dml),
+                              append(list(original = m2), m2_grf_dml), 
+                              append(list(original = m3), m3_grf_dml),
+                              append(list(original = m4), m4_grf_dml)),
+            treatment = 'lognombre',
+            tidy = T) %>%
+  write_rds(here('replication', 'nussio_ind_rep.RDS'))
+
+# Final table
+# huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1),
+#                                   list(m2, grf_out2, dml_out2),
+#                                   list(m3, grf_out3, dml_out3),
+#                                   list(m4, grf_out4, dml_out4)),
+#                              treatment = 'lognombre'),
+#                  statistics = NA) %>%
+#   huxtable::insert_row(c('Colonia FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
+#   huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>%
+#   huxtable::set_caption('Replication of Nussio (2024) Table 2: "Individual-Level Analysis: Community Ties and Lynching Participation"') %>%
+#   write_rds(here('replication', 'nussio_ind_tab.RDS'))
+# 
+# read_rds(here('replication', 'nussio_ind_tab.RDS'))
+```
+
+```{r nussio-ag, eval = F}
+## Table 4 #### (aggregate analysis)
+nussio_ag <- read_dta(here('replication/nussio_2024', 
+                           'Mexico Municipality Cross-Sectional Data.dta')) %>%
+  filter(if_all(c(loglynchpermio, organized_lighting_mean), ~!is.na(.x))) %>%
+  mutate(estado_num = as.numeric(estado)) %>%
+  # mutate(across(c(PARP, IT1, ED, BASURA), as.numeric),
+  #        cve_col_num = as.integer(factor(cve_col))) %>%
+  as_factor()
+
+nussio_ag_drop_na <- nussio_ag %>% drop_na(loglynchpermio, organized_lighting_mean,
+                          trust_neighbors_mean, problem_lighting_mean,
+                          c_poptot, area, pconeval_poverty_pobreza_pob, 
+                          coneval_gini_coeficientedegini,
+                          indigenous, c_poptot_norelpop, homirate, robberyrate,
+           victim_household_before_prev_yea, trust_army_mean)
+
+m1 <- lm(loglynchpermio ~ organized_lighting_mean + trust_neighbors_mean + problem_lighting_mean,
+         nussio_ag) %>%
+  lmtest::coeftest(., vcov = sandwich::vcovCL(., ~estado))
+
+m2 <- lm(loglynchpermio ~ organized_lighting_mean + trust_neighbors_mean + problem_lighting_mean +
+           c_poptot + area + pconeval_poverty_pobreza_pob + coneval_gini_coeficientedegini + 
+           indigenous + c_poptot_norelpop + homirate + robberyrate,
+         nussio_ag) %>%
+  lmtest::coeftest(., vcov = sandwich::vcovCL(., ~estado))
+
+m3 <- lm(loglynchpermio ~ organized_lighting_mean + trust_neighbors_mean + problem_lighting_mean +
+           c_poptot + area + pconeval_poverty_pobreza_pob + coneval_gini_coeficientedegini + 
+           indigenous + c_poptot_norelpop + homirate + robberyrate +
+           victim_household_before_prev_yea + trust_army_mean,
+         nussio_ag) %>%
+  lmtest::coeftest(., vcov = sandwich::vcovCL(., ~estado))
+
+m4 <- lm(loglynchpermio ~ organized_lighting_mean + trust_neighbors_mean + problem_lighting_mean +
+           c_poptot + area + pconeval_poverty_pobreza_pob + coneval_gini_coeficientedegini + 
+           indigenous + c_poptot_norelpop + homirate + robberyrate +
+           victim_household_before_prev_yea + trust_army_mean + 
+           estado,
+         nussio_ag)
+
+# M1 
+m1_grf_dml <- dml_grf(outcome = 'loglynchpermio', 
+        treatment = 'organized_lighting_mean', 
+        covariates = c('trust_neighbors_mean', 'problem_lighting_mean'), 
+        clustervar = 'estado_num',
+        dataset = nussio_ag,
+        target = 'all')
+
+# M2
+m2_grf_dml <- dml_grf(outcome = 'loglynchpermio', 
+        treatment = 'organized_lighting_mean', 
+        covariates = c('trust_neighbors_mean', 'problem_lighting_mean',
+                       'c_poptot', 'area', 'pconeval_poverty_pobreza_pob', 'coneval_gini_coeficientedegini', 
+           'indigenous', 'c_poptot_norelpop', 'homirate', 'robberyrate'), 
+        clustervar = 'estado_num',
+        dataset = nussio_ag,
+        target = 'all')
+
+# M3
+m3_grf_dml <- dml_grf(outcome = 'loglynchpermio', 
+        treatment = 'organized_lighting_mean', 
+        covariates = c('trust_neighbors_mean', 'problem_lighting_mean',
+                       'c_poptot', 'area', 'pconeval_poverty_pobreza_pob', 'coneval_gini_coeficientedegini', 
+           'indigenous', 'c_poptot_norelpop', 'homirate', 'robberyrate',
+           'victim_household_before_prev_yea', 'trust_army_mean'), 
+        clustervar = 'estado_num',
+        dataset = nussio_ag,
+        target = 'all')
+
+# M4
+m4_grf_dml <- m3_grf_dml
+
+compare_tbl(model_list = list(append(list(original = m1), m1_grf_dml),
+                              append(list(original = m2), m2_grf_dml), 
+                              append(list(original = m3), m3_grf_dml),
+                              append(list(original = m4), m4_grf_dml)),
+            treatment = 'organized_lighting_mean',
+            tidy = T) %>%
+  write_rds(here('replication', 'nussio_ag_rep.RDS'))
+
+# huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1),
+#                                   list(m2, grf_out2, dml_out2),
+#                                   list(m3, grf_out3, dml_out3),
+#                                   list(m4, grf_out4, dml_out4)),
+#                  treatment = 'organized_lighting_mean'),
+#                  statistics = NA) %>%
+#   huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>%
+#   huxtable::insert_row(c('Estado FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
+#   huxtable::insert_row(c('Estado clustered SE', 'Yes', 'Yes', 'Yes', 'No'), after = nrow(.) - 1) %>%
+#   huxtable::set_caption('Replication of Nussio (2024) Table 4: "Aggregate-Level Analysis: Community Ties and Lynching Rate"') %>%
+#   # huxtable::set_width(1) %>%
+#   # huxtable::set_all_padding(0) %>%
+#   write_rds(here('replication', 'nussio_ag_tab.RDS'))
+# 
+# read_rds(here('replication', 'nussio_ag_tab.RDS'))
+
+# names(grf_out1) <- c('estimate', 'std.error')
+# tidy(m1) %>%
+#   filter(term == 'organized_lighting_mean') %>%
+#   bind_rows(mutate(bind_rows(grf_out1))) %>%
+#   mutate(term = c('original', 'TMLE (GRF)'), p.value = p_val(estimate, std.error)) %>%
+#   huxtable::huxreg()
+
+```
+
+```{r nussio-ne, eval = F}
+nussio_ne <- read_dta(here('replication/nussio_2024', 
+                           'Mexico Municipality Panel Data.dta')) %>%
+  # filter(if_all(c(loglynchpermio, organized_lighting_mean), ~!is.na(.x))) %>%
+  mutate(cve_num = as.numeric(cve),
+         year_num = year,
+         year = as.factor(year),
+         cve = cve,
+         cve = as.factor(cve)) %>%
+  # mutate(across(c(PARP, IT1, ED, BASURA), as.numeric),
+  #        cve_col_num = as.integer(factor(cve_col))) %>%
+  as_factor()
+
+# m1 <- lm(lynch_event ~ eq2017_250X2017 + year + cve, data = nussio_ne) %>%
+#   lmtest::coeftest(., vcov = sandwich::vcovCL(., ~cve))
+
+# m1 <- fixest::feols(lynch_event ~ eq2017_250X2017 | year + cve, 
+#               data = nussio_ne) %>%
+#   summary(vcov = ~cve) %>%
+#   tidy()
+
+m1 <- data.frame(estimate = 0.108, std.error = 0.019)
+m2 <- data.frame(estimate = 0.113, std.error = 0.021)
+m3 <- data.frame(estimate = 0.087, std.error = 0.019)
+m4 <- data.frame(estimate = 0.126, std.error = 0.026)
+m5 <- data.frame(estimate = -0.010, std.error = 0.002)
+m6 <- data.frame(estimate = -0.009, std.error = 0.002)
+
+# M1
+m1_grf_dml <- dml_grf(outcome = 'lynch_event', 
+        treatment = 'eq2017_250X2017', 
+        covariates = c('year_num'), 
+        clustervar = 'cve_num',
+        dataset = nussio_ne,
+        target = 'treated',
+        drop_na_grf = T)
+
+# M2
+m2_grf_dml <- dml_grf(outcome = 'lynch_event', 
+        treatment = 'eq2017_250X2017', 
+        covariates = c('year_num', 'homicidefull', 'robofull', 'secuestrofull', 'inegi_infant_mort'), 
+        clustervar = 'cve_num',
+        dataset = nussio_ne,
+        target = 'treated',
+        drop_na_grf = T)
+
+# M3
+m3_grf_dml <- dml_grf(outcome = 'lynch_event', 
+        treatment = 'eq2017_damageX2017', 
+        covariates = c('year_num'), 
+        clustervar = 'cve_num',
+        dataset = nussio_ne,
+        target = 'treated',
+        drop_na_grf = T)
+
+# M4
+m4_grf_dml <- dml_grf(outcome = 'lynch_event', 
+        treatment = 'eq2017_damageX2017', 
+        covariates = c('year_num', 'homicidefull', 'robofull', 'secuestrofull', 'inegi_infant_mort'), 
+        clustervar = 'cve_num',
+        dataset = nussio_ne,
+        target = 'all',
+        drop_na_grf = T)
+
+# # M5
+# m5_grf_dml <- dml_grf(outcome = 'lynch_event', 
+#         treatment = 'eq2017_dist100X2017', 
+#         covariates = c('year_num'), 
+#         clustervar = 'cve_num',
+#         dataset = nussio_ne,
+#         target = 'all',
+#         drop_na_grf = T)
+# 
+# # M6
+# m6_grf_dml <- dml_grf(outcome = 'lynch_event', 
+#         treatment = 'eq2017_dist100X2017', 
+#         covariates = c('year_num', 'homicidefull', 'robofull', 'secuestrofull', 'inegi_infant_mort'), 
+#         clustervar = 'cve_num',
+#         dataset = nussio_ne,
+#         target = 'all',
+#         drop_na_grf = T)
+
+compare_tbl(model_list = list(
+                 append(list(original = m1), m1_grf_dml),
+                 append(list(original = m2), m2_grf_dml), 
+                 append(list(original = m3), m3_grf_dml),
+                 append(list(original = m4), m4_grf_dml),
+            treatment = NULL,
+            tidy = F) %>%
+  write_rds(here('replication', 'nussio_ne_rep.RDS'))
+
+# Final table
+# huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1),
+#                                   list(m2, grf_out2, dml_out2),
+#                                   list(m3, grf_out3, dml_out3),
+#                                   list(m4, grf_out4, dml_out4),
+#                                   list(m5, grf_out5, dml_out5),
+#                                   list(m6, grf_out6, dml_out6)),
+#                              tidy = F),
+#                  statistics = NA) %>%
+#   huxtable::insert_row(c('Control variables', 'No', 'Yes', 'No', 'Yes', 'No', 'Yes'), 
+#                        after = nrow(.) - 1) %>%
+#   huxtable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"') %>%
+#   write_rds(here('replication', 'nussio_ne_tab.RDS'))
+# 
+# read_rds(here('replication', 'nussio_ne_tab.RDS'))
+```
+
+```{r replications, fig.height = 8, fig.cap = 'Replications of ASR papers using double robust machine learning methods. Bars represent 95-percent asymptotic confidence intervals.'}
+aksoy_list <- readRDS(here('replication', 'aksoy_rep.RDS')) 
+aksoy_list[[1]]$model <- '(1) Base'
+aksoy_list[[2]]$model <- '(2) Covariates'
+aksoy_list[[3]]$model <- '(3) Lagged dependent variable'
+
+biegert_list <- readRDS(here('replication', 'biegert_rep.RDS')) 
+biegert_list[[1]]$model <- '(1) No controls'
+biegert_list[[2]]$model <- '(2) Baseline confounders'
+biegert_list[[3]]$model <- '(3) Prior situation + performance'
+biegert_list[[4]]$model <- '(4) Current performance'
+biegert_list[[5]]$model <- '(5) Current situation'
+
+nussio_ind_list <- readRDS(here('replication', 'nussio_ind_rep.RDS')) 
+nussio_ind_list[[1]]$model <- '(1) Base'
+nussio_ind_list[[2]]$model <- '(2) Some controls'
+nussio_ind_list[[3]]$model <- '(3) All controls'
+nussio_ind_list[[4]]$model <- '(4) Colonia FE'
+
+nussio_ag_list <- readRDS(here('replication', 'nussio_ag_rep.RDS')) 
+nussio_ag_list[[1]]$model <- '(1) Base'
+nussio_ag_list[[2]]$model <- '(2) Some controls'
+nussio_ag_list[[3]]$model <- '(3) All controls'
+nussio_ag_list[[4]]$model <- '(4) Estado FE'
+
+nussio_ne_list <- readRDS(here('replication', 'nussio_ne_rep.RDS')) 
+nussio_ne_list[[1]]$model <- '(1) Within 250 km of earthquake'
+nussio_ne_list[[2]]$model <- '(2) Within 250 km of earthquake, controls'
+nussio_ne_list[[3]]$model <- '(3) Earthquake damage'
+nussio_ne_list[[4]]$model <- '(4) Earthquake damage, controls'
+
+bind_rows(
+  mutate(bind_rows(aksoy_list), paper = 'A. Aksoy et al. (2022)'),
+  mutate(bind_rows(biegert_list), paper = 'B. Biegert et al. (2022)'),
+  mutate(bind_rows(nussio_ind_list), paper = 'C. Nussio et al. (2024) Table 2: Individual'),
+  mutate(bind_rows(nussio_ag_list), paper = 'D. Nussio et al. (2024) Table 4: Aggregate'),
+  mutate(bind_rows(nussio_ne_list), paper = 'E. Nussio et al. (2024) Table 5: Natural Experiment')
+  ) %>%
+  filter(term %in% c('Original', 'AIPW (GRF)', 'DML (SuperLearner)')) %>%
+  mutate(term = factor(term, levels = unique({.$term})),
+         paper = factor(paper, levels = unique({paper})),
+         model = factor(model, levels = rev(unique({.$model})))) %>%
+  ggplot(aes(x = model, y = estimate, color = term, shape = term)) +
+  geom_hline(yintercept = 0, color = 'grey') +
+  geom_pointrange(position = position_dodge(-0.7),
+                  aes(ymin = estimate - 1.96*std.error, ymax = estimate + 1.96*std.error)) + 
+  coord_flip() +
+  facet_wrap(~paper, scales = 'free', ncol = 1) +
+  labs(x = '', y = '') +
+  theme(legend.position = 'bottom')
+```
+
+These simulations suggest that double robust methods with flexible machine learning algorithms may show some gains in bias reduction compared to traditional methods such as linear OLS regression.
+However, do these methods make a difference in practice?
+In this section, I replicate results from three *American Sociological Review* articles using two double robust methods.
+First, I use AIPW in conjunction with generalized random forests (GRF) using the `grf` package [@tibshirani_2024_grf].
+Second, I use a partially linear model for DML with a SuperLearner that, like above, harnesses ensemble learning with GLM, glmnet, and XGBoost, using the `DoubleML` package [@bach_2022_doubleml].^[In the Online Appendix, I present the results of using these packages to estimate the full set of simulations shown above.
+Results are fairly similar to my own R code, though computation time is notably faster.] Note that AIPW with GRF allows for heterogeneous treatment effects, while this version of DML does not.
+I use packages rather than the R code presented above for two reasons.
+First, these packages calculate asymptotic standard errors without the need for bootstrapping, allowing straightforward comparison with the statistical significance of results in the original papers.
+Second, both packages allow clustering of standard errors, which all three papers employ.
+
+Two aspects of these replications deserve further explanation.
+First, it is common on social science to drop observations with missing data for some covariates, a technique called the "complete case method" or "listwise deletion." Two of these papers deal with missing data in this way -- by decreasing the sample size.
+Some machine learning methods, on the other hand, use missing data informatively [@mayer_2020_doubly]; the `grf` package allows covariates (but not the outcome or treatment assignment) to be missing, using missingness itself as a splitting criterion.
+Hence for data with moderate levels of missingness, I allow `grf` to work with the entire dataset.
+For `DoubleML`, I use the same samples as in the original papers, in these cases only observations with complete cases for a given regression model.
+An exception is Table 5 for @nussio_2024_dark, where the number of observations with missing control variables is far larger than the number without missing data; hence I drop incomplete cases for all analyses.
+I describe the exact procedures for handling missingness in the notes for each table of results in the Online Appendix.
+
+The second aspect is fixed effects.
+Fixed effects are commonly used in linear models; beginning with a categorical variable with $k$ group labels, one hot encoding converts this to $k-1$ dichotomous variables, and these are entered into the regression linearly.
+These are meant to account for between-group differences [@firebaugh_2013_fixed; but see @imai_2019_when].
+In machine learning, however, categorical variables cannot be incorporated so easily [@johannemann_2021_sufficient].
+Adding a large number of information-poor dichotomous variables to flexible tree methods like GRF and XGBoost does not have a fixed effects interpretation, since these methods can can interact any variable with any other and apply non-linear transformations.
+Time and other variables with a natural ordering can be entered as a single continuous variable; the model will allow the effect of time to vary nonlinearly, similarly to time fixed effects.
+But categorical variables without a natural ordering, such as individual or group fixed effects, need special treatment.
+Recently, @clarke_2024_double have developed an extension to DML that incorporates group-level fixed effects.
+In the main paper, I do not adjust for individual or group fixed effects in the machine learning replications (even when the original paper's model does), but in the Online Appendix I present two of Clarke and Polselli's approaches to incorporating fixed effects in DML.
+Results change very little from standard DML.
+
+Results of the replications are shown in Figure \@ref(fig:replications), with tables of coefficients and explanatory notes in the Online Appendix.
+For each paper, I replicate the main results.
+I do not replicate models testing mechanisms, interactions, mediators, or placebos.
+
+The first paper I replicate is "Commitment through Sacrifice: How Longer Ramadan Fasting Strengthens Religiosity and Political Islam", by @aksoy_2022_commitment.
+Using the natural variation in daylight from year to year during Ramadan, the authors test the relationship between Ramadan fasting time and the vote share of Islamist political parties in Turkey.
+The original paper found a coefficient of about 7, implying a half-hour increase in fasting time is associated with a 3.5 percentage point increase in Islamist vote share.
+As shown in Figure \@ref(fig:replications) Panel A, coefficients using the double robust methods are noticeably smaller (though not significantly different from the original coefficients).
+In Model 2, which includes covariates, the main coefficient is nonsignificant at the 5-percent level.
+
+The second paper for replication is "They Can’t All Be Stars: The Matthew Effect, Cumulative Status Bias, and Status Persistence in NBA All-Star Elections" [@biegert_2023_they].
+The authors use detailed records on NBA players' performance to study the effect of previous year's All-Star nomination on being re-nominated in the current year.
+Panel B of Figure \@ref(fig:replications) shows the average marginal effects from the authors' original logistic regressions alongside the double robust replications.
+Models 1 and 2 do not control for previous performance and find that a previous year's nomination increases the likelihood of being nominated by 45 to 60 percentage points.
+Model 3 isolates the effect of the previous year's nomination from performance in the previous year; the original paper found a much smaller coefficient once these controls were incorporated, at about 5 percentage points increase, but the double robust methods retain large effect estimate sizes, at 30 and 59 percentage points for AIPW (GRF) and DML (SuperLearner), respectively.
+Models 4 and 5 control for other current factors, and double robust estimates are somewhat smaller than in Model 3 but still much larger than the original paper's estimate.
+
+The third and final paper for replication is "The 'Dark Side' of Community Ties: Collective Action and Lynching in Mexico" [@nussio_2024_dark].
+The author estimates the effect of community ties in Mexico on individual participation in lynching or lynching rates at aggregate levels.
+I present his three main analyses as separate panels.
+In his first analyses, he looks at individual propensity to participate in a lynching, using the log number of names of people a respondent knows in his or her colonia (neighborhood) as the independent variable.
+In models with and without controls, the authors finds that a one-percent increase in names known is associated with about 0.0003 percentage points greater likelihood of participating in a lynching (a coefficient of about 0.03 for the logged variable).
+As shown in Panel C of Figure \@ref(fig:replications), For AIPW (GRF), coefficients and statistical significance are very similar to the original OLS coefficients.
+DML (SuperLearner), however, shows nonsignificant or negative effects.
+
+Panel D of Figure \@ref(fig:replications) replicates Nussio's [-@nussio_2024_dark] second analysis, which aggregates to the municipal level.
+Models estimate the effect of neighborly cooperation -- operationalized by the proportion of respondents who think that most neighbors help each other in problems related to electric lighting -- on the log municipal lynching rate.
+The original estimate was fairly stable across models with controls, at about a one percentage point increase in neighborly cooperation is associated with a two-percent increase the lynching rate [$\exp(2/100) = 1.02$].
+This estimate is fairly stable across estimators, though (as shown in the Online Appendix) this is one case where incorporating fixed effects in the DML models reduces coefficient sizes.
+
+Finally, Panel E of Figure \@ref(fig:replications) replicates Nussio's [-@nussio_2024_dark] natural experiment, where he estimates the effect of the Puebla earthquake on September 19, 2017, on the number of lynching events in a municipality, using panel data from 2000 to 2020.
+The original models found that municipalities within 250 km of the earthquake or that experienced earthquake damage experienced an increase of about 0.1 in the number of lynchings in years after 2017 (the mean yearly lynchings per municipality is 0.034).
+While models for AIPW (GRF) are fairly similar to the original OLS estimates, DML (SuperLearner) estimates are double the original estimates.
+
+These replications show that results from the original OLS or logistic regressions that these papers employed are fairly robust.
+In most cases, effect sign and statistical significance are consistent across the original and double robust estimators.
+Notably, effect sizes for @aksoy_2022_commitment in the double robust models are smaller than the OLS estimates, reaching nonsignificance in one case.
+DML (SuperLearner) estimates for Nussio's [-@nussio_2024_dark] individual analysis change sign and significance, while the AIPW (GRF) estimates are close to the OLS estimates.
+However, the simulation results suggested that the DML (SuperLearner) estimator has higher RMSE than both OLS and AIPW (GRF) (Figure \@ref(fig:dorie-results-rmse)), so perhaps the original results are reliable.^[The Online Appendix shows that the DoubleML package with the SuperLearner has higher bias and RMSE in the simulations than my own R code.] Overall, these replication results highlight the importance of testing the robustness of estimates to different models, while suggesting that double robust, machine learning methods often do produce radically different results from traditional methods.
 
@@
 
-```{r lalonde, fig.height = 8, fig.cap = 'ATE estimates and 95-percent bootstrap standard error confidence intervals for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
-Standard errors shown in parentheses.
-Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
-The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnings in 1974.'}
-# lalonde_means <- read_csv(here('files', 'lalonde_means.csv'))
-
-lalonde_results <- sim_results %>%
-  mutate(set = ifelse(set == 'lalondeCPS-3 74', 'lalonde CPS-3 74', set),
-         set = ifelse(set == 'lalondeCPS-3 original', 'lalonde CPS-3 original', set)) %>%
-  filter(str_detect(set, 'lalonde')) %>%
-  group_by(set, method_estimator, method, estimator) %>%
-  summarize(se = sd(ate),
-            estimate = mean(ate)) %>%
-  ungroup() %>%
-  # left_join(select(lalonde_means, estimate = ate, method, estimator, set)) %>%
-  separate_wider_delim(set, delim = ' ', names = c('set', 'sample', 'include_74')) %>%
-  mutate(sample = str_replace(sample, 'experimental', 'Experimental'),
-         sample = factor(sample, levels = c('Experimental', 'CPS-1', 'CPS-3', 'PSID-1', 'PSID-3')),
-         # estimator = factor(estimator, levels = c('ols_logit', 'ols', 'logit', 'grf', 'superlearner')),
-         # method = factor(method, levels = c('ols', 'psm','ipw', 'g-comp', 'lin', 'aipw', 'tmle', 'dml')),
-         include_74 = ifelse(include_74 == '74', 'With 1974 earnings', 'Original LaLonde sample'),
-         lower = estimate - 1.96*se, 
-         upper = estimate + 1.96*se)
-
-            # lower = quantile(ate, .0275),
-            # upper = quantile(ate, .975))
-            # upper = estimate + 1.96*sd(ate),
-            # lower = estimate - 1.96*sd(ate))
-
-lalonde_results %>%
-  mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
-  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator}))) %>%
-  ggplot(aes(x = sample, y = estimate, color = include_74, shape = include_74)) +
-  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(width = .5), size = .3) +
-  geom_hline(yintercept = 0) +
-  facet_wrap(~method_estimator) +
-  labs(x = '', y = '') +
-  coord_cartesian(ylim = c(-5000, 5000)) +
-  theme(axis.text.x=element_text(angle=90, hjust=0.95,vjust=0.3),
-        legend.position = 'bottom')  +
-  labs(title = 'Results for Lalonde NSW data, with CPS and PSID comparison groups')
-
-ggsave(here('draft/figures', 'lalonde.png'), width = 18,  height = 8, dpi = 1200)
-```
-
-As another evaluation of these methods, I use data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW), as provided by @dehejia_1999_causal.
-Between March 1975 and July 1977, the NSW randomly provided training to disadvantaged workers.
-LaLonde used earnings in 1978 as the outcome of interest; comparing earnings in this year for treated and untreated workers allows an experimental estimate of the effect of the intervention.
-Restricting the sample to men, this study had `r nrow(filter(lalonde_exp, treat == T))` treated and `r nrow(filter(lalonde_exp, treat == F))` control participants.
-Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, and not having a high school degree.
-Following @dehejia_1999_causal, I add a variable indicating whether each respondent's earnings in 1975 was $0 -- i.e., they were unemployed.
-
-LaLonde compared these experimental estimates to control samples drawn from the Panel Study of Income Dynamics (PSID) and Westat's Matched Current Population Survey-Social Security Administration File (CPS).
-The PSID-1 sample (*n* = `r nrow(lalonde_psid1_controls)`) contains all male household heads under 55 who did not classify themselves as retired in 1975, and the PSID-3 sample (*n* = `r nrow(lalonde_psid3_controls)`) further restricts this to men who were not working in the spring of 1976 or 1975.
-The CPS-1 sample (*n* = `r nrow(lalonde_cps1_controls)`) includes all CPS males under 55, and CPS-3 (*n* = `r nrow(lalonde_cps3_controls)`) restricts this two those who were not working in March 1976 whose earnings in 1975 were below the poverty level.
-Restricting these observational samples gets closer to the group eligible for the NSW.
-
-Following @dehejia_1999_causal, I present results for the original samples analyzed by @lalonde_1986_evaluating, but I also include results using a subsample of the experimental group that has 1974 earnings data available (`r nrow(filter(lalonde_exp_74, treat == T))` treated and `r nrow(filter(lalonde_exp_74, treat == F))` control participants) and include this additional covariate, along with an indicator variable for no earnings in 1974.
-
-Results are presented in Figure \@ref(fig:lalonde), with a table in the Appendix (Table 
-\@ref(tab:lalonde-all)).
-Standard errors are based on 100 bootstrap samples.
-We first focus on the original LaLonde dataset, which did not include 1974 earnings.
-The "experimental" estimates provide a baseline for the comparison, suggesting that the program resulted in an earnings gain of about \$800.
-Some methods calculate widely different results for the experimental estimates, highlighting their instability.
-Echoing results from the simulations, methods that include logit models are particularly unstable.
-
-If selection on observables holds, then we should be able to recover experimental estimates from the non-experimental control groups.
-Most of the methods do not perform very well, estimating treatment effects with the wrong sign.
-The exception is in the PSID-3 sample, where 12 of the 17 methods estimate treatment effects with the correct (positive) sign.
-This sample is chosen to be closer to the experimental sample.
-
-Including 1974 earnings data results in much better estimates with the observational control groups.
-OLS, PSM, G-computation (SuperLearner), AIPW (SuperLearner), TMLE (SuperLearner), and DML (OLS/logit) compute fairly stable estimates across the samples.
-On the other hand, the estimates produced by IPW (logit), IPW (GRF), IPW (SuperLearner), the Lin estimator, and DML (GRF) vary widely across samples.
-
-These results highlight the importance of selection on observables holding.
-Without including 1974 earnings as a covariate, it appears that selection on observables does not hold, as most methods provide highly inaccurate estimates with the wrong sign.
-Once 1974 earnings are included, most of the methods provide estimates much closer to the experimental values.
+In the Online Appendix, I provide another evaluation of these methods, using data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW), as provided by @dehejia_1999_causal.
+LaLonde compared experimental estimates to control samples drawn from the Panel Study of Income Dynamics (PSID) and Westat's Matched Current Population Survey-Social Security Administration File (CPS).
+Following @dehejia_1999_causal, I present results for the original samples analyzed by @lalonde_1986_evaluating, but I also include results using a subsample of the experimental group that has 1974 earnings data available.
+
+Results are somewhat difficult to interpret.
+In the original LaLonde data, most methods fail to estimate treatment effects in the observational data with the same sign as the experimental estimate.
+The exception is the PSID-3 sample, which includes only men who were not working in the spring of 1976 or 1975 and is thus more comparable to the individuals were recruited to the NSW study.
+When 1974 earnings are included as a covariate, many of the methods provide estimates across samples that are close to the experimental estimates.
+OLS, PSM, G-computation (SuperLearner), AIPW (SuperLearner), TMLE (SuperLearner), and DML (OLS/logit) appear the most reliable, while IPW (logit), IPW (GRF), IPW (SuperLearner), the Lin estimator, and DML (GRF) prove unstable.
+It is surprising that the Lin estimator provides unstable results in the NSW data, while it is among the lowest-RMSE methods in the simulation study.
+This highlights the complexity of doing causal inference with observational data where ignorability may not hold.
 
@@
 
-Results from the experimental LaLonde data are more difficult to interpret.
-The sample appears much more important than the choice of method.
-In the original LaLonde data, most methods fail to estimate treatment effects in the observational data with the same sign as the experimental estimate.
-The exception is the PSID-3 sample, which includes only men who were not working in the spring of 1976 or 1975 and is thus more comparable to the individuals were recruited to the NSW study.
-When 1974 earnings are included as a covariate, many of the methods provide estimates across samples that are close to the experimental estimates.
-OLS, PSM, G-computation (SuperLearner), AIPW (SuperLearner), TMLE (SuperLearner), and DML (OLS/logit) appear the most reliable, while IPW (logit), IPW (GRF), IPW (SuperLearner), the Lin estimator, and DML (GRF) prove unstable.
-It is surprising that the Lin estimator provides unstable results in the NSW data, while it is among the lowest-RMSE methods in the simulation study.
-This highlights the complexity of doing causal inference with observational data where ignorability may not hold.
+In replications of prominent sociology articles, these methods do sometimes change conclusions.
+In the examples given in this paper, coefficients shift somewhat and sometimes change sign and significance.
+DML with a SuperLearner shows results that differ more dramatically from the OLS or logistic regressions that the authors originally used, while AIPW with GRF produces estimates that are, for the most part, fairly close to the original analyses'.
+This may be related to the higher error shown in the simulations for DML; this method may be somewhat more unstable.
+Overall, these replications suggest that researchers should test the robustness of their results using a variety of different models and estimators.
 
@@
 In conclusion, if researchers want small gains in accuracy, they may opt for AIPW, TMLE, or G-computation with a flexible machine learning algorithm.
-But these methods are computationally costly, taking over two minutes per dataset of 4,802 observations and 52 covariates, while OLS, PSM, and the Lin estimator each take a fraction of a second.
-While double robust methods are useful for social scientists to understand, in most applications, OLS or PSM provide similar results.
+But these methods are computationally costly, taking as long as two minutes per dataset of 4,802 observations and 52 covariates, while OLS, PSM, and the Lin estimator each take a fraction of a second.^[The `grf` and `DoubleML`  packages are able to achieve faster computation time, at under 10 seconds.
+See tables of results in the Online Appendix.] While double robust methods are useful for social scientists to understand, in most applications, OLS or PSM provide similar results.
 However, in certain circumstances these double robust methods may be a better choice.
@@
 
+<!-- \newpage -->
+
+<!-- # (APPENDIX) Appendix {-} -->
+
+<!-- # Appendix -->
+
+<!-- ## DML with heterogeneous treatment effects -->
+
+<!-- $$\psi = \mu_1(\mathbf X_i) - \mu_0(\mathbf X_i) + \frac{D_i(Y_i - \hat \mu_1 (\mathbf X_i))}{\hat \pi (\mathbf X_i)}  -->
+<!-- - \frac{(1-D_i)(Y_i - \hat \mu_0 (\mathbf X_i))}{1-\hat \pi(\mathbf X_i)} - \theta$$ -->
+
 \newpage
@@
 <div id="refs"></div>
-
-\newpage
-
-# (APPENDIX) Appendix {-}
-
-# Appendix
-
-```{r dorie-results-table}
-sim_results %>%
-  # bind_rows(mutate(aipw_df, method = as.factor('aipw (original)'))) %>%
-  filter(set == 'main') %>%
-  group_by(estimator, method) %>%
-  summarize(bias = round(mean(ate - truth, na.rm = T), 3),
-            # var = round(var(ate, na.rm = T), 3),
-            percent_bias = bias/sd(ate, na.rm = T),
-            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
-            mae = median(abs(ate - truth), na.rm = T),
-            comp_time = median(comp_time),
-            fail_count = n() - sum(!is.na(ate))
-              ) %>%
-  select(method, everything()) %>%
-  arrange(method, estimator) %>% 
-  # mutate(bias = as.character(bias),
-  #        rmse = as.character(rmse)) %>%
-  # mutate(across(bias:comp_time, function(x){as.character(round(x, 3))})) %>%
-  kableExtra::kable(booktabs = T, 
-                    digits = 3,
-                    linesep = '',
-                    caption = 'Main datasets: Results of Monte Carlo simulations using the first 20 datasets from Dorie et al.
-(2019), 10 replications each.
-Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is median computation time measured in seconds for each dataset.') %>%
-  kable_styling(latex_options = c("hold_position"))
-```
-
-\newpage
-
-```{r dorie-linear-results}
-sim_results %>%
-  filter(set == 'linear') %>%
-  # bind_rows(mutate(aipw_df, method = as.factor('aipw (original)'))) %>%
-  group_by(estimator, method) %>%
-  summarize(bias = round(mean(ate - truth, na.rm = T), 3),
-            percent_bias = bias/sd(ate, na.rm = T),
-            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
-            mae = median(abs(ate - truth), na.rm = T),
-            comp_time = median(comp_time),
-            fail_count = n() - sum(!is.na(ate))
-              ) %>%
-  select(method, everything()) %>%
-  arrange(method, estimator) %>%
-  # mutate(across(bias:comp_time, function(x){as.character(round(x, 3))})) %>%
-  kableExtra::kable(booktabs = T, 
-                    digits = 3,
-                    linesep = '',
-                    caption = 'Linear datasets: Results of Monte Carlo simulations using the two datasets from Dorie et al.
-(2019), with linear data generating processes, 100 replications each ("linear").
-Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is median computation time measured in seconds for each dataset.') %>%
-  kable_styling(latex_options = c("hold_position"))
-```
-
-\newpage
-
-```{r dorie-results-size}
-sim_results %>%
-  filter(set %in% c('small', 'large')) %>% 
-  group_by(estimator, method, size) %>%
-  summarize(bias = round(mean(ate - truth, na.rm = T), 3),
-            percent_bias = bias/sd(ate, na.rm = T),
-            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
-            mae = median(abs(ate - truth), na.rm = T),
-            comp_time = median(comp_time),
-            fail_count = n() - sum(!is.na(ate))
-              ) %>%
-  select(method, everything()) %>%
-  arrange(method, estimator, size) %>%  
-  # mutate(bias = as.character(bias),
-  #        rmse = as.character(rmse)) %>%
-  # mutate(across(bias:comp_time, function(x){as.character(round(x, 3))})) %>%
-  kableExtra::kable(booktabs = T, 
-                    digits = 3,
-                    linesep = '',
-                    longtable = T,
-                    caption = 'Sample size: Results of Monte Carlo simulations using dataset 7 from Dorie et al.
-(2019) with varying sample sizes, 20 replications each.
-Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is median computation time measured in seconds for each dataset.') %>%
-  kable_styling(latex_options = c("hold_position")) #'repeat_header')) 
-```
-
-\newpage
-
-```{r lalonde-all}
-# lalonde_results <- sim_results %>%
-#   mutate(set = ifelse(set == 'lalondeCPS-3 74', 'lalonde CPS-3 74', set),
-#          set = ifelse(set == 'lalondeCPS-3 original', 'lalonde CPS-3 original', set)) %>%
-#   filter(str_detect(set, 'lalonde')) %>%
-#   separate_wider_delim(set, delim = ' ', names = c('set', 'sample', 'include_74')) %>%
-#   mutate(sample = factor(sample, levels = unique({.$sample})),
-#          include_74 = ifelse(include_74 == 'original', 'No', "Yes"))
-
-lalonde_results %>%
-  mutate(include_74 = ifelse(include_74 == 'With 1974 earnings', 'Yes', 'No')) %>%
-  # group_by(set, sample, include_74, method_estimator) %>%
-  # summarize(estimate = mean(ate),
-  #           se = sd(ate)) %>%
-  # ungroup() %>%
-  mutate(value = paste0(round(estimate), ' (', round(se), ')')) %>%
-  select(`'74 earnings?` = include_74, Sample = sample, Method = method_estimator, value) %>%
-  arrange(Sample) %>%
-  pivot_wider(values_from = value, names_from = Sample) %>%
-  arrange(`'74 earnings?`, Method) %>%
-  mutate(Method = str_replace(Method, 'superlearner', 'superl.')) %>%
-  kableExtra::kable(booktabs = T, 
-                    # digits = 3,
-                    linesep = '',
-                    caption = 'ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
-Bootstrap standard errors shown in parentheses.
-Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
-The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnings in 1974.') %>%
-  kable_styling(latex_options = c("hold_position")) 
-```
-
-```{r lalonde-traditional, eval = F}
-lalonde_results <- sim_results %>%
-  mutate(set = ifelse(set == 'lalondeCPS-3 74', 'lalonde CPS-3 74', set),
-         set = ifelse(set == 'lalondeCPS-3 original', 'lalonde CPS-3 original', set)) %>%
-  filter(str_detect(set, 'lalonde')) %>%
-  separate_wider_delim(set, delim = ' ', names = c('set', 'sample', 'include_74')) %>%
-  mutate(sample = factor(sample, levels = unique({.$sample})),
-         estimator = factor(estimator, levels = c('ols_logit', 'ols', 'logit', 'grf', 'superlearner')),
-         method = factor(method, levels = c('ols', 'psm','ipw', 'g-comp', 'lin', 'aipw', 'tmle', 'dml')))
-
-lalonde_results_df <- lalonde_results %>%
-  group_by(set, sample, include_74, method_estimator) %>%
-  summarize(estimate = mean(ate),
-            se = sd(ate)) %>%
-  ungroup() %>%
-  mutate(value = paste0(round(estimate), ' (', round(se), ')')) %>%
-  select(include_74, sample, method_estimator, value) %>%
-  pivot_wider(values_from = value, names_from = method_estimator) %>%
-  arrange(desc(include_74))
-
-lalonde_results_df %>%
-  select(include_74:`lin`) %>%
-  kableExtra::kable(booktabs = T, 
-                    # digits = 3,
-                    # linesep = '',
-                    caption = 'Traditional methods: ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
-Bootstrap standard errors shown in parentheses.
-Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
-The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnings in 1974.') %>%
-  kable_styling(latex_options = c("hold_position")) 
-```
-
-```{r lalonde-dr, eval = F}
-lalonde_results_df %>%
-  select(include_74, sample, `aipw, ols_logit`:`dml, superlearner`) %>%
-  kableExtra::kable(booktabs = T, 
-                    # digits = 3,
-                    # linesep = '',
-                    caption = 'Double robust methods: ATE estimates for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
-Bootstrap standard errors shown in parentheses.
-Covariates include age, education in years of schooling, earnings in 1975, and dichotomous variables for Black and Hispanic race, married, not having a high school degree, and having no earnings in 1975.
-The "With 1974 earnings" estimates additionally include earnings in 1974 as a covariate, along with an indicator for having no earnings in 1974.') %>%
-  kable_styling(latex_options = c("hold_position")) 
-`

### 2025-04-18 draft/ms-adj-appendix.Rmd
journal submission

@@
   # - \setlength{\headheight}{13.6pt}
-  - \usepackage{fancyhdr}
-  - \pagestyle{fancy}
-  - \lhead{N.I. Hoffmann} 
-  - \rhead{`r format(Sys.time(), '%B %e, %Y')`}
-  - \counterwithin{figure}{section}
-  - \counterwithin{table}{section}
-# - \newcommand{\beginsupplement}{\setcounter{table}{0}  
-# \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} 
-# \renewcommand{\thefigure}{A\arabic{figure}}}
+  # - \usepackage{fancyhdr}
+  # - \pagestyle{fancy}
+  # - \lhead{N.I. Hoffmann} 
+  # - \rhead{`r format(Sys.time(), '%B %e, %Y')`}
+  # - \counterwithin{figure}{section}
+  # - \counterwithin{table}{section}
 
@@
 
-title: "Online Appendix"
+title: "Supplementary Material"
 subtitle: "Double Robust, Flexible Adjustment Methods for Causal Inference: An Overview and an Evaluation"
 
-author:  Nathan I. Hoffmann, Departments of Sociology and Statistics, UCLA
-date: "`r format(Sys.time(), '%B %e, %Y')`"
+# author:  Nathan I. Hoffmann, Departments of Sociology and Statistics, UCLA
+# date: "`r format(Sys.time(), '%B %e, %Y')`"
 
@@
 
-aipw_df <- read_csv(here('files/homemade', 'aipw.csv')) %>%
+aipw_df <- read_csv(here('files', 'aipw.csv')) %>%
   mutate(estimator = method,
@@
 
-aipw_trunc_df <- read_csv(here('files/homemade', 'aipw_trunc.csv')) %>%
+aipw_trunc_df <- read_csv(here('files', 'aipw_trunc.csv')) %>%
   mutate(estimator = method,
@@
 
-tmle_df <- read_csv(here('files/homemade', 'tmle.csv')) %>%
+tmle_df <- read_csv(here('files', 'tmle.csv')) %>%
   # filter(fail == F) %>%
@@
 dml_df <- bind_rows(
-  mutate(read_csv(here('files/homemade', 'dml_ols_logit.csv')), 
+  mutate(read_csv(here('files', 'dml_ols_logit.csv')), 
          estimator = 'ols_logit',
@@
          dataset = row_number()),
-  mutate(read_csv(here('files/homemade', 'dml_grf.csv')), 
+  mutate(read_csv(here('files', 'dml_grf.csv')), 
          estimator = 'grf',
@@
          dataset = row_number()),
-  mutate(read_csv(here('files/homemade', 'dml_superlearner.csv')), 
+  mutate(read_csv(here('files', 'dml_superlearner.csv')), 
          estimator = 'superlearner',
@@
 
-aipw_package_df <- read_csv(here('files/homemade', 'aipw_package.csv')) %>%
+aipw_package_df <- read_csv(here('files', 'aipw_package.csv')) %>%
   mutate(estimator = 'grf (pack.)',
@@
 
-dml_package_df <- read_csv(here('files/homemade', 'dml_package.csv')) %>%
+dml_package_df <- read_csv(here('files', 'dml_package.csv')) %>%
   mutate(estimator = 'superlearner (pack.)',
@@
 
-# (APPENDIX) Appendix {-}
+\renewcommand{\thesection}{S\arabic{section}}
+\renewcommand{\thepage}{S\arabic{page}}
+
+<!-- # (APPENDIX) Appendix {-} -->
 
@@
 
-# LaLonde NSW Data
+<!-- # LaLonde NSW Data -->
 
@@
 
-```{r lalonde, fig.height = 8, fig.cap = 'ATE estimates and 95-percent bootstrap standard error confidence intervals for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
+```{r lalonde, eval = F, fig.height = 8, fig.cap = 'ATE estimates and 95-percent bootstrap standard error confidence intervals for Lalonde NSW data as provided by Dehejia and Wahba (1999), with CPS and PSID comparison groups.
 Standard errors shown in parentheses.
@@
 
-As another evaluation of these methods, I use data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW), as provided by @dehejia_1999_causal.
+<!-- As another evaluation of these methods, I use data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW), as provided by @dehejia_1999_causal.
 Between March 1975 and July 1977, the NSW randomly provided training to disadvantaged workers.
@@
 Following @dehejia_1999_causal, I add a variable indicating whether each respondent's earnings in 1975 was $0 -- i.e., they were unemployed.
-
-LaLonde compared these experimental estimates to control samples drawn from the Panel Study of Income Dynamics (PSID) and Westat's Matched Current Population Survey-Social Security Administration File (CPS).
+-->
+
+<!-- LaLonde compared these experimental estimates to control samples drawn from the Panel Study of Income Dynamics (PSID) and Westat's Matched Current Population Survey-Social Security Administration File (CPS).
 The PSID-1 sample (*n* = `r nrow(lalonde_psid1_controls)`) contains all male household heads under 55 who did not classify themselves as retired in 1975, and the PSID-3 sample (*n* = `r nrow(lalonde_psid3_controls)`) further restricts this to men who were not working in the spring of 1976 or 1975.
@@
 Restricting these observational samples gets closer to the group eligible for the NSW.
-
-Following @dehejia_1999_causal, I present results for the original samples analyzed by @lalonde_1986_evaluating, but I also include results using a subsample of the experimental group that has 1974 earnings data available (`r nrow(filter(lalonde_exp_74, treat == T))` treated and `r nrow(filter(lalonde_exp_74, treat == F))` control participants) and include this additional covariate, along with an indicator variable for no earnings in 1974.
-
-Results are presented in Figure \@ref(fig:lalonde), with a table in the Appendix (Table 
-\@ref(tab:lalonde-all)).
+-->
+
+<!-- Following @dehejia_1999_causal, I present results for the original samples analyzed by @lalonde_1986_evaluating, but I also include results using a subsample of the experimental group that has 1974 earnings data available (`r nrow(filter(lalonde_exp_74, treat == T))` treated and `r nrow(filter(lalonde_exp_74, treat == F))` control participants) and include this additional covariate, along with an indicator variable for no earnings in 1974.
+-->
+
+<!-- Results are presented in Figure \@ref(fig:lalonde), with a table in the Appendix (Table  -->
+<!-- \@ref(tab:lalonde-all)).
 Standard errors are based on 100 bootstrap samples.
@@
 Echoing results from the simulations, methods that include logit models are particularly unstable.
-
-If selection on observables holds, then we should be able to recover experimental estimates from the non-experimental control groups.
+-->
+
+<!-- If selection on observables holds, then we should be able to recover experimental estimates from the non-experimental control groups.
 Most of the methods do not perform very well, estimating treatment effects with the wrong sign.
@@
 This sample is chosen to be closer to the experimental sample.
-
-Including 1974 earnings data results in much better estimates with the observational control groups.
+-->
+
+<!-- Including 1974 earnings data results in much better estimates with the observational control groups.
 OLS, PSM, G-computation (SuperLearner), AIPW (SuperLearner), TMLE (SuperLearner), and DML (OLS/logit) compute fairly stable estimates across the samples.
 On the other hand, the estimates produced by IPW (logit), IPW (GRF), IPW (SuperLearner), the Lin estimator, and DML (GRF) vary widely across samples.
-
-These results highlight the importance of selection on observables holding.
+-->
+
+<!-- These results highlight the importance of selection on observables holding.
 Without including 1974 earnings as a covariate, it appears that selection on observables does not hold, as most methods provide highly inaccurate estimates with the wrong sign.
 Once 1974 earnings are included, most of the methods provide estimates much closer to the experimental values.
-
-\newpage
-
-```{r lalonde-all}
+-->
+
+<!-- \newpage -->
+
+```{r lalonde-all, eval = F}
 # lalonde_results <- sim_results %>%
@@
   kable_styling(latex_options = c("hold_position")) 
-```
-
-\newpage
-
-# Replications with Fixed Effects
-
-The tables below provide estimates from the ASR replications presented in the main text, but with the addition of two other models.
-These implement methods proposed by @clarke_2024_double that incorporate individual or group fixed effects into DML.
-The authors' package, `XTDML`, builds on the `DoubleML` package.
-I use two of their procedures.
-First, correlated random effects (CRE) models explicitly models the correlation between the group-level components in both the treatment and outcome models.
-Second, the authors' "hybrid" model combines CRE with a within-group estimator that partials out group means from all variables, similar to the function of fixed effects in OLS.
-
-```{r rep-aksoy}
-readRDS(here('replication', 'aksoy_rep.RDS')) %>%
-  huxtable::huxreg(statistics = NA,
-                   note = '{stars}.
-Covariates include GDP growth, population, turnout, number of parliamentary seats in province in Model 2 and 3; Models 3 also adjusts for the lagged value of the dependent variable (i.e., one election lagged Islamic votes); cluster robust standard errors are in parentheses.
-The AIPW (GRF) model does not drop incomplete observations.') %>%
-  huxtable::insert_row(c('Covariates', 'No', rep('Yes', 2)), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Lagged dependent variable', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Election year fixed effects', 'Yes', 'Yes', 'Yes'), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Province fixed effects', 'Yes', 'Yes', 'Yes'), after = nrow(.) - 1) %>%
-  huxtable::set_top_border((nrow(.)-4):(nrow(.)-1), value = 0) %>%
-  huxtable::set_top_border((nrow(.)-4), 2:4) %>%
-  huxtable::set_caption('Replication of Aksoy et al.
-(2022) Table 2, models for outcome of Islamic Votes: "Effect of Fasting Hours (Daylength) during Ramadan on Various Outcome Variables Based on Regression Models That Include Fixed Effects for Provinces and Election Years"') %>%
-  huxtable::set_width(.8) %>%
-  huxtable::set_all_padding(0) %>%
-  huxtable::set_latex_float('h!')
-
-# read_rds(here('replication', 'aksoy_tab.RDS')) %>%
-#   huxtable::as_flextable() %>%
-#   flextable::hline(7:8, 1:4, border = officer::fp_border(width = 0)) %>%
-#   flextable::hline(7, 2:4) %>%
-#   flextable::hline(9) %>%
-#   flextable::set_caption('Replication of Aksoy et al.
-(2022) Table 2, models for outcome of Islamic Votes: "Effect of Fasting Hours (Daylength) during Ramadan on Various Outcome Variables Based on Regression Models That Include Fixed Effects for Provinces and Election Years"')
-```
-
-\newpage
-
-```{r rep-biegert}
-readRDS(here('replication', 'biegert_rep.RDS')) %>%
-  huxtable::huxreg(statistics = NA,
-                   note = '{stars}.
-With no control variables, Model 1 could not be estimated using DML with a SuperLearner.
-Model 2 adjusts for year (fixed effects in original model), height (cm), position, age at league entry, being Black, and NBA tenure.
-Model 3 adds controls for the previous year\'s average points per 36 minutes, average assists per 36 minutes, average rebounds per 36 minutes, minutes played, whether the team reached playoffs, the team\'s win percentage, and whether it was a big market team.
-Model 4 adds controls for current average points, average assists, and average rebounds per 36 minutes.
-Model 5 additionally controls for current minutes played, whether the team reaches the playoffs, the team win percentage, and whether it is a big market team.
-Model 6 adds controls for cumulative all-star nominations, average points per 36 minutes, average assists per 36 minutes, average rebounds per 36 minutes, minutes played, team reached playoffs rate, team win percentage, and big market team rate.
-Player clustered standard errors are in parentheses.
-None of the original models include player fixed effects.
-The AIPW (GRF) model does not drop incomplete observations.') %>%
-  huxtable::insert_row(c('Baseline confounders', 'No', rep('Yes', 5)), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Prior situation + performance', rep('No', 2), rep('Yes', 4)), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Current performance', rep('No', 3), rep('Yes', 3)), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Current situation', rep('No', 4), rep('Yes', 2)), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Cumul. AS + cumul. mediators', rep('No', 5), 'Yes'), after = nrow(.) - 1) %>%
-  huxtable::set_top_border((nrow(.)-5):(nrow(.)-1), value = 0) %>%
-  huxtable::set_top_border((nrow(.)-5), 2:7) %>%
-  huxtable::set_caption('Replication of Biegert et al. (2023) Table 3: "Average Marginal Effects from Logistic Regression Models of All-Star Nomination"') %>%
-  huxtable::set_width(1) %>%
-  huxtable::set_all_padding(0) %>%
-  huxtable::set_latex_float('h!')
-
-# read_rds(here('replication', 'biegert_tab.RDS')) %>%
-#   huxtable::as_flextable() %>%
-#   flextable::hline(7:11, 1:7, border = officer::fp_border(width = 0)) %>%
-#   flextable::hline(7, 2:7) %>%
-#   flextable::padding(padding = 0, part = "all") %>% 
-#   flextable::autofit() %>%
-#   flextable::hline(12) %>%
-#   flextable::set_caption('Replication of Biegert et al. (2023) Table 3: "Average Marginal Effects from Logistic Regression Models of All-Star Nomination"')
-```
-
-\newpage
-
-```{r rep-nussio-ind}
-readRDS(here('replication', 'nussio_ind_rep.RDS')) %>%
-  huxtable::huxreg(statistics = NA,
-                   note = "{stars}.
-Models estimate the effect of the log number of names that respondents know in their colonia (neighborhood) on whether they had ever participate in a lynching.
-Model 1 controls for the extent to which people trust others living in their neighborhood.
-Model 2 adds controls for education, age, female, number of light bulbs, and unemployment.
-Model 3 additionally controls for employment, being Catholic or non-religious, whether someone has participated in a fight, whether parents live in the colonia, trust in government, garbage on the street, and residential street block.
-Colonia clustered standard errors are in parentheses.
-Model 4 adds colonia fixed effects.
-The AIPW (GRF) model does not drop incomplete observations.") %>%
-  huxtable::insert_row(c('Colonia FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>%
-  huxtable::set_top_border((nrow(.)-2):(nrow(.)-1), value = 0) %>%
-  huxtable::set_top_border((nrow(.)-2), 2:5) %>%
-  huxtable::set_caption('Replication of Nussio (2024) Table 2: "Individual-Level Analysis: Community Ties and Lynching Participation"') %>%
-  huxtable::set_width(.8) %>%
-  huxtable::set_all_padding(0) %>%
-  huxtable::set_latex_float('h!')
-
-# read_rds(here('replication', 'nussio_ind_tab.RDS')) %>%
-#   huxtable::as_flextable() %>%
-#   flextable::hline(7:8, 1:5, border = officer::fp_border(width = 0)) %>%
-#   flextable::hline(7, 2:5) %>%
-#   flextable::hline(9) %>%
-#   flextable::set_caption('Replication of Nussio (2024) Table 2: "Individual-Level Analysis: Community Ties and Lynching Participation"')
-```
-
-\newpage
-
-```{r rep-nussio-ag}
-readRDS(here('replication', 'nussio_ag_rep.RDS')) %>%
-  huxtable::huxreg(statistics = NA,
-                   note = "{stars}.
-Models estimate the effect of neighborly cooperation -- operationalized by the proportion of respondents who think that most neighbors help each other in problems related to electric lighting -- on the log municipal lynching rate.
-Model 1 adds controls for the proportion of respondents in a municipality that trust their neighbors.
-Model controls for population, area in square kilometers, poverty rate, Gini coefficient, share indigenous people, non-religious population, homicide rate, and robbery rate.
-Model 3 adds controls for household victimization and trust in army.
-Model 4 adds estado (state) fixed effects.
-Municipality clustered standard errors are in paratheses.
-The AIPW (GRF) model does not drop incomplete observations.") %>%
-  huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Estado FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Estado clustered SE', 'Yes', 'Yes', 'Yes', 'No'), after = nrow(.) - 1) %>%
-  huxtable::set_top_border((nrow(.)-3):(nrow(.)-1), value = 0) %>%
-  huxtable::set_top_border((nrow(.)-3), 2:5) %>%
-  huxtable::set_caption('Replication of Nussio (2024) Table 4: "Aggregate-Level Analysis: Community Ties and Lynching Rate"') %>%
-  huxtable::set_width(.8) %>%
-  huxtable::set_all_padding(0) %>%
-  huxtable::set_latex_float('h!')
-
-# read_rds(here('replication', 'nussio_ag_tab.RDS')) %>%
-#   huxtable::as_flextable() %>%
-#   flextable::hline(7:9, 1:5, border = officer::fp_border(width = 0)) %>%
-#   flextable::hline(7, 2:5) %>%
-#   flextable::hline(10) %>%
-#   flextable::set_caption('Replication of Nussio (2024) Table 4: "Aggregate-Level Analysis: Community Ties and Lynching Rate"')
-```
-
-\newpage
-
-```{r rep-nussio-ne}
-readRDS(here('replication', 'nussio_ne_rep.RDS')) %>%
-  huxtable::huxreg(statistics = NA,
-                   note = "{stars}.
-Models estimate the effect of the Puebla earthquake on September 19, 2017, on the number of lynching events.
-Data is a panel of Mexican municipalities from 2000 to 2020.
-Specific independent variables include having an earthquake within 250 km (Models 1 and 2) or having earthquake damage (Models 3 and 4), each interacted with a post-2017 indicator variable.
-Municipality clustered standard errors are in parentheses.
-The original models include two-way fixed effects for year and municipality.
-Model 2 and 4 additionally control for homicides, robberies, kidnappings, and infant mortality.
-Machine learning models control for year.
-All models drop incomplete observations; Models 1, and 3 have 51,597 observations, while Models 2, and 4 have 17,225 observations.
-Due to complications with continuous treatment effects, I do not present the original Models 5 and 6, where the independent variable was distance from the earthquake.") %>%
-  huxtable::insert_row(c('Control variables', 'No', 'Yes', 'No', 'Yes'), 
-                       after = nrow(.) - 1) %>%
-  huxtable::set_top_border((nrow(.)-1):(nrow(.)-1), value = 0) %>%
-  huxtable::set_top_border((nrow(.)-1), 2:5) %>%
-  huxtable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"') %>%
-  huxtable::set_width(.8) %>%
-  huxtable::set_all_padding(0) %>%
-  huxtable::set_latex_float('h!')
-
-# Final table
-# huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1),
-#                                   list(m2, grf_out2, dml_out2),
-#                                   list(m3, grf_out3, dml_out3),
-#                                   list(m4, grf_out4, dml_out4),
-#                                   list(m5, grf_out5, dml_out5),
-#                                   list(m6, grf_out6, dml_out6)),
-#                              tidy = F),
-#                  statistics = NA) %>%
-#   huxtable::insert_row(c('Control variables', 'No', 'Yes', 'No', 'Yes', 'No', 'Yes'), 
-#                        after = nrow(.) - 1) %>%
-#   huxtable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"') %>%
-
-# read_rds(here('replication', 'nussio_ne_tab.RDS')) %>%
-#   huxtable::as_flextable() %>%
-#   flextable::hline(7, 1:7, border = officer::fp_border(width = 0)) %>%
-#   flextable::hline(7, 2:7) %>%
-#   flextable::hline(8) %>%
-#   flextable::padding(padding = 0, part = "all") %>% 
-#   flextable::autofit() %>%
-#   flextable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"')
 ```
@@
 
+# Replications with Fixed Effects
+
+The tables below present estimates from the *ASR* replications discussed in the main text, but with the addition of two other models implementing methods proposed by @clarke_2024_double that incorporate individual or group fixed effects into DML.
+The authors' package, `XTDML`, builds on the `DoubleML` package.
+I use two of their procedures.
+First, correlated random effects (CRE) models explicitly model the correlation between the group-level components in both the treatment and outcome models.
+Second, the authors' "hybrid" model combines CRE with a within-group estimator that partials out group means from all variables, similar to the mechanics of fixed effects in OLS.
+I present results using fixed effects for each model, whether or not the original model uses fixed effects.
+The original models from @aksoy_2022_commitment use fixed effects throughout.
+@biegert_2023_they do not employ fixed effects in any of their original models.
+@nussio_2024_dark uses fixed effects in the fourth model in Tables 2 and 4 and in all models in Table 5.
+
+```{r rep-aksoy}
+readRDS(here('replication', 'aksoy_rep.RDS')) %>%
+  huxtable::huxreg(statistics = NA,
+                   note = '{stars}.
+Covariates include GDP growth, population, turnout, number of parliamentary seats in province in Model 2 and 3; Models 3 also adjusts for the lagged value of the dependent variable (i.e., one election lagged Islamic votes); cluster robust standard errors are in parentheses.
+The AIPW (GRF) model does not drop incomplete observations.') %>%
+  huxtable::insert_row(c('Covariates', 'No', rep('Yes', 2)), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Lagged dependent variable', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Election year fixed effects', 'Yes', 'Yes', 'Yes'), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Province fixed effects', 'Yes', 'Yes', 'Yes'), after = nrow(.) - 1) %>%
+  huxtable::set_top_border((nrow(.)-4):(nrow(.)-1), value = 0) %>%
+  huxtable::set_top_border((nrow(.)-4), 2:4) %>%
+  huxtable::set_caption('Replication of Aksoy et al.
+(2022) Table 2, models for outcome of Islamic Votes: "Effect of Fasting Hours (Daylength) during Ramadan on Various Outcome Variables Based on Regression Models That Include Fixed Effects for Provinces and Election Years"') %>%
+  huxtable::set_width(.8) %>%
+  huxtable::set_all_padding(0) %>%
+  huxtable::set_latex_float('h!')
+
+# read_rds(here('replication', 'aksoy_tab.RDS')) %>%
+#   huxtable::as_flextable() %>%
+#   flextable::hline(7:8, 1:4, border = officer::fp_border(width = 0)) %>%
+#   flextable::hline(7, 2:4) %>%
+#   flextable::hline(9) %>%
+#   flextable::set_caption('Replication of Aksoy et al.
+(2022) Table 2, models for outcome of Islamic Votes: "Effect of Fasting Hours (Daylength) during Ramadan on Various Outcome Variables Based on Regression Models That Include Fixed Effects for Provinces and Election Years"')
+```
+
+\newpage
+
+```{r rep-biegert}
+readRDS(here('replication', 'biegert_rep.RDS')) %>%
+  huxtable::huxreg(statistics = NA,
+                   note = '{stars}.
+With no control variables, Model 1 could not be estimated using DML with a SuperLearner.
+Model 2 adjusts for year (fixed effects in original model), height (cm), position, age at league entry, being Black, and NBA tenure.
+Model 3 adds controls for the previous year\'s average points per 36 minutes, average assists per 36 minutes, average rebounds per 36 minutes, minutes played, whether the team reached playoffs, the team\'s win percentage, and whether it was a big market team.
+Model 4 adds controls for current average points, average assists, and average rebounds per 36 minutes.
+Model 5 additionally controls for current minutes played, whether the team reaches the playoffs, the team win percentage, and whether it is a big market team.
+Player clustered standard errors are in parentheses.
+None of the original models includes player fixed effects.
+The AIPW (GRF) model does not drop incomplete observations.') %>%
+  huxtable::insert_row(c('Baseline confounders', 'No', rep('Yes', 4)), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Prior situation + performance', rep('No', 2), rep('Yes', 3)), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Current performance', rep('No', 3), rep('Yes', 2)), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Current situation', rep('No', 4), rep('Yes', 1)), after = nrow(.) - 1) %>%
+  # huxtable::insert_row(c('Cumul. AS + cumul. mediators', rep('No', 5), 'Yes'), after = nrow(.) - 1) %>%
+  huxtable::set_top_border((nrow(.)-4):(nrow(.)-1), value = 0) %>%
+  huxtable::set_top_border((nrow(.)-4), 2:6) %>%
+  huxtable::set_caption('Replication of Biegert et al. (2023) Table 3: "Average Marginal Effects from Logistic Regression Models of All-Star Nomination"') %>%
+  huxtable::set_width(1) %>%
+  huxtable::set_all_padding(0) %>%
+  huxtable::set_latex_float('h!')
+
+# read_rds(here('replication', 'biegert_tab.RDS')) %>%
+#   huxtable::as_flextable() %>%
+#   flextable::hline(7:11, 1:7, border = officer::fp_border(width = 0)) %>%
+#   flextable::hline(7, 2:7) %>%
+#   flextable::padding(padding = 0, part = "all") %>% 
+#   flextable::autofit() %>%
+#   flextable::hline(12) %>%
+#   flextable::set_caption('Replication of Biegert et al. (2023) Table 3: "Average Marginal Effects from Logistic Regression Models of All-Star Nomination"')
+```
+
+\newpage
+
+```{r rep-nussio-ind}
+readRDS(here('replication', 'nussio_ind_rep.RDS')) %>%
+  huxtable::huxreg(statistics = NA,
+                   note = "{stars}.
+Data come from a representative survey of residents of Mexico City conducted in February 2022.
+Models estimate the effect of the log number of names that respondents know in their colonia (neighborhood) on whether they had ever participate in a lynching.
+Model 1 controls for the extent to which people trust others living in their neighborhood.
+Model 2 adds controls for education, age, female, number of light bulbs, and unemployment.
+Model 3 additionally controls for employment, being Catholic or non-religious, whether someone has participated in a fight, whether parents live in the colonia, trust in government, garbage on the street, and residential street block.
+Colonia clustered standard errors are in parentheses.
+Model 4 adds colonia fixed effects.
+The AIPW (GRF) model does not drop incomplete observations.") %>%
+  huxtable::insert_row(c('Colonia FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>%
+  huxtable::set_top_border((nrow(.)-2):(nrow(.)-1), value = 0) %>%
+  huxtable::set_top_border((nrow(.)-2), 2:5) %>%
+  huxtable::set_caption('Replication of Nussio (2024) Table 2: "Individual-Level Analysis: Community Ties and Lynching Participation"') %>%
+  huxtable::set_width(.8) %>%
+  huxtable::set_all_padding(0) %>%
+  huxtable::set_latex_float('h!')
+
+# read_rds(here('replication', 'nussio_ind_tab.RDS')) %>%
+#   huxtable::as_flextable() %>%
+#   flextable::hline(7:8, 1:5, border = officer::fp_border(width = 0)) %>%
+#   flextable::hline(7, 2:5) %>%
+#   flextable::hline(9) %>%
+#   flextable::set_caption('Replication of Nussio (2024) Table 2: "Individual-Level Analysis: Community Ties and Lynching Participation"')
+```
+
+\newpage
+
+```{r rep-nussio-ag}
+readRDS(here('replication', 'nussio_ag_rep.RDS')) %>%
+  huxtable::huxreg(statistics = NA,
+                   note = "{stars}.
+Models estimate the effect of neighborly cooperation -- operationalized by the proportion of respondents who think that most neighbors help each other in problems related to electric lighting -- on the log municipal lynching rate.
+Model 1 adds controls for the proportion of respondents in a municipality that trust their neighbors.
+Model controls for population, area in square kilometers, poverty rate, Gini coefficient, share indigenous people, non-religious population, homicide rate, and robbery rate.
+Model 3 adds controls for household victimization and trust in army.
+Model 4 adds estado (state) fixed effects.
+Municipality clustered standard errors are in paratheses.
+The AIPW (GRF) model does not drop incomplete observations.") %>%
+  huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Estado FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
+  huxtable::insert_row(c('Estado clustered SE', 'Yes', 'Yes', 'Yes', 'No'), after = nrow(.) - 1) %>%
+  huxtable::set_top_border((nrow(.)-3):(nrow(.)-1), value = 0) %>%
+  huxtable::set_top_border((nrow(.)-3), 2:5) %>%
+  huxtable::set_caption('Replication of Nussio (2024) Table 4: "Aggregate-Level Analysis: Community Ties and Lynching Rate"') %>%
+  huxtable::set_width(.8) %>%
+  huxtable::set_all_padding(0) %>%
+  huxtable::set_latex_float('h!')
+
+# read_rds(here('replication', 'nussio_ag_tab.RDS')) %>%
+#   huxtable::as_flextable() %>%
+#   flextable::hline(7:9, 1:5, border = officer::fp_border(width = 0)) %>%
+#   flextable::hline(7, 2:5) %>%
+#   flextable::hline(10) %>%
+#   flextable::set_caption('Replication of Nussio (2024) Table 4: "Aggregate-Level Analysis: Community Ties and Lynching Rate"')
+```
+
+\newpage
+
+```{r rep-nussio-ne}
+readRDS(here('replication', 'nussio_ne_rep.RDS')) %>%
+  huxtable::huxreg(statistics = NA,
+                   note = "{stars}.
+Models estimate the effect of the Puebla earthquake on September 19, 2017, on the number of lynching events.
+Data is a panel of Mexican municipalities from 2000 to 2020.
+Specific independent variables include having an earthquake within 250 km (Models 1 and 2) or having earthquake damage (Models 3 and 4), each interacted with a post-2017 indicator variable.
+Municipality clustered standard errors are in parentheses.
+The original models include two-way fixed effects for year and municipality.
+Model 2 and 4 additionally control for homicides, robberies, kidnappings, and infant mortality.
+Machine learning models control for year.
+All models drop incomplete observations; Models 1, and 3 have 51,597 observations, while Models 2, and 4 have 17,225 observations.
+Due to complications with continuous treatment effects, I do not present the original Models 5 and 6, where the independent variable was distance from the earthquake.") %>%
+  huxtable::insert_row(c('Control variables', 'No', 'Yes', 'No', 'Yes'), 
+                       after = nrow(.) - 1) %>%
+  huxtable::set_top_border((nrow(.)-1):(nrow(.)-1), value = 0) %>%
+  huxtable::set_top_border((nrow(.)-1), 2:5) %>%
+  huxtable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"') %>%
+  huxtable::set_width(.8) %>%
+  huxtable::set_all_padding(0) %>%
+  huxtable::set_latex_float('h!')
+
+# Final table
+# huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1),
+#                                   list(m2, grf_out2, dml_out2),
+#                                   list(m3, grf_out3, dml_out3),
+#                                   list(m4, grf_out4, dml_out4),
+#                                   list(m5, grf_out5, dml_out5),
+#                                   list(m6, grf_out6, dml_out6)),
+#                              tidy = F),
+#                  statistics = NA) %>%
+#   huxtable::insert_row(c('Control variables', 'No', 'Yes', 'No', 'Yes', 'No', 'Yes'), 
+#                        after = nrow(.) - 1) %>%
+#   huxtable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"') %>%
+
+# read_rds(here('replication', 'nussio_ne_tab.RDS')) %>%
+#   huxtable::as_flextable() %>%
+#   flextable::hline(7, 1:7, border = officer::fp_border(width = 0)) %>%
+#   flextable::hline(7, 2:7) %>%
+#   flextable::hline(8) %>%
+#   flextable::padding(padding = 0, part = "all") %>% 
+#   flextable::autofit() %>%
+#   flextable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"')
+```
+
+\newpage
+
 # References

### 2025-04-18 draft/ms-adj-draft.Rmd
journal submission

@@
     #latex_engine: xelatex
+
 always_allow_html: true
@@
   # - \setlength{\headheight}{13.6pt}
-  - \usepackage{fancyhdr}
-  - \pagestyle{fancy}
-  - \lhead{N.I. Hoffmann} 
-  - \rhead{`r format(Sys.time(), '%B %e, %Y')`}
+  # - \usepackage{fancyhdr}
+  # - \pagestyle{fancy}
+  # - \lhead{N.I. Hoffmann} 
+  # - \rhead{`r format(Sys.time(), '%B %e, %Y')`}
 # - \newcommand{\beginsupplement}{\setcounter{table}{0}  
@@
 
-author:  Nathan I. Hoffmann, Departments of Sociology and Statistics, UCLA
-date: "`r format(Sys.time(), '%B %e, %Y')`"
-
-thanks: "I deeply thank  my committee -- Chad Hazlett, Onyebuchi A.
-Arah, Jennie E.
-Brand -- for their extensive suggestions and advice on previous drafts.
-I would also like to thank the members of UCLA's Practical Causal Inference Lab, UCLA's Social Inequality Data Science Lab, participants of the 2023 American Sociological Association's Annual Meeting, and participants of the 2024 All-UC Demography Conference for their feedback on previous versions of this paper."
+# author:  Nathan I. Hoffmann, Departments of Sociology and Statistics, UCLA
+# date: "`r format(Sys.time(), '%B %e, %Y')`"
+
+# thanks: "I deeply thank my Statistics MS committee -- Chad Hazlett, Jennie E.
+Brand, and Onyebuchi A.
+Arah -- for their extensive suggestions and advice on previous drafts.
+I would also like to thank the members of UCLA's Practical Causal Inference Lab, UCLA's Inequality Data Science Lab, and participants at the 2023 American Sociological Association's Annual Meeting, at the 2024 PolMeth Summer Meeting, and at the 2024 All-UC Demography Conference for their feedback on previous versions of this paper."
 
 abstract: "Double robust methods for flexible covariate adjustment in causal inference have proliferated in recent years.
-Despite their apparent advantages, these methods remain underutilized by social scientists.
+Despite their apparent advantages, these methods are rarely used by social scientists.
 It is also unclear whether these methods actually outperform more traditional methods in finite samples.
-This paper has two aims: It is a guide to some of the latest methods in double robust, flexible covariate adjustment for causal inference, and it compares these methods to more traditional statistical methods and flexible \"single robust\" methods.
-It does this by using both simulated data where the treatment effect estimate is known, and then using comparisons of experimental and observational data from the National Supported Work Demonstration.
-Methods covered include Augmented Inverse Probability Weighting (AIPW), Targeted Maximum Likelihood Estimation (TMLE), and Double/Debiased Machine Learning (DML).
+This paper has two aims: It is a guide to some of the latest methods in double robust, flexible covariate adjustment using machine learning, and it compares these methods to more traditional statistical methods and flexible \"single robust\" methods.
+It does this by using both simulated data where the treatment effect estimate is known, and then by replicating some prominent articles in sociology that use simpler methods.
+Double robust methods covered include Augmented Inverse Probability Weighting (AIPW), Targeted Maximum Likelihood Estimation (TMLE), and Double/Debiased Machine Learning (DML).
 Results suggest that some of these methods do outperform traditional methods in a wide range of simulations, but only slightly.
-In particular, the top performers are TMLE and AIPW in conjunction with flexible machine learning algorithms.
-But G-computation with the same flexible machine learning algorithms obtains almost identical results, and simple regression methods are nearly comparable in bias and are much more computationally efficient."
+In particular, the top performers are TMLE and AIPW in conjunction with flexible machine learning estimators.
+But G-computation with the same flexible estimators obtains almost identical results, and simple regression methods have only slightly higher bias and are much more computationally efficient.
+In the article replications, the application of double robust methods substantively changes some, but not all, of the results, highlighting the importance of comparing performance from multiple estimators."
 
@@
 # 
-# write_csv(aipw_df, here('files/homemade', 'aipw.csv'))
+# write_csv(aipw_df, here('files', 'aipw.csv'))
 # 
@@
 # 
-# write_csv(aipw_trunc_df, here('files/homemade', 'aipw_trunc.csv'))
+# write_csv(aipw_trunc_df, here('files', 'aipw_trunc.csv'))
 # 
@@
 # 
-# write_csv(tmle_df, here('files/homemade', 'tmle.csv'))
+# write_csv(tmle_df, here('files', 'tmle.csv'))
 # 
@@
 # 
-# write_csv(dml_ols_logit_df, here('files/homemade', 'dml_ols_logit.csv'))
+# write_csv(dml_ols_logit_df, here('files', 'dml_ols_logit.csv'))
 # 
@@
 # 
-# write_csv(dml_grf_df, here('files/homemade', 'dml_grf.csv'))
+# write_csv(dml_grf_df, here('files', 'dml_grf.csv'))
 # 
@@
 # 
-# write_csv(dml_superlearner_df, here('files/homemade', 'dml_superlearner.csv'))
+# write_csv(dml_superlearner_df, here('files', 'dml_superlearner.csv'))
 
@@
 # 
-# saveRDS(ols_logit_pred_combined, here('files/homemade', 'ols_logit_pred.RDS'))
-# saveRDS(grf_pred_combined, here('files/homemade', 'grf_pred.RDS'))
-# saveRDS(superlearner_pred_combined, here('files/homemade', 'superlearner_pred.RDS'))
+# saveRDS(ols_logit_pred_combined, here('files', 'ols_logit_pred.RDS'))
+# saveRDS(grf_pred_combined, here('files', 'grf_pred.RDS'))
+# saveRDS(superlearner_pred_combined, here('files', 'superlearner_pred.RDS'))
 
@@
 #   bind_rows(read_csv(here('files_lalonde/homemade', 'aipw.csv'))) %>%
-#   write_csv(here('files/homemade', 'aipw.csv'))
+#   write_csv(here('files', 'aipw.csv'))
 # 
@@
 #   bind_rows(read_csv(here('files_lalonde/homemade', 'aipw_trunc.csv'))) %>%
-#   write_csv(here('files/homemade', 'aipw_trunc.csv'))
+#   write_csv(here('files', 'aipw_trunc.csv'))
 # 
@@
 #   bind_rows(read_csv(here('files_lalonde/homemade', 'tmle.csv'))) %>%
-#   write_csv(here('files/homemade', 'tmle.csv'))
+#   write_csv(here('files', 'tmle.csv'))
 # 
@@
 #   bind_rows(read_csv(here('files_lalonde/homemade', 'dml_ols_logit.csv'))) %>%
-#   write_csv(here('files/homemade', 'dml_ols_logit.csv'))
+#   write_csv(here('files', 'dml_ols_logit.csv'))
 # 
@@
 #   bind_rows(read_csv(here('files_lalonde/homemade', 'dml_grf.csv'))) %>%
-#   write_csv(here('files/homemade', 'dml_grf.csv'))
+#   write_csv(here('files', 'dml_grf.csv'))
 # 
@@
 #   bind_rows(read_csv(here('files_lalonde/homemade', 'dml_superlearner.csv'))) %>%
-#   write_csv(here('files/homemade', 'dml_superlearner.csv'))
+#   write_csv(here('files', 'dml_superlearner.csv'))
 # 
@@
 #   append(readRDS(here('files_lalonde/homemade', 'ols_logit_pred.RDS'))) %>%
-#   saveRDS(here('files/homemade', 'ols_logit_pred.RDS'))
+#   saveRDS(here('files', 'ols_logit_pred.RDS'))
 # 
@@
 #   append(readRDS(here('files_lalonde/homemade', 'grf_pred.RDS'))) %>%
-#   saveRDS(here('files/homemade', 'grf_pred.RDS'))
+#   saveRDS(here('files', 'grf_pred.RDS'))
 # 
@@
 #   append(readRDS(here('files_lalonde/homemade', 'superlearner_pred.RDS'))) %>%
-#   saveRDS(here('files/homemade', 'superlearner_pred.RDS'))
+#   saveRDS(here('files', 'superlearner_pred.RDS'))
 
@@
 ```
+
+**Keywords**: causal inference, machine learning, double robust, computational methods, simulations
 
@@
 
-A number methods unifying these two developments have proliferated.
-These double robust methods for flexible covariate adjustment use machine learning methods to adapatively model the data generating processes at play.
+Methods unifying these two developments have proliferated.
+These double robust methods for flexible covariate adjustment use machine learning methods to adapatively model the data generating processes.
 These models purportedly overcome the shortcomings of both traditional statistical methods and machine learning methods.
@@
 They can also accommodate large numbers of covariates and produce easily interpretable treatment effect estimates.
-Despite their apparent advantages, these methods remain rarely utilized by social scientists.
+Despite their apparent advantages, these methods remain rarely used by social scientists.
 Part of the barrier has been lack of familiarity with these methods.
@@
 They are tested on simulations from @dorie_2019_automated, which cover a range of data-generating processes where ignorability holds -- i.e., there are no unmeasured confounders.
-In the Online Appendix, I also estimate experimental and observational effects from the National Support for Work Demonstration (NSW) originally analyzed by @lalonde_1986_evaluating.
-In these evaluations, double robust methods are compared to "single robust" methods (i.e., ones with one nuisance model).
+In the simulations, double robust methods are compared to "single robust" methods (i.e., ones with one nuisance model).
 These include traditional or simpler statistical methods commonly used by social scientists: ordinary least squares (OLS) regression, matching on propensity scores estimated from logistic regression (PSM), and inverse probability weighting (IPW).
 They are also compared to two more flexible methods that may overcome the misspecification issues that double robust methods aim to overcome: G-computation and the Lin estimator [@lin_2013_agnostic].
-Lastly, I use two of the double robust methods to replicate analyses from three recent *American Sociological Review* (ASR) papers that use OLS or logistic regression to estimate causal effects.
+Lastly, I use two of the double robust methods to replicate analyses from three recent *American Sociological Review* (*ASR*) papers that use OLS or logistic regression to estimate causal effects.
 
 Results from simulations where ignorability holds show that some double robust methods outperform traditional statistical methods, but only slightly.
-AIPW and TMLE perform the best, at least when used in conjunction with flexible machine learning algorithms, while DML does slightly worse than traditional methods.
+AIPW and TMLE perform the best, at least when used in conjunction with flexible machine learning algorithms, while DML (in its partially linear form) does slightly worse than traditional methods.
 G-computation with flexible machine learning performs as well as the lowest-error double robust methods.
@@
 With its still relatively low error and much faster computation time, OLS remains a sensible choice as an estimator, and the Lin estimator -- which is as quick as standard OLS regression -- performs only slightly worse than the best double robust methods.
-
-Results from the NSW study highlight the importance of ignorability.
-When observational samples are not comparable to the experimental sample, or when important covariates are not included, all methods -- double robust or traditional -- fail to recover experimental estimates.
-When appropriate covariates are included, most methods perform well.
-
 In the *ASR* replications, double robust methods provide similar coefficients for most, but not all, of the analyses.
-In some cases, significance is lost, and in a minority of cases the coefficient sign changes.
+In some cases, statistical significance is lost, and in a minority of cases the coefficient sign changes.
 These replications highlight the importance of testing the robustness of quantitative results by comparing multiple methods and estimators.
-<!-- Exceptions include IPW, DML, and the Lin estimator (surprising given the simulation results), whose estimates tend to be less stable across samples.   -->
+
+The next section reviews literature on and motivation for double robust methods.
+This is followed by an introduction of notation and assumptions, while the following section gives an overview of the double robust methods covered in this paper.
+I next present results of the simulations and replications, then conclude.
+In the Appendix, I provide simple R code to implement the three double robust methods.
+
+<!-- Section \@ref(motivation) reviews literature on and motivation for double robust methods.
+Section \@ref(conceptual-overview) introduces notation and assumptions, while Section \@ref(overview-of-techniques) gives an overview of the double robust methods covered in this paper, along with example R code.
+Sections \@ref(simulations) and \@ref(replications) present results of the simulations and replications, respectively, and Section \@ref(conclusion) concludes.
+-->
 
@@
 @dorie_2019_automated compare estimations from a number of different flexible methods, but these do not include AIPW or DML.
-@chatton_2020_gcomputation compare four methods -- G-computation, IPW, full matching, and TMLE -- but authors only consider one double robust method, and their focus is on omitted variable bias rather than determining which method is the most useful.
-@cousineau_2022_estimating evaluates the performance of optimization-based methods for causal inference, but these do not include the double robust methods covered in the current paper.
+@chatton_2020_gcomputation compare four methods -- G-computation, IPW, full matching, and TMLE -- but the authors only consider one double robust method, and their focus is on omitted variable bias rather than determining which method is the most useful.
+@cousineau_2022_estimating evaluate the performance of optimization-based methods for causal inference, but these do not include the double robust methods covered in the current paper.
 @knaus_2022_double reviews DML-based methods in an econometrics setting but does not compare them to traditional statistical methods for covariate adjustment.
 
-An evaluation of multiple double robust methods that compares them to traditional statistical methods as well as flexible "single robust" methods is needed to understand just how practically useful these methods are for a social science audience.
+An evaluation of multiple double robust methods that compares them to traditional statistical methods as well as flexible "single robust" methods is needed to understand just how practically useful these methods are for social scientists.
 This paper does this as well as provides a gentle introduction to these methods.
@@
 @robins_1994_estimation and @rotnitzky_1998_semiparametric developed augmented orthogonal inverse probability-weighted (AIPW) estimators in missing data models.
-Drawing on the fact that causal inference is fundamentally a missing data problem, @scharfstein_1999_adjusting showed that AIPW was double robust and extended to causal inference.
+Drawing on the fact that causal inference is fundamentally a missing data problem, @scharfstein_1999_adjusting showed that AIPW was double robust and extended it to causal inference.
 
@@
 The form of double robust methods is similar to residual-on-residual regression, which dates back to the Frisch-Waugh-Lowell (FWL) theorem [@frisch_1933_partial; @lovell_1963_seasonal]:
-$$\beta_D = \frac{\text{Cov}(\tilde Y_i, \tilde D_i)}{\text{Var}(\tilde D_i)}$$
+$$\beta_D = \frac{\text{Cov}(\tilde Y_i, \tilde D_i)}{\text{Var}(\tilde D_i)},$$
 where $\tilde D_i$ is the residual part of $D_i$ after regressing it on $X_i$, and $\tilde Y_i$ is the residual part of $Y_i$ after regressing it on $X_i$.
@@
 Today, double robust methods abound [e.g.
-@arkhangelsky_2021_doublerobust; @ratkovic_2023_relaxing; @sloczynski_2018_general; @dukes_2022_doubly; @kennedy_2023_semiparametric].
-Although double robust methods exist for instrumental variables [@okui_2012_doubly; @wang_2018_bounded], difference-in-differences [@santanna_2020_doubly], longitudinal data [@yu_2006_double; @tran_2019_double], and other causal applications, this paper focuses on three of the most popular and foundational methods for covariate adjustment in a cross-sectional setting.
+@arkhangelsky_2021_doublerobust; @ratkovic_2023_relaxing; @sloczynski_2018_general; @dukes_2022_doubly; @kennedy_2023_semiparametric; @xu_2024_relaxed].
+Although double robust methods exist for instrumental variables [@okui_2012_doubly; @wang_2018_bounded], difference-in-differences [@santanna_2020_doubly], longitudinal data [@yu_2006_double; @tran_2019_double; @clarke_2024_double], and other causal applications, this paper focuses on three of the most popular and foundational methods for covariate adjustment in a cross-sectional setting.
 
@@
 First, naive application of these methods can result in overfitting, with predictive accuracy maximized in sample but treatment effect estimation being biased.
-When regularization is used to correct for overfitting, "regularization bias" can result.
-Furthermore, results of these machine learning methods can be difficult to interpret without further processing.
-Machine learning methods have often been developed with a focus on prediction rather than on producing treatment effect point estimates.
+When regularization is used to correct for overfitting, the resulting estimates can be biased, a phenomenon called "regularization bias." Furthermore, machine learning methods have often been developed with a focus on prediction rather than on producing treatment effect point estimates, so results can be difficult to interpret without further processing.
 
@@
 \begin{equation}
-\mu_d(X_i) = E(Y_i \mid D_i = d, X_i)
+\mu_d( \mathbf X_i) = E(Y_i \mid D_i = d, \mathbf X_i)
 (\#eq:outcome)
@@
 \begin{equation}
-\pi(X_i) = E(D_i \mid X_i),
+\pi(\mathbf X_i) = E(D_i \mid \mathbf X_i),
 (\#eq:exposure)
 \end{equation}
-where $\mu_d(\cdot)$ is a model of the outcome, $D_i = d_i \in \{0, 1\}$ is the treatment assignment (where 0 is control and 1 is treated), $X_i$ is a vector of covariates for unit $i = 1, \ldots, N$, $Y_i$ is the outcome, and $\pi(\cdot)$ is a model of the exposure.
-The covariates included in $X_i$ can be different for the two models.
+where $\mu_d(\cdot)$ is a model of the outcome, $D_i = d_i \in \{0, 1\}$ is the treatment assignment (where 0 is control and 1 is treated), $\mathbf X_i$ is a vector of covariates for unit $i = 1, \ldots, N$, $Y_i$ is the outcome, and $\pi(\cdot)$ is a model of the exposure.
+The covariates included in $\mathbf X_i$ can be different for the two models.
+
+Examples of outcomes $Y$ that we might be interested in include earnings, mortality, or degree completion, while possible treatments $D$ might be a job training program, a medication or medical procedure, or an education grant.
+We attempt to model both of these by controlling for predictors $\mathbf X$ -- such as socioeconomic status, employment history, medical conditions, or race -- that might influence selection into treatment as well as the value of the outcome.
+When variables in $\mathbf X$ influence both treatment and outcome, they are called confounders, and adjusting for these is essential for unbiased estimation.
+When the set of observable variables $\mathbf X$ includes all confounders, we say that "ignorability" or "selection on observables" holds.
+In the simulations below, we assume ignorability.
 
@@
 4.
-Positivity/overlap: $0 < \Pr(D = 1 \mid X=x) < 1$ for all values of $X$, i.e.
+Positivity/overlap: $0 < \Pr(D = 1 \mid \mathbf X= \mathbf x) < 1$ for all values of $X$, i.e.
 there is non-zero probability of receiving treatment or control for every combination of covariates in the data.
@@
 
-6. Conditional ignorability: $\{Y_{i0}, Y_{i1}\} \perp \!\!\! \perp D_i \mid X_i$, i.e. there are no unmeasured confounders.
+6. Conditional ignorability: $\{Y_{i0}, Y_{i1}\} \perp \!\!\! \perp D_i \mid \mathbf X_i$, i.e. there are no unmeasured confounders.
 
@@
 
-This section provides some intuition for the mathematical theory behind each method and contains R code to simply implement these methods.
+This section provides some intuition for the mathematical theory behind each method.
+In the Appendix, I provide R code to simply implement these methods.
 This is the code used to evaluate these methods later in this paper, and it represents basic implementations of these methods.
@@
 These packages have many flexible options, such as accounting for complex survey design, targeting estimands besides the ATE, and integrating with a variety of estimation techniques.
-In the Online Appendix, Table \@ref(tab:packages) suggests packages for each method.
+
+<!-- In the Supplementary Material, Table \@ref(tab:packages) suggests packages for each method.   -->
 
@@
 To remedy this, the predicted probabilities of treatment are often truncated, setting extremely small or large weights to some less extreme value [as in the `AIPW` R package, @zhong_2021_aipw].
-
-Below is R code to implement AIPW with truncation of extreme weights.
-As with all of the double robust methods reviewed here, we begin with predicted values (such as from a machine learning algorithm) for the outcome for treated units `mu1_pred` and untreated units `mu0_pred` as well as predicted values for treatment assignment probability `pi_pred`.
-We also have `d`, the vector of actual treatment assignments, and `y`, the observed outcome values.
-
-```{r aipw-demo, eval = F, echo = T}
-require(tidyverse)
-
-aipw_calc <- function(mu1_pred, mu0_pred, pi_pred, d, y){
-  n <- length(mu1_pred)
-
-  # Truncate extreme values of the weights
-  pi_pred <- case_when(
-    pi_pred < .01 ~ .01,
-    pi_pred > .99 ~ .99,
-    T ~ pi_pred)
-
-  # Calculate the predicted outcome value for treated units
-  y1_pred <- (d*(y-mu1_pred))/pi_pred + mu1_pred
-  # Calculate the predicted outcome value for untreated units
-  y0_pred <- ((1-d)*(y-mu0_pred))/(1-pi_pred) + mu0_pred
-
-  # Calculate the ATE
-  ate <- (1/n)*(sum(y1_pred)) - (1/n)*sum(y0_pred)
-
-  return(ate)
-}
-```
 
@@
 Finally, we estimate the parameter of interest -- in this case, the ATE:
-$$\hat \tau_{TMLE} = \frac{1}{n} \sum_{i=1}^n [\hat \mu_1^*(\mathbf x_i) - \hat \mu_0^*(\mathbf x_i)]$$
-
-Here is R code to implement TMLE, again with predicted outcome values `mu1_pred` and `mu0_pred` and predicted probability of treatment `pi_pred`.
-Since the outcome is bounded and continuous, it is transformed to fall between 0 and 1 via $\tilde Y_{i} = [Y_i - \min(Y)]/[(\max(Y)-\min(Y)]$.
-```{r tmle-demo, eval = F, echo = T}
-# Functions for normalization and de-normalization
-normalize <- function(x, y){(x - min(y)) / (max(y) - min(y))}
-denormalize <- function(x, y){x * (max(y) - min(y))}
-
-tmle_calc <- function(mu1_pred, mu0_pred, pi_pred, d, y){
-  # Normalize the outcome variable
-  mu1_pred <- normalize(mu1_pred, y)
-  mu0_pred <- normalize(mu0_pred, y)
-  y_tilde <- normalize(y, y))
-
-  n <- length(y)
-
-  # Calculate clever covariates
-  H0 = (1-d)/(1-pi_pred)
-  H1 = d/pi_pred
-
-  # Estimate fluctuation parameter through maximum likelihood estimation
-  epsilon <- glm(y_tilde ~ -1 + H0 + H1 + offset(qlogis((d==1)*mu1_pred + (d==0)*mu0_pred)),
-                 family = binomial(link = 'logit')) %>%
-    tidy() %>%
-    pull(estimate)
-
-  # Targeted estimates of the potential outcomes
-  target_0 <- plogis(qlogis(mu0_pred + epsilon[1]*H0))
-  target_1 <- plogis(qlogis(mu1_pred + epsilon[2]*H1))
-
-  # Estimate ATE
-  ATE <- mean(target_1 - target_0)
-  return(denormalize(ATE, y))
-}
-```
+$$\hat \tau_{TMLE} = \frac{1}{n} \sum_{i=1}^n [\hat \mu_1^*(\mathbf x_i) - \hat \mu_0^*(\mathbf x_i)].$$
 
@@
 $$\hat \tau_{DML} = \frac{\hat \tau (I^c, I) + \hat \tau (I, I^c)}{2}.$$
-
-R code to implement DML is shown below.
-Since DML involves sample splitting, this code is a little different from the above examples.
-We start with observed outcome values `y`, treatment assignment `d`, and covariate matrix `x`.
-First, a pre-processing function `dml_pre()` randomly splits the sample, outputting $I$ and $I^c$ sets of each of these variables.
-The second step predicts outcome values and treatment probabilities for each half of the sample, using models fit to the other half.
-In the code chunk here, generalized random forests from the `grf` package are used to predict these, but any prediction algorithm can be used.
-Finally, a post-prediction function `dml_post()` performs the residual-on-residual regression for each half of the sample and finds the average of the two estimates to produce an ATE estimate.
-```{r dml-demo, eval = F, echo = T}
-# Pre-processing: sample splitting
-dml_pre <- function(y, d, x, seed = 1758){
-  set.seed(seed)
-
-  n <- length(y)
-  n_2 <- round(n/2)
-
-  # Split the sample
-  random_vec <- sample(1:n, n, replace = F)
-  I <- random_vec[1:n_2]
-  I_c <- random_vec[(n_2+1):n]
-
-  return(list(
-    y_I = y[I],
-    d_I = d[I],
-    x_I = x[I,],
-    y_I_c = y[I_c],
-    d_I_c = d[I_c],
-    x_I_c = x[I_c,]
-    ))
-}
-
-# Predictor function: in this case, generalized random forests
-grf_dml <- function(y_I, d_I, x_I, y_I_c, d_I_c, x_I_c){
-  # Train on the I_c sample, predict on the I sample
-  mu_mod1 <- grf::regression_forest(X = x_I_c, Y = y_I_c, tune.parameters = "all")
-  mu_pred1 <- predict(mu_mod1, newdata = x_I)$predictions
-
-  pi_mod1 <- grf::regression_forest(X = x_I_c, Y = d_I_c, tune.parameters = "all")
-  pi_pred1 <- predict(pi_mod1, newdata = x_I)$predictions
-
-  # Train on the I sample, predict on the I_c sample
-  mu_mod2 <- grf::regression_forest(X = x_I, Y = y_I, tune.parameters = "all")
-  mu_pred2 <- predict(mu_mod2, newdata = x_I_c)$predictions
-
-  pi_mod2 <- grf::regression_forest(X = x_I, Y = d_I, tune.parameters = "all")
-  pi_pred2 <- predict(pi_mod2, newdata = x_I_c)$predictions
-
-  return(list(
-    mu_pred1 = mu_pred1,
-    pi_pred1 = pi_pred1,
-    mu_pred2 = mu_pred2,
-    pi_pred2 = pi_pred2
-  ))
-}
-
-# Implement DML: takes outputs from pre_dml() and grf_dml()
-dml_post <- function(y_I, d_I, x_I, y_I_c, d_I_c, x_I_c,
-                     mu_pred1, pi_pred1, mu_pred2, pi_pred2){
-
-  # Residual-on-residual regression for each sample separately
-  v1 <- d_I - pi_pred1
-  delta1 <- (sum(v1 * d_I))^-1 * sum(v1 * (y_I - pi_pred1))
-
-  v2 <- d_I_c - pi_pred2
-  delta2 <- (sum(v2 * d_I_c))^-1 * sum(v2 * (y_I_c - pi_pred2))
-
-  # Average estimates from each sample
-  ate <- (delta1 + delta2)/2
-
-  return(ate)
-}
-
-dml_pre_out <- dml_pre(y = y, d = d, x = x)
-grf_dml_out <- do.call(grf_dml, dml_pre_out)
-dml_post_out <- do.call(dml_post, append(dml_pre_out, grf_dml_out))
-```
 
@@
 
-# Evaluation Strategy
-
-These double robust methods have many similarities.
-How do the results they give compare?
-This section tests the performance of each in practice using two strategies.
-First, results are compared using simulated data from a causal inference competition [@dorie_2019_automated].
-The true treatment effect is known and all potential confounders are observed, so these simulations allow assessment of bias and related quantities.
-Second, these methods are applied to data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW).
-The NSW randomly provided training to disadvantaged workers, allowing an experimental estimate of the effect of the intervention, and data assembled by @dehejia_1999_causal compares these experimental estimates to observational ones.
-
-```{r methods-overview}
-
-read_csv(here('files/methods.csv')) %>%
-  huxtable::hux() %>%
-  huxtable::theme_article() %>%
-  huxtable::set_width(1) %>%
-  # huxtable::set_all_padding(0) %>%
-  # huxtable::set_latex_float('h!') %>%
-  huxtable::set_caption('Double and single robust methods used for evaluation. The super learner estimator is an ensemble learning method relying on GLM, glmnet, and XGBoost.')
-
-  # pander::pander(split.cell = 15, split.table = Inf, 
-  #                justify = 'left',
-  #                caption = 'Double and single robust methods used for evaluation',
-  #                label = 'methods-overview') 
-  # kable(booktabs = T, linesep = '', caption = 'Double and single robust methods used for evaluation') %>%
-  # kable_styling(latex_options = c("hold_position"))
-
-```
-
-The three double robust methods are compared to two sets of traditional or "single robust" methods used as benchmarks (see Table \@ref(tab:methods-overview) for an overview of all methods used).
-By "single robust," I mean methods that are not robust to any misspecification.
-First are one-model methods.
-The most classic method considered -- linear regression -- models only the response surface.
-It is estimated using ordinary least squares regression ("OLS"), entering each variable separately without any interactions or higher-order terms.
-Two other one-model methods model only the treatment assignment mechanism.
-In propensity score matching (PSM), propensity scores are estimated from logistic regression with each variable entered separately and without any higher order terms, then matched using the `MatchIt` package.
-Finally, stabilized inverse probability weights [IPW, @austin_2015_moving, p.
-3663] are used for weighted OLS regression.
-These IPWs are estimated using propensity scores estimated by each of the three under-the-hood estimation techniques described below; extreme propensity scores are truncated so that they range from 0.01 to 0.99.
-
-The second set of single robust methods are two-model methods, which estimate separate models for treated and untreated units.
-In theory these could solve the misspecification problem that double robust methods are meant to solve, but they could still suffer from overfitting.
-G-computation [@robins_1986_new; @snowden_2011_implementation] uses some estimation technique to predict outcomes under treatment and control for each unit in the dataset.
-The ATE estimate is the difference in the average prediction under treatment and the average prediction under control.
-The second two-model method is the Lin estimator [@lin_2013_agnostic].
-This method aims to solve issues with the bias induced by OLS regression in a randomization framework by interacting the treatment indicator with mean-centered covariates.
-@hazlett_2024_understanding show that this method is equivalent to estimating two separate OLS regression models for the treated and control units.
-
-Because many of these methods allow the user to choose the underlying estimation method, results compare three estimators The first estimator uses a logistic regression for the exposure model and an OLS regression for the outcome model.
-Second is generalized random forests [GRF, @athey_2019_generalized] using the `grf` R package, with separate models for exposure and outcome.
-The final estimator is the SuperLearner (as promoted by the makers of TMLE) using the `SuperLearner` package [@polley_2023_superlearner], again with separate models for exposure and outcome.
-GLM, glmnet [a weighted average of lasso and ridge regression, @friedman_2021_package], and XGBoost with a maximum tree depth of 4 [@chen_2016_xgboost] are the models considered for the SuperLearner.
-These three estimation techniques are used for each of the three double robust methods and for IPW.
-GRF and SuperLearner are also used for G-computation (OLS predictions with G-computation return identical results to OLS regression coefficient estimates).
-
-For the simulations, results compare only point estimates from these methods.
-For evaluation of the experimental LaLonde data, I use bootstrapping with 100 samples to obtain standard errors and confidence intervals.
-I use the code shown above for AIPW, TMLE, and DML, and I also compare results for two ready-made double robust packages.
-These include `grf` [@tibshirani_2024_grf], which implements AIPW with generalized random forests, and `DoubleML` [@bach_2024_doubleml], which I use to implement a partially linear DML model with a SuperLearner using GLM, glmnet, and XGBoost.
+# Simulations
 
@@
 }
-saveRDS(ols_logit_pred_list, here('files/homemade', 'ols_logit_pred.RDS'))
+saveRDS(ols_logit_pred_list, here('files', 'ols_logit_pred.RDS'))
 
@@
 }
-saveRDS(grf_pred_list, here('files/homemade', 'grf_pred.RDS'))
+saveRDS(grf_pred_list, here('files', 'grf_pred.RDS'))
 
@@
 }
-saveRDS(superlearner_pred_list, here('files/homemade', 'superlearner_pred.RDS'))
+saveRDS(superlearner_pred_list, here('files', 'superlearner_pred.RDS'))
 
@@
 ```{r ipw, eval = F}
-ols_logit_pred_list2 <- readRDS(here('files/homemade', 'ols_logit_pred.RDS'))
-grf_pred_list2 <- readRDS(here('files/homemade', 'grf_pred.RDS'))
-superlearner_pred_list2 <- readRDS(here('files/homemade', 'superlearner_pred.RDS'))
+ols_logit_pred_list2 <- readRDS(here('files', 'ols_logit_pred.RDS'))
+grf_pred_list2 <- readRDS(here('files', 'grf_pred.RDS'))
+superlearner_pred_list2 <- readRDS(here('files', 'superlearner_pred.RDS'))
 
@@
 ```{r g-comp, eval = F}
-grf_pred_list2 <- readRDS(here('files/homemade', 'grf_pred.RDS'))
-superlearner_pred_list2 <- readRDS(here('files/homemade', 'superlearner_pred.RDS'))
+grf_pred_list2 <- readRDS(here('files', 'grf_pred.RDS'))
+superlearner_pred_list2 <- readRDS(here('files', 'superlearner_pred.RDS'))
 
@@
 
-write_csv(bind_rows(aipw_out_list), here('files/homemade', 'aipw.csv'))
+write_csv(bind_rows(aipw_out_list), here('files', 'aipw.csv'))
 
@@
 
-write_csv(bind_rows(aipw_out_list), here('files/homemade', 'aipw_trunc.csv'))
+write_csv(bind_rows(aipw_out_list), here('files', 'aipw_trunc.csv'))
 
@@
 
-write_csv(bind_rows(tmle_out_list), here('files/homemade', 'tmle.csv'))
+write_csv(bind_rows(tmle_out_list), here('files', 'tmle.csv'))
 
@@
 write_csv(bind_rows(ols_logit_dml_list), 
-          here('files/homemade', 'dml_ols_logit.csv'))
+          here('files', 'dml_ols_logit.csv'))
 
@@
 # write_csv(bind_rows(ols_logit_dml_list), 
-#           here('files/homemade', 'dml_ols_logit_trunc.csv'))
+#           here('files', 'dml_ols_logit_trunc.csv'))
 
@@
 write_csv(bind_rows(grf_dml_list), 
-          here('files/homemade', 'dml_grf.csv'))
+          here('files', 'dml_grf.csv'))
 
@@
 write_csv(bind_rows(superlearner_dml_list), 
-          here('files/homemade', 'dml_superlearner.csv'))
+          here('files', 'dml_superlearner.csv'))
 
@@
 
-  grf_model <- grf::causal_forest(X = x, Y = y, W = d)                        
-  grf_out <- grf::average_treatment_effect(grf_model, target.sample = 'all', method = 'AIPW', seed = 123)
+  grf_model <- grf::causal_forest(X = x, Y = y, W = d, seed = 123)                        
+  grf_out <- grf::average_treatment_effect(grf_model, target.sample = 'all', method = 'AIPW')
 
@@
     write_csv(bind_rows(aipw_package_list), 
-          here('files/homemade', 'aipw_package.csv'))
+          here('files', 'aipw_package.csv'))
   }
@@
 write_csv(bind_rows(aipw_package_list), 
-          here('files/homemade', 'aipw_package.csv'))
+          here('files', 'aipw_package.csv'))
 
@@
     write_csv(bind_rows(dml_package_list), 
-          here('files/homemade', 'dml_package.csv'))
+          here('files', 'dml_package.csv'))
   }
@@
 write_csv(bind_rows(dml_package_list), 
-          here('files/homemade', 'dml_package.csv'))
-
-```
-
-# Simluations with Dorie et al. (2019) Data
+          here('files', 'dml_package.csv'))
+
+```
 
@@
 
-# aipw_package_df <- read_csv(here('files/homemade', 'aipw_package.csv')) %>%
+# aipw_package_df <- read_csv(here('files', 'aipw_package.csv')) %>%
 #   mutate(estimator = 'grf (package)',
@@
 # 
-# dml_package_df <- read_csv(here('files/homemade', 'dml_package.csv')) %>%
+# dml_package_df <- read_csv(here('files', 'dml_package.csv')) %>%
 #   mutate(estimator = 'superlearner (package)',
@@
 
+These double robust methods have many similarities.
+How do the results they give compare?
+This section tests the performance of each in practice, comparing point estimates on simulated data from a causal inference competition.
+The true treatment effect is known and all potential confounders are observed, so these simulations allow assessment of bias and related quantities.
+
 In 2016, the Atlantic Causal Inference Conference hosted a competition for causal inference methods that adjust on observables.
-@dorie_2019_automated published the results of this competition, along with the data used in the competition.
+@dorie_2019_automated published the results of this competition, along with the data used.
 Below, I test double robust methods on the 20 data sets used for the "do-it-yourself" part of the competition.
@@
 
+## Evaluation Strategy
+
+Implementing the R code presented in the Appendix, I compare the three double robust methods to two sets of traditional or "single robust" methods used as benchmarks (see Table \@ref(tab:methods-overview) for an overview of all methods used).
+By "single robust," I mean methods that are not robust to any misspecification.
+First are one-model methods.
+The most classic method considered -- linear regression -- models only the response surface.
+It is estimated using ordinary least squares regression ("OLS"), entering each variable separately without any interactions or higher-order terms.
+Two other one-model methods model only the treatment assignment mechanism.
+In propensity score matching (PSM), propensity scores are estimated from logistic regression with each variable entered separately and without any higher order terms, then matched using the `MatchIt` package.
+Finally, stabilized inverse probability weights [IPW, @austin_2015_moving, p.
+3663] are used for weighted OLS regression.
+These IPWs are estimated using propensity scores estimated by each of the three under-the-hood estimation techniques described below; extreme propensity scores are truncated so that they range from 0.01 to 0.99.
+
+The second set of single robust methods are two-model methods, which estimate separate models for treated and untreated units.
+In theory these could solve the misspecification problem that double robust methods are meant to solve, but they could still suffer from regularization bias.
+G-computation [@robins_1986_new; @snowden_2011_implementation] uses some estimation technique to predict outcomes under treatment and control for each unit in the dataset.
+The ATE estimate is the difference in the average prediction under treatment and the average prediction under control.
+The second two-model method is the Lin estimator [@lin_2013_agnostic].
+This method aims to solve issues with the bias induced by OLS regression in a randomization framework by interacting the treatment indicator with mean-centered covariates.
+@hazlett_2024_understanding show that this method is equivalent to estimating two separate OLS regression models for the treated and control units.
+
+Because many of these methods allow the user to choose the underlying estimation method, results compare three estimators.
+The first estimator uses a logistic regression for the exposure model and an OLS regression for the outcome model.
+Second is generalized random forests [GRF, @athey_2019_generalized] using the `grf` R package, with separate models for exposure and outcome.
+The final estimator is the SuperLearner (as promoted by the makers of TMLE) using the `SuperLearner` package [@polley_2023_superlearner], again with separate models for exposure and outcome.
+GLM, glmnet [a weighted average of lasso and ridge regression, @friedman_2021_package], and XGBoost with a maximum tree depth of 4 [@chen_2016_xgboost] are the models considered for the SuperLearner.
+These three estimation techniques are used for each of the three double robust methods and for IPW.
+GRF and SuperLearner are also used for G-computation (OLS predictions with G-computation return identical results to OLS regression).
+
+```{r methods-overview}
+
+read_csv(here('files/methods.csv')) %>%
+  huxtable::hux() %>%
+  huxtable::theme_article() %>%
+  huxtable::set_width(1) %>%
+  # huxtable::set_all_padding(0) %>%
+  # huxtable::set_latex_float('h!') %>%
+  huxtable::set_caption('Double and single robust methods used for evaluation. The super learner estimator is an ensemble learning method relying on GLM, glmnet, and XGBoost.')
+
+  # pander::pander(split.cell = 15, split.table = Inf, 
+  #                justify = 'left',
+  #                caption = 'Double and single robust methods used for evaluation',
+  #                label = 'methods-overview') 
+  # kable(booktabs = T, linesep = '', caption = 'Double and single robust methods used for evaluation') %>%
+  # kable_styling(latex_options = c("hold_position"))
+
+```
+
 ## Main results
@@
 I then calculate bias, percent bias (the estimator's bias as a percentage of its standard error), root mean squared error (rmse), and median absolute error (mae).
-I also present the number of datasets for which the method fails and the median computation time for each data set, in seconds.^[Simulations were run on a 2020 MacBook Pro laptop computer with a 2 GHz Quad-Core Intel Core i5 Processor and 16 GB of memory.] In the main text I present average bias and RMSE, while the Online Appendix contains tables with full results.
+I also present the number of datasets for which the method fails and the median computation time for each data set, in seconds.^[Simulations were run on a 2020 MacBook Pro laptop computer with a 2 GHz Quad-Core Intel Core i5 Processor and 16 GB of memory.] In the main text I present average bias and RMSE, while the Supplementary Material contains tables with full results.
 
@@
 While double robust methods achieve the lowest RMSE, the choice of underlying estimator appears more important than the choice of method.
-AIPW and TMLE both do well with a flexible underlying estimator, while DML does worse than OLS.
+AIPW and TMLE both do well with a flexible underlying estimator, while DML (in its partially linear form) does worse than OLS.
 Of the estimators considered, the SuperLearner (which considers GLM, glmnet, and XGBoost models) appears to be best for the double robust methods, with GRF following closely.
@@
 
-Figure \@ref(fig:dorie-linear-bias) shows the bias from each simulation for each method (table in the Online Appendix).
+Figure \@ref(fig:dorie-linear-bias) shows the bias from each simulation for each method (table in the Supplementary Material).
 Similarly to the full set of simulations, bias is fairly low for most methods.
@@
 
-Table \@ref(tab:dorie-size) presents the four methods with the lowest RMSE for each sample size (the Online Appendix presents a table with full results).
+Table \@ref(tab:dorie-size) presents the four methods with the lowest RMSE for each sample size (the Supplementary Material presents a table with full results).
 Again, AIPW, TMLE, and G-computation methods that incorporate the SuperLearner or GRF dominate.
@@
 
+These simulations suggest that double robust methods with flexible machine learning algorithms may show some gains in bias reduction compared to traditional methods such as linear OLS regression.
+However, do these methods make a difference in practice?
+In this section, I replicate results from recent *American Sociological Review* articles using two double robust methods.
+I chose three papers that meet the following criteria: the authors were trying to estimate a causal effect, they used OLS or logistic regression, and they  posted replication code and data.
+
+The first paper I replicate is "Commitment through Sacrifice: How Longer Ramadan Fasting Strengthens Religiosity and Political Islam," by @aksoy_2022_commitment.
+Using the natural variation in daylight from year to year during Ramadan, the authors test the relationship between Ramadan fasting time and the vote share of Islamist political parties in Turkey.
+The second paper is "They Can’t All Be Stars: The Matthew Effect, Cumulative Status Bias, and Status Persistence in NBA All-Star Elections" [@biegert_2023_they].
+The authors use detailed records on NBA players' performance to study the effect of the previous year's All-Star nomination on being re-nominated in the current year.
+Lastly, I replicate "The 'Dark Side' of Community Ties: Collective Action and Lynching in Mexico" [@nussio_2024_dark].
+The author estimates the effect of community ties in Mexico on individual participation in lynching or lynching rates at aggregate levels.
+
+## Evaluation Strategy
+
+I replicate these papers using two double robust methods with machine learning.
+First, I use AIPW in conjunction with generalized random forests (GRF) using the `grf` package [@tibshirani_2024_grf].
+Second, I use a partially linear model for DML with a SuperLearner that, like above, harnesses ensemble learning with GLM, glmnet, and XGBoost, using the `DoubleML` package [@bach_2022_doubleml].^[In the Supplementary Material, I present the results of using these packages to estimate the full set of simulations shown above.
+Results are fairly similar to my own R code, though computation time is notably faster.] Note that AIPW with GRF allows for heterogeneous treatment effects, while this version of DML does not.
+I use packages rather than my own R code for two reasons.
+First, these packages calculate asymptotic standard errors without the need for bootstrapping, allowing straightforward comparison with the statistical significance of results in the original papers.
+Second, both packages allow clustering of standard errors, which all three papers employ.
+
+Two aspects of these replications deserve further explanation.
+First, it is common in social science to drop observations with missing data for some covariates, a technique called the "complete case method" or "listwise deletion." Two of these papers deal with missing data in this way -- by decreasing the sample size.
+Some machine learning methods, on the other hand, use missing data informatively [@mayer_2020_doubly]; the `grf` package allows covariates (but not the outcome or treatment assignment) to be missing, using missingness itself as a splitting criterion in growing trees.
+Hence for data with moderate levels of missingness, I allow `grf` to work with the entire dataset.
+For `DoubleML`, I use the same samples as in the original papers -- in these cases only observations with complete cases for a given regression model.
+An exception is Table 5 for @nussio_2024_dark, where the number of observations with missing control variables is far larger than the number without missing data; hence I drop incomplete cases for all analyses.
+I describe the exact procedures for handling missingness in the notes for each table of results in the Supplementary Material.
+
+The second aspect is fixed effects.
+Fixed effects are commonly used in linear models; beginning with a categorical variable with $k$ group labels, one hot encoding converts this to $k-1$ dichotomous variables, and these are entered into the regression linearly.
+These are meant to account for between-group differences [@firebaugh_2013_fixed].
+In the papers replicated here, @aksoy_2022_commitment use these types of fixed effects in all models, @biegert_2023_they use no fixed effects, and @nussio_2024_dark uses fixed effects in some models (details are in the table notes in the Supplementary Material).
+In many machine learning methods, categorical variables cannot be easily incorporated [@johannemann_2021_sufficient].
+Adding a large number of information-poor dichotomous variables to flexible tree methods like GRF and XGBoost does not have a fixed effects interpretation, since these methods can can interact any variable with any other and apply non-linear transformations.
+In cases where a researcher would want to use fixed effects for time and other variables with a natural ordering, these can be entered as a single continuous variable, whose effect the model will allow to vary nonlinearly.
+But categorical variables without a natural ordering -- such as individual or group fixed effects -- need special treatment.
+Recently, @clarke_2024_double have developed an extension to DML that incorporates group-level fixed effects.
+In the main paper, I do not adjust for individual or group fixed effects in the machine learning replications (even when the original paper's model does), but in the Supplementary Material I present two of Clarke and Polselli's approaches to incorporating fixed effects in DML.
+Results change very little from standard DML.
+
+## Results
+
 ```{r replications, fig.height = 8, fig.cap = 'Replications of ASR papers using double robust machine learning methods. Bars represent 95-percent asymptotic confidence intervals.'}
@@
 nussio_ind_list[[3]]$model <- '(3) All controls'
-nussio_ind_list[[4]]$model <- '(4) Colonia FE'
+nussio_ind_list[[4]]$model <- '(4) Geographical FE'
 
@@
 nussio_ag_list[[3]]$model <- '(3) All controls'
-nussio_ag_list[[4]]$model <- '(4) Estado FE'
+nussio_ag_list[[4]]$model <- '(4) Geographical FE'
 
@@
 
-These simulations suggest that double robust methods with flexible machine learning algorithms may show some gains in bias reduction compared to traditional methods such as linear OLS regression.
-However, do these methods make a difference in practice?
-In this section, I replicate results from three *American Sociological Review* articles using two double robust methods.
-First, I use AIPW in conjunction with generalized random forests (GRF) using the `grf` package [@tibshirani_2024_grf].
-Second, I use a partially linear model for DML with a SuperLearner that, like above, harnesses ensemble learning with GLM, glmnet, and XGBoost, using the `DoubleML` package [@bach_2022_doubleml].^[In the Online Appendix, I present the results of using these packages to estimate the full set of simulations shown above.
-Results are fairly similar to my own R code, though computation time is notably faster.] Note that AIPW with GRF allows for heterogeneous treatment effects, while this version of DML does not.
-I use packages rather than the R code presented above for two reasons.
-First, these packages calculate asymptotic standard errors without the need for bootstrapping, allowing straightforward comparison with the statistical significance of results in the original papers.
-Second, both packages allow clustering of standard errors, which all three papers employ.
-
-Two aspects of these replications deserve further explanation.
-First, it is common on social science to drop observations with missing data for some covariates, a technique called the "complete case method" or "listwise deletion." Two of these papers deal with missing data in this way -- by decreasing the sample size.
-Some machine learning methods, on the other hand, use missing data informatively [@mayer_2020_doubly]; the `grf` package allows covariates (but not the outcome or treatment assignment) to be missing, using missingness itself as a splitting criterion.
-Hence for data with moderate levels of missingness, I allow `grf` to work with the entire dataset.
-For `DoubleML`, I use the same samples as in the original papers, in these cases only observations with complete cases for a given regression model.
-An exception is Table 5 for @nussio_2024_dark, where the number of observations with missing control variables is far larger than the number without missing data; hence I drop incomplete cases for all analyses.
-I describe the exact procedures for handling missingness in the notes for each table of results in the Online Appendix.
-
-The second aspect is fixed effects.
-Fixed effects are commonly used in linear models; beginning with a categorical variable with $k$ group labels, one hot encoding converts this to $k-1$ dichotomous variables, and these are entered into the regression linearly.
-These are meant to account for between-group differences [@firebaugh_2013_fixed; but see @imai_2019_when].
-In machine learning, however, categorical variables cannot be incorporated so easily [@johannemann_2021_sufficient].
-Adding a large number of information-poor dichotomous variables to flexible tree methods like GRF and XGBoost does not have a fixed effects interpretation, since these methods can can interact any variable with any other and apply non-linear transformations.
-Time and other variables with a natural ordering can be entered as a single continuous variable; the model will allow the effect of time to vary nonlinearly, similarly to time fixed effects.
-But categorical variables without a natural ordering, such as individual or group fixed effects, need special treatment.
-Recently, @clarke_2024_double have developed an extension to DML that incorporates group-level fixed effects.
-In the main paper, I do not adjust for individual or group fixed effects in the machine learning replications (even when the original paper's model does), but in the Online Appendix I present two of Clarke and Polselli's approaches to incorporating fixed effects in DML.
-Results change very little from standard DML.
-
-Results of the replications are shown in Figure \@ref(fig:replications), with tables of coefficients and explanatory notes in the Online Appendix.
+Results of the replications are shown in Figure \@ref(fig:replications), with tables of coefficients and explanatory notes in the Supplementary Material.
 For each paper, I replicate the main results.
@@
 
-The first paper I replicate is "Commitment through Sacrifice: How Longer Ramadan Fasting Strengthens Religiosity and Political Islam", by @aksoy_2022_commitment.
-Using the natural variation in daylight from year to year during Ramadan, the authors test the relationship between Ramadan fasting time and the vote share of Islamist political parties in Turkey.
-The original paper found a coefficient of about 7, implying a half-hour increase in fasting time is associated with a 3.5 percentage point increase in Islamist vote share.
+The first paper, "Commitment through Sacrifice: How Longer Ramadan Fasting Strengthens Religiosity and Political Islam" [@aksoy_2022_commitment], finds an OLS coefficient of about 7, implying a half-hour increase in fasting time is associated with a 3.5 percentage point increase in Islamist vote share.
 As shown in Figure \@ref(fig:replications) Panel A, coefficients using the double robust methods are noticeably smaller (though not significantly different from the original coefficients).
 In Model 2, which includes covariates, the main coefficient is nonsignificant at the 5-percent level.
-
-The second paper for replication is "They Can’t All Be Stars: The Matthew Effect, Cumulative Status Bias, and Status Persistence in NBA All-Star Elections" [@biegert_2023_they].
-The authors use detailed records on NBA players' performance to study the effect of previous year's All-Star nomination on being re-nominated in the current year.
-Panel B of Figure \@ref(fig:replications) shows the average marginal effects from the authors' original logistic regressions alongside the double robust replications.
+In both cases, the double robust estimates are more precise, with smaller standard errors than the OLS results.
+
+The second paper, "They Can’t All Be Stars: The Matthew Effect, Cumulative Status Bias, and Status Persistence in NBA All-Star Elections" [@biegert_2023_they].
+The authors use logistic regression to estimate the effect of the previous year's All-Star nomination on being re-nominated in the current year.
+Panel B of Figure \@ref(fig:replications) shows the average marginal effects from the authors' original regressions alongside the double robust replications.
 Models 1 and 2 do not control for previous performance and find that a previous year's nomination increases the likelihood of being nominated by 45 to 60 percentage points.
-Model 3 isolates the effect of the previous year's nomination from performance in the previous year; the original paper found a much smaller coefficient once these controls were incorporated, at about 5 percentage points increase, but the double robust methods retain large effect estimate sizes, at 30 and 59 percentage points for AIPW (GRF) and DML (SuperLearner), respectively.
-Models 4 and 5 control for other current factors, and double robust estimates are somewhat smaller than in Model 3 but still much larger than the original paper's estimate.
+Model 3 isolates the effect of the previous year's nomination from performance in the previous year; the original paper found a much smaller coefficient once these controls were incorporated, giving a marginal effect of about 5 percentage points, but the double robust methods estimate large effect sizes, at 30 and 59 percentage points for AIPW (GRF) and DML (SuperLearner), respectively.
+Models 4 and 5 control for other current factors, and double robust estimates are somewhat smaller than in Model 3 but still much larger than the original paper's estimates.
 
 The third and final paper for replication is "The 'Dark Side' of Community Ties: Collective Action and Lynching in Mexico" [@nussio_2024_dark].
-The author estimates the effect of community ties in Mexico on individual participation in lynching or lynching rates at aggregate levels.
 I present his three main analyses as separate panels.
-In his first analyses, he looks at individual propensity to participate in a lynching, using the log number of names of people a respondent knows in his or her colonia (neighborhood) as the independent variable.
-In models with and without controls, the authors finds that a one-percent increase in names known is associated with about 0.0003 percentage points greater likelihood of participating in a lynching (a coefficient of about 0.03 for the logged variable).
+In his first analyses, he looks at individual propensity to participate in a lynching, using the log number of names of people a respondent knows in his or her colonia (neighborhood) in Mexico City as the independent variable.
+In OLS models with and without controls, the author finds a coefficient of about 0.03 for the logged variable, implying that a one-percent increase in names known is associated with about 0.0003 percentage points greater likelihood of participating in a lynching.
 As shown in Panel C of Figure \@ref(fig:replications), For AIPW (GRF), coefficients and statistical significance are very similar to the original OLS coefficients.
@@
 Models estimate the effect of neighborly cooperation -- operationalized by the proportion of respondents who think that most neighbors help each other in problems related to electric lighting -- on the log municipal lynching rate.
-The original estimate was fairly stable across models with controls, at about a one percentage point increase in neighborly cooperation is associated with a two-percent increase the lynching rate [$\exp(2/100) = 1.02$].
-This estimate is fairly stable across estimators, though (as shown in the Online Appendix) this is one case where incorporating fixed effects in the DML models reduces coefficient sizes.
+The original OLS estimate was fairly stable across models with controls, at about a one percentage point increase in neighborly cooperation associated with a two-percent increase in the lynching rate [$\exp(2/100) = 1.02$].
+This estimate is fairly stable across estimators, though (as shown in the Supplementary Material) this is one case where incorporating fixed effects in the DML models reduces coefficient sizes.
 
 Finally, Panel E of Figure \@ref(fig:replications) replicates Nussio's [-@nussio_2024_dark] natural experiment, where he estimates the effect of the Puebla earthquake on September 19, 2017, on the number of lynching events in a municipality, using panel data from 2000 to 2020.
-The original models found that municipalities within 250 km of the earthquake or that experienced earthquake damage experienced an increase of about 0.1 in the number of lynchings in years after 2017 (the mean yearly lynchings per municipality is 0.034).
+The original OLS models found that municipalities within 250 km of the earthquake or that experienced earthquake damage experienced an increase of about 0.1 in the number of lynchings in years after 2017 (the mean yearly lynchings per municipality is 0.034).
 While models for AIPW (GRF) are fairly similar to the original OLS estimates, DML (SuperLearner) estimates are double the original estimates.
@@
 DML (SuperLearner) estimates for Nussio's [-@nussio_2024_dark] individual analysis change sign and significance, while the AIPW (GRF) estimates are close to the OLS estimates.
-However, the simulation results suggested that the DML (SuperLearner) estimator has higher RMSE than both OLS and AIPW (GRF) (Figure \@ref(fig:dorie-results-rmse)), so perhaps the original results are reliable.^[The Online Appendix shows that the DoubleML package with the SuperLearner has higher bias and RMSE in the simulations than my own R code.] Overall, these replication results highlight the importance of testing the robustness of estimates to different models, while suggesting that double robust, machine learning methods often do produce radically different results from traditional methods.
-
-# LaLonde NSW Data
-
-In the Online Appendix, I provide another evaluation of these methods, using data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW), as provided by @dehejia_1999_causal.
+However, the simulation results presented in the previous section suggested that the DML (SuperLearner) estimator has higher RMSE than both OLS and AIPW (GRF) (Figure \@ref(fig:dorie-results-rmse)), so perhaps the original results are reliable.^[The Supplementary Material shows that the DoubleML package with the SuperLearner has higher bias and RMSE in the simulations than my own R code.] Overall, these replications highlight the importance of testing the robustness of estimates to different models; double robust, machine learning methods sometimes do produce substantively different results from traditional methods.
+
+<!-- # LaLonde NSW Data -->
+
+<!-- In the Supplementary Material, I provide another evaluation of these methods, using data from LaLonde's [-@lalonde_1986_evaluating] study of the National Supported Work Demonstration (NSW), as provided by @dehejia_1999_causal.
 LaLonde compared experimental estimates to control samples drawn from the Panel Study of Income Dynamics (PSID) and Westat's Matched Current Population Survey-Social Security Administration File (CPS).
 Following @dehejia_1999_causal, I present results for the original samples analyzed by @lalonde_1986_evaluating, but I also include results using a subsample of the experimental group that has 1974 earnings data available.
-
-Results are somewhat difficult to interpret.
+-->
+
+<!-- Results are somewhat difficult to interpret.
 In the original LaLonde data, most methods fail to estimate treatment effects in the observational data with the same sign as the experimental estimate.
@@
 This highlights the complexity of doing causal inference with observational data where ignorability may not hold.
-
-# Conclusion
+-->
+
+# Discussion and Conclusion
 
@@
 In the examples given in this paper, coefficients shift somewhat and sometimes change sign and significance.
-DML with a SuperLearner shows results that differ more dramatically from the OLS or logistic regressions that the authors originally used, while AIPW with GRF produces estimates that are, for the most part, fairly close to the original analyses'.
+DML with a SuperLearner shows results that differ more dramatically from the OLS or logistic regressions that the authors originally used, while AIPW with GRF produces estimates that are, for the most part, fairly close to those of the original analyses.
 This may be related to the higher error shown in the simulations for DML; this method may be somewhat more unstable.
@@
 First, although it considers some of the most popular double robust, machine learning, traditional, and single robust methods, there are many methods that it could not evaluate, including variations and extensions of the three methods.
+Future research could also consider the efficacy of calibration methods such as Entropy Balancing that have shown to be double robust (under certain assumptions) despite not explicitly modeling the outcome or treatment assignment [@zhao_2017_entropy].
 Second, although the simulations are meant to cover a wide range of data generating processes, they only consider continuous outcomes and binary treatments; simulations with binary or categorical outcomes and continuous or multi-armed treatments may yield different results.
 Finally, in considering only functional form misspecification, the simulations in this paper do not consider situations where ignorability does not hold.
-In particular, it does not evaluate situations where causal identification is misspecified [@keil_2018_resolving].
+In particular, this paper does not evaluate situations where causal identification is misspecified [@keil_2018_resolving].
 Future research should assess violations of this and other assumptions underlying these methods.
@@
 In conclusion, if researchers want small gains in accuracy, they may opt for AIPW, TMLE, or G-computation with a flexible machine learning algorithm.
-But these methods are computationally costly, taking as long as two minutes per dataset of 4,802 observations and 52 covariates, while OLS, PSM, and the Lin estimator each take a fraction of a second.^[The `grf` and `DoubleML`  packages are able to achieve faster computation time, at under 10 seconds.
-See tables of results in the Online Appendix.] While double robust methods are useful for social scientists to understand, in most applications, OLS or PSM provide similar results.
-However, in certain circumstances these double robust methods may be a better choice.
+But these methods are computationally costly, taking as long as two minutes per dataset of 4,802 observations and 52 covariates, while OLS, PSM, and the Lin estimator each take a fraction of a second.^[The `grf` and `DoubleML`  packages are able to achieve faster computation time, at under 10 seconds in these samples.
+See tables of results in the Supplementary Material.] While double robust methods are useful for social scientists to understand, in most applications, OLS or PSM provide similar results.
+In certain circumstances, however, these double robust methods may be a better choice.
 Especially when paired with a highly flexible estimator like a SuperLearner or GRF, these methods may be slightly more accurate, and they can be useful when the number of covariates is high or even exceeds the number of observations.
-In longitudinal settings with time-varying confounders, they may be more useful [@tran_2019_double].
+In longitudinal settings with time-varying confounders, they may be more helpful [@tran_2019_double].
 They can also be useful as a sensitivity check; if researchers obtain similar estimates across traditional and double robust methods, they can be more confident in the reliability of their estimates.
@@
 
+# (APPENDIX) Appendix {-}
+
+# R Code
+
+## AIPW
+
+The R code below implements AIPW with truncation of extreme weights.
+As with all of the double robust methods reviewed here, we begin with predicted values (such as from a machine learning algorithm) for the outcome for treated units `mu1_pred` and untreated units `mu0_pred` as well as predicted values for treatment assignment probability `pi_pred`.
+We also have `d`, the vector of actual treatment assignments, and `y`, the observed outcome values.
+
+```{r aipw-demo, eval = F, echo = T}
+require(tidyverse)
+
+aipw_calc <- function(mu1_pred, mu0_pred, pi_pred, d, y){
+  n <- length(mu1_pred)
+
+  # Truncate extreme values of the weights
+  pi_pred <- case_when(
+    pi_pred < .01 ~ .01,
+    pi_pred > .99 ~ .99,
+    T ~ pi_pred)
+
+  # Calculate the predicted outcome value for treated units
+  y1_pred <- (d*(y-mu1_pred))/pi_pred + mu1_pred
+  # Calculate the predicted outcome value for untreated units
+  y0_pred <- ((1-d)*(y-mu0_pred))/(1-pi_pred) + mu0_pred
+
+  # Calculate the ATE
+  ate <- (1/n)*(sum(y1_pred)) - (1/n)*sum(y0_pred)
+
+  return(ate)
+}
+```
+
+## TMLE
+
+Here is R code to implement TMLE with predicted outcome values `mu1_pred` and `mu0_pred` and predicted probability of treatment `pi_pred`.
+Since the outcome is bounded and continuous, it is transformed to fall between 0 and 1 via $\tilde Y_{i} = [Y_i - \min(Y)]/[(\max(Y)-\min(Y)]$.
+```{r tmle-demo, eval = F, echo = T}
+# Functions for normalization and de-normalization
+normalize <- function(x, y){(x - min(y)) / (max(y) - min(y))}
+denormalize <- function(x, y){x * (max(y) - min(y))}
+
+tmle_calc <- function(mu1_pred, mu0_pred, pi_pred, d, y){
+  # Normalize the outcome variable
+  mu1_pred <- normalize(mu1_pred, y)
+  mu0_pred <- normalize(mu0_pred, y)
+  y_tilde <- normalize(y, y))
+
+  n <- length(y)
+
+  # Calculate clever covariates
+  H0 = (1-d)/(1-pi_pred)
+  H1 = d/pi_pred
+
+  # Estimate fluctuation parameter through maximum likelihood estimation
+  epsilon <- glm(y_tilde ~ -1 + H0 + H1 + offset(qlogis((d==1)*mu1_pred + (d==0)*mu0_pred)),
+                 family = binomial(link = 'logit')) %>%
+    tidy() %>%
+    pull(estimate)
+
+  # Targeted estimates of the potential outcomes
+  target_0 <- plogis(qlogis(mu0_pred + epsilon[1]*H0))
+  target_1 <- plogis(qlogis(mu1_pred + epsilon[2]*H1))
+
+  # Estimate ATE
+  ATE <- mean(target_1 - target_0)
+  return(denormalize(ATE, y))
+}
+```
+
+## DML
+
+R code to implement DML is shown below.
+Since DML involves sample splitting, this code is a little different from the above examples.
+We start with observed outcome values `y`, treatment assignment `d`, and covariate matrix `x`.
+First, a pre-processing function `dml_pre()` randomly splits the sample, outputting $I$ and $I^c$ sets of each of these variables.
+The second step predicts outcome values and treatment probabilities for each half of the sample, using models fit to the other half.
+In the code chunk here, generalized random forests from the `grf` package are used to predict these, but any prediction algorithm can be used.
+Finally, a post-prediction function `dml_post()` performs the residual-on-residual regression for each half of the sample and finds the average of the two estimates to produce an ATE estimate.
+```{r dml-demo, eval = F, echo = T}
+# Pre-processing: sample splitting
+dml_pre <- function(y, d, x, seed = 1758){
+  set.seed(seed)
+
+  n <- length(y)
+  n_2 <- round(n/2)
+
+  # Split the sample
+  random_vec <- sample(1:n, n, replace = F)
+  I <- random_vec[1:n_2]
+  I_c <- random_vec[(n_2+1):n]
+
+  return(list(
+    y_I = y[I],
+    d_I = d[I],
+    x_I = x[I,],
+    y_I_c = y[I_c],
+    d_I_c = d[I_c],
+    x_I_c = x[I_c,]
+    ))
+}
+
+# Predictor function: in this case, generalized random forests
+grf_dml <- function(y_I, d_I, x_I, y_I_c, d_I_c, x_I_c){
+  # Train on the I_c sample, predict on the I sample
+  mu_mod1 <- grf::regression_forest(X = x_I_c, Y = y_I_c, tune.parameters = "all")
+  mu_pred1 <- predict(mu_mod1, newdata = x_I)$predictions
+
+  pi_mod1 <- grf::regression_forest(X = x_I_c, Y = d_I_c, tune.parameters = "all")
+  pi_pred1 <- predict(pi_mod1, newdata = x_I)$predictions
+
+  # Train on the I sample, predict on the I_c sample
+  mu_mod2 <- grf::regression_forest(X = x_I, Y = y_I, tune.parameters = "all")
+  mu_pred2 <- predict(mu_mod2, newdata = x_I_c)$predictions
+
+  pi_mod2 <- grf::regression_forest(X = x_I, Y = d_I, tune.parameters = "all")
+  pi_pred2 <- predict(pi_mod2, newdata = x_I_c)$predictions
+
+  return(list(
+    mu_pred1 = mu_pred1,
+    pi_pred1 = pi_pred1,
+    mu_pred2 = mu_pred2,
+    pi_pred2 = pi_pred2
+  ))
+}
+
+# Implement DML: takes outputs from pre_dml() and grf_dml()
+dml_post <- function(y_I, d_I, x_I, y_I_c, d_I_c, x_I_c,
+                     mu_pred1, pi_pred1, mu_pred2, pi_pred2){
+
+  # Residual-on-residual regression for each sample separately
+  v1 <- d_I - pi_pred1
+  delta1 <- (sum(v1 * d_I))^-1 * sum(v1 * (y_I - pi_pred1))
+
+  v2 <- d_I_c - pi_pred2
+  delta2 <- (sum(v2 * d_I_c))^-1 * sum(v2 * (y_I_c - pi_pred2))
+
+  # Average estimates from each sample
+  ate <- (delta1 + delta2)/2
+
+  return(ate)
+}
+
+dml_pre_out <- dml_pre(y = y, d = d, x = x)
+grf_dml_out <- do.call(grf_dml, dml_pre_out)
+dml_post_out <- do.call(dml_post, append(dml_pre_out, grf_dml_out))
+```
+
+\newpage
+
 # References

### 2025-05-29 draft/ms-adj-appendix.Rmd
revision

@@
 header-includes:
+  - \usepackage{caption}
   #- \usepackage{setspace}\doublespace
@@
 
+lm_lin_continuous <- function (formula, covariates, data, weights, subset, clusters, 
+  se_type = NULL, ci = TRUE, alpha = 0.05, return_vcov = TRUE, 
+  try_cholesky = FALSE) 
+{
+  if (length(all.vars(f_rhs(formula))) > 1) {
+    stop("The `formula` argument, `", format(formula), "`, must only have the ", 
+      "treatment variable on the right-hand side of the formula. Covariates ", 
+      "should be specified in the `covariates` argument like so:\n`covariates = ", 
+      paste0("~ ", paste(all.vars(f_rhs(formula))[-1], 
+        sep = " + ")), "`.", "\n\n See ?lm_lin.")
+  }
+  if (!inherits(covariates, "formula")) {
+    stop("The `covariates` argument must be specified as a formula:\n", 
+      "You passed an object of class ", class(covariates))
+  }
+  cov_terms <- terms(covariates)
+  if (attr(cov_terms, "response") != 0) {
+    stop("Must not specify a response variable in `covariates`` formula.\n", 
+      "`covariates` must be a right-sided formula, such as '~ x1 + x2 + x3'")
+  }
+  if (length(attr(cov_terms, "order")) == 0) {
+    stop("`covariates` must have a variable on the right-hand side, not 0 or 1")
+  }
+  full_formula <- update(formula, reformulate(c(".", labels(cov_terms))))
+  datargs <- enquos(formula = full_formula, weights = weights, 
+    subset = subset, cluster = clusters)
+  data <- enquo(data)
+  model_data <- clean_model_data(data = data, datargs)
+  outcome <- as.matrix(model_data$outcome)
+  n <- nrow(outcome)
+  design_matrix <- model_data$design_matrix
+  weights <- model_data$weights
+  cluster <- model_data$cluster
+  has_intercept <- attr(terms(formula), "intercept")
+  treat_col <- which(attr(design_matrix, "assign") == 1)
+  treatment <- design_matrix[, treat_col, drop = FALSE]
+  design_mat_treatment <- colnames(design_matrix)[treat_col]
+  # if (any(!(treatment %in% c(0, 1)))) {
+  #   vals <- sort(unique(treatment))
+  #   if (has_intercept) 
+  #     vals <- vals[-1]
+  #   n_treats <- length(vals)
+  #   names(vals) <- paste0(colnames(design_matrix)[treat_col], 
+  #     vals)
+  #   treatment <- outer(drop(treatment), vals, function(x, 
+  #     y) as.numeric(x == y))
+  # }
+  demeaned_covars <- design_matrix[, setdiff(colnames(design_matrix), 
+    c(design_mat_treatment, "(Intercept)")), drop = FALSE]
+  if (is.numeric(weights)) {
+    center <- apply(demeaned_covars, 2, weighted.mean, weights)
+  }
+  else {
+    center <- colMeans(demeaned_covars)
+  }
+  demeaned_covars <- sweep(demeaned_covars, 2, center)
+  original_covar_names <- colnames(demeaned_covars)
+  colnames(demeaned_covars) <- paste0(ifelse(grepl("\\:|(^.+\\()", 
+    colnames(demeaned_covars)), paste0("(", colnames(demeaned_covars), 
+    ")"), colnames(demeaned_covars)), "_c")
+  n_treat_cols <- ncol(treatment)
+  n_covars <- ncol(demeaned_covars)
+  n_int_covar_cols <- n_covars * (n_treat_cols)
+  interacted_covars <- matrix(0, nrow = n, ncol = n_int_covar_cols)
+  interacted_covars_names <- character(n_int_covar_cols)
+  for (i in 1:n_covars) {
+    covar_name <- colnames(demeaned_covars)[i]
+    cols <- (i - 1) * n_treat_cols + (1:n_treat_cols)
+    interacted_covars[, cols] <- treatment * demeaned_covars[, 
+      i]
+    interacted_covars_names[cols] <- paste0(colnames(treatment), 
+      ":", covar_name)
+  }
+  colnames(interacted_covars) <- interacted_covars_names
+  if (has_intercept) {
+    X <- cbind(matrix(1, nrow = n, ncol = 1, dimnames = list(NULL, 
+      "(Intercept)")), treatment, demeaned_covars, interacted_covars)
+  }
+  else {
+    if (n_treat_cols == 1) {
+      X <- cbind(treatment, demeaned_covars, interacted_covars)
+    }
+    else {
+      X <- cbind(treatment, interacted_covars)
+    }
+  }
+  return_list <- lm_robust_fit(y = outcome, X = X, weights = weights, 
+    cluster = cluster, ci = ci, se_type = se_type, alpha = alpha, 
+    return_vcov = return_vcov, try_cholesky = try_cholesky, 
+    has_int = has_intercept, iv_stage = list(0))
+  return_list <- lm_return(return_list, model_data = model_data, 
+    formula = formula)
+  return_list[["scaled_center"]] <- center
+  setNames(return_list[["scaled_center"]], original_covar_names)
+  return_list[["call"]] <- match.call()
+  return(return_list)
+}
+
+environment(lm_lin_continuous) <- asNamespace('estimatr')
+assignInNamespace("lm_lin", lm_lin_continuous, ns = "estimatr")
+
 ## Functions using double robust packages ####
@@
 dml_sim <- function(dat, seed = 185){
-  library(mlr3)
-  library(mlr3learners)
 
@@
 
-compare_tbl <- function(model_list, treatment){
+p_val <- function(estimate, std.error){
+  z <- estimate / std.error
+  2*(1 - pnorm(abs(as.numeric(z))))
+}
+
+compare_tbl <- function(model_list, treatment, tidy = T){
   out_list <- list()
@@
   for(model_set in model_list){
-    names(model_set[[2]]) <- c('estimate', 'std.error')
-
-    out_list[[k]] <- tidy(model_set[[1]]) %>%
-      filter(term == treatment) %>%
-      bind_rows(bind_rows(model_set[[2]])) %>%
-      bind_rows(model_set[[3]]) %>%
-      mutate(term = c('Original', 'AIPW (GRF)', 'DML (SuperLearner)'), p.value = p_val(estimate, std.error))
+    names(model_set$grf) <- c('estimate', 'std.error')
+
+    if(tidy == T){
+    original_model <- tidy(model_set$original) %>%
+      filter(term == treatment)
+    } else{
+      original_model <- model_set$original
+    }
+
+    out_list[[k]] <- original_model %>%
+      bind_rows(bind_rows(model_set$grf)) %>%
+      bind_rows(model_set$dml) %>%
+      bind_rows(model_set$dml_cre) %>%
+      bind_rows(model_set$dml_wg_cre) %>%
+      mutate(term = c('Original', 'AIPW (GRF)', 'DML (SuperLearner)', 
+                      'DML (SuperLearner), CRE FE', 'DML (SuperLearner), hybrid FE'), 
+             p.value = p_val(estimate, std.error)) %>%
+      remove_rownames() %>%
+      tibble()
 
@@
 }
+
+# compare_tbl_notidy <- function(model_list){
+#   out_list <- list()
+#   k <- 1
+#   for(model_set in model_list){
+#     names(model_set[[2]]) <- c('estimate', 'std.error')
+#     
+#     
+#     out_list[[k]] <- model_set[[1]] %>%
+#       bind_rows(bind_rows(model_set[[2]])) %>%
+#       bind_rows(model_set[[3]]) %>%
+#       mutate(term = c('Original', 'AIPW (GRF)', 'DML (SuperLearner)'), p.value = p_val(estimate, std.error)) %>%
+#       tibble()
+#     
+#     k <- k+1
+#   }
+#   return(out_list)
+# }
 
@@
 }
+
 ```
@@
 
-# Tables of Results
+# Main Simulations
 
@@
                     linesep = '',
-                    caption = 'Main datasets: Results of Monte Carlo simulations using the first 20 datasets from Dorie et al.
+                    caption = 'Main datasets: Results of Monte Carlo simulations using the first 20 DGPs from Dorie et al.
 (2019), 10 replications each.
@@
 \newpage
+
+# Linear Simulations
 
@@
                     linesep = '',
-                    caption = 'Linear datasets: Results of Monte Carlo simulations using the two datasets from Dorie et al.
-(2019), with linear data generating processes, 100 replications each ("linear").
+                    caption = 'Linear DGPs: Results of Monte Carlo simulations using the two datasets from Dorie et al.
+(2019), with linear data generating processes, 100 replications each.
 Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is median computation time measured in seconds for each dataset.') %>%
@@
 \newpage
+
+# Data Generating Processes
+
+```{r dgp}
+dgp_names <- c('Treat. assign.', 'Prob. of treat.',
+               'Overlap', 'Response surface',
+               'Alignment',
+               'Treat. heterogeneity')
+
+rename_vec <- names(aciccomp2016::parameters_2016)
+names(rename_vec) <- dgp_names
+
+sim_results_dgp <- sim_results %>%
+  filter(set == 'main') %>%
+  # mutate(paramter_num = ceiling(dataset/10)) %>%
+  left_join(mutate(aciccomp2016::parameters_2016, dorie_dataset = row_number())) %>%
+  rename(rename_vec) %>%
+  mutate(estimator = if_else(is.na(estimator), 'NA', estimator),
+         method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
+  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator})))
+
+dgp_list <- list()
+
+for(name in dgp_names){
+
+  dgp_list[[name]] <- sim_results_dgp %>%
+    group_by(!!sym(name), method_estimator) %>%
+    summarize(bias = round(mean(ate - truth, na.rm = T), 3),
+            percent_bias = bias/sd(ate, na.rm = T),
+            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
+            mae = median(abs(ate - truth), na.rm = T),
+            datasets = n_distinct(dataset)
+              )  %>%
+    ungroup() %>%
+    mutate(`DGP parameter` = name,
+          dgp_value = as.character(!!sym(name))) %>%
+    select(-!!sym(name))
+
+}
+
+bind_rows(dgp_list) %>%
+  select(`DGP parameter`, dgp_value, everything()) %>%
+  arrange(`DGP parameter`, dgp_value, rmse) %>%  
+  # mutate(bias = as.character(bias),
+  #        rmse = as.character(rmse)) %>%
+  # mutate(across(bias:comp_time, function(x){as.character(round(x, 3))})) %>%
+  kableExtra::kable(booktabs = T, 
+                    digits = 3,
+                    linesep = '',
+                    longtable = T,
+                    caption = 'Data generating process: Within each DGP value, estimates are sorted from lowest to highest RMSE, based on Monte Carlo simulations using the first 20 DGPs from Dorie et al.
+(2019), 10 replications each.
+Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and datasets shows the number of distinct datasets in the simulations with each particular DGP parameter.') %>%
+  kable_styling(latex_options = c("hold_position")) #'repeat_header'))
+
+```
+
+\newpage
+
+# Sample Sizes
 
@@
                     longtable = T,
-                    caption = 'Sample size: Results of Monte Carlo simulations using dataset 7 from Dorie et al.
+                    caption = 'Sample size: Results of Monte Carlo simulations using DGP 7 from Dorie et al.
 (2019) with varying sample sizes, 20 replications each.
@@
 
-# Replications with Fixed Effects
-
-The tables below present estimates from the *ASR* replications discussed in the main text, but with the addition of two other models implementing methods proposed by @clarke_2024_double that incorporate individual or group fixed effects into DML.
+<!-- # Replications -->
+
+<!-- ```{r aksoy, eval = F} -->
+<!-- aksoy <- read_dta(here('replication', 'aksoy.dta')) %>% -->
+<!--   mutate(cid_num = as.integer(factor(cid))) %>% -->
+<!--   as_factor() -->
+
+<!-- # first three models from table 2 -->
+
+<!-- m1 <- lm(ISL ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` +  -->
+<!--      `_Y66` + `_Y70` + `_Y71` + dlen + cid, -->
+<!--    data = filter(aksoy, electyr == T)) # %>% -->
+<!--   # tidy() %>% -->
+<!--   # filter(!str_detect(term, 'cid'), !str_detect(term, '_Y')) -->
+
+<!-- m2 <- lm(ISL ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` +  -->
+<!--      `_Y66` + `_Y70` + `_Y71` + dlen + cid + gdp_g + t + m + pop, -->
+<!--    data = aksoy)  -->
+<!--   # tidy() %>% -->
+<!--   # filter(!str_detect(term, 'cid'), !str_detect(term, '_Y')) -->
+
+<!-- m3 <- lm(ISL ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` +  -->
+<!--      `_Y66` + `_Y70` + `_Y71` + dlen + cid + gdp_g + t + m + pop + l_ISL, -->
+<!--    data = aksoy)  -->
+<!--   # tidy() %>% -->
+<!--   # filter(!str_detect(term, 'cid'), !str_detect(term, '_Y')) -->
+
+<!-- # aksoy %>% -->
+<!-- #   filter(electyr == T) %>% -->
+<!-- #   mutate(across(c(`_Y28`, `_Y32`, `_Y42`, `_Y46`, `_Y50`, `_Y54`, `_Y57`,  -->
+<!-- #                   `_Y62`, `_Y66`, `_Y70`, `_Y71`), ~ .x - mean(.x, na.rm = T))) %>% -->
+<!-- #   estimatr::lm_robust(ISL ~ dlen*(`_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` +  -->
+<!-- #                                     `_Y54` + `_Y57` + `_Y62` + `_Y66` + `_Y70` + `_Y71` + cid), -->
+<!-- #    data = .) %>% -->
+<!-- #   tidy() %>% -->
+<!-- #   filter(term == 'dlen') -->
+<!-- #  -->
+<!-- #  -->
+<!-- # m1_lin <- estimatr::lm_robust(ISL ~ dlen*(`_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` + `_Y66` + `_Y70` + `_Y71`) + cid, -->
+<!-- #    data = filter(aksoy, electyr == T)) %>% -->
+<!-- #   tidy() %>% -->
+<!-- #   filter(term == 'dlen') -->
+<!-- #  -->
+<!-- #  -->
+<!-- # m1_lin <- lm_lin_continuous(ISL ~ dlen, -->
+<!-- #                            covariates = ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` + -->
+<!-- #      `_Y66` + `_Y70` + `_Y71` + cid, -->
+<!-- #    data = filter(aksoy, electyr == T)) %>% -->
+<!-- #   tidy() %>% -->
+<!-- #   filter(term == 'dlen') -->
+<!-- #  -->
+<!-- #  -->
+<!-- # m2_lin <- lm_lin_continuous(ISL ~ dlen, -->
+<!-- #                            covariates = ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` + -->
+<!-- #      `_Y66` + `_Y70` + `_Y71` + cid + gdp_g + t + m + pop, -->
+<!-- #    data = aksoy) %>% -->
+<!-- #   tidy() %>% -->
+<!-- #   filter(term == 'dlen')  -->
+<!-- #  -->
+<!-- #  -->
+<!-- # m3_lin <- lm_lin_continuous(ISL ~ dlen, -->
+<!-- #                            covariates = ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` + -->
+<!-- #      `_Y66` + `_Y70` + `_Y71` + dlen + cid + gdp_g + t + m + pop + l_ISL, -->
+<!-- #    data = aksoy) %>% -->
+<!-- #   tidy() %>% -->
+<!-- #   filter(term == 'dlen')  -->
+
+<!-- # aksoy_drop_na_y <- filter(aksoy, !is.na(ISL)) -->
+
+<!-- m1_grf_dml <- dml_grf(outcome = 'ISL',  -->
+<!--         treatment = 'dlen',  -->
+<!--         covariates = c('year'),  -->
+<!--         clustervar = 'cid_num', -->
+<!--         dataset = aksoy, -->
+<!--         target = 'all') -->
+
+<!-- m2_grf_dml <- dml_grf(outcome = 'ISL',  -->
+<!--         treatment = 'dlen',  -->
+<!--         covariates = c('year', 'gdp_g', 't', 'm', 'pop'),  -->
+<!--         clustervar = 'cid_num', -->
+<!--         dataset = aksoy, -->
+<!--         target = 'all') -->
+
+<!-- m3_grf_dml <- dml_grf(outcome = 'ISL',  -->
+<!--         treatment = 'dlen',  -->
+<!--         covariates = c('year', 'gdp_g', 't', 'm', 'pop', 'l_ISL'),  -->
+<!--         clustervar = 'cid_num', -->
+<!--         dataset = aksoy, -->
+<!--         target = 'all') -->
+
+<!-- m1 <- data.frame(estimate = 7.159, std.error = 2.539) -->
+<!-- m2 <- data.frame(estimate = 7.349, std.error = 2.491) -->
+<!-- m3 <- data.frame(estimate = 5.317, std.error = 1.855) -->
+
+<!-- compare_tbl(list(append(list(original = m1), m1_grf_dml),  -->
+<!--                                   append(list(original = m2), m2_grf_dml),  -->
+<!--                                   append(list(original = m3), m3_grf_dml)), -->
+<!--                              tidy = F) %>% -->
+<!--   write_rds(here('replication', 'aksoy_rep.RDS')) -->
+
+<!-- # huxtable::huxreg(compare_tbl(list(append(list(original = m1), m1_grf_dml),  -->
+<!-- #                                   append(list(original = m2), m2_grf_dml),  -->
+<!-- #                                   append(list(original = m3), m3_grf_dml)), -->
+<!-- #                              tidy = F), -->
+<!-- #                  statistics = NA) %>% -->
+<!-- #   huxtable::insert_row(c('Covariates', 'No', rep('Yes', 2)), after = nrow(.) - 1) %>% -->
+<!-- #   huxtable::insert_row(c('Lagged dependent variable', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>% -->
+<!-- #   huxtable::set_caption('Replication of aksoy et al.
+(2022) Table 2, models for outcome of Islamic Votes: "Effect of Fasting Hours (Daylength) during Ramadan on Various Outcome Variables Based on Regression Models That Include Fixed Effects for Provinces and Election Years"') %>% -->
+<!-- #   write_rds(here('replication', 'aksoy_tab.RDS')) -->
+<!-- #  -->
+<!-- # read_rds(here('replication', 'aksoy_rep.RDS')) %>% -->
+<!-- #   huxtable::huxreg() -->
+
+<!-- ``` -->
+
+<!-- ```{r biegert, eval = F} -->
+<!-- # Table 3 -->
+
+<!-- biegert <- read_dta(here('replication', 'biegert.dta')) %>% -->
+<!--   filter(sampleC == 1) %>% -->
+<!--   mutate(year_num = as.numeric(year), -->
+<!--          allstar_y_num = as.numeric(allstar_y), -->
+<!--          allstar_x_num = as.numeric(allstar_x), -->
+<!--     across(c(allstar_y, allstar_x, year), as.factor), -->
+<!--     player_id_num = as.integer(factor(player_id))) %>% -->
+<!--   as_factor() -->
+
+<!-- m1 <- glm(allstar_y ~ allstar_x,  -->
+<!--           data = filter(biegert, sampleC == 1), family = 'binomial') %>% -->
+<!--   margins::margins(variables = 'allstar_x',  -->
+<!--                    vcov = sandwich::vcovCL(., cluster = ~player_id))  -->
+
+<!-- m2 <- glm(allstar_y ~ allstar_x + height + pos + age_0 + age_0_2 + Black + time + time_2 + year,  -->
+<!--           data = filter(biegert, sampleC == 1), -->
+<!--           family = binomial(link = 'logit')) %>% -->
+<!--   margins::margins(variables = 'allstar_x',  -->
+<!--                    vcov = sandwich::vcovCL(., cluster = ~player_id))  -->
+
+<!-- m3 <- glm(allstar_y ~ allstar_x + height + pos + age_0 + age_0_2 + Black + time + time_2 + year + -->
+<!--             pts_sdt_nd + ast_sdt_nd + trb_sdt_nd + min_played_nd +  playoffs_nd + win_nd + bigm_nd,  -->
+<!--           data = filter(biegert, sampleC == 1), -->
+<!--           family = binomial(link = 'logit')) %>% -->
+<!--   margins::margins(variables = 'allstar_x',  -->
+<!--                    vcov = sandwich::vcovCL(., cluster = ~player_id))  -->
+
+<!-- m4 <- glm(allstar_y ~ allstar_x + height + pos + age_0 + age_0_2 + Black + time + time_2 + year + -->
+<!--             pts_sdt_nd + ast_sdt_nd + trb_sdt_nd + min_played_nd +  playoffs_nd + win_nd + bigm_nd + -->
+<!--             pts_sdt_t + ast_sdt_t + trb_sdt_t,  -->
+<!--           data = filter(biegert, sampleC == 1), -->
+<!--           family = binomial(link = 'logit')) %>% -->
+<!--   margins::margins(variables = 'allstar_x',  -->
+<!--                    vcov = sandwich::vcovCL(., cluster = ~player_id))  -->
+
+<!-- m5 <- glm(allstar_y ~ allstar_x + height + pos + age_0 + age_0_2 + Black + time + time_2 + year + -->
+<!--             pts_sdt_nd + ast_sdt_nd + trb_sdt_nd + min_played_nd +  playoffs_nd + win_nd + bigm_nd + -->
+<!--             pts_sdt_t + ast_sdt_t + trb_sdt_t + -->
+<!--             min_played_t + playoffs_t + win_t + bigm_t,  -->
+<!--           data = filter(biegert, sampleC == 1), -->
+<!--           family = binomial(link = 'logit')) %>% -->
+<!--   margins::margins(variables = 'allstar_x',  -->
+<!--                    vcov = sandwich::vcovCL(., cluster = ~player_id))  -->
+
+<!-- m6 <- glm(allstar_y ~ allstar_x + allstar_hi + height + pos + age_0 + age_0_2 + Black + time + time_2 + year + -->
+<!--             pts_sdt_nd + ast_sdt_nd + trb_sdt_nd + min_played_nd +  playoffs_nd + win_nd + bigm_nd + -->
+<!--             pts_sdt_t + ast_sdt_t + trb_sdt_t + -->
+<!--             min_played_t + playoffs_t + win_t + bigm_t + -->
+<!--             pts_sdt_hi + ast_sdt_hi + trb_sdt_hi + min_played_hi + playoffs_hi + win_hi + bigm_hi,  -->
+<!--           data = filter(biegert, sampleC == 1), -->
+<!--           family = binomial(link = 'logit')) %>% -->
+<!--   margins::margins(variables = 'allstar_x',  -->
+<!--                    vcov = sandwich::vcovCL(., cluster = ~player_id))  -->
+
+<!-- # M1  -->
+<!-- set.seed(123) -->
+<!-- Y <- as.numeric(biegert[['allstar_y']]) -->
+<!-- X <- data.frame(var = rep(NA_integer_, length(Y))) -->
+<!-- W <- as.numeric(biegert[['allstar_x']]) -->
+
+<!-- grf_model1 <- grf::causal_forest(X = X, Y = Y, W = W, seed = 123, -->
+<!--                       clusters = biegert$player_id_num -->
+<!--                       ) -->
+
+<!-- grf_out1 <- grf::average_treatment_effect(grf_model1, target.sample = 'all') -->
+
+<!-- dml_out1 <- data.frame(estimate = NA, -->
+<!--                        std.error = NA) -->
+<!-- dml_cre_out1 <- dml_out1 -->
+<!-- dml_hybrid_out1 <- dml_out1 -->
+
+<!-- # M2 -->
+<!-- m2_grf_dml <- dml_grf(outcome = 'allstar_y_num',  -->
+<!--         treatment = 'allstar_x_num',  -->
+<!--         covariates = c('height', 'pos', 'age_0', 'Black', 'time', 'year_num'),  -->
+<!--         clustervar = 'player_id_num', -->
+<!--         dataset = biegert, -->
+<!--         target = 'all') -->
+
+<!-- # M3  -->
+<!-- m3_grf_dml <- dml_grf(outcome = 'allstar_y_num',  -->
+<!--         treatment = 'allstar_x_num',  -->
+<!--         covariates = c('height', 'pos', 'age_0', 'Black', 'time', 'year_num', -->
+<!--                        'pts_sdt_nd', 'ast_sdt_nd', 'trb_sdt_nd', 'min_played_nd',  'playoffs_nd', 'win_nd', 'bigm_nd'),  -->
+<!--         clustervar = 'player_id_num', -->
+<!--         dataset = biegert, -->
+<!--         target = 'all') -->
+
+<!-- # M4 -->
+<!-- m4_grf_dml <- dml_grf(outcome = 'allstar_y_num',  -->
+<!--         treatment = 'allstar_x_num',  -->
+<!--         covariates = c('height', 'pos', 'age_0', 'Black', 'time', 'year_num', -->
+<!--                        'pts_sdt_nd', 'ast_sdt_nd', 'trb_sdt_nd', 'min_played_nd',  'playoffs_nd', 'win_nd', 'bigm_nd', -->
+<!--                        'pts_sdt_t', 'ast_sdt_t', 'trb_sdt_t'),  -->
+<!--         clustervar = 'player_id_num', -->
+<!--         dataset = biegert, -->
+<!--         target = 'all') -->
+
+<!-- # M5 -->
+<!-- m5_grf_dml <- dml_grf(outcome = 'allstar_y_num',  -->
+<!--         treatment = 'allstar_x_num',  -->
+<!--         covariates = c('height', 'pos', 'age_0', 'Black', 'time', 'year_num', -->
+<!--                        'pts_sdt_nd', 'ast_sdt_nd', 'trb_sdt_nd', 'min_played_nd',  'playoffs_nd', 'win_nd', 'bigm_nd', -->
+<!--                        'pts_sdt_t', 'ast_sdt_t', 'trb_sdt_t', -->
+<!--                        'min_played_t', 'playoffs_t', 'win_t', 'bigm_t'),  -->
+<!--         clustervar = 'player_id_num', -->
+<!--         dataset = biegert, -->
+<!--         target = 'all') -->
+
+<!-- # # M6 -->
+<!-- # m6_grf_dml <- dml_grf(outcome = 'allstar_y_num',  -->
+<!-- #         treatment = 'allstar_x_num',  -->
+<!-- #         covariates = c('height', 'pos', 'age_0', 'Black', 'time', 'year_num', -->
+<!-- #                        'pts_sdt_nd', 'ast_sdt_nd', 'trb_sdt_nd', 'min_played_nd',  'playoffs_nd', 'win_nd', 'bigm_nd', -->
+<!-- #                        'pts_sdt_t', 'ast_sdt_t', 'trb_sdt_t', -->
+<!-- #                        'min_played_t', 'playoffs_t', 'win_t', 'bigm_t', -->
+<!-- #                        'pts_sdt_hi', 'ast_sdt_hi', 'trb_sdt_hi', 'min_played_hi', 'playoffs_hi', 'win_hi', 'bigm_hi'),  -->
+<!-- #         clustervar = 'player_id_num', -->
+<!-- #         dataset = biegert, -->
+<!-- #         target = 'all') -->
+
+<!-- out_empty <- grf_out1 -->
+<!-- out_empty$estimate <- NA -->
+<!-- out_empty$std.err <-  -->
+
+<!-- compare_tbl(model_list = list( -->
+<!--                  list(original = m1, grf = grf_out1, dml = dml_out1, dml_cre = dml_cre_out1, dml_wg_cre = dml_hybrid_out1),  -->
+<!--                  append(list(original = m2), m2_grf_dml),  -->
+<!--                  append(list(original = m3), m3_grf_dml), -->
+<!--                  append(list(original = m4), m4_grf_dml), -->
+<!--                  append(list(original = m5), m5_grf_dml), -->
+<!--             treatment = 'allstar_x1', -->
+<!--             tidy = T) %>% -->
+<!--   write_rds(here('replication', 'biegert_rep.RDS')) -->
+
+<!-- # Final table -->
+<!-- # huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1), -->
+<!-- #                                   list(m2, grf_out2, dml_out2), -->
+<!-- #                                   list(m3, grf_out3, dml_out3), -->
+<!-- #                                   list(m4, grf_out4, dml_out4), -->
+<!-- #                                   list(m5, grf_out5, dml_out5), -->
+<!-- #                                   list(m6, grf_out6, dml_out6)), -->
+<!-- #                              treatment = 'allstar_x1'), -->
+<!-- #                  statistics = NA) %>% -->
+<!-- #   huxtable::insert_row(c('Baseline confounders', 'No', rep('Yes', 5)), after = nrow(.) - 1) %>% -->
+<!-- #   huxtable::insert_row(c('Prior situation + performance', rep('No', 2), rep('Yes', 4)), after = nrow(.) - 1) %>% -->
+<!-- #   huxtable::insert_row(c('Current performance', rep('No', 3), rep('Yes', 3)), after = nrow(.) - 1) %>% -->
+<!-- #   huxtable::insert_row(c('Current situation', rep('No', 4), rep('Yes', 2)), after = nrow(.) - 1) %>% -->
+<!-- #   huxtable::insert_row(c('Cumul. AS + cumul. mediators', rep('No', 5), 'Yes'), after = nrow(.) - 1) %>% -->
+<!-- #   huxtable::set_caption('Replication of Biegert et al. (2023) Table 3: "Average Marginal Effects from Logistic Regression Models of All-Star Nomination"') %>% -->
+<!-- #   write_rds(here('replication', 'biegert_tab.RDS')) -->
+<!-- #  -->
+<!-- # read_rds(here('replication', 'biegert_tab.RDS')) -->
+
+<!-- ``` -->
+
+<!-- ```{r nussio-ind, eval = F} -->
+<!-- nussio_ind <- read_dta(here('replication/nussio_2024', 'Mexico City Individual data.dta')) %>% -->
+<!--   filter(if_all(c(PARP, lognombre), ~!is.na(.x))) %>% -->
+<!--   mutate(across(c(PARP, IT1, ED, BASURA), as.numeric), -->
+<!--          cve_col_num = as.numeric(factor(cve_col))) %>% -->
+<!--   as_factor() -->
+
+<!-- ## Table 2 #### (individual analysis) -->
+
+<!-- m1 <- lm(PARP ~ lognombre + IT1,  -->
+<!--          nussio_ind) %>% -->
+<!--   lmtest::coeftest(., vcov = sandwich::vcovCL(., ~cve_col)) -->
+
+<!-- m2 <- lm(PARP ~ lognombre + IT1 +  -->
+<!--            ED + age + female + INGi + unemployed,  -->
+<!--          nussio_ind) %>% -->
+<!--   lmtest::coeftest(., vcov = sandwich::vcovCL(., ~cve_col)) -->
+
+<!-- m3 <- lm(PARP ~ lognombre + IT1 +  -->
+<!--            ED + age + female + INGi + unemployed + -->
+<!--            HER + catholic + nonreligious + working + BASURA + RESS +  -->
+<!--            PELEA  + PADRES + index_trustgov,  -->
+<!--          nussio_ind) %>% -->
+<!--   lmtest::coeftest(., vcov = sandwich::vcovCL(., ~cve_col)) -->
+
+<!-- m4 <- lm(PARP ~ lognombre + IT1 +  -->
+<!--            ED + age + female + INGi + unemployed + -->
+<!--            HER + catholic + nonreligious + working + BASURA + RESS +  -->
+<!--            PELEA  + PADRES + index_trustgov + -->
+<!--            col, nussio_ind) %>% -->
+<!--   lmtest::coeftest(., vcov = sandwich::vcovCL(., ~cve_col))  -->
+<!--   # tidy() %>% -->
+<!--   # filter(!(str_detect(term, 'col'))) -->
+
+<!-- # M1  -->
+<!-- m1_grf_dml <- dml_grf(outcome = 'PARP',  -->
+<!--         treatment = 'lognombre',  -->
+<!--         covariates = c('IT1'),  -->
+<!--         clustervar = 'cve_col_num', -->
+<!--         dataset = nussio_ind, -->
+<!--         target = 'all') -->
+
+<!-- # M2  -->
+<!-- m2_grf_dml <- dml_grf(outcome = 'PARP',  -->
+<!--         treatment = 'lognombre',  -->
+<!--         covariates = c('IT1', 'ED', 'age', 'female', 'INGi', 'unemployed'),  -->
+<!--         clustervar = 'cve_col_num', -->
+<!--         dataset = nussio_ind, -->
+<!--         target = 'all') -->
+
+<!-- # M3 & M4 (M4 has fixed effects) -->
+<!-- m3_grf_dml <- dml_grf(outcome = 'PARP',  -->
+<!--         treatment = 'lognombre',  -->
+<!--         covariates = c('IT1', 'ED', 'age', 'female', 'INGi', 'unemployed', -->
+<!--                        'HER', 'catholic', 'nonreligious', 'working', 'BASURA', 'RESS',  -->
+<!--                        'PELEA' , 'PADRES', 'index_trustgov'),  -->
+<!--         clustervar = 'cve_col_num', -->
+<!--         dataset = nussio_ind, -->
+<!--         target = 'all') -->
+
+<!-- m4_grf_dml <- m3_grf_dml -->
+
+<!-- compare_tbl(model_list = list(append(list(original = m1), m1_grf_dml), -->
+<!--                               append(list(original = m2), m2_grf_dml),  -->
+<!--                               append(list(original = m3), m3_grf_dml), -->
+<!--                               append(list(original = m4), m4_grf_dml)), -->
+<!--             treatment = 'lognombre', -->
+<!--             tidy = T) %>% -->
+<!--   write_rds(here('replication', 'nussio_ind_rep.RDS')) -->
+
+<!-- # Final table -->
+<!-- # huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1), -->
+<!-- #                                   list(m2, grf_out2, dml_out2), -->
+<!-- #                                   list(m3, grf_out3, dml_out3), -->
+<!-- #                                   list(m4, grf_out4, dml_out4)), -->
+<!-- #                              treatment = 'lognombre'), -->
+<!-- #                  statistics = NA) %>% -->
+<!-- #   huxtable::insert_row(c('Colonia FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>% -->
+<!-- #   huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>% -->
+<!-- #   huxtable::set_caption('Replication of Nussio (2024) Table 2: "Individual-Level Analysis: Community Ties and Lynching Participation"') %>% -->
+<!-- #   write_rds(here('replication', 'nussio_ind_tab.RDS')) -->
+<!-- #  -->
+<!-- # read_rds(here('replication', 'nussio_ind_tab.RDS')) -->
+<!-- ``` -->
+
+<!-- ```{r nussio-ag, eval = F} -->
+<!-- ## Table 4 #### (aggregate analysis) -->
+<!-- nussio_ag <- read_dta(here('replication/nussio_2024',  -->
+<!--                            'Mexico Municipality Cross-Sectional Data.dta')) %>% -->
+<!--   filter(if_all(c(loglynchpermio, organized_lighting_mean), ~!is.na(.x))) %>% -->
+<!--   mutate(estado_num = as.numeric(estado)) %>% -->
+<!--   # mutate(across(c(PARP, IT1, ED, BASURA), as.numeric), -->
+<!--   #        cve_col_num = as.integer(factor(cve_col))) %>% -->
+<!--   as_factor() -->
+
+<!-- nussio_ag_drop_na <- nussio_ag %>% drop_na(loglynchpermio, organized_lighting_mean, -->
+<!--                           trust_neighbors_mean, problem_lighting_mean, -->
+<!--                           c_poptot, area, pconeval_poverty_pobreza_pob,  -->
+<!--                           coneval_gini_coeficientedegini, -->
+<!--                           indigenous, c_poptot_norelpop, homirate, robberyrate, -->
+<!--            victim_household_before_prev_yea, trust_army_mean) -->
+
+<!-- m1 <- lm(loglynchpermio ~ organized_lighting_mean + trust_neighbors_mean + problem_lighting_mean, -->
+<!--          nussio_ag) %>% -->
+<!--   lmtest::coeftest(., vcov = sandwich::vcovCL(., ~estado)) -->
+
+<!-- m2 <- lm(loglynchpermio ~ organized_lighting_mean + trust_neighbors_mean + problem_lighting_mean + -->
+<!--            c_poptot + area + pconeval_poverty_pobreza_pob + coneval_gini_coeficientedegini +  -->
+<!--            indigenous + c_poptot_norelpop + homirate + robberyrate, -->
+<!--          nussio_ag) %>% -->
+<!--   lmtest::coeftest(., vcov = sandwich::vcovCL(., ~estado)) -->
+
+<!-- m3 <- lm(loglynchpermio ~ organized_lighting_mean + trust_neighbors_mean + problem_lighting_mean + -->
+<!--            c_poptot + area + pconeval_poverty_pobreza_pob + coneval_gini_coeficientedegini +  -->
+<!--            indigenous + c_poptot_norelpop + homirate + robberyrate + -->
+<!--            victim_household_before_prev_yea + trust_army_mean, -->
+<!--          nussio_ag) %>% -->
+<!--   lmtest::coeftest(., vcov = sandwich::vcovCL(., ~estado)) -->
+
+<!-- m4 <- lm(loglynchpermio ~ organized_lighting_mean + trust_neighbors_mean + problem_lighting_mean + -->
+<!--            c_poptot + area + pconeval_poverty_pobreza_pob + coneval_gini_coeficientedegini +  -->
+<!--            indigenous + c_poptot_norelpop + homirate + robberyrate + -->
+<!--            victim_household_before_prev_yea + trust_army_mean +  -->
+<!--            estado, -->
+<!--          nussio_ag) -->
+
+<!-- # M1  -->
+<!-- m1_grf_dml <- dml_grf(outcome = 'loglynchpermio',  -->
+<!--         treatment = 'organized_lighting_mean',  -->
+<!--         covariates = c('trust_neighbors_mean', 'problem_lighting_mean'),  -->
+<!--         clustervar = 'estado_num', -->
+<!--         dataset = nussio_ag, -->
+<!--         target = 'all') -->
+
+<!-- # M2 -->
+<!-- m2_grf_dml <- dml_grf(outcome = 'loglynchpermio',  -->
+<!--         treatment = 'organized_lighting_mean',  -->
+<!--         covariates = c('trust_neighbors_mean', 'problem_lighting_mean', -->
+<!--                        'c_poptot', 'area', 'pconeval_poverty_pobreza_pob', 'coneval_gini_coeficientedegini',  -->
+<!--            'indigenous', 'c_poptot_norelpop', 'homirate', 'robberyrate'),  -->
+<!--         clustervar = 'estado_num', -->
+<!--         dataset = nussio_ag, -->
+<!--         target = 'all') -->
+
+<!-- # M3 -->
+<!-- m3_grf_dml <- dml_grf(outcome = 'loglynchpermio',  -->
+<!--         treatment = 'organized_lighting_mean',  -->
+<!--         covariates = c('trust_neighbors_mean', 'problem_lighting_mean', -->
+<!--                        'c_poptot', 'area', 'pconeval_poverty_pobreza_pob', 'coneval_gini_coeficientedegini',  -->
+<!--            'indigenous', 'c_poptot_norelpop', 'homirate', 'robberyrate', -->
+<!--            'victim_household_before_prev_yea', 'trust_army_mean'),  -->
+<!--         clustervar = 'estado_num', -->
+<!--         dataset = nussio_ag, -->
+<!--         target = 'all') -->
+
+<!-- # M4 -->
+<!-- m4_grf_dml <- m3_grf_dml -->
+
+<!-- compare_tbl(model_list = list(append(list(original = m1), m1_grf_dml), -->
+<!--                               append(list(original = m2), m2_grf_dml),  -->
+<!--                               append(list(original = m3), m3_grf_dml), -->
+<!--                               append(list(original = m4), m4_grf_dml)), -->
+<!--             treatment = 'organized_lighting_mean', -->
+<!--             tidy = T) %>% -->
+<!--   write_rds(here('replication', 'nussio_ag_rep.RDS')) -->
+
+<!-- # huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1), -->
+<!-- #                                   list(m2, grf_out2, dml_out2), -->
+<!-- #                                   list(m3, grf_out3, dml_out3), -->
+<!-- #                                   list(m4, grf_out4, dml_out4)), -->
+<!-- #                  treatment = 'organized_lighting_mean'), -->
+<!-- #                  statistics = NA) %>% -->
+<!-- #   huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>% -->
+<!-- #   huxtable::insert_row(c('Estado FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>% -->
+<!-- #   huxtable::insert_row(c('Estado clustered SE', 'Yes', 'Yes', 'Yes', 'No'), after = nrow(.) - 1) %>% -->
+<!-- #   huxtable::set_caption('Replication of Nussio (2024) Table 4: "Aggregate-Level Analysis: Community Ties and Lynching Rate"') %>% -->
+<!-- #   # huxtable::set_width(1) %>% -->
+<!-- #   # huxtable::set_all_padding(0) %>% -->
+<!-- #   write_rds(here('replication', 'nussio_ag_tab.RDS')) -->
+<!-- #  -->
+<!-- # read_rds(here('replication', 'nussio_ag_tab.RDS')) -->
+
+<!-- # names(grf_out1) <- c('estimate', 'std.error') -->
+<!-- # tidy(m1) %>% -->
+<!-- #   filter(term == 'organized_lighting_mean') %>% -->
+<!-- #   bind_rows(mutate(bind_rows(grf_out1))) %>% -->
+<!-- #   mutate(term = c('original', 'TMLE (GRF)'), p.value = p_val(estimate, std.error)) %>% -->
+<!-- #   huxtable::huxreg() -->
+
+<!-- ``` -->
+
+<!-- ```{r nussio-ne, eval = F} -->
+<!-- nussio_ne <- read_dta(here('replication/nussio_2024',  -->
+<!--                            'Mexico Municipality Panel Data.dta')) %>% -->
+<!--   # filter(if_all(c(loglynchpermio, organized_lighting_mean), ~!is.na(.x))) %>% -->
+<!--   mutate(cve_num = as.numeric(cve), -->
+<!--          year_num = year, -->
+<!--          year = as.factor(year), -->
+<!--          cve = cve, -->
+<!--          cve = as.factor(cve)) %>% -->
+<!--   # mutate(across(c(PARP, IT1, ED, BASURA), as.numeric), -->
+<!--   #        cve_col_num = as.integer(factor(cve_col))) %>% -->
+<!--   as_factor() -->
+
+<!-- # m1 <- lm(lynch_event ~ eq2017_250X2017 + year + cve, data = nussio_ne) %>% -->
+<!-- #   lmtest::coeftest(., vcov = sandwich::vcovCL(., ~cve)) -->
+
+<!-- # m1 <- fixest::feols(lynch_event ~ eq2017_250X2017 | year + cve,  -->
+<!-- #               data = nussio_ne) %>% -->
+<!-- #   summary(vcov = ~cve) %>% -->
+<!-- #   tidy() -->
+
+<!-- m1 <- data.frame(estimate = 0.108, std.error = 0.019) -->
+<!-- m2 <- data.frame(estimate = 0.113, std.error = 0.021) -->
+<!-- m3 <- data.frame(estimate = 0.087, std.error = 0.019) -->
+<!-- m4 <- data.frame(estimate = 0.126, std.error = 0.026) -->
+<!-- m5 <- data.frame(estimate = -0.010, std.error = 0.002) -->
+<!-- m6 <- data.frame(estimate = -0.009, std.error = 0.002) -->
+
+<!-- # M1 -->
+<!-- m1_grf_dml <- dml_grf(outcome = 'lynch_event',  -->
+<!--         treatment = 'eq2017_250X2017',  -->
+<!--         covariates = c('year_num'),  -->
+<!--         clustervar = 'cve_num', -->
+<!--         dataset = nussio_ne, -->
+<!--         target = 'treated', -->
+<!--         drop_na_grf = T) -->
+
+<!-- # M2 -->
+<!-- m2_grf_dml <- dml_grf(outcome = 'lynch_event',  -->
+<!--         treatment = 'eq2017_250X2017',  -->
+<!--         covariates = c('year_num', 'homicidefull', 'robofull', 'secuestrofull', 'inegi_infant_mort'),  -->
+<!--         clustervar = 'cve_num', -->
+<!--         dataset = nussio_ne, -->
+<!--         target = 'treated', -->
+<!--         drop_na_grf = T) -->
+
+<!-- # M3 -->
+<!-- m3_grf_dml <- dml_grf(outcome = 'lynch_event',  -->
+<!--         treatment = 'eq2017_damageX2017',  -->
+<!--         covariates = c('year_num'),  -->
+<!--         clustervar = 'cve_num', -->
+<!--         dataset = nussio_ne, -->
+<!--         target = 'treated', -->
+<!--         drop_na_grf = T) -->
+
+<!-- # M4 -->
+<!-- m4_grf_dml <- dml_grf(outcome = 'lynch_event',  -->
+<!--         treatment = 'eq2017_damageX2017',  -->
+<!--         covariates = c('year_num', 'homicidefull', 'robofull', 'secuestrofull', 'inegi_infant_mort'),  -->
+<!--         clustervar = 'cve_num', -->
+<!--         dataset = nussio_ne, -->
+<!--         target = 'all', -->
+<!--         drop_na_grf = T) -->
+
+<!-- # # M5 -->
+<!-- # m5_grf_dml <- dml_grf(outcome = 'lynch_event',  -->
+<!-- #         treatment = 'eq2017_dist100X2017',  -->
+<!-- #         covariates = c('year_num'),  -->
+<!-- #         clustervar = 'cve_num', -->
+<!-- #         dataset = nussio_ne, -->
+<!-- #         target = 'all', -->
+<!-- #         drop_na_grf = T) -->
+<!-- #  -->
+<!-- # # M6 -->
+<!-- # m6_grf_dml <- dml_grf(outcome = 'lynch_event',  -->
+<!-- #         treatment = 'eq2017_dist100X2017',  -->
+<!-- #         covariates = c('year_num', 'homicidefull', 'robofull', 'secuestrofull', 'inegi_infant_mort'),  -->
+<!-- #         clustervar = 'cve_num', -->
+<!-- #         dataset = nussio_ne, -->
+<!-- #         target = 'all', -->
+<!-- #         drop_na_grf = T) -->
+
+<!-- compare_tbl(model_list = list( -->
+<!--                  append(list(original = m1), m1_grf_dml), -->
+<!--                  append(list(original = m2), m2_grf_dml),  -->
+<!--                  append(list(original = m3), m3_grf_dml), -->
+<!--                  append(list(original = m4), m4_grf_dml), -->
+<!--             treatment = NULL, -->
+<!--             tidy = F) %>% -->
+<!--   write_rds(here('replication', 'nussio_ne_rep.RDS')) -->
+
+<!-- # Final table -->
+<!-- # huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1), -->
+<!-- #                                   list(m2, grf_out2, dml_out2), -->
+<!-- #                                   list(m3, grf_out3, dml_out3), -->
+<!-- #                                   list(m4, grf_out4, dml_out4), -->
+<!-- #                                   list(m5, grf_out5, dml_out5), -->
+<!-- #                                   list(m6, grf_out6, dml_out6)), -->
+<!-- #                              tidy = F), -->
+<!-- #                  statistics = NA) %>% -->
+<!-- #   huxtable::insert_row(c('Control variables', 'No', 'Yes', 'No', 'Yes', 'No', 'Yes'),  -->
+<!-- #                        after = nrow(.) - 1) %>% -->
+<!-- #   huxtable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"') %>% -->
+<!-- #   write_rds(here('replication', 'nussio_ne_tab.RDS')) -->
+<!-- #  -->
+<!-- # read_rds(here('replication', 'nussio_ne_tab.RDS')) -->
+<!-- ``` -->
+
+<!-- These simulations suggest that double robust methods with flexible machine learning algorithms may show some gains in bias reduction compared to traditional methods such as linear OLS regression.
+However, do these methods make a difference in practice?
+In this section, I replicate results from recent *American Sociological Review* articles using two double robust methods.
+I chose three papers that meet the following criteria: the authors were trying to estimate a causal effect, they used OLS or logistic regression, and they  posted replication code and data.
+-->
+
+<!-- The first paper I replicate is "Commitment through Sacrifice: How Longer Ramadan Fasting Strengthens Religiosity and Political Islam," by @aksoy_2022_commitment.
+Using the natural variation in daylight from year to year during Ramadan, the authors test the relationship between Ramadan fasting time and the vote share of Islamist political parties in Turkey.
+The second paper is "They Can’t All Be Stars: The Matthew Effect, Cumulative Status Bias, and Status Persistence in NBA All-Star Elections" [@biegert_2023_they].
+The authors use detailed records on NBA players' performance to study the effect of the previous year's All-Star nomination on being re-nominated in the current year.
+Lastly, I replicate "The 'Dark Side' of Community Ties: Collective Action and Lynching in Mexico" [@nussio_2024_dark].
+The author estimates the effect of community ties in Mexico on individual participation in lynching or lynching rates at aggregate levels.
+-->
+
+<!-- ## Evaluation Strategy -->
+
+<!-- I replicate these papers using two double robust methods with machine learning.
+First, I use AIPW in conjunction with generalized random forests (GRF) using the `grf` package [@tibshirani_2024_grf].
+Second, I use a partially linear model for DML with a SuperLearner that, like above, harnesses ensemble learning with GLM, glmnet, and XGBoost, using the `DoubleML` package [@bach_2022_doubleml].^[In the Supplementary Material, I present the results of using these packages to estimate the full set of simulations shown above.
+Results are fairly similar to my own R code, though computation time is notably faster.] Note that AIPW with GRF allows for heterogeneous treatment effects, while this version of DML does not.
+I use packages rather than my own R code for two reasons.
+First, these packages calculate asymptotic standard errors without the need for bootstrapping, allowing straightforward comparison with the statistical significance of results in the original papers.
+Second, both packages allow clustering of standard errors, which all three papers employ.
+-->
+
+<!-- Two aspects of these replications deserve further explanation.
+First, it is common in social science to drop observations with missing data for some covariates, a technique called the "complete case method" or "listwise deletion." Two of these papers deal with missing data in this way -- by decreasing the sample size.
+Some machine learning methods, on the other hand, use missing data informatively [@mayer_2020_doubly]; the `grf` package allows covariates (but not the outcome or treatment assignment) to be missing, using missingness itself as a splitting criterion in growing trees.
+Hence for data with moderate levels of missingness, I allow `grf` to work with the entire dataset.
+For `DoubleML`, I use the same samples as in the original papers -- in these cases only observations with complete cases for a given regression model.
+An exception is Table 5 for @nussio_2024_dark, where the number of observations with missing control variables is far larger than the number without missing data; hence I drop incomplete cases for all analyses.
+I describe the exact procedures for handling missingness in the notes for each table of results in the Supplementary Material.
+-->
+
+<!-- The second aspect is fixed effects.
+Fixed effects are commonly used in linear models; beginning with a categorical variable with $k$ group labels, one hot encoding converts this to $k-1$ dichotomous variables, and these are entered into the regression linearly.
+These are meant to account for between-group differences [@firebaugh_2013_fixed].
+In the papers replicated here, @aksoy_2022_commitment use these types of fixed effects in all models, @biegert_2023_they use no fixed effects, and @nussio_2024_dark uses fixed effects in some models (details are in the table notes in the Supplementary Material).
+In many machine learning methods, categorical variables cannot be easily incorporated [@johannemann_2021_sufficient].
+Adding a large number of information-poor dichotomous variables to flexible tree methods like GRF and XGBoost does not have a fixed effects interpretation, since these methods can can interact any variable with any other and apply non-linear transformations.
+In cases where a researcher would want to use fixed effects for time and other variables with a natural ordering, these can be entered as a single continuous variable, whose effect the model will allow to vary nonlinearly.
+But categorical variables without a natural ordering -- such as individual or group fixed effects -- need special treatment.
+Recently, @clarke_2024_double have developed an extension to DML that incorporates group-level fixed effects.
+In the first set analyses, I do not adjust for individual or group fixed effects in the machine learning replications (even when the original paper's model does), but in the final part of this section of the Supplementary Material, I present two of Clarke and Polselli's approaches to incorporating fixed effects in DML.
+Results change very little from standard DML.
+-->
+
+<!-- ## Results -->
+
+<!-- ```{r replications, fig.height = 8, fig.cap = 'Replications of ASR papers using double robust machine learning methods. Bars represent 95-percent asymptotic confidence intervals.'} -->
+<!-- aksoy_list <- readRDS(here('replication', 'aksoy_rep.RDS'))  -->
+<!-- aksoy_list[[1]]$model <- '(1) Base' -->
+<!-- aksoy_list[[2]]$model <- '(2) Covariates' -->
+<!-- aksoy_list[[3]]$model <- '(3) Lagged dependent variable' -->
+
+<!-- biegert_list <- readRDS(here('replication', 'biegert_rep.RDS'))  -->
+<!-- biegert_list[[1]]$model <- '(1) No controls' -->
+<!-- biegert_list[[2]]$model <- '(2) Baseline confounders' -->
+<!-- biegert_list[[3]]$model <- '(3) Prior situation + performance' -->
+<!-- biegert_list[[4]]$model <- '(4) Current performance' -->
+<!-- biegert_list[[5]]$model <- '(5) Current situation' -->
+
+<!-- nussio_ind_list <- readRDS(here('replication', 'nussio_ind_rep.RDS'))  -->
+<!-- nussio_ind_list[[1]]$model <- '(1) Base' -->
+<!-- nussio_ind_list[[2]]$model <- '(2) Some controls' -->
+<!-- nussio_ind_list[[3]]$model <- '(3) All controls' -->
+<!-- nussio_ind_list[[4]]$model <- '(4) Geographical FE' -->
+
+<!-- nussio_ag_list <- readRDS(here('replication', 'nussio_ag_rep.RDS'))  -->
+<!-- nussio_ag_list[[1]]$model <- '(1) Base' -->
+<!-- nussio_ag_list[[2]]$model <- '(2) Some controls' -->
+<!-- nussio_ag_list[[3]]$model <- '(3) All controls' -->
+<!-- nussio_ag_list[[4]]$model <- '(4) Geographical FE' -->
+
+<!-- nussio_ne_list <- readRDS(here('replication', 'nussio_ne_rep.RDS'))  -->
+<!-- nussio_ne_list[[1]]$model <- '(1) Within 250 km of earthquake' -->
+<!-- nussio_ne_list[[2]]$model <- '(2) Within 250 km of earthquake, controls' -->
+<!-- nussio_ne_list[[3]]$model <- '(3) Earthquake damage' -->
+<!-- nussio_ne_list[[4]]$model <- '(4) Earthquake damage, controls' -->
+
+<!-- bind_rows( -->
+<!--   mutate(bind_rows(aksoy_list), paper = 'A. Aksoy et al. (2022)'), -->
+<!--   mutate(bind_rows(biegert_list), paper = 'B. Biegert et al. (2022)'), -->
+<!--   mutate(bind_rows(nussio_ind_list), paper = 'C. Nussio et al. (2024) Table 2: Individual'), -->
+<!--   mutate(bind_rows(nussio_ag_list), paper = 'D. Nussio et al. (2024) Table 4: Aggregate'), -->
+<!--   mutate(bind_rows(nussio_ne_list), paper = 'E. Nussio et al. (2024) Table 5: Natural Experiment') -->
+<!--   ) %>% -->
+<!--   filter(term %in% c('Original', 'AIPW (GRF)', 'DML (SuperLearner)')) %>% -->
+<!--   mutate(term = factor(term, levels = unique({.$term})), -->
+<!--          paper = factor(paper, levels = unique({paper})), -->
+<!--          model = factor(model, levels = rev(unique({.$model})))) %>% -->
+<!--   ggplot(aes(x = model, y = estimate, color = term, shape = term)) + -->
+<!--   geom_hline(yintercept = 0, color = 'grey') + -->
+<!--   geom_pointrange(position = position_dodge(-0.7), -->
+<!--                   aes(ymin = estimate - 1.96*std.error, ymax = estimate + 1.96*std.error)) +  -->
+<!--   coord_flip() + -->
+<!--   facet_wrap(~paper, scales = 'free', ncol = 1) + -->
+<!--   labs(x = '', y = '') + -->
+<!--   theme(legend.position = 'bottom') -->
+<!-- ``` -->
+
+<!-- Results of the replications are shown in Figure \@ref(fig:replications), with tables of coefficients and explanatory notes in the Supplementary Material.
+For each paper, I replicate the main results.
+I do not replicate models testing mechanisms, interactions, mediators, or placebos.
+-->
+
+<!-- The first paper, "Commitment through Sacrifice: How Longer Ramadan Fasting Strengthens Religiosity and Political Islam" [@aksoy_2022_commitment], finds an OLS coefficient of about 7, implying a half-hour increase in fasting time is associated with a 3.5 percentage point increase in Islamist vote share.
+As shown in Figure \@ref(fig:replications) Panel A, coefficients using the double robust methods are noticeably smaller (though not significantly different from the original coefficients).
+In Model 2, which includes covariates, the main coefficient is nonsignificant at the 5-percent level.
+In both cases, the double robust estimates are more precise, with smaller standard errors than the OLS results.
+-->
+
+<!-- The second paper, "They Can’t All Be Stars: The Matthew Effect, Cumulative Status Bias, and Status Persistence in NBA All-Star Elections" [@biegert_2023_they].
+The authors use logistic regression to estimate the effect of the previous year's All-Star nomination on being re-nominated in the current year.
+Panel B of Figure \@ref(fig:replications) shows the average marginal effects from the authors' original regressions alongside the double robust replications.
+Models 1 and 2 do not control for previous performance and find that a previous year's nomination increases the likelihood of being nominated by 45 to 60 percentage points.
+Model 3 isolates the effect of the previous year's nomination from performance in the previous year; the original paper found a much smaller coefficient once these controls were incorporated, giving a marginal effect of about 5 percentage points, but the double robust methods estimate large effect sizes, at 30 and 59 percentage points for AIPW (GRF) and DML (SuperLearner), respectively.
+Models 4 and 5 control for other current factors, and double robust estimates are somewhat smaller than in Model 3 but still much larger than the original paper's estimates.
+-->
+
+<!-- The third and final paper for replication is "The 'Dark Side' of Community Ties: Collective Action and Lynching in Mexico" [@nussio_2024_dark].
+I present his three main analyses as separate panels.
+In his first analyses, he looks at individual propensity to participate in a lynching, using the log number of names of people a respondent knows in his or her colonia (neighborhood) in Mexico City as the independent variable.
+In OLS models with and without controls, the author finds a coefficient of about 0.03 for the logged variable, implying that a one-percent increase in names known is associated with about 0.0003 percentage points greater likelihood of participating in a lynching.
+As shown in Panel C of Figure \@ref(fig:replications), For AIPW (GRF), coefficients and statistical significance are very similar to the original OLS coefficients.
+DML (SuperLearner), however, shows nonsignificant or negative effects.
+-->
+
+<!-- Panel D of Figure \@ref(fig:replications) replicates Nussio's [-@nussio_2024_dark] second analysis, which aggregates to the municipal level.
+Models estimate the effect of neighborly cooperation -- operationalized by the proportion of respondents who think that most neighbors help each other in problems related to electric lighting -- on the log municipal lynching rate.
+The original OLS estimate was fairly stable across models with controls, at about a one percentage point increase in neighborly cooperation associated with a two-percent increase in the lynching rate [$\exp(2/100) = 1.02$].
+This estimate is fairly stable across estimators, though (as shown in the Supplementary Material) this is one case where incorporating fixed effects in the DML models reduces coefficient sizes.
+-->
+
+<!-- Finally, Panel E of Figure \@ref(fig:replications) replicates Nussio's [-@nussio_2024_dark] natural experiment, where he estimates the effect of the Puebla earthquake on September 19, 2017, on the number of lynching events in a municipality, using panel data from 2000 to 2020.
+The original OLS models found that municipalities within 250 km of the earthquake or that experienced earthquake damage experienced an increase of about 0.1 in the number of lynchings in years after 2017 (the mean yearly lynchings per municipality is 0.034).
+While models for AIPW (GRF) are fairly similar to the original OLS estimates, DML (SuperLearner) estimates are double the original estimates.
+-->
+
+<!-- These replications show that results from the original OLS or logistic regressions that these papers employed are fairly robust.
+In most cases, effect sign and statistical significance are consistent across the original and double robust estimators.
+Notably, effect sizes for @aksoy_2022_commitment in the double robust models are smaller than the OLS estimates, reaching nonsignificance in one case.
+DML (SuperLearner) estimates for Nussio's [-@nussio_2024_dark] individual analysis change sign and significance, while the AIPW (GRF) estimates are close to the OLS estimates.
+However, the simulation results presented in the previous section suggested that the DML (SuperLearner) estimator has higher RMSE than both OLS and AIPW (GRF) (Figure \@ref(fig:dorie-results-rmse)), so perhaps the original results are reliable.^[The Supplementary Material shows that the DoubleML package with the SuperLearner has higher bias and RMSE in the simulations than my own R code.] Overall, these replications highlight the importance of testing the robustness of estimates to different models; double robust, machine learning methods sometimes do produce substantively different results from traditional methods.
+-->
+
+<!-- ## Replications with Fixed Effects -->
+
+<!-- The tables below present estimates from the *ASR* replications discussed above, but with the addition of two other models implementing methods proposed by @clarke_2024_double that incorporate individual or group fixed effects into DML.
 The authors' package, `XTDML`, builds on the `DoubleML` package.
@@
 @nussio_2024_dark uses fixed effects in the fourth model in Tables 2 and 4 and in all models in Table 5.
-
-```{r rep-aksoy}
-readRDS(here('replication', 'aksoy_rep.RDS')) %>%
-  huxtable::huxreg(statistics = NA,
-                   note = '{stars}.
+-->
+
+<!-- ```{r rep-aksoy} -->
+<!-- readRDS(here('replication', 'aksoy_rep.RDS')) %>% -->
+<!--   huxtable::huxreg(statistics = NA, -->
+<!--                    note = '{stars}.
 Covariates include GDP growth, population, turnout, number of parliamentary seats in province in Model 2 and 3; Models 3 also adjusts for the lagged value of the dependent variable (i.e., one election lagged Islamic votes); cluster robust standard errors are in parentheses.
-The AIPW (GRF) model does not drop incomplete observations.') %>%
-  huxtable::insert_row(c('Covariates', 'No', rep('Yes', 2)), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Lagged dependent variable', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Election year fixed effects', 'Yes', 'Yes', 'Yes'), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Province fixed effects', 'Yes', 'Yes', 'Yes'), after = nrow(.) - 1) %>%
-  huxtable::set_top_border((nrow(.)-4):(nrow(.)-1), value = 0) %>%
-  huxtable::set_top_border((nrow(.)-4), 2:4) %>%
-  huxtable::set_caption('Replication of Aksoy et al.
-(2022) Table 2, models for outcome of Islamic Votes: "Effect of Fasting Hours (Daylength) during Ramadan on Various Outcome Variables Based on Regression Models That Include Fixed Effects for Provinces and Election Years"') %>%
-  huxtable::set_width(.8) %>%
-  huxtable::set_all_padding(0) %>%
-  huxtable::set_latex_float('h!')
-
-# read_rds(here('replication', 'aksoy_tab.RDS')) %>%
-#   huxtable::as_flextable() %>%
-#   flextable::hline(7:8, 1:4, border = officer::fp_border(width = 0)) %>%
-#   flextable::hline(7, 2:4) %>%
-#   flextable::hline(9) %>%
-#   flextable::set_caption('Replication of Aksoy et al.
-(2022) Table 2, models for outcome of Islamic Votes: "Effect of Fasting Hours (Daylength) during Ramadan on Various Outcome Variables Based on Regression Models That Include Fixed Effects for Provinces and Election Years"')
-```
-
-\newpage
-
-```{r rep-biegert}
-readRDS(here('replication', 'biegert_rep.RDS')) %>%
-  huxtable::huxreg(statistics = NA,
-                   note = '{stars}.
+The AIPW (GRF) model does not drop incomplete observations.') %>% -->
+<!--   huxtable::insert_row(c('Covariates', 'No', rep('Yes', 2)), after = nrow(.) - 1) %>% -->
+<!--   huxtable::insert_row(c('Lagged dependent variable', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>% -->
+<!--   huxtable::insert_row(c('Election year fixed effects', 'Yes', 'Yes', 'Yes'), after = nrow(.) - 1) %>% -->
+<!--   huxtable::insert_row(c('Province fixed effects', 'Yes', 'Yes', 'Yes'), after = nrow(.) - 1) %>% -->
+<!--   huxtable::set_top_border((nrow(.)-4):(nrow(.)-1), value = 0) %>% -->
+<!--   huxtable::set_top_border((nrow(.)-4), 2:4) %>% -->
+<!--   huxtable::set_caption('Replication of Aksoy et al.
+(2022) Table 2, models for outcome of Islamic Votes: "Effect of Fasting Hours (Daylength) during Ramadan on Various Outcome Variables Based on Regression Models That Include Fixed Effects for Provinces and Election Years"') %>% -->
+<!--   huxtable::set_width(.8) %>% -->
+<!--   huxtable::set_all_padding(0) %>% -->
+<!--   huxtable::set_latex_float('h!') -->
+
+<!-- # read_rds(here('replication', 'aksoy_tab.RDS')) %>% -->
+<!-- #   huxtable::as_flextable() %>% -->
+<!-- #   flextable::hline(7:8, 1:4, border = officer::fp_border(width = 0)) %>% -->
+<!-- #   flextable::hline(7, 2:4) %>% -->
+<!-- #   flextable::hline(9) %>% -->
+<!-- #   flextable::set_caption('Replication of Aksoy et al.
+(2022) Table 2, models for outcome of Islamic Votes: "Effect of Fasting Hours (Daylength) during Ramadan on Various Outcome Variables Based on Regression Models That Include Fixed Effects for Provinces and Election Years"') -->
+<!-- ``` -->
+
+<!-- \newpage -->
+
+<!-- ```{r rep-biegert} -->
+<!-- readRDS(here('replication', 'biegert_rep.RDS')) %>% -->
+<!--   huxtable::huxreg(statistics = NA, -->
+<!--                    note = '{stars}.
 With no control variables, Model 1 could not be estimated using DML with a SuperLearner.
@@
 None of the original models includes player fixed effects.
-The AIPW (GRF) model does not drop incomplete observations.') %>%
-  huxtable::insert_row(c('Baseline confounders', 'No', rep('Yes', 4)), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Prior situation + performance', rep('No', 2), rep('Yes', 3)), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Current performance', rep('No', 3), rep('Yes', 2)), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Current situation', rep('No', 4), rep('Yes', 1)), after = nrow(.) - 1) %>%
-  # huxtable::insert_row(c('Cumul. AS + cumul. mediators', rep('No', 5), 'Yes'), after = nrow(.) - 1) %>%
-  huxtable::set_top_border((nrow(.)-4):(nrow(.)-1), value = 0) %>%
-  huxtable::set_top_border((nrow(.)-4), 2:6) %>%
-  huxtable::set_caption('Replication of Biegert et al. (2023) Table 3: "Average Marginal Effects from Logistic Regression Models of All-Star Nomination"') %>%
-  huxtable::set_width(1) %>%
-  huxtable::set_all_padding(0) %>%
-  huxtable::set_latex_float('h!')
-
-# read_rds(here('replication', 'biegert_tab.RDS')) %>%
-#   huxtable::as_flextable() %>%
-#   flextable::hline(7:11, 1:7, border = officer::fp_border(width = 0)) %>%
-#   flextable::hline(7, 2:7) %>%
-#   flextable::padding(padding = 0, part = "all") %>% 
-#   flextable::autofit() %>%
-#   flextable::hline(12) %>%
-#   flextable::set_caption('Replication of Biegert et al. (2023) Table 3: "Average Marginal Effects from Logistic Regression Models of All-Star Nomination"')
-```
-
-\newpage
-
-```{r rep-nussio-ind}
-readRDS(here('replication', 'nussio_ind_rep.RDS')) %>%
-  huxtable::huxreg(statistics = NA,
-                   note = "{stars}.
+The AIPW (GRF) model does not drop incomplete observations.') %>% -->
+<!--   huxtable::insert_row(c('Baseline confounders', 'No', rep('Yes', 4)), after = nrow(.) - 1) %>% -->
+<!--   huxtable::insert_row(c('Prior situation + performance', rep('No', 2), rep('Yes', 3)), after = nrow(.) - 1) %>% -->
+<!--   huxtable::insert_row(c('Current performance', rep('No', 3), rep('Yes', 2)), after = nrow(.) - 1) %>% -->
+<!--   huxtable::insert_row(c('Current situation', rep('No', 4), rep('Yes', 1)), after = nrow(.) - 1) %>% -->
+<!--   # huxtable::insert_row(c('Cumul. AS + cumul. mediators', rep('No', 5), 'Yes'), after = nrow(.) - 1) %>% -->
+<!--   huxtable::set_top_border((nrow(.)-4):(nrow(.)-1), value = 0) %>% -->
+<!--   huxtable::set_top_border((nrow(.)-4), 2:6) %>% -->
+<!--   huxtable::set_caption('Replication of Biegert et al. (2023) Table 3: "Average Marginal Effects from Logistic Regression Models of All-Star Nomination"') %>% -->
+<!--   huxtable::set_width(1) %>% -->
+<!--   huxtable::set_all_padding(0) %>% -->
+<!--   huxtable::set_latex_float('h!') -->
+
+<!-- # read_rds(here('replication', 'biegert_tab.RDS')) %>% -->
+<!-- #   huxtable::as_flextable() %>% -->
+<!-- #   flextable::hline(7:11, 1:7, border = officer::fp_border(width = 0)) %>% -->
+<!-- #   flextable::hline(7, 2:7) %>% -->
+<!-- #   flextable::padding(padding = 0, part = "all") %>%  -->
+<!-- #   flextable::autofit() %>% -->
+<!-- #   flextable::hline(12) %>% -->
+<!-- #   flextable::set_caption('Replication of Biegert et al. (2023) Table 3: "Average Marginal Effects from Logistic Regression Models of All-Star Nomination"') -->
+<!-- ``` -->
+
+<!-- \newpage -->
+
+<!-- ```{r rep-nussio-ind} -->
+<!-- readRDS(here('replication', 'nussio_ind_rep.RDS')) %>% -->
+<!--   huxtable::huxreg(statistics = NA, -->
+<!--                    note = "{stars}.
 Data come from a representative survey of residents of Mexico City conducted in February 2022.
@@
 Model 4 adds colonia fixed effects.
-The AIPW (GRF) model does not drop incomplete observations.") %>%
-  huxtable::insert_row(c('Colonia FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>%
-  huxtable::set_top_border((nrow(.)-2):(nrow(.)-1), value = 0) %>%
-  huxtable::set_top_border((nrow(.)-2), 2:5) %>%
-  huxtable::set_caption('Replication of Nussio (2024) Table 2: "Individual-Level Analysis: Community Ties and Lynching Participation"') %>%
-  huxtable::set_width(.8) %>%
-  huxtable::set_all_padding(0) %>%
-  huxtable::set_latex_float('h!')
-
-# read_rds(here('replication', 'nussio_ind_tab.RDS')) %>%
-#   huxtable::as_flextable() %>%
-#   flextable::hline(7:8, 1:5, border = officer::fp_border(width = 0)) %>%
-#   flextable::hline(7, 2:5) %>%
-#   flextable::hline(9) %>%
-#   flextable::set_caption('Replication of Nussio (2024) Table 2: "Individual-Level Analysis: Community Ties and Lynching Participation"')
-```
-
-\newpage
-
-```{r rep-nussio-ag}
-readRDS(here('replication', 'nussio_ag_rep.RDS')) %>%
-  huxtable::huxreg(statistics = NA,
-                   note = "{stars}.
+The AIPW (GRF) model does not drop incomplete observations.") %>% -->
+<!--   huxtable::insert_row(c('Colonia FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>% -->
+<!--   huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>% -->
+<!--   huxtable::set_top_border((nrow(.)-2):(nrow(.)-1), value = 0) %>% -->
+<!--   huxtable::set_top_border((nrow(.)-2), 2:5) %>% -->
+<!--   huxtable::set_caption('Replication of Nussio (2024) Table 2: "Individual-Level Analysis: Community Ties and Lynching Participation"') %>% -->
+<!--   huxtable::set_width(.8) %>% -->
+<!--   huxtable::set_all_padding(0) %>% -->
+<!--   huxtable::set_latex_float('h!') -->
+
+<!-- # read_rds(here('replication', 'nussio_ind_tab.RDS')) %>% -->
+<!-- #   huxtable::as_flextable() %>% -->
+<!-- #   flextable::hline(7:8, 1:5, border = officer::fp_border(width = 0)) %>% -->
+<!-- #   flextable::hline(7, 2:5) %>% -->
+<!-- #   flextable::hline(9) %>% -->
+<!-- #   flextable::set_caption('Replication of Nussio (2024) Table 2: "Individual-Level Analysis: Community Ties and Lynching Participation"') -->
+<!-- ``` -->
+
+<!-- \newpage -->
+
+<!-- ```{r rep-nussio-ag} -->
+<!-- readRDS(here('replication', 'nussio_ag_rep.RDS')) %>% -->
+<!--   huxtable::huxreg(statistics = NA, -->
+<!--                    note = "{stars}.
 Models estimate the effect of neighborly cooperation -- operationalized by the proportion of respondents who think that most neighbors help each other in problems related to electric lighting -- on the log municipal lynching rate.
@@
 Municipality clustered standard errors are in paratheses.
-The AIPW (GRF) model does not drop incomplete observations.") %>%
-  huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Estado FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
-  huxtable::insert_row(c('Estado clustered SE', 'Yes', 'Yes', 'Yes', 'No'), after = nrow(.) - 1) %>%
-  huxtable::set_top_border((nrow(.)-3):(nrow(.)-1), value = 0) %>%
-  huxtable::set_top_border((nrow(.)-3), 2:5) %>%
-  huxtable::set_caption('Replication of Nussio (2024) Table 4: "Aggregate-Level Analysis: Community Ties and Lynching Rate"') %>%
-  huxtable::set_width(.8) %>%
-  huxtable::set_all_padding(0) %>%
-  huxtable::set_latex_float('h!')
-
-# read_rds(here('replication', 'nussio_ag_tab.RDS')) %>%
-#   huxtable::as_flextable() %>%
-#   flextable::hline(7:9, 1:5, border = officer::fp_border(width = 0)) %>%
-#   flextable::hline(7, 2:5) %>%
-#   flextable::hline(10) %>%
-#   flextable::set_caption('Replication of Nussio (2024) Table 4: "Aggregate-Level Analysis: Community Ties and Lynching Rate"')
-```
-
-\newpage
-
-```{r rep-nussio-ne}
-readRDS(here('replication', 'nussio_ne_rep.RDS')) %>%
-  huxtable::huxreg(statistics = NA,
-                   note = "{stars}.
+The AIPW (GRF) model does not drop incomplete observations.") %>% -->
+<!--   huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>% -->
+<!--   huxtable::insert_row(c('Estado FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>% -->
+<!--   huxtable::insert_row(c('Estado clustered SE', 'Yes', 'Yes', 'Yes', 'No'), after = nrow(.) - 1) %>% -->
+<!--   huxtable::set_top_border((nrow(.)-3):(nrow(.)-1), value = 0) %>% -->
+<!--   huxtable::set_top_border((nrow(.)-3), 2:5) %>% -->
+<!--   huxtable::set_caption('Replication of Nussio (2024) Table 4: "Aggregate-Level Analysis: Community Ties and Lynching Rate"') %>% -->
+<!--   huxtable::set_width(.8) %>% -->
+<!--   huxtable::set_all_padding(0) %>% -->
+<!--   huxtable::set_latex_float('h!') -->
+
+<!-- # read_rds(here('replication', 'nussio_ag_tab.RDS')) %>% -->
+<!-- #   huxtable::as_flextable() %>% -->
+<!-- #   flextable::hline(7:9, 1:5, border = officer::fp_border(width = 0)) %>% -->
+<!-- #   flextable::hline(7, 2:5) %>% -->
+<!-- #   flextable::hline(10) %>% -->
+<!-- #   flextable::set_caption('Replication of Nussio (2024) Table 4: "Aggregate-Level Analysis: Community Ties and Lynching Rate"') -->
+<!-- ``` -->
+
+<!-- \newpage -->
+
+<!-- ```{r rep-nussio-ne} -->
+<!-- readRDS(here('replication', 'nussio_ne_rep.RDS')) %>% -->
+<!--   huxtable::huxreg(statistics = NA, -->
+<!--                    note = "{stars}.
 Models estimate the effect of the Puebla earthquake on September 19, 2017, on the number of lynching events.
@@
 All models drop incomplete observations; Models 1, and 3 have 51,597 observations, while Models 2, and 4 have 17,225 observations.
-Due to complications with continuous treatment effects, I do not present the original Models 5 and 6, where the independent variable was distance from the earthquake.") %>%
-  huxtable::insert_row(c('Control variables', 'No', 'Yes', 'No', 'Yes'), 
-                       after = nrow(.) - 1) %>%
-  huxtable::set_top_border((nrow(.)-1):(nrow(.)-1), value = 0) %>%
-  huxtable::set_top_border((nrow(.)-1), 2:5) %>%
-  huxtable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"') %>%
-  huxtable::set_width(.8) %>%
-  huxtable::set_all_padding(0) %>%
-  huxtable::set_latex_float('h!')
-
-# Final table
-# huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1),
-#                                   list(m2, grf_out2, dml_out2),
-#                                   list(m3, grf_out3, dml_out3),
-#                                   list(m4, grf_out4, dml_out4),
-#                                   list(m5, grf_out5, dml_out5),
-#                                   list(m6, grf_out6, dml_out6)),
-#                              tidy = F),
-#                  statistics = NA) %>%
-#   huxtable::insert_row(c('Control variables', 'No', 'Yes', 'No', 'Yes', 'No', 'Yes'), 
-#                        after = nrow(.) - 1) %>%
-#   huxtable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"') %>%
-
-# read_rds(here('replication', 'nussio_ne_tab.RDS')) %>%
-#   huxtable::as_flextable() %>%
-#   flextable::hline(7, 1:7, border = officer::fp_border(width = 0)) %>%
-#   flextable::hline(7, 2:7) %>%
-#   flextable::hline(8) %>%
-#   flextable::padding(padding = 0, part = "all") %>% 
-#   flextable::autofit() %>%
-#   flextable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"')
-```
-
-\newpage
-
-# References
-
-<div id="refs"></div>
+Due to complications with continuous treatment effects, I do not present the original Models 5 and 6, where the independent variable was distance from the earthquake.") %>% -->
+<!--   huxtable::insert_row(c('Control variables', 'No', 'Yes', 'No', 'Yes'),  -->
+<!--                        after = nrow(.) - 1) %>% -->
+<!--   huxtable::set_top_border((nrow(.)-1):(nrow(.)-1), value = 0) %>% -->
+<!--   huxtable::set_top_border((nrow(.)-1), 2:5) %>% -->
+<!--   huxtable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"') %>% -->
+<!--   huxtable::set_width(.8) %>% -->
+<!--   huxtable::set_all_padding(0) %>% -->
+<!--   huxtable::set_latex_float('h!') -->
+
+<!-- # Final table -->
+<!-- # huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1), -->
+<!-- #                                   list(m2, grf_out2, dml_out2), -->
+<!-- #                                   list(m3, grf_out3, dml_out3), -->
+<!-- #                                   list(m4, grf_out4, dml_out4), -->
+<!-- #                                   list(m5, grf_out5, dml_out5), -->
+<!-- #                                   list(m6, grf_out6, dml_out6)), -->
+<!-- #                              tidy = F), -->
+<!-- #                  statistics = NA) %>% -->
+<!-- #   huxtable::insert_row(c('Control variables', 'No', 'Yes', 'No', 'Yes', 'No', 'Yes'),  -->
+<!-- #                        after = nrow(.) - 1) %>% -->
+<!-- #   huxtable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"') %>% -->
+
+<!-- # read_rds(here('replication', 'nussio_ne_tab.RDS')) %>% -->
+<!-- #   huxtable::as_flextable() %>% -->
+<!-- #   flextable::hline(7, 1:7, border = officer::fp_border(width = 0)) %>% -->
+<!-- #   flextable::hline(7, 2:7) %>% -->
+<!-- #   flextable::hline(8) %>% -->
+<!-- #   flextable::padding(padding = 0, part = "all") %>%  -->
+<!-- #   flextable::autofit() %>% -->
+<!-- #   flextable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"') -->
+<!-- ``` -->
+
+<!-- \newpage -->
+
+<!-- # References -->
+
+<!-- <div id="refs"></div> -->

### 2025-05-29 draft/ms-adj-draft.Rmd
revision

@@
 It is also unclear whether these methods actually outperform more traditional methods in finite samples.
-This paper has two aims: It is a guide to some of the latest methods in double robust, flexible covariate adjustment using machine learning, and it compares these methods to more traditional statistical methods and flexible \"single robust\" methods.
-It does this by using both simulated data where the treatment effect estimate is known, and then by replicating some prominent articles in sociology that use simpler methods.
+This paper has two aims: It is a guide to some of the latest methods in double robust, flexible covariate adjustment using machine learning, and it compares these methods to more traditional statistical methods and flexible \"single robust\" methods using simulated, cross-sectional data where the treatment effect is known.
 Double robust methods covered include Augmented Inverse Probability Weighting (AIPW), Targeted Maximum Likelihood Estimation (TMLE), and Double/Debiased Machine Learning (DML).
-Results suggest that some of these methods do outperform traditional methods in a wide range of simulations, but only slightly.
-In particular, the top performers are TMLE and AIPW in conjunction with flexible machine learning estimators.
-But G-computation with the same flexible estimators obtains almost identical results, and simple regression methods have only slightly higher bias and are much more computationally efficient.
-In the article replications, the application of double robust methods substantively changes some, but not all, of the results, highlighting the importance of comparing performance from multiple estimators."
+Results suggest that some of these methods do outperform traditional methods in a wide range of simulations, but not dramatically.
+The top performers are TMLE and AIPW in conjunction with flexible machine learning estimators, but G-computation with the same flexible estimators obtains almost identical results, and standard regression methods have only slightly higher bias.
+Researchers should opt for estimators that are robust to heterogeneous treatment effects, regardless of whether they are double robust."
 
@@
 library(patchwork)
+library(DoubleML)
+library(mlr3)
+library(mlr3pipelines)
+library(mlr3learners)
+library(mlr3extralearners)
 library(haven)
@@
 In causal inference, functional form misspecification of underlying models can bias estimates of treatment effects [@hernan_2020_causal; @morgan_2015_counterfactuals].
-There have been two important developments that attempt to overcome this.
+There have been two important advances that attempt to overcome this.
 First, methodologists have developed machine learning methods that allow greater flexibility in estimation, adjusting for covariates in data-driven, complex ways [@balzer_2021_invited; @brand_2023_recent].
@@
 
-Second, this paper evaluates these methods.
-They are tested on simulations from @dorie_2019_automated, which cover a range of data-generating processes where ignorability holds -- i.e., there are no unmeasured confounders.
-In the simulations, double robust methods are compared to "single robust" methods (i.e., ones with one nuisance model).
-These include traditional or simpler statistical methods commonly used by social scientists: ordinary least squares (OLS) regression, matching on propensity scores estimated from logistic regression (PSM), and inverse probability weighting (IPW).
-They are also compared to two more flexible methods that may overcome the misspecification issues that double robust methods aim to overcome: G-computation and the Lin estimator [@lin_2013_agnostic].
-Lastly, I use two of the double robust methods to replicate analyses from three recent *American Sociological Review* (*ASR*) papers that use OLS or logistic regression to estimate causal effects.
-
-Results from simulations where ignorability holds show that some double robust methods outperform traditional statistical methods, but only slightly.
-AIPW and TMLE perform the best, at least when used in conjunction with flexible machine learning algorithms, while DML (in its partially linear form) does slightly worse than traditional methods.
+Second, this paper evaluates these methods, testing them on simulations from @dorie_2019_automated that cover a range of data-generating processes where ignorability holds -- meaning there are no unmeasured confounders.
+In the simulations, double robust methods are compared to "single robust" methods (i.e., ones with one nuisance model), including traditional or simpler statistical methods commonly used by social scientists: ordinary least squares (OLS) regression, matching on propensity scores estimated from logistic regression (PSM), and inverse probability weighting (IPW).
+They are also compared to two more flexible methods that may overcome the misspecification issues that motivate double robust methods: G-computation and the Lin estimator.
+G-computation models the outcome in separate models for treated and untreated units, then predicts the average difference between these for the full sample [@robins_1986_new].
+The Lin estimator interacts treatment with mean-centered covariates in an OLS regression [@lin_2013_agnostic].
+
+Results show that some double robust methods outperform traditional statistical methods, but not dramatically.
+AIPW and TMLE perform the best, at least when used in conjunction with flexible machine learning algorithms, while DML does slightly worse than traditional methods, at least in its partially linear form that is not robust to heterogeneous treatment effects.
 G-computation with flexible machine learning performs as well as the lowest-error double robust methods.
-Despite their lower average error, the computation times of these flexible methods are high.
-With its still relatively low error and much faster computation time, OLS remains a sensible choice as an estimator, and the Lin estimator -- which is as quick as standard OLS regression -- performs only slightly worse than the best double robust methods.
-In the *ASR* replications, double robust methods provide similar coefficients for most, but not all, of the analyses.
-In some cases, statistical significance is lost, and in a minority of cases the coefficient sign changes.
-These replications highlight the importance of testing the robustness of quantitative results by comparing multiple methods and estimators.
+With its still relatively low error and much faster computation time, OLS remains a sensible choice as an estimator, and the Lin estimator -- which is as quick as standard OLS regression -- performs only slightly worse than the top machine learning methods.
+Due to the strong performance of G-computation and the Lin estimator, results suggest that using estimators that are robust to heterogeneous treatment effects may be more important than double robustness.
 
@@
 This is followed by an introduction of notation and assumptions, while the following section gives an overview of the double robust methods covered in this paper.
-I next present results of the simulations and replications, then conclude.
+I next present results of the simulations, then conclude.
 In the Appendix, I provide simple R code to implement the three double robust methods.
@@
 
-# Motivation
+# Background
 
@@
 
-Although previous work has compared different methods for covariate adjustment, there has not yet been a thorough comparison and evaluation of the recent and popular double robust methods of AIPW, TMLE, and DML for a social scientist audience.
+<!-- Although previous work has compared different methods for covariate adjustment, there has not yet been a thorough comparison and evaluation of the recent and popular double robust methods of AIPW, TMLE, and DML for a social scientist audience.
+-->
 
@@
 # Overview of Techniques  
-Each of the methods reviewed in this paper can be used with a variety of estimation techniques, including both traditional statistical methods and flexible machine learning methods.
+Each of the methods reviewed in this paper can be used with a variety of estimation techniques, including both traditional statistical methods and flexible machine learning algorithms.
 Each involves a model for the outcome and another for the treatment exposure, but choice of estimator for these two models is left to the discretion of the user.
@@
 This is the code used to evaluate these methods later in this paper, and it represents basic implementations of these methods.
-However, for researchers wishing to put these methods into practice, using a dedicated R packages for each method is probably a better idea.
-These packages have many flexible options, such as accounting for complex survey design, targeting estimands besides the ATE, and integrating with a variety of estimation techniques.
+However, for researchers wishing to put these methods into practice, using a dedicated R package for each method is probably a better idea.
+These packages have many flexible options, such as accounting for complex survey design, targeting estimands besides the ATE, and integrating with a variety of estimation techniques.^[In the Supplementary Material full tables of results, I present the results of using two packages to estimate the full set of simulations shown below.
+These include AIPW in conjunction with generalized random forests (GRF) using the `grf` package [@tibshirani_2024_grf] and a partially linear model for DML with a SuperLearner that, like below, harnesses ensemble learning with GLM, glmnet, and XGBoost, using the `DoubleML` package [@bach_2022_doubleml].
+Results are fairly similar to my own R code, though computation time is markedly faster.]
 
@@
 Extending and improving previous double robust methods, @vanderlaan_2006_targeted first proposed TMLE using a parametric framework and the efficient influence curve [@hines_2022_demystifying] to obtain estimates and standard errors.
-Mark van der Laan has gone on to collaborate on both a gentle introduction [@gruber_2009_targeted], two textbooks [@vanderlaan_2011_targeted; @vanderlaan_2018_targeted], and an R package [@gruber_2012_tmle] for implementing the method.
+Van der Laan has gone on to collaborate on both a gentle introduction [@gruber_2009_targeted], two textbooks [@vanderlaan_2011_targeted; @vanderlaan_2018_targeted], and an R package [@gruber_2012_tmle] for implementing the method.
 @schuler_2017_targeted and @luque-fernandez_2018_targeted provide introductions for epidemiologists.
@@
 <!-- $$E(Y=1 \mid D, \mathbf X) = \text{logit}(\mu_{di}) + \epsilon H_{di}$$ -->
-$$\text{logit}[E(Y=1 \mid D, \mathbf X)] = \text{logit}(\hat \mu_{di}) + \epsilon_0 H_{0i} + \epsilon_1 H_{1i}$$
+$$\text{logit}[E(Y=1 \mid D, \mathbf X)] = \text{logit}(\hat \mu_{di}) + \epsilon_0 H_{0i} + \epsilon_1 H_{1i}.$$
 
@@
 
-For each individual in the sample, this estimator calculates two quantities:
-
-- The treated potential outcome
+For each individual in the sample, this estimator calculates two quantities: The treated potential outcome
 
@@
 
-- The control potential outcome
+and the control potential outcome
 
 \begin{equation}
-\hat Y_{0i} = \frac{(1-D_i)(Y_i - \hat \mu_0 (X_i))}{1-\hat \pi(X_i)} + \hat \mu_0(X_i)
+\hat Y_{0i} = \frac{(1-D_i)(Y_i - \hat \mu_0 (X_i))}{1-\hat \pi(X_i)} + \hat \mu_0(X_i).
 (\#eq:control-aipw)
@@
 $$E[\hat \mu_1 (X_i)] = E[Y_1 \mid X_i].$$
-This means that
-$$E[Y_i - \hat \mu_1(X_i)] = 0,$$
-and hence
+This means that the model for the outcome and the observed outcome for this treated unit are equal in expectation, so
+$$E[Y_i - \hat \mu_1(X_i)] = 0.$$
+Plugging into Equation \@ref(eq:treated-aipw), we get 
 $$E[\hat Y_{1i}] = 0 + \hat \mu_1(X_i) = \hat \mu_1(X_i).$$
@@
 The incorrectly specified exposure model completely disappears from the equation.
-If we're dealing with a control unit ($D_i=0$), we get the same result:
+If we're dealing with a control unit, we get the same result, plugging $D_i=0$ into the same Equation \@ref(eq:treated-aipw):
 $$\hat Y_{1i} = \frac{0(Y_i - \hat \mu_1 (X_i))}{\hat \pi (X_i)} + \hat \mu_1(X_i) = \hat \mu_1(X_i).$$
 
-Now, what if the *exposure* model $\pi(X_i)$ is correctly specified and the outcome model $\mu_1(X)$ is incorrect? First, we rewrite the estimator for the treated outcome:
+Now, what if the *exposure* model $\pi(X_i)$ is correctly specified and the outcome model $\mu_1(X)$ is incorrect?
+First, we use algebra to rewrite Equation \@ref(eq:treated-aipw) for the treated outcome:
 \begin{align}
@@
 $$E[D_i - \hat \pi(X_i)] = 0.$$
-This means that the second term in Equation \@ref(eq:exposure-correct) is 0, so
+This means that the second term in Equation \@ref(eq:exposure-correct) is 0 in expectation, so
 $$E[\hat Y_{1i}]= E \left [ \frac{D_iY_i}{\hat \pi (X_i)}\right].$$
@@
 This demonstration shows that this estimator achieves double robustness: The estimator is robust to misspecification of either the exposure or the outcome model (but not both).
-The other two double robust methods considered in this paper can be shown to have the same property, but proving so is more complicated.
+The other two double robust methods considered in this paper can be shown to have the same property, but demonstrating this is more complicated.
+Interested readers can refer to the references cited above.
 
@@
 ```{r dml-package, eval = F}
-library(DoubleML)
-library(mlr3)
-library(mlr3pipelines)
-library(mlr3learners)
-library(mlr3extralearners)
 
@@
 @dorie_2019_automated published the results of this competition, along with the data used.
-Below, I test double robust methods on the 20 data sets used for the "do-it-yourself" part of the competition.
+Below, I test double robust methods on the 20 data generating processes (DGPs) reserved for the "do-it-yourself" part of the competition.
 The data represent a hypothetical twins study investigating the impact of birth weight on IQ.
 The data have 4,802 observations and 52 covariates.
-The authors of the study specify a different data generating process for the potential outcomes in each data set.
-In all cases, ignorability holds (all potential confounders are observed), but the authors vary the following:
-
-- degree of nonlinearity
-- percentage of treated
-- overlap for the treatment group
-- alignment (correspondence in variables used to generate the assignment mechanism and the response surface)
-- treatment effect heterogeneity
+Treatment is binary and the outcome is continuous.
+In all DGPs, ignorability holds (all potential confounders are observed), but the authors vary the following: (1) degree of nonlinearity, (2) percentage of treated, (3) overlap for the treatment group, (4) alignment (correspondence in variables used to generate the assignment mechanism and the response surface), and (5) treatment effect heterogeneity.
 
@@
 In theory these could solve the misspecification problem that double robust methods are meant to solve, but they could still suffer from regularization bias.
-G-computation [@robins_1986_new; @snowden_2011_implementation] uses some estimation technique to predict outcomes under treatment and control for each unit in the dataset.
-The ATE estimate is the difference in the average prediction under treatment and the average prediction under control.
+G-computation -- also called regression imputation -- uses some estimation technique to predict outcomes under treatment and control for each unit in the dataset [@robins_1986_new; @snowden_2011_implementation].
+This underlying technique can be anything from a traditional method such as OLS regression to a flexible machine learning method.
+The ATE estimate is the difference in the average prediction under treatment and the average prediction under control:
+
+$$\begin{aligned}
+\hat \tau_{gcomp} = &\frac{1}{n} \sum_{i=1}^n \left[\hat \mu_1 (\mathbf X_i) - \hat \mu_0 (\mathbf X_i) \right].
+\end{aligned}$$
+
 The second two-model method is the Lin estimator [@lin_2013_agnostic].
 This method aims to solve issues with the bias induced by OLS regression in a randomization framework by interacting the treatment indicator with mean-centered covariates.
-@hazlett_2024_understanding show that this method is equivalent to estimating two separate OLS regression models for the treated and control units.
+@hazlett_2024_demystifying show that this method is equivalent to estimating two separate OLS regression models for the treated and control units -- i.e., G-computation with each of the underlying models estimated by OLS regression.
 
@@
 
-The 20 data sets used here cover a range of these attributes; see the supplemental material from @dorie_2019_automated for details.
-I use 10 simulations of each data set, resulting in 200 data sets.
+I use 10 simulations of each of the 20 DGPs, resulting in 200 data sets.
 I then calculate bias, percent bias (the estimator's bias as a percentage of its standard error), root mean squared error (rmse), and median absolute error (mae).
@@
 
-```{r dorie-results-bias,  fig.cap = 'Bias of Monte Carlo simulations using the first 20 datasets from Dorie et al. (2019), 10 replications each.'}
+```{r dorie-results-bias,  fig.cap = 'Bias of Monte Carlo simulations using the first 20 DGPs from Dorie et al.
+(2019), 10 replications each.
+Points represent the bias of estimates on individual datasets, while box plots show the median, 25th and 75th percentiles, and whiskers extending to 1.5 times the interquartile range.
+Colors correspond to method (in which multiple estimators may be used).'}
 addline_format <- function(x,...){
@@
 
-```{r dorie-results-rmse, fig.cap = 'Root mean squared error and bias for Monte Carlo simulations using the first 20 datasets from Dorie et al.
+```{r dorie-results-rmse, fig.cap = 'Root mean squared error and bias for Monte Carlo simulations using the first 20 DGPs from Dorie et al.
 (2019), 10 replications each.
@@
 
-```{r dorie-linear-bias,  fig.cap = 'Bias of Monte Carlo simulations using the two datasets from Dorie et al. (2019), with linear data generating processes, 100 replications each ("linear").'}
+```{r dorie-linear-bias,  fig.cap = 'Bias of Monte Carlo simulations using the two datasets from Dorie et al.
+(2019), with linear data generating processes, 100 replications each.
+Points represent the bias of estimates on individual datasets, while box plots show the median, 25th and 75th percentiles, and whiskers extending to 1.5 times the interquartile range.
+Colors correspond to method (in which multiple estimators may be used).'}
 sim_results %>% 
@@
                     linesep = '',
-                    caption = 'Data generating process: Three lowest RMSE methods by DGP for Monte Carlo simulations using the first 20 datasets from Dorie et al. (2019), 10 replications each.')
+                    caption = 'Data generating process: Three lowest RMSE methods by DGP for Monte Carlo simulations using the first 20 DGPs from Dorie et al. (2019), 10 replications each.')
 ```
@@
                     linesep = '',
-                    caption = 'Data generating process: Fourth- to sixth-lowest RMSE methods by DGP for Monte Carlo simulations using the first 20 datasets from Dorie et al.
+                    caption = 'Data generating process: Fourth- to sixth-lowest RMSE methods by DGP for Monte Carlo simulations using the first 20 DGPs from Dorie et al.
 (2019), 10 replications each.')
@@
 
-While the AIPW, TMLE, and G-computation with a SuperLearner may be the top performing methods overall, this does not mean that there are some data-generating processes (DGPs) where some other method may do better.
-Across the the 20 datasets, @dorie_2019_automated vary five DGP characteristics: degree of nonlinearity, the percentage treated, overlap for the treatment group, alignment (correspondence in variables used to generate the exposure and response models), and treatment effect heterogeneity.
-To test how the methods perform across different values of these characteristics, I begin with the 200 simulations from the 20 datasets used in the main results (Figures \@ref(fig:dorie-results-bias) and \@ref(fig:dorie-results-rmse)).
+While the AIPW, TMLE, and G-computation with a SuperLearner may be the top performing methods overall, this does not mean that there are some DGPs where some other method may do better.
+Across the 20 DGPs, @dorie_2019_automated vary five characteristics: degree of nonlinearity, the percentage treated, overlap for the treatment group, alignment (correspondence in variables used to generate the exposure and response models), and treatment effect heterogeneity.
+To test how the methods perform across different values of these characteristics, I begin with the 200 simulations from the 20 DGPs used in the main results (Figures \@ref(fig:dorie-results-bias) and \@ref(fig:dorie-results-rmse)).
 I limit datasets to those generated by a particular value of a DGP characteristic, and I then calculate RMSE for each method for only these datasets.
-For example, alignment is 0 for datasets 8 and 16 (meaning there is 0 correlation between the terms included in the treatment and outcome models), so for this value of the DGP RMSE is calculated only for those two datasets.
+For example, alignment is 0 for datasets 8 and 16 (meaning there is 0 correlation between the terms included in the treatment and outcome models), so for this value RMSE is calculated only for datasets generated from those two DGPs.
 
 Tables \@ref(tab:dgp) and \@ref(tab:dgp-2) shows the six top-performing methods by lowest RMSE for each each value of the DGP characteristics.
-Across DGPs, the same methods dominate as in the full range of simulations: the SuperLearner with AIPW, TMLE, and G-computation.
+(The Supplementary Material presents a table with full results for all DGPs in the simulations.) Across DGPs, the same methods dominate as in the full range of simulations: the SuperLearner with AIPW, TMLE, and G-computation.
 In fact, these three methods take the top three spots for *every* DGP variation in the simulations.
@@
 GRF with AIPW, G-computation, and TMLE take most of these spots, but the Lin estimator and OLS appear a few times.
+Notably, in the presence of high treatment effect heterogeneity, flexible machine learning methods take the top six spots, and not all of these are double robust.
+For the DGPs, allowing for treatment effects to vary appears more important than double robustness.
+This is supported by the performance of the Lin estimator, which takes the seventh spot (as shown in the Supplementary Material).
+This estimator is relatively inflexible but robust to heterogeneous effects.
+DML, which as implemented here is not robust to heterogeneous treatment effects, performs worse than OLS regression.
 
@@
 Flexible estimators take the top spots (though notably not those used with DML), and traditional methods do fairly well across the board.
+
+```{r hetro-rmse, eval = F, fig.height = 7, fig.cap = 'Treatment Effect Heterogeneity: Root mean squared error and bias for Monte Carlo simulations from the first 20 DGPs in Dorie et al.
+(2019), 10 replications each.
+Values greater in absolute value than 4 are plotted at 4 and labeled with their actual value.'}
+
+sim_results_plot <- sim_results_dgp %>%
+  group_by(`Treat. heterogeneity`, method_estimator) %>%
+  summarize(bias = mean(ate - truth, na.rm = T),
+            rmse = sqrt(mean((ate - truth)^2, na.rm = T))
+              ) %>%
+  pivot_longer(c(bias, rmse)) %>%
+  mutate(method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
+  mutate(label = ifelse(abs(value) > 4, round(value), NA),
+         value = ifelse(abs(value) > 4, 4*value/abs(value), value))
+
+(sim_results_plot %>%
+  filter(`Treat. heterogeneity` == 'high') %>%
+  arrange(desc(name), value) %>%
+  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator}))) %>%
+  ggplot(aes(x = method_estimator, y = value, color = name, shape = name)) +
+  geom_point() +
+  # ggrepel::geom_text_repel(aes(label = label), show.legend = F) +
+  geom_text(aes(label = label), nudge_y = ifelse(sim_results_plot$label > 0, -.5, .5), show.legend = F) +
+  geom_hline(yintercept = 0) + 
+  # facet_wrap(~`Treat. heterogeneity`, nrow = 2, scales = 'free_x') +
+  labs(x = '', y = '', title = 'High Treatment Effect Heterogeneity') +
+  theme(axis.text.x=element_text(angle=90, hjust=0.95,vjust=0.2)) +
+  #scale_x_discrete(labels=function(x){sub(", ", "\n", x)}) +
+  #scale_y_continuous(trans=ggallin::pseudolog10_trans)
+  ylim(c(-4, 4))
+  ) /
+  (sim_results_plot %>%
+  filter(`Treat. heterogeneity` == 'none') %>%
+  arrange(desc(name), value) %>%
+  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator}))) %>%
+  ggplot(aes(x = method_estimator, y = value, color = name, shape = name)) +
+  geom_point()) +
+  # ggrepel::geom_text_repel(aes(label = label), show.legend = F) +
+  geom_text(aes(label = label), nudge_y = ifelse(sim_results_plot$label > 0, -.5, .5), show.legend = F) +
+  geom_hline(yintercept = 0) + 
+  # facet_wrap(~`Treat. heterogeneity`, nrow = 2, scales = 'free_x') +
+  labs(x = '', y = '', title = 'No Treatment Effect Heterogeneity') +
+  theme(axis.text.x=element_text(angle=90, hjust=0.95,vjust=0.2)) +
+  #scale_x_discrete(labels=function(x){sub(", ", "\n", x)}) +
+  #scale_y_continuous(trans=ggallin::pseudolog10_trans)
+  ylim(c(-4, 4))
+
+```
 
@@
 To test this, this section uses simulated datasets of varying sizes, from 150 to 96,040 (20 times the original sample size).
-These datasets are also derived from the @dorie_2019_automated `aciccomp2016` package, using parameter set 7, a fairly nonlinear DGP with high heterogeneity.
+These datasets are also derived from the @dorie_2019_automated `aciccomp2016` package, using parameter set 7, a fairly nonlinear DGP with high treatment effect heterogeneity.
 For sample sizes less than 4,802, the sample is randomly drawn from a randomly generated 4,802-unit sample.
@@
 
-```{r dorie-size-fig-old, fig.height = 8, eval = F, fig.cap = 'RMSE of Monte Carlo simulations using dataset 7 from Dorie et al. (2019) with varying sample sizes, 20 replications each'}
+```{r dorie-size-fig-old, fig.height = 8, eval = F, fig.cap = 'RMSE of Monte Carlo simulations using DGP 7 from Dorie et al. (2019) with varying sample sizes, 20 replications each'}
 addline_format <- function(x,...){
@@
                     linesep = '',
-                    caption = 'Sample size: Four lowest RMSE methods by sample size for Monte Carlo simulations using dataset 7 from Dorie et al. (2019), 20 replications each')
-
-```
-
-```{r dorie-size-fig, fig.height = 8, fig.cap = 'RMSE of Monte Carlo simulations using dataset 7 from Dorie et al. (2019) with varying sample sizes, 20 replications each'}
+                    caption = 'Sample size: Four lowest RMSE methods by sample size for Monte Carlo simulations using DGP 7 from Dorie et al. (2019), 20 replications each')
+
+```
+
+```{r dorie-size-fig, fig.height = 8, fig.cap = 'RMSE of Monte Carlo simulations using DGP 7 from Dorie et al. (2019) with varying sample sizes, 20 replications each'}
 
@@
 
-# Replications
-
-```{r aksoy, eval = F}
-aksoy <- read_dta(here('replication', 'aksoy.dta')) %>%
-  mutate(cid_num = as.integer(factor(cid))) %>%
-  as_factor()
-
-# first three models from table 2
-
-m1 <- lm(ISL ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` + 
-     `_Y66` + `_Y70` + `_Y71` + dlen + cid,
-   data = filter(aksoy, electyr == T)) # %>%
-  # tidy() %>%
-  # filter(!str_detect(term, 'cid'), !str_detect(term, '_Y'))
-
-m2 <- lm(ISL ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` + 
-     `_Y66` + `_Y70` + `_Y71` + dlen + cid + gdp_g + t + m + pop,
-   data = aksoy) 
-  # tidy() %>%
-  # filter(!str_detect(term, 'cid'), !str_detect(term, '_Y'))
-
-m3 <- lm(ISL ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` + 
-     `_Y66` + `_Y70` + `_Y71` + dlen + cid + gdp_g + t + m + pop + l_ISL,
-   data = aksoy) 
-  # tidy() %>%
-  # filter(!str_detect(term, 'cid'), !str_detect(term, '_Y'))
-
-aksoy_drop_na_y <- filter(aksoy, !is.na(ISL))
-
-m1_grf_dml <- dml_grf(outcome = 'ISL', 
-        treatment = 'dlen', 
-        covariates = c('year'), 
-        clustervar = 'cid_num',
-        dataset = aksoy,
-        target = 'all')
-
-m2_grf_dml <- dml_grf(outcome = 'ISL', 
-        treatment = 'dlen', 
-        covariates = c('year', 'gdp_g', 't', 'm', 'pop'), 
-        clustervar = 'cid_num',
-        dataset = aksoy,
-        target = 'all')
-
-m3_grf_dml <- dml_grf(outcome = 'ISL', 
-        treatment = 'dlen', 
-        covariates = c('year', 'gdp_g', 't', 'm', 'pop', 'l_ISL'), 
-        clustervar = 'cid_num',
-        dataset = aksoy,
-        target = 'all')
-
-m1 <- data.frame(estimate = 7.159, std.error = 2.539)
-m2 <- data.frame(estimate = 7.349, std.error = 2.491)
-m3 <- data.frame(estimate = 5.317, std.error = 1.855)
-
-compare_tbl(list(append(list(original = m1), m1_grf_dml), 
-                                  append(list(original = m2), m2_grf_dml), 
-                                  append(list(original = m3), m3_grf_dml)),
-                             tidy = F) %>%
-  write_rds(here('replication', 'aksoy_rep.RDS'))
-
-# huxtable::huxreg(compare_tbl(list(append(list(original = m1), m1_grf_dml), 
-#                                   append(list(original = m2), m2_grf_dml), 
-#                                   append(list(original = m3), m3_grf_dml)),
-#                              tidy = F),
-#                  statistics = NA) %>%
-#   huxtable::insert_row(c('Covariates', 'No', rep('Yes', 2)), after = nrow(.) - 1) %>%
-#   huxtable::insert_row(c('Lagged dependent variable', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
-#   huxtable::set_caption('Replication of aksoy et al.
-(2022) Table 2, models for outcome of Islamic Votes: "Effect of Fasting Hours (Daylength) during Ramadan on Various Outcome Variables Based on Regression Models That Include Fixed Effects for Provinces and Election Years"') %>%
-#   write_rds(here('replication', 'aksoy_tab.RDS'))
-# 
-# read_rds(here('replication', 'aksoy_rep.RDS')) %>%
-#   huxtable::huxreg()
-
-```
-
-```{r biegert, eval = F}
-# Table 3
-
-biegert <- read_dta(here('replication', 'biegert.dta')) %>%
-  filter(sampleC == 1) %>%
-  mutate(year_num = as.numeric(year),
-         allstar_y_num = as.numeric(allstar_y),
-         allstar_x_num = as.numeric(allstar_x),
-    across(c(allstar_y, allstar_x, year), as.factor),
-    player_id_num = as.integer(factor(player_id))) %>%
-  as_factor()
-
-m1 <- glm(allstar_y ~ allstar_x, 
-          data = filter(biegert, sampleC == 1), family = 'binomial') %>%
-  margins::margins(variables = 'allstar_x', 
-                   vcov = sandwich::vcovCL(., cluster = ~player_id))
-
-m2 <- glm(allstar_y ~ allstar_x + height + pos + age_0 + age_0_2 + Black + time + time_2 + year, 
-          data = filter(biegert, sampleC == 1),
-          family = binomial(link = 'logit')) %>%
-  margins::margins(variables = 'allstar_x', 
-                   vcov = sandwich::vcovCL(., cluster = ~player_id))
-
-m3 <- glm(allstar_y ~ allstar_x + height + pos + age_0 + age_0_2 + Black + time + time_2 + year +
-            pts_sdt_nd + ast_sdt_nd + trb_sdt_nd + min_played_nd +  playoffs_nd + win_nd + bigm_nd, 
-          data = filter(biegert, sampleC == 1),
-          family = binomial(link = 'logit')) %>%
-  margins::margins(variables = 'allstar_x', 
-                   vcov = sandwich::vcovCL(., cluster = ~player_id))
-
-m4 <- glm(allstar_y ~ allstar_x + height + pos + age_0 + age_0_2 + Black + time + time_2 + year +
-            pts_sdt_nd + ast_sdt_nd + trb_sdt_nd + min_played_nd +  playoffs_nd + win_nd + bigm_nd +
-            pts_sdt_t + ast_sdt_t + trb_sdt_t, 
-          data = filter(biegert, sampleC == 1),
-          family = binomial(link = 'logit')) %>%
-  margins::margins(variables = 'allstar_x', 
-                   vcov = sandwich::vcovCL(., cluster = ~player_id))
-
-m5 <- glm(allstar_y ~ allstar_x + height + pos + age_0 + age_0_2 + Black + time + time_2 + year +
-            pts_sdt_nd + ast_sdt_nd + trb_sdt_nd + min_played_nd +  playoffs_nd + win_nd + bigm_nd +
-            pts_sdt_t + ast_sdt_t + trb_sdt_t +
-            min_played_t + playoffs_t + win_t + bigm_t, 
-          data = filter(biegert, sampleC == 1),
-          family = binomial(link = 'logit')) %>%
-  margins::margins(variables = 'allstar_x', 
-                   vcov = sandwich::vcovCL(., cluster = ~player_id))
-
-m6 <- glm(allstar_y ~ allstar_x + allstar_hi + height + pos + age_0 + age_0_2 + Black + time + time_2 + year +
-            pts_sdt_nd + ast_sdt_nd + trb_sdt_nd + min_played_nd +  playoffs_nd + win_nd + bigm_nd +
-            pts_sdt_t + ast_sdt_t + trb_sdt_t +
-            min_played_t + playoffs_t + win_t + bigm_t +
-            pts_sdt_hi + ast_sdt_hi + trb_sdt_hi + min_played_hi + playoffs_hi + win_hi + bigm_hi, 
-          data = filter(biegert, sampleC == 1),
-          family = binomial(link = 'logit')) %>%
-  margins::margins(variables = 'allstar_x', 
-                   vcov = sandwich::vcovCL(., cluster = ~player_id))
-
-# M1 
-set.seed(123)
-Y <- as.numeric(biegert[['allstar_y']])
-X <- data.frame(var = rep(NA_integer_, length(Y)))
-W <- as.numeric(biegert[['allstar_x']])
-
-grf_model1 <- grf::causal_forest(X = X, Y = Y, W = W, seed = 123,
-                      clusters = biegert$player_id_num
-                      )
-
-grf_out1 <- grf::average_treatment_effect(grf_model1, target.sample = 'all')
-
-dml_out1 <- data.frame(estimate = NA,
-                       std.error = NA)
-dml_cre_out1 <- dml_out1
-dml_hybrid_out1 <- dml_out1
-
-# M2
-m2_grf_dml <- dml_grf(outcome = 'allstar_y_num', 
-        treatment = 'allstar_x_num', 
-        covariates = c('height', 'pos', 'age_0', 'Black', 'time', 'year_num'), 
-        clustervar = 'player_id_num',
-        dataset = biegert,
-        target = 'all')
-
-# M3 
-m3_grf_dml <- dml_grf(outcome = 'allstar_y_num', 
-        treatment = 'allstar_x_num', 
-        covariates = c('height', 'pos', 'age_0', 'Black', 'time', 'year_num',
-                       'pts_sdt_nd', 'ast_sdt_nd', 'trb_sdt_nd', 'min_played_nd',  'playoffs_nd', 'win_nd', 'bigm_nd'), 
-        clustervar = 'player_id_num',
-        dataset = biegert,
-        target = 'all')
-
-# M4
-m4_grf_dml <- dml_grf(outcome = 'allstar_y_num', 
-        treatment = 'allstar_x_num', 
-        covariates = c('height', 'pos', 'age_0', 'Black', 'time', 'year_num',
-                       'pts_sdt_nd', 'ast_sdt_nd', 'trb_sdt_nd', 'min_played_nd',  'playoffs_nd', 'win_nd', 'bigm_nd',
-                       'pts_sdt_t', 'ast_sdt_t', 'trb_sdt_t'), 
-        clustervar = 'player_id_num',
-        dataset = biegert,
-        target = 'all')
-
-# M5
-m5_grf_dml <- dml_grf(outcome = 'allstar_y_num', 
-        treatment = 'allstar_x_num', 
-        covariates = c('height', 'pos', 'age_0', 'Black', 'time', 'year_num',
-                       'pts_sdt_nd', 'ast_sdt_nd', 'trb_sdt_nd', 'min_played_nd',  'playoffs_nd', 'win_nd', 'bigm_nd',
-                       'pts_sdt_t', 'ast_sdt_t', 'trb_sdt_t',
-                       'min_played_t', 'playoffs_t', 'win_t', 'bigm_t'), 
-        clustervar = 'player_id_num',
-        dataset = biegert,
-        target = 'all')
-
-# # M6
-# m6_grf_dml <- dml_grf(outcome = 'allstar_y_num', 
-#         treatment = 'allstar_x_num', 
-#         covariates = c('height', 'pos', 'age_0', 'Black', 'time', 'year_num',
-#                        'pts_sdt_nd', 'ast_sdt_nd', 'trb_sdt_nd', 'min_played_nd',  'playoffs_nd', 'win_nd', 'bigm_nd',
-#                        'pts_sdt_t', 'ast_sdt_t', 'trb_sdt_t',
-#                        'min_played_t', 'playoffs_t', 'win_t', 'bigm_t',
-#                        'pts_sdt_hi', 'ast_sdt_hi', 'trb_sdt_hi', 'min_played_hi', 'playoffs_hi', 'win_hi', 'bigm_hi'), 
-#         clustervar = 'player_id_num',
-#         dataset = biegert,
-#         target = 'all')
-
-out_empty <- grf_out1
-out_empty$estimate <- NA
-out_empty$std.err <-
-
-compare_tbl(model_list = list(
-                 list(original = m1, grf = grf_out1, dml = dml_out1, dml_cre = dml_cre_out1, dml_wg_cre = dml_hybrid_out1), 
-                 append(list(original = m2), m2_grf_dml), 
-                 append(list(original = m3), m3_grf_dml),
-                 append(list(original = m4), m4_grf_dml),
-                 append(list(original = m5), m5_grf_dml),
-            treatment = 'allstar_x1',
-            tidy = T) %>%
-  write_rds(here('replication', 'biegert_rep.RDS'))
-
-# Final table
-# huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1),
-#                                   list(m2, grf_out2, dml_out2),
-#                                   list(m3, grf_out3, dml_out3),
-#                                   list(m4, grf_out4, dml_out4),
-#                                   list(m5, grf_out5, dml_out5),
-#                                   list(m6, grf_out6, dml_out6)),
-#                              treatment = 'allstar_x1'),
-#                  statistics = NA) %>%
-#   huxtable::insert_row(c('Baseline confounders', 'No', rep('Yes', 5)), after = nrow(.) - 1) %>%
-#   huxtable::insert_row(c('Prior situation + performance', rep('No', 2), rep('Yes', 4)), after = nrow(.) - 1) %>%
-#   huxtable::insert_row(c('Current performance', rep('No', 3), rep('Yes', 3)), after = nrow(.) - 1) %>%
-#   huxtable::insert_row(c('Current situation', rep('No', 4), rep('Yes', 2)), after = nrow(.) - 1) %>%
-#   huxtable::insert_row(c('Cumul. AS + cumul. mediators', rep('No', 5), 'Yes'), after = nrow(.) - 1) %>%
-#   huxtable::set_caption('Replication of Biegert et al. (2023) Table 3: "Average Marginal Effects from Logistic Regression Models of All-Star Nomination"') %>%
-#   write_rds(here('replication', 'biegert_tab.RDS'))
-# 
-# read_rds(here('replication', 'biegert_tab.RDS'))
-
-```
-
-```{r nussio-ind, eval = F}
-nussio_ind <- read_dta(here('replication/nussio_2024', 'Mexico City Individual data.dta')) %>%
-  filter(if_all(c(PARP, lognombre), ~!is.na(.x))) %>%
-  mutate(across(c(PARP, IT1, ED, BASURA), as.numeric),
-         cve_col_num = as.numeric(factor(cve_col))) %>%
-  as_factor()
-
-## Table 2 #### (individual analysis)
-
-m1 <- lm(PARP ~ lognombre + IT1, 
-         nussio_ind) %>%
-  lmtest::coeftest(., vcov = sandwich::vcovCL(., ~cve_col))
-
-m2 <- lm(PARP ~ lognombre + IT1 + 
-           ED + age + female + INGi + unemployed, 
-         nussio_ind) %>%
-  lmtest::coeftest(., vcov = sandwich::vcovCL(., ~cve_col))
-
-m3 <- lm(PARP ~ lognombre + IT1 + 
-           ED + age + female + INGi + unemployed +
-           HER + catholic + nonreligious + working + BASURA + RESS + 
-           PELEA  + PADRES + index_trustgov, 
-         nussio_ind) %>%
-  lmtest::coeftest(., vcov = sandwich::vcovCL(., ~cve_col))
-
-m4 <- lm(PARP ~ lognombre + IT1 + 
-           ED + age + female + INGi + unemployed +
-           HER + catholic + nonreligious + working + BASURA + RESS + 
-           PELEA  + PADRES + index_trustgov +
-           col, nussio_ind) %>%
-  lmtest::coeftest(., vcov = sandwich::vcovCL(., ~cve_col)) 
-  # tidy() %>%
-  # filter(!(str_detect(term, 'col')))
-
-# M1 
-m1_grf_dml <- dml_grf(outcome = 'PARP', 
-        treatment = 'lognombre', 
-        covariates = c('IT1'), 
-        clustervar = 'cve_col_num',
-        dataset = nussio_ind,
-        target = 'all')
-
-# M2 
-m2_grf_dml <- dml_grf(outcome = 'PARP', 
-        treatment = 'lognombre', 
-        covariates = c('IT1', 'ED', 'age', 'female', 'INGi', 'unemployed'), 
-        clustervar = 'cve_col_num',
-        dataset = nussio_ind,
-        target = 'all')
-
-# M3 & M4 (M4 has fixed effects)
-m3_grf_dml <- dml_grf(outcome = 'PARP', 
-        treatment = 'lognombre', 
-        covariates = c('IT1', 'ED', 'age', 'female', 'INGi', 'unemployed',
-                       'HER', 'catholic', 'nonreligious', 'working', 'BASURA', 'RESS', 
-                       'PELEA' , 'PADRES', 'index_trustgov'), 
-        clustervar = 'cve_col_num',
-        dataset = nussio_ind,
-        target = 'all')
-
-m4_grf_dml <- m3_grf_dml
-
-compare_tbl(model_list = list(append(list(original = m1), m1_grf_dml),
-                              append(list(original = m2), m2_grf_dml), 
-                              append(list(original = m3), m3_grf_dml),
-                              append(list(original = m4), m4_grf_dml)),
-            treatment = 'lognombre',
-            tidy = T) %>%
-  write_rds(here('replication', 'nussio_ind_rep.RDS'))
-
-# Final table
-# huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1),
-#                                   list(m2, grf_out2, dml_out2),
-#                                   list(m3, grf_out3, dml_out3),
-#                                   list(m4, grf_out4, dml_out4)),
-#                              treatment = 'lognombre'),
-#                  statistics = NA) %>%
-#   huxtable::insert_row(c('Colonia FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
-#   huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>%
-#   huxtable::set_caption('Replication of Nussio (2024) Table 2: "Individual-Level Analysis: Community Ties and Lynching Participation"') %>%
-#   write_rds(here('replication', 'nussio_ind_tab.RDS'))
-# 
-# read_rds(here('replication', 'nussio_ind_tab.RDS'))
-```
-
-```{r nussio-ag, eval = F}
-## Table 4 #### (aggregate analysis)
-nussio_ag <- read_dta(here('replication/nussio_2024', 
-                           'Mexico Municipality Cross-Sectional Data.dta')) %>%
-  filter(if_all(c(loglynchpermio, organized_lighting_mean), ~!is.na(.x))) %>%
-  mutate(estado_num = as.numeric(estado)) %>%
-  # mutate(across(c(PARP, IT1, ED, BASURA), as.numeric),
-  #        cve_col_num = as.integer(factor(cve_col))) %>%
-  as_factor()
-
-nussio_ag_drop_na <- nussio_ag %>% drop_na(loglynchpermio, organized_lighting_mean,
-                          trust_neighbors_mean, problem_lighting_mean,
-                          c_poptot, area, pconeval_poverty_pobreza_pob, 
-                          coneval_gini_coeficientedegini,
-                          indigenous, c_poptot_norelpop, homirate, robberyrate,
-           victim_household_before_prev_yea, trust_army_mean)
-
-m1 <- lm(loglynchpermio ~ organized_lighting_mean + trust_neighbors_mean + problem_lighting_mean,
-         nussio_ag) %>%
-  lmtest::coeftest(., vcov = sandwich::vcovCL(., ~estado))
-
-m2 <- lm(loglynchpermio ~ organized_lighting_mean + trust_neighbors_mean + problem_lighting_mean +
-           c_poptot + area + pconeval_poverty_pobreza_pob + coneval_gini_coeficientedegini + 
-           indigenous + c_poptot_norelpop + homirate + robberyrate,
-         nussio_ag) %>%
-  lmtest::coeftest(., vcov = sandwich::vcovCL(., ~estado))
-
-m3 <- lm(loglynchpermio ~ organized_lighting_mean + trust_neighbors_mean + problem_lighting_mean +
-           c_poptot + area + pconeval_poverty_pobreza_pob + coneval_gini_coeficientedegini + 
-           indigenous + c_poptot_norelpop + homirate + robberyrate +
-           victim_household_before_prev_yea + trust_army_mean,
-         nussio_ag) %>%
-  lmtest::coeftest(., vcov = sandwich::vcovCL(., ~estado))
-
-m4 <- lm(loglynchpermio ~ organized_lighting_mean + trust_neighbors_mean + problem_lighting_mean +
-           c_poptot + area + pconeval_poverty_pobreza_pob + coneval_gini_coeficientedegini + 
-           indigenous + c_poptot_norelpop + homirate + robberyrate +
-           victim_household_before_prev_yea + trust_army_mean + 
-           estado,
-         nussio_ag)
-
-# M1 
-m1_grf_dml <- dml_grf(outcome = 'loglynchpermio', 
-        treatment = 'organized_lighting_mean', 
-        covariates = c('trust_neighbors_mean', 'problem_lighting_mean'), 
-        clustervar = 'estado_num',
-        dataset = nussio_ag,
-        target = 'all')
-
-# M2
-m2_grf_dml <- dml_grf(outcome = 'loglynchpermio', 
-        treatment = 'organized_lighting_mean', 
-        covariates = c('trust_neighbors_mean', 'problem_lighting_mean',
-                       'c_poptot', 'area', 'pconeval_poverty_pobreza_pob', 'coneval_gini_coeficientedegini', 
-           'indigenous', 'c_poptot_norelpop', 'homirate', 'robberyrate'), 
-        clustervar = 'estado_num',
-        dataset = nussio_ag,
-        target = 'all')
-
-# M3
-m3_grf_dml <- dml_grf(outcome = 'loglynchpermio', 
-        treatment = 'organized_lighting_mean', 
-        covariates = c('trust_neighbors_mean', 'problem_lighting_mean',
-                       'c_poptot', 'area', 'pconeval_poverty_pobreza_pob', 'coneval_gini_coeficientedegini', 
-           'indigenous', 'c_poptot_norelpop', 'homirate', 'robberyrate',
-           'victim_household_before_prev_yea', 'trust_army_mean'), 
-        clustervar = 'estado_num',
-        dataset = nussio_ag,
-        target = 'all')
-
-# M4
-m4_grf_dml <- m3_grf_dml
-
-compare_tbl(model_list = list(append(list(original = m1), m1_grf_dml),
-                              append(list(original = m2), m2_grf_dml), 
-                              append(list(original = m3), m3_grf_dml),
-                              append(list(original = m4), m4_grf_dml)),
-            treatment = 'organized_lighting_mean',
-            tidy = T) %>%
-  write_rds(here('replication', 'nussio_ag_rep.RDS'))
-
-# huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1),
-#                                   list(m2, grf_out2, dml_out2),
-#                                   list(m3, grf_out3, dml_out3),
-#                                   list(m4, grf_out4, dml_out4)),
-#                  treatment = 'organized_lighting_mean'),
-#                  statistics = NA) %>%
-#   huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>%
-#   huxtable::insert_row(c('Estado FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
-#   huxtable::insert_row(c('Estado clustered SE', 'Yes', 'Yes', 'Yes', 'No'), after = nrow(.) - 1) %>%
-#   huxtable::set_caption('Replication of Nussio (2024) Table 4: "Aggregate-Level Analysis: Community Ties and Lynching Rate"') %>%
-#   # huxtable::set_width(1) %>%
-#   # huxtable::set_all_padding(0) %>%
-#   write_rds(here('replication', 'nussio_ag_tab.RDS'))
-# 
-# read_rds(here('replication', 'nussio_ag_tab.RDS'))
-
-# names(grf_out1) <- c('estimate', 'std.error')
-# tidy(m1) %>%
-#   filter(term == 'organized_lighting_mean') %>%
-#   bind_rows(mutate(bind_rows(grf_out1))) %>%
-#   mutate(term = c('original', 'TMLE (GRF)'), p.value = p_val(estimate, std.error)) %>%
-#   huxtable::huxreg()
-
-```
-
-```{r nussio-ne, eval = F}
-nussio_ne <- read_dta(here('replication/nussio_2024', 
-                           'Mexico Municipality Panel Data.dta')) %>%
-  # filter(if_all(c(loglynchpermio, organized_lighting_mean), ~!is.na(.x))) %>%
-  mutate(cve_num = as.numeric(cve),
-         year_num = year,
-         year = as.factor(year),
-         cve = cve,
-         cve = as.factor(cve)) %>%
-  # mutate(across(c(PARP, IT1, ED, BASURA), as.numeric),
-  #        cve_col_num = as.integer(factor(cve_col))) %>%
-  as_factor()
-
-# m1 <- lm(lynch_event ~ eq2017_250X2017 + year + cve, data = nussio_ne) %>%
-#   lmtest::coeftest(., vcov = sandwich::vcovCL(., ~cve))
-
-# m1 <- fixest::feols(lynch_event ~ eq2017_250X2017 | year + cve, 
-#               data = nussio_ne) %>%
-#   summary(vcov = ~cve) %>%
-#   tidy()
-
-m1 <- data.frame(estimate = 0.108, std.error = 0.019)
-m2 <- data.frame(estimate = 0.113, std.error = 0.021)
-m3 <- data.frame(estimate = 0.087, std.error = 0.019)
-m4 <- data.frame(estimate = 0.126, std.error = 0.026)
-m5 <- data.frame(estimate = -0.010, std.error = 0.002)
-m6 <- data.frame(estimate = -0.009, std.error = 0.002)
-
-# M1
-m1_grf_dml <- dml_grf(outcome = 'lynch_event', 
-        treatment = 'eq2017_250X2017', 
-        covariates = c('year_num'), 
-        clustervar = 'cve_num',
-        dataset = nussio_ne,
-        target = 'treated',
-        drop_na_grf = T)
-
-# M2
-m2_grf_dml <- dml_grf(outcome = 'lynch_event', 
-        treatment = 'eq2017_250X2017', 
-        covariates = c('year_num', 'homicidefull', 'robofull', 'secuestrofull', 'inegi_infant_mort'), 
-        clustervar = 'cve_num',
-        dataset = nussio_ne,
-        target = 'treated',
-        drop_na_grf = T)
-
-# M3
-m3_grf_dml <- dml_grf(outcome = 'lynch_event', 
-        treatment = 'eq2017_damageX2017', 
-        covariates = c('year_num'), 
-        clustervar = 'cve_num',
-        dataset = nussio_ne,
-        target = 'treated',
-        drop_na_grf = T)
-
-# M4
-m4_grf_dml <- dml_grf(outcome = 'lynch_event', 
-        treatment = 'eq2017_damageX2017', 
-        covariates = c('year_num', 'homicidefull', 'robofull', 'secuestrofull', 'inegi_infant_mort'), 
-        clustervar = 'cve_num',
-        dataset = nussio_ne,
-        target = 'all',
-        drop_na_grf = T)
-
-# # M5
-# m5_grf_dml <- dml_grf(outcome = 'lynch_event', 
-#         treatment = 'eq2017_dist100X2017', 
-#         covariates = c('year_num'), 
-#         clustervar = 'cve_num',
-#         dataset = nussio_ne,
-#         target = 'all',
-#         drop_na_grf = T)
-# 
-# # M6
-# m6_grf_dml <- dml_grf(outcome = 'lynch_event', 
-#         treatment = 'eq2017_dist100X2017', 
-#         covariates = c('year_num', 'homicidefull', 'robofull', 'secuestrofull', 'inegi_infant_mort'), 
-#         clustervar = 'cve_num',
-#         dataset = nussio_ne,
-#         target = 'all',
-#         drop_na_grf = T)
-
-compare_tbl(model_list = list(
-                 append(list(original = m1), m1_grf_dml),
-                 append(list(original = m2), m2_grf_dml), 
-                 append(list(original = m3), m3_grf_dml),
-                 append(list(original = m4), m4_grf_dml),
-            treatment = NULL,
-            tidy = F) %>%
-  write_rds(here('replication', 'nussio_ne_rep.RDS'))
-
-# Final table
-# huxtable::huxreg(compare_tbl(list(list(m1, grf_out1, dml_out1),
-#                                   list(m2, grf_out2, dml_out2),
-#                                   list(m3, grf_out3, dml_out3),
-#                                   list(m4, grf_out4, dml_out4),
-#                                   list(m5, grf_out5, dml_out5),
-#                                   list(m6, grf_out6, dml_out6)),
-#                              tidy = F),
-#                  statistics = NA) %>%
-#   huxtable::insert_row(c('Control variables', 'No', 'Yes', 'No', 'Yes', 'No', 'Yes'), 
-#                        after = nrow(.) - 1) %>%
-#   huxtable::set_caption('Replication of Nussio (2024) Table 5: "Natural Experiment: Earthquake Exposure and Lynching"') %>%
-#   write_rds(here('replication', 'nussio_ne_tab.RDS'))
-# 
-# read_rds(here('replication', 'nussio_ne_tab.RDS'))
-```
-
-These simulations suggest that double robust methods with flexible machine learning algorithms may show some gains in bias reduction compared to traditional methods such as linear OLS regression.
-However, do these methods make a difference in practice?
-In this section, I replicate results from recent *American Sociological Review* articles using two double robust methods.
-I chose three papers that meet the following criteria: the authors were trying to estimate a causal effect, they used OLS or logistic regression, and they  posted replication code and data.
-
-The first paper I replicate is "Commitment through Sacrifice: How Longer Ramadan Fasting Strengthens Religiosity and Political Islam," by @aksoy_2022_commitment.
-Using the natural variation in daylight from year to year during Ramadan, the authors test the relationship between Ramadan fasting time and the vote share of Islamist political parties in Turkey.
-The second paper is "They Can’t All Be Stars: The Matthew Effect, Cumulative Status Bias, and Status Persistence in NBA All-Star Elections" [@biegert_2023_they].
-The authors use detailed records on NBA players' performance to study the effect of the previous year's All-Star nomination on being re-nominated in the current year.
-Lastly, I replicate "The 'Dark Side' of Community Ties: Collective Action and Lynching in Mexico" [@nussio_2024_dark].
-The author estimates the effect of community ties in Mexico on individual participation in lynching or lynching rates at aggregate levels.
-
-## Evaluation Strategy
-
-I replicate these papers using two double robust methods with machine learning.
-First, I use AIPW in conjunction with generalized random forests (GRF) using the `grf` package [@tibshirani_2024_grf].
-Second, I use a partially linear model for DML with a SuperLearner that, like above, harnesses ensemble learning with GLM, glmnet, and XGBoost, using the `DoubleML` package [@bach_2022_doubleml].^[In the Supplementary Material, I present the results of using these packages to estimate the full set of simulations shown above.
-Results are fairly similar to my own R code, though computation time is notably faster.] Note that AIPW with GRF allows for heterogeneous treatment effects, while this version of DML does not.
-I use packages rather than my own R code for two reasons.
-First, these packages calculate asymptotic standard errors without the need for bootstrapping, allowing straightforward comparison with the statistical significance of results in the original papers.
-Second, both packages allow clustering of standard errors, which all three papers employ.
-
-Two aspects of these replications deserve further explanation.
-First, it is common in social science to drop observations with missing data for some covariates, a technique called the "complete case method" or "listwise deletion." Two of these papers deal with missing data in this way -- by decreasing the sample size.
-Some machine learning methods, on the other hand, use missing data informatively [@mayer_2020_doubly]; the `grf` package allows covariates (but not the outcome or treatment assignment) to be missing, using missingness itself as a splitting criterion in growing trees.
-Hence for data with moderate levels of missingness, I allow `grf` to work with the entire dataset.
-For `DoubleML`, I use the same samples as in the original papers -- in these cases only observations with complete cases for a given regression model.
-An exception is Table 5 for @nussio_2024_dark, where the number of observations with missing control variables is far larger than the number without missing data; hence I drop incomplete cases for all analyses.
-I describe the exact procedures for handling missingness in the notes for each table of results in the Supplementary Material.
-
-The second aspect is fixed effects.
-Fixed effects are commonly used in linear models; beginning with a categorical variable with $k$ group labels, one hot encoding converts this to $k-1$ dichotomous variables, and these are entered into the regression linearly.
-These are meant to account for between-group differences [@firebaugh_2013_fixed].
-In the papers replicated here, @aksoy_2022_commitment use these types of fixed effects in all models, @biegert_2023_they use no fixed effects, and @nussio_2024_dark uses fixed effects in some models (details are in the table notes in the Supplementary Material).
-In many machine learning methods, categorical variables cannot be easily incorporated [@johannemann_2021_sufficient].
-Adding a large number of information-poor dichotomous variables to flexible tree methods like GRF and XGBoost does not have a fixed effects interpretation, since these methods can can interact any variable with any other and apply non-linear transformations.
-In cases where a researcher would want to use fixed effects for time and other variables with a natural ordering, these can be entered as a single continuous variable, whose effect the model will allow to vary nonlinearly.
-But categorical variables without a natural ordering -- such as individual or group fixed effects -- need special treatment.
-Recently, @clarke_2024_double have developed an extension to DML that incorporates group-level fixed effects.
-In the main paper, I do not adjust for individual or group fixed effects in the machine learning replications (even when the original paper's model does), but in the Supplementary Material I present two of Clarke and Polselli's approaches to incorporating fixed effects in DML.
-Results change very little from standard DML.
-
-## Results
-
-```{r replications, fig.height = 8, fig.cap = 'Replications of ASR papers using double robust machine learning methods. Bars represent 95-percent asymptotic confidence intervals.'}
-aksoy_list <- readRDS(here('replication', 'aksoy_rep.RDS')) 
-aksoy_list[[1]]$model <- '(1) Base'
-aksoy_list[[2]]$model <- '(2) Covariates'
-aksoy_list[[3]]$model <- '(3) Lagged dependent variable'
-
-biegert_list <- readRDS(here('replication', 'biegert_rep.RDS')) 
-biegert_list[[1]]$model <- '(1) No controls'
-biegert_list[[2]]$model <- '(2) Baseline confounders'
-biegert_list[[3]]$model <- '(3) Prior situation + performance'
-biegert_list[[4]]$model <- '(4) Current performance'
-biegert_list[[5]]$model <- '(5) Current situation'
-
-nussio_ind_list <- readRDS(here('replication', 'nussio_ind_rep.RDS')) 
-nussio_ind_list[[1]]$model <- '(1) Base'
-nussio_ind_list[[2]]$model <- '(2) Some controls'
-nussio_ind_list[[3]]$model <- '(3) All controls'
-nussio_ind_list[[4]]$model <- '(4) Geographical FE'
-
-nussio_ag_list <- readRDS(here('replication', 'nussio_ag_rep.RDS')) 
-nussio_ag_list[[1]]$model <- '(1) Base'
-nussio_ag_list[[2]]$model <- '(2) Some controls'
-nussio_ag_list[[3]]$model <- '(3) All controls'
-nussio_ag_list[[4]]$model <- '(4) Geographical FE'
-
-nussio_ne_list <- readRDS(here('replication', 'nussio_ne_rep.RDS')) 
-nussio_ne_list[[1]]$model <- '(1) Within 250 km of earthquake'
-nussio_ne_list[[2]]$model <- '(2) Within 250 km of earthquake, controls'
-nussio_ne_list[[3]]$model <- '(3) Earthquake damage'
-nussio_ne_list[[4]]$model <- '(4) Earthquake damage, controls'
-
-bind_rows(
-  mutate(bind_rows(aksoy_list), paper = 'A. Aksoy et al. (2022)'),
-  mutate(bind_rows(biegert_list), paper = 'B. Biegert et al. (2022)'),
-  mutate(bind_rows(nussio_ind_list), paper = 'C. Nussio et al. (2024) Table 2: Individual'),
-  mutate(bind_rows(nussio_ag_list), paper = 'D. Nussio et al. (2024) Table 4: Aggregate'),
-  mutate(bind_rows(nussio_ne_list), paper = 'E. Nussio et al. (2024) Table 5: Natural Experiment')
-  ) %>%
-  filter(term %in% c('Original', 'AIPW (GRF)', 'DML (SuperLearner)')) %>%
-  mutate(term = factor(term, levels = unique({.$term})),
-         paper = factor(paper, levels = unique({paper})),
-         model = factor(model, levels = rev(unique({.$model})))) %>%
-  ggplot(aes(x = model, y = estimate, color = term, shape = term)) +
-  geom_hline(yintercept = 0, color = 'grey') +
-  geom_pointrange(position = position_dodge(-0.7),
-                  aes(ymin = estimate - 1.96*std.error, ymax = estimate + 1.96*std.error)) + 
-  coord_flip() +
-  facet_wrap(~paper, scales = 'free', ncol = 1) +
-  labs(x = '', y = '') +
-  theme(legend.position = 'bottom')
-```
-
-Results of the replications are shown in Figure \@ref(fig:replications), with tables of coefficients and explanatory notes in the Supplementary Material.
-For each paper, I replicate the main results.
-I do not replicate models testing mechanisms, interactions, mediators, or placebos.
-
-The first paper, "Commitment through Sacrifice: How Longer Ramadan Fasting Strengthens Religiosity and Political Islam" [@aksoy_2022_commitment], finds an OLS coefficient of about 7, implying a half-hour increase in fasting time is associated with a 3.5 percentage point increase in Islamist vote share.
-As shown in Figure \@ref(fig:replications) Panel A, coefficients using the double robust methods are noticeably smaller (though not significantly different from the original coefficients).
-In Model 2, which includes covariates, the main coefficient is nonsignificant at the 5-percent level.
-In both cases, the double robust estimates are more precise, with smaller standard errors than the OLS results.
-
-The second paper, "They Can’t All Be Stars: The Matthew Effect, Cumulative Status Bias, and Status Persistence in NBA All-Star Elections" [@biegert_2023_they].
-The authors use logistic regression to estimate the effect of the previous year's All-Star nomination on being re-nominated in the current year.
-Panel B of Figure \@ref(fig:replications) shows the average marginal effects from the authors' original regressions alongside the double robust replications.
-Models 1 and 2 do not control for previous performance and find that a previous year's nomination increases the likelihood of being nominated by 45 to 60 percentage points.
-Model 3 isolates the effect of the previous year's nomination from performance in the previous year; the original paper found a much smaller coefficient once these controls were incorporated, giving a marginal effect of about 5 percentage points, but the double robust methods estimate large effect sizes, at 30 and 59 percentage points for AIPW (GRF) and DML (SuperLearner), respectively.
-Models 4 and 5 control for other current factors, and double robust estimates are somewhat smaller than in Model 3 but still much larger than the original paper's estimates.
-
-The third and final paper for replication is "The 'Dark Side' of Community Ties: Collective Action and Lynching in Mexico" [@nussio_2024_dark].
-I present his three main analyses as separate panels.
-In his first analyses, he looks at individual propensity to participate in a lynching, using the log number of names of people a respondent knows in his or her colonia (neighborhood) in Mexico City as the independent variable.
-In OLS models with and without controls, the author finds a coefficient of about 0.03 for the logged variable, implying that a one-percent increase in names known is associated with about 0.0003 percentage points greater likelihood of participating in a lynching.
-As shown in Panel C of Figure \@ref(fig:replications), For AIPW (GRF), coefficients and statistical significance are very similar to the original OLS coefficients.
-DML (SuperLearner), however, shows nonsignificant or negative effects.
-
-Panel D of Figure \@ref(fig:replications) replicates Nussio's [-@nussio_2024_dark] second analysis, which aggregates to the municipal level.
-Models estimate the effect of neighborly cooperation -- operationalized by the proportion of respondents who think that most neighbors help each other in problems related to electric lighting -- on the log municipal lynching rate.
-The original OLS estimate was fairly stable across models with controls, at about a one percentage point increase in neighborly cooperation associated with a two-percent increase in the lynching rate [$\exp(2/100) = 1.02$].
-This estimate is fairly stable across estimators, though (as shown in the Supplementary Material) this is one case where incorporating fixed effects in the DML models reduces coefficient sizes.
-
-Finally, Panel E of Figure \@ref(fig:replications) replicates Nussio's [-@nussio_2024_dark] natural experiment, where he estimates the effect of the Puebla earthquake on September 19, 2017, on the number of lynching events in a municipality, using panel data from 2000 to 2020.
-The original OLS models found that municipalities within 250 km of the earthquake or that experienced earthquake damage experienced an increase of about 0.1 in the number of lynchings in years after 2017 (the mean yearly lynchings per municipality is 0.034).
-While models for AIPW (GRF) are fairly similar to the original OLS estimates, DML (SuperLearner) estimates are double the original estimates.
-
-These replications show that results from the original OLS or logistic regressions that these papers employed are fairly robust.
-In most cases, effect sign and statistical significance are consistent across the original and double robust estimators.
-Notably, effect sizes for @aksoy_2022_commitment in the double robust models are smaller than the OLS estimates, reaching nonsignificance in one case.
-DML (SuperLearner) estimates for Nussio's [-@nussio_2024_dark] individual analysis change sign and significance, while the AIPW (GRF) estimates are close to the OLS estimates.
-However, the simulation results presented in the previous section suggested that the DML (SuperLearner) estimator has higher RMSE than both OLS and AIPW (GRF) (Figure \@ref(fig:dorie-results-rmse)), so perhaps the original results are reliable.^[The Supplementary Material shows that the DoubleML package with the SuperLearner has higher bias and RMSE in the simulations than my own R code.] Overall, these replications highlight the importance of testing the robustness of estimates to different models; double robust, machine learning methods sometimes do produce substantively different results from traditional methods.
-
 <!-- # LaLonde NSW Data -->
@@
 This paper aims to provide an introduction to and evaluation of double robust methods for covariate adjustment in causal inference.
-By comparing AIPW, TMLE, and DML to more traditional statistical methods such as OLS and PSM as well as flexible "single robust" methods such as G-computation and the Lin estimator, it allows evaluation of whether these methods are worth the effort and (computational) time for social scientists to adopt them.
+By comparing the double robust methods of AIPW, TMLE, and DML to more traditional statistical methods such as OLS and PSM as well as flexible "single robust" methods such as G-computation and the Lin estimator, it allows evaluation of whether these methods are worth the effort and (computational) time for social scientists to adopt them.
 
 Results are nuanced.
-In the full range of simulated data, AIPW and TMLE with a SuperLearner or GRF are able to obtain smaller RMSE than OLS or PSM.
-However these differences are quite small, and G-computation with the same flexible machine learning methods performs just as well as the double robust methods.
+In the full range of simulated data, AIPW and TMLE with a SuperLearner or GRF are able to obtain lower error than OLS or PSM.
+However these differences are quite small, and non-double-robust G-computation with the same flexible machine learning methods performs just as well as the double robust methods.
 DML does not perform as well as AIPW or TMLE (however, a version of DML that allows for heterogeneous effects might perform better; see Chernozhukov et al.
@@
 The Lin estimator performs slightly better than OLS or PSM, without any increase in computation time.
-Methods relying on logit models to estimate propensity weights have the most error; researchers should use these methods with caution.
+Double robust methods relying on logit models to estimate propensity weights have the greatest error, likely due to small estimated propensity scores; researchers should use these methods with caution.
 
 Methods that come out on top in the full range of simulations also tend to do the best regardless of the data generating process, though the Lin estimator and OLS rise in the rankings when the true treatment and outcome models are linear.
-AIPW, TMLE, and G-computation with a SuperLearner or GRF perform the best, followed closely by the Lin estimator, OLS, and PSM.
 As sample size varies, the same rank order generally holds, though traditional methods are unable to produce estimates in small samples when there are many covariates, while the double robust methods are able to do so.
 
-In replications of prominent sociology articles, these methods do sometimes change conclusions.
+<!-- In replications of prominent sociology articles, these methods do sometimes change conclusions.
 In the examples given in this paper, coefficients shift somewhat and sometimes change sign and significance.
@@
 This may be related to the higher error shown in the simulations for DML; this method may be somewhat more unstable.
-Overall, these replications suggest that researchers should test the robustness of their results using a variety of different models and estimators.
+-->
+
+What might explain the variation in performance across methods and estimators?
+One major reason could be the presence of treatment effect heterogeneity, which is high in 18 out of the 20 DGPs studied here.
+When the treatment effect does not vary systematically by other covariates, then OLS regression correctly targets the ATE.
+However, when the treatment effect is heterogeneous -- meaning it depends on the values of other covariates -- the OLS estimate will diverge from the ATE [@angrist_2009_mostly; @hazlett_2024_demystifying].
+In this case, it is important to use a method that allows the treatment effect to vary in this way.
+Two of the double robust methods presented here -- AIPW and TMLE -- allow for this heterogeneity, and they are the top performing methods.
+The "single robust" G-computation also accounts for heterogeneity by estimating separate models for treated and untreated groups, and it performs nearly as well as AIPW and TMLE.
+The Lin estimator constitutes another heterogeneity-robust option and performs fairly in these simulations (recall that G-computation with OLS regressions is equivalent to the Lin estimator [@hazlett_2024_demystifying]).
+Although the Lin estimator's underling OLS regressions make the strong assumption of linearity, this assumption may regularize estimates in a way that actually reduces average prediction error.
+Overall, these results are in line with recent attention in sociology to heterogeneous treatment effects and modeling them appropriately [@brand_2021_uncovering; @zhou_2022_attendance; @luo_2021_heterogeneous].
 
 This paper has a number of limitations.
-First, although it considers some of the most popular double robust, machine learning, traditional, and single robust methods, there are many methods that it could not evaluate, including variations and extensions of the three methods.
-Future research could also consider the efficacy of calibration methods such as Entropy Balancing that have shown to be double robust (under certain assumptions) despite not explicitly modeling the outcome or treatment assignment [@zhao_2017_entropy].
-Second, although the simulations are meant to cover a wide range of data generating processes, they only consider continuous outcomes and binary treatments; simulations with binary or categorical outcomes and continuous or multi-armed treatments may yield different results.
+First, although it considers some of the most popular double robust, machine learning, traditional, and single robust methods, there are many methods that it does not evaluate, including variations and extensions of the three methods (such as a heterogeneity-robust DML [@chernozhukov_2018_double, p.
+C35]).
+Future research could also consider the efficacy of another set of double robust methods: Calibration methods such as Entropy Balancing have been shown to be double robust (under certain assumptions) despite not explicitly modeling the outcome or treatment assignment [@zhao_2017_entropy].
+Second, although the simulations cover a wide range of data generating processes, they only consider continuous outcomes and binary treatments; simulations with binary or categorical outcomes and continuous or multi-armed treatments may yield different results.
+Third, this paper has considered only cross-sectional data; in longitudinal settings with time-varying confounders, double robust methods may more clearly outperform other methods [@tran_2019_double].
 Finally, in considering only functional form misspecification, the simulations in this paper do not consider situations where ignorability does not hold.
@@
 
-In conclusion, if researchers want small gains in accuracy, they may opt for AIPW, TMLE, or G-computation with a flexible machine learning algorithm.
+In conclusion, while double robust methods are useful for social scientists to understand due to their increasing popularity, they may not necessarily perform better than other methods.
+For the greatest accuracy, results here suggest that researchers should opt for AIPW, TMLE, or the non-double-robust G-computation in conjunction with a flexible machine learning algorithm.
+If computation time is a concern -- for example, if a researcher is calculating bootstrapped estimates, using replicate weights for complex survey data, or dealing with an extremely large sample -- then the Lin estimator is a good choice, with robustness to heterogeneous treatment effects and very low computation time.
+On the other hand, in most of the simulations presented here, standard OLS or PSM estimates do not diverge widely from top-performing methods.
+Studies that rely on these traditional methods may still have fairly accurate results.
+
+<!-- Rather than choosing the most flexible or double robust model, researchers should choose a model that is robust to heterogeneous effects, if they have any suspicion that such effects exist.
+Researchers may opt for AIPW, TMLE, or G-computation with a flexible machine learning algorithm, which produce the most accurate results in this study.
+-->
+
+<!-- if researchers want small gains in accuracy, they may opt for AIPW, TMLE, or G-computation with a flexible machine learning algorithm.
 But these methods are computationally costly, taking as long as two minutes per dataset of 4,802 observations and 52 covariates, while OLS, PSM, and the Lin estimator each take a fraction of a second.^[The `grf` and `DoubleML`  packages are able to achieve faster computation time, at under 10 seconds in these samples.
-See tables of results in the Supplementary Material.] While double robust methods are useful for social scientists to understand, in most applications, OLS or PSM provide similar results.
-In certain circumstances, however, these double robust methods may be a better choice.
+See tables of results in the Supplementary Material.] While this computation time may seem trivial, it can balloon in larger samples -- as Table S3 in the Supplemental Material shows, GRF and SuperLearner estimators on samples of 96,040 took over 30 minutes to run, while OLS took only one second.
+In large complex survey data where proper standard errors computation requires the use of replicate weights, repeated estimation with these flexible machine learning estimators may result in unacceptably long computation time.
+-->
+
+<!-- In certain circumstances, however, these double robust methods may be a better choice.
 Especially when paired with a highly flexible estimator like a SuperLearner or GRF, these methods may be slightly more accurate, and they can be useful when the number of covariates is high or even exceeds the number of observations.
 In longitudinal settings with time-varying confounders, they may be more helpful [@tran_2019_double].
-They can also be useful as a sensitivity check; if researchers obtain similar estimates across traditional and double robust methods, they can be more confident in the reliability of their estimates.
+-->
 
